### 2020-03-23 manuscript.Rmd
Opening paragraph

---
title             : "Mapping the predictors of adolescent emotion dysregulation: A text-mining based systematic review"
shorttitle        : "ADOLESCENT EMOTION DYSREGULATION"

author: 
  - name          : "Caspar J. van Lissa"
    affiliation   : "1,2"
    corresponding : yes    # Define only one corresponding author
    address       : "Padualaan 14, 3584CH Utrecht, The Netherlands"
    email         : "c.j.vanlissa@uu.nl"

affiliation:
  - id            : "1"
    institution   : "Utrecht University faculty of Social and Behavioral Sciences, department of Methodology & Statistics"
  - id            : "2"
    institution   : "Open Science Community Utrecht"

authornote: |
  Caspar van Lissa, Department of Methodology and Statistics, Utrecht
  University, P.O. Box 80140, 3508 TC, Utrecht, The Netherlands. E-mail:
  C.vanLissa@uu.nl. This work is supported by a NWO Veni grant (NWO
  grant number VI.Veni.191G.090).

abstract: |

keywords          : "keywords"
wordcount         : "X"

bibliography      : ["r-references.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library("papaja")
library(bibliometrix)
library(revtools)
library(bib2df)
```
<!-- Reviewer suggestions:
Kristin Buss -->

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

A key developmental challenge in adolescence is acquiring mature emotion regulation skills [croneUnderstandingAdolescencePeriod2012; zimmermannEmotionRegulationEarly2014]. Emotion regulation is integral to mental health[aldaoEmotionregulationStrategiesPsychopathology2010; schaferEmotionRegulationStrategies2017; braetEmotionRegulationChildren2014] and social functioning [reindlSocializationEmotionRegulation2016]. There is mounting evidence, however, for a "maturity gap" in middle-adolescence [craccoEmotionRegulationChildhood2017; caseyBrakingAcceleratingAdolescent2011; croneUnderstandingAdolescencePeriod2012]: A developmental asymmetry between emotional and regulatory brain circuits, which motivates most youngsters to seek out challenges in life and love, but renders some of them vulnerable to emotion dysregulation. For as many as one in five adolescence, this stage marks the onset of mental illness, which can persist throughout the life course [see leeAdolescentMentalHealth2014]. Despite burgeoning empirical interest in adolescent emotion regulation, the literature is somewhat fragmented. There have been only few notable efforts to provide an encompassing framework of the risk factors and environmental hazards render adolescents susceptible to emotional difficulties [coe-odessEmergentEmotionsAdolescence2019; bussTheoriesEmotionalDevelopment2019; riedigerEmotionRegulationAdolescence2014]. These efforts at unifiaction have all been performed in a top-down, theory-driven manner. The present study instead takes an inductive approach to map the correlates of adolescents' emotion regulation. From this mapping, we proceed to classify correlates as potential risk factors, manifestations, and outcomes of adolescent emotion regulation. The results provide a conceptual overview of the existing literature, can help identify blind spots in existing theory, and might inspire new hypotheses to guide future deductive research.

Unfortunately, there is little theory about which risk factors and environmental hazards render adolescents susceptible to emotional difficulties11

Initially, much of the research on emotion regulation focused on either adulthood or early childhood. In recent years, however, a substantial body of research on emotion regulation in adolescence has accrued.

What are the predictors of emotion regulation in adolescence?

* Emotion regulation is important for mental health and social relationships
* Adolescence is a key developmental period
*

Emotion regulation can be defined as the ability to modulate emotional experience and expression through automatic or deliberate processes.

Substantial research has addressed issues related to emotion regulation, because it plays a central role in mental health and social functioning throughout the life course. Recent findings suggest that adolescence is a sensitive period for the development of mature emotion regulation skills.

Most of the literature has addressed emotion regulation in adult or infant samples. A smaller, but substantial, portion of the literature has examined emotion regulation in adolescents.

Wat is het vershcil dat het verschil maakt?

on adolescent emotion regulation development is limited27–29. The field is therefore at an impasse: We know that some adolescents are more susceptible to emotion dysregulation than others, but lack tools and theory to identify important predictors of individual development30.

<!-- NIET TEVEEL OVER THEORIE PRATEN; IK KIJK NIET NAAR THEORIE. IK KIJK NAAR FACTOREN DIE IN VERBAND GEBRACHT WORDEN MET EMOTIEREGULATIE. -->
<!--The life phase of adolescence differs qualitatively from both childhood and adulthood. It is therefore not sufficient to extend -->

Influences on emotion regulation (Riediger Klipker)
* Neurophysiological development 
* Familial context

There are sufficient *relevant* theories, but few explicitly tailored to adolescence, and few explicit (define explicit).

Despite widespread interest in emotion regulation in adolescence, there is a lack of explicit theories about which risk factors and environmental hazards render adolescents susceptible to emotional difficulties. Some theories can be considered relevant, but these theories are rarely explicit enough to generate specific predictions. 
As many as one in five adolescents experiences severe emotional problems. A key question is therefore which factors render adolescents at-risk for difficulties in emotion regulation.

Unfortunately, relevant theory on adolescent emotion regulation development is limited27–29. The field is therefore at an impasse: We know that some adolescents are more susceptible to emotion dysregulation than others, but lack tools and theory to identify important predictors of individual development30.

inductive approach, thereby facilitating a more complete understanding of developmental processes, and nourishing theory formation

My work addresses this lacuna by taking an inductive approach to theory formation; paying special attention to between-person differences. This paves the way for a new wave of person-centered research

MAKE SURE THAT DICTIONARY TERMS ARE SEQUENTIALLY IMPLEMENTED
Key questions:
Why focus on theory?
Why focus on emotion regulation specifically, instead of other aspects of emotional development?

* Biological determinants
* Social determinants

* Existing developmental theories do not focus on adolescence (rather, on adults, or development in infancy and childhood). However, many interesting emotion-related things happen in adolescence.

Important:
Buss: theories of emotion and emotional development
Cracco: Evidence for a maladaptive shift in emotion regulation in adolescence
Zimmermann & Iwanski: Dip in adolescence

Sroufe 1995: Development of emotion regulation until preschool age
"the key progression in emotional regulation is from caregiver-orchestrated
regulation to dyadic regulation to self-regulation."
* attachment - dyadic regulation of emotion (Sroufe 1996)
* Caregiver-guided self-regulation 
* Autonomous self-regulation
***** HOWEVER: In adolescence, regulatory brain regions still developing!!!! So Sroufe stops too early

Polyvagal theory Porges 1995

## Theories of adolescent emotion dysregulation

The present paper aims to develop a nomological network of the constructs related to adolescent emotion dysregulation. A nomological network is a diagrammatic representation of a phenomenon; it is a proto-theoretical device that describes relationships between constructs relevant to the theory (REF: Cronbach & Meehl 1955; McKenna, 2006; Alavi 2018). It can be useful as a precursor to a more explicit theory of the phenomenon. The present paper uses an inductive approach to develop this nomological network. First, we use a systematic search to elicit a corpus of relevant literature. Second, we extract constructs from the corpus. Third, we use a dictionary to pare down the extracted constructs to meaningful superordinate categories. Fourth, we map interrelations between these constructs. Fifth, we classify contstructs as potential predictors or outcomes, and we categorize predictors by level of analysis (CJ: Sameroff, which level of biopsychosocial).

t, using text mining to map potential predictors of adolescent emotion dysregulation.

identify relevant constructs  of adolescents’ emotion regulation development, and moderators of parents’ role therein. The resulting insights are consolidated into theory.

The present study intends to map the extant literature 
First, I will systematically review predictors currently considered relevant in the adolescent emotion regulation literature.

# Methods

## Search strategy

All searches were conducted on Web of Science. The search strategy was based on procedures described by Janneke Staaks on https://osf.io/49t8x/, DOI:10.17605/OSF.IO/49T8X, accessed on 27-01-2020. First, we manually constructed a reference set of 15 articles. Then we constructed a search string to retrieve these articles from Web of Science. The search was overly inclusive, returning 29 records, but these were all highly relevant, so we used all 29 results as reference set. Next, we tested our search string, which consisted of synonyms of emotion regulation and adolescence:
```
TS=("emotio* regulation" OR "anger regulation" OR "sadness regulation" OR "emotion* competence" OR "emotion* adjustment" OR "emotio* dysregulation" OR "anger dysregulation" OR "sadness dysregulation" OR "emotio* problem*" OR "emotion* maladjustment") AND TS=(adolescent* OR teen* OR pubert* OR youth)
```
This string returned 6653 results, and matched 25 of the 29 records in the reference set. Three search terms could be added to match all 29 reference set items. The terms `"emotio* socialization" OR "emotio* processes"`, as synonyms of emotion regulation, added 191 new hits. However, many of these hits were not directly relevant to emotion regulation. The term `"development*`, as synonym of adolescence, added 3628 new hits, many of which were not focused on the age range of adolescence. We thus deemed these terms to be overly inclusive, and proceeded with the original search string.
```{r readrecs}
filenam <- "recs_6653.RData"
if(!file.exists(filenam)){
  f <- list.files("./recs/18-3-2020/", full.names = TRUE)
  f <- readFiles(f)
  recs <- convert2df(f)
  saveRDS(recs, filenam)
} else {
  recs <- readRDS(filenam)
}
```

## Deduplication

```{r removeduplicates}
filenam <- "unique_recs.RData"
if(!file.exists(filenam)){
  recs$doi <- recs$DI
  recs$doi[is.na(recs$doi)] <- paste0("fake", 1:sum(is.na(recs$doi)))
  if(any(duplicated(recs$doi))){
    recs$doi[duplicated(recs$doi)|duplicated(recs$doi, fromLast = T)]
    dup_doi <- duplicated(recs$doi)
    recs <- recs[!dup_doi, ]
  }
  recs$title <- recs$TI
  # locate and extract unique references
  potential_dups <- find_duplicates(recs, match_variable = "title", match_function = "stringdist", threshold = 5, to_lower = TRUE, remove_punctuation = TRUE)
  unique_recs <- extract_unique_references(recs, matches = potential_dups)
  saveRDS(unique_recs, filenam)
  write.csv(data.frame(dup_doi = sum(dup_doi), dup_title = (nrow(recs)-nrow(unique_recs))-sum(dup_doi)), "dups.csv")
} else {
  unique_recs <- readRDS(filenam)
  dups <- read.csv("dups.csv")
}
unique_recs$id_num <- 1:nrow(unique_recs)
```
Duplicates were detected based on exact DOI matches (`r dups[["dup_doi"]]` duplicates), and title similarity (`r dups[["dup_title"]]` duplicates). Manual screening in Rayyan resulted in the removal of an additional 13 duplicates.

## Screening

```{r}
head(unique_recs$SN)
df_screen <- unique_recs[, c("id_num", "TI", "AB")]
names(df_screen) <- c("id_num", "title", "abstract")
write.csv(df_screen, file = "asreview.csv", row.names = FALSE, fileEncoding = "UTF-8")
df_screen <- unique_recs[, c("id_num", "TI", "AU", "SO", "SN", "VL", "IS", "BP", "PY", "PU", "DI", "AB")]
names(df_screen) <- c("key", "title", "authors", "journal", "issn", "volume", "issue", "pages", "year", "publisher", "url", "abstract")
write.csv(df_screen, file = "rayyan.csv", row.names = FALSE)

```

Unknown. In the initial screening, we will include all studies 1) returned by the specified search strategy 2) in the specified databases 3) for which abstracts are available. We will manually screen a maximum of 500 abstracts, and have the remainder scanned by ASReview.

In the initial screening, we will include all studies 1) returned by the specified search strategy 2) in the specified databases 3) for which abstracts are available. We will manually screen a maximum of 500 abstracts, and have the remainder scanned by ASReview.

### Reference set

Our reference set is documented in `reference_set.bib`.

```{r removeduplicates}
filenam <- "title_sim.RData"
if(!file.exists(filenam)){
  recs$doi <- recs$DI
  recs$doi[is.na(recs$doi)] <- paste0("fake", 1:sum(is.na(recs$doi)))
  if(any(duplicated(recs$doi))){
    recs <- recs[!duplicated(recs$doi), ]
  }
  recs$title <- recs$TI
  # locate and extract unique references
  potential_dups <- find_duplicates(recs, match_variable = "title", match_function = "stringdist", threshold = 5, to_lower = TRUE, remove_punctuation = TRUE)
  unique_recs <- extract_unique_references(recs, matches = potential_dups)
  saveRDS(unique_recs, filenam)
} else {
  unique_recs <- readRDS(filenam)
}
```

\newpage

# References
```{r create_r-references}
r_refs(file = "r-references.bib")
```

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id = "refs"></div>
\endgroup

### 2020-05-18 Manuscript2.Rmd
Synchronize remote

---
title             : "Mapping the predictors of adolescent emotion dysregulation: A text-mining based systematic review"
shorttitle        : "Title"

author: 
  - name          : "Caspar J. van Lissa"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "my@email.com"
  - name          : "Ernst-August Doelle"
    affiliation   : "1,2"

affiliation:
  - id            : "1"
    institution   : "Wilhelm-Wundt-University"
  - id            : "2"
    institution   : "Konstanz Business School"

authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

  Enter author note here.

abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.

  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.

  One sentence clearly stating the **general problem** being addressed by  this particular study.

  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).

  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.

  One or two sentences to put the results into a more **general context**.

  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.

  <!-- https://tinyurl.com/ybremelq -->

keywords          : "keywords"
wordcount         : "X"

bibliography      : ["r-references.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library("papaja")
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

# Methods
We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study. <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->

## Participants

## Material

## Procedure

## Data analysis
We used `r cite_r("r-references.bib")` for all our analyses.

# Results

# Discussion

\newpage

# References
```{r create_r-references}
r_refs(file = "r-references.bib")
```

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id="refs" custom-style="Bibliography"></div>
\endgroup

### 2020-05-18 manuscript.Rmd
Synchronize remote

@@
 ---
-title             : "Mapping the predictors of adolescent emotion dysregulation: A text-mining based systematic review"
+title             : "Mapping factors associated with adolescents' emotion dysregulation: A text-mining based systematic review"
 shorttitle        : "ADOLESCENT EMOTION DYSREGULATION"
@@
 abstract: |
+  Test me
 
@@
 wordcount         : "X"
-
-bibliography      : ["r-references.bib"]
-
+bibliography      : ["veni_sysrev.bib"]
 floatsintext      : no
@@
 draft             : no
-
 documentclass     : "apa6"
@@
 
-A key developmental challenge in adolescence is acquiring mature emotion regulation skills [croneUnderstandingAdolescencePeriod2012; zimmermannEmotionRegulationEarly2014].
-Emotion regulation is integral to mental health[aldaoEmotionregulationStrategiesPsychopathology2010; schaferEmotionRegulationStrategies2017; braetEmotionRegulationChildren2014] and social functioning [reindlSocializationEmotionRegulation2016].
-There is mounting evidence, however, for a "maturity gap" in middle-adolescence [craccoEmotionRegulationChildhood2017; caseyBrakingAcceleratingAdolescent2011; croneUnderstandingAdolescencePeriod2012]: A developmental asymmetry between emotional and regulatory brain circuits, which motivates most youngsters to seek out challenges in life and love, but renders some of them vulnerable to emotion dysregulation.
-For as many as one in five adolescence, this stage marks the onset of mental illness, which can persist throughout the life course [see leeAdolescentMentalHealth2014].
-Despite burgeoning empirical interest in adolescent emotion regulation, the literature is somewhat fragmented.
-There have been only few notable efforts to provide an encompassing framework of the risk factors and environmental hazards render adolescents susceptible to emotional difficulties [coe-odessEmergentEmotionsAdolescence2019; bussTheoriesEmotionalDevelopment2019; riedigerEmotionRegulationAdolescence2014].
-These efforts at unifiaction have all been performed in a top-down, theory-driven manner.
-The present study instead takes an inductive approach to map the correlates of adolescents' emotion regulation.
+<!-- Development and Psychopathology is the most relevant source of articles reviewed herein
+Most Relevant Sources
+
+                                                       Sources        Articles
+1  DEVELOPMENT AND PSYCHOPATHOLOGY                                         120
+
+on adolescent emotion regulation development is limited27–29.
+The field is therefore at an impasse: We know that some adolescents are more susceptible to emotion dysregulation than others, but lack tools and theory to identify important predictors of individual development30.
+-->
+
+<!-- Emotion regulation in adolescence is important -->
+A key developmental challenge in adolescence is acquiring mature emotion regulation skills [@croneUnderstandingAdolescencePeriod2012; @zimmermannEmotionRegulationEarly2014].
+Emotion regulation is integral to mental health[@aldaoEmotionregulationStrategiesPsychopathology2010; @schaferEmotionRegulationStrategies2017; @braetEmotionRegulationChildren2014] and social functioning [@reindlSocializationEmotionRegulation2016].
+For as many as one in five people, adolescence marks the onset of emotion regulation-related mental illness, which can persist throughout the life course [see @leeAdolescentMentalHealth2014].
+It is therefore crucial to identify which risk factors and environmental hazards render some adolescents more susceptible to emotional difficulties than others.
+Although there is an abundance of empirical work on adolescents' emotion regulation, the literature is somewhat fragmented, as the topic has been investigated from different (sub)disciplines.
+This study seeks to overcome this limitation by mapping all factors currently thought to be relevant to adolescent emotion regulation, based on a systematic review and bibliographic analysis.
+<!-- Ergens anders: Similarly, although there are several *relevant* theories, there is no specific theoretical framework to guide research on adolescents' emotion regulation.
+Although theory development is beyond the scope of this paper, we set out to generate a proto-theoretical nomological network of the potential risk factors, manifestations, and outcomes of emotion regulation in adolescence.
+We discuss how this nomological network relates to existing relevant theory, and conclude with recommendations for future theory-generating efforts.-->
+
+## Why adolescence is an important life phase for emotion regulation
+
+Adolescence is defined as a life phase ranging from pubertal onset to adult-like independence [@steinbergAgeOpportunityLessons2014].
+This definition invokes both biological- and socio-cultural factors.
+It has been argued that, due to accellerated pubertal onset and delayed transitions to adult roles, adolescence now ranges from 10-24 years in the modern Western world [@sawyerAgeAdolescence2018].
+
+<!-- From Barriola:
+* adolescence, more than adulthood or childhood, is characterized by frequent and intense emotions (Larson et al. 1980; Larson and Lampmanpetraitis 1989).
+* signiﬁcant psychosocial changes that call for an increase in sophistication of ER strategies (Steinberg 2005)
+* novel stressors associated with social relationships, including pressures to conform to adult expectations relating to maturity, educational achievement, gender appropriate conduct, and other socially competent behaviors (Yap et al.
+2007)
+* Additionally, adolescents have an increased orientation toward autonomy (Spear 2000) including autonomous emotional regulation-->
+
+Adolescence is increasingly seen as a developmentally sensitive period for mature emotion regulation skills.
+During this period, children experience rapid biological, cognitive, and social changes that prompt new emotional experiences, and tax existing regulatory abilities [@steinbergAgeOpportunityLessons2014].
+At the same time, the staggered development of motivational-emotional and regulatory brain circuits gives rise to a maturity gap, where youngsters pursue new experiences in life and love, without being fully prepared to cope with the emotional outcomes [@croneUnderstandingAdolescencePeriod2012].
+Due to these coalescing changes, adolescents display a restricted repertoire of emotion regulation strategies compared to younger or older individuals [@zimmermannEmotionRegulationEarly2014].
+Consequently, adolescents experience more frequent and intense (negative) emotions than children or adults [see @silkAdolescentsEmotionRegulation2003].
+The literature thus paints a picture of adolescence as a chrysalis for emotional development: Children enter this stage with emotion regulation skills adapted to the challenges of childhood.
+During adolescence, emotional systems are rearranged substantially.
+These changes render adolescents temporarily vulnerable to emotional dysregulation, but ultimately serve a functional role in acquiring mature emotion regulation skills.
+Eventually, most adolescents emerge ready to take on the challenges of early adulthood.
+Unfortunately, a sizeable proportion of adolescents instead manifests enduring emotional difficulties.
+
+<!--
+* intense negative emotions in daily life (Silk, Steinberg, & Morris, 2003) 
+* unstable peer or romantic relationships (Furman & Collins, 2009)
+* decrease in perceived support from parents (Furman & Buhrmester, 1992).
+* early adolescence is characterized by a higher rate of conflicts with parents (Laursen, Coy, & Collins, 1998)
+* higher variability of negative emotions compared to late adolescence (Larson, Moneta, Richards, & Wilson, 2002).
+* relative to other developmental stages, adolescence involves a particularly large number of transitions, novel situations, and new stimuli, physical, cognitive, emotional, and social development—particularly in early and mid-adolescence (Seiffge-Krenke, 2000)
+-->
+
+## The consequences of difficulties in emotion regulation
+
+<!--Acquiring mature emotion regulation abilities is important, because t-->The consequences of difficulties in emotion regulation are extensive, well-documented, and persist throughout the life course.
+Meta-analyses indicate that such difficulties are associated with externalizing, and more strongly, with internalizing psychopathology [@aldaoEmotionregulationStrategiesPsychopathology2010; @schaferEmotionRegulationStrategies2017].
+Individuals who engage in maladaptive emotion regulation strategies also experience more negative emotions, diminished well-being, and greater strain in interpersonal relationships [@grossIndividualDifferencesTwo2003a; @bellRelationshipsInputsOutputs2000].
+<!--Adolescence also appears to be a key period for developing mature emotion regulation skills - but not all adolescents do so successfully.
+As many as one in five adolescents instead develop severe emotional difficulties.--> Given the prevalence of emotional difficulties and their extensive implications for individual mental health, wellbeing, and social functioning, and downstream cost to society as a whole [@leeAdolescentMentalHealth2014], it is essential to have a solid understanding of the risk factors associated with adolescents' emotion regulation difficulties.
+
+## Existing relevant theory
+
+Theory is of paramount importance when seeking to understand or explain a phenomenon.
+Although there are many relevant theories, none have specifically addressed emotion regulation development in adolescence.
+Several recent publications have undertaken the monumental task of comprehensively reviewing theory relevant to emotional development [@bussTheoriesEmotionalDevelopment2019; @riedigerEmotionRegulationAdolescence2014].
+Thanks, in part, to their efforts, we can provide a summary review of the theoretical landscape as context for our empirical contribution.<!--Several recent publications have undertaken the monumental task of providing a comprehensive overview of theories of emotional development [e.g., @bussTheoriesEmotionalDevelopment2019; @holodynskiDevelopmentEmotionsEmotion2006; @riedigerEmotionRegulationAdolescence2014], and of the empirical work pertaining to emotions in adolescence [@coe-odessEmergentEmotionsAdolescence2019].
+-->
+Two theories widely invoked to frame research on development, including emotional development, are Bronfenbrenner's bioecological model, and Sameroff's transactional model.
+Bronfenbrenner's model [@bronfenbrennerBioecologicalModelHuman2007] describes how the environment shapes individual development.
+Each individual is imbued with certain biological predispositions, and develops over time, in interaction with contextual influences.
+These influences range from the microsystem, composed of those people close to the individual, to the macrosystem, consisting of indirect political and economic influences, to the exosystem, consisting of cultural norms and values.
+Sameroff's model is somewhat compatible with the bioecological model [@sameroffUnifiedTheoryDevelopment2010], but focuses more on the interplay between nature and nurture.
+It conceptualizes development as a product of reciprocal influences between the child and the environment.
+Sameroff distinguishes between proximal influences, for instance, through parents (the microsystem in Bronfenbrenner's model), and distal influences; structural factors indirectly shaping development, like socio-economic status, schools, and the community (macro- and exosystem).
+With increasing age, distal influences gradually gain ground on proximal influences.
+
+Turning now towards theories specifically addressing emotion regulation in adolescence, Hall's notion of "storm and stress" is one of the oldest [see @arnettAdolescentStormStress1999].
+It describes how hormonal changes diminish self-control and increase reactivity, leading to difficulties in emotion regulation, conflict with parents, and risky behavior.
+Recent work provides a more nuanced perspective on this theory.
+For example, although the notion of diminished self-control and increased emotional reactivity has been upheld, it has been recast as a necessary change that facilitates emotional maturation [@croneUnderstandingAdolescencePeriod2012], at the risk of emotional disturbance [@arnettAdolescentStormStress1999; @leeAdolescentMentalHealth2014].
+More recently, Sroufe [-@sroufeEmotionalDevelopmentOrganization1995] presented a theory focused on normative emotional development in early childhood.
+It argues that, as children grow older, their increasing self-regulatory abilities drive a transition from external emotion regulation by primary caregivers towards autonomous emotion regulation.
+This theory focuses on two drivers of development: social and cognitive influences.
+Social influences mainly occur through parents' co-regulation, parenting behaviors, and parent-child attachment.
+Cognitive influences occur through the development of the central nervous system (CNS), cognition, and self-regulation.
+Several other theories, introduced below, have extemporized on these sources of influence.
+
+The emphasis on neorocognitive development as a driver of emotional development, including emotion regulation development, is echoed in several other models.
+For example, polyvagal theory closely links emotional experience - and regulation - to autonomous nervous system functioning [@porgesOrientingDefensiveWorld1995].
+A more recent neorocognitive theory, with substantial relevance to adolescents' emotion regulation development, is Crone and Dahl's model of social-affective engagement and goal flexibility [@croneUnderstandingAdolescencePeriod2012].
+This theory is based on the notion of a "maturity gap" in middle-adolescence, arising from a developmental asymmetry between motivational and inhibitory brain circuits [@craccoEmotionRegulationChildhood2017; @caseyBrakingAcceleratingAdolescent2011].
+However, it sets out to explain - to a greater extent than other writings - adolescents' diverging destinies; the question why some youngsters flourish while others languish.
+Crone and Dahl argue that adolescents' cognitive engagement is dynamically responsive to social and motivational goal salience.
+This flexibility, on the one hand, prepares adolescents to effectively engage cognitive systems in novel challenging situations in a way that facilitates developing mature regulatory abilities.
+On the other hand, it places them at risk to act impulsively in pursuit of peer approval.
+This theory focuses primarily on cognitive factors and the role of peers, with less attention to factors such as parenting.
+
+A theory focused specifically on parents' role in emotion regulation development is Morris' tripartite model [-@morrisRoleFamilyContext2007].
+It describes three pathways through which parents shape emotion regulation development: Through observation and modeling, parenting practices, and the emotional family climate, which in turn involves attachment and marital relationship quality.
+Morris and colleagues also emphasize the relevance of fathers and siblings, and others have adapted the tripartite model to describe the role of peers in adolescents' emotion regulation development [@reindlSocializationEmotionRegulation2016].
+
+Aside from theories of emotional development, theories of the phenomenon of emotion regulation are also somewhat relevant.
+One influential theory is Gross' [-@grossHandbookEmotionRegulation2013] process model, which describes the process of emotion regulation, from eliciting cue to ultimate response.
+Individuals modulate the different stages of this process using strategies, consciously or otherwise.
+The effectiveness, desireability, and consequences of different strategies depend on the cultural context [see @bariolaChildAdolescentEmotion2011].
+Similar to Gross' theory, the social information processing theory of emotion also describe the role of intrapsychic processes and strategies in emotion experience and reulation [@lemeriseIntegratedModelEmotion2000].
+
+Another theory worth mentioning in this context is @holodynskiDevelopmentEmotionsEmotion2006's internalization model of emotional development.
+It applies Vygotsky's theory of development to the domain of emotion, and presents a detailed integrated model of emotional experience and regulation.
+Like Sroufe's work, this work describes a transition from interpersonal to intrapersonal emotion regulation.
+Other important features of this work include the interplay between emotion and communication, and the internalization of the socio-cultural symbolic function of emotion throughout development.
+<!--Theories like this are particularly relevant to a fine-grained understanding of the process of emotion regulation, but their developmental relevance has unfortunately not yet been considered (REF Buss).
+-->
+
+<!--Parents are widely considered to be the primary proximal influence driving emotion regulation development.
+
+Yet several limitations remain. 
+@coe-odessEmergentEmotionsAdolescence2019; 
+instead takes an inductive approach to map the correlates of adolescents' emotion regulation based on all available literature.
+
+The present study instead takes an inductive approach to map the correlates of adolescents' emotion regulation based on all available literature.
 From this mapping, we proceed to classify correlates as potential risk factors, manifestations, and outcomes of adolescent emotion regulation.
@@
 
-Unfortunately, there is little theory about which risk factors and environmental hazards render adolescents susceptible to emotional difficulties11
+Several limitations emerge from prior efforts to provide an encompassing framework of this literature
 
-Initially, much of the research on emotion regulation focused on either adulthood or early childhood.
-In recent years, however, a substantial body of research on emotion regulation in adolescence has accrued.
+These efforts at unification have, thusfar, been conducted in a top-down, theory-driven manner.
 
-What are the predictors of emotion regulation in adolescence?
+which motivates most youngsters to seek out challenges in life and love, but renders some of them vulnerable to emotion dysregulation.  -->
 
-* Emotion regulation is important for mental health and social relationships
-* Adolescence is a key developmental period
-*
+## Shortcomings of the theory
 
-Emotion regulation can be defined as the ability to modulate emotional experience and expression through automatic or deliberate processes.
+Existing theoretical models have several limitations.
+One crucial shortcoming is the lack of explicit attention to the life phase of adolescence.
+This is unfortunate, as empirical research consistently indicates that adolescence is a crucial life phase for emotion regulation development.
+Adolescence differs qualitatively from infancy, childhood, and adulthood.
+It is therefore insufficient to simply extrapolate theories focused on these ages.
+Other theories do focus on adolescence specifically [e.g., @croneUnderstandingAdolescencePeriod2012], but only address emotion regulation in passing.
+A second, related, shortcoming is that some relevant theories lack a developmental component <!--, and thus lack a well-substantiated understanding of developmental processes--> [see @bussTheoriesEmotionalDevelopment2019; @croneUnderstandingAdolescencePeriod2012].
+A third shortcoming is that theories vary widely in scope: Some are very broad and all-encompassing, but somewhat non-specific, such as the biopsychosocial models of Bronfenbrenner and Sameroff.
+Others describe a specific phenomenon in great detail, but are not embedded in a larger unifying framework.
+Examples include Morris' tripartite model, Crone and Dahl's model, and polyvagal theory.
+It would be beneficial to bridge these two levels of theory.
+One limitation echoed across many publications in this field is that more theory formation is required to provide a unified framework that could guide future empirical work.
+The present study seeks to aid such theory development, by providing an inductive conceptual review of the field.
 
-Substantial research has addressed issues related to emotion regulation, because it plays a central role in mental health and social functioning throughout the life course.
-Recent findings suggest that adolescence is a sensitive period for the development of mature emotion regulation skills.
+<!--
+Barriola: What is most
+* evident from the reviewed studies is that the samples
+investigated have been mainly non-clinical, within the
+early childhood period of development and have examined
+predominantly maternal socialization factors. 
+* the vast
+majority have been restricted to toddlers and young chil-
+dren and have only examined the inﬂuence of maternal,
+and not paternal, expression.
+Most of the literature has addressed emotion regulation in adult or infant samples. A smaller, but substantial, portion of the literature has examined emotion regulation in adolescents. 
+-->
 
-Most of the literature has addressed emotion regulation in adult or infant samples. A smaller, but substantial, portion of the literature has examined emotion regulation in adolescents.
+<!-- Next paper: * Existing theory is not very specific, in the sense that it can give rise to concrete, testable predictions.
+"either is not guided by hypotheses of an explicit theory or cites a theory but does not explicitly test the theory." (Buss) (Smaldino)-->
+<!--Unfortunately, there is little theory about which risk factors and environmental hazards render adolescents susceptible to emotional difficulties11-->
 
-Wat is het vershcil dat het verschil maakt?
+<!--Initially, much of the research on emotion regulation focused on either adulthood or early childhood.
+In recent years, however, a substantial body of research on emotion regulation in adolescence has accrued.-->
 
-on adolescent emotion regulation development is limited27–29.
-The field is therefore at an impasse: We know that some adolescents are more susceptible to emotion dysregulation than others, but lack tools and theory to identify important predictors of individual development30.
+<!--What are the predictors of emotion regulation in adolescence?-->
+
+<!--Emotion regulation can be defined as the ability to modulate emotional experience and expression through automatic or deliberate processes. -->
+
+<!--
+
+## Why focus on theory?
+
+A focus on theory is becoming increasingly important, given the concern about the replicability of social scientific findings [@KLEIN].
+
+Several authors of comprehensive reviews have noted that developmental theories of emotion are still in their infancy [@bussTheoriesEmotionalDevelopment2019].
+Several specific limitations of the theoretical landscapes precipitate the present study.
+First, although there are many *relevant* theories, few are focused specifically on emotion regulation.
+Second, the phase of adolescence is rarely addressed, although empirical research has indicated that this is a crucial period of emotion regulation development.
+"emotion theory has largely focused on adults, and emotional development theory has largely focused on infancy and early childhood (see Chap.
+24 on adolescent emotional development)." Buss et al 2019:20
+
+## Why inductive -->
+
+## Bottom-up insights from narrative reviews
+
+While theory provides a top-down understanding of an area of research, literature reviews can provide a bottom-up, inductive understanding.
+Given the noted absence of a single overarching theory, reviews might provide additional insight into factors considered relevant in the etiology of adolescents' emotion regulation competencies.
+For example, a review by @bariolaChildAdolescentEmotion2011 addresses individual psychological factors such as temperament, and biological factors like neurocognitive development and genetic predispositions.
+Furthermore, they address proximal social influences, including parents, teachers, and peers, and specific mechanisms through which these individuals exert their influence, including parenting and modeling.
+Finally, they address distal factors, including the role of culture and the media.
+Barriola and colleagues also offer recommendations for future research, <!--most notably, they call for a robust theoretical framework to guide future research.--> calling for research on the role of parents beyond early childhood, and including the role of fathers - a limitation which has since been addressed by a new wave of empirical research on fathers' role in emotional development [@vanlissaRoleFathersMothers2019; @vanlissaMothersFathersQuantitative2020].
+
+Another review, by @coe-odessEmergentEmotionsAdolescence2019, offers a nuanced discussion of several issues that complement prior publications in this field.
+For instance, the authors cover the implications of physiological changes in detail, including neurocognitive development and pubertal maturation.
+As adolescents become increasingly individuated, conflict with parents peaks.
+This conflict, in turn, impacts emotion regulation, both in terms of day-to-day mood variability and dispositional emotion dysregulation [see also @vanlissaCostEmpathyParentadolescent2017].
+As parental importance diminishes, adolescents become increasingly oriented towards peers.
+This includes increased sensitivity to social status and norms, along with the associated increase in peer pressure and risk taking.
+Pubertal development also initiates the emergence of sexual and romantic behavior, and the intensification of both biological sex differences and gender stereotyped behavior.
+With regard to the process of emotion regulation, Coe-Odess and colleagues discuss the importance of strategies, and point out that, in addition to negative emotionality, positive emotionality also peaks in adolescence.
+Relatedly, the authors describe how hormonal changes precipitate an increased stress response, which might help explain adolescents' greater susceptibility to emotion dysregulation.
+Finally, going beyond the implications of cognitive development discussed in other publications, the authors discuss how an greater capacity for abstract thought relates to identity formation - a key challenge in adolescence [@meeusStudyAdolescentIdentity2011] - and to increased emotional understanding, and by extension, empathy [see also @vanlissaLongitudinalInterplayAffective2014].
+
+There are notable parallels between the relevant factors highlighted by these narrative reviews, and the aforementioned theoretical literature.
+Nevertheless, these literature reviews also touch upon issues that have received little attention in theoretical work.
+This highlights the value of both top-down and bottom-up approaches to understanding the phenomenon of adolescents' emotion regulation.
+One remaining limitation is that, to date, all reviews in this field have been unstructured narrative reviews.
+The present publication seeks to further complement preceding work by conducting a comprehensive empirical literature review, and mapping the factors associated with adolescent emotion regulation.
 
@@
 
+<!--
 Influences on emotion regulation (Riediger Klipker)
@@
 * Familial context
-
-There are sufficient *relevant* theories, but few explicitly tailored to adolescence, and few explicit (define explicit).
 
@@
 
-MAKE SURE THAT DICTIONARY TERMS ARE SEQUENTIALLY IMPLEMENTED
 Key questions:
-Why focus on theory?
+
 Why focus on emotion regulation specifically, instead of other aspects of emotional development?
@@
 
-Polyvagal theory Porges 1995
+Polyvagal theory Porges 1995 -->
 
-## Theories of adolescent emotion dysregulation
+## The present paper
 
-The present paper aims to develop a nomological network of the constructs related to adolescent emotion dysregulation.
-A nomological network is a diagrammatic representation of a phenomenon; it is a proto-theoretical device that describes relationships between constructs relevant to the theory (REF: Cronbach & Meehl 1955; McKenna, 2006; Alavi 2018).
-It can be useful as a precursor to a more explicit theory of the phenomenon.
+The present paper aims to develop a nomological network of the constructs related to adolescent emotion dysregulation, based on a systematic review of the literature.
+A nomological network is a diagrammatic representation of a phenomenon; a proto-theoretical device that describes relationships between constructs relevant to the theory (REF: Cronbach & Meehl 1955; McKenna, 2006; Alavi 2018).
+It is a precursor to a more explicit theory of the phenomenon.
 The present paper uses an inductive approach to develop this nomological network.
-First, we use a systematic search to elicit a corpus of relevant literature.
-Second, we extract constructs from the corpus.
+First, we conduct a systematic search to elicit a corpus of relevant literature.
+Second, we use text mining techniques to extract relevant constructs from the corpus.
 Third, we use a dictionary to pare down the extracted constructs to meaningful superordinate categories.
 Fourth, we map interrelations between these constructs.
-Fifth, we classify contstructs as potential predictors or outcomes, and we categorize predictors by level of analysis (CJ: Sameroff, which level of biopsychosocial).
-
-t, using text mining to map potential predictors of adolescent emotion dysregulation.
-
+Fifth, we classify contstructs as potential predictors or outcomes, and we categorize predictors by level of analysis<!-- (CJ: Sameroff, which level of biopsychosocial)-->.
+<!-- t, using text mining to map potential predictors of adolescent emotion dysregulation.
 identify relevant constructs  of adolescents’ emotion regulation development, and moderators of parents’ role therein. The resulting insights are consolidated into theory.
-
 The present study intends to map the extant literature 
-First, I will systematically review predictors currently considered relevant in the adolescent emotion regulation literature.
+First, I will systematically review predictors currently considered relevant in the adolescent emotion regulation literature.  -->
 
@@
 All searches were conducted on Web of Science.
-The search strategy was based on procedures described by Janneke Staaks on https://osf.io/49t8x/, DOI:10.17605/OSF.IO/49T8X, accessed on 27-01-2020.
+The search strategy was based on procedures described by Staaks [@staaksSystematicReviewSearch].
 First, we manually constructed a reference set of 15 articles.
 Then we constructed a search string to retrieve these articles from Web of Science.
-The search was overly inclusive, returning 29 records, but these were all highly relevant, so we used all 29 results as reference set.
-Next, we tested our search string, which consisted of synonyms of emotion regulation and adolescence:
+The search was overly inclusive, returning 29 records.
+As these were all highly relevant, we updated the reference set to include all 29 results.
+Next, we tested our search string, which consisted of synonyms of emotion regulation and adolescence: <!-- ### Reference set Our reference set is documented in `reference_set.bib`.
+-->
 ```
@@
 The term `"development*`, as synonym of adolescence, added 3628 new hits, many of which were not focused on the age range of adolescence.
-We thus deemed these terms to be overly inclusive, and proceeded with the original search string.
+We thus deemed these terms to be overly inclusive, and proceeded with the original search string above.
 ```{r readrecs}
@@
 ```
-Duplicates were detected based on exact DOI matches (`r dups[["dup_doi"]]` duplicates), and title similarity (`r dups[["dup_title"]]` duplicates).
+Duplicates were identified based on exact DOI matches (`r dups[["dup_doi"]]` duplicates), and title similarity (`r dups[["dup_title"]]` duplicates).
 Manual screening in Rayyan resulted in the removal of an additional 13 duplicates.
@@
 ```
+We manually screened 500 abstracts for suitability in Rayyan.
+Then, we used ASReview to rank the predicted relevance of all papers based on the manually included and excluded articles.
+We screened the lowest-ranked articles to find an inflection point below which most articles were irrelevant, and excluded those from analysis.
 
-Unknown.
-In the initial screening, we will include all studies 1) returned by the specified search strategy 2) in the specified databases 3) for which abstracts are available.
-We will manually screen a maximum of 500 abstracts, and have the remainder scanned by ASReview.
+# Analysis 1: Keyword mapping
 
-In the initial screening, we will include all studies 1) returned by the specified search strategy 2) in the specified databases 3) for which abstracts are available.
-We will manually screen a maximum of 500 abstracts, and have the remainder scanned by ASReview.
+For this first analysis, we relied on author-provided keywords. We extracted keywords by document, and used a dictionary approach to classify closely related terms.
 
-### Reference set
+# Analysis 2: Abstract text mining
 
-Our reference set is documented in `reference_set.bib`.
+This second analysis focused on the abstracts of our corpus.
+Keywords are carefully chosen to capture the core tenets of a study.
+However, as authors are typically limited to 5 keywords, some of a study's nuance may be lost.
+Abstracts offer greater freedom of expression, which is a challenge when it comes to extracting relevant information.
+We took a two-pronged approach to extract relevant topic terms from the abstracts.
+First, we used the natural language processing technique part-of-speech tagging (POS-tagging) to identify nouns in the abstract.
+Using nouns only in text mining can lead to more interpretable models [@martinMoreEfficientTopic2015].
+Secondly, we used stemming to reduce these nouns to their root form.
+Finally, we applied a dictionary approach as before.
 
-```{r removeduplicates}
-filenam <- "title_sim.RData"
-if(!file.exists(filenam)){
-  recs$doi <- recs$DI
-  recs$doi[is.na(recs$doi)] <- paste0("fake", 1:sum(is.na(recs$doi)))
-  if(any(duplicated(recs$doi))){
-    recs <- recs[!duplicated(recs$doi), ]
-  }
-  recs$title <- recs$TI
-  # locate and extract unique references
-  potential_dups <- find_duplicates(recs, match_variable = "title", match_function = "stringdist", threshold = 5, to_lower = TRUE, remove_punctuation = TRUE)
-  unique_recs <- extract_unique_references(recs, matches = potential_dups)
-  saveRDS(unique_recs, filenam)
-} else {
-  unique_recs <- readRDS(filenam)
-}
-```
+offer an incomplete understanding of a study topic due to the limite
+authors are typically limited to provide a maximum of 
+abstracts offer a little more
+
+used part-of-speech tagging, a natural language processing technique
+
+to identify nouns in the abstracts.
+, we relied on author-provided keywords. We extracted keywords by document, and used a dictionary approach to classify closely related terms.
+
+# Discussion
+
+<!--it is worth noting that many different theories of *emotion* exist, and yet there is relatively little attention for the subtleties of 
+distinct from theories of emotional development, and that there is no one-to-one relationship between theories of emotion (regulation) development and theories of emotion.
+This issue is beyond the scope of the present study -->
 

### 2020-05-18 manuscript.tex
Synchronize remote

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  english,
  man]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Mapping the predictors of adolescent emotion dysregulation: A text-mining based systematic review},
  pdfkeywords={keywords},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

% Table formatting
\usepackage{longtable}
\usepackage{lscape}
% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
\usepackage{multirow}		% Table styling
\usepackage{tabularx}		% Control Column width
\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
\usepackage{threeparttablex}            % Lets threeparttable work with longtable

% Create new environments so endfloat can handle them
% \newenvironment{ltable}
%   {\begin{landscape}\begin{center}\begin{threeparttable}}
%   {\end{threeparttable}\end{center}\end{landscape}}
\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}

% Enables adjusting longtable caption width to table width
% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
\makeatletter
\newcommand\LastLTentrywidth{1em}
\newlength\longtablewidth
\setlength{\longtablewidth}{1in}
\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}

% \setlength{\parindent}{0.5in}
% \setlength{\parskip}{0pt plus 0pt minus 0pt}

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\makeatother
\shorttitle{ADOLESCENT EMOTION DYSREGULATION}
\author{Caspar J. van Lissa\textsuperscript{1,2}}
\affiliation{
\vspace{0.5cm}
\textsuperscript{1} Utrecht University faculty of Social and Behavioral Sciences, department of Methodology \& Statistics\\\textsuperscript{2} Open Science Community Utrecht}
\authornote{Caspar van Lissa, Department of Methodology and Statistics, Utrecht
University, P.O. Box 80140, 3508 TC, Utrecht, The Netherlands. E-mail:
C.vanLissa@uu.nl. This work is supported by a NWO Veni grant (NWO
grant number VI.Veni.191G.090).

Correspondence concerning this article should be addressed to Caspar J. van Lissa, Padualaan 14, 3584CH Utrecht, The Netherlands. E-mail: c.j.vanlissa@uu.nl}
\keywords{keywords\newline\indent Word count: X}
\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{lineno}

\linenumbers
\usepackage{csquotes}
\ifxetex
  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
  \usepackage{polyglossia}
  \setmainlanguage[]{english}
\else
  \usepackage[shorthands=off,main=english]{babel}
\fi

\title{Mapping the predictors of adolescent emotion dysregulation: A text-mining based systematic review}

\date{}

\abstract{
Test me
}

\begin{document}
\maketitle

A key developmental challenge in adolescence is acquiring mature emotion regulation skills (Crone \& Dahl, 2012; Zimmermann \& Iwanski, 2014). Emotion regulation is integral to mental health(Aldao, Nolen-Hoeksema, \& Schweizer, 2010; Braet et al., 2014; Schäfer, Naumann, Holmes, Tuschen-Caffier, \& Samson, 2017) and social functioning (Reindl, Gniewosz, \& Reinders, 2016). For as many as one in five adolescents, this phase marks the onset of emotion regulation-related mental illness, which can persist throughout the life course (see Lee et al., 2014). It is therefore crucial to identify which risk factors and environmental hazards render some adolescents more susceptible to emotional difficulties than others. Although there is an abundance of empirical work on factors associated with adolescents' emotion regulation, the literature is somewhat fragmented, as the topic has been investigated from different (sub)disciplines. This study seeks to address this limitation by mapping all factors currently thought to be relevant to adolescent emotion regulation, based on a systematic review of the literature. Similarly, although there are several \emph{relevant} theories, there is no specific theoretical framework to guide research on adolescents' emotion regulation. Although theory development is beyond the scope of this paper, we set out to generate a proto-theoretical nomological network of the potential risk factors, manifestations, and outcomes of emotion regulation in adolescence. We discuss how this nomological network relates to existing relevant theory, and conclude with recommendations for future theory-generating efforts.

There have been only few notable efforts to provide an encompassing framework (Buss, Cole, \& Zhou, 2019; Coe-Odess, Narr, \& Allen, 2019; Riediger \& Klipker, 2014). Yet several limitations remain.

instead takes an inductive approach to map the correlates of adolescents' emotion regulation based on all available literature.

The present study instead takes an inductive approach to map the correlates of adolescents' emotion regulation based on all available literature. From this mapping, we proceed to classify correlates as potential risk factors, manifestations, and outcomes of adolescent emotion regulation. The results provide a conceptual overview of the existing literature, can help identify blind spots in existing theory, and might inspire new hypotheses to guide future deductive research.

Several limitations emerge from prior efforts to provide an encompassing framework of this literature

These efforts at unification have, thusfar, been conducted in a top-down, theory-driven manner.

\hypertarget{existing-relevant-theory}{%
\subsection{Existing relevant theory}\label{existing-relevant-theory}}

Several recent publications have undertaken the monumental task of providing a comprehensive overview of theories of emotional development (e.g., Buss et al., 2019; {\textbf{???}}; Riediger \& Klipker, 2014), and of the empirical work pertaining to emotions in adolescence (Coe-Odess et al., 2019). We provide a summary review of the theoretical landscape as context for our empirical contribution.

Two of the most frequently cited theories in research on development, including emotional development, are biopsychosocial models. One is Bronfenbrenner's bioecological model, which describes how the environment shapes individual development. The individual is imbued with certain biological predispositions, and changes over the course of developmental time. Moreover, this individual development takes place in interaction with contextual influences. These range from the microsystem, composed of other people in close interaction with the individual, to the macrosystem, consisting of indirect political and economic influences, to the exosystem, consisting of cultural norms and values. Sameroff's transactional model is another bioecological theory, which focuses heavily on social influences (the microsystem in Bronfenbrenner's model). Its main contribution is that it conceptualized development as a product of reciprocal influences between child and parent (or another individual).

With regard to theories specifically addressing emotion regulation in adolescence, Hall's notion of \enquote{storm and stress} is one of the oldest. It describes how hormonal changes diminish self-control and increase reactivity, leading to difficulties in emotion regulation, conflict with parents, and risky behavior. Recent work provides a more nuanced perspective on this theory. For example, although the notion of diminished self-control and increased emotional reactivity has been upheld, it has been recast as a necessary change that facilitates emotional maturation (Crone \& Dahl, 2012), at the risk of emotional disturbance (Arnett, 1999; Lee et al., 2014). This again highlights the importance of identifying factors that predict or explain between-adolescent differences in emotional dysregulation.

Another theory of emotion regulation development was proposed by Sroufe (1995). This theory focuses on normative emotional development in early childhood. It argues that children's self-regulatory abilities increase with age, which drives a transition from external emotion regulation by primary caregivers towards autonomous emotion regulation. This work describes social and cognitive influences. Social influences mainly occur through parents' co-regulation, parenting behaviors, and parent-child attachment. Cognitive influences occur through the development of the central nervous system (CNS), cognition, and self-regulation. This emphasis on neorocognitive development is mirrored in polyvagal theory (Porges, 1995), which closely links emotional experience - and regulation - to autonomous nervous system functioning.

A more recent neorocognitive theory, with greater relevance to adolescents' emotion regulation development, is Crone and Dahl's model of social-affective engagement and goal flexibility (Crone \& Dahl, 2012). This theory is based on the notion of a \enquote{maturity gap} in middle-adolescence, arising from a developmental asymmetry between motivational and inhibitory brain circuits ({\textbf{???}}; Cracco, Goossens, \& Braet, 2017). However, it explicitly sets out to explain adolescents' diverging destinies - the observation that some youngsters flourish while others languish. Crone and Dahl argue that adolescents' cognitive engagement is dynamically responsive to social and motivational goal salience. This flexibility, on the one hand, prepares adolescents to effectively engage cognitive systems in novel challenging situations in a way that facilitates developing mature regulatory abilities. On the other hand, it places them at risk to act impulsively in pursuit of peer approval. This theory focuses primarily on cognitive factors and the role of peers, with little reference to parenting or other factors.

A theory focused specifically on parents' role in emotion regulation development is Morris' tripartite model (2007). It describes three pathways through which parents shape emotion regulation development: Through observation and modeling, parenting practices, and the emotional family climate, which in turn involves attachment and marital relationship quality. Morris and colleagues also emphasize the relevance of fathers and siblings, and others have adapted the tripartite model to describe the role of peers in adolescents' emotion regulation development (Reindl et al., 2016).

Holodynski and Friedlmeier's ({\textbf{???}}) internalization theory applies Vygotsky's theory of development to the domain of emotion. Like Sroufe's work, it captures the transition from interpersonal to intrapersonal emotion regulation. Unique features of this work include, most notably, the integrative view of emotion and emotion regulation, the interplay between emotion and communication, and the role of culture in emotion regulation development.

Aside from theories of emotional development, theories of the phenomenon of emotion regulation are also somewhat relevant. One influential theory is Gross' (2013) process model, which describes the process of emotion regulation, from eliciting cue to ultimate response. Individuals modulate the different stages of this process using strategies, consciously or otherwise. The effectiveness, desireability, and consequences of different strategies depend on the cultural context (see Bariola, Gullone, \& Hughes, 2011). Similar to Gross' theory, the social information processing theory of emotion also describe the role of intrapsychic processes and strategies in emotion experience and reulation (Lemerise \& Arsenio, 2000). Such theories are particularly relevant to a fine-grained understanding of the process of emotion regulation, but their developmental relevance has unfortunately not yet been considered (REF Buss).

Parents are widely considered to be the primary proximal influence driving emotion regulation development.

\hypertarget{shortcomings}{%
\subsection{Shortcomings}\label{shortcomings}}

Extant theoretical models have several noteable shortcomings. The most notable shortcoming is the lack of explicit attention to the life phase of adolescence. This is unfortunate, as empirical research consistently indicates that adolescence is a crucial life phase for emotion regulation development. As this life phase differs qualitatively from infancy, childhood, and adulthood, it is insufficient to simply extrapolate from theories focused on these ages. Other theories do focus on adolescence specifically, but only address emotion regulation in passing. A second, related, shortcoming is that some relevant theories lack a developmental component, or are based on a near-exclusively cross-sectional body of research (see Buss et al., 2019; Crone \& Dahl, 2012). A third shortcoming is that theories vary widely in scope: On the macro-level, there are theories such as the biopsychosocial models of Bronfenbrenner and Sameroff, which are all-encompassing but non-specific. On the micro-level, there are theories such as Morriss' tripartite model, Crone and Dahl's model, and polyvagal theory, which originated in subdisciplines and describe one facet of the issue in great detail, but have not been placed within a unifying framework (Buss et al., 2019). To conclude, one limitation echoed across many publications in this field is that more theory formation is required to provide a unified framework that could guide future empirical work. A systematic conceptual review of the field could address this shortcoming.

\hypertarget{relevant-factors}{%
\subsection{Relevant factors}\label{relevant-factors}}

As there are few theories specifically relevant to the field of adolescent emotion regulation development, it is perhaps unsurprising that some literature has proceeded in a somewhat less theoretical manner. Such studies do often focus on specific factors that are considered relevant for emotion regulation development.

These include neurological (Fox 1994;
Porges et al.~1994; Quirk 2007; Stansbury and Gunnar
1994), genetic (Goldsmith et al.~1997; Hariri and Forbes
2007), and temperamental inﬂuences (Calkins 2004)
A range of social factors have been proposed to be linked to
ER development, including interactions with parents,
teachers, and peers, as well as more distal societal inﬂu-
ences such as culture and the media (Eisenberg and Morris
2002; Klimes-Dougan et al.~2007; Morris et al.~2007;
Thompson 1994).

on adolescent emotion regulation development is limited27--29. The field is therefore at an impasse: We know that some adolescents are more susceptible to emotion dysregulation than others, but lack tools and theory to identify important predictors of individual development30.

\hypertarget{the-present-study}{%
\subsection{The present study}\label{the-present-study}}

The present paper aims to develop a nomological network of the constructs related to adolescent emotion dysregulation by mapping the available literature. A nomological network is a diagrammatic representation of a phenomenon; a proto-theoretical device that describes relationships between constructs relevant to the theory (REF: Cronbach \& Meehl 1955; McKenna, 2006; Alavi 2018). It can be useful as a precursor to a more explicit theory of the phenomenon. The present paper uses an inductive approach to develop this nomological network. First, we conduct a systematic search to elicit a corpus of relevant literature. Second, we extract constructs from the corpus. Third, we use a dictionary to pare down the extracted constructs to meaningful superordinate categories. Fourth, we map interrelations between these constructs. Fifth, we classify contstructs as potential predictors or outcomes, and we categorize predictors by level of analysis (CJ: Sameroff, which level of biopsychosocial).

\hypertarget{methods}{%
\section{Methods}\label{methods}}

\hypertarget{search-strategy}{%
\subsection{Search strategy}\label{search-strategy}}

All searches were conducted on Web of Science. The search strategy was based on procedures described by Staaks (Staaks, n.d.). First, we manually constructed a reference set of 15 articles. Then we constructed a search string to retrieve these articles from Web of Science. The search was overly inclusive, returning 29 records. As these were all highly relevant, we updated the reference set to include all 29 results. Next, we tested our search string, which consisted of synonyms of emotion regulation and adolescence:

\begin{verbatim}
TS=("emotio* regulation" OR "anger regulation" OR "sadness regulation" OR "emotion* competence" OR "emotion* adjustment" OR "emotio* dysregulation" OR "anger dysregulation" OR "sadness dysregulation" OR "emotio* problem*" OR "emotion* maladjustment") AND TS=(adolescent* OR teen* OR pubert* OR youth)
\end{verbatim}

This string returned 6653 results, and matched 25 of the 29 records in the reference set. Three search terms could be added to match all 29 reference set items. The terms \texttt{"emotio*\ socialization"\ OR\ "emotio*\ processes"}, as synonyms of emotion regulation, added 191 new hits. However, many of these hits were not directly relevant to emotion regulation. The term \texttt{"development*}, as synonym of adolescence, added 3628 new hits, many of which were not focused on the age range of adolescence. We thus deemed these terms to be overly inclusive, and proceeded with the original search string above.

\hypertarget{deduplication}{%
\subsection{Deduplication}\label{deduplication}}

Duplicates were detected based on exact DOI matches (2 duplicates), and title similarity (54 duplicates). Manual screening in Rayyan resulted in the removal of an additional 13 duplicates.

\hypertarget{screening}{%
\subsection{Screening}\label{screening}}

\begin{verbatim}
## [1] "2000-8198" "1540-2002" "2152-0828" "2152-0828" "0021-5368" "0021-9630"
\end{verbatim}

We manually screened 500 abstracts for suitability in Rayyan. Then, we used ASReview to rank the predicted relevance of all papers based on the manually included and excluded articles. We screened the lowest-ranked articles to find an inflection point below which most articles were irrelevant, and excluded those from analysis.

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

\newpage

\hypertarget{references}{%
\section{References}\label{references}}

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-aldaoEmotionregulationStrategiesPsychopathology2010}{}%
Aldao, A., Nolen-Hoeksema, S., \& Schweizer, S. (2010). Emotion-regulation strategies across psychopathology: A meta-analytic review. \emph{Clinical Psychology Review}, \emph{30}(2), 217--237.

\leavevmode\hypertarget{ref-arnettAdolescentStormStress1999}{}%
Arnett, J. J. (1999). Adolescent storm and stress, reconsidered. \emph{American Psychologist}, \emph{54}(5), 317--326. \url{https://doi.org/10.1037/0003-066X.54.5.317}

\leavevmode\hypertarget{ref-bariolaChildAdolescentEmotion2011}{}%
Bariola, E., Gullone, E., \& Hughes, E. K. (2011). Child and adolescent emotion regulation: The role of parental emotion regulation and expression. \emph{Clinical Child and Family Psychology Review}, \emph{14}(2), 198. \url{https://doi.org/10.1007/s10567-011-0092-5}

\leavevmode\hypertarget{ref-braetEmotionRegulationChildren2014}{}%
Braet, C., Theuwis, L., Durme, K. V., Vandewalle, J., Vandevivere, E., Wante, L., \ldots{} Goossens, L. (2014). Emotion regulation in children with emotional problems. \emph{Cognitive Therapy and Research}, \emph{38}(5), 493--504. \url{https://doi.org/10.1007/s10608-014-9616-x}

\leavevmode\hypertarget{ref-bussTheoriesEmotionalDevelopment2019}{}%
Buss, K. A., Cole, P. M., \& Zhou, A. M. (2019). Theories of Emotional Development: Where Have We Been and Where Are We Now? In V. LoBue, K. Pérez-Edgar, \& K. A. Buss (Eds.), \emph{Handbook of Emotional Development} (pp. 7--25). Cham: Springer International Publishing. \url{https://doi.org/10.1007/978-3-030-17332-6_2}

\leavevmode\hypertarget{ref-coe-odessEmergentEmotionsAdolescence2019}{}%
Coe-Odess, S. J., Narr, R. K., \& Allen, J. P. (2019). Emergent Emotions in Adolescence. In V. LoBue, K. Pérez-Edgar, \& K. A. Buss (Eds.), \emph{Handbook of Emotional Development} (pp. 595--625). Cham: Springer International Publishing. \url{https://doi.org/10.1007/978-3-030-17332-6_23}

\leavevmode\hypertarget{ref-craccoEmotionRegulationChildhood2017}{}%
Cracco, E., Goossens, L., \& Braet, C. (2017). Emotion regulation across childhood and adolescence: Evidence for a maladaptive shift in adolescence. \emph{European Child \& Adolescent Psychiatry}, \emph{26}(8), 909--921. \url{https://doi.org/10.1007/s00787-017-0952-8}

\leavevmode\hypertarget{ref-croneUnderstandingAdolescencePeriod2012}{}%
Crone, E. A., \& Dahl, R. E. (2012). Understanding adolescence as a period of social--affective engagement and goal flexibility. \emph{Nature Reviews Neuroscience}, \emph{13}(9), 636--650. \url{https://doi.org/10.1038/nrn3313}

\leavevmode\hypertarget{ref-grossHandbookEmotionRegulation2013}{}%
Gross, J. J. (2013). \emph{Handbook of emotion regulation}. Guilford publications.

\leavevmode\hypertarget{ref-leeAdolescentMentalHealth2014}{}%
Lee, F. S., Heimer, H., Giedd, J. N., Lein, E. S., Šestan, N., Weinberger, D. R., \& Casey, B. J. (2014). Adolescent mental health---Opportunity and obligation. \emph{Science}, \emph{346}(6209), 547--549. \url{https://doi.org/10.1126/science.1260497}

\leavevmode\hypertarget{ref-lemeriseIntegratedModelEmotion2000}{}%
Lemerise, E. A., \& Arsenio, W. F. (2000). An Integrated Model of Emotion Processes and Cognition in Social Information Processing. \emph{Child Development}, \emph{71}(1), 107--118. \url{https://doi.org/10.1111/1467-8624.00124}

\leavevmode\hypertarget{ref-morrisRoleFamilyContext2007}{}%
Morris, A. S., Silk, J. S., Steinberg, L., Myers, S. S., \& Robinson, L. R. (2007). The role of the family context in the development of emotion regulation. \emph{Social Development}, \emph{16}(2), 361--388.

\leavevmode\hypertarget{ref-porgesOrientingDefensiveWorld1995}{}%
Porges, S. W. (1995). Orienting in a defensive world: Mammalian modifications of our evolutionary heritage. A Polyvagal Theory. \emph{Psychophysiology}, \emph{32}(4), 301--318. \url{https://doi.org/10.1111/j.1469-8986.1995.tb01213.x}

\leavevmode\hypertarget{ref-reindlSocializationEmotionRegulation2016}{}%
Reindl, M., Gniewosz, B., \& Reinders, H. (2016). Socialization of emotion regulation strategies through friends. \emph{Journal of Adolescence}, \emph{49}, 146--157. \url{https://doi.org/10.1016/j.adolescence.2016.03.008}

\leavevmode\hypertarget{ref-riedigerEmotionRegulationAdolescence2014}{}%
Riediger, M., \& Klipker, K. (2014). Emotion regulation in adolescence. In \emph{Handbook of emotion regulation} (Vols. 1--Book, Section, pp. 187--202). Guilford Press.

\leavevmode\hypertarget{ref-schaferEmotionRegulationStrategies2017}{}%
Schäfer, J. Ö., Naumann, E., Holmes, E. A., Tuschen-Caffier, B., \& Samson, A. C. (2017). Emotion Regulation Strategies in Depressive and Anxiety Symptoms in Youth: A Meta-Analytic Review. \emph{Journal of Youth and Adolescence}, \emph{46}(2), 261--276. \url{https://doi.org/10.1007/s10964-016-0585-0}

\leavevmode\hypertarget{ref-sroufeEmotionalDevelopmentOrganization1995}{}%
Sroufe, L. A. (1995). \emph{Emotional Development: The Organization of Emotional Life in the Early Years}. Cambridge: Cambridge University Press. \url{https://doi.org/10.1017/CBO9780511527661}

\leavevmode\hypertarget{ref-staaksSystematicReviewSearch}{}%
Staaks, J. (n.d.). Systematic Review Search Support. Retrieved March 23, 2020, from \url{https://osf.io/49t8x/}

\leavevmode\hypertarget{ref-zimmermannEmotionRegulationEarly2014}{}%
Zimmermann, P., \& Iwanski, A. (2014). Emotion regulation from early adolescence to emerging adulthood and middle adulthood: Age differences, gender differences, and emotion-specific developmental variations. \emph{International Journal of Behavioral Development}, \emph{38}(2), 182--194.

\endgroup

\end{document}

### 2020-05-18 preregistration.Rmd
Synchronize remote

---
title           : "Predictors of emotion regulation in adolescence: A Systematic Review"
shorttitle      : "EMOTION REGULATION ADOLESCENCE"
date            : "`r Sys.setlocale('LC_TIME', 'C'); format(Sys.time(), '%d\\\\. %B %Y')`"

author: 
  - name        : Caspar J. van Lissa
    affiliation : 1

affiliation:
  - id          : 1
    institution : Utrecht University

output: prereg::cos_prereg
---

# Study Information

## Title
<!-- Provide the working title of your study. It may be the same title that you submit for publication of your final manuscript, but it is not a requirement. The title should be a specific and informative description of a project. Vague titles such as 'Fruit fly preregistration plan' are not appropriate.

Example: Effect of sugar on brownie tastiness. -->

`r rmarkdown::metadata$title`

## Description
<!-- Please give a brief description of your study, including some background, the purpose of the of the study, or broad research questions. The description should be no longer than the length of an abstract. It can give some context for the proposed study, but great detail is not needed here for your preregistration.

Example: Though there is strong evidence to suggest that sugar affects taste preferences, the effect has never been demonstrated in brownies. Therefore, we will measure taste preference for four different levels of sugar concentration in a standard brownie recipe to determine if the effect exists in this pastry. -->

This systematic review aims to identify all predictors considered relevant in relation to adolescent emotion regulation.

## Hypotheses
<!-- List specific, concise, and testable hypotheses. Please state if the hypotheses are directional or non-directional. If directional, state the direction. A predicted effect is also appropriate here. If a specific interaction or moderation is important to your research, you can list that as a separate hypothesis.

Example: If taste affects preference, then mean preference indices will be higher with higher concentrations of sugar. -->

This is an inductive study. There are no hypotheses.

# Design Plan
<!-- In this section, you will be asked to describe the overall design of your study. Remember that this research plan is designed to register a single study, so if you have multiple experimental designs, please complete a separate preregistration. -->

## Study type

**Other**. This is a systematic review of published studies. However, the purpose of the systematic review is not to meta-analyze effect sizes, but to identify and categorize predictors of adolescent emotion regulation.

## Blinding
<!-- Blinding describes who is aware of the experimental manipulations within a study. Select all that apply. Is there any additional blinding in this study? -->

No blinding is involved in this study.

## Study design
<!-- Describe your study design. Examples include two-group, factorial, randomized block, and repeated measures. Is it a between (unpaired), within-subject (paired), or mixed design? Describe any counterbalancing required. Typical study designs for observation studies include cohort, cross sectional, and case-control studies.

This question has a variety of possible answers. The key is for a researcher to be as detailed as is necessary given the specifics of their design. Be careful to determine if every parameter has been specified in the description of the study design. There may be some overlap between this question and the following questions. That is OK, as long as sufficient detail is given in one of the areas to provide all of the requested information. For example, if the study design describes a complete factorial, 2 X 3 design and the treatments and levels are specified previously, you do not have to repeat that information.

Example: We have a between subjects design with 1 factor (sugar by mass) with 4 levels. -->

Does not apply.

## Randomization
<!-- If you are doing a randomized study, how will you randomize, and at what level? Typical randomization techniques include: simple, block, stratified, and adaptive covariate randomization. If randomization is required for the study, the method should be specified here, not simply the source of random numbers.

Example: We will use block randomization, where each participant will be randomly assigned to one of the four equally sized, predetermined blocks. The random number list used to create these four blocks will be created using the web applications available at http://random.org. -->

Does not apply.

# Sampling Plan
<!-- In this section we’ll ask you to describe how you plan to collect samples, as well as the number of samples you plan to collect and your rationale for this decision. Please keep in mind that the data described in this section should be the actual data used for analysis, so if you are using a subset of a larger dataset, please describe the subset that will actually be used in your study. -->

## Existing data
<!-- Preregistration is designed to make clear the distinction between confirmatory tests, specified prior to seeing the data, and exploratory analyses conducted after observing the data. Therefore, creating a research plan in which existing data will be used presents unique challenges. Please select the description that best describes your situation. Please do not hesitate to contact us if you have questions about how to answer this question (prereg@cos.io). -->

**Registration prior to accessing the data**. As of the date of submission, the data exist, but have not been accessed by you or your collaborators. Commonly, this includes data that has been collected by another researcher or institution.

This preregistration is composed before the systematic search is conducted.

## Explanation of existing data
<!-- If you indicate that you will be using some data that already exist in this study, please describe the steps you have taken to assure that you are unaware of any patterns or summary statistics in the data. This may include an explanation of how access to the data has been limited, who has observed the data, or how you have avoided observing any analysis of the specific data you will use in your study.

An appropriate instance of using existing data would be collecting a sample size much larger than is required for the study, using a small portion of it to conduct exploratory analysis, and then registering one particular analysis that showed promising results. After registration, conduct the specified analysis on that part of the dataset that had not been investigated by the researcher up to that point.

Example: An appropriate instance of using existing data would be collecting a sample size much larger than is required for the study, using a small portion of it to conduct exploratory analysis, and then registering one particular analysis that showed promising results. After registration, conduct the specified analysis on that part of the dataset that had not been investigated by the researcher up to that point. -->

The present study concerns a systematic review of the published literature on adolescent emotion regulation. No effort has been made, as of this writing, to search that literature.

## Data collection procedures
<!-- Please describe the process by which you will collect your data. If you are using human subjects, this should include the population from which you obtain subjects, recruitment efforts, payment for participation, how subjects will be selected for eligibility from the initial pool (e.g. inclusion and exclusion rules), and your study timeline. For studies that donÍt include human subjects, include information about how you will collect samples, duration of data gathering efforts, source or location of samples, or batch numbers you will use.

The answer to this question requires a specific set of instructions so that another person could repeat the data collection procedures and recreate the study population. Alternatively, if the study population would be unable to be reproduced because it relies on a specific set of circumstances unlikely to be recreated (e.g., a community of people from a specific time and location), the criteria and methods for creating the group and the rationale for this unique set of subjects should be clear.

Example: Participants will be recruited through advertisements at local pastry shops. Participants will be paid $10 for agreeing to participate (raised to $30 if our sample size is not reached within 15 days of beginning recruitment). Participants must be at least 18 years old and be able to eat the ingredients of the pastries. -->

To collect the data, we will follow the procedures described by Janneke Staaks on https://osf.io/49t8x/, DOI:10.17605/OSF.IO/49T8X, accessed on 27-01-2020. Specifically, we will follow the guidelines in these documents:

1. Systematic searching
* Building a search strategy.pdf
* Database Syntax .pdf
* Subject Headings and Other Search Fields.pdf
3. Exporting from databases
* Exporting References.pdf
* Word Distance.pdf

### Reference set

Our reference set is documented in `reference_set.bib`.

### Search terms

We will use the following search terms:

* emotion regulation
* anger regulation
* sadness regulation
* emotion* competence
* emotion* adjustment
* internalizing

* emotion dysregulation
* anger dysregulation
* sadness dysregulation
* emotion* problems
* emotion* maladjustment

* adolescent*
* teen*
* pubert*
* youth

TS=(("emotio* regulation" OR "anger regulation" OR "sadness regulation" OR "emotion* competence" OR "emotion* adjustment" OR "internalizing" OR "emotio* dysregulation" OR "anger dysregulation" OR "sadness dysregulation" OR "emotio* problem*" OR "emotion* maladjustment") AND (adolescent* OR teen* OR puber* OR youth))

### Databases

We will apply these procedures to the following databases, provided we can access them and can export citations + abstracts from them (the abstracts are required for screening in ASReview):

* PsychInfo
* Scopus
* Web of Science

## Sample size
<!-- Describe the sample size of your study. How many units will be analyzed in the study? This could be the number of people, birds, classrooms, plots, interactions, or countries included. If the units are not individuals, then describe the size requirements for each unit. If you are using a clustered or multilevel design, how many units are you collecting at each level of the analysis? For some studies, this will simply be the number of samples or the number of clusters. For others, this could be an expected range, minimum, or maximum number.

Example: Our target sample size is 280 participants. We will attempt to recruit up to 320, assuming that not all will complete the total task. -->

Unknown.

## Sample size rationale
<!-- This could include a power analysis or an arbitrary constraint such as time, money, or personnel. This gives you an opportunity to specifically state how the sample size will be determined. A wide range of possible answers is acceptable; remember that transparency is more important than principled justifications. If you state any reason for a sample size upfront, it is better than stating no reason and leaving the reader to "fill in the blanks." Acceptable rationales include: a power analysis, an arbitrary number of subjects, or a number based on time or monetary constraints.

Example: We used the software program G*Power to conduct a power analysis. Our goal was to obtain .95 power to detect a medium effect size of .25 at the standard .05 alpha error probability. -->

Unknown. In the initial screening, we will include all studies 1) returned by the specified search strategy 2) in the specified databases 3) for which abstracts are available. We will manually screen a maximum of 500 abstracts, and have the remainder scanned by ASReview.

## Stopping rule
<!-- If your data collection procedures do not give you full control over your exact sample size, specify how you will decide when to terminate your data collection.

You may specify a stopping rule based on p-values only in the specific case of sequential analyses with pre-specified checkpoints, alphas levels, and stopping rules. Unacceptable rationales include stopping based on p-values if checkpoints and stopping rules are not specified. If you have control over your sample size, then including a stopping rule is not necessary, though it must be clear in this question or a previous question how an exact sample size is attained.

Example: We will post participant sign-up slots by week on the preceding Friday night, with 20 spots posted per week. We will post 20 new slots each week if, on that Friday night, we are below 320 participants. -->

In the initial screening, we will include all studies 1) returned by the specified search strategy 2) in the specified databases 3) for which abstracts are available. We will manually screen a maximum of 500 abstracts, and have the remainder scanned by ASReview.

# Variables
<!-- In this section you can describe all variables (both manipulated and measured variables) that will later be used in your confirmatory analysis plan. In your analysis plan, you will have the opportunity to describe how each variable will be used. If you have variables which you are measuring for exploratory analyses, you are not required to list them, though you are permitted to do so. -->

## Manipulated variables
<!-- Describe all variables you plan to manipulate and the levels or treatment arms of each variable. This is not applicable to any observational study. For any experimental manipulation, you should give a precise definition of each manipulated variable. This must include a precise description of the levels at which each variable will be set, or a specific definition for each categorical treatment. For example, “loud or quiet,” should instead give either a precise decibel level or a means of recreating each level. 'Presence/absence' or 'positive/negative' is an acceptable description if the variable is precisely described.

Example: We manipulated the percentage of sugar by mass added to brownies. The four levels of this categorical variable are: 15%, 20%, 25%, or 40% cane sugar by mass. -->

Does not apply.

## Measured variables
<!-- Describe each variable that you will measure. This will include outcome measures, as well as any predictors or covariates that you will measure. You do not need to include any variables that you plan on collecting if they are not going to be included in the confirmatory analyses of this study.

Observational studies and meta-analyses will include only measured variables. As with the previous questions, the answers here must be precise. For example, 'intelligence,' 'accuracy,' 'aggression,' and 'color' are too vague. Acceptable alternatives could be 'IQ as measured by Wechsler Adult Intelligence Scale' 'percent correct,' 'number of threat displays,' and 'percent reflectance at 400 nm.'

Example: The single outcome variable will be the perceived tastiness of the single brownie each participant will eat. We will measure this by asking participants ‘How much did you enjoy eating the brownie’ (on a scale of 1-7, 1 being 'not at all', 7 being 'a great deal') and 'How good did the brownie taste' (on a scale of 1-7, 1 being 'very bad', 7 being 'very good'). -->

For each included paper, we will code the following:

* sc_authors: The authors
* sc_pub_year: Year of publication
* sc_title: Study title
* sc_journal: Outlet of publication
* sc_doi: DOI
* sc_pub_type: Type of publication
* sc_country: Country of lead author
* sc_eligible: Eligibility
* sc_exclude_reason: Optional reason for exclusion
* sa_dataset_name: If applicable, which larger dataset the sample is obtained from
* sa_data_year: Optional, year of data collection
* sa_N: Sample size
* sa_age_m: Mean age of adolescents
* sa_p_male: Proportion of male adolescents
* sa_country: Sample country of origin
* de_manipulation: Dichotomous; was an (experimental) manipulation or intervention applied?
* de_longitudinal: Dichotomous; is this a longitudinal study?
* dv_des: Describe the DV (emotion regulation)
* dv_instrumentname: What instrument was used to measure emotion regulation?
* dv_type: Categorize this DV (e.g., emotion regulation, emotional adjustment, internalizing problems)
* relevance: How relevant the article is on a scale of 1-4
* theories: References of theoretical papers used to substantiate the analyses, if any. DOIs, separated by ;.
* cormat: Filename of a .csv file; If emotion regulation is included in a correlation matrix, we will digitize the correlation matrix as a .csv file.
* predictors: Variables that were used to predict emotion regulation, separated by commas
* covars: Control variables that were used to predict emotion regulation, separated by commas

## Indices
<!-- If any measurements are  going to be combined into an index (or even a mean), what measures will you use and how will they be combined? Include either a formula or a precise description of your method. If your are using a more complicated statistical method to combine measures (e.g. a factor analysis), you can note that here but describe the exact method in the analysis plan section.

If you are using multiple pieces of data to construct a single variable, how will this occur? Both the data that are included and the formula or weights for each measure must be specified. Standard summary statistics, such as "means" do not require a formula, though more complicated indices require either the exact formula or, if it is an established index in the field, the index must be unambiguously defined. For example, "biodiversity index" is too broad, whereas "Shannon’s biodiversity index" is appropriate.

Example: We will take the mean of the two questions above to create a single measure of 'brownie enjoyment.'  -->

Does not apply.

# Analysis Plan
<!-- You may describe one or more confirmatory analysis in this preregistration. Please remember that all analyses specified below must be reported in the final article, and any additional analyses must be noted as exploratory or hypothesis generating.

A confirmatory analysis plan must state up front which variables are predictors (independent) and which are the outcomes (dependent), otherwise it is an exploratory analysis. You are allowed to describe any exploratory work here, but a clear confirmatory analysis is required. -->

## Statistical models
<!-- What statistical model will you use to test each hypothesis? Please include the type of model (e.g. ANOVA, multiple regression, SEM, etc) and the specification of the model (this includes each variable that will be included as predictors, outcomes, or covariates). Please specify any interactions, subgroup analyses, pairwise or complex contrasts, or follow-up tests from omnibus tests. If you plan on using any positive controls, negative controls, or manipulation checks you may mention that here. Remember that any test not included here must be noted as an exploratory test in your final article.

This is perhaps the most important and most complicated question within the preregistration. As with all of the other questions, the key is to provide a specific recipe for analyzing the collected data. Ask yourself: is enough detail provided to run the same analysis again with the information provided by the user? Be aware for instances where the statistical models appear specific, but actually leave openings for the precise test. See the following examples:

- If someone specifies a 2x3 ANOVA with both factors within subjects, there is still flexibility with the various types of ANOVAs that could be run. Either a repeated measures ANOVA (RMANOVA) or a multivariate ANOVA (MANOVA) could be used for that design, which are two different tests. 
- If you are going to perform a sequential analysis and check after 50, 100, and 150 samples, you must also specify the p-values you’ll test against at those three points.

Example:  We will use a one-way between subjects ANOVA to analyze our results. The manipulated, categorical independent variable is 'sugar' whereas the dependent variable is our taste index. -->

Does not apply.

## Transformations
<!-- If you plan on transforming, centering, recoding the data, or will require a coding scheme for categorical variables, please describe that process. If any categorical predictors are included in a regression, indicate how those variables will be coded (e.g. dummy coding, summation coding, etc.) and what the reference category will be.

Example: The "Effect of sugar on brownie tastiness" does not require any additional transformations. However, if it were using a regression analysis and each level of sweet had been categorically described (e.g. not sweet, somewhat sweet, sweet, and very sweet), 'sweet' could be dummy coded with 'not sweet' as the reference category. -->

Does not apply.

## Inference criteria
<!-- What criteria will you use to make inferences? Please describe the information youÍll use (e.g. p-values, bayes factors, specific model fit indices), as well as cut-off criterion, where appropriate. Will you be using one or two tailed tests for each of your analyses? If you are comparing multiple conditions or testing multiple hypotheses, will you account for this?

p-values, confidence intervals, and effect sizes are standard means for making an inference, and any level is acceptable, though some criteria must be specified in this or previous fields. Bayesian analyses should specify a Bayes factor or a credible interval. If you are selecting models, then how will you determine the relative quality of each? In regards to multiple comparisons, this is a question with few "wrong" answers. In other words, transparency is more important than any specific method of controlling the false discovery rate or false error rate. One may state an intention to report all tests conducted or one may conduct a specific correction procedure; either strategy is acceptable.

Example: We will use the standard p<.05 criteria for determining if the ANOVA and the post hoc test suggest that the results are significantly different from those expected if the null hypothesis were correct. The post-hoc Tukey-Kramer test adjusts for multiple comparisons. -->

Does not apply.

## Data exclusion
<!-- How will you determine what data or samples, if any, to exclude from your analyses? How will outliers be handled? Will you use any awareness check? Any rule for excluding a particular set of data is acceptable. One may describe rules for excluding a participant or for identifying outlier data.

Example: No checks will be performed to determine eligibility for inclusion besides verification that each subject answered each of the three tastiness indices. Outliers will be included in the analysis. -->

Studies will be excluded if:

* They do not examine emotion regulation as a dependent variable
* They do not include any predictors of emotion regulation
* They do not study adolescents (age 10-19)
* They do not conduct quantitative analysis

## Missing data
<!-- How will you deal with incomplete or missing data? Any relevant explanation is acceptable. As a final reminder, remember that the final analysis must follow the specified plan, and deviations must be either strongly justified or included as a separate, exploratory analysis.

Example: If a subject does not complete any of the three indices of tastiness, that subject will not be included in the analysis. -->

Does not apply.

## Exploratory analyses (optional)
<!-- If you plan to explore your data set to look for unexpected differences or relationships, you may describe those tests here. An exploratory test is any test where a prediction is not made up front, or there are multiple possible tests that you are going to use. A statistically significant finding in an exploratory test is a great way to form a new confirmatory hypothesis, which could be registered at a later time.

Example: We expect that certain demographic traits may be related to taste preferences. Therefore, we will look for relationships between demographic variables (age, gender, income, and marital status) and the primary outcome measures of taste preferences. -->

Does not apply.

# Other

## Other (Optional)
<!-- If there is any additional information that you feel needs to be included in your preregistration, please enter it here. Literature cited, disclosures of any related work such as replications or work that uses the same data, or other context that will be helpful for future readers would be appropriate here. -->

Enter your response here.

# References
## 
\vspace{-2pc}
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{-1in}
\setlength{\parskip}{8pt}
\noindent

### 2020-05-18 ASREVIEW.R

@@ -1,0 +1,7 @@
+library(reticulate)
+use_python()
+
+asreview oracle YOUR_DATA.csv --state_file myreview.h5
+use_condaenv("veni_sysrev") #C:\Users\lissa102\AppData\Local\Continuum\miniconda3\envs\veni_sysrev
+
+asreview <- import("asreview")

### 2020-05-18 bibliometrix_tutorial.R

@@ -1,0 +1,71 @@
+recs$TI[grepl("THEOR", recs$TI)]
+tmp <- recs[recs$TI]
+which(duplicated(recs$TI))
+recs$TI[(duplicated(recs$TI))]
+
+recs$AB[recs$TI == "FAMILY DYNAMICS AND CHILD OUTCOMES IN EARLY INTERVENTION: THE ROLE OF DEVELOPMENTAL THEORY IN THE SPECIFICATION OF EFFECTS"]
+
+recs$AB[recs$TI == "PEER VICTIMIZATION AND NEUROBIOLOGICAL MODELS: BUILDING TOWARD COMPREHENSIVE DEVELOPMENTAL THEORIES"]
+
+
+ANXIETY AND DEPRESSION DURING CHILDHOOD AND ADOLESCENCE: TESTING THEORETICAL MODELS OF CONTINUITY AND DISCONTINUITY"
+
+FAMILY DYNAMICS AND CHILD OUTCOMES IN EARLY INTERVENTION: THE ROLE OF DEVELOPMENTAL THEORY IN THE SPECIFICATION OF EFFECTS"
+
+GENERAL STRAIN THEORY, GENDER, AND THE CONDITIONING INFLUENCE OF NEGATIVE INTERNALIZING EMOTIONS ON YOUTH RISK BEHAVIORS
+
+library(bibliometrix)
+library(dplyr)
+library(igraph)
+library(ggraph)
+
+results <- biblioAnalysis(recs, sep = ";")
+
+S <- summary(object = results, k = 10, pause = FALSE)
+plot(S$AnnualGrowthRate)
+
+plot(x = results, k = 10, pause = FALSE)
+
+NetMatrix <- biblioNetwork(recs, analysis = "collaboration", network = "authors")
+range(NetMatrix)
+tmp <- NetMatrix
+max_collab <- vector(length = nrow(tmp))
+for(i in 1:nrow(tmp)){
+  max_collab[i] <- max(tmp[i, -i], na.rm = TRUE)
+}
+tb <- table(max_collab)
+plot(1:length(tb), tb, type = "b")
+sum(max_collab > 5)
+keep_these <- max_collab > 10
+sum(keep_these)
+tmp2 <- tmp[keep_these, keep_these]
+colnames(tmp2) <- rownames(tmp2) <- gsub(" [A-Z]+?$", "", rownames(tmp2))
+set.seed(36478)
[…]

### 2020-05-18 chord_diagrams.R

@@ -1,0 +1,33 @@
+# Create an edge list: a list of connections between 10 origin nodes, and 10 destination nodes:
+origin <- paste0("dest ", sample(c(1:10), 20, replace = T))
+destination <- paste0("dest ", sample(c(1:10), 20, replace = T))
+data <- data.frame(origin, destination)
+head(data)
+
+# Transform input data in a adjacency matrix
+adjacencyData <- with(data, table(origin, destination))
+
+# Charge the circlize library
+library(circlize)
+head(adjacencyData)
+# Make the circular plot
+chordDiagram(adjacencyData, transparency = 0.5)
+
+df_chord <- word_cooccurences
+df_chord <- df_chord[!(df_chord$term1 == "youth" | df_chord$term2 == "youth"),]
+
+df_chord <- reshape2::dcast(df_chord, term1~term2)[, -1]
+df_chord[is.na(df_chord)] <- 0
+df_chord <- as.matrix(df_chord)
+rownames(df_chord) <- colnames(df_chord)
+plot(1:length(table(df_chord)), table(df_chord))
+df_chord[df_chord < 4] <- 0
+chordDiagram(df_chord, transparency = 0.5)
+
+chordDiagram(df_chord, annotationTrack = "grid", #grid.col = grid.col, 
+             preAllocateTracks = list(track.height = max(strwidth(unlist(dimnames(df_chord))))))
+# we go back to the first track and customize sector labels
+circos.track(track.index = 1, panel.fun = function(x, y) {
+  circos.text(CELL_META$xcenter, CELL_META$ylim[1], CELL_META$sector.index, 
+              facing = "clockwise", niceFacing = TRUE, adj = c(0, 0.5))
+}, bg.border = NA) # here set bg.border to NA is a

### 2020-05-18 dictionary.R

@@ -1,0 +1,1 @@
+acceptance = c("AFQ-Y")

### 2020-05-18 fuzzy_dedup.R

@@ -1,0 +1,36 @@
+fuzzy_dedup <- function(txt, threshold = 5, labs = txt){
+  UseMethod("fuzzy_dedup", txt)
+}
+
+fuzzy_dedup.character <- function(txt, threshold = 5, labs){
+  cl <- as.list(match.call()[-1])
+  cl$txt <- stringdistmatrix(txt)
+  cl$labs <- txt
+  do.call(fuzzy_dedup, cl)
+}
+
+fuzzy_dedup.matrix <- function(txt, threshold = 5, labs){
+  tmp <- txt < threshold
+  tmp <- rowSums(tmp)
+  dups <- which(tmp > 1)
+  if(any(dups)){
+    sim_dups <- txt[dups, ]
+    remove_these <- NULL
+    for(this_ref in 1:length(dups)){
+      potential_matches <- which(sim_dups[this_ref, ] < threshold)
+      for(i in 1:length(dups)){
+        
+      }
+      cat(labs[dups[which(sim_dups[, this_group]  < threshold)]], sep = "\n")
+      user_response <- readline("All the same: 1\nNot the same: 2")
+      if(user_response == "1"){
+        remove_these <- c(remove_these, dups[which(sim_dups[, this_group]  < threshold)][-1])
+      } else {
+        user_response <- readline("Which elements should be preserved?")
+        remove_these <- c(remove_these, dups[which(sim_dups[, this_group]  < 5)][-c(1,as.numeric(strsplit(user_response, ",")[[1]]))])
+      }
+    }
+  } else {
+    cat("No duplicates found.")
+  }
+}

### 2020-05-18 keywords_9811.R

@@ -1,0 +1,152 @@
+library(data.table)
+library(bibliometrix)
+source("word_functions.R")
+exclude_terms <- readLines("exclude_terms.txt")
+dict_synon <- dget("dictionary_synonyms.txt")
+resolve_dups <- dget("resolve_duplicates.txt")
+f <- list.files("recs/", ".txt", full.names = TRUE)
+csums <- tools::md5sum(f)
+any(duplicated(csums))
+recs <- do.call(readFiles, as.list(f))
+recs <- convert2df(recs)
+#saveRDS(recs, "9811_2.RData")
+recs <- as.data.table(readRDS("9811_2.RData"))
+
+recs <- recs[!(duplicated(TI) | duplicated(DI)), ]
+
+df <- lapply(recs$ID, function(x){strsplit(x, split = "; ")[[1]]})
+df <- data.table(word = unlist(df), doc = rep(1:length(df), times = sapply(df, length)))
+df$word <- tolower(df$word)
+
+exclude_these <- unique(unlist(lapply(exclude_terms, grep, x = df$word)))
+
+df <- df[!exclude_these, ]
+
+res_cat <- cat_words2(df$word, dict_synon, resolve_dups)
+
+res_cat$dup
+head(res_cat$unmatched)
+writeClipboard(names(res_cat$unmatched))
+
+# Remove duplicate words per doc
+df$word <- res_cat$words
+df$id <- paste0(df$word, df$doc)
+df <- df[!duplicated(df$id), -3]
+
+library(lattice)
+library(topicmodels)
+library(udpipe)
+library(slam)
+library(wordcloud)
+
+dtm <- udpipe::document_term_matrix(document_term_frequencies(df[, c(2,1)]))
+topterms <- col_sums(dtm)
+topterms <- sort(topterms, decreasing = TRUE)
+hist(topterms, breaks = 100)
+
+tt <- table(topterms)
+plot(1:10, tt[1:10], type = "b")
+
+topterms <- topterms[topterms > round(.005*nrow(recs))]
+topterms <- head(topterms, 250)
+topterms <- names(topterms)
+dtm_top <- dtm[, topterms]
+dtm_top <- dtm_top[row_sums(dtm_top) > 0, ]
+
+set.seed(43892)
+
+topics <- LDA(x = dtm_top, k = 5, method = "VEM", control = list(alpha = 0.1, estimate.alpha = TRUE, seed = as.integer(10:1), verbose = FALSE, nstart = 10, save = 0, best = TRUE))
[…]

### 2020-05-18 neighboring_words.R

@@ -1,0 +1,16 @@
+neighboring_words <- function(words, pattern, position = +1){
+  where_word <- grep(pattern, words)
+  tb <- table(words[(where_word+position)])
+  sort(tb, ddecreasing = TRUE)
+}
+neighboring_words(words = df_nouns$word.lemma, pattern = "substance")
+neighboring_words(words = df_nouns$word.lemma, pattern = "use", -1)
+neighboring_words(words = df_nouns$word.lemma, pattern = "regulation", -1)
+grep("(ab|mis|)use$", df_nouns$word.lemma, value = TRUE)
+
+grep("auti", df_nouns$word.lemma, value = T)
+
+
+
+neighboring_words(words = dft$word, pattern = "activity", -1)
+neighboring_words(words = dft$word.lemma, pattern = "problem")

### 2020-05-18 pretty_network.R

@@ -1,0 +1,67 @@
+doInstall <- F  # Change to FALSE if you don't want packages installed.
+toInstall <- c("sna", "ggplot2", "Hmisc", "reshape2")
+if(doInstall){install.packages(toInstall, repos = "http://cran.r-project.org")}
+lapply(toInstall, library, character.only = TRUE)
+
+# Empty ggplot2 theme
+new_theme_empty <- theme_bw()
+new_theme_empty$line <- element_blank()
+new_theme_empty$rect <- element_blank()
+new_theme_empty$strip.text <- element_blank()
+new_theme_empty$axis.text <- element_blank()
+new_theme_empty$plot.title <- element_blank()
+new_theme_empty$axis.title <- element_blank()
+new_theme_empty$plot.margin <- structure(c(0, 0, -1, -1), unit = "lines",
+                                         valid.unit = 3L, class = "unit")
+
+data(coleman)  # Load a high school friendship network
+adjacencyMatrix <- coleman[1, , ]  # Fall semester
+layoutCoordinates <- gplot(adjacencyMatrix)  # Get graph layout coordinates
+
+adjacencyList <- melt(adjacencyMatrix)  # Convert to list of ties only
+adjacencyList <- adjacencyList[adjacencyList$value > 0, ]
+head(adjacencyList)
+# Function to generate paths between each connected node
+edgeMaker <- function(whichRow, len = 100, curved = TRUE){
+  fromC <- layoutCoordinates[adjacencyList[whichRow, 1], ]  # Origin
+  toC <- layoutCoordinates[adjacencyList[whichRow, 2], ]  # Terminus
+  
+  # Add curve:
+  graphCenter <- colMeans(layoutCoordinates)  # Center of the overall graph
+  bezierMid <- c(fromC[1], toC[2])  # A midpoint, for bended edges
+  distance1 <- sum((graphCenter - bezierMid)^2)
+  if(distance1 < sum((graphCenter - c(toC[1], fromC[2]))^2)){
+    bezierMid <- c(toC[1], fromC[2])
+  }  # To select the best Bezier midpoint
+  bezierMid <- (fromC + toC + bezierMid) / 3  # Moderate the Bezier midpoint
+  if(curved == FALSE){bezierMid <- (fromC + toC) / 2}  # Remove the curve
+  
+  edge <- data.frame(bezier(c(fromC[1], bezierMid[1], toC[1]),  # Generate
[…]

### 2020-05-18 rayyan.R

@@ -1,0 +1,15 @@
+rayyan <- read.csv("articles.csv")
+rayyan <- rayyan[, c("key", "notes")]
+if(all(rayyan$key == unique_recs$id_num)){
+  unique_recs$rayyan <- NA
+  unique_recs$rayyan[rayyan$notes == " RAYYAN-INCLUSION: {\"Caspar\"=>\"Included\"}"] <- TRUE
+  unique_recs$rayyan[rayyan$notes == " RAYYAN-INCLUSION: {\"Caspar\"=>\"Excluded\"}"] <- FALSE
+} else {
+  stop("Rayyan and R id numbers did not match")
+}
+# Include papers for ASReview
+write.table(paste(unique_recs$id_num[which(unique_recs$rayyan)]-1, collapse = " "), "clipboard", quote = FALSE, row.names = FALSE, col.names = FALSE)
+
+# Exclude papers for ASReview
+write.table(paste(unique_recs$id_num[which(!unique_recs$rayyan)]-1, collapse = " "), "clipboard", quote = FALSE, row.names = FALSE, col.names = FALSE)
+

### 2020-05-18 study1.R

@@ -1,0 +1,150 @@
+library(data.table)
+library(bibliometrix)
+source("word_functions.R")
+exclude_terms <- readLines("exclude_terms.txt")
+dict_synon <- dget("dictionary_synonyms.txt")
+#recs <- convert2df(bibliometrix::readFiles("savedrecs_full.txt"))
+#saveRDS(recs, "savedrecs.RData")
+recs <- readRDS("recs_6653.RData")
+#recs <- unique_recs
+df <- lapply(recs$DE, function(x){strsplit(x, split = "; ")[[1]]})
+df <- data.table(word = tolower(unlist(df)), doc = rep(1:length(df), times = sapply(df, length)))
+
+#table(grep("disease", df$word, value = T))
+exclude_these <- unique(unlist(lapply(exclude_terms, grep, x = df$word)))
+
+df <- df[!exclude_these, ]
+
+res_cat <- cat_words(df$word, dict_synon)
+# head(sort(table(res_cat$words), decreasing = T), 20)
+# res_cat$dup
+# head(res_cat$unmatched)
+# writeClipboard(names(res_cat$unmatched))
+
+# Remove duplicate words per doc
+df[, word := res_cat$words]
+df[, id := paste0(word, doc)]
+df <- df[!duplicated(id), ]
+df[, id := NULL]
+#head(df)
+## Look at POS tags
+library(lattice)
+
+# What are these texts about? 
+library(topicmodels)
+library(udpipe)
+library(slam)
+
+nounbydoc <- df[, list(freq = .N), by = list(document = doc, term = word)]
+
+dtm <- udpipe::document_term_matrix(document_term_frequencies(nounbydoc)) # document_frequency_matrix(x)
+topterms <- col_sums(dtm)
+topterms <- sort(topterms, decreasing = TRUE)
+hist(topterms, breaks = 100)
+tt <- table(topterms)
+plot(1:10, tt[1:10], type = "l")
+topterms <- topterms[topterms > .005*nrow(recs)]
+
+topterms <- head(topterms, 250)
+topterms <- names(topterms)
+dtm_top <- dtm[, topterms]
+dtm_top <- dtm_top[row_sums(dtm_top) > 0, ]
+
+set.seed(43892)
+
+topics <- LDA(x = dtm_top, k = 5, method = "VEM", control = list(alpha = 0.1, estimate.alpha = TRUE, seed = as.integer(10:1), verbose = FALSE, nstart = 10, save = 0, best = TRUE))
[…]

### 2020-05-18 tm_references.R

@@ -1,0 +1,14 @@
+df <- read.table("c:/tmp/savedrecs.txt", sep = "\t", header = TRUE, quote = "", row.names = NULL, stringsAsFactors = FALSE, fileEncoding = "UTF-16")
+
+library(reticulate)
+ed <- import("editdistance")
+
+library(findpython)
+can_find_python_cmd(required_modules = "pattern.db")
+options('python_cmd'='C:/Python27/python.exe')
+Sys.setenv(PYTHON2 = "C:/Python27/python.exe")
+
+py_config()
+
+ts <- import_from_path("textrank", path = "c:/git_repositories/textrank")
+py_run_string('textrank extract-summary "c:\tmp\test_sum.txt"')

### 2020-05-18 tm_references2.R

@@ -1,0 +1,118 @@
+# https://www.bnosac.be/index.php/blog/56-an-overview-of-text-mining-visualisations-possibilities-with-r-on-the-ceta-trade-agreement
+library(data.table)
+count.matches <- function(pat, vec) sapply(regmatches(vec, gregexpr(pat, vec)), length)
+
+df <- read.table("c:/tmp/savedrecs.txt", sep = "\t", header = TRUE, quote = "", row.names = NULL, stringsAsFactors = FALSE, fileEncoding = "UTF-16")
+
+## Natural Language Processing: POS tagging
+library(pattern.nlp)
+#df <- df[1:33, ]
+if(!file.exists("df_tagged.RData")){
+  df_tagged <- lapply(1:nrow(df), function(thisrow){
+    tryCatch(cbind(pattern_pos(x = df$ID[thisrow], language = "english", core = TRUE), thisrow), error = function(e){NULL})
+  })  
+  saveRDS(df_tagged, "df_tagged.RData")
+} else {
+  df_tagged <- readRDS("df_tagged.RData")
+}
+dft <- rbindlist(df_tagged, use.names = FALSE)
+
+table(dft$word.type)[order(table(dft$word.type), decreasing = T)]
+
+## Take only nouns
+df_nouns <- dft[grepl("^NN", word.type), ]
+df_nouns <- df_nouns[count.matches("[a-z]", tolower(word.lemma)) > 2, ]
+
+
+## Look at POS tags
+library(lattice)
+barchart(sort(table(dft$word.type)), col = "lightblue", xlab = "Term frequency", 
+         main = "Parts of Speech Tag term frequency")
+head(dft[dft$word.type == "JJ", ])
+
+
+# Topic model -------------------------------------------------------------
+
+# What are these texts about? 
+library(topicmodels)
+library(udpipe)
+library(slam)
+
+nounbydoc <- df_nouns[, list(freq = .N), by = list(document = thisrow, term = word.lemma)]
+
+dtm <- udpipe::document_term_matrix(document_term_frequencies(nounbydoc)) # document_frequency_matrix(x)
+topterms <- col_sums(dtm)
+topterms <- sort(topterms, decreasing = TRUE)
+hist(topterms, breaks = 100)
+tt <- table(topterms)
+plot(1:10, tt[1:10], type = "l")
+topterms <- topterms[topterms > 5]
+topterms <- head(topterms, 250)
+topterms <- names(topterms)
[…]

### 2020-05-18 topterms.R

@@ -1,0 +1,18 @@
+df_tagged <- readRDS("df_tagged.RData")
+dft <- rbindlist(df_tagged, use.names = FALSE)
+
+df_sub <- dft[grepl("^VB", word.type), ]
+
+df_sub_sum <- df_sub[, list(freq = .N), by = list(document = thisrow, term = word.lemma)]
+df_sub_sum$freq <- 1
+dtm <- udpipe::document_term_matrix(document_term_frequencies(df_sub_sum))
+
+topterms <- col_sums(dtm)
+topterms <- sort(topterms, decreasing = TRUE)
+tt <- table(topterms)
+ggplot(data.frame(x = 1:10, y = as.vector(tt[1:10])), aes(x, y)) + geom_point()
+head(topterms)
+topterms <- topterms[topterms > 10]
+topterms <- head(topterms, 250)
+topterms <- names(topterms)
+tail(topterms)

### 2020-05-18 use_keywords.R

@@ -1,0 +1,148 @@
+library(data.table)
+library(bibliometrix)
+source("word_functions.R")
+exclude_terms <- readLines("exclude_terms.txt")
+dict_synon <- dget("dictionary_synonyms.txt")
+#recs <- convert2df(bibliometrix::readFiles("savedrecs_full.txt"))
+#saveRDS(recs, "savedrecs.RData")
+recs <- readRDS("9811_2.RData")
+recs <- unique_recs
+df <- lapply(recs$ID, function(x){strsplit(x, split = "; ")[[1]]})
+df <- data.table(word = unlist(df), doc = rep(1:length(df), times = sapply(df, length)))
+df$word <- tolower(df$word)
+table(grep("disease", df$word, value = T))
+exclude_these <- unique(unlist(lapply(exclude_terms, grep, x = df$word)))
+
+df <- df[!exclude_these, ]
+
+res_cat <- cat_words(df$word, dict_synon)
+head(sort(table(res_cat$words), decreasing = T), 20)
+res_cat$dup
+head(res_cat$unmatched)
+writeClipboard(names(res_cat$unmatched))
+
+# Remove duplicate words per doc
+df$word <- res_cat$words
+df$id <- paste0(df$word, df$doc)
+df <- df[!duplicated(df$id), -3]
+
+## Look at POS tags
+library(lattice)
+
+# What are these texts about? 
+library(topicmodels)
+library(udpipe)
+library(slam)
+
+nounbydoc <- df[, list(freq = .N), by = list(document = doc, term = word)]
+
+dtm <- udpipe::document_term_matrix(document_term_frequencies(nounbydoc)) # document_frequency_matrix(x)
+topterms <- col_sums(dtm)
+topterms <- sort(topterms, decreasing = TRUE)
+hist(topterms, breaks = 100)
+tt <- table(topterms)
+plot(1:10, tt[1:10], type = "l")
+topterms <- topterms[topterms > 2]
+topterms <- head(topterms, 250)
+topterms <- names(topterms)
+dtm_top <- dtm[, topterms]
+dtm_top <- dtm_top[row_sums(dtm_top) > 0, ]
+
+set.seed(43892)
+
+topics <- LDA(x = dtm_top, k = 5, method = "VEM", control = list(alpha = 0.1, estimate.alpha = TRUE, seed = as.integer(10:1), verbose = FALSE, nstart = 10, save = 0, best = TRUE))
+# What topics are there?
[…]

### 2020-05-18 visNetwork.R

@@ -1,0 +1,39 @@
+# Libraries ---------------------------------------------------------------
+library(visNetwork)
+library(geomnet)
+library(igraph)
+
+# Data Preparation --------------------------------------------------------
+
+#Nodes
+df_plot <- df_plot2
+
+df_plot$cooc <- scales::rescale(df_plot$cooc, from = range(df_plot$cooc), to = c(1, 10))
+nodes <- unique(c(df_plot$term1, df_plot$term2))
+nodes <- data.frame(id = nodes, label = nodes, stringsAsFactors = FALSE)
+#id has to be the same like from and to columns in edges
+
+#Edges
+edges <- df_plot
+colnames(edges) <- c("from", "to", "width")
+
+#Create graph for Louvain
+graph <- graph_from_data_frame(edges, directed = FALSE)
+
+#Louvain Comunity Detection
+cluster <- cluster_louvain(graph)
+
+cluster_df <- data.frame(as.list(membership(cluster)))
+cluster_df <- as.data.frame(t(cluster_df))
+cluster_df$label <- rownames(cluster_df)
+
+#Create group column
+nodes <- dplyr::left_join(nodes, cluster_df, by = "label")
+colnames(nodes)[3] <- "group"
+
+visNetwork(nodes, edges) %>%
+  visPhysics(solver = "repulsion", barnesHut = list(gravitationalConstant = -20000)) %>%
+  visSave(file = "tmp.html")
+
+visNetwork(nodes, edges) %>%
+  visPhysics(solver = "forceAtlas2Based", forceAtlas2Based = list(gravitationalConstant = -50))

### 2020-05-18 word_functions.R

@@ -1,0 +1,201 @@
+conflicting_matches <- function(words, dict){
+  dict_matches <- lapply(unlist(dict), function(this_reg){
+    grep(this_reg, words)
+  })
+  names(dict_matches) <- unlist(dict)
+  
+  tmp <- unlist(dict_matches)
+  dups <- unique(tmp[duplicated(tmp)])
+  dup_words <- words[dups]
+  dups <- dups[!duplicated(dup_words)]
+  dup_words <- words[dups]
+  if(length(dups)){
+    out <- lapply(dups, function(this_dup){
+      names(dict_matches)[sapply(dict_matches, `%in%`, x = this_dup)]
+    })
+    names(out) <- dup_words
+    out
+  }
+}
+unmatched <- function(words, dict){
+  dict_matches <- lapply(unlist(dict), function(this_reg){
+    grep(this_reg, words)
+  })
+  sort(table(words[c(1:length(words))[-unique(unlist(dict_matches))]]), decreasing = TRUE)
+}
+
+count_fun <- function(x) rowSums(x)>0
+
+cat_internal <- function(words, dict){
+  dict <- dict[order(names(dict))]
+  rexes <- unlist(dict)
+  reps <- sapply(dict, length)
+  new_name <- rep(names(dict), times = reps)
+  dict_matches <- sapply(rexes, function(this_reg){
+    grepl(this_reg, words, perl = TRUE)})
+  matches <- as.data.table(dict_matches)
+  dropthese <- vector("numeric")
+  for(this_name in names(dict)){
+    sum_cols <- which(new_name == this_name)
+    if(length(sum_cols) > 1){
+      matches[, (this_name) := count_fun(.SD), .SDcols=sum_cols]
+      dropthese <- append(dropthese, sum_cols)
+    }
+  }
+  matches[, (dropthese):=NULL]  
+  setcolorder(matches, names(dict))
+  matches
+}
+
+cat_words2 <- function(words, dict, resolve_dups){
+  dict <- dict[order(names(dict))]
+  resolve_dups <- dict[order(names(resolve_dups))]
+  rexes <- unlist(dict)
+  matches <- cat_internal(words, dict)
+  num_matches <- rowSums(matches)
+  onematch <- which(num_matches == 1)
+  outwords <- words
+  outwords[onematch] <- names(dict)[apply(matches[onematch, ] == 1, 1, which)]
+  out <- list(
+    words = outwords
+  )
+  if(any(num_matches > 1)){
[…]

### 2020-05-18 wos.R

@@ -1,0 +1,72 @@
+# pDjRe9w.HNEEDsY!
+wos <- function(tag){
+  tags <- c(FN = "File Name", VR = "Version Number", PT = "Publication Type (J=Journal; B=Book; S=Series; P=Patent)", 
+            AU = "Authors", AF = "Author Full Name", BA = "Book Authors", 
+            BF = "Book Authors Full Name", CA = "Group Authors", GP = "Book Group Authors", 
+            BE = "Editors", TI = "Document Title", SO = "Publication Name", 
+            SE = "Book Series Title", BS = "Book Series Subtitle", LA = "Language", 
+            DT = "Document Type", CT = "Conference Title", CY = "Conference Date", 
+            CL = "Conference Location", SP = "Conference Sponsors", HO = "Conference Host", 
+            DE = "Author Keywords", ID = "Keywords Plus®", AB = "Abstract", 
+            C1 = "Author Address", RP = "Reprint Address", EM = "E-mail Address", 
+            RI = "ResearcherID Number", OI = "ORCID Identifier (Open Researcher and Contributor ID)", 
+            FU = "Funding Agency and Grant Number", FX = "Funding Text", 
+            CR = "Cited References", NR = "Cited Reference Count", TC = "Web of Science Core Collection Times Cited Count", 
+            Z9 = "Total Times Cited Count (Web of Science Core Collection, BIOSIS Citation Index, Chinese Science Citation Database, Data Citation Index, Russian Science Citation Index, SciELO Citation Index)", 
+            U1 = "Usage Count (Last 180 Days)", U2 = "Usage Count (Since 2013)", 
+            PU = "Publisher", PI = "Publisher City", PA = "Publisher Address", 
+            SN = "International Standard Serial Number (ISSN)", EI = "Electronic International Standard Serial Number (eISSN)", 
+            BN = "International Standard Book Number (ISBN)", J9 = "29-Character Source Abbreviation", 
+            JI = "ISO Source Abbreviation", PD = "Publication Date", PY = "Year Published", 
+            VL = "Volume", IS = "Issue", SI = "Special Issue", PN = "Part Number", 
+            SU = "Supplement", MA = "Meeting Abstract", BP = "Beginning Page", 
[…]

### 2020-06-07 manuscript.Rmd
Final screening done

@@
 output            : papaja::apa6_pdf
+knit              : worcs:::cite_essential
 ---
@@
 <!-- Emotion regulation in adolescence is important -->
-A key developmental challenge in adolescence is acquiring mature emotion regulation skills [@croneUnderstandingAdolescencePeriod2012; @zimmermannEmotionRegulationEarly2014].
-Emotion regulation is integral to mental health[@aldaoEmotionregulationStrategiesPsychopathology2010; @schaferEmotionRegulationStrategies2017; @braetEmotionRegulationChildren2014] and social functioning [@reindlSocializationEmotionRegulation2016].
-For as many as one in five people, adolescence marks the onset of emotion regulation-related mental illness, which can persist throughout the life course [see @leeAdolescentMentalHealth2014].
-It is therefore crucial to identify which risk factors and environmental hazards render some adolescents more susceptible to emotional difficulties than others.
-Although there is an abundance of empirical work on adolescents' emotion regulation, the literature is somewhat fragmented, as the topic has been investigated from different (sub)disciplines.
-This study seeks to overcome this limitation by mapping all factors currently thought to be relevant to adolescent emotion regulation, based on a systematic review and bibliographic analysis.
-<!-- Ergens anders: Similarly, although there are several *relevant* theories, there is no specific theoretical framework to guide research on adolescents' emotion regulation.
-Although theory development is beyond the scope of this paper, we set out to generate a proto-theoretical nomological network of the potential risk factors, manifestations, and outcomes of emotion regulation in adolescence.
-We discuss how this nomological network relates to existing relevant theory, and conclude with recommendations for future theory-generating efforts.-->
+A key developmental challenge in adolescence is acquiring mature emotion
+regulation skills [@croneUnderstandingAdolescencePeriod2012;
+@zimmermannEmotionRegulationEarly2014]. Emotion regulation is integral to
+mental health[@aldaoEmotionregulationStrategiesPsychopathology2010;
+@schaferEmotionRegulationStrategies2017; @braetEmotionRegulationChildren2014]
+and social functioning [@reindlSocializationEmotionRegulation2016]. For as many
+as one in five people, adolescence marks the onset of emotion
+regulation-related mental illness, which can persist throughout the life course
+[see @leeAdolescentMentalHealth2014]. It is therefore crucial to identify which
+risk factors and environmental hazards render some adolescents more susceptible
+to emotional difficulties than others. Although there is an abundance of
+empirical work on adolescents' emotion regulation, the literature is somewhat
+fragmented, as the topic has been investigated from different (sub)disciplines.
+This study seeks to overcome this limitation by mapping all factors currently
+thought to be relevant to adolescent emotion regulation, based on a systematic
+review and bibliographic analysis. <!-- Ergens anders: Similarly, although
+there are several *relevant* theories, there is no specific theoretical
+framework to guide research on adolescents' emotion regulation. Although theory
+development is beyond the scope of this paper, we set out to generate a
+proto-theoretical nomological network of the potential risk factors,
+manifestations, and outcomes of emotion regulation in adolescence. We discuss
+how this nomological network relates to existing relevant theory, and conclude
+with recommendations for future theory-generating efforts.-->
 
@@
 
-Adolescence is defined as a life phase ranging from pubertal onset to adult-like independence [@steinbergAgeOpportunityLessons2014].
-This definition invokes both biological- and socio-cultural factors.
-It has been argued that, due to accellerated pubertal onset and delayed transitions to adult roles, adolescence now ranges from 10-24 years in the modern Western world [@sawyerAgeAdolescence2018].
+Adolescence is defined as a life phase ranging from pubertal onset to
+adult-like independence [@steinbergAgeOpportunityLessons2014]. This definition
+invokes both biological- and socio-cultural factors. It has been argued that,
+due to accellerated pubertal onset and delayed transitions to adult roles,
+adolescence now ranges from 10-24 years in the modern Western world
+[@sawyerAgeAdolescence2018].
 
 <!-- From Barriola:
-* adolescence, more than adulthood or childhood, is characterized by frequent and intense emotions (Larson et al. 1980; Larson and Lampmanpetraitis 1989).
-* signiﬁcant psychosocial changes that call for an increase in sophistication of ER strategies (Steinberg 2005)
-* novel stressors associated with social relationships, including pressures to conform to adult expectations relating to maturity, educational achievement, gender appropriate conduct, and other socially competent behaviors (Yap et al.
+* adolescence, more than adulthood or childhood, is characterized by frequent
+and intense emotions (Larson et al. 1980; Larson and Lampmanpetraitis 1989).
+* signi?cant psychosocial changes that call for an increase in sophistication
+of ER strategies (Steinberg 2005)
+* novel stressors associated with social relationships, including pressures to
+conform to adult expectations relating to maturity, educational achievement,
+gender appropriate conduct, and other socially competent behaviors (Yap et al.
 2007)
-* Additionally, adolescents have an increased orientation toward autonomy (Spear 2000) including autonomous emotional regulation-->
+* Additionally, adolescents have an increased orientation toward autonomy
+(Spear 2000) including autonomous emotional regulation-->
 
-Adolescence is increasingly seen as a developmentally sensitive period for mature emotion regulation skills.
-During this period, children experience rapid biological, cognitive, and social changes that prompt new emotional experiences, and tax existing regulatory abilities [@steinbergAgeOpportunityLessons2014].
-At the same time, the staggered development of motivational-emotional and regulatory brain circuits gives rise to a maturity gap, where youngsters pursue new experiences in life and love, without being fully prepared to cope with the emotional outcomes [@croneUnderstandingAdolescencePeriod2012].
-Due to these coalescing changes, adolescents display a restricted repertoire of emotion regulation strategies compared to younger or older individuals [@zimmermannEmotionRegulationEarly2014].
-Consequently, adolescents experience more frequent and intense (negative) emotions than children or adults [see @silkAdolescentsEmotionRegulation2003].
-The literature thus paints a picture of adolescence as a chrysalis for emotional development: Children enter this stage with emotion regulation skills adapted to the challenges of childhood.
-During adolescence, emotional systems are rearranged substantially.
-These changes render adolescents temporarily vulnerable to emotional dysregulation, but ultimately serve a functional role in acquiring mature emotion regulation skills.
-Eventually, most adolescents emerge ready to take on the challenges of early adulthood.
-Unfortunately, a sizeable proportion of adolescents instead manifests enduring emotional difficulties.
+Adolescence is increasingly seen as a developmentally sensitive period for
+mature emotion regulation skills. During this period, children experience rapid
+biological, cognitive, and social changes that prompt new emotional
+experiences, and tax existing regulatory abilities
+[@steinbergAgeOpportunityLessons2014]. At the same time, the staggered
+development of motivational-emotional and regulatory brain circuits gives rise
+to a maturity gap, where youngsters pursue new experiences in life and love,
+without being fully prepared to cope with the emotional outcomes
+[@croneUnderstandingAdolescencePeriod2012]. Due to these coalescing changes,
+adolescents display a restricted repertoire of emotion regulation strategies
+compared to younger or older individuals
+[@zimmermannEmotionRegulationEarly2014]. Consequently, adolescents experience
+more frequent and intense (negative) emotions than children or adults [see
+@silkAdolescentsEmotionRegulation2003]. The literature thus paints a picture of
+adolescence as a chrysalis for emotional development: Children enter this stage
+with emotion regulation skills adapted to the challenges of childhood. During
+adolescence, emotional systems are rearranged substantially. These changes
+render adolescents temporarily vulnerable to emotional dysregulation, but
+ultimately serve a functional role in acquiring mature emotion regulation
+skills. Eventually, most adolescents emerge ready to take on the challenges of
+early adulthood. Unfortunately, a sizeable proportion of adolescents instead
+manifests enduring emotional difficulties.
 
@@
 
-<!--Acquiring mature emotion regulation abilities is important, because t-->The consequences of difficulties in emotion regulation are extensive, well-documented, and persist throughout the life course.
-Meta-analyses indicate that such difficulties are associated with externalizing, and more strongly, with internalizing psychopathology [@aldaoEmotionregulationStrategiesPsychopathology2010; @schaferEmotionRegulationStrategies2017].
-Individuals who engage in maladaptive emotion regulation strategies also experience more negative emotions, diminished well-being, and greater strain in interpersonal relationships [@grossIndividualDifferencesTwo2003a; @bellRelationshipsInputsOutputs2000].
-<!--Adolescence also appears to be a key period for developing mature emotion regulation skills - but not all adolescents do so successfully.
-As many as one in five adolescents instead develop severe emotional difficulties.--> Given the prevalence of emotional difficulties and their extensive implications for individual mental health, wellbeing, and social functioning, and downstream cost to society as a whole [@leeAdolescentMentalHealth2014], it is essential to have a solid understanding of the risk factors associated with adolescents' emotion regulation difficulties.
+<!--Acquiring mature emotion regulation abilities is important, because t-->The
+consequences of difficulties in emotion regulation are extensive,
+well-documented, and persist throughout the life course. Meta-analyses indicate
+that such difficulties are associated with externalizing, and more strongly,
+with internalizing psychopathology
+[@aldaoEmotionregulationStrategiesPsychopathology2010;
+@schaferEmotionRegulationStrategies2017]. Individuals who engage in maladaptive
+emotion regulation strategies also experience more negative emotions,
+diminished well-being, and greater strain in interpersonal relationships
+[@grossIndividualDifferencesTwo2003a; @bellRelationshipsInputsOutputs2000].
+<!--Adolescence also appears to be a key period for developing mature emotion
+regulation skills - but not all adolescents do so successfully. As many as one
+in five adolescents instead develop severe emotional difficulties.--> Given the
+prevalence of emotional difficulties and their extensive implications for
+individual mental health, wellbeing, and social functioning, and downstream
+cost to society as a whole [@leeAdolescentMentalHealth2014], it is essential to
+have a solid understanding of the risk factors associated with adolescents'
+emotion regulation difficulties.
 
@@
 
-Theory is of paramount importance when seeking to understand or explain a phenomenon.
-Although there are many relevant theories, none have specifically addressed emotion regulation development in adolescence.
-Several recent publications have undertaken the monumental task of comprehensively reviewing theory relevant to emotional development [@bussTheoriesEmotionalDevelopment2019; @riedigerEmotionRegulationAdolescence2014].
-Thanks, in part, to their efforts, we can provide a summary review of the theoretical landscape as context for our empirical contribution.<!--Several recent publications have undertaken the monumental task of providing a comprehensive overview of theories of emotional development [e.g., @bussTheoriesEmotionalDevelopment2019; @holodynskiDevelopmentEmotionsEmotion2006; @riedigerEmotionRegulationAdolescence2014], and of the empirical work pertaining to emotions in adolescence [@coe-odessEmergentEmotionsAdolescence2019].
--->
-Two theories widely invoked to frame research on development, including emotional development, are Bronfenbrenner's bioecological model, and Sameroff's transactional model.
-Bronfenbrenner's model [@bronfenbrennerBioecologicalModelHuman2007] describes how the environment shapes individual development.
-Each individual is imbued with certain biological predispositions, and develops over time, in interaction with contextual influences.
-These influences range from the microsystem, composed of those people close to the individual, to the macrosystem, consisting of indirect political and economic influences, to the exosystem, consisting of cultural norms and values.
-Sameroff's model is somewhat compatible with the bioecological model [@sameroffUnifiedTheoryDevelopment2010], but focuses more on the interplay between nature and nurture.
-It conceptualizes development as a product of reciprocal influences between the child and the environment.
-Sameroff distinguishes between proximal influences, for instance, through parents (the microsystem in Bronfenbrenner's model), and distal influences; structural factors indirectly shaping development, like socio-economic status, schools, and the community (macro- and exosystem).
-With increasing age, distal influences gradually gain ground on proximal influences.
+Theory is of paramount importance when seeking to understand or explain a
+phenomenon. Although there are many relevant theories, none have specifically
+addressed emotion regulation development in adolescence. Several recent
+publications have undertaken the monumental task of comprehensively reviewing
+theory relevant to emotional development
+[@bussTheoriesEmotionalDevelopment2019;
+@riedigerEmotionRegulationAdolescence2014]. Thanks, in part, to their efforts,
+we can provide a summary review of the theoretical landscape as context for our
+empirical contribution.<!--Several recent publications have undertaken the
+monumental task of providing a comprehensive overview of theories of emotional
+development [e.g., @bussTheoriesEmotionalDevelopment2019;
+@holodynskiDevelopmentEmotionsEmotion2006;
+@riedigerEmotionRegulationAdolescence2014], and of the empirical work
+pertaining to emotions in adolescence
+[@coe-odessEmergentEmotionsAdolescence2019].  -->
+Two theories widely invoked to frame research on development, including
+emotional development, are Bronfenbrenner's bioecological model, and Sameroff's
+transactional model. Bronfenbrenner's model
+[@bronfenbrennerBioecologicalModelHuman2007] describes how the environment
+shapes individual development. Each individual is imbued with certain
+biological predispositions, and develops over time, in interaction with
+contextual influences. These influences range from the microsystem, composed of
+those people close to the individual, to the macrosystem, consisting of
+indirect political and economic influences, to the exosystem, consisting of
+cultural norms and values. Sameroff's model is somewhat compatible with the
+bioecological model [@sameroffUnifiedTheoryDevelopment2010], but focuses more
+on the interplay between nature and nurture. It conceptualizes development as a
+product of reciprocal influences between the child and the environment.
+Sameroff distinguishes between proximal influences, for instance, through
+parents (the microsystem in Bronfenbrenner's model), and distal influences;
+structural factors indirectly shaping development, like socio-economic status,
+schools, and the community (macro- and exosystem). With increasing age, distal
+influences gradually gain ground on proximal influences.
 
-Turning now towards theories specifically addressing emotion regulation in adolescence, Hall's notion of "storm and stress" is one of the oldest [see @arnettAdolescentStormStress1999].
-It describes how hormonal changes diminish self-control and increase reactivity, leading to difficulties in emotion regulation, conflict with parents, and risky behavior.
-Recent work provides a more nuanced perspective on this theory.
-For example, although the notion of diminished self-control and increased emotional reactivity has been upheld, it has been recast as a necessary change that facilitates emotional maturation [@croneUnderstandingAdolescencePeriod2012], at the risk of emotional disturbance [@arnettAdolescentStormStress1999; @leeAdolescentMentalHealth2014].
-More recently, Sroufe [-@sroufeEmotionalDevelopmentOrganization1995] presented a theory focused on normative emotional development in early childhood.
-It argues that, as children grow older, their increasing self-regulatory abilities drive a transition from external emotion regulation by primary caregivers towards autonomous emotion regulation.
-This theory focuses on two drivers of development: social and cognitive influences.
-Social influences mainly occur through parents' co-regulation, parenting behaviors, and parent-child attachment.
-Cognitive influences occur through the development of the central nervous system (CNS), cognition, and self-regulation.
-Several other theories, introduced below, have extemporized on these sources of influence.
+Turning now towards theories specifically addressing emotion regulation in
+adolescence, Hall's notion of "storm and stress" is one of the oldest [see
+@arnettAdolescentStormStress1999]. It describes how hormonal changes diminish
+self-control and increase reactivity, leading to difficulties in emotion
+regulation, conflict with parents, and risky behavior. Recent work provides a
+more nuanced perspective on this theory. For example, although the notion of
+diminished self-control and increased emotional reactivity has been upheld, it
+has been recast as a necessary change that facilitates emotional maturation
+[@croneUnderstandingAdolescencePeriod2012], at the risk of emotional
+disturbance [@arnettAdolescentStormStress1999; @leeAdolescentMentalHealth2014].
+More recently, Sroufe [-@sroufeEmotionalDevelopmentOrganization1995] presented
+a theory focused on normative emotional development in early childhood. It
+argues that, as children grow older, their increasing self-regulatory abilities
+drive a transition from external emotion regulation by primary caregivers
+towards autonomous emotion regulation. This theory focuses on two drivers of
+development: social and cognitive influences. Social influences mainly occur
+through parents' co-regulation, parenting behaviors, and parent-child
+attachment. Cognitive influences occur through the development of the central
+nervous system (CNS), cognition, and self-regulation. Several other theories,
+introduced below, have extemporized on these sources of influence.
 
-The emphasis on neorocognitive development as a driver of emotional development, including emotion regulation development, is echoed in several other models.
-For example, polyvagal theory closely links emotional experience - and regulation - to autonomous nervous system functioning [@porgesOrientingDefensiveWorld1995].
-A more recent neorocognitive theory, with substantial relevance to adolescents' emotion regulation development, is Crone and Dahl's model of social-affective engagement and goal flexibility [@croneUnderstandingAdolescencePeriod2012].
-This theory is based on the notion of a "maturity gap" in middle-adolescence, arising from a developmental asymmetry between motivational and inhibitory brain circuits [@craccoEmotionRegulationChildhood2017; @caseyBrakingAcceleratingAdolescent2011].
-However, it sets out to explain - to a greater extent than other writings - adolescents' diverging destinies; the question why some youngsters flourish while others languish.
-Crone and Dahl argue that adolescents' cognitive engagement is dynamically responsive to social and motivational goal salience.
-This flexibility, on the one hand, prepares adolescents to effectively engage cognitive systems in novel challenging situations in a way that facilitates developing mature regulatory abilities.
-On the other hand, it places them at risk to act impulsively in pursuit of peer approval.
-This theory focuses primarily on cognitive factors and the role of peers, with less attention to factors such as parenting.
+The emphasis on neorocognitive development as a driver of emotional
+development, including emotion regulation development, is echoed in several
+other models. For example, polyvagal theory closely links emotional experience
+- and regulation - to autonomous nervous system functioning
+[@porgesOrientingDefensiveWorld1995]. A more recent neorocognitive theory, with
+substantial relevance to adolescents' emotion regulation development, is Crone
+and Dahl's model of social-affective engagement and goal flexibility
+[@croneUnderstandingAdolescencePeriod2012]. This theory is based on the notion
+of a "maturity gap" in middle-adolescence, arising from a developmental
+asymmetry between motivational and inhibitory brain circuits
+[@craccoEmotionRegulationChildhood2017;
+@caseyBrakingAcceleratingAdolescent2011]. However, it sets out to explain - to
+a greater extent than other writings - adolescents' diverging destinies; the
+question why some youngsters flourish while others languish. Crone and Dahl
+argue that adolescents' cognitive engagement is dynamically responsive to
+social and motivational goal salience. This flexibility, on the one hand,
+prepares adolescents to effectively engage cognitive systems in novel
+challenging situations in a way that facilitates developing mature regulatory
+abilities. On the other hand, it places them at risk to act impulsively in
+pursuit of peer approval. This theory focuses primarily on cognitive factors
+and the role of peers, with less attention to factors such as parenting.
 
-A theory focused specifically on parents' role in emotion regulation development is Morris' tripartite model [-@morrisRoleFamilyContext2007].
-It describes three pathways through which parents shape emotion regulation development: Through observation and modeling, parenting practices, and the emotional family climate, which in turn involves attachment and marital relationship quality.
-Morris and colleagues also emphasize the relevance of fathers and siblings, and others have adapted the tripartite model to describe the role of peers in adolescents' emotion regulation development [@reindlSocializationEmotionRegulation2016].
+A theory focused specifically on parents' role in emotion regulation
+development is Morris' tripartite model [-@morrisRoleFamilyContext2007]. It
+describes three pathways through which parents shape emotion regulation
+development: Through observation and modeling, parenting practices, and the
+emotional family climate, which in turn involves attachment and marital
+relationship quality. Morris and colleagues also emphasize the relevance of
+fathers and siblings, and others have adapted the tripartite model to describe
+the role of peers in adolescents' emotion regulation development
+[@reindlSocializationEmotionRegulation2016].
 
-Aside from theories of emotional development, theories of the phenomenon of emotion regulation are also somewhat relevant.
-One influential theory is Gross' [-@grossHandbookEmotionRegulation2013] process model, which describes the process of emotion regulation, from eliciting cue to ultimate response.
-Individuals modulate the different stages of this process using strategies, consciously or otherwise.
-The effectiveness, desireability, and consequences of different strategies depend on the cultural context [see @bariolaChildAdolescentEmotion2011].
-Similar to Gross' theory, the social information processing theory of emotion also describe the role of intrapsychic processes and strategies in emotion experience and reulation [@lemeriseIntegratedModelEmotion2000].
+Aside from theories of emotional development, theories of the phenomenon of
+emotion regulation are also somewhat relevant. One influential theory is Gross'
+[-@grossHandbookEmotionRegulation2013] process model, which describes the
+process of emotion regulation, from eliciting cue to ultimate response.
+Individuals modulate the different stages of this process using strategies,
+consciously or otherwise. The effectiveness, desireability, and consequences of
+different strategies depend on the cultural context [see
+@bariolaChildAdolescentEmotion2011]. Similar to Gross' theory, the social
+information processing theory of emotion also describe the role of intrapsychic
+processes and strategies in emotion experience and reulation
+[@lemeriseIntegratedModelEmotion2000].
 
-Another theory worth mentioning in this context is @holodynskiDevelopmentEmotionsEmotion2006's internalization model of emotional development.
-It applies Vygotsky's theory of development to the domain of emotion, and presents a detailed integrated model of emotional experience and regulation.
-Like Sroufe's work, this work describes a transition from interpersonal to intrapersonal emotion regulation.
-Other important features of this work include the interplay between emotion and communication, and the internalization of the socio-cultural symbolic function of emotion throughout development.
-<!--Theories like this are particularly relevant to a fine-grained understanding of the process of emotion regulation, but their developmental relevance has unfortunately not yet been considered (REF Buss).
--->
+Another theory worth mentioning in this context is
+@holodynskiDevelopmentEmotionsEmotion2006's internalization model of emotional
+development. It applies Vygotsky's theory of development to the domain of
+emotion, and presents a detailed integrated model of emotional experience and
+regulation. Like Sroufe's work, this work describes a transition from
+interpersonal to intrapersonal emotion regulation. Other important features of
+this work include the interplay between emotion and communication, and the
+internalization of the socio-cultural symbolic function of emotion throughout
+development. <!--Theories like this are particularly relevant to a fine-grained
+understanding of the process of emotion regulation, but their developmental
+relevance has unfortunately not yet been considered (REF Buss). -->
 
-<!--Parents are widely considered to be the primary proximal influence driving emotion regulation development.
+<!--Parents are widely considered to be the primary proximal influence driving
+emotion regulation development.
 
@@
 @coe-odessEmergentEmotionsAdolescence2019;
-instead takes an inductive approach to map the correlates of adolescents' emotion regulation based on all available literature.
+instead takes an inductive approach to map the correlates of adolescents'
+emotion regulation based on all available literature.
 
-The present study instead takes an inductive approach to map the correlates of adolescents' emotion regulation based on all available literature.
-From this mapping, we proceed to classify correlates as potential risk factors, manifestations, and outcomes of adolescent emotion regulation.
-The results provide a conceptual overview of the existing literature, can help identify blind spots in existing theory, and might inspire new hypotheses to guide future deductive research.
+The present study instead takes an inductive approach to map the correlates of
+adolescents' emotion regulation based on all available literature. From this
+mapping, we proceed to classify correlates as potential risk factors,
+manifestations, and outcomes of adolescent emotion regulation. The results
+provide a conceptual overview of the existing literature, can help identify
+blind spots in existing theory, and might inspire new hypotheses to guide
+future deductive research.
 
-Several limitations emerge from prior efforts to provide an encompassing framework of this literature
+Several limitations emerge from prior efforts to provide an encompassing
+framework of this literature
 
-These efforts at unification have, thusfar, been conducted in a top-down, theory-driven manner.
+These efforts at unification have, thusfar, been conducted in a top-down,
+theory-driven manner.
 
-which motivates most youngsters to seek out challenges in life and love, but renders some of them vulnerable to emotion dysregulation.  -->
+which motivates most youngsters to seek out challenges in life and love, but
+renders some of them vulnerable to emotion dysregulation.  -->
 
@@
 
-Existing theoretical models have several limitations.
-One crucial shortcoming is the lack of explicit attention to the life phase of adolescence.
-This is unfortunate, as empirical research consistently indicates that adolescence is a crucial life phase for emotion regulation development.
-Adolescence differs qualitatively from infancy, childhood, and adulthood.
-It is therefore insufficient to simply extrapolate theories focused on these ages.
-Other theories do focus on adolescence specifically [e.g., @croneUnderstandingAdolescencePeriod2012], but only address emotion regulation in passing.
-A second, related, shortcoming is that some relevant theories lack a developmental component <!--, and thus lack a well-substantiated understanding of developmental processes--> [see @bussTheoriesEmotionalDevelopment2019; @croneUnderstandingAdolescencePeriod2012].
-A third shortcoming is that theories vary widely in scope: Some are very broad and all-encompassing, but somewhat non-specific, such as the biopsychosocial models of Bronfenbrenner and Sameroff.
-Others describe a specific phenomenon in great detail, but are not embedded in a larger unifying framework.
-Examples include Morris' tripartite model, Crone and Dahl's model, and polyvagal theory.
-It would be beneficial to bridge these two levels of theory.
-One limitation echoed across many publications in this field is that more theory formation is required to provide a unified framework that could guide future empirical work.
-The present study seeks to aid such theory development, by providing an inductive conceptual review of the field.
+Existing theoretical models have several limitations. One crucial shortcoming
+is the lack of explicit attention to the life phase of adolescence. This is
+unfortunate, as empirical research consistently indicates that adolescence is a
+crucial life phase for emotion regulation development. Adolescence differs
+qualitatively from infancy, childhood, and adulthood. It is therefore
+insufficient to simply extrapolate theories focused on these ages. Other
+theories do focus on adolescence specifically [e.g.,
+@croneUnderstandingAdolescencePeriod2012], but only address emotion regulation
+in passing. A second, related, shortcoming is that some relevant theories lack
+a developmental component <!--, and thus lack a well-substantiated
+understanding of developmental processes--> [see
+@bussTheoriesEmotionalDevelopment2019;
+@croneUnderstandingAdolescencePeriod2012]. A third shortcoming is that theories
+vary widely in scope: Some are very broad and all-encompassing, but somewhat
+non-specific, such as the biopsychosocial models of Bronfenbrenner and
+Sameroff. Others describe a specific phenomenon in great detail, but are not
+embedded in a larger unifying framework. Examples include Morris' tripartite
+model, Crone and Dahl's model, and polyvagal theory. It would be beneficial to
+bridge these two levels of theory. One limitation echoed across many
+publications in this field is that more theory formation is required to provide
+a unified framework that could guide future empirical work. The present study
+seeks to aid such theory development, by providing an inductive conceptual
+review of the field.
 
@@
 majority have been restricted to toddlers and young chil-
-dren and have only examined the inﬂuence of maternal,
+dren and have only examined the in?uence of maternal,
 and not paternal, expression.
-Most of the literature has addressed emotion regulation in adult or infant samples. A smaller, but substantial, portion of the literature has examined emotion regulation in adolescents. 
+Most of the literature has addressed emotion regulation in adult or infant
+samples. A smaller, but substantial, portion of the literature has examined
+emotion regulation in adolescents.
 -->
 
-<!-- Next paper: * Existing theory is not very specific, in the sense that it can give rise to concrete, testable predictions.
-"either is not guided by hypotheses of an explicit theory or cites a theory but does not explicitly test the theory." (Buss) (Smaldino)-->
-<!--Unfortunately, there is little theory about which risk factors and environmental hazards render adolescents susceptible to emotional difficulties11-->
+<!-- Next paper: * Existing theory is not very specific, in the sense that it
+can give rise to concrete, testable predictions. "either is not guided by
+hypotheses of an explicit theory or cites a theory but does not explicitly test
+the theory." (Buss) (Smaldino)-->
+<!--Unfortunately, there is little theory about which risk factors and
+environmental hazards render adolescents susceptible to emotional
+difficulties11-->
 
-<!--Initially, much of the research on emotion regulation focused on either adulthood or early childhood.
-In recent years, however, a substantial body of research on emotion regulation in adolescence has accrued.-->
+<!--Initially, much of the research on emotion regulation focused on either
+adulthood or early childhood. In recent years, however, a substantial body of
+research on emotion regulation in adolescence has accrued.-->
 
@@
 
-<!--Emotion regulation can be defined as the ability to modulate emotional experience and expression through automatic or deliberate processes. -->
+<!--Emotion regulation can be defined as the ability to modulate emotional
+experience and expression through automatic or deliberate processes. -->
 
@@
 
-A focus on theory is becoming increasingly important, given the concern about the replicability of social scientific findings [@KLEIN].
+A focus on theory is becoming increasingly important, given the concern about
+the replicability of social scientific findings [@KLEIN].
 
-Several authors of comprehensive reviews have noted that developmental theories of emotion are still in their infancy [@bussTheoriesEmotionalDevelopment2019].
-Several specific limitations of the theoretical landscapes precipitate the present study.
-First, although there are many *relevant* theories, few are focused specifically on emotion regulation.
-Second, the phase of adolescence is rarely addressed, although empirical research has indicated that this is a crucial period of emotion regulation development.
-"emotion theory has largely focused on adults, and emotional development theory has largely focused on infancy and early childhood (see Chap.
-24 on adolescent emotional development)." Buss et al 2019:20
+Several authors of comprehensive reviews have noted that developmental theories
+of emotion are still in their infancy [@bussTheoriesEmotionalDevelopment2019].
+Several specific limitations of the theoretical landscapes precipitate the
+present study. First, although there are many *relevant* theories, few are
+focused specifically on emotion regulation. Second, the phase of adolescence is
+rarely addressed, although empirical research has indicated that this is a
+crucial period of emotion regulation development.
+"emotion theory has largely focused on adults, and emotional development theory
+has largely focused on infancy and early childhood (see Chap. 24 on adolescent
+emotional development)." Buss et al 2019:20
 
@@
 
-While theory provides a top-down understanding of an area of research, literature reviews can provide a bottom-up, inductive understanding.
-Given the noted absence of a single overarching theory, reviews might provide additional insight into factors considered relevant in the etiology of adolescents' emotion regulation competencies.
-For example, a review by @bariolaChildAdolescentEmotion2011 addresses individual psychological factors such as temperament, and biological factors like neurocognitive development and genetic predispositions.
-Furthermore, they address proximal social influences, including parents, teachers, and peers, and specific mechanisms through which these individuals exert their influence, including parenting and modeling.
-Finally, they address distal factors, including the role of culture and the media.
-Barriola and colleagues also offer recommendations for future research, <!--most notably, they call for a robust theoretical framework to guide future research.--> calling for research on the role of parents beyond early childhood, and including the role of fathers - a limitation which has since been addressed by a new wave of empirical research on fathers' role in emotional development [@vanlissaRoleFathersMothers2019; @vanlissaMothersFathersQuantitative2020].
+While theory provides a top-down understanding of an area of research,
+literature reviews can provide a bottom-up, inductive understanding. Given the
+noted absence of a single overarching theory, reviews might provide additional
+insight into factors considered relevant in the etiology of adolescents'
+emotion regulation competencies. For example, a review by
+@bariolaChildAdolescentEmotion2011 addresses individual psychological factors
+such as temperament, and biological factors like neurocognitive development and
+genetic predispositions. Furthermore, they address proximal social influences,
+including parents, teachers, and peers, and specific mechanisms through which
+these individuals exert their influence, including parenting and modeling.
+Finally, they address distal factors, including the role of culture and the
+media. Barriola and colleagues also offer recommendations for future research,
+<!--most notably, they call for a robust theoretical framework to guide future
+research.--> calling for research on the role of parents beyond early
+childhood, and including the role of fathers - a limitation which has since
+been addressed by a new wave of empirical research on fathers' role in
+emotional development [@vanlissaRoleFathersMothers2019;
+@vanlissaMothersFathersQuantitative2020].
 
-Another review, by @coe-odessEmergentEmotionsAdolescence2019, offers a nuanced discussion of several issues that complement prior publications in this field.
-For instance, the authors cover the implications of physiological changes in detail, including neurocognitive development and pubertal maturation.
-As adolescents become increasingly individuated, conflict with parents peaks.
-This conflict, in turn, impacts emotion regulation, both in terms of day-to-day mood variability and dispositional emotion dysregulation [see also @vanlissaCostEmpathyParentadolescent2017].
-As parental importance diminishes, adolescents become increasingly oriented towards peers.
-This includes increased sensitivity to social status and norms, along with the associated increase in peer pressure and risk taking.
-Pubertal development also initiates the emergence of sexual and romantic behavior, and the intensification of both biological sex differences and gender stereotyped behavior.
-With regard to the process of emotion regulation, Coe-Odess and colleagues discuss the importance of strategies, and point out that, in addition to negative emotionality, positive emotionality also peaks in adolescence.
-Relatedly, the authors describe how hormonal changes precipitate an increased stress response, which might help explain adolescents' greater susceptibility to emotion dysregulation.
-Finally, going beyond the implications of cognitive development discussed in other publications, the authors discuss how an greater capacity for abstract thought relates to identity formation - a key challenge in adolescence [@meeusStudyAdolescentIdentity2011] - and to increased emotional understanding, and by extension, empathy [see also @vanlissaLongitudinalInterplayAffective2014].
+Another review, by @coe-odessEmergentEmotionsAdolescence2019, offers a nuanced
+discussion of several issues that complement prior publications in this field.
+For instance, the authors cover the implications of physiological changes in
+detail, including neurocognitive development and pubertal maturation. As
+adolescents become increasingly individuated, conflict with parents peaks. This
+conflict, in turn, impacts emotion regulation, both in terms of day-to-day mood
+variability and dispositional emotion dysregulation [see also
+@vanlissaCostEmpathyParentadolescent2017]. As parental importance diminishes,
+adolescents become increasingly oriented towards peers. This includes increased
+sensitivity to social status and norms, along with the associated increase in
+peer pressure and risk taking. Pubertal development also initiates the
+emergence of sexual and romantic behavior, and the intensification of both
+biological sex differences and gender stereotyped behavior. With regard to the
+process of emotion regulation, Coe-Odess and colleagues discuss the importance
+of strategies, and point out that, in addition to negative emotionality,
+positive emotionality also peaks in adolescence. Relatedly, the authors
+describe how hormonal changes precipitate an increased stress response, which
+might help explain adolescents' greater susceptibility to emotion
+dysregulation. Finally, going beyond the implications of cognitive development
+discussed in other publications, the authors discuss how an greater capacity
+for abstract thought relates to identity formation - a key challenge in
+adolescence [@meeusStudyAdolescentIdentity2011] - and to increased emotional
+understanding, and by extension, empathy [see also
+@vanlissaLongitudinalInterplayAffective2014].
 
-There are notable parallels between the relevant factors highlighted by these narrative reviews, and the aforementioned theoretical literature.
-Nevertheless, these literature reviews also touch upon issues that have received little attention in theoretical work.
-This highlights the value of both top-down and bottom-up approaches to understanding the phenomenon of adolescents' emotion regulation.
-One remaining limitation is that, to date, all reviews in this field have been unstructured narrative reviews.
-The present publication seeks to further complement preceding work by conducting a comprehensive empirical literature review, and mapping the factors associated with adolescent emotion regulation.
+There are notable parallels between the relevant factors highlighted by these
+narrative reviews, and the aforementioned theoretical literature. Nevertheless,
+these literature reviews also touch upon issues that have received little
+attention in theoretical work. This highlights the value of both top-down and
+bottom-up approaches to understanding the phenomenon of adolescents' emotion
+regulation. One remaining limitation is that, to date, all reviews in this
+field have been unstructured narrative reviews. The present publication seeks
+to further complement preceding work by conducting a comprehensive empirical
+literature review, and mapping the factors associated with adolescent emotion
+regulation.
 
@@
 
-The present paper aims to develop a nomological network of the constructs related to adolescent emotion dysregulation, based on a systematic review of the literature.
-A nomological network is a diagrammatic representation of a phenomenon; a proto-theoretical device that describes relationships between constructs relevant to the theory (REF: Cronbach & Meehl 1955; McKenna, 2006; Alavi 2018).
-It is a precursor to a more explicit theory of the phenomenon.
-The present paper uses an inductive approach to develop this nomological network.
-First, we conduct a systematic search to elicit a corpus of relevant literature.
-Second, we use text mining techniques to extract relevant constructs from the corpus.
-Third, we use a dictionary to pare down the extracted constructs to meaningful superordinate categories.
-Fourth, we map interrelations between these constructs.
-Fifth, we classify contstructs as potential predictors or outcomes, and we categorize predictors by level of analysis<!-- (CJ: Sameroff, which level of biopsychosocial)-->.
-<!-- t, using text mining to map potential predictors of adolescent emotion dysregulation.
-identify relevant constructs  of adolescents’ emotion regulation development, and moderators of parents’ role therein. The resulting insights are consolidated into theory.
+The present paper aims to develop a nomological network of the constructs
+related to adolescent emotion dysregulation, based on a systematic review of
+the literature. A nomological network is a diagrammatic representation of a
+phenomenon; a proto-theoretical device that describes relationships between
+constructs relevant to the theory [see @alaviAligningTheoryMethodology2018;
+@@cronbachConstructValidityPsychological1955;
+@@mastersonNomologicalNetworkResearch2009]. It is a precursor to a more
+explicit theory of the phenomenon. The present paper uses an inductive approach
+to develop this nomological network. First, we conduct a systematic search to
+elicit a corpus of relevant literature. Second, we use text mining techniques
+to extract relevant constructs from the corpus. Third, we use a dictionary to
+pare down the extracted constructs to meaningful superordinate categories.
+Fourth, we map interrelations between these constructs. Fifth, we classify
+contstructs as potential predictors or outcomes, and we categorize predictors
+by level of analysis<!-- (CJ: Sameroff, which level of biopsychosocial)-->.
+<!-- t, using text mining to map potential predictors of adolescent emotion
+dysregulation.
+identify relevant constructs of adolescents’ emotion regulation development,
+and moderators of parents’ role therein. The resulting insights are
+consolidated into theory.
 The present study intends to map the extant literature
-First, I will systematically review predictors currently considered relevant in the adolescent emotion regulation literature.  -->
+First, I will systematically review predictors currently considered relevant in
+the adolescent emotion regulation literature.  -->
 
@@
 
-All searches were conducted on Web of Science.
-The search strategy was based on procedures described by Staaks [@staaksSystematicReviewSearch].
-First, we manually constructed a reference set of 15 articles.
-Then we constructed a search string to retrieve these articles from Web of Science.
-The search was overly inclusive, returning 29 records.
-As these were all highly relevant, we updated the reference set to include all 29 results.
-Next, we tested our search string, which consisted of synonyms of emotion regulation and adolescence: <!-- ### Reference set Our reference set is documented in `reference_set.bib`.
--->
+All searches were conducted on Web of Science. The search strategy was based on
+procedures described by Staaks [@staaksSystematicReviewSearch]. First, we
+manually constructed a reference set of 15 articles. Then we constructed a
+search string to retrieve these articles from Web of Science. The search was
+overly inclusive, returning 29 records. As these were all highly relevant, we
+updated the reference set to include all 29 results. Next, we tested our search
+string, which consisted of synonyms of emotion regulation and adolescence: <!--
+### Reference set Our reference set is documented in `reference_set.bib`. -->
 ```
-TS=("emotio* regulation" OR "anger regulation" OR "sadness regulation" OR "emotion* competence" OR "emotion* adjustment" OR "emotio* dysregulation" OR "anger dysregulation" OR "sadness dysregulation" OR "emotio* problem*" OR "emotion* maladjustment") AND TS=(adolescent* OR teen* OR pubert* OR youth)
+TS=("emotio* regulation" OR "anger regulation" OR "sadness regulation" OR
+"emotion* competence" OR "emotion* adjustment" OR "emotio* dysregulation" OR
+"anger dysregulation" OR "sadness dysregulation" OR "emotio* problem*" OR
+"emotion* maladjustment") AND TS=(adolescent* OR teen* OR pubert* OR youth)
 ```
-This string returned 6653 results, and matched 25 of the 29 records in the reference set.
-Three search terms could be added to match all 29 reference set items.
-The terms `"emotio* socialization" OR "emotio* processes"`, as synonyms of emotion regulation, added 191 new hits.
-However, many of these hits were not directly relevant to emotion regulation.
-The term `"development*`, as synonym of adolescence, added 3628 new hits, many of which were not focused on the age range of adolescence.
-We thus deemed these terms to be overly inclusive, and proceeded with the original search string above.
+This string returned 6653 results, and matched 25 of the 29 records in the
+reference set. Three search terms could be added to match all 29 reference set
+items. The terms `"emotio* socialization" OR "emotio* processes"`, as synonyms
+of emotion regulation, added 191 new hits. However, many of these hits were not
+directly relevant to emotion regulation. The term `"development*"`, as synonym
+of adolescence, added 3628 new hits, many of which were not focused on the age
+range of adolescence. We thus deemed these terms to be overly inclusive, and
+proceeded with the original search string above.
 ```{r readrecs}
@@
   saveRDS(unique_recs, filenam)
-  write.csv(data.frame(dup_doi = sum(dup_doi), dup_title = (nrow(recs)-nrow(unique_recs))-sum(dup_doi)), "dups.csv")
+  write.csv(data.frame(dup_doi = sum(dup_doi), dup_title = (nrow(recs)-nrow(unique_recs))-sum(dup_doi)), "dups.csv", row.names = FALSE)
 } else {
@@
 unique_recs$id_num <- 1:nrow(unique_recs)
+
+if(FALSE){
+  # df_screen <- unique_recs[, c("id_num", "TI", "AB")]
+  # names(df_screen) <- c("id_num", "title", "abstract")
+  # write.csv(df_screen, file = "asreview.csv", row.names = FALSE, fileEncoding = "UTF-8")
+  df_screen <- unique_recs[, c("id_num", "TI", "AU", "SO", "SN", "VL", "IS", "BP", "PY", "PU", "DI", "AB")]
+  names(df_screen) <- c("key", "title", "authors", "journal", "issn", "volume", "issue", "pages", "year", "publisher", "url", "abstract")
+  write.csv(df_screen, file = "rayyan.csv", row.names = FALSE)
+}
+rayyan_res <- read.csv("rayyan_exports/articles.csv")
+rayyan_dups <- nrow(unique_recs) - nrow(rayyan_res)
+
 ```
-Duplicates were identified based on exact DOI matches (`r dups[["dup_doi"]]` duplicates), and title similarity (`r dups[["dup_title"]]` duplicates).
-Manual screening in Rayyan resulted in the removal of an additional 13 duplicates.
+Duplicates were identified based on exact DOI matches (`r dups[["dup_doi"]]` 
+duplicates), and title similarity (`r dups[["dup_title"]]` duplicates). 
+Manual screening in Rayyan resulted in the removal of an additional `r rayyan_dups` duplicates.
 
@@
 
-```{r}
-head(unique_recs$SN)
-df_screen <- unique_recs[, c("id_num", "TI", "AB")]
-names(df_screen) <- c("id_num", "title", "abstract")
-write.csv(df_screen, file = "asreview.csv", row.names = FALSE, fileEncoding = "UTF-8")
-df_screen <- unique_recs[, c("id_num", "TI", "AU", "SO", "SN", "VL", "IS", "BP", "PY", "PU", "DI", "AB")]
-names(df_screen) <- c("key", "title", "authors", "journal", "issn", "volume", "issue", "pages", "year", "publisher", "url", "abstract")
-write.csv(df_screen, file = "rayyan.csv", row.names = FALSE)
+```{r, message=FALSE}
+screen <- read.csv("asreview_result_sysrevemotprob.csv")
+screen <- screen[screen$key %in% rayyan_res$key, ]
+screen$drop_these <- FALSE
+screen$drop_these[which(screen$included == 1 | screen$rayyan == "False")] <- TRUE
 
+if(!file.exists("recs_final.csv")){
+  recs_final <- unique_recs[screen$key[!screen$drop_these], ]
+write.csv(recs_final, "recs_final.csv", row.names = FALSE)
+} else {
+  recs_final <- read.csv("recs_final.csv")
+}
 ```
-We manually screened 500 abstracts for suitability in Rayyan.
-Then, we used ASReview to rank the predicted relevance of all papers based on the manually included and excluded articles.
-We screened the lowest-ranked articles to find an inflection point below which most articles were irrelevant, and excluded those from analysis.
+Papers were screened based on two main criteria: First, papers had to address emotion regulation, emotional problems, or similar.
+Second, the target population must overlap (at least in part) with adolescence, defined as the age range from 10-25.
+Thus, for example, an article reviewing the role of hormonal changes in emotional adjustment throughout the entire life course, including adolescence, would be deemed relevant.
+Screening was initially conducted in Rayyan QRCI [@Ouzzani2016].
+Papers were sorted using Rayyan's ranking algorithm.
+To train the algorithm on exclusion criteria, screening focused on abstracts most likely to be excluded.
+After coding `r sum(screen$rayyan == "True")+sum(screen$rayyan == "False")` papers, screening continued in ASReview - a free, open source alternative to Rayyan QRCI [@van_de_schoot_rens_2020_3828293].
+This program uses text mining and active learning to build a customizable machine learning model for article inclusion.
+We used a naive Bayes model, and focused on exclusion of irrelevant papers.
+In ASReview, an additional `r sum(table(screen$included, screen$rayyan)[, 1])` papers were screened.
+Screening again focused on articles most likely to be excluded, and continued until, among the most recently screened 100 papers, only 6 were excluded.
+The screening procedure is detailed in Figure \@ref(prismachart).
+In total, `r nrow(recs_final)` papers were retained for analysis.
+
+```{r prismachart, fig.cap="Record screening flowchart"}
+library(tidySEM)
+
+lo <- matrix(c("start", "dedup", "rayyan", "asreview", "included",
+               "", "dedup2", "excluded", "", ""), nrow = 5, ncol = 2)
+nodes <- data.frame(
+  name = c("start", "dedup", "dedup2", "rayyan", "asreview", "included", "excluded"), 
+  label = c(
+    paste0("Records identified through\nWeb of Science (n = ", nrow(recs), ")"), 
+    paste0("Records after duplicates removed\n(n = ", nrow(unique_recs), ")"), 
+    paste0("Duplicates removed\n(n = ", nrow(recs)-nrow(screen), ")"), 
+    paste0("Articles screened for eligibility\nusing Rayyan (n = ", nrow(screen), ")"), 
+    paste0("Articles screened for eligibility\nusing ASReview (n = ", nrow(screen), ")"), 
+    paste0("Studies included in\nqualitative synthesis (n = ", nrow(recs_final), ")"),
+    paste0("Excluded studies (n = ", nrow(screen)-nrow(recs_final), ")"))
+)
+edges <- data.frame(
+  from = c("start", "dedup", "rayyan", "asreview",
+           "dedup", "rayyan", "rayyan", "asreview"),
+  to = c("dedup", "rayyan", "asreview", "included",
+         "dedup2", "dedup2", "excluded", "excluded"),
+  label = c("",   "", sum(screen$rayyan == "True"), "",
+            paste0("n = ", sum(dups)), 
+            paste0("n = ", rayyan_dups),
+            paste0("n = ", sum(screen$rayyan == "False")),
+            paste0("n = ", sum(screen$included == 1, na.rm = TRUE)-sum(screen$rayyan == "False"))
+  )
+)
+p <- graph_sem(layout = lo, nodes = nodes, edges = edges, angle = 1, rect_height = 1.2, rect_width = 1.3)
+ggsave("prismachart.png", p, device = "png")
+ggsave("prismachart.svg", p, device = "svg")
+knitr::include_graphics("prismachart.svg")
+```
 
@@
 
-For this first analysis, we relied on author-provided keywords. We extracted keywords by document, and used a dictionary approach to classify closely related terms.
+For this first analysis, we relied on author-provided keywords.
+We extracted keywords by document, and used a dictionary approach
+to classify closely related terms.
+The dictionary was created specifically for this study.
+The lead author composed a first draft of the dictionary based on prior knowledge of the field.
+This draft was subsequently updated in two ways:
+First, while writing the introduction for this paper, key terms from the theoretical and empirical literature were added to the dictionary.
+Second, by including commonly occurring uncategorized words during preliminary analyses of the data.
+An exclusion list of methodological terms and other non-substantive words was generated using the same procedure.
 
@@
 
-This second analysis focused on the abstracts of our corpus.
-Keywords are carefully chosen to capture the core tenets of a study.
-However, as authors are typically limited to 5 keywords, some of a study's nuance may be lost.
-Abstracts offer greater freedom of expression, which is a challenge when it comes to extracting relevant information.
-We took a two-pronged approach to extract relevant topic terms from the abstracts.
-First, we used the natural language processing technique part-of-speech tagging (POS-tagging) to identify nouns in the abstract.
-Using nouns only in text mining can lead to more interpretable models [@martinMoreEfficientTopic2015].
-Secondly, we used stemming to reduce these nouns to their root form.
-Finally, we applied a dictionary approach as before.
+This second analysis focused on the abstracts of our corpus. Keywords are
+carefully chosen to capture the core tenets of a study. However, as authors are
+typically limited to 5 keywords, some of a study's nuance may be lost.
+Abstracts offer greater freedom of expression, which is a challenge when it
+comes to extracting relevant information. We took a two-pronged approach to
+extract relevant topic terms from the abstracts. First, we used the natural
+language processing technique part-of-speech tagging (POS-tagging) to identify
+nouns in the abstract. Using nouns only in text mining can lead to more
+interpretable models [@martinMoreEfficientTopic2015]. Secondly, we used
+stemming to reduce these nouns to their root form. Finally, we applied a
+dictionary approach as before.
 

### 2020-06-07 manuscript.tex
Final screening done

@@
 \hypersetup{
-  pdftitle={Mapping the predictors of adolescent emotion dysregulation: A text-mining based systematic review},
+  pdftitle={Mapping factors associated with adolescents' emotion dysregulation: A text-mining based systematic review},
   pdfkeywords={keywords},
@@
 
-\title{Mapping the predictors of adolescent emotion dysregulation: A text-mining based systematic review}
+\title{Mapping factors associated with adolescents' emotion dysregulation: A text-mining based systematic review}
 
@@
 
-A key developmental challenge in adolescence is acquiring mature emotion regulation skills (Crone \& Dahl, 2012; Zimmermann \& Iwanski, 2014).
-Emotion regulation is integral to mental health(Aldao, Nolen-Hoeksema, \& Schweizer, 2010; Braet et al., 2014; Schäfer, Naumann, Holmes, Tuschen-Caffier, \& Samson, 2017) and social functioning (Reindl, Gniewosz, \& Reinders, 2016).
-For as many as one in five adolescents, this phase marks the onset of emotion regulation-related mental illness, which can persist throughout the life course (see Lee et al., 2014).
-It is therefore crucial to identify which risk factors and environmental hazards render some adolescents more susceptible to emotional difficulties than others.
-Although there is an abundance of empirical work on factors associated with adolescents' emotion regulation, the literature is somewhat fragmented, as the topic has been investigated from different (sub)disciplines.
-This study seeks to address this limitation by mapping all factors currently thought to be relevant to adolescent emotion regulation, based on a systematic review of the literature.
-Similarly, although there are several \emph{relevant} theories, there is no specific theoretical framework to guide research on adolescents' emotion regulation.
-Although theory development is beyond the scope of this paper, we set out to generate a proto-theoretical nomological network of the potential risk factors, manifestations, and outcomes of emotion regulation in adolescence.
-We discuss how this nomological network relates to existing relevant theory, and conclude with recommendations for future theory-generating efforts.
+A key developmental challenge in adolescence is acquiring mature emotion
+regulation skills (Crone \& Dahl, 2012; Zimmermann \& Iwanski, 2014). Emotion regulation is integral to
+mental health(Aldao, Nolen-Hoeksema, \& Schweizer, 2010; Braet et al., 2014; Schäfer, Naumann, Holmes, Tuschen-Caffier, \& Samson, 2017)
+and social functioning (Reindl, Gniewosz, \& Reinders, 2016). For as many
+as one in five people, adolescence marks the onset of emotion
+regulation-related mental illness, which can persist throughout the life course
+(see Lee et al., 2014). It is therefore crucial to identify which
+risk factors and environmental hazards render some adolescents more susceptible
+to emotional difficulties than others. Although there is an abundance of
+empirical work on adolescents' emotion regulation, the literature is somewhat
+fragmented, as the topic has been investigated from different (sub)disciplines.
+This study seeks to overcome this limitation by mapping all factors currently
+thought to be relevant to adolescent emotion regulation, based on a systematic
+review and bibliographic analysis.
 
-There have been only few notable efforts to provide an encompassing framework (Buss, Cole, \& Zhou, 2019; Coe-Odess, Narr, \& Allen, 2019; Riediger \& Klipker, 2014). Yet several limitations remain.
+\hypertarget{why-adolescence-is-an-important-life-phase-for-emotion-regulation}{%
+\subsection{Why adolescence is an important life phase for emotion regulation}\label{why-adolescence-is-an-important-life-phase-for-emotion-regulation}}
 
-instead takes an inductive approach to map the correlates of adolescents' emotion regulation based on all available literature.
+Adolescence is defined as a life phase ranging from pubertal onset to
+adult-like independence (Steinberg, 2014). This definition
+invokes both biological- and socio-cultural factors. It has been argued that,
+due to accellerated pubertal onset and delayed transitions to adult roles,
+adolescence now ranges from 10-24 years in the modern Western world
+(Sawyer, Azzopardi, Wickremarathne, \& Patton, 2018).
 
-The present study instead takes an inductive approach to map the correlates of adolescents' emotion regulation based on all available literature.
-From this mapping, we proceed to classify correlates as potential risk factors, manifestations, and outcomes of adolescent emotion regulation.
-The results provide a conceptual overview of the existing literature, can help identify blind spots in existing theory, and might inspire new hypotheses to guide future deductive research.
+Adolescence is increasingly seen as a developmentally sensitive period for
+mature emotion regulation skills. During this period, children experience rapid
+biological, cognitive, and social changes that prompt new emotional
+experiences, and tax existing regulatory abilities
+(Steinberg, 2014). At the same time, the staggered
+development of motivational-emotional and regulatory brain circuits gives rise
+to a maturity gap, where youngsters pursue new experiences in life and love,
+without being fully prepared to cope with the emotional outcomes
+(Crone \& Dahl, 2012). Due to these coalescing changes,
+adolescents display a restricted repertoire of emotion regulation strategies
+compared to younger or older individuals
+(Zimmermann \& Iwanski, 2014). Consequently, adolescents experience
+more frequent and intense (negative) emotions than children or adults (see Silk, Steinberg, \& Morris, 2003). The literature thus paints a picture of
+adolescence as a chrysalis for emotional development: Children enter this stage
+with emotion regulation skills adapted to the challenges of childhood. During
+adolescence, emotional systems are rearranged substantially. These changes
+render adolescents temporarily vulnerable to emotional dysregulation, but
+ultimately serve a functional role in acquiring mature emotion regulation
+skills. Eventually, most adolescents emerge ready to take on the challenges of
+early adulthood. Unfortunately, a sizeable proportion of adolescents instead
+manifests enduring emotional difficulties.
 
-Several limitations emerge from prior efforts to provide an encompassing framework of this literature
+\hypertarget{the-consequences-of-difficulties-in-emotion-regulation}{%
+\subsection{The consequences of difficulties in emotion regulation}\label{the-consequences-of-difficulties-in-emotion-regulation}}
 
-These efforts at unification have, thusfar, been conducted in a top-down, theory-driven manner.
+The
+consequences of difficulties in emotion regulation are extensive,
+well-documented, and persist throughout the life course. Meta-analyses indicate
+that such difficulties are associated with externalizing, and more strongly,
+with internalizing psychopathology
+(Aldao et al., 2010; Schäfer et al., 2017). Individuals who engage in maladaptive
+emotion regulation strategies also experience more negative emotions,
+diminished well-being, and greater strain in interpersonal relationships
+(Bell \& Calkins, 2000; Gross \& John, 2003).
+Given the
+prevalence of emotional difficulties and their extensive implications for
+individual mental health, wellbeing, and social functioning, and downstream
+cost to society as a whole (Lee et al., 2014), it is essential to
+have a solid understanding of the risk factors associated with adolescents'
+emotion regulation difficulties.
 
@@
 
-Several recent publications have undertaken the monumental task of providing a comprehensive overview of theories of emotional development (e.g., Buss et al., 2019; {\textbf{???}}; Riediger \& Klipker, 2014), and of the empirical work pertaining to emotions in adolescence (Coe-Odess et al., 2019).
-We provide a summary review of the theoretical landscape as context for our empirical contribution.
+Theory is of paramount importance when seeking to understand or explain a
+phenomenon. Although there are many relevant theories, none have specifically
+addressed emotion regulation development in adolescence. Several recent
+publications have undertaken the monumental task of comprehensively reviewing
+theory relevant to emotional development
+(Buss, Cole, \& Zhou, 2019; Riediger \& Klipker, 2014). Thanks, in part, to their efforts,
+we can provide a summary review of the theoretical landscape as context for our
+empirical contribution.
+Two theories widely invoked to frame research on development, including
+emotional development, are Bronfenbrenner's bioecological model, and Sameroff's
+transactional model. Bronfenbrenner's model
+(Bronfenbrenner \& Morris, 2007) describes how the environment
+shapes individual development. Each individual is imbued with certain
+biological predispositions, and develops over time, in interaction with
+contextual influences. These influences range from the microsystem, composed of
+those people close to the individual, to the macrosystem, consisting of
+indirect political and economic influences, to the exosystem, consisting of
+cultural norms and values. Sameroff's model is somewhat compatible with the
+bioecological model ({\textbf{???}}), but focuses more
+on the interplay between nature and nurture. It conceptualizes development as a
+product of reciprocal influences between the child and the environment.
+Sameroff distinguishes between proximal influences, for instance, through
+parents (the microsystem in Bronfenbrenner's model), and distal influences;
+structural factors indirectly shaping development, like socio-economic status,
+schools, and the community (macro- and exosystem). With increasing age, distal
+influences gradually gain ground on proximal influences.
 
-Two of the most frequently cited theories in research on development, including emotional development, are biopsychosocial models.
-One is Bronfenbrenner's bioecological model, which describes how the environment shapes individual development.
-The individual is imbued with certain biological predispositions, and changes over the course of developmental time.
-Moreover, this individual development takes place in interaction with contextual influences.
-These range from the microsystem, composed of other people in close interaction with the individual, to the macrosystem, consisting of indirect political and economic influences, to the exosystem, consisting of cultural norms and values.
-Sameroff's transactional model is another bioecological theory, which focuses heavily on social influences (the microsystem in Bronfenbrenner's model).
-Its main contribution is that it conceptualized development as a product of reciprocal influences between child and parent (or another individual).
+Turning now towards theories specifically addressing emotion regulation in
+adolescence, Hall's notion of \enquote{storm and stress} is one of the oldest (see Arnett, 1999). It describes how hormonal changes diminish
+self-control and increase reactivity, leading to difficulties in emotion
+regulation, conflict with parents, and risky behavior. Recent work provides a
+more nuanced perspective on this theory. For example, although the notion of
+diminished self-control and increased emotional reactivity has been upheld, it
+has been recast as a necessary change that facilitates emotional maturation
+(Crone \& Dahl, 2012), at the risk of emotional
+disturbance (Arnett, 1999; Lee et al., 2014).
+More recently, Sroufe (1995) presented
+a theory focused on normative emotional development in early childhood. It
+argues that, as children grow older, their increasing self-regulatory abilities
+drive a transition from external emotion regulation by primary caregivers
+towards autonomous emotion regulation. This theory focuses on two drivers of
+development: social and cognitive influences. Social influences mainly occur
+through parents' co-regulation, parenting behaviors, and parent-child
+attachment. Cognitive influences occur through the development of the central
+nervous system (CNS), cognition, and self-regulation. Several other theories,
+introduced below, have extemporized on these sources of influence.
 
-With regard to theories specifically addressing emotion regulation in adolescence, Hall's notion of \enquote{storm and stress} is one of the oldest.
-It describes how hormonal changes diminish self-control and increase reactivity, leading to difficulties in emotion regulation, conflict with parents, and risky behavior.
-Recent work provides a more nuanced perspective on this theory.
-For example, although the notion of diminished self-control and increased emotional reactivity has been upheld, it has been recast as a necessary change that facilitates emotional maturation (Crone \& Dahl, 2012), at the risk of emotional disturbance (Arnett, 1999; Lee et al., 2014).
-This again highlights the importance of identifying factors that predict or explain between-adolescent differences in emotional dysregulation.
+The emphasis on neorocognitive development as a driver of emotional
+development, including emotion regulation development, is echoed in several
+other models. For example, polyvagal theory closely links emotional experience
+- and regulation - to autonomous nervous system functioning
+(Porges, 1995). A more recent neorocognitive theory, with
+substantial relevance to adolescents' emotion regulation development, is Crone
+and Dahl's model of social-affective engagement and goal flexibility
+(Crone \& Dahl, 2012). This theory is based on the notion
+of a \enquote{maturity gap} in middle-adolescence, arising from a developmental
+asymmetry between motivational and inhibitory brain circuits
+({\textbf{???}}; Cracco, Goossens, \& Braet, 2017). However, it sets out to explain - to
+a greater extent than other writings - adolescents' diverging destinies; the
+question why some youngsters flourish while others languish. Crone and Dahl
+argue that adolescents' cognitive engagement is dynamically responsive to
+social and motivational goal salience. This flexibility, on the one hand,
+prepares adolescents to effectively engage cognitive systems in novel
+challenging situations in a way that facilitates developing mature regulatory
+abilities. On the other hand, it places them at risk to act impulsively in
+pursuit of peer approval. This theory focuses primarily on cognitive factors
+and the role of peers, with less attention to factors such as parenting.
 
-Another theory of emotion regulation development was proposed by Sroufe (1995).
-This theory focuses on normative emotional development in early childhood.
-It argues that children's self-regulatory abilities increase with age, which drives a transition from external emotion regulation by primary caregivers towards autonomous emotion regulation.
-This work describes social and cognitive influences.
-Social influences mainly occur through parents' co-regulation, parenting behaviors, and parent-child attachment.
-Cognitive influences occur through the development of the central nervous system (CNS), cognition, and self-regulation.
-This emphasis on neorocognitive development is mirrored in polyvagal theory (Porges, 1995), which closely links emotional experience - and regulation - to autonomous nervous system functioning.
+A theory focused specifically on parents' role in emotion regulation
+development is Morris' tripartite model (2007). It
+describes three pathways through which parents shape emotion regulation
+development: Through observation and modeling, parenting practices, and the
+emotional family climate, which in turn involves attachment and marital
+relationship quality. Morris and colleagues also emphasize the relevance of
+fathers and siblings, and others have adapted the tripartite model to describe
+the role of peers in adolescents' emotion regulation development
+(Reindl et al., 2016).
 
-A more recent neorocognitive theory, with greater relevance to adolescents' emotion regulation development, is Crone and Dahl's model of social-affective engagement and goal flexibility (Crone \& Dahl, 2012).
-This theory is based on the notion of a \enquote{maturity gap} in middle-adolescence, arising from a developmental asymmetry between motivational and inhibitory brain circuits ({\textbf{???}}; Cracco, Goossens, \& Braet, 2017).
-However, it explicitly sets out to explain adolescents' diverging destinies - the observation that some youngsters flourish while others languish.
-Crone and Dahl argue that adolescents' cognitive engagement is dynamically responsive to social and motivational goal salience.
-This flexibility, on the one hand, prepares adolescents to effectively engage cognitive systems in novel challenging situations in a way that facilitates developing mature regulatory abilities.
-On the other hand, it places them at risk to act impulsively in pursuit of peer approval.
-This theory focuses primarily on cognitive factors and the role of peers, with little reference to parenting or other factors.
+Aside from theories of emotional development, theories of the phenomenon of
+emotion regulation are also somewhat relevant. One influential theory is Gross'
+(2013) process model, which describes the
+process of emotion regulation, from eliciting cue to ultimate response.
+Individuals modulate the different stages of this process using strategies,
+consciously or otherwise. The effectiveness, desireability, and consequences of
+different strategies depend on the cultural context (see Bariola, Gullone, \& Hughes, 2011). Similar to Gross' theory, the social
+information processing theory of emotion also describe the role of intrapsychic
+processes and strategies in emotion experience and reulation
+(Lemerise \& Arsenio, 2000).
 
-A theory focused specifically on parents' role in emotion regulation development is Morris' tripartite model (2007).
-It describes three pathways through which parents shape emotion regulation development: Through observation and modeling, parenting practices, and the emotional family climate, which in turn involves attachment and marital relationship quality.
-Morris and colleagues also emphasize the relevance of fathers and siblings, and others have adapted the tripartite model to describe the role of peers in adolescents' emotion regulation development (Reindl et al., 2016).
+Another theory worth mentioning in this context is
+Holodynski and Friedlmeier (2006)'s internalization model of emotional
+development. It applies Vygotsky's theory of development to the domain of
+emotion, and presents a detailed integrated model of emotional experience and
+regulation. Like Sroufe's work, this work describes a transition from
+interpersonal to intrapersonal emotion regulation. Other important features of
+this work include the interplay between emotion and communication, and the
+internalization of the socio-cultural symbolic function of emotion throughout
+development.
 
-Holodynski and Friedlmeier's ({\textbf{???}}) internalization theory applies Vygotsky's theory of development to the domain of emotion.
-Like Sroufe's work, it captures the transition from interpersonal to intrapersonal emotion regulation.
-Unique features of this work include, most notably, the integrative view of emotion and emotion regulation, the interplay between emotion and communication, and the role of culture in emotion regulation development.
+\hypertarget{shortcomings-of-the-theory}{%
+\subsection{Shortcomings of the theory}\label{shortcomings-of-the-theory}}
 
-Aside from theories of emotional development, theories of the phenomenon of emotion regulation are also somewhat relevant.
-One influential theory is Gross' (2013) process model, which describes the process of emotion regulation, from eliciting cue to ultimate response.
-Individuals modulate the different stages of this process using strategies, consciously or otherwise.
-The effectiveness, desireability, and consequences of different strategies depend on the cultural context (see Bariola, Gullone, \& Hughes, 2011).
-Similar to Gross' theory, the social information processing theory of emotion also describe the role of intrapsychic processes and strategies in emotion experience and reulation (Lemerise \& Arsenio, 2000).
-Such theories are particularly relevant to a fine-grained understanding of the process of emotion regulation, but their developmental relevance has unfortunately not yet been considered (REF Buss).
+Existing theoretical models have several limitations. One crucial shortcoming
+is the lack of explicit attention to the life phase of adolescence. This is
+unfortunate, as empirical research consistently indicates that adolescence is a
+crucial life phase for emotion regulation development. Adolescence differs
+qualitatively from infancy, childhood, and adulthood. It is therefore
+insufficient to simply extrapolate theories focused on these ages. Other
+theories do focus on adolescence specifically (e.g., Crone \& Dahl, 2012), but only address emotion regulation
+in passing. A second, related, shortcoming is that some relevant theories lack
+a developmental component (see Buss et al., 2019; Crone \& Dahl, 2012). A third shortcoming is that theories
+vary widely in scope: Some are very broad and all-encompassing, but somewhat
+non-specific, such as the biopsychosocial models of Bronfenbrenner and
+Sameroff. Others describe a specific phenomenon in great detail, but are not
+embedded in a larger unifying framework. Examples include Morris' tripartite
+model, Crone and Dahl's model, and polyvagal theory. It would be beneficial to
+bridge these two levels of theory. One limitation echoed across many
+publications in this field is that more theory formation is required to provide
+a unified framework that could guide future empirical work. The present study
+seeks to aid such theory development, by providing an inductive conceptual
+review of the field.
 
-Parents are widely considered to be the primary proximal influence driving emotion regulation development.
+\hypertarget{bottom-up-insights-from-narrative-reviews}{%
+\subsection{Bottom-up insights from narrative reviews}\label{bottom-up-insights-from-narrative-reviews}}
 
-\hypertarget{shortcomings}{%
-\subsection{Shortcomings}\label{shortcomings}}
+While theory provides a top-down understanding of an area of research,
+literature reviews can provide a bottom-up, inductive understanding. Given the
+noted absence of a single overarching theory, reviews might provide additional
+insight into factors considered relevant in the etiology of adolescents'
+emotion regulation competencies. For example, a review by
+Bariola et al. (2011) addresses individual psychological factors
+such as temperament, and biological factors like neurocognitive development and
+genetic predispositions. Furthermore, they address proximal social influences,
+including parents, teachers, and peers, and specific mechanisms through which
+these individuals exert their influence, including parenting and modeling.
+Finally, they address distal factors, including the role of culture and the
+media. Barriola and colleagues also offer recommendations for future research,
+calling for research on the role of parents beyond early
+childhood, and including the role of fathers - a limitation which has since
+been addressed by a new wave of empirical research on fathers' role in
+emotional development (Van Lissa \& Keizer, 2020; Van Lissa, Keizer, Van Lier, Meeus, \& Branje, 2019).
 
-Extant theoretical models have several noteable shortcomings.
-The most notable shortcoming is the lack of explicit attention to the life phase of adolescence.
-This is unfortunate, as empirical research consistently indicates that adolescence is a crucial life phase for emotion regulation development.
-As this life phase differs qualitatively from infancy, childhood, and adulthood, it is insufficient to simply extrapolate from theories focused on these ages.
-Other theories do focus on adolescence specifically, but only address emotion regulation in passing.
-A second, related, shortcoming is that some relevant theories lack a developmental component, or are based on a near-exclusively cross-sectional body of research (see Buss et al., 2019; Crone \& Dahl, 2012).
-A third shortcoming is that theories vary widely in scope: On the macro-level, there are theories such as the biopsychosocial models of Bronfenbrenner and Sameroff, which are all-encompassing but non-specific.
-On the micro-level, there are theories such as Morriss' tripartite model, Crone and Dahl's model, and polyvagal theory, which originated in subdisciplines and describe one facet of the issue in great detail, but have not been placed within a unifying framework (Buss et al., 2019).
-To conclude, one limitation echoed across many publications in this field is that more theory formation is required to provide a unified framework that could guide future empirical work.
-A systematic conceptual review of the field could address this shortcoming.
+Another review, by Coe-Odess, Narr, and Allen (2019), offers a nuanced
+discussion of several issues that complement prior publications in this field.
+For instance, the authors cover the implications of physiological changes in
+detail, including neurocognitive development and pubertal maturation. As
+adolescents become increasingly individuated, conflict with parents peaks. This
+conflict, in turn, impacts emotion regulation, both in terms of day-to-day mood
+variability and dispositional emotion dysregulation (see also Van Lissa, Hawk, Koot, Branje, \& Meeus, 2017). As parental importance diminishes,
+adolescents become increasingly oriented towards peers. This includes increased
+sensitivity to social status and norms, along with the associated increase in
+peer pressure and risk taking. Pubertal development also initiates the
+emergence of sexual and romantic behavior, and the intensification of both
+biological sex differences and gender stereotyped behavior. With regard to the
+process of emotion regulation, Coe-Odess and colleagues discuss the importance
+of strategies, and point out that, in addition to negative emotionality,
+positive emotionality also peaks in adolescence. Relatedly, the authors
+describe how hormonal changes precipitate an increased stress response, which
+might help explain adolescents' greater susceptibility to emotion
+dysregulation. Finally, going beyond the implications of cognitive development
+discussed in other publications, the authors discuss how an greater capacity
+for abstract thought relates to identity formation - a key challenge in
+adolescence ({\textbf{???}}) - and to increased emotional
+understanding, and by extension, empathy (see also Van Lissa et al., 2014).
 
-\hypertarget{relevant-factors}{%
-\subsection{Relevant factors}\label{relevant-factors}}
+There are notable parallels between the relevant factors highlighted by these
+narrative reviews, and the aforementioned theoretical literature. Nevertheless,
+these literature reviews also touch upon issues that have received little
+attention in theoretical work. This highlights the value of both top-down and
+bottom-up approaches to understanding the phenomenon of adolescents' emotion
+regulation. One remaining limitation is that, to date, all reviews in this
+field have been unstructured narrative reviews. The present publication seeks
+to further complement preceding work by conducting a comprehensive empirical
+literature review, and mapping the factors associated with adolescent emotion
+regulation.
 
-As there are few theories specifically relevant to the field of adolescent emotion regulation development, it is perhaps unsurprising that some literature has proceeded in a somewhat less theoretical manner.
-Such studies do often focus on specific factors that are considered relevant for emotion regulation development.
+\hypertarget{the-present-paper}{%
+\subsection{The present paper}\label{the-present-paper}}
 
-These include neurological (Fox 1994;
-Porges et al.~1994; Quirk 2007; Stansbury and Gunnar
-1994), genetic (Goldsmith et al.~1997; Hariri and Forbes
-2007), and temperamental inﬂuences (Calkins 2004)
-A range of social factors have been proposed to be linked to
-ER development, including interactions with parents,
-teachers, and peers, as well as more distal societal inﬂu-
-ences such as culture and the media (Eisenberg and Morris
-2002; Klimes-Dougan et al.~2007; Morris et al.~2007;
-Thompson 1994).
-
-on adolescent emotion regulation development is limited27--29.
-The field is therefore at an impasse: We know that some adolescents are more susceptible to emotion dysregulation than others, but lack tools and theory to identify important predictors of individual development30.
-
-\hypertarget{the-present-study}{%
-\subsection{The present study}\label{the-present-study}}
-
-The present paper aims to develop a nomological network of the constructs related to adolescent emotion dysregulation by mapping the available literature.
-A nomological network is a diagrammatic representation of a phenomenon; a proto-theoretical device that describes relationships between constructs relevant to the theory (REF: Cronbach \& Meehl 1955; McKenna, 2006; Alavi 2018).
-It can be useful as a precursor to a more explicit theory of the phenomenon.
-The present paper uses an inductive approach to develop this nomological network.
-First, we conduct a systematic search to elicit a corpus of relevant literature.
-Second, we extract constructs from the corpus.
-Third, we use a dictionary to pare down the extracted constructs to meaningful superordinate categories.
-Fourth, we map interrelations between these constructs.
-Fifth, we classify contstructs as potential predictors or outcomes, and we categorize predictors by level of analysis (CJ: Sameroff, which level of biopsychosocial).
+The present paper aims to develop a nomological network of the constructs
+related to adolescent emotion dysregulation, based on a systematic review of
+the literature. A nomological network is a diagrammatic representation of a
+phenomenon; a proto-theoretical device that describes relationships between
+constructs relevant to the theory (see Alavi, Archibald, McMaster, Lopez, \& Cleary, 2018). It is a precursor to a more
+explicit theory of the phenomenon. The present paper uses an inductive approach
+to develop this nomological network. First, we conduct a systematic search to
+elicit a corpus of relevant literature. Second, we use text mining techniques
+to extract relevant constructs from the corpus. Third, we use a dictionary to
+pare down the extracted constructs to meaningful superordinate categories.
+Fourth, we map interrelations between these constructs. Fifth, we classify
+contstructs as potential predictors or outcomes, and we categorize predictors
+by level of analysis.
 
@@
 
-All searches were conducted on Web of Science.
-The search strategy was based on procedures described by Staaks (Staaks, n.d.).
-First, we manually constructed a reference set of 15 articles.
-Then we constructed a search string to retrieve these articles from Web of Science.
-The search was overly inclusive, returning 29 records.
-As these were all highly relevant, we updated the reference set to include all 29 results.
-Next, we tested our search string, which consisted of synonyms of emotion regulation and adolescence:
+All searches were conducted on Web of Science. The search strategy was based on
+procedures described by Staaks (Staaks, n.d.). First, we
+manually constructed a reference set of 15 articles. Then we constructed a
+search string to retrieve these articles from Web of Science. The search was
+overly inclusive, returning 29 records. As these were all highly relevant, we
+updated the reference set to include all 29 results. Next, we tested our search
+string, which consisted of synonyms of emotion regulation and adolescence:
 
 \begin{verbatim}
-TS=("emotio* regulation" OR "anger regulation" OR "sadness regulation" OR "emotion* competence" OR "emotion* adjustment" OR "emotio* dysregulation" OR "anger dysregulation" OR "sadness dysregulation" OR "emotio* problem*" OR "emotion* maladjustment") AND TS=(adolescent* OR teen* OR pubert* OR youth)
+TS=("emotio* regulation" OR "anger regulation" OR "sadness regulation" OR
+"emotion* competence" OR "emotion* adjustment" OR "emotio* dysregulation" OR
+"anger dysregulation" OR "sadness dysregulation" OR "emotio* problem*" OR
+"emotion* maladjustment") AND TS=(adolescent* OR teen* OR pubert* OR youth)
 \end{verbatim}
 
-This string returned 6653 results, and matched 25 of the 29 records in the reference set.
-Three search terms could be added to match all 29 reference set items.
-The terms \texttt{"emotio*\ socialization"\ OR\ "emotio*\ processes"}, as synonyms of emotion regulation, added 191 new hits.
-However, many of these hits were not directly relevant to emotion regulation.
-The term \texttt{"development*}, as synonym of adolescence, added 3628 new hits, many of which were not focused on the age range of adolescence.
-We thus deemed these terms to be overly inclusive, and proceeded with the original search string above.
+This string returned 6653 results, and matched 25 of the 29 records in the
+reference set. Three search terms could be added to match all 29 reference set
+items. The terms \texttt{"emotio*\ socialization"\ OR\ "emotio*\ processes"}, as synonyms
+of emotion regulation, added 191 new hits. However, many of these hits were not
+directly relevant to emotion regulation. The term \texttt{"development*"}, as synonym
+of adolescence, added 3628 new hits, many of which were not focused on the age
+range of adolescence. We thus deemed these terms to be overly inclusive, and
+proceeded with the original search string above.
 
@@
 
-Duplicates were detected based on exact DOI matches (2 duplicates), and title similarity (54 duplicates). Manual screening in Rayyan resulted in the removal of an additional 13 duplicates.
+Duplicates were identified based on exact DOI matches (2
+duplicates), and title similarity (54 duplicates).
+Manual screening in Rayyan resulted in the removal of an additional 13 duplicates.
 
@@
 
-\begin{verbatim}
-## [1] "2000-8198" "1540-2002" "2152-0828" "2152-0828" "0021-5368" "0021-9630"
-\end{verbatim}
+Papers were screened based on two main criteria: First, papers had to address emotion regulation, emotional problems, or similar.
+Second, the target population must overlap (at least in part) with adolescence, defined as the age range from 10-25.
+Thus, for example, an article reviewing the role of hormonal changes in emotional adjustment throughout the entire life course, including adolescence, would be deemed relevant.
+Screening was initially conducted in Rayyan QRCI ({\textbf{???}}).
+Papers were sorted using Rayyan's ranking algorithm.
+To train the algorithm on exclusion criteria, screening focused on abstracts most likely to be excluded.
+After coding 559 papers, screening continued in ASReview - a free, open source alternative to Rayyan QRCI ({\textbf{???}}).
+This program uses text mining and active learning to build a customizable machine learning model for article inclusion.
+We used a naive Bayes model, and focused on exclusion of irrelevant papers.
+In ASReview, an additional 541 papers were screened.
+Screening again focused on articles most likely to be excluded, and continued until, among the most recently screened 100 papers, only 6 were excluded.
+The screening procedure is detailed in Figure \ref{prismachart}.
+In total, 6305 papers were retained for analysis.
 
-We manually screened 500 abstracts for suitability in Rayyan.
-Then, we used ASReview to rank the predicted relevance of all papers based on the manually included and excluded articles.
-We screened the lowest-ranked articles to find an inflection point below which most articles were irrelevant, and excluded those from analysis.
+\begin{figure}
+\centering
+\includegraphics{manuscript_files/figure-latex/prismachart-1.pdf}
+\caption{\label{fig:prismachart}Record screening flowchart}
+\end{figure}
+
+\hypertarget{analysis-1-keyword-mapping}{%
+\section{Analysis 1: Keyword mapping}\label{analysis-1-keyword-mapping}}
+
+For this first analysis, we relied on author-provided keywords.
+We extracted keywords by document, and used a dictionary approach
+to classify closely related terms.
+
+\hypertarget{analysis-2-abstract-text-mining}{%
+\section{Analysis 2: Abstract text mining}\label{analysis-2-abstract-text-mining}}
+
+This second analysis focused on the abstracts of our corpus. Keywords are
+carefully chosen to capture the core tenets of a study. However, as authors are
+typically limited to 5 keywords, some of a study's nuance may be lost.
+Abstracts offer greater freedom of expression, which is a challenge when it
+comes to extracting relevant information. We took a two-pronged approach to
+extract relevant topic terms from the abstracts. First, we used the natural
+language processing technique part-of-speech tagging (POS-tagging) to identify
+nouns in the abstract. Using nouns only in text mining can lead to more
+interpretable models (Martin \& Johnson, 2015). Secondly, we used
+stemming to reduce these nouns to their root form. Finally, we applied a
+dictionary approach as before.
+
+offer an incomplete understanding of a study topic due to the limite
+authors are typically limited to provide a maximum of
+abstracts offer a little more
+
+used part-of-speech tagging, a natural language processing technique
+
+to identify nouns in the abstracts.
+, we relied on author-provided keywords. We extracted keywords by document, and used a dictionary approach to classify closely related terms.
 
@@
 \hypertarget{refs}{}
+\leavevmode\hypertarget{ref-alaviAligningTheoryMethodology2018}{}%
+Alavi, M., Archibald, M., McMaster, R., Lopez, V., \& Cleary, M.
+(2018).
+Aligning theory and methodology in mixed methods research: Before Design Theoretical Placement.
+\emph{International Journal of Social Research Methodology}, \emph{21}(5), 527--540.
+\url{https://doi.org/10.1080/13645579.2018.1435016}
+
 \leavevmode\hypertarget{ref-aldaoEmotionregulationStrategiesPsychopathology2010}{}%
@@
 
+\leavevmode\hypertarget{ref-bellRelationshipsInputsOutputs2000}{}%
+Bell, K. L., \& Calkins, S. D. (2000). Relationships as Inputs and Outputs of Emotion Regulation. \emph{Psychological Inquiry}, \emph{11}(3), 160--163.
+
 \leavevmode\hypertarget{ref-braetEmotionRegulationChildren2014}{}%
@@
 \url{https://doi.org/10.1007/s10608-014-9616-x}
+
+\leavevmode\hypertarget{ref-bronfenbrennerBioecologicalModelHuman2007}{}%
+Bronfenbrenner, U., \& Morris, P.
+A.
+(2007).
+The bioecological model of human development.
+In \emph{Handbook of Child Psychology}.
+John Wiley \& Sons, Inc.
+\url{https://doi.org/10.1002/9780470147658.chpsy0114}
 
@@
 (2012).
-Understanding adolescence as a period of social--affective engagement and goal flexibility.
+Understanding adolescence as a period of socialAffective engagement and goal flexibility.
 \emph{Nature Reviews Neuroscience}, \emph{13}(9), 636--650.
@@
 Gross, J. J. (2013). \emph{Handbook of emotion regulation}. Guilford publications.
+
+\leavevmode\hypertarget{ref-grossIndividualDifferencesTwo2003a}{}%
+Gross, J.
+J., \& John, O.
+P.
+(2003).
+Individual differences in two emotion regulation processes: Implications for affect, relationships, and well-being.
+\emph{Journal of Personality and Social Psychology}, \emph{85}(2), 348--362.
+\url{https://doi.org/10.1037/0022-3514.85.2.348}
+
+\leavevmode\hypertarget{ref-holodynskiDevelopmentEmotionsEmotion2006}{}%
+Holodynski, M., \& Friedlmeier, W. (2006). \emph{Development of Emotions and Emotion Regulation}. Springer Science \& Business Media.
 
@@
 (2014).
-Adolescent mental health---Opportunity and obligation.
+Adolescent mental healthOpportunity and obligation.
 \emph{Science}, \emph{346}(6209), 547--549.
@@
 \url{https://doi.org/10.1111/1467-8624.00124}
+
+\leavevmode\hypertarget{ref-martinMoreEfficientTopic2015}{}%
+Martin, F., \& Johnson, M. (2015). More Efficient Topic Modelling Through a Noun Only Approach. In \emph{Proceedings of Australasian Language Technology Association Workshop} (pp. 111--115).
 
@@
 \leavevmode\hypertarget{ref-riedigerEmotionRegulationAdolescence2014}{}%
-Riediger, M., \& Klipker, K. (2014). Emotion regulation in adolescence. In \emph{Handbook of emotion regulation} (Vols. 1--Book, Section, pp. 187--202). Guilford Press.
+Riediger, M., \& Klipker, K. (2014). Emotion regulation in adolescence. In \emph{Handbook of emotion regulation} (pp. 187--202). Guilford Press.
+
+\leavevmode\hypertarget{ref-sawyerAgeAdolescence2018}{}%
+Sawyer, S.
+M., Azzopardi, P.
+S., Wickremarathne, D., \& Patton, G.
+C.
+(2018).
+The age of adolescence.
+\emph{The Lancet.
+Child \& Adolescent Health}, \emph{2}(3), 223--228.
+\url{https://doi.org/10.1016/S2352-4642(18)30022-1}
 
@@
 
+\leavevmode\hypertarget{ref-silkAdolescentsEmotionRegulation2003}{}%
+Silk, J.
+S., Steinberg, L., \& Morris, A.
+S.
+(2003).
+Adolescents' emotion regulation in daily life: Links to depressive symptoms and problem behavior.
+\emph{Child Development}, \emph{74}(6), 1869--1880.
+
 \leavevmode\hypertarget{ref-sroufeEmotionalDevelopmentOrganization1995}{}%
@@
 \leavevmode\hypertarget{ref-staaksSystematicReviewSearch}{}%
-Staaks, J. (n.d.). Systematic Review Search Support. Retrieved March 23, 2020, from \url{https://osf.io/49t8x/}
+Staaks, J. (n.d.). Systematic Review Search Support. https://osf.io/49t8x/.
+
+\leavevmode\hypertarget{ref-steinbergAgeOpportunityLessons2014}{}%
+Steinberg, L. (2014). \emph{Age of Opportunity: Lessons from the New Science of Adolescence}. Houghton Mifflin Harcourt.
+
+\leavevmode\hypertarget{ref-vanlissaLongitudinalInterplayAffective2014}{}%
+Van Lissa, C.
+J., Hawk, S.
+T., de Wied, M., Koot, H.
+M., van Lier, P., \& Meeus, W.
+(2014).
+The longitudinal interplay of affective and cognitive empathy within and between adolescents and mothers.
+\emph{Developmental Psychology}, \emph{50}(4), 1219--1225.
+\url{https://doi.org/10.1037/a0035050}
+
+\leavevmode\hypertarget{ref-vanlissaCostEmpathyParentadolescent2017}{}%
+Van Lissa, C.
+J., Hawk, S.
+T., Koot, H.
+M., Branje, S., \& Meeus, W.
+H.
+J.
+(2017).
+The cost of empathy: Parent-adolescent conflict predicts emotion dysregulation for highly empathic youth.
+\emph{Developmental Psychology}, \emph{ePub}(ePub), ePub.
+\url{https://doi.org/10.1037/dev0000361}
+
+\leavevmode\hypertarget{ref-vanlissaMothersFathersQuantitative2020}{}%
+Van Lissa, C.
+J., \& Keizer, R.
+(2020).
+Mothers' and fathers' quantitative and qualitative parenting in relation to children's emotional adjustment: A between- and within-family investigation.
+\emph{Developmental Psychology}, \emph{in press}.
+
+\leavevmode\hypertarget{ref-vanlissaRoleFathersMothers2019}{}%
+Van Lissa, C.
+J., Keizer, R., Van Lier, P.
+A.
+C., Meeus, W.
+H.
+J., \& Branje, S.
+(2019).
+The role of fathers' versus mothers' parenting in emotion-regulation development from midLate adolescence: Disentangling between-family differences from within-family effects.
+\emph{Developmental Psychology}, \emph{55}(2), 377--389.
+\url{https://doi.org/10.1037/dev0000612}
 

### 2020-06-07 study1.R

@@ -1,11 +1,15 @@
 library(data.table)
 library(bibliometrix)
+library(yaml)
 source("word_functions.R")
 exclude_terms <- readLines("exclude_terms.txt")
-dict_synon <- dget("dictionary_synonyms.txt")
+dict_synon <- read_yaml("yaml_dict.txt")
 #recs <- convert2df(bibliometrix::readFiles("savedrecs_full.txt"))
 #saveRDS(recs, "savedrecs.RData")
 recs <- readRDS("recs_6653.RData")
+recs <- readRDS("unique_recs.RData")
+
+hea
 #recs <- unique_recs
 df <- lapply(recs$DE, function(x){strsplit(x, split = "; ")[[1]]})
 df <- data.table(word = tolower(unlist(df)), doc = rep(1:length(df), times = sapply(df, length)))
@@ -14,8 +18,9 @@ df <- data.table(word = tolower(unlist(df)), doc = rep(1:length(df), times = sap
 exclude_these <- unique(unlist(lapply(exclude_terms, grep, x = df$word)))
 
 df <- df[!exclude_these, ]
-
+head(df)
 res_cat <- cat_words(df$word, dict_synon)
+head(res_cat$unmatched)
 # head(sort(table(res_cat$words), decreasing = T), 20)
 # res_cat$dup
 # head(res_cat$unmatched)

### 2020-06-07 word_functions.R

@@ -158,7 +158,24 @@ dict <- list(a = "a", b = "b")
 # tmp <- cat_words(words, dict)
 # cbind(words, tmp$words)
 # words <- df$word[56:(56+10)]
-cat_words <- function(words, dict){
+
+cat_words <- function(x, dict, handle_dups = c("first", "all", "random"), ...){
+  UseMethod("cat_words", x)
+}
+
+cat_words.data.frame <- function(x, dict, handle_dups = c("first", "all", "random"), column = "word", ...){
+  Args <- as.list(match.call()[-1])
+  Args$x <- x[[column]]
+  categorized <- do.call(cat_words, Args)
+  if(is.list(out)){
+    
+  } else {
+    
+    return()
+  }
+}
+
+cat_words.character <- function(x, dict, handle_dups = c("first", "all", "random"), ...){
   rexes <- unlist(dict)
   
   #new_name <- rep(names(dict), times = reps)
@@ -173,25 +190,28 @@ cat_words <- function(words, dict){
   num_matches <- rowSums(matches)
   has_matches <- !num_matches == 0
   which_matches <- which(has_matches)
-  outwords <- words
-  outwords[has_matches] <- names(dict)[apply(matches[which_matches, ], 1, function(lv){min(which(lv))})]
-  #cbind(words, outwords)
+  outwords <- switch(handle_dups[1],
+                     first = apply(matches[which_matches, ], 1, function(lv){names(dict)[min(which(lv))]}),
+                     random = apply(matches[which_matches, ], 1, function(lv){names(dict)[sample(which(lv), 1)]}),
+                     apply(matches[which_matches, ], 1, function(lv){names(dict)[which(lv)]})
+                     )
+  
   out <- list(
     words = outwords
   )
   multimatch <- num_matches > 1
   if(any(multimatch)){
-    warning("Duplicate matches found; see the '$dup' element of the output.", call. = FALSE)
+    message("Duplicate matches found; see the '$dup' element of the output.")
     dups <- unique(words[multimatch])
-    out_dups <- lapply(dups, function(x){
-      tmp <- which(words == x & multimatch)[1]
-      unname(rexes[dict_matches[tmp, ]])
+    out_dups <- lapply(dups, function(this_dup){
+      these_matches <- which(words == this_dup & multimatch)[1]
+      unname(rexes[dict_matches[these_matches, ]])
     })
     names(out_dups) <- dups
     out$dup <- out_dups
   }
   if(any(!has_matches)){
[…]

### 2020-06-09 manuscript.Rmd
Updates

@@
   - name          : "Caspar J. van Lissa"
-    affiliation   : "1,2"
+    affiliation   : "1"
     corresponding : yes    # Define only one corresponding author
@@
     institution   : "Utrecht University faculty of Social and Behavioral Sciences, department of Methodology & Statistics"
-  - id            : "2"
-    institution   : "Open Science Community Utrecht"
 
 authornote: |
-  Caspar van Lissa, Department of Methodology and Statistics, Utrecht
-  University, P.O. Box 80140, 3508 TC, Utrecht, The Netherlands. E-mail:
-  C.vanLissa@uu.nl. This work is supported by a NWO Veni grant (NWO
-  grant number VI.Veni.191G.090).
+  This work is supported by a NWO Veni grant (NWO
+  grant number VI.Veni.191G.090). Acknowledgement: Lukas Beinhauer contributed
+  substantially to the screening of articles.
 
@@
 phenomenon; a proto-theoretical device that describes relationships between
-constructs relevant to the theory [see @alaviAligningTheoryMethodology2018;
-@@cronbachConstructValidityPsychological1955;
-@@mastersonNomologicalNetworkResearch2009]. It is a precursor to a more
+constructs relevant to the theory [see @alaviAligningTheoryMethodology2018]. It is a precursor to a more
 explicit theory of the phenomenon. The present paper uses an inductive approach
@@
 ```
-Papers were screened based on two main criteria: First, papers had to address emotion regulation, emotional problems, or similar.
+Papers were screened based on two main criteria:
+First, papers had to address emotion regulation, emotional problems, or similar.
 Second, the target population must overlap (at least in part) with adolescence, defined as the age range from 10-25.
@@
                "", "dedup2", "excluded", "", ""), nrow = 5, ncol = 2)
+
 nodes <- data.frame(
@@
     paste0("Records identified through\nWeb of Science (n = ", nrow(recs), ")"), 
-    paste0("Records after duplicates removed\n(n = ", nrow(unique_recs), ")"), 
-    paste0("Duplicates removed\n(n = ", nrow(recs)-nrow(screen), ")"), 
+    paste0("After duplicates removed\n(n = ", nrow(unique_recs), ")"), 
+    paste0("Duplicates\n(n = ", nrow(recs)-nrow(screen), ")"), 
     paste0("Articles screened for eligibility\nusing Rayyan (n = ", nrow(screen), ")"), 
@@
 )
+
 edges <- data.frame(
   from = c("start", "dedup", "rayyan", "asreview",
-           "dedup", "rayyan", "rayyan", "asreview"),
+           "start", "rayyan", "rayyan", "asreview"),
   to = c("dedup", "rayyan", "asreview", "included",
          "dedup2", "dedup2", "excluded", "excluded"),
-  label = c("",   "", sum(screen$rayyan == "True"), "",
+  label = c("",   "", paste0("n = ", sum(screen$rayyan == "True")), paste0("n = ", sum(screen$included == 0, na.rm = TRUE)-sum(screen$rayyan == "True")),
             paste0("n = ", sum(dups)), 
@@
 )
+
 p <- graph_sem(layout = lo, nodes = nodes, edges = edges, angle = 1, rect_height = 1.2, rect_width = 1.3)
@@
 ggsave("prismachart.svg", p, device = "svg")
-knitr::include_graphics("prismachart.svg")
+knitr::include_graphics("prismachart.png")
+```
+
+## Corpus description
+
+```{r, eval = FALSE}
+# Plot papers per year
+df_plot <- as.data.frame(table(recs_final$PY), stringsAsFactors = FALSE)
+df_plot$Year = as.numeric(df_plot$Var1)
+ggplot(df_plot, aes(x= Year, y= Freq))+geom_point() + geom_path(group =1)+
+  theme_bw() + scale_y_log10()
 ```
@@
 
-For this first analysis, we relied on author-provided keywords.
+The corpus for this first analysis consisted of the author-provided keywords for the selected articles.
 We extracted keywords by document, and used a dictionary approach
-to classify closely related terms.
+to classify related terms.
 The dictionary was created specifically for this study.
@@
 An exclusion list of methodological terms and other non-substantive words was generated using the same procedure.
+
+## Structural topic modeling
+
+```{r}
+if(run_everything) source("LDA_analysis.R")
+```
+To assess the homogeneity of the corpus, we conducted topic modeling using latent dirichlet allocation [@bleiLatentDirichletAllocation2003]. 
+A range of 2-20 topics was considered.
+Fit was evaluated based on the BIC, and interpretability was evaluated on the entropy of the posterior probabilities of documents to be assigned to the different topics.
+The BICs followed a near-perfect linearly increasing trend, indicating that no subcorpora could be identified.
+Congruently, all entropies were near-zero, which means that the posterior probabilities of documents to be assigned to the different topics were uniformly distributed.
+Thus, no interpretable subcorpora could be identified, and we proceed with an analysis of the whole sample. <!-- Probably because each set of keywords has only a few indicators. -->
 

### 2020-06-09 LDA_analysis.R

@@ -1,0 +1,105 @@
+library(Rmpfr)
+library(topicmodels)
+library(udpipe)
+library(slam)
+library(tidytext)
+# Functions:
+harmonicMean <- function(logLikelihoods, precision = 2000L) {
+  llMed <- median(logLikelihoods)
+  as.double(llMed - log(mean(exp(-mpfr(logLikelihoods,
+                                       prec = precision) + llMed))))
+}
+BIC <- function(ll, p, n){
+  -2 * ll + p * log(n)
+}
+entropy <- function(post_prob){
+  1 + (1/(nrow(post_prob) * 
+            log(ncol(post_prob)))) * (sum(rowSums(post_prob * 
+                                                    log(post_prob + 1e-12))))
+}
+
+# Preprocessing -----------------------------------------------------------
+
+nounbydoc <- df[, list(freq = .N), by = list(doc_id = doc, term = word_coded)]
+df_lda <- nounbydoc[nounbydoc$term %in% names(dict), ]
+df_lda <- df_lda %>%
+  bind_tf_idf(term, doc_id, freq)
+summary(df_lda$idf)
+df_lda[order(df_lda$idf),]
+
+select_words <- df_lda[!duplicated(df_lda$term), ]
+select_words <- select_words$term[select_words$idf >= median(select_words$idf)]
+select_words <- names(dict)
+df_lda <- df_lda[df_lda$term %in% select_words, ]
+
+dtm <- udpipe::document_term_matrix(document_term_frequencies(df_lda))
+
+# dtm <- as.simple_triplet_matrix(dtm)
+# dim(dtm)
+# summary(col_sums(dtm))
+# term_tfidf <- tapply(dtm$v/row_sums(dtm)[dtm$i], dtm$j, mean) * log2(dim(dtm)[1]/col_sums(dtm > 0))
+# summary(term_tfidf)
+
+
+summary(col_sums(dtm))
+dim(dtm)
+
+# Build topic models
+
+seqk <- seq(2, 20, 1)
+burnin <- 1000
+iter <- 1000
+keep <- 50
+set.seed(44773)
+res_lda <- lapply(seqk, function(k) {
+  topicmodels::LDA(
+    dtm,
+    k = k,
+    method = "Gibbs",
+    control = list(
+      burnin = burnin,
+      iter = iter,
+      keep = keep
+    )
+  )
+})
+
+
[…]

### 2020-06-09 study1.R

@@ -1,89 +1,119 @@
 library(data.table)
 library(bibliometrix)
 library(yaml)
-source("word_functions.R")
-exclude_terms <- readLines("exclude_terms.txt")
-dict_synon <- read_yaml("yaml_dict.txt")
-#recs <- convert2df(bibliometrix::readFiles("savedrecs_full.txt"))
-#saveRDS(recs, "savedrecs.RData")
-recs <- readRDS("recs_6653.RData")
-recs <- readRDS("unique_recs.RData")
-
-hea
-#recs <- unique_recs
-df <- lapply(recs$DE, function(x){strsplit(x, split = "; ")[[1]]})
-df <- data.table(word = tolower(unlist(df)), doc = rep(1:length(df), times = sapply(df, length)))
-
-#table(grep("disease", df$word, value = T))
-exclude_these <- unique(unlist(lapply(exclude_terms, grep, x = df$word)))
-
-df <- df[!exclude_these, ]
-head(df)
-res_cat <- cat_words(df$word, dict_synon)
-head(res_cat$unmatched)
-# head(sort(table(res_cat$words), decreasing = T), 20)
-# res_cat$dup
-# head(res_cat$unmatched)
-# writeClipboard(names(res_cat$unmatched))
-
-# Remove duplicate words per doc
-df[, word := res_cat$words]
-df[, id := paste0(word, doc)]
-df <- df[!duplicated(id), ]
-df[, id := NULL]
-#head(df)
-## Look at POS tags
+library(stringr)
 library(lattice)
-
-# What are these texts about? 
 library(topicmodels)
 library(udpipe)
 library(slam)
-
-nounbydoc <- df[, list(freq = .N), by = list(document = doc, term = word)]
-
-dtm <- udpipe::document_term_matrix(document_term_frequencies(nounbydoc)) # document_frequency_matrix(x)
-topterms <- col_sums(dtm)
-topterms <- sort(topterms, decreasing = TRUE)
-hist(topterms, breaks = 100)
-tt <- table(topterms)
-plot(1:10, tt[1:10], type = "l")
-topterms <- topterms[topterms > .005*nrow(recs)]
-
-topterms <- head(topterms, 250)
-topterms <- names(topterms)
-dtm_top <- dtm[, topterms]
-dtm_top <- dtm_top[row_sums(dtm_top) > 0, ]
-
-set.seed(43892)
-
[…]

### 2020-06-09 word_functions.R

@@ -177,23 +177,26 @@ cat_words.data.frame <- function(x, dict, handle_dups = c("first", "all", "rando
 
 cat_words.character <- function(x, dict, handle_dups = c("first", "all", "random"), ...){
   rexes <- unlist(dict)
-  
+  words <- x
   #new_name <- rep(names(dict), times = reps)
   dict_matches <- sapply(rexes, function(this_reg){
     grepl(this_reg, words, perl = TRUE)})
+  if(is.null(dim(dict_matches))) dict_matches <- t(dict_matches)
   matches <- matrix(FALSE, nrow = length(words), ncol = length(dict))
   reps <- c(0, sapply(dict, length))
-  for(this_word in 1:length(dict)){
-    sum_cols <- (sum(reps[1:this_word])+1):sum(reps[1:(this_word+1)])
-    matches[, this_word] <- apply(dict_matches[, sum_cols, drop = FALSE], 1, any)
+  for(dict_item in 1:length(dict)){
+    sum_cols <- (sum(reps[1:dict_item])+1):sum(reps[1:(dict_item+1)])
+    matches[, dict_item] <- apply(dict_matches[, sum_cols, drop = FALSE], 1, any)
   }
+  
   num_matches <- rowSums(matches)
   has_matches <- !num_matches == 0
   which_matches <- which(has_matches)
-  outwords <- switch(handle_dups[1],
-                     first = apply(matches[which_matches, ], 1, function(lv){names(dict)[min(which(lv))]}),
-                     random = apply(matches[which_matches, ], 1, function(lv){names(dict)[sample(which(lv), 1)]}),
-                     apply(matches[which_matches, ], 1, function(lv){names(dict)[which(lv)]})
+  outwords <- words
+  outwords[has_matches] <- switch(handle_dups[1],
+                                  first = apply(matches[which_matches, ], 1, function(lv){names(dict)[min(which(lv))]}),
+                                  random = apply(matches[which_matches, ], 1, function(lv){names(dict)[sample(which(lv), 1)]}),
+                                  apply(matches[which_matches, ], 1, function(lv){names(dict)[which(lv)]})
                      )
   
   out <- list(
@@ -218,4 +221,17 @@ cat_words.character <- function(x, dict, handle_dups = c("first", "all", "random
   }
   class(out) <- c("word_matches", class(out))
   out
+}
+
+# x <- list(v1 = letters[1:3],
[…]

### 2020-06-09 manuscript.Rmd
Finished analyses for study 1

@@
 
+```{r}
+source("study1.R")
+if(run_everything | !file.exists("Study1_lda_dims.txt")) source("LDA_analysis.R")
+lda_dims <- read_yaml("Study1_lda_dims.txt")
+```
 The corpus for this first analysis consisted of the author-provided keywords for the selected articles.
-We extracted keywords by document, and used a dictionary approach
+We extracted keywords by document, and used a dictionary,
+created specifically for this study,
 to classify related terms.
-The dictionary was created specifically for this study.
+The dictionary describes `r length(dict)` terms using `r length(unlist(dict))`
+regular expression queries.
 The lead author composed a first draft of the dictionary based on prior knowledge of the field.
@@
 An exclusion list of methodological terms and other non-substantive words was generated using the same procedure.
+After applying the dictionary and exclusion filter,
+and removing records with no (remaining) keywords,
+the resulting corpus consisted of `r number_docs_words["docs"]` documents with `r number_docs_words["words"]` unique words.
+As term-document frequency is irrelevant in the context of keywords (i.e., keywords should not occur twice within the same document, except when two synonyms have been recoded using the dictionary),
+the term-document matrix was dichotomized.
 
@@
 
-```{r}
-if(run_everything) source("LDA_analysis.R")
+To assess the homogeneity of the corpus, we conducted topic modeling using latent dirichlet allocation [@bleiLatentDirichletAllocation2003].
+For this analysis, we used the term frequency/inverse document frequency (TF-IDF) to select terms
+not used frequently in the corpus,
+which could therefore be more diagnostic of subgroup membership.
+Selection terms with an TF-IDF greater than the median resulted in a corpus of `r lda_dims[1]` documents and `r lda_dims[2]` terms.
+We considered a range from 2-20 topics, evaluating fit based on the BIC, and interpretability based on the entropy of the posterior document/topic probabilities.
+The BICs followed a near-perfect linearly increasing trend, indicating that no subcorpora could be identified.
+Congruently, all entropies were near-zero, which means that the posterior document/topic probabilities were effectively uniformly distributed.
+Thus, no interpretable subcorpora could be identified,
+and we proceed with an analysis of the whole sample. <!-- Probably because each set of keywords has only a few indicators. -->
+
+## Mapping the literature
+
+To map the cooccurrence of terms within documents,
+it is pertinent to select the most common terms, instead of using IDF.
+As a cutoff, we required terms to occur in at least $0.5%$ of documents.
+This selection criterion resulted in a corpus of `r dim(dtm_top)[1]` documents and `r dim(dtm_top)[2]` terms.
+The marginal occurrence of the selected terms is displayed in Figure \@ref(study1wordcloud).
+To determine the frequency with which terms were addressed in documents,
+we constructed a term-document matrix
+
+```{r study1wordcloud, fig.cap="Wordcloud of terms selected for Study 1 co-occurrence analysis. More common words are centered and printed in larger font."}
+knitr::include_graphics("study1_wordcloud.png")
 ```
-To assess the homogeneity of the corpus, we conducted topic modeling using latent dirichlet allocation [@bleiLatentDirichletAllocation2003]. 
-A range of 2-20 topics was considered.
-Fit was evaluated based on the BIC, and interpretability was evaluated on the entropy of the posterior probabilities of documents to be assigned to the different topics.
-The BICs followed a near-perfect linearly increasing trend, indicating that no subcorpora could be identified.
-Congruently, all entropies were near-zero, which means that the posterior probabilities of documents to be assigned to the different topics were uniformly distributed.
-Thus, no interpretable subcorpora could be identified, and we proceed with an analysis of the whole sample. <!-- Probably because each set of keywords has only a few indicators. -->
 

### 2020-06-09 manuscript.tex
Finished analyses for study 1

@@
 
-Papers were screened based on two main criteria: First, papers had to address emotion regulation, emotional problems, or similar.
+Papers were screened based on two main criteria:
+First, papers had to address emotion regulation, emotional problems, or similar.
 Second, the target population must overlap (at least in part) with adolescence, defined as the age range from 10-25.
 Thus, for example, an article reviewing the role of hormonal changes in emotional adjustment throughout the entire life course, including adolescence, would be deemed relevant.
-Screening was initially conducted in Rayyan QRCI ({\textbf{???}}).
+Screening was initially conducted in Rayyan QRCI (Ouzzani, Hammady, Fedorowicz, \& Elmagarmid, 2016).
 Papers were sorted using Rayyan's ranking algorithm.
 To train the algorithm on exclusion criteria, screening focused on abstracts most likely to be excluded.
-After coding 559 papers, screening continued in ASReview - a free, open source alternative to Rayyan QRCI ({\textbf{???}}).
+After coding 559 papers, screening continued in ASReview - a free, open source alternative to Rayyan QRCI (Van de Schoot et al., 2020).
 This program uses text mining and active learning to build a customizable machine learning model for article inclusion.
@@
 \begin{figure}
-\centering
-\includegraphics{manuscript_files/figure-latex/prismachart-1.pdf}
-\caption{\label{fig:prismachart}Record screening flowchart}
+\includegraphics[width=6.5in]{prismachart} \caption{Record screening flowchart}\label{fig:prismachart}
 \end{figure}
@@
 
-For this first analysis, we relied on author-provided keywords.
+The corpus for this first analysis consisted of the author-provided keywords for the selected articles.
 We extracted keywords by document, and used a dictionary approach
-to classify closely related terms.
+to classify related terms.
+The dictionary was created specifically for this study.
+The lead author composed a first draft of the dictionary based on prior knowledge of the field.
+This draft was subsequently updated in two ways:
+First, while writing the introduction for this paper, key terms from the theoretical and empirical literature were added to the dictionary.
+Second, by including commonly occurring uncategorized words during preliminary analyses of the data.
+An exclusion list of methodological terms and other non-substantive words was generated using the same procedure.
+
+\hypertarget{structural-topic-modeling}{%
+\subsection{Structural topic modeling}\label{structural-topic-modeling}}
+
+To determine whether the corpus could
 
@@
 
+\leavevmode\hypertarget{ref-Ouzzani2016}{}%
+Ouzzani, M., Hammady, H., Fedorowicz, Z., \& Elmagarmid, A.
+(2016).
+Rayyana web and mobile app for systematic reviews.
+\emph{Systematic Reviews}, \emph{5}(1), 210.
+\url{https://doi.org/10.1186/s13643-016-0384-4}
+
 \leavevmode\hypertarget{ref-porgesOrientingDefensiveWorld1995}{}%
@@
 
+\leavevmode\hypertarget{ref-van_de_schoot_rens_2020_3828293}{}%
+Van de Schoot, R., De Bruin, J., Schram, R., Zahedi, P., De Boer, J., Weijdema, F., \ldots{} Oberski, D. (2020). ASReview: Active learning for systematic reviews (Version v0.9.5). Zenodo.
+
 \leavevmode\hypertarget{ref-vanlissaLongitudinalInterplayAffective2014}{}%

### 2020-06-09 LDA_analysis.R

@@ -20,16 +20,15 @@ entropy <- function(post_prob){
 
 # Preprocessing -----------------------------------------------------------
 
-nounbydoc <- df[, list(freq = .N), by = list(doc_id = doc, term = word_coded)]
-df_lda <- nounbydoc[nounbydoc$term %in% names(dict), ]
+#nounbydoc <- df[, list(freq = .N), by = list(doc_id = doc, term = word_coded)]
+df_lda <- nounbydoc #[nounbydoc$term %in% names(dict), ]
 df_lda <- df_lda %>%
   bind_tf_idf(term, doc_id, freq)
-summary(df_lda$idf)
-df_lda[order(df_lda$idf),]
+summary(df_lda$tf_idf)
+df_lda <- df_lda[order(df_lda$tf_idf),]
 
 select_words <- df_lda[!duplicated(df_lda$term), ]
-select_words <- select_words$term[select_words$idf >= median(select_words$idf)]
-select_words <- names(dict)
+select_words <- select_words$term[select_words$tf_idf >= median(select_words$tf_idf)]
 df_lda <- df_lda[df_lda$term %in% select_words, ]
 
 dtm <- udpipe::document_term_matrix(document_term_frequencies(df_lda))
@@ -40,9 +39,7 @@ dtm <- udpipe::document_term_matrix(document_term_frequencies(df_lda))
 # term_tfidf <- tapply(dtm$v/row_sums(dtm)[dtm$i], dtm$j, mean) * log2(dim(dtm)[1]/col_sums(dtm > 0))
 # summary(term_tfidf)
 
-
-summary(col_sums(dtm))
-dim(dtm)
+yaml::write_yaml(dim(dtm), file = "Study1_lda_dims.txt")
 
 # Build topic models
 
@@ -63,7 +60,6 @@ res_lda <- lapply(seqk, function(k) {
     )
   )
 })
-
 
 ll <- sapply(res_lda, function(x){harmonicMean(x@logLiks[-c(1:(burnin/keep))])})
 

### 2020-06-09 study1.R

@@ -1,19 +1,14 @@
 library(data.table)
-library(bibliometrix)
-library(yaml)
+#library(bibliometrix)
+#library(yaml)
 library(stringr)
-library(lattice)
-library(topicmodels)
+#library(lattice)
+#library(topicmodels)
 library(udpipe)
-library(slam)
-library(tidytext)
-library(ggraph)
-library(ggforce)
 library(igraph)
-library(tidytext)
-
+library(wordcloud)
+library(Matrix)
 source("word_functions.R")
-
 ## Look at POS tags?
 
 recs <- data.table(read.csv("recs_final.csv"))
@@ -33,6 +28,7 @@ df[, word := tolower(word)]
 
 # Clean
 df <- na.omit(df, cols = "word")
+number_docs_words <- c(docs = length(unique(df$doc)), words = length(unique(df$word)))
 
 # Exclude words
 exclude_terms <- readLines("exclude_terms.txt")
@@ -47,8 +43,8 @@ res_cat <- cat_words(df$word, dict, handle_dups = "all")
 #res_cat$dup
 #head(res_cat$unmatched)
 df <- merge_df(df, res_cat$words, "word_coded")
-
-
+length(unique(df$word))
+length(unique(df$doc))
 # Create plot data --------------------------------------------------------
 nounbydoc <- df[, list(freq = .N), by = list(doc_id = doc, term = word)]
 nounbydoc$freq <- 1
@@ -75,17 +71,26 @@ nounbydoc$freq <- 1
 # tmp <- nounbydoc %>%
 #   bind_tf_idf(term, doc_id, freq)
 # summary(tmp$tf_idf)
+
 dtm <- udpipe::document_term_matrix(document_term_frequencies(nounbydoc))
 topterms <- col_sums(dtm)
 topterms <- sort(topterms, decreasing = TRUE)
+
+
+# Continue plotting word frequency ----------------------------------------
 
 tt <- as.data.frame(table(topterms), stringsAsFactors = FALSE)
 tt$Frequency <- as.numeric(tt$topterms)
 tt$Words <- tt$Freq
 tt$Dictionary <- "Recoded"
 df_plot <- rbind(df_plot, tt[, c("Frequency", "Words", "Dictionary")])
-ggplot(df_plot, aes(x=Frequency, y = Words, linetype = Dictionary))+geom_point() + geom_path()+
[…]

### 2020-06-13 manuscript.Rmd
Finish analyse

@@
 library(bib2df)
+library(knitr)
+library(kableExtra)
+run_everything = FALSE
 ```
@@
 Screening again focused on articles most likely to be excluded, and continued until, among the most recently screened 100 papers, only 6 were excluded.
-The screening procedure is detailed in Figure \@ref(prismachart).
+The screening procedure is detailed in Figure \@ref(fig:prismachart).
 In total, `r nrow(recs_final)` papers were retained for analysis.
@@
 
+<!--
 ## Corpus description
 
-```{r, eval = FALSE}
+{r, eval = FALSE}
 # Plot papers per year
@@
   theme_bw() + scale_y_log10()
-```
+-->
 
@@
 
-To map the cooccurrence of terms within documents,
-it is pertinent to select the most common terms, instead of using IDF.
-As a cutoff, we required terms to occur in at least $0.5%$ of documents.
-This selection criterion resulted in a corpus of `r dim(dtm_top)[1]` documents and `r dim(dtm_top)[2]` terms.
-The marginal occurrence of the selected terms is displayed in Figure \@ref(study1wordcloud).
-To determine the frequency with which terms were addressed in documents,
-we constructed a term-document matrix
+Next, we mapped the cooccurrence of terms within documents as an undirected graph.
+When examining cooccurrence,
+it is pertinent to select the most common terms, instead of using TF-IDF.
+We retained terms present in at least $0.5%$ of the entire corpus,
+resulting in a selection of `r dim(dtm_top)[1]` documents and `r dim(dtm_top)[2]` terms.
+The marginal occurrence of the selected terms is displayed in Figure \@ref(fig:study1wordcloud).
+This indicates how frequently each term occurred in the corpus, and illustrates what this body of literature is about.
 
-```{r study1wordcloud, fig.cap="Wordcloud of terms selected for Study 1 co-occurrence analysis. More common words are centered and printed in larger font."}
-knitr::include_graphics("study1_wordcloud.png")
+```{r study1wordcloud, out.width = "100%", fig.cap="Wordcloud of terms selected for Study 1 co-occurrence analysis. More common words are centered and printed in larger font."}
+knitr::include_graphics("study1_wordcloud.svg")
 ```
+
+Based on our theoretical review, each of the selected terms was coded as being either a putative 'Cause', 'Outcome', 'Protective factor', or 'Indicator' (a closely related construct) of emotion dysregulation.
+We stress that this is a simplification; many of these associations are likely to be bidirectional [e.g., emotion dysregulation is known to be both cause and consequence of conflict with parents, @vanlissaCostEmpathyParentadolescent2017].
+Figure \@ref(fig:study1network) displays the term cooccurrence matrix as a force directed graph.
+<!--The classification is presented in Table \@ref(tab:study1table1).
+
+r study1table1, results = "asis"}
+df <- tapply(pretty_words(categ$name), categ$category, function(i){paste(strwrap(paste(i, collapse = ", "), width = 90), collapse = "\\\\")})
+df <- data.frame(Category = names(df), Terms = df, row.names = NULL)
+apa_table(df, escape = F)
+-->
+
+```{r study1network, out.width = "100%", fig.cap="Force directed graph for Study 1 co-occurrence analysis.
+Vertex size represents term frequency; dashed lines for co-occurrences not involving dysregulation.
+Two different layouts are presented to aid interpretation."}
+#knitr::include_graphics("study1_network1.svg")
+library(cowplot)
+fig_svg <- cowplot::ggdraw()+cowplot::draw_image("study1_network1.svg")
+plot(fig_svg)
+```
+
+## Results
+
+```{r}
+notingraph <- names(topterms)[!names(topterms) %in% unique(c(edg$term1, edg$term2))]
+notingraph <- categ[categ$name %in% notingraph, ]
+notingraph <- tapply(tolower(pretty_words(notingraph$name)), notingraph$category, function(i){paste0(paste(paste0("*", i[-length(i)], "*"), collapse = ", "), ", and ", i[length(i)])})
+```
+
+Inspecting the co-occurrence graph for the keyword data,
+it is evident that there are relatively few interconnections between elements,
+with a matrix sparsity 
+it becomes evident that emotion dysregulation is the most common and central construct,
+as could be expected based on the search terms.
+Most of the other constructs in the corpus are directly linked to emotion dysregulation,
+which suggests that our search was successful in identifying factors considered to be relevant
+for adolescents' emotion dysregulation.
+The fact that only few of the constructs were interrelated substantiates our impression that this literature is somewhat fragmented.
+One emergent cluster of interrelated constructs pertains to the mental health-related outcomes of emotion dysregulation, most notably anxiety, depression, and externalizing symptoms.
+
+A more surprising finding is that some of the most prevalent terms were not connected to emotion dysregulation -
+for example, *Rumination*, only showed a direct link with *Depression*.
+Other prevalent terms are entirely absent from Figure \@ref(fig:study1network), as they were not related
+to any other terms in the main network. 
+These terms, which are displayed in Figure \@ref(fig:study1wordcloud), include the potential causes `r notingraph["Cause"]`, the potential outcomes `r notingraph["Outcome"]`, and the potential protective factors `r notingraph["Protective"]`.
+
+## Discussion
+
+Several of these constructs represent active ongoing areas of research - such as the role of fathers in adolescents' emotional development [@vanlissaRoleFathersMothers2019], *identity* [@campbellFriendsEducationIdentity2019], *friendship* and *social support* [@bukowskiPopularityFriendshipEmotional1993], *autonomy* [@vrolijkLongitudinalLinkagesFatherunderreview; @brenningPerceivedMaternalAutonomy2015], *sexual risk* [@brownDepressiveSymptomsPredictor2006], and *Loneliness* [@spithovenItAllTheir2017].
+The absence of these terms from the graph thus does not reflect so much a lack of importance.
+Rather, these constructs - being important, but not yet well-integrated in the literature,
+are prime candidates for future research;
+particularly in conjunction with more well-established constructs.
 

### 2020-06-13 dictionary.R

@@ -1,1 +1,0 @@
-acceptance = c("AFQ-Y")

### 2020-06-13 study1.R

@@ -8,53 +8,55 @@ library(udpipe)
 library(igraph)
 library(wordcloud)
 library(Matrix)
+library(ggplot2)
+library(yaml)
 source("word_functions.R")
+run_everything = FALSE
+study1_details <- read_yaml("study1_details.yml")
 ## Look at POS tags?
+if(run_everything){
+  recs <- data.table(read.csv("recs_final.csv"))
+  recs[, "doc" := 1:nrow(recs)]
+  study1details <- list(dim_recs = dim(recs))
+  
+  # Extract individual words
+  df <- lapply(recs$DE, function(x){strsplit(x, split = "; ")[[1]]})
+  df <- merge_df(recs, df, "word")
+  
+  df[, word := tolower(word)]
+  
+  # Clean
+  df <- na.omit(df, cols = "word")
+  number_docs_words <- c(docs = length(unique(df$doc)), words = length(unique(df$word)))
+  
+  # Exclude words
+  exclude_terms <- readLines("exclude_terms.txt")
+  exclude_these <- unique(unlist(lapply(exclude_terms, grep, x = df$word)))
+  
+  df <- df[!exclude_these, ]
+  
+  # Categorize words
+  dict <- read_yaml("yaml_dict.txt")
+  res_cat <- cat_words(df$word, dict, handle_dups = "all")
+  # Check coding issues
+  #res_cat$dup
+  #head(res_cat$unmatched)
+  df <- merge_df(df, res_cat$words, "word_coded")
+  saveRDS(df, "study1_df.RData")
+} else {
+  df <- readRDS("study1_df.RData")
+}
 
-recs <- data.table(read.csv("recs_final.csv"))
-recs[, "doc" := 1:nrow(recs)]
-
-# Try quanteda
-#library(quanteda)
-#corp <- corpus(recs, text_field = "DE")  # build a new corpus from the texts
-# Try kwic
-#kwic(corp, pattern = "drug")
-
-# Extract individual words
-df <- lapply(recs$DE, function(x){strsplit(x, split = "; ")[[1]]})
-df <- merge_df(recs, df, "word")
-
-df[, word := tolower(word)]
-
-# Clean
-df <- na.omit(df, cols = "word")
-number_docs_words <- c(docs = length(unique(df$doc)), words = length(unique(df$word)))
-
-# Exclude words
-exclude_terms <- readLines("exclude_terms.txt")
[…]

### 2020-06-13 study2.R

@@ -1,0 +1,388 @@
+library(data.table)
+#library(bibliometrix)
+#library(yaml)
+library(stringr)
+#library(lattice)
+#library(topicmodels)
+library(udpipe)
+library(igraph)
+library(wordcloud)
+library(Matrix)
+library(yaml)
+library(Rmpfr)
+library(topicmodels)
+library(udpipe)
+library(slam)
+library(tidytext)
+library(ggplot2)
+library(textrank)
+source("word_functions.R")
+run_everything <- FALSE
+
+## Look at POS tags?
+
+recs <- data.table(read.csv("recs_final.csv"))
+recs[, "doc" := 1:nrow(recs)]
+recs$AB <- tolower(recs$AB)
+
+# Detect languages not necessary; only one abstract is (partly) in Spanish.
+#library(cld3)
+#languages <- cld3::detect_language(recs$AB)
+#table(languages)
+#recs$AB[languages == "es"]
+
+
+if(!file.exists("english-ewt-ud-2.4-190531.udpipe")) {
+  ud_model <- udpipe_download_model(language = "english")
+} else {
+  ud_model <- udpipe_load_model("english-ewt-ud-2.4-190531.udpipe")
+  ud_model <- udpipe_load_model(ud_model$file_model)
+}
+
+
+if(run_everything){
+  udp_res <- udpipe_annotate(ud_model, x = recs$AB, doc_id = recs$doc)
+  df <- as.data.table(udp_res)
+  saveRDS(df, "study2_df.RData")
+} else {
+  df <- readRDS("study2_df.RData")
+}
+
+
+# LDA analysis ------------------------------------------------------------
+
+if(run_everything){
+  # Functions:
+  harmonicMean <- function(logLikelihoods, precision = 2000L) {
+    llMed <- median(logLikelihoods)
+    as.double(llMed - log(mean(exp(-mpfr(logLikelihoods,
+                                         prec = precision) + llMed))))
+  }
+  BIC <- function(ll, p, n){
+    -2 * ll + p * log(n)
+  }
+  entropy <- function(post_prob){
+    1 + (1/(nrow(post_prob) * 
+              log(ncol(post_prob)))) * (sum(rowSums(post_prob * 
+                                                      log(post_prob + 1e-12))))
+  }
+  
[…]

### 2020-06-13 tm_references2.R

@@ -7,7 +7,7 @@ df <- read.table("c:/tmp/savedrecs.txt", sep = "\t", header = TRUE, quote = "", 
 ## Natural Language Processing: POS tagging
 library(pattern.nlp)
 #df <- df[1:33, ]
-if(!file.exists("df_tagged.RData")){
+if(!file.exists("study2_tagged.RData")){
   df_tagged <- lapply(1:nrow(df), function(thisrow){
     tryCatch(cbind(pattern_pos(x = df$ID[thisrow], language = "english", core = TRUE), thisrow), error = function(e){NULL})
   })  

### 2020-06-13 word_functions.R

@@ -1,3 +1,86 @@
+boot_dtm_old <- function(dtm, iterations = 1000, confidence_boundary = .95){
+  bt <- replicate(iterations, {
+    b <- dtm[sample.int(nrow(dtm), replace = TRUE), ]
+    colSums(b)
+  })
+  interesting <- rowSums(bt > 0)
+  cb <- confidence_boundary * iterations
+  interesting > cb
+}
+
+boot_dtm <- function(dtm, iterations = 100, confidence_boundary = .95){
+  cb <- confidence_boundary * iterations
+  m_logical <- dtm > 0
+  interesting <- vector(length = ncol(dtm))
+  len <- nrow(dtm)
+  for(j in 1:ncol(dtm)){
+    interesting[j] <- sum(replicate(iterations, {
+        any(sample(m_logical[, j], len, replace = TRUE))
+      })) > cb
+  }
+  
+}
+
+library(fitdistrplus)
+select_words <- function(dtm, q = .95){
+  d <- colSums(dtm)
+  fit <- fitdist(d, "nbinom")
+  thres <- qnbinom(q, size=fit$estimate["size"], mu=fit$estimate["mu"])
+  return(d > thres)
+}
+
+select_cooc <- function(cooc, q = .95){
+  mat.summ   <- summary(cooc)
+  mat.summ <- mat.summ[!mat.summ$i == mat.summ$j, ]
+  lower.summ <- subset(mat.summ, i >= j)
+  fit <- fitdist(lower.summ$x, "nbinom")
+  thres <- qnbinom(q, size=fit$estimate["size"], mu=fit$estimate["mu"])
+  lower.summ <- lower.summ[!lower.summ$x < thres, ]
+  out <- sparseMatrix(i = lower.summ$i,
+               j = lower.summ$j,
+               x = lower.summ$x,
+               dims = dim(cooc), symmetric = TRUE)
+  rownames(out) <- rownames(cooc)
+  colnames(out) <- colnames(cooc)
+  return(out)
+}
+
+create_cooc <- function(dtm){
+  dtm_binary <- dtm > 0
+  Matrix::t(dtm_binary) %*% dtm
+}
+
+net_dens <- function(cooc){
+  potential_connections <- dim(cooc)[1]*(dim(cooc)[2]-1)/2
+  sum(cooc[lower.tri(cooc)] > 0) / potential_connections
+}
+
+library(RaschSampler)
+library(abind)
[…]

### 2020-10-18 manuscript.Rmd
Submit to DPP

--- 2020-06-09 manuscript.Rmd
@@
 ---
-title             : "Mapping factors associated with adolescents' emotion dysregulation: A text-mining based systematic review"
+title             : "Mapping correlates of adolescent emotion dysregulation: A text-mining based systematic review"
 shorttitle        : "ADOLESCENT EMOTION DYSREGULATION"
@@
   grant number VI.Veni.191G.090). Acknowledgement: Lukas Beinhauer contributed
-  substantially to the screening of articles.
+  substantially to the screening of articles. Conflicts of Interest: None.
 
 abstract: |
-  Test me
+  For many, adolescence marks the onset of emotion dysregulation and related mental health problems.
+It is therefore essential to have a solid grasp of relevant risk factors.
+Despite an abundance of empirical research, the literature is somewhat fragmented, as the topic has been investigated from different perspectives across subdisciplines.
+This systematic review uses text mining to map factors related to adolescent emotion dysregulation.
+A systematic search for publications that addressed emotion regulation in participants between the ages of 10-25 yielded 6305 suitable papers.
+One analysis focused on author-provided keywords, and a second extracted sequences of adjectives and nouns from the abstracts.
+Terms were classified with a dictionary describing 105 terms using 434 regular expressions.
+Terms were coded as putative “Causes”, “Outcomes”, “Protective factors”, or “Indicators” of emotion dysregulation.
+We reported term/document frequency, and force-directed graphs of term co-occurrence.
+These results reﬂected constructs commonly featured in theory and narrative reviews, but also identified underrepresented terms.
+This illustrates how text mining review may complement narrative reviews.
+Importantly, most constructs were directly related to emotion dysregulation, with few interconnections between constructs – reflecting the fragmented literature.
+This research constitutes a first step towards integrating the literature, and may inspire future empirical and theoretical work.
 
-keywords          : "keywords"
-wordcount         : "X"
+keywords          : "emotion regulation, adolescence, systematic review, text mining, machine learning"
+wordcount         : "5400"
 bibliography      : ["veni_sysrev.bib"]
@@
 footnotelist      : no
-linenumbers       : yes
+linenumbers       : no
 mask              : no
@@
 documentclass     : "apa6"
-classoption       : "man"
+classoption       : "man,noextraspace"
 output            : papaja::apa6_pdf
@@
 library(bib2df)
+library(knitr)
+library(kableExtra)
+library(cowplot)
+run_everything = FALSE
 ```
@@
 fragmented, as the topic has been investigated from different (sub)disciplines.
-This study seeks to overcome this limitation by mapping all factors currently
-thought to be relevant to adolescent emotion regulation, based on a systematic
-review and bibliographic analysis. <!-- Ergens anders: Similarly, although
+This systematic review seeks to overcome this limitation by using
+bibliographic analysis to map all factors currently
+considered to be relevant to adolescent emotion regulation. <!-- Ergens anders: Similarly, although
 there are several *relevant* theories, there is no specific theoretical
@@
 Adolescence is defined as a life phase ranging from pubertal onset to
-adult-like independence [@steinbergAgeOpportunityLessons2014]. This definition
-invokes both biological- and socio-cultural factors. It has been argued that,
+adult-like independence [@steinbergAgeOpportunityLessons2014].
+It is thus demarcated by both biological- and socio-cultural factors.
+It has been argued that,
 due to accellerated pubertal onset and delayed transitions to adult roles,
@@
 without being fully prepared to cope with the emotional outcomes
-[@croneUnderstandingAdolescencePeriod2012]. Due to these coalescing changes,
+[@croneUnderstandingAdolescencePeriod2012].
+Due to these coalescing changes,
 adolescents display a restricted repertoire of emotion regulation strategies
@@
 early adulthood. Unfortunately, a sizeable proportion of adolescents instead
-manifests enduring emotional difficulties.
+manifests enduring emotional difficulties [@leeAdolescentMentalHealth2014].
 
@@
 well-documented, and persist throughout the life course. Meta-analyses indicate
-that such difficulties are associated with externalizing, and more strongly,
-with internalizing psychopathology
+that such difficulties are associated with internalizing, and to a lesser extent, externalizing, psychopathology
 [@aldaoEmotionregulationStrategiesPsychopathology2010;
-@schaferEmotionRegulationStrategies2017]. Individuals who engage in maladaptive
+@schaferEmotionRegulationStrategies2017]. 
+Individuals who engage in maladaptive
 emotion regulation strategies also experience more negative emotions,
@@
 regulation skills - but not all adolescents do so successfully. As many as one
-in five adolescents instead develop severe emotional difficulties.--> Given the
-prevalence of emotional difficulties and their extensive implications for
-individual mental health, wellbeing, and social functioning, and downstream
+in five adolescents instead develop severe emotional difficulties.--> 
+Given the
+prevalence of emotional difficulties and their implications for
+individual mental health, wellbeing, and social functioning, and their downstream
 cost to society as a whole [@leeAdolescentMentalHealth2014], it is essential to
@@
 [@bussTheoriesEmotionalDevelopment2019;
-@riedigerEmotionRegulationAdolescence2014]. Thanks, in part, to their efforts,
+@riedigerEmotionRegulationAdolescence2014]. Thanks, in part, to these efforts,
 we can provide a summary review of the theoretical landscape as context for our
@@
 [@coe-odessEmergentEmotionsAdolescence2019].  -->
+
 Two theories widely invoked to frame research on development, including
@@
 development: social and cognitive influences. Social influences mainly occur
-through parents' co-regulation, parenting behaviors, and parent-child
+through parental co-regulation, parenting behaviors, and parent-child
 attachment. Cognitive influences occur through the development of the central
@@
 
-The emphasis on neorocognitive development as a driver of emotional
-development, including emotion regulation development, is echoed in several
-other models. For example, polyvagal theory closely links emotional experience
+Several other models echo this emphasis on neorocognitive development as a driver of emotional
+development, including emotion regulation development.
+For example, polyvagal theory closely links emotional experience
 - and regulation - to autonomous nervous system functioning
@@
 [@craccoEmotionRegulationChildhood2017;
-@caseyBrakingAcceleratingAdolescent2011]. However, it sets out to explain - to
-a greater extent than other writings - adolescents' diverging destinies; the
+@caseyBrakingAcceleratingAdolescent2011]. To
+a greater extent than related writings, however, @croneUnderstandingAdolescencePeriod2012
+set out to explain adolescents' diverging destinies; the
 question why some youngsters flourish while others languish. Crone and Dahl
@@
 abilities. On the other hand, it places them at risk to act impulsively in
-pursuit of peer approval. This theory focuses primarily on cognitive factors
+pursuit of peer approval. In terms of explanans,
+this theory focuses primarily on cognitive factors
 and the role of peers, with less attention to factors such as parenting.
@@
 
-Aside from theories of emotional development, theories of the phenomenon of
+Whereas our primary interest is in theories of emotional development,
+theories of the phenomenon of
 emotion regulation are also somewhat relevant. One influential theory is Gross'
@@
 
-## Shortcomings of the theory
+## Shortcomings of existing theory
 
-Existing theoretical models have several limitations. One crucial shortcoming
+Despite the abundance of relevant theory,
+the existing literature has several limitations when the goals is to
+identify which
+risk factors render some adolescents more susceptible
+to maladaptive emotional development than others.
+One crucial shortcoming
 is the lack of explicit attention to the life phase of adolescence. This is
@@
 qualitatively from infancy, childhood, and adulthood. It is therefore
-insufficient to simply extrapolate theories focused on these ages. Other
-theories do focus on adolescence specifically [e.g.,
+questionable whether theories focused on different ages can be generalized to adolescents.
+By contrast, some theories focus on adolescence specifically [e.g.,
 @croneUnderstandingAdolescencePeriod2012], but only address emotion regulation
-in passing. A second, related, shortcoming is that some relevant theories lack
+in passing.
+A second, related, shortcoming is that some relevant theories lack
 a developmental component <!--, and thus lack a well-substantiated
@@
 @bussTheoriesEmotionalDevelopment2019;
-@croneUnderstandingAdolescencePeriod2012]. A third shortcoming is that theories
+@croneUnderstandingAdolescencePeriod2012]. 
+A third shortcoming is that theories
 vary widely in scope: Some are very broad and all-encompassing, but somewhat
@@
 model, Crone and Dahl's model, and polyvagal theory. It would be beneficial to
-bridge these two levels of theory. One limitation echoed across many
+bridge these levels of analysis.
+One limitation echoed across many
 publications in this field is that more theory formation is required to provide
-a unified framework that could guide future empirical work. The present study
-seeks to aid such theory development, by providing an inductive conceptual
+a unified framework that could guide future empirical work.
+The present study
+seeks to lay the groundwork for such theory development,
+by providing an inductive conceptual
 review of the field.
@@
 
-While theory provides a top-down understanding of an area of research,
+Whereas theory provides a top-down understanding of an area of research,
 literature reviews can provide a bottom-up, inductive understanding. Given the
@@
 such as temperament, and biological factors like neurocognitive development and
-genetic predispositions. Furthermore, they address proximal social influences,
+genetic predispositions. Furthermore, the authors address proximal social influences,
 including parents, teachers, and peers, and specific mechanisms through which
@@
 field have been unstructured narrative reviews. The present publication seeks
-to further complement preceding work by conducting a comprehensive empirical
+to complement preceding work by conducting a comprehensive empirical
 literature review, and mapping the factors associated with adolescent emotion
@@
 Fourth, we map interrelations between these constructs. Fifth, we classify
-contstructs as potential predictors or outcomes, and we categorize predictors
-by level of analysis<!-- (CJ: Sameroff, which level of biopsychosocial)-->.
+contstructs as potential predictors or outcomes.
+<!--, and we categorize predictors
+by level of analysis-->
+<!-- (CJ: Sameroff, which level of biopsychosocial)-->.
 <!-- t, using text mining to map potential predictors of adolescent emotion
@@
 First, papers had to address emotion regulation, emotional problems, or similar.
-Second, the target population must overlap (at least in part) with adolescence, defined as the age range from 10-25.
+Second, the target population must overlap with the life phase of adolescence, defined as the age range from 10-25.
 Thus, for example, an article reviewing the role of hormonal changes in emotional adjustment throughout the entire life course, including adolescence, would be deemed relevant.
@@
   theme_bw() + scale_y_log10()
+-->
+
+# Analysis 1: Author keyword mapping
+
+```{r, warning=FALSE, message=FALSE}
+source("study1.R")
+if(run_everything | !file.exists("Study1_lda_dims.txt")) source("LDA_analysis.R")
+lda_dims <- read_yaml("Study1_lda_dims.txt")
 ```
-
-# Analysis 1: Keyword mapping
-
 The corpus for this first analysis consisted of the author-provided keywords for the selected articles.
-We extracted keywords by document, and used a dictionary approach
-to classify related terms.
-The dictionary was created specifically for this study.
-The lead author composed a first draft of the dictionary based on prior knowledge of the field.
+We extracted keywords by document, and used a dictionary
+created specifically for this study to classify related terms.
+The dictionary describes `r length(dict)` terms using `r length(unlist(dict))`
+regular expression queries.
+The lead author composed a first draft of the dictionary.
 This draft was subsequently updated in two ways:
-First, while writing the introduction for this paper, key terms from the theoretical and empirical literature were added to the dictionary.
-Second, by including commonly occurring uncategorized words during preliminary analyses of the data.
+First, while writing the introduction for this paper,
+key terms from the literature were added to the dictionary.
+Second, by including frequently occurring uncategorized words during preliminary analyses of the data until no more frequently occurring uncategorized words were found.
 An exclusion list of methodological terms and other non-substantive words was generated using the same procedure.
+After applying the dictionary and exclusion filter,
+and removing records with no (remaining) keywords,
+the resulting corpus consisted of `r number_docs_words[1]` documents with `r number_docs_words[2]` unique words.
+<!--As term-document frequency is irrelevant in the context of keywords (i.e., keywords should not occur twice within the same document, except when two synonyms have been recoded using the dictionary),
+the term-document matrix was dichotomized.-->
 
@@
 
+To assess the homogeneity of the corpus, we conducted topic modeling using latent dirichlet allocation [@bleiLatentDirichletAllocation2003].
+For this analysis, we used the term frequency/inverse document frequency (TF-IDF) to select terms
+used frequently in a document, but not used frequently in the corpus,
+which could therefore be more diagnostic of subgroup membership.
+Selection terms with an TF-IDF greater than the median resulted in a corpus of `r lda_dims[1]` documents and `r lda_dims[2]` terms.
+We considered a range from 2-20 topics, evaluating fit based on the BIC, and interpretability based on the entropy of the posterior document/topic probabilities.
+The BICs followed a near-perfect linearly increasing trend, indicating that no subcorpora could be identified.
+Congruently, all entropies were near-zero, which means that the posterior document/topic probabilities were effectively uniformly distributed.
+Thus, no interpretable subcorpora could be identified,
+and we proceed with an analysis of the whole sample. <!-- Probably because each set of keywords has only a few indicators. -->
+
+## Identifying common terms
+
+To identify what issues are covered in this corpus,
+we examined the terms occurring in the largest number of texts.
+We modeled word frequency using a negative binomial distribution,
+and retained those exceeding the $97.5^{th}$ percentile.
+This resulted in `r dim(dtm_top)[2]` terms, which occurred in `r dim(dtm_top)[1]` documents.
+To illustrates what issues are covered in this body of literature, the selected terms are displayed in Figure \@ref(fig:study1varimp), on a logarithmic scale to reduce the skew of the negative binomial distribution.<!--;
+word size represents frequency of occurrence (squared to reduce the skew of the negative binomial distribution).-->
+
+```{r study1wordcloud, warning=FALSE, eval = FALSE, out.width = "100%", fig.cap="Wordcloud of terms selected for Study 1. More common words are centered and printed in larger font."}
+knitr::include_graphics("study1_wordcloud.svg")
+```
+
+```{r study1varimp, warning=FALSE, eval = TRUE, out.width = "100%", fig.cap="Document frequency of terms selected for Study 1."}
+knitr::include_graphics("s1_varimp.png") 
+#fig_svg <- cowplot::ggdraw()+cowplot::draw_image("s1_varimp.svg")
+#plot(fig_svg)
+```
+
+## Mapping the literature
+
+Based on our theoretical review, each of the selected terms was coded as being either a putative 'Cause', 'Outcome', 'Protective factor', or 'Indicator' (a closely related construct) of emotion dysregulation.
+We stress that this is a rudimentary and simplistic classification; many of these associations are likely to be bidirectional [e.g., emotion dysregulation is known to be both a cause and consequence of conflict with parents, @vanlissaCostEmpathyParentadolescent2017].
+Next, we computed a term co-occurrence matrix,
+which represents how frequently words occurred within the same document.
+To aid interpretability, we again pruned small coefficients by
+modeling co-occurrence using a negative binomial distribution,
+and retaining co-occurrences exceeding the $97.5^{th}$ percentile.
+Figure \@ref(fig:study1network) displays the pruned term cooccurrence matrix as a force directed graph.
+<!--The classification is presented in Table \@ref(tab:study1table1).
+
+r study1table1, results = "asis"}
+df <- tapply(pretty_words(categ$name), categ$category, function(i){paste(strwrap(paste(i, collapse = ", "), width = 90), collapse = "\\\\")})
+df <- data.frame(Category = names(df), Terms = df, row.names = NULL)
+apa_table(df, escape = F)
+-->
+
+```{r study1network, warning=FALSE, out.width = "100%", fig.cap="Force directed graph for Study 1 co-occurrence analysis.
+Vertex size represents term frequency; dashed lines for co-occurrences not involving dysregulation.
+Two different layouts are presented to aid interpretation."}
+#knitr::include_graphics("study1_network1.svg")
+library(cowplot)
+fig_svg <- cowplot::ggdraw()+cowplot::draw_image("study1_network1.svg")
+plot(fig_svg)
+```
+
+## Results
+
 ```{r}
-if(run_everything) source("LDA_analysis.R")
+notingraph <- names(topterms)[!names(topterms) %in% unique(c(edg$term1, edg$term2))]
+notingraph <- categ[categ$name %in% notingraph, ]
+notingraph <- tapply(tolower(pretty_words(notingraph$name)), notingraph$category, function(i){paste0(paste(paste0("*", i[-length(i)], "*"), collapse = ", "), ", and *", i[length(i)], "*")})
 ```
-To assess the homogeneity of the corpus, we conducted topic modeling using latent dirichlet allocation [@bleiLatentDirichletAllocation2003]. 
-A range of 2-20 topics was considered.
-Fit was evaluated based on the BIC, and interpretability was evaluated on the entropy of the posterior probabilities of documents to be assigned to the different topics.
-The BICs followed a near-perfect linearly increasing trend, indicating that no subcorpora could be identified.
-Congruently, all entropies were near-zero, which means that the posterior probabilities of documents to be assigned to the different topics were uniformly distributed.
-Thus, no interpretable subcorpora could be identified, and we proceed with an analysis of the whole sample. <!-- Probably because each set of keywords has only a few indicators. -->
+
+Based on term document frequency (Figure \@ref(fig:study1varimp)), it is clear that emotion dysregulation and its mental health-related outcomes are foremost among the common terms in the corpus. 
+Other frequent terms reflect important themes discussed in the theoretical review of the literature;
+for instance, the term *neural*, *parenting*, and *stress* correspond to major themes discussed by  @coe-odessEmergentEmotionsAdolescence2019:
+Neurocognitive development, the role of the parents, and adolescents' increased stress response.
+Importantly, the most common terms also include several concepts not featured prominently in the theoretical review.
+For example, *ADHD/CD* [cf.
+@braetEmotionRegulationChildren2014], *substance* use [cf.
+@coe-odessEmergentEmotionsAdolescence2019; @pierrehumbertStrategiesEmotionRegulation2002], and *minority status* [cf.
+@myersEthnicitySocioeconomicStatusrelated2009; @myersEthnicitySocioeconomicStatusrelated2009] are common in the corpus,
+but featured less prominently in the theoretical review.
+
+Based on the co-occurrence graph (Figure \@ref(fig:study1network)),
+it is evident that 
+emotion dysregulation is a central construct,
+and that most of the other constructs are linked directly to emotion dysregulation,
+which suggests that our search was successful in identifying factors considered to be relevant
+for adolescents' emotion dysregulation.
+Otherwise, the graph is relatively sparse, with few interconnections between terms.
+
+## Discussion
+
+This first analysis used author keywords to map common topics in the literature pertaining to adolescents' emotion dysregulation.
+The results reflected some of the constructs commonly accepted as relevant in theoretical literature and empirical reviews.
+However, the analysis also revealed important areas less prominently featured in narrative reviews. 
+This illustrates how inductive reviews may complement existing theory and narrative reviews, and can reveal blindspots.
+
+It was found that connections among topics were relatively sparse: Many constructs were only related to emotion regulation,
+and there were relatively few interconnections between elements.
+This observation substantiates the prior claim that this literature is somewhat fragmented [@bussTheoriesEmotionalDevelopment2019].
+<!--One exception is an emergent cluster of interrelated constructs pertaining to mental health, anxiety, depression, and externalizing symptoms - the frequently occurring mental health-related outcomes.-->
+
+This sparse property of the network explains, in part,
+why some of the most prevalent terms based on term document frequency
+(see Figure \@ref(fig:study1varimp)) are absent from the co-occurrence graph.
+These terms were not strongly related to any other terms in the main network. 
+Amongst the terms culled from the co-occurrence graph are the potential causes `r notingraph["Cause"]`, the potential outcomes `r notingraph["Outcome"]`, and the potential protective factors `r notingraph["Protective"]`.
+
+Many of these excluded constructs represent active ongoing areas of research - such as the role of *fathers* [@vanlissaRoleFathersMothers2019], *identity* [@campbellFriendsEducationIdentity2019], *friendship* and *social support* [@bukowskiPopularityFriendshipEmotional1993], *autonomy* [@vrolijkLongitudinalLinkagesFatherunderreview; @brenningPerceivedMaternalAutonomy2015], *sexual risk* [@brownDepressiveSymptomsPredictor2006], and *loneliness* [@spithovenItAllTheir2017] in adolescents' emotional development.
+The fact that these constructs are absent from the graph does not suggest that they are unimportant.
+Rather, it indicates that they are not yet well-integrated in the literature,
+and are therefore prime candidates for future research.
+One recommendation for future research might be to study such important but unembedded constructs
+in conjunction with other more well-established constructs,
+as such an approach might help fill gaps in existing knowledge.
 
@@
 
-This second analysis focused on the abstracts of our corpus. Keywords are
-carefully chosen to capture the core tenets of a study. However, as authors are
+```{r, warning=FALSE, message=FALSE}
+source("study2.R")
+if(run_everything | !file.exists("Study2_lda_dims.txt")) source("LDA_analysis.R")
+lda_dims_2 <- read_yaml("Study2_lda_dims.txt")
+```
+The corpus for this second analysis consisted of the abstracts of the selected articles.
+Author keywords, as examined in Analysis 1, are carefully chosen to capture the core tenets of a study,
+and thus convey high-quality information directly relevant to the topic of a text.
+However, as authors are
 typically limited to 5 keywords, some of a study's nuance may be lost.
-Abstracts offer greater freedom of expression, which is a challenge when it
-comes to extracting relevant information. We took a two-pronged approach to
-extract relevant topic terms from the abstracts. First, we used the natural
-language processing technique part-of-speech tagging (POS-tagging) to identify
-nouns in the abstract. Using nouns only in text mining can lead to more
-interpretable models [@martinMoreEfficientTopic2015]. Secondly, we used
-stemming to reduce these nouns to their root form. Finally, we applied a
-dictionary approach as before.
+Abstracts, by contrast, offer greater freedom of expression,
+but present a greater challenge when it
+comes to extracting relevant information.
+To perform feature extraction,
+we first applied the natural language processing technique "part-of-speech tagging" (POS-tagging), which identifies a word's grammatical function within the sentence context.
+Then, we used POS-tagging to retain only nouns and adjectives,
+which helps derive more interpretable text mining models [@martinMoreEfficientTopic2015].
+Finally, we used stemming to reduce the retained terms to their root form.
 
-offer an incomplete understanding of a study topic due to the limite
-authors are typically limited to provide a maximum of 
-abstracts offer a little more
+## Structural topic modeling
 
-used part-of-speech tagging, a natural language processing technique
+To assess the homogeneity of the corpus of abstracts,
+we again conducted topic modeling [@bleiLatentDirichletAllocation2003],
+with features selected based on TF-IDF.
+This in a dataset consisting of `r lda_dims_2[1]` documents and `r lda_dims_2[2]` terms.
+We considered a range from 2-20 topics, evaluating fit based on the BIC, and interpretability based on the entropy of the posterior document/topic probabilities.
+As before, the BICs followed a near-perfect linearly increasing trend, and all entropies were near-zero.
+Thus, no interpretable subcorpora could be identified,
+and we proceed with an analysis of the whole sample.
 
-to identify nouns in the abstracts.
-, we relied on author-provided keywords. We extracted keywords by document, and used a dictionary approach to classify closely related terms.
+## Identifying keywords
 
-# Discussion
+When conducting text mining analysis on unstructured text data (as opposed to author key words), focusing on individual words out of context can reduce interpretability.
+For instance, our core construct "emotion dysregulation" is already a bigram.
+To identify more meaningful units of analysis,
+we applied the `textrank` algorithm [@wijffelsTextrankSummarizeText2019], an extention of Google's PageRank [@pageMethodNodeRanking2006], to identify relevant $n$-grams (with $n \leq 3$).
+The resulting $n$-grams were merged with the original data.
+After applying the dictionary and exclusion filter as explained in Analysis 1,
+the resulting corpus consisted of `r number_docs_words2[1]` documents with `r number_docs_words2[2]` unique words.
+Terms exceeding the $97.5^{th}$ percentile of a negative binomial distribution were retained for analysis.
+The identified important keywords are displayed in Figure \@ref(fig:study2varimp).
+
+```{r study2wordcloud, eval = FALSE, out.width = "100%", fig.cap="Wordcloud of terms selected for Study 2. More common words are centered and printed in larger font."}
+knitr::include_graphics("study2_wordcloud.svg")
+```
+
+```{r study2varimp, eval = TRUE, out.width = "100%", fig.cap="Document frequency of terms selected for Study 2."}
+knitr::include_graphics("s2_varimp.png") 
+# fig_svg <- cowplot::ggdraw()+cowplot::draw_image("s1_varimp.svg")
+# plot(fig_svg)
+```
+
+## Mapping the literature
+
+A term co-occurrence matrix was constructed following the procedure described in Analysis 1.
+Figure \@ref(fig:study2network) displays the resulting matrix as a force directed graph.
+<!--The classification is presented in Table \@ref(tab:study1table1).
+
+r study1table1, results = "asis"}
+df <- tapply(pretty_words(categ$name), categ$category, function(i){paste(strwrap(paste(i, collapse = ", "), width = 90), collapse = "\\\\")})
+df <- data.frame(Category = names(df), Terms = df, row.names = NULL)
+apa_table(df, escape = F)
+-->
+
+```{r study2network, out.width = "100%", fig.cap="Force directed graph for Study 2 co-occurrence analysis.
+Vertex size represents term frequency; dashed lines for co-occurrences not involving dysregulation.
+Two different layouts are presented to aid interpretation."}
+#knitr::include_graphics("study2_network1.svg")
+library(cowplot)
+fig_svg <- cowplot::ggdraw()+cowplot::draw_image("study2_network1.svg")
+plot(fig_svg)
+```
+
+## Results
+
+```{r}
+tt <- sort(topterms, decreasing = TRUE)
+notingraph <- names(tt)[!names(tt) %in% unique(c(edg$term1, edg$term2))]
+notingraph <- categ[categ$name %in% notingraph, ]
+notingraph <- tapply(tolower(pretty_words(notingraph$name)), notingraph$category, function(i){paste0(paste(paste0("*", i[-length(i)], "*"), collapse = ", "), ", and *", i[length(i)], "*")})
+```
+
+Based on term document frequency, it is clear that emotion dysregulation and mental health-related outcomes of emotion dysregulation are among the most common terms in the corpus of abstracts.
+The term "neural", again, occurred frequently, but other top terms were somewhat less predictable than those emerging in Analysis 1.
+The term "sex" is more frequent, and instead of "parenting", we now see "mothers" on top of the list.
+We see that "minority status", "substance use", "attachment","ptsd", and "bullying" are once more among the most frequent words.
+
+Inspecting the co-occurrence graph for the keyword data,
+we see a much sparser network than in Analysis 1, with a different structure.
+We now see that dysregulation and mental health-related terms form a central axis,
+and that many related terms are connected to this axis, but not always directly to
+dysregulation. Only the terms "neural", "mothers", "attachment" and "ptsd" are 
+connected directly to dysregulation.
+
+Again, some prevalent terms are entirely absent from Figure \@ref(fig:study2network), as they were not strongly related
+to any other terms in the main network. 
+These terms, which are displayed in Figure \@ref(fig:study2varimp),\include the potential causes `r notingraph["Cause"]`, the potential outcomes `r notingraph["Outcome"]`, and the potential protective factors `r notingraph["Protective"]`.
+
+```{r}
+s1 <- read_yaml("s1_words.yml")
+s2 <- read_yaml("s2_words.yml")
+
+#length(unique(c(s1, s2)))
+
+oneintwo <- round(length(s1[s1 %in% s2])/length(s1)*100)
+twoinone <- round(length(s2[s2 %in% s1])/length(s2)*100)
+
+```
+There was substantial agreement between the findings of Analysis 1 and 2;
+$`r oneintwo`%$ of the most frequent terms identified in the author keywords (Analysis 1)
+were also present in the frequent terms extracted from the abstracts using `textrank` (Analysis 2),
+and conversely, $`r twoinone`%$ of the most frequent terms from Analysis 2 were present in Analysis 1.
+
+## Discussion
+
+This second analysis focused on the abstracts of the reviewed articles.
+We observed a sparser network, with fewer selected terms.
+This might be explained by the unstructured format of abstracts,
+which likely introduces greater noise in the analysis.
+Thus, fewer terms will exceed the detection threshold.
+Nonetheless, the selected terms displayed substantial consistency with the
+analysis of author keywords.
+This supports the validity of the findings,
+suggesting that automatic keyword extraction from abstracts can identify relevant constructs,
+and may constitute a suitable alternative to author-provided keywords.
+
+The emergence of a "central axis" of dysregulation and mental health-related outcomes suggest that these phenomena are consistently studied together.
+By contrast, the lack of interconnectivity among other related constructs
+again suggests that the literature is somewhat fragmented.
+This impression is reinforced by the absence of many frequently occurring terms
+from the term co-occurrence graph.
+Finally, the substitution of "parenting" with "mothers" amonst the top-ranking terms 
+might suggest that parenting is commonly operationalized in terms of mothering [@pleckPaternalInvolvementRevised2004].
+
+# General discussion
 
@@
 This issue is beyond the scope of the present study -->
+The present study conducted a systematic review of the literature,
+and performed bibliographic analysis to map factors currently
+considered to be relevant to adolescent emotion regulation in a nomological network.
+The results of this inductive approach echoed many of the constructs considered
+relevant in the theoretical literature.
+It also revealed several constructs that have been underrepresented in theory,
+but nonetheless occur frequently in the empirical literature.
+The structure of the term co-occurrence networks revealed that most of the relevant constructs are connected
+directly with emotion dysregulation or its mental health correlates,
+with relatively few interconnections amongst constructs.
+This echoes the sentiment by @bussTheoriesEmotionalDevelopment2019 that this
+literature is somewhat fragmented.
+The present systematic review takes a first step towards integrating this diffuse field.
+
+Our work represents one of the first efforts to map the literature on adolescents' emotion dysregulation [cf. @bariolaChildAdolescentEmotion2011; @coe-odessEmergentEmotionsAdolescence2019].
+Moreover, it is one of the first applications of inductive text mining methods in a systematic review.
+Traditional narrative literature reviews have been shown to be marred by reliance on (small) convenience samples of the literature, confirmation bias, and an undue emphasis on positive results [@littellEvidencebasedBiasedQuality2008].
+Text mining, by contrast, is uniquely suited to provide a comprehensive overview of the literature.
+It can cover vastly greater corpora than a human reader,
+and the process by which text mining gleans insights from the literature is less subjective, and more transparant and reproducible.
+The inherent "fairness" of text mining gives emerging themes in the literature a chance to come to the fore,
+where human readers might be inclined to structure their reading of the literature around established ideas.
+
+Of course, the present study also has limitations.
+One such limitation is the fact that the text mining techniques used
+are not able to extract *meaning* from the literature in the way a human reader would.
+This limitation is best addressed by using the output of our text mining analysis as a starting point for further inductive thought,
+or a more in-depth reading of a subset of the reviewed literature.
+Relatedly, our methods do not capture the nature of the relationship between co-occurring terms.
+Instead, we manually classified terms as potential causes, outcomes, protective factors, or indicators based on domain knowledge.
+It is worth noting that efforts are underway to develop unsupervised algorithms capable of distilling causal links from bodies of scientific abstracts [@anExtractingCausalRelations2019].
+Applying such methods to the present corpus might substantially advance theory formation.
+<!--For example, a human reader would understand that the influence of mothers and fathers both
+falls under the header of "parenting". 
+Furthermore, a human reader would swiftly learn that the term "parenting" has historically been used primarily to represent maternal influences,
+and has increasingly come to represent paternal influence as well. -->
+
+One final limitation of the present study is that our analysis was limited to keywords and abstracts.
+Analysis of full-text papers would undoubtedly yield additional insights.
+Regrettably, paywalls and the lack of a unified API currently prevent such analysis.
+This highlights the importance of open science: 
+With comprehensive open access publishing, we may one day be able to mine the entire published literature for insights.
+A proof of concept for this approach was recently provided by the release of 50k+ full-text papers on topics related to COVID-19 for text mining analysis [@wangCORD19Covid19Open2020].
+
+To conclude, this paper set out to map the factors associated with adolescents' emotion dysregulation, based on a systematic review of the literature, and text mining analysis of author keywords and abstracts.
+We provided a map of the literature on adolescents' emotion dysregulation,
+covering both familiar ground, and charting unknown territories.
+Our results suggested that several key constructs are currently underrepresented in theory,
+and that the empirical literature is somewhat fragmented by sub-topic.
+These inductive insights are relevant for the design of new deductive studies which,
+even though grounded in theory,
+might benefit from incorporating additional relevant factors
+to better elucidate the nature of their association with adolescents' emotion dysregulation.
+Our analysis also identified several factors currently on the fringes of the literature,
+which might represent emerging themes that would benefit from further research [including, for example, the role of fathers @vanlissaMothersFathersQuantitative2020].
+Most importantly, given the lack of an overarching theory tailored specifically to adolescent emotion dysregulation,
+our nomological networks might serve as a starting point for theory development,
+with the aim of integrating the present inductive insights within the framework of existing relevant theory.
 

### 2020-10-18 study1.R

@@ -12,7 +12,8 @@ library(ggplot2)
 library(yaml)
 source("word_functions.R")
 run_everything = FALSE
-study1_details <- read_yaml("study1_details.yml")
+study1details <- read_yaml("study1_details.yml")
+dict <- read_yaml("yaml_dict.txt")
 ## Look at POS tags?
 if(run_everything){
   recs <- data.table(read.csv("recs_final.csv"))
@@ -28,7 +29,7 @@ if(run_everything){
   # Clean
   df <- na.omit(df, cols = "word")
   number_docs_words <- c(docs = length(unique(df$doc)), words = length(unique(df$word)))
-  
+  yaml::write_yaml(number_docs_words, "study1_number_docs_words.txt")
   # Exclude words
   exclude_terms <- readLines("exclude_terms.txt")
   exclude_these <- unique(unlist(lapply(exclude_terms, grep, x = df$word)))
@@ -36,7 +37,6 @@ if(run_everything){
   df <- df[!exclude_these, ]
   
   # Categorize words
-  dict <- read_yaml("yaml_dict.txt")
   res_cat <- cat_words(df$word, dict, handle_dups = "all")
   # Check coding issues
   #res_cat$dup
@@ -45,6 +45,7 @@ if(run_everything){
   saveRDS(df, "study1_df.RData")
 } else {
   df <- readRDS("study1_df.RData")
+  number_docs_words <- yaml::read_yaml("study1_number_docs_words.txt")
 }
 
 # Create plot data --------------------------------------------------------
@@ -119,7 +120,55 @@ topterms <- colSums(dtm_top)
 word_freq <- data.frame(Word = names(topterms), Frequency = topterms, row.names = NULL)
 write.csv(word_freq, "study1_word_freq.csv", row.names = FALSE)
 df_plot <- word_freq
+categ <- read.csv("study1_categorization.csv", stringsAsFactors = FALSE)
+df_plot$cat <- categ$category[match(df_plot$Word, categ$name)]
 df_plot$Word <- pretty_words(df_plot$Word)
+
+df_plot <- df_plot[order(df_plot$Frequency, decreasing = TRUE), ]
+df_plot$Word <- ordered(df_plot$Word, levels = df_plot$Word[order(df_plot$Frequency)])
+
+cat_cols <- c(Outcome = "gray50", Indicator = "tomato", Cause = "gold", Protective = "forestgreen")
[…]

### 2020-10-18 study2.R

@@ -36,7 +36,7 @@ if(!file.exists("english-ewt-ud-2.4-190531.udpipe")) {
   ud_model <- udpipe_download_model(language = "english")
 } else {
   ud_model <- udpipe_load_model("english-ewt-ud-2.4-190531.udpipe")
-  ud_model <- udpipe_load_model(ud_model$file_model)
+  ud_model <- udpipe_load_model(ud_model$file)
 }
 
 
@@ -81,7 +81,7 @@ if(run_everything){
   df_lda <- df_lda[df_lda$term %in% select_words, ]
   
   dtm <- udpipe::document_term_matrix(document_term_frequencies(df_lda))
-  
+  yaml::write_yaml(dim(dtm), file = "Study2_lda_dims.txt")
   
   # Build topic models
   seqk <- seq(2, 20, 1)
@@ -191,6 +191,8 @@ if(run_everything){
 
 # Frequency of word by doc
 nounbydoc <- df_analyze[, list(freq = .N), by = list(doc_id = doc_id, term = word_coded)]
+number_docs_words2 <- c(docs = length(unique(nounbydoc$doc_id)), words = length(unique(nounbydoc$term)))
+
 nounbydoc$freq <- 1
 dtm <- udpipe::document_term_matrix(document_term_frequencies(nounbydoc))
 topterms <- colSums(dtm)
@@ -233,6 +235,44 @@ dev.off()
 png("study2_wordcloud.png")
 eval(p)
 dev.off()
+
+
+# Feature importance ------------------------------------------------------
+topterms <- colSums(dtm_top)
+word_freq <- data.frame(Word = names(topterms), Frequency = topterms, row.names = NULL)
+df_plot <- word_freq
+categ <- read.csv("study1_categorization.csv", stringsAsFactors = FALSE)
+df_plot$cat <- categ$category[match(df_plot$Word, categ$name)]
+df_plot$Word <- pretty_words(df_plot$Word)
+
+df_plot <- df_plot[order(df_plot$Frequency, decreasing = TRUE), ]
+df_plot$Word <- ordered(df_plot$Word, levels = df_plot$Word[order(df_plot$Frequency)])
+
+cat_cols <- c(Outcome = "gray50", Indicator = "tomato", Cause = "gold", Protective = "forestgreen")
+df_plot$cat <- ordered(df_plot$cat, levels = c("Outcome", "Indicator", "Cause", "Protective"))
+
[…]

### 2020-10-18 varimpplot.R

@@ -1,0 +1,56 @@
+VarImpPlot <- function (mf, n.var = 30, sort = TRUE, ...){
+  UseMethod("VarImpPlot", mf)
+}
+
+VarImpPlot.numeric <- function (mf, n.var = 30, sort = TRUE, ...) 
+{
+  if(is.null(names(mf))){
+    stop("VarImpPlot.numeric requires a named vector.", call. = FALSE)
+  }
+  var_importance <- data.frame(Variable = names(mf), 
+                               importance = abs(mf))
+  if(any(mf < 0)){
+    var_importance$Sign <- c("-", NA, "+")[sign(mf)+2]
+  }
+  rownames(var_importance) <- NULL
+  if (sort) {
+    var_importance <- var_importance[order(-var_importance$importance), 
+    ]
+  }
+  n.var <- min(n.var, nrow(var_importance))
+  var_importance <- var_importance[1:n.var, ]
+  var_importance <- var_importance[rev(rownames(var_importance)), 
+  ]
+  var_importance$Variable <- factor(var_importance$Variable, 
+                                    levels = var_importance$Variable)
+  p <- ggplot(var_importance, aes_string(y = "Variable", x = "importance")) + 
+    geom_segment(aes_string(x = 0, xend = "importance", 
+                            y = "Variable", yend = "Variable"), colour = "grey50", 
+                 linetype = 2) + geom_vline(xintercept = 0, colour = "grey50", 
+                                            linetype = 1) + xlab("Variable Importance (absolute value)") + 
+    theme_bw() + theme(panel.grid.major.x = element_blank(), 
+                       panel.grid.minor.x = element_blank(), axis.title.y = element_blank())
+  if(ncol(var_importance) == 3){
+    p <- p + geom_point(aes_string(fill = "Sign"), shape = 21) + 
+      scale_fill_manual(values = c("+" = "white", "-" = "black")) + 
+      theme(legend.position = c(0.96, 0.09))
+  } else {
+    p <- p + geom_point(shape = 1, size = 2)
+  }
+  
+  if (hasArg("label_elements")) {
+    label_elements <- eval(match.call()[["label_elements"]])
+    levels(p$data$Variable) <- rename_fun(levels(p$data$Variable), 
+                                          names(label_elements), label_elements)
+  }
+  return(p)
+}
+
[…]

### 2020-11-24 manuscript.Rmd
Rewrite theoretical section

@@
 abstract: |
-  For many, adolescence marks the onset of emotion dysregulation and related mental health problems.
-It is therefore essential to have a solid grasp of relevant risk factors.
-Despite an abundance of empirical research, the literature is somewhat fragmented, as the topic has been investigated from different perspectives across subdisciplines.
-This systematic review uses text mining to map factors related to adolescent emotion dysregulation.
-A systematic search for publications that addressed emotion regulation in participants between the ages of 10-25 yielded 6305 suitable papers.
-One analysis focused on author-provided keywords, and a second extracted sequences of adjectives and nouns from the abstracts.
-Terms were classified with a dictionary describing 105 terms using 434 regular expressions.
-Terms were coded as putative “Causes”, “Outcomes”, “Protective factors”, or “Indicators” of emotion dysregulation.
+  Adolesence is a developmentally sensititve period for emotion dysregulation.
+Although substantial empirical research has addressed relevant risk factors, an integrating framework is lacking.
+This systematic review of 6305 papers uses text mining to map correlates of adolescents’ (ages 10-25) emotion dysregulation.
+One analysis focused on author-provided keywords; a second analysis parsed the abstracts.
+Terms were coded as putative “Causes”, “Outcomes”, “Protective factors”, or “Indicators”.
 We reported term/document frequency, and force-directed graphs of term co-occurrence.
 These results reﬂected constructs commonly featured in theory and narrative reviews, but also identified underrepresented terms.
-This illustrates how text mining review may complement narrative reviews.
-Importantly, most constructs were directly related to emotion dysregulation, with few interconnections between constructs – reflecting the fragmented literature.
 This research constitutes a first step towards integrating the literature, and may inspire future empirical and theoretical work.
+It also illustrates how text mining reviews may complement narrative reviews.
+<!--SH I would end with a more memorable take-home about how text-mining can be useful to researchers (e.g., when topics are of multi-disciplinary interest but each field has their own preferred methods and/or terminology)-->
 
@@
 classoption       : "man,noextraspace"
-output            : papaja::apa6_pdf
+output            : papaja::apa6_word
 knit              : worcs:::cite_essential
@@
 @zimmermannEmotionRegulationEarly2014]. Emotion regulation is integral to
-mental health[@aldaoEmotionregulationStrategiesPsychopathology2010;
+mental health [@aldaoEmotionregulationStrategiesPsychopathology2010;
 @schaferEmotionRegulationStrategies2017; @braetEmotionRegulationChildren2014]
@@
 regulation-related mental illness, which can persist throughout the life course
-[see @leeAdolescentMentalHealth2014]. It is therefore crucial to identify which
+[see @leeAdolescentMentalHealth2014]. 
+It is therefore crucial to identify which
 risk factors and environmental hazards render some adolescents more susceptible
-to emotional difficulties than others. Although there is an abundance of
-empirical work on adolescents' emotion regulation, the literature is somewhat
-fragmented, as the topic has been investigated from different (sub)disciplines.
-This systematic review seeks to overcome this limitation by using
-bibliographic analysis to map all factors currently
-considered to be relevant to adolescent emotion regulation. <!-- Ergens anders: Similarly, although
+to emotional difficulties than others. <!--SH: Main goal of paper -->
+The present review set out to address this question.
+Although there is an abundance of empirical work on adolescents' emotion regulation, the literature is somewhat fragmented, as the topic has been investigated from different (sub)disciplines.
+This systematic review seeks to overcome this limitation by adopting a novel method -
+text mining based bibliographic analysis - to map all factors currently
+considered to be relevant to adolescent emotion regulation.
+Text mining can reveal important topics in a body of literature,
+and reveal which constructs are often studied together.
+It is therefore uniquely suited to comprehensively review a prolific but fragmented field,
+potentially revealing topics and connections missed by narrative reviewers,
+and laying the groundwork for future empirical and theoretical work.
+<!-- SH: this implies that the main contribution of the paper is predominantly methodological is that the case?
+Is there some primary thesis/argument that will be advanced?
+It is really important to take a top-down approach to that messaging, beginning here in the first paragraph-->
+<!-- Ergens anders: Similarly, although
 there are several *relevant* theories, there is no specific theoretical
@@
 
-## Why adolescence is an important life phase for emotion regulation
-
-Adolescence is defined as a life phase ranging from pubertal onset to
+## Why adolescence is an important life stage for emotion regulation
+
+Adolescence is defined as a life stage ranging from pubertal onset to
 adult-like independence [@steinbergAgeOpportunityLessons2014].
-It is thus demarcated by both biological- and socio-cultural factors.
+It is thus demarcated by both biological and socio-cultural factors.
 It has been argued that,
@@
 
-## Existing relevant theory
-
-Theory is of paramount importance when seeking to understand or explain a
-phenomenon. Although there are many relevant theories, none have specifically
-addressed emotion regulation development in adolescence. Several recent
-publications have undertaken the monumental task of comprehensively reviewing
-theory relevant to emotional development
-[@bussTheoriesEmotionalDevelopment2019;
-@riedigerEmotionRegulationAdolescence2014]. Thanks, in part, to these efforts,
-we can provide a summary review of the theoretical landscape as context for our
-empirical contribution.<!--Several recent publications have undertaken the
+## Existing theoretical landscape
+
+The structure of the empirical literature on adolescents' emotion regulation is best understood against the backdrop of the existing theoretical landscape.
+This allows us to see in what respects 
+phenomenon.
+We therefore provide a summary review of the theoretical landscape as context for our
+empirical contribution.
+Several recent publications provide more detailed reviews of theories of emotional development [@bussTheoriesEmotionalDevelopment2019] and emotion regulation in adolescence [@riedigerEmotionRegulationAdolescence2014].
+It is apparent from these reviews that, although many theories are *relevant* for emotion regulation development in adolescence, few have addressed this topic directly.
+Fewer theories still have comprehensively addressed important predictors of development in this life stage,
+and none directly guide contemporary research in the field [see @bussTheoriesEmotionalDevelopment2019].
+There is thus a need for more integrative theory formation [see @riedigerEmotionRegulationAdolescence2014].
+
+Hall's notion of "storm and stress" is one of the oldest relevant theories of adolescents' emotional development [see
+@arnettAdolescentStormStress1999]. It describes how hormonal changes diminish
+self-control and increase reactivity, leading to difficulties in emotion
+regulation, conflict with parents, and risky behavior.
+In modern theories, this notion of diminished self-control and increased emotional reactivity has been - although it is now considered to be a normative change that facilitates emotional maturation
+[@croneUnderstandingAdolescencePeriod2012], at the risk of emotional
+disturbance [@arnettAdolescentStormStress1999; @leeAdolescentMentalHealth2014].
+
+<!--SH I am still not sure what the empirical contribution is - can you be more specific with it in this sentence? -->
+<!--Several recent publications have undertaken the
 monumental task of providing a comprehensive overview of theories of emotional
@@
 influences gradually gain ground on proximal influences.
-
-Turning now towards theories specifically addressing emotion regulation in
-adolescence, Hall's notion of "storm and stress" is one of the oldest [see
-@arnettAdolescentStormStress1999]. It describes how hormonal changes diminish
-self-control and increase reactivity, leading to difficulties in emotion
-regulation, conflict with parents, and risky behavior. Recent work provides a
-more nuanced perspective on this theory. For example, although the notion of
-diminished self-control and increased emotional reactivity has been upheld, it
-has been recast as a necessary change that facilitates emotional maturation
-[@croneUnderstandingAdolescencePeriod2012], at the risk of emotional
-disturbance [@arnettAdolescentStormStress1999; @leeAdolescentMentalHealth2014].
-More recently, Sroufe [-@sroufeEmotionalDevelopmentOrganization1995] presented
-a theory focused on normative emotional development in early childhood. It
-argues that, as children grow older, their increasing self-regulatory abilities
+<!--SH I am not sure what contribution this paragraph ultimately makes - you should consider condensing it substantially to just note that these theories have something to say about emotional development but are not adolescent-specific-->
+
+One example of a normative theory of emotional development in early childhood is presented by Sroufe [-@sroufeEmotionalDevelopmentOrganization1995].
+Sroufe argues that, as children grow older,
+their increasing self-regulatory abilities
 drive a transition from external emotion regulation by primary caregivers
@@
 attachment. Cognitive influences occur through the development of the central
-nervous system (CNS), cognition, and self-regulation. Several other theories,
-introduced below, have extemporized on these sources of influence.
-
-Several other models echo this emphasis on neorocognitive development as a driver of emotional
-development, including emotion regulation development.
+nervous system (CNS), cognition, and self-regulation.
+
+This emphasis on social influences and neurocognitive development is reflected in many theories.
+Some of these focus primarily on neurocognitive development.
 For example, polyvagal theory closely links emotional experience
 - and regulation - to autonomous nervous system functioning
-[@porgesOrientingDefensiveWorld1995]. A more recent neorocognitive theory, with
+[@porgesOrientingDefensiveWorld1995].
+A more recent neurocognitive theory, with
 substantial relevance to adolescents' emotion regulation development, is Crone
 and Dahl's model of social-affective engagement and goal flexibility
-[@croneUnderstandingAdolescencePeriod2012]. This theory is based on the notion
-of a "maturity gap" in middle-adolescence, arising from a developmental
-asymmetry between motivational and inhibitory brain circuits
-[@craccoEmotionRegulationChildhood2017;
-@caseyBrakingAcceleratingAdolescent2011]. To
-a greater extent than related writings, however, @croneUnderstandingAdolescencePeriod2012
-set out to explain adolescents' diverging destinies; the
-question why some youngsters flourish while others languish. Crone and Dahl
-argue that adolescents' cognitive engagement is dynamically responsive to
+[@croneUnderstandingAdolescencePeriod2012]. Like other authors 
+[e.g., @caseyBrakingAcceleratingAdolescent2011; @craccoEmotionRegulationChildhood2017],
+Crone and Dahl argue that the developmental
+asymmetry between motivational and inhibitory brain circuits gives rise to a
+"maturity gap" in middle adolescence. 
+What sets Crone and Dahl apart from related writings, however, 
+is the greater attention to adolescents' diverging destinies:
+the question why some youngsters flourish while others languish.
+They argue that adolescents' cognitive engagement is dynamically responsive to
 social and motivational goal salience. This flexibility, on the one hand,
@@
 
-A theory focused specifically on parents' role in emotion regulation
-development is Morris' tripartite model [-@morrisRoleFamilyContext2007]. It
-describes three pathways through which parents shape emotion regulation
+Other theories emphasize socialization to a greater extent.
+One such theory is Morris' tripartite model, which focuses specifically on parents' role in emotion regulation development [-@morrisRoleFamilyContext2007].
+It describes three pathways through which parents shape emotion regulation
 development: Through observation and modeling, parenting practices, and the
@@
 [@reindlSocializationEmotionRegulation2016].
-
-Whereas our primary interest is in theories of emotional development,
-theories of the phenomenon of
-emotion regulation are also somewhat relevant. One influential theory is Gross'
+A more abstract take on socialization is found in @holodynskiDevelopmentEmotionsEmotion2006's
+internalization model of emotional development. 
+Unique aspects emphasized in this theory are the interplay between emotion and communication,
+and the internalization of the cultural symbolic function of emotion.
+<!--Like Sroufe, Holodynski describes an age graded transition from
+interpersonal to intrapersonal emotion regulation.
+In doing so, Holodynski applies Vygotsky's theory of development to the domain of
+emotion, and presents a detailed integrated model of emotional experience and
+regulation.-->
+
+Finally, theories of the phenomenon of emotion regulation offer a unique perspective on potential proximal drivers of emotion regulation development.
+One influential theory is Gross'
 [-@grossHandbookEmotionRegulation2013] process model, which describes the
 process of emotion regulation, from eliciting cue to ultimate response.
-Individuals modulate the different stages of this process using strategies,
-consciously or otherwise. The effectiveness, desireability, and consequences of
-different strategies depend on the cultural context [see
+According to Gross, individuals use strategies to modulate the different stages of this process,
+consciously or otherwise. Culture plays a role too, as the effectiveness, desireability, and consequences of different strategies depend on the social context [see
 @bariolaChildAdolescentEmotion2011]. Similar to Gross' theory, the social
-information processing theory of emotion also describe the role of intrapsychic
-processes and strategies in emotion experience and reulation
+information processing theory of emotion also describe the role of cognitive
+processes and strategies in emotion experience and regulation
 [@lemeriseIntegratedModelEmotion2000].
 
-Another theory worth mentioning in this context is
-@holodynskiDevelopmentEmotionsEmotion2006's internalization model of emotional
-development. It applies Vygotsky's theory of development to the domain of
-emotion, and presents a detailed integrated model of emotional experience and
-regulation. Like Sroufe's work, this work describes a transition from
-interpersonal to intrapersonal emotion regulation. Other important features of
-this work include the interplay between emotion and communication, and the
-internalization of the socio-cultural symbolic function of emotion throughout
-development. <!--Theories like this are particularly relevant to a fine-grained
+<!--Theories like this are particularly relevant to a fine-grained
 understanding of the process of emotion regulation, but their developmental
@@
 One crucial shortcoming
-is the lack of explicit attention to the life phase of adolescence. This is
+is the lack of explicit attention to the life stage of adolescence. This is
 unfortunate, as empirical research consistently indicates that adolescence is a
-crucial life phase for emotion regulation development. Adolescence differs
+crucial life stage for emotion regulation development. Adolescence differs
 qualitatively from infancy, childhood, and adulthood. It is therefore
@@
 present study. First, although there are many *relevant* theories, few are
-focused specifically on emotion regulation. Second, the phase of adolescence is
+focused specifically on emotion regulation. Second, the stage of adolescence is
 rarely addressed, although empirical research has indicated that this is a
@@
 <!-- NIET TEVEEL OVER THEORIE PRATEN; IK KIJK NIET NAAR THEORIE. IK KIJK NAAR FACTOREN DIE IN VERBAND GEBRACHT WORDEN MET EMOTIEREGULATIE. -->
-<!--The life phase of adolescence differs qualitatively from both childhood and adulthood. It is therefore not sufficient to extend -->
+<!--The life stage of adolescence differs qualitatively from both childhood and adulthood. It is therefore not sufficient to extend -->
 
@@
 First, papers had to address emotion regulation, emotional problems, or similar.
-Second, the target population must overlap with the life phase of adolescence, defined as the age range from 10-25.
+Second, the target population must overlap with the life stage of adolescence, defined as the age range from 10-25.
 Thus, for example, an article reviewing the role of hormonal changes in emotional adjustment throughout the entire life course, including adolescence, would be deemed relevant.
@@
 lda_dims <- read_yaml("Study1_lda_dims.txt")
+dtm_top <- read_yaml("study1_dtm_top.yml")
 ```

### 2020-11-24 baseline.R

@@ -1,0 +1,97 @@
+library(data.table)
+#library(bibliometrix)
+#library(yaml)
+library(stringr)
+#library(lattice)
+#library(topicmodels)
+library(udpipe)
+library(igraph)
+library(wordcloud)
+library(Matrix)
+library(ggplot2)
+library(yaml)
+source("word_functions.R")
+run_everything = TRUE
+dict <- read_yaml("yaml_dict.txt")
+## Look at POS tags?
+if(run_everything){
+  recs <- readLines("concepts_review.txt")
+  df <- data.frame(word = trimws(tolower(recs)))
+  
+  # Categorize words
+  res_cat <- cat_words(df$word, dict, handle_dups = "all")
+  baseline <- c("dysregulation", unique(res_cat$words))
+  saveRDS(baseline, "baseline.RData")
+} else {
+  baseline <- readRDS("baseline.RData")
+}
+
+
+df_plot <- data.frame(term1 = baseline, term2 = "dysregulation")
+
+edg <- df_plot
+
+edg$width = 1
+
+vert <- data.frame(name = baseline, label = pretty_words(baseline), size = 1)
+vert <- vert[vert$name %in% unique(c(edg$term1, edg$term2)), ]
+
+categ <- read.csv("study1_categorization.csv", stringsAsFactors = FALSE)
+if(any(!vert$name %in% categ$name)){
+  write.table(vert$name[!vert$name %in% categ$name], "clipboard", sep = "\n", row.names = FALSE, col.names= FALSE)
+  stop("Please re-categorize missing vertices.")
+} 
+vert$Category <- categ$category[match(vert$name, categ$name)]
+
+cat_cols <- c(Outcome = "gray50", Indicator = "tomato", Cause = "gold", Protective = "forestgreen")
+cat_cols <- c(Outcome = "gray50", Indicator = "tomato", Cause = "gold", Protective = "olivedrab2")
+vert$color <- cat_cols[vert$Category]
+
+#min_size <- (strwidth(vert$name[max(nchar(vert$name))]) + strwidth("oo")) * 100
+vert$size <- scales::rescale(log(vert$size), c(4, 12))
+g <- graph_from_data_frame(edg, vertices = vert,
+                           directed = FALSE)
+#g <- Rsenal::pruneEdg
+#min_size <- (strwidth(vert$label[max(nchar(vert$label))]) + strwidth("oo"))*100
+
+# edge thickness
[…]

### 2020-11-24 study1.R

@@ -67,121 +67,145 @@ if(run_everything){
 #df[, id := NULL]
 #head(df)
 
-# Frequency of word by doc
-nounbydoc <- df[, list(freq = .N), by = list(doc_id = doc, term = word_coded)]
-# Set frequency to 1; we're not interpreting word frequency, only occurrence
-nounbydoc$freq <- 1
-# tmp <- nounbydoc %>%
-#   bind_tf_idf(term, doc_id, freq)
-# summary(tmp$tf_idf)
-
-dtm <- udpipe::document_term_matrix(document_term_frequencies(nounbydoc))
-# topterms <- colSums(dtm)
-# topterms <- sort(topterms, decreasing = TRUE)
-
-
-# Continue plotting word frequency ----------------------------------------
-
-# tt <- as.data.frame(table(topterms), stringsAsFactors = FALSE)
-# tt$Frequency <- as.numeric(tt$topterms)
-# tt$Words <- tt$Freq
-# tt$Dictionary <- "Recoded"
-# df_plot <- rbind(df_plot, tt[, c("Frequency", "Words", "Dictionary")])
-# p <- ggplot(df_plot, aes(x=Frequency, y = Words, linetype = Dictionary))+geom_point() + geom_path()+
-#          theme_bw() + scale_y_log10()+scale_x_log10()
-# 
-# ggsave("study1_word_frequency.png", p, device = "png")
-
-
-# Select most common terms ------------------------------------------------
-
-# tmp <- as.data.frame.table(table(topterms), stringsAsFactors = FALSE)
-# tmp$Var1 <- as.numeric(tmp$topterms)
-# plot(tmp$Var1, tmp$Freq, type = "b")
-
-#interesting_terms <- select_words(dtm, q = .975)
-#sum(interesting_terms)
-
-#topterms <- topterms[topterms > .005*nrow(recs)]
-#topterms <- colSums(dtm)[select_words(dtm)]
-#topterms <- sort(topterms, decreasing = TRUE)
-#topterms <- topterms[topterms > 13]
-#which_topterms <- head(topterms, 250)
-#which_topterms <- names(which_topterms)
-set.seed(5348)
-dtm_top <- dtm[, select_words(dtm, .975)]
-dtm_top <- dtm_top[rowSums(dtm_top) > 0, ]
-dim(dtm_top)
-
-# Wordcloud ---------------------------------------------------------------
-
-## Word frequencies
-topterms <- colSums(dtm_top)
[…]

### 2020-11-24 study2.R

@@ -17,7 +17,7 @@ library(tidytext)
 library(ggplot2)
 library(textrank)
 source("word_functions.R")
-run_everything <- FALSE
+run_everything <- TRUE
 
 ## Look at POS tags?
 
@@ -31,16 +31,13 @@ recs$AB <- tolower(recs$AB)
 #table(languages)
 #recs$AB[languages == "es"]
 
-
-if(!file.exists("english-ewt-ud-2.4-190531.udpipe")) {
-  ud_model <- udpipe_download_model(language = "english")
-} else {
-  ud_model <- udpipe_load_model("english-ewt-ud-2.4-190531.udpipe")
-  ud_model <- udpipe_load_model(ud_model$file)
-}
-
-
 if(run_everything){
+  if(!file.exists("english-ewt-ud-2.4-190531.udpipe")) {
+    ud_model <- udpipe_download_model(language = "english")
+  } else {
+    ud_model <- udpipe_load_model("english-ewt-ud-2.4-190531.udpipe")
+    ud_model <- udpipe_load_model(ud_model$file)
+  }
   udp_res <- udpipe_annotate(ud_model, x = recs$AB, doc_id = recs$doc)
   df <- as.data.table(udp_res)
   saveRDS(df, "study2_df.RData")
@@ -168,13 +165,12 @@ if(run_everything){
   kw_tr <- readRDS("study2_textrank.RData")
 }
 
-# Merge back with original data
-df_kw$keyword <- txt_recode_ngram(df_kw$lemma, compound = kw_tr$keywords$keyword, ngram = kw_tr$keywords$ngram, sep = " ")
-df_kw$keyword[!df_kw$keyword %in% kw_tr$keywords$keyword] <- NA
-
-df_analyze <- df_kw[!is.na(df_kw$keyword), ]
-
 if(run_everything){
+  # Merge back with original data
+  df_kw$keyword <- txt_recode_ngram(df_kw$lemma, compound = kw_tr$keywords$keyword, ngram = kw_tr$keywords$ngram, sep = " ")
+  df_kw$keyword[!df_kw$keyword %in% kw_tr$keywords$keyword] <- NA
+  
+  df_analyze <- df_kw[!is.na(df_kw$keyword), ]
   dict <- read_yaml("yaml_dict.txt")
   res_cat <- cat_words(df_analyze$keyword, dict, handle_dups = "all")
   # Check coding issues
@@ -189,204 +185,211 @@ if(run_everything){
 
[…]

### 2020-11-28 manuscript.Rmd
Add baseline

@@
 abstract: |
-  Adolesence is a developmentally sensititve period for emotion dysregulation.
+  <!--RK: Wat is je onderzoeksvraag?-->Adolesence is a developmentally sensititve period for emotion dysregulation.
   Although substantial empirical research has addressed relevant risk factors, an integrating framework is lacking.
@@
 These results reﬂected constructs commonly featured in theory and narrative reviews, but also identified underrepresented terms.
-This research constitutes a first step towards integrating the literature, and may inspire future empirical and theoretical work.
-It also illustrates how text mining reviews may complement narrative reviews.
-<!--SH I would end with a more memorable take-home about how text-mining can be useful to researchers (e.g., when topics are of multi-disciplinary interest but each field has their own preferred methods and/or terminology)-->
+This research constitutes a first step towards integrating the literature, and illustrates how text mining reviews may complement narrative reviews.
+<!--may inspire future empirical and theoretical work.
+SH: I would end with a more memorable take-home about how text-mining can be useful to researchers (e.g., when topics are of multi-disciplinary interest but each field has their own preferred methods and/or terminology)-->
 
@@
 and social functioning [@reindlSocializationEmotionRegulation2016]. For as many
-as one in five people, adolescence marks the onset of emotion
+as one in five, adolescence marks the onset of emotion
 regulation-related mental illness, which can persist throughout the life course
@@
 The present review set out to address this question.
-Although there is an abundance of empirical work on adolescents' emotion regulation, the literature is somewhat fragmented, as the topic has been investigated from different (sub)disciplines.
-This systematic review seeks to overcome this limitation by adopting a novel method -
+Although there is an abundance of empirical work on adolescents' emotion regulation, the literature is somewhat fragmented, because the topic has been investigated from different (sub)disciplines.
+As a result, there is a lack of unifying theory, and narrative reviews fall short of comprehensive coverage of the vast but diffuse literature [@bussTheoriesEmotionalDevelopment2019].
+
+The present systematic review seeks to overcome this limitation by adopting a novel method -
 text mining based bibliographic analysis - to map all factors currently
 considered to be relevant to adolescent emotion regulation.
-Text mining can reveal important topics in a body of literature,
-and reveal which constructs are often studied together.
-It is therefore uniquely suited to comprehensively review a prolific but fragmented field,
-potentially revealing topics and connections missed by narrative reviewers,
-and laying the groundwork for future empirical and theoretical work.
+Traditional narrative literature reviews have been shown to be marred by reliance on (small) convenience samples of the literature, confirmation bias,
+and an undue emphasis on positive results [@littellEvidencebasedBiasedQuality2008]. 
+Text mining, by contrast, is uniquely suited to provide a comprehensive overview of the literature.
+It can cover vastly greater corpora than a human reader,
+and the process by which text mining gleans insights from the literature is more objective, transparant, and reproducible.
+Where human readers might be inclined to structure their reading of the literature around established ideas,
+the inherent "fairness" of text mining gives emerging themes in the literature a chance to come to the fore.
+Text mining identifies important topics in a body of literature and reveals which constructs are often studied together.
+This potentially reveals topics and connections missed by narrative reviewers,
+thereby laying the groundwork for future empirical and theoretical work. <!-- CJ To fill out gaps, following up on promising constructs and unify heretofore disparate regions of the lit -->
 <!-- SH: this implies that the main contribution of the paper is predominantly methodological is that the case?
@@
 
-The structure of the empirical literature on adolescents' emotion regulation is best understood against the backdrop of the existing theoretical landscape.
-This allows us to see in what respects 
-phenomenon.
-We therefore provide a summary review of the theoretical landscape as context for our
-empirical contribution.
-Several recent publications provide more detailed reviews of theories of emotional development [@bussTheoriesEmotionalDevelopment2019] and emotion regulation in adolescence [@riedigerEmotionRegulationAdolescence2014].
-It is apparent from these reviews that, although many theories are *relevant* for emotion regulation development in adolescence, few have addressed this topic directly.
+The results of our text mining analysis of the empirical literature on adolescents' emotion regulation will be best understood against the backdrop of the existing theoretical landscape.
+We distinguish the topics covered in this theoretical review visually to highlight new issues
+in the subsequent text mining analysis.
+This allows us to see in what respects the text mining analysis reflects existing theory,
+and in what respects it complements it.
+We provide only a summary theoretical review here, as other recent publications offer more detailed reviews of theories of emotional development [@bussTheoriesEmotionalDevelopment2019] and emotion regulation in adolescence [@riedigerEmotionRegulationAdolescence2014].
+These prior reviews remark that,
+although many theories are *relevant* for emotion regulation development in adolescence,
+few have addressed this topic directly.
 Fewer theories still have comprehensively addressed important predictors of development in this life stage,
@@
 There is thus a need for more integrative theory formation [see @riedigerEmotionRegulationAdolescence2014].
-
-Hall's notion of "storm and stress" is one of the oldest relevant theories of adolescents' emotional development [see
+Inductive analysis of the empirical literature may constitute a first step to this end.
+
+Among the oldest relevant theories of adolescents' emotional development is Hall's notion of "storm and stress" [see
 @arnettAdolescentStormStress1999]. It describes how hormonal changes diminish
@@
 regulation, conflict with parents, and risky behavior.
-In modern theories, this notion of diminished self-control and increased emotional reactivity has been - although it is now considered to be a normative change that facilitates emotional maturation
+In modern theories, this notion of diminished self-control and increased emotional reactivity has been retained - although it is now considered to be a normative change that facilitates emotional maturation
 [@croneUnderstandingAdolescencePeriod2012], at the risk of emotional
@@
 
-Two theories widely invoked to frame research on development, including
-emotional development, are Bronfenbrenner's bioecological model, and Sameroff's
+One example of a normative theory of emotional development in early childhood is presented by Sroufe [-@sroufeEmotionalDevelopmentOrganization1995].
+Sroufe argues that, as children grow older,
+their increasing self-regulatory abilities
+drive a transition from external emotion regulation by primary caregivers
+towards autonomous emotion regulation. This theory focuses on two drivers of
+development: social and cognitive influences. Social influences mainly occur
+through parental co-regulation, parenting behaviors, and parent-child
+attachment. Cognitive influences occur through the development of the central
+nervous system (CNS), cognition, and self-regulation.
+
+This emphasis on social influences and neurocognitive development is reflected in many theories.
+Some of these focus primarily on neurocognitive development.
+For example, polyvagal theory closely links emotional experience
+- and regulation - to autonomous nervous system functioning
+[@porgesOrientingDefensiveWorld1995].
+A more recent neurocognitive theory relevant to adolescents' emotion regulation development is Crone
+and Dahl's model of social-affective engagement and goal flexibility
+[@croneUnderstandingAdolescencePeriod2012]. Like other authors 
+[e.g., @caseyBrakingAcceleratingAdolescent2011; @craccoEmotionRegulationChildhood2017],
+Crone and Dahl argue that the developmental
+asymmetry between motivational and inhibitory brain circuits gives rise to a
+"maturity gap" in middle adolescence. 
+What distinguishes Crone and Dahl from related writings
+is the greater attention to adolescents' diverging destinies:
+the question why some youngsters flourish while others languish.
+They argue that adolescents' cognitive engagement is dynamically responsive to
+social and motivational goal salience. This flexibility, on the one hand,
+prepares adolescents to effectively engage cognitive systems in novel
+challenging situations in a way that facilitates developing mature regulatory
+abilities. On the other hand, it places them at risk to act impulsively in
+pursuit of peer approval. In terms of explanans,
+this theory focuses primarily on cognitive factors
+and the role of peers, with less attention to factors such as parenting.
+Although this theory focuses on adolescence specifically,
+an important limitation is that it only tangentially relates to emotion regulation.
+
+Other theories emphasize socialization to a greater extent.
+One such theory is Morris' tripartite model, which focuses specifically on parents' role in emotion regulation development [-@morrisRoleFamilyContext2007].
+It describes three pathways through which parents shape emotion regulation
+development: Through observation and modeling, parenting practices, and the
+emotional family climate, which in turn involves attachment and marital
+relationship quality. Morris and colleagues also emphasize the relevance of
+fathers and siblings, and others have adapted the tripartite model to describe
+the role of peers in adolescents' emotion regulation development
+[@reindlSocializationEmotionRegulation2016].
+A more abstract take on socialization is found in @holodynskiDevelopmentEmotionsEmotion2006's
+internalization model of emotional development. 
+Unique aspects emphasized in this theory are the interplay between emotion and communication,
+and the internalization of the cultural symbolic function of emotion.
+These theories explain socialization in great detail,
+but one potential limitation is that tey are not embedded in a larger unifying framework.
+<!--Like Sroufe, Holodynski describes an age graded transition from
+interpersonal to intrapersonal emotion regulation.
+In doing so, Holodynski applies Vygotsky's theory of development to the domain of
+emotion, and presents a detailed integrated model of emotional experience and
+regulation.-->
+
+Looking beyond the developmental literature,
+theories of the phenomenon of emotion regulation offer additional insight into
+intra-individual drivers of emotion regulation development.
+Perhaps the most influential theory is Gross'
+[-@grossHandbookEmotionRegulation2013] process model, which describes the
+process of emotion regulation from eliciting cue to ultimate response.
+According to Gross, individuals use strategies to modulate the different stages of this process,
+consciously or otherwise. Culture plays a role too, as the effectiveness, desireability, and consequences of different strategies depend on the social context [see
+@bariolaChildAdolescentEmotion2011]. Similar to Gross' theory, the social
+information processing theory of emotion also describe the role of cognitive
+processes and strategies in emotion experience and regulation
+[@lemeriseIntegratedModelEmotion2000].
+
+Finally, given our interest in risk factors that render adolescents susceptible
+to emotional difficulties, we should mention two theories widely invoked to frame research on developmental influences: Bronfenbrenner's bioecological model, and Sameroff's
 transactional model. Bronfenbrenner's model
@@
 influences gradually gain ground on proximal influences.
+These theories are broad enough to contextualize any developmental study,
+but limited by a lack of specificity, which hampers their utility in generating hypotheses.
+<!-- RK: What do you take from these broad perspectives for your RQ?-->
 <!--SH I am not sure what contribution this paragraph ultimately makes - you should consider condensing it substantially to just note that these theories have something to say about emotional development but are not adolescent-specific-->
-
-One example of a normative theory of emotional development in early childhood is presented by Sroufe [-@sroufeEmotionalDevelopmentOrganization1995].
-Sroufe argues that, as children grow older,
-their increasing self-regulatory abilities
-drive a transition from external emotion regulation by primary caregivers
-towards autonomous emotion regulation. This theory focuses on two drivers of
-development: social and cognitive influences. Social influences mainly occur
-through parental co-regulation, parenting behaviors, and parent-child
-attachment. Cognitive influences occur through the development of the central
-nervous system (CNS), cognition, and self-regulation.
-
-This emphasis on social influences and neurocognitive development is reflected in many theories.
-Some of these focus primarily on neurocognitive development.
-For example, polyvagal theory closely links emotional experience
-- and regulation - to autonomous nervous system functioning
-[@porgesOrientingDefensiveWorld1995].
-A more recent neurocognitive theory, with
-substantial relevance to adolescents' emotion regulation development, is Crone
-and Dahl's model of social-affective engagement and goal flexibility
-[@croneUnderstandingAdolescencePeriod2012]. Like other authors 
-[e.g., @caseyBrakingAcceleratingAdolescent2011; @craccoEmotionRegulationChildhood2017],
-Crone and Dahl argue that the developmental
-asymmetry between motivational and inhibitory brain circuits gives rise to a
-"maturity gap" in middle adolescence. 
-What sets Crone and Dahl apart from related writings, however, 
-is the greater attention to adolescents' diverging destinies:
-the question why some youngsters flourish while others languish.
-They argue that adolescents' cognitive engagement is dynamically responsive to
-social and motivational goal salience. This flexibility, on the one hand,
-prepares adolescents to effectively engage cognitive systems in novel
-challenging situations in a way that facilitates developing mature regulatory
-abilities. On the other hand, it places them at risk to act impulsively in
-pursuit of peer approval. In terms of explanans,
-this theory focuses primarily on cognitive factors
-and the role of peers, with less attention to factors such as parenting.
-
-Other theories emphasize socialization to a greater extent.
-One such theory is Morris' tripartite model, which focuses specifically on parents' role in emotion regulation development [-@morrisRoleFamilyContext2007].
-It describes three pathways through which parents shape emotion regulation
-development: Through observation and modeling, parenting practices, and the
-emotional family climate, which in turn involves attachment and marital
-relationship quality. Morris and colleagues also emphasize the relevance of
-fathers and siblings, and others have adapted the tripartite model to describe
-the role of peers in adolescents' emotion regulation development
-[@reindlSocializationEmotionRegulation2016].
-A more abstract take on socialization is found in @holodynskiDevelopmentEmotionsEmotion2006's
-internalization model of emotional development. 
-Unique aspects emphasized in this theory are the interplay between emotion and communication,
-and the internalization of the cultural symbolic function of emotion.
-<!--Like Sroufe, Holodynski describes an age graded transition from
-interpersonal to intrapersonal emotion regulation.
-In doing so, Holodynski applies Vygotsky's theory of development to the domain of
-emotion, and presents a detailed integrated model of emotional experience and
-regulation.-->
-
-Finally, theories of the phenomenon of emotion regulation offer a unique perspective on potential proximal drivers of emotion regulation development.
-One influential theory is Gross'
-[-@grossHandbookEmotionRegulation2013] process model, which describes the
-process of emotion regulation, from eliciting cue to ultimate response.
-According to Gross, individuals use strategies to modulate the different stages of this process,
-consciously or otherwise. Culture plays a role too, as the effectiveness, desireability, and consequences of different strategies depend on the social context [see
-@bariolaChildAdolescentEmotion2011]. Similar to Gross' theory, the social
-information processing theory of emotion also describe the role of cognitive
-processes and strategies in emotion experience and regulation
-[@lemeriseIntegratedModelEmotion2000].
-
 <!--Theories like this are particularly relevant to a fine-grained
@@
 relevance has unfortunately not yet been considered (REF Buss). -->
-
 <!--Parents are widely considered to be the primary proximal influence driving
 emotion regulation development.
-
 Yet several limitations remain.
@@
 
-## Shortcomings of existing theory
-
+### Shortcomings of existing theory
+
+<!--Consider splitting this up and putting the shortcomings next to the existing theories-->
 Despite the abundance of relevant theory,
@@
 to maladaptive emotional development than others.
-One crucial shortcoming
-is the lack of explicit attention to the life stage of adolescence. This is
-unfortunate, as empirical research consistently indicates that adolescence is a
-crucial life stage for emotion regulation development. Adolescence differs
-qualitatively from infancy, childhood, and adulthood. It is therefore
-questionable whether theories focused on different ages can be generalized to adolescents.
-By contrast, some theories focus on adolescence specifically [e.g.,
-@croneUnderstandingAdolescencePeriod2012], but only address emotion regulation
-in passing.
-A second, related, shortcoming is that some relevant theories lack
-a developmental component <!--, and thus lack a well-substantiated
+One crucial shortcoming is that most theories lack of explicit attention to the life stage of adolescence.
+It is questionable whether theories focused on different ages can be generalized to adolescents,
+because this stage differs qualitatively from infancy, childhood, and adulthood [@bariolaChildAdolescentEmotion2011].
+A related limitation is that many relevant theories lack
+an explicit developmental component <!--, and thus lack a well-substantiated
 understanding of developmental processes--> [see
@@
 @croneUnderstandingAdolescencePeriod2012]. 
-A third shortcoming is that theories
-vary widely in scope: Some are very broad and all-encompassing, but somewhat
-non-specific, such as the biopsychosocial models of Bronfenbrenner and
-Sameroff. Others describe a specific phenomenon in great detail, but are not
-embedded in a larger unifying framework. Examples include Morris' tripartite
-model, Crone and Dahl's model, and polyvagal theory. It would be beneficial to
-bridge these levels of analysis.
-One limitation echoed across many
-publications in this field is that more theory formation is required to provide
-a unified framework that could guide future empirical work.
-The present study
-seeks to lay the groundwork for such theory development,
+Perhaps most importantly, however, these theories
+vary widely in scope: Some are broad but somewhat non-specific, such as the biopsychosocial models of Bronfenbrenner and Sameroff, and others describe a specific phenomenon, but lack a broader perspective.
+It would be beneficial to bridge these levels of analysis.
+Based on these shortcomings,
+there appears to be a need for more theory generation,
+in order to provide a unified framework that could guide future empirical work.
+<!--Such a theory should focus on -->
+The present study lays the groundwork for such theory development,
 by providing an inductive conceptual
 review of the field.
+Concepts covered in the preceding theoretical review will be tagged in the text mining analysis,
+to highlight the contribution of the inductive approach.
 
@@
 Finally, they address distal factors, including the role of culture and the
-media. Barriola and colleagues also offer recommendations for future research,
+media. Barriola and colleagues also 
 <!--most notably, they call for a robust theoretical framework to guide future
-research.--> calling for research on the role of parents beyond early
-childhood, and including the role of fathers - a limitation which has since
-been addressed by a new wave of empirical research on fathers' role in
-emotional development [@vanlissaRoleFathersMothers2019;
+research.--> call for future research to address parents' role beyond early
+childhood.
+They further argued that the role of fathers in emotion socialization warrants further scrutiny - a topic that is now receiving more attention [@vanlissaRoleFathersMothers2019;
 @vanlissaMothersFathersQuantitative2020].
 
-Another review, by @coe-odessEmergentEmotionsAdolescence2019, offers a nuanced
+Another review by @coe-odessEmergentEmotionsAdolescence2019 offers a nuanced
 discussion of several issues that complement prior publications in this field.
@@
 variability and dispositional emotion dysregulation [see also
-@vanlissaCostEmpathyParentadolescent2017]. As parental importance diminishes,
-adolescents become increasingly oriented towards peers. This includes increased
+@vanlissaCostEmpathyParentadolescent2017].
+Compared to children, adolescents also become increasingly oriented towards peers.
+This includes increased
 sensitivity to social status and norms, along with the associated increase in
@@
 There are notable parallels between the relevant factors highlighted by these
-narrative reviews, and the aforementioned theoretical literature. Nevertheless,
+narrative reviews, and the aforementioned theoretical literature.
+Nevertheless,
 these literature reviews also touch upon issues that have received little
-attention in theoretical work. This highlights the value of both top-down and
-bottom-up approaches to understanding the phenomenon of adolescents' emotion
-regulation. One remaining limitation is that, to date, all reviews in this
-field have been unstructured narrative reviews. The present publication seeks
+attention in theoretical work.
+These include individual differences, both at the biological and psychological level, including genetic predisposition, hormones, pubertal onset, gender, sexuality, temperament, identity, empathy, and stress.
+Proximal influences not covered in theory include the role of media, norms, and social status.
+Thus, reviews of the empirical literature can contribute additional insight into key factors in adolescents' emotion regulation development.
+One remaining limitation is that all reviews in this field have been unstructured narrative reviews.
+The present publication seeks
 to complement preceding work by conducting a comprehensive empirical
 literature review, and mapping the factors associated with adolescent emotion
-regulation.
+regulation using text mining.
 
@@
 
+<!-- SH: ultimately I think that the introduction is too long - considering that the introduction, itself, is a literature review to some extent, I don't come away with a clear delineation between the literature review up this point and the new work you are going to contribute.
+I think you need to review the Introduction with an eye on focusing the discussion on the problems/gaps that exist and how the lit review method usually used are insufficient for addressing those issues-->
+
 ## The present paper
@@
 explicit theory of the phenomenon. The present paper uses an inductive approach
-to develop this nomological network. First, we conduct a systematic search to
-elicit a corpus of relevant literature. Second, we use text mining techniques
-to extract relevant constructs from the corpus. Third, we use a dictionary to
+to develop this nomological network. <!-- CJ Consider removing the following if the purpose is sufficiently clarified in the introduction -->
+First, we conducted a systematic search to
+elicit a corpus of relevant literature. Second, we used text mining techniques
+to extract relevant constructs from the corpus. Third, we used a dictionary to
 pare down the extracted constructs to meaningful superordinate categories.
-Fourth, we map interrelations between these constructs. Fifth, we classify
+Fourth, we mapped interrelations between these constructs. Fifth, we classified
 contstructs as potential predictors or outcomes.
@@
 items. The terms `"emotio* socialization" OR "emotio* processes"`, as synonyms
-of emotion regulation, added 191 new hits. However, many of these hits were not
-directly relevant to emotion regulation. The term `"development*"`, as synonym
+of emotion regulation, added 191 new hits. However, most of these did not meet the inclusion criteria used for screening, as explained below.
+The term `"development*"`, as synonym
 of adolescence, added 3628 new hits, many of which were not focused on the age
@@
 Papers were screened based on two main criteria:
-First, papers had to address emotion regulation, emotional problems, or similar.
-Second, the target population must overlap with the life stage of adolescence, defined as the age range from 10-25.
+First, papers had to address emotion regulation or a synonymous construct.
+Second, the target population must overlap with the life stage of adolescence,
+defined as the age range from 10-24.
 Thus, for example, an article reviewing the role of hormonal changes in emotional adjustment throughout the entire life course, including adolescence, would be deemed relevant.
@@
 regular expression queries.
-The lead author composed a first draft of the dictionary.
+The author composed a first draft of the dictionary.
 This draft was subsequently updated in two ways:
-First, while writing the introduction for this paper,
-key terms from the literature were added to the dictionary.
-Second, by including frequently occurring uncategorized words during preliminary analyses of the data until no more frequently occurring uncategorized words were found.
+First, key terms from the literature were added to the dictionary while writing the Introduction.
+Second, all frequently occurring uncategorized words were added to the dictionary, until none remained.
 An exclusion list of methodological terms and other non-substantive words was generated using the same procedure.
@@
 
+<!-- it might be useful to insert a sentence or two when you are using a method many readers are not familiar with, just to explain the utility of the chose method (what it does/doesn't do potentially as compared to other options)-->
 To assess the homogeneity of the corpus, we conducted topic modeling using latent dirichlet allocation [@bleiLatentDirichletAllocation2003].
@@
 This resulted in `r dim(dtm_top)[2]` terms, which occurred in `r dim(dtm_top)[1]` documents.
-To illustrates what issues are covered in this body of literature, the selected terms are displayed in Figure \@ref(fig:study1varimp), on a logarithmic scale to reduce the skew of the negative binomial distribution.<!--;
+To illustrate what issues are covered in this body of literature, the selected terms are displayed in Figure \@ref(fig:study1varimp), on a logarithmic scale to reduce the skew of the negative binomial distribution.<!--;
 word size represents frequency of occurrence (squared to reduce the skew of the negative binomial distribution).-->
@@
 However, the analysis also revealed important areas less prominently featured in narrative reviews. 
-This illustrates how inductive reviews may complement existing theory and narrative reviews, and can reveal blindspots.
-
-It was found that connections among topics were relatively sparse: Many constructs were only related to emotion regulation,
+This illustrates how inductive reviews may complement existing theory and narrative reviews, and can reveal blindspots.<!-- SH: this point/advantage needs to feature more prominently in the introduction!-->
+
+Connections among topics were relatively sparse: Many constructs were only related to emotion regulation,
 and there were relatively few interconnections between elements.
@@
 
-Many of these excluded constructs represent active ongoing areas of research - such as the role of *fathers* [@vanlissaRoleFathersMothers2019], *identity* [@campbellFriendsEducationIdentity2019], *friendship* and *social support* [@bukowskiPopularityFriendshipEmotional1993], *autonomy* [@vrolijkLongitudinalLinkagesFatherunderreview; @brenningPerceivedMaternalAutonomy2015], *sexual risk* [@brownDepressiveSymptomsPredictor2006], and *loneliness* [@spithovenItAllTheir2017] in adolescents' emotional development.
+Many of these excluded constructs represent active ongoing areas of research - such as the role of *fathers* [@vanlissaRoleFathersMothers2019], *identity* [@campbellFriendsEducationIdentity2019], *friendship* and *social support* [@wangBidirectionalEffectsExpressive2020], *autonomy* [@vrolijkLongitudinalLinkagesFatherunderreview; @brenningPerceivedMaternalAutonomy2015], *sexual risk* [@brownDepressiveSymptomsPredictor2006], and *loneliness* [@spithovenItAllTheir2017] in adolescents' emotional development.
 The fact that these constructs are absent from the graph does not suggest that they are unimportant.
 Rather, it indicates that they are not yet well-integrated in the literature,
-and are therefore prime candidates for future research.
+and are therefore prime candidates for future research.<!-- RK: Or could they also suggest that they were relevant in the past, but not any longer?
+Might it be important to run sensitivity analyses by publication year?-->
 One recommendation for future research might be to study such important but unembedded constructs
@@
 The corpus for this second analysis consisted of the abstracts of the selected articles.
-Author keywords, as examined in Analysis 1, are carefully chosen to capture the core tenets of a study,
-and thus convey high-quality information directly relevant to the topic of a text.
+Keywords, as examined in Analysis 1, convey high-quality information because they are carefully chosen by authors to capture the essence of a study.
 However, as authors are
-typically limited to 5 keywords, some of a study's nuance may be lost.
+typically limited to 5 keywords, some nuance may be lost.
 Abstracts, by contrast, offer greater freedom of expression,
@@
 with features selected based on TF-IDF.
-This in a dataset consisting of `r lda_dims_2[1]` documents and `r lda_dims_2[2]` terms.
+This resulted in a dataset consisting of `r lda_dims_2[1]` documents and `r lda_dims_2[2]` terms.
 We considered a range from 2-20 topics, evaluating fit based on the BIC, and interpretability based on the entropy of the posterior document/topic probabilities.
@@
 to any other terms in the main network. 
-These terms, which are displayed in Figure \@ref(fig:study2varimp),\include the potential causes `r notingraph["Cause"]`, the potential outcomes `r notingraph["Outcome"]`, and the potential protective factors `r notingraph["Protective"]`.
+These terms, which are displayed in Figure \@ref(fig:study2varimp), include the potential causes `r notingraph["Cause"]`, the potential outcomes `r notingraph["Outcome"]`, and the potential protective factors `r notingraph["Protective"]`.
 
@@
 
-# General discussion
+# General Discussion
 
@@
 It also revealed several constructs that have been underrepresented in theory,
-but nonetheless occur frequently in the empirical literature.
+but nonetheless occur frequently in the empirical literature.<!--RK: But is that a bad thing? Can you please elaborate?-->
 The structure of the term co-occurrence networks revealed that most of the relevant constructs are connected
@@
 
+<!--CJ: Cut this here
 Our work represents one of the first efforts to map the literature on adolescents' emotion dysregulation [cf. @bariolaChildAdolescentEmotion2011; @coe-odessEmergentEmotionsAdolescence2019].
@@
 The inherent "fairness" of text mining gives emerging themes in the literature a chance to come to the fore,
-where human readers might be inclined to structure their reading of the literature around established ideas.
+where human readers might be inclined to structure their reading of the literature around established ideas.-->
 
 Of course, the present study also has limitations.
-One such limitation is the fact that the text mining techniques used
-are not able to extract *meaning* from the literature in the way a human reader would.
+One such limitation is the fact that the text mining techniques used here
+are not able to extract *meaning* from the literature in the way a sentient reader would.
 This limitation is best addressed by using the output of our text mining analysis as a starting point for further inductive thought,
@@
 
+<!-- RK: But please give us more content!
+Based on your meta-analysis, how would you move theory-formation forward?
+As the text stands now, this feels a bit empty.
+An that is a pity, given that in the intro you have beautifully sketched what theories we have.
+I think this paper would improve if you also explicitly mention what avenues are suggested by your meta-analysis.-->
+
 \newpage

### 2020-11-28 baseline.R

@@ -15,20 +15,33 @@ run_everything = TRUE
 dict <- read_yaml("yaml_dict.txt")
 ## Look at POS tags?
 if(run_everything){
-  recs <- readLines("concepts_review.txt")
-  df <- data.frame(word = trimws(tolower(recs)))
-  
+  bl_theory <- readLines("baseline_theory.txt")
+  bl_review <- readLines("baseline_reviews.txt")
+  df <- data.frame(word = trimws(tolower(bl_theory)), source = "theory")
+  df <- rbind(df, data.frame(word = trimws(tolower(bl_review)), source = "reviews"))
   # Categorize words
   res_cat <- cat_words(df$word, dict, handle_dups = "all")
-  baseline <- c("dysregulation", unique(res_cat$words))
+  df$cat <- res_cat$words
+  if(!is.null(res_cat[["unmatched"]])){
+    df <- df[!df$cat %in% names(res_cat$unmatched), ]
+  }
+  
+  baseline_cat <- df
+  baseline <- c("dysregulation", unique(df$words[df$source == "theory"]))
+  
   saveRDS(baseline, "baseline.RData")
+  saveRDS(baseline_cat, "baseline_cat.RData")
 } else {
   baseline <- readRDS("baseline.RData")
+  baseline_cat <- readRDS("baseline_cat.RData")
 }
 
+in_theory <- df$word[df$source == "theory"]
+in_rev <- df$word[!df$source == "theory"]
+in_rev[!in_rev %in% in_theory]
 
 df_plot <- data.frame(term1 = baseline, term2 = "dysregulation")
-
+df_plot <- df_plot[!df_plot$term1 == df_plot$term2, ]
 edg <- df_plot
 
 edg$width = 1
@@ -59,9 +72,9 @@ g <- graph_from_data_frame(edg, vertices = vert,
 
 
 
-set.seed(2) #4 #2 #3
+set.seed(3) #4 #2 #3
 l1 <- l <- layout_with_fr(g)
-set.seed(64)
+set.seed(33)
 l2 <- layout_in_circle(g)
 
 p <- quote({

### 2020-11-28 study1.R

@@ -11,6 +11,7 @@ library(Matrix)
 library(ggplot2)
 library(yaml)
 source("word_functions.R")
+
 run_everything = FALSE
 study1details <- read_yaml("study1_details.yml")
 dict <- read_yaml("yaml_dict.txt")
@@ -48,67 +49,19 @@ if(run_everything){
   number_docs_words <- yaml::read_yaml("study1_number_docs_words.txt")
 }
 
-# Create plot data --------------------------------------------------------
-# nounbydoc <- df[, list(freq = .N), by = list(doc_id = doc, term = word)]
-# nounbydoc$freq <- 1
-# dtm <- udpipe::document_term_matrix(document_term_frequencies(nounbydoc))
-# tt <- as.data.frame(table(colSums(dtm)), stringsAsFactors = FALSE)
-# tt$Frequency <- as.numeric(tt$Var1)
-# tt$Words <- tt$Freq
-# tt$Dictionary <- "Original"
-# df_plot <- tt[, c("Frequency", "Words", "Dictionary")]
-# rm(nounbydoc, dtm, tt)
-# End plot data -----------------------------------------------------------
-
-
-# Remove duplicate words per doc
-#df[, id := paste0(word_coded, doc)]
-#df <- df[!duplicated(id), ]
-#df[, id := NULL]
-#head(df)
 
 if(run_everything){
   # Frequency of word by doc
   nounbydoc <- df[, list(freq = .N), by = list(doc_id = doc, term = word_coded)]
   # Set frequency to 1; we're not interpreting word frequency, only occurrence
   nounbydoc$freq <- 1
-  # tmp <- nounbydoc %>%
-  #   bind_tf_idf(term, doc_id, freq)
-  # summary(tmp$tf_idf)
   
   dtm <- udpipe::document_term_matrix(document_term_frequencies(nounbydoc))
-  # topterms <- colSums(dtm)
-  # topterms <- sort(topterms, decreasing = TRUE)
-  
-  
+ 
   # Continue plotting word frequency ----------------------------------------
   
-  # tt <- as.data.frame(table(topterms), stringsAsFactors = FALSE)
-  # tt$Frequency <- as.numeric(tt$topterms)
-  # tt$Words <- tt$Freq
-  # tt$Dictionary <- "Recoded"
-  # df_plot <- rbind(df_plot, tt[, c("Frequency", "Words", "Dictionary")])
[…]

### 2020-12-16 manuscript.Rmd
Finalize manuscript

@@
 abstract: |
-  <!--RK: Wat is je onderzoeksvraag?-->Adolesence is a developmentally sensititve period for emotion dysregulation.
-  Although substantial empirical research has addressed relevant risk factors, an integrating framework is lacking.
-This systematic review of 6305 papers uses text mining to map correlates of adolescents’ (ages 10-25) emotion dysregulation.
-One analysis focused on author-provided keywords; a second analysis parsed the abstracts.
-Terms were coded as putative “Causes”, “Outcomes”, “Protective factors”, or “Indicators”.
-We reported term/document frequency, and force-directed graphs of term co-occurrence.
-These results reﬂected constructs commonly featured in theory and narrative reviews, but also identified underrepresented terms.
+  Adolesence is a developmentally sensititve period for emotion dysregulation.
+  Although substantial empirical research has addressed relevant risk factors,
+  the literature is fragmented across subdisciplines, and
+  an integrating framework is lacking.
+  This systematic review of 6305 papers used text mining to map correlates of adolescents’ (ages 10-25) emotion dysregulation.
+First, we established a baseline of relevant terms gleaned from theory and recent narrative reviews.
+Then, we conducted two text mining analyses to examine term/document frequency and co-occurrence in author-provided keywords and abstracts.
+Results reﬂected constructs commonly featured in theory and narrative reviews, but also identified underrepresented themes.
 This research constitutes a first step towards integrating the literature, and illustrates how text mining reviews may complement narrative reviews.
@@
 
-keywords          : "emotion regulation, adolescence, systematic review, text mining, machine learning"
 wordcount         : "5400"
@@
 classoption       : "man,noextraspace"
-output            : papaja::apa6_word
+output            : papaja::apa6_pdf
 knit              : worcs:::cite_essential
@@
 run_everything = FALSE
+notingraph <- list()
 ```
@@
 and social functioning [@reindlSocializationEmotionRegulation2016]. For as many
-as one in five, adolescence marks the onset of emotion
+as one in five individuals, adolescence marks the onset of emotion
 regulation-related mental illness, which can persist throughout the life course
@@
 to emotional difficulties than others. <!--SH: Main goal of paper -->
-The present review set out to address this question.
 Although there is an abundance of empirical work on adolescents' emotion regulation, the literature is somewhat fragmented, because the topic has been investigated from different (sub)disciplines.
-As a result, there is a lack of unifying theory, and narrative reviews fall short of comprehensive coverage of the vast but diffuse literature [@bussTheoriesEmotionalDevelopment2019].
-
-The present systematic review seeks to overcome this limitation by adopting a novel method -
-text mining based bibliographic analysis - to map all factors currently
-considered to be relevant to adolescent emotion regulation.
-Traditional narrative literature reviews have been shown to be marred by reliance on (small) convenience samples of the literature, confirmation bias,
+As a result, there is a lack of unifying theory,
+and intrinsic limitations of narrative reviews prohibit comprehensive coverage of the vast but diffuse literature [@bussTheoriesEmotionalDevelopment2019].
+
+The present systematic review seeks to overcome these limitations by adopting a novel method:
+the text mining based systematic review.
+We set out to map the constructs associated with adolescent emotion regulation based on a systematic review of the empirical literature.
+Traditional narrative literature reviews have been shown to be marred by reliance on small convenience samples of the literature, confirmation bias,
 and an undue emphasis on positive results [@littellEvidencebasedBiasedQuality2008]. 
@@
 [@sawyerAgeAdolescence2018].
-
 <!-- From Barriola:
@@
 (Spear 2000) including autonomous emotional regulation-->
-
 Adolescence is increasingly seen as a developmentally sensitive period for
@@
 development of motivational-emotional and regulatory brain circuits gives rise
-to a maturity gap, where youngsters pursue new experiences in life and love,
-without being fully prepared to cope with the emotional outcomes
-[@croneUnderstandingAdolescencePeriod2012].
+to a maturity gap [@croneUnderstandingAdolescencePeriod2012]. 
+This leads youngsters to pursue new experiences in life and love,
+without being fully prepared to cope with the emotional outcomes.
 Due to these coalescing changes,
@@
 
-The results of our text mining analysis of the empirical literature on adolescents' emotion regulation will be best understood against the backdrop of the existing theoretical landscape.
-We distinguish the topics covered in this theoretical review visually to highlight new issues
-in the subsequent text mining analysis.
-This allows us to see in what respects the text mining analysis reflects existing theory,
-and in what respects it complements it.
-We provide only a summary theoretical review here, as other recent publications offer more detailed reviews of theories of emotional development [@bussTheoriesEmotionalDevelopment2019] and emotion regulation in adolescence [@riedigerEmotionRegulationAdolescence2014].
-These prior reviews remark that,
-although many theories are *relevant* for emotion regulation development in adolescence,
-few have addressed this topic directly.
-Fewer theories still have comprehensively addressed important predictors of development in this life stage,
-and none directly guide contemporary research in the field [see @bussTheoriesEmotionalDevelopment2019].
-There is thus a need for more integrative theory formation [see @riedigerEmotionRegulationAdolescence2014].
-Inductive analysis of the empirical literature may constitute a first step to this end.
+The results of our text mining analysis of the empirical literature are best understood against a backdrop of the existing theoretical landscape.
+We therefore provide a summary theoretical review.
+Other recent publications offer more detailed reviews of theories of emotional development [@bussTheoriesEmotionalDevelopment2019] and emotion regulation in adolescence [@riedigerEmotionRegulationAdolescence2014].
+The correlates of emotion regulation difficulties discussed in the theoretical review below
+are visually summarized in the left panel of Figure \@ref(fig:baseline)^[Based on an author-curated list of keywords, caterogized using the dictionary method introduced in Analysis 1.].
+
+```{r baseline, warning=FALSE, eval = TRUE, out.width = "100%", fig.cap="Correlates of emotion regulation difficulties according to theory (left panel) and narrative reviews (right panel).
+Transparent circles indicate constructs also represented in the theory."}
+knitr::include_graphics("baseline_network.png") 
+#fig_svg <- cowplot::ggdraw()+cowplot::draw_image("s1_varimp.svg")
+#plot(fig_svg)
+keyw <- function(x){
+  cat(x)
+}
+```
 
 Among the oldest relevant theories of adolescents' emotional development is Hall's notion of "storm and stress" [see
-@arnettAdolescentStormStress1999]. It describes how hormonal changes diminish
-self-control and increase reactivity, leading to difficulties in emotion
-regulation, conflict with parents, and risky behavior.
+@arnettAdolescentStormStress1999]. It describes how `r keyw("hormonal")` changes diminish
+`r keyw("self-control")` and increase `r keyw("reactivity")`, leading to difficulties in emotion
+regulation, `r keyw("conflict with parents")`, and `r keyw("risky behavior")`.
 In modern theories, this notion of diminished self-control and increased emotional reactivity has been retained - although it is now considered to be a normative change that facilitates emotional maturation
@@
 Sroufe argues that, as children grow older,
-their increasing self-regulatory abilities
-drive a transition from external emotion regulation by primary caregivers
+their increasing `r keyw("self-regulatory")` abilities
+drive a transition from external emotion regulation by `r keyw("primary caregivers")`
 towards autonomous emotion regulation. This theory focuses on two drivers of
-development: social and cognitive influences. Social influences mainly occur
-through parental co-regulation, parenting behaviors, and parent-child
-attachment. Cognitive influences occur through the development of the central
-nervous system (CNS), cognition, and self-regulation.
-
-This emphasis on social influences and neurocognitive development is reflected in many theories.
+development: `r keyw("social")` and `r keyw("cognitive influences")`. Social influences mainly occur
+through `r keyw("parental co-regulation")`, `r keyw("parenting behaviors")`, and parent-child
+`r keyw("attachment")`. Cognitive influences occur through the development of the `r keyw("central
+nervous system")` (CNS), `r keyw("cognition")`, and `r keyw("self-regulation")`.
+
+This emphasis on social influences and `r keyw("neurocognitive development")` is reflected in many theories.
 Some of these focus primarily on neurocognitive development.
-For example, polyvagal theory closely links emotional experience
+For example, `r keyw("polyvagal theory")` closely links `r keyw("emotional experience")`
 - and regulation - to autonomous nervous system functioning
@@
 A more recent neurocognitive theory relevant to adolescents' emotion regulation development is Crone
-and Dahl's model of social-affective engagement and goal flexibility
+and Dahl's model of social-affective engagement and `r keyw("goal flexibility")`
 [@croneUnderstandingAdolescencePeriod2012]. Like other authors 
@@
 Crone and Dahl argue that the developmental
-asymmetry between motivational and inhibitory brain circuits gives rise to a
+asymmetry between `r keyw("motivational")` and inhibitory `r keyw("brain")` circuits gives rise to a
 "maturity gap" in middle adolescence. 
@@
 They argue that adolescents' cognitive engagement is dynamically responsive to
-social and motivational goal salience. This flexibility, on the one hand,
+social and motivational `r keyw("goal salience")`. This flexibility, on the one hand,
 prepares adolescents to effectively engage cognitive systems in novel
@@
 abilities. On the other hand, it places them at risk to act impulsively in
-pursuit of peer approval. In terms of explanans,
+pursuit of `r keyw("peer approval")`. In terms of explanans,
 this theory focuses primarily on cognitive factors
@@
 Other theories emphasize socialization to a greater extent.
-One such theory is Morris' tripartite model, which focuses specifically on parents' role in emotion regulation development [-@morrisRoleFamilyContext2007].
+One such theory is Morris' tripartite model, which focuses specifically on `r keyw("parents")`' role in emotion regulation development [-@morrisRoleFamilyContext2007].
 It describes three pathways through which parents shape emotion regulation
-development: Through observation and modeling, parenting practices, and the
-emotional family climate, which in turn involves attachment and marital
-relationship quality. Morris and colleagues also emphasize the relevance of
-fathers and siblings, and others have adapted the tripartite model to describe
+development: Through observation and `r keyw("modeling")`, `r keyw("parenting practices")`, and the
+emotional `r keyw("family climate")`, which in turn involves attachment and `r keyw("marital
+relationship")` quality. Morris and colleagues emphasize the relevance of `r keyw("mothers")`, 
+`r keyw("fathers")`, and siblings.
+Others have adapted the tripartite model to describe
 the role of peers in adolescents' emotion regulation development
@@
 internalization model of emotional development. 
-Unique aspects emphasized in this theory are the interplay between emotion and communication,
-and the internalization of the cultural symbolic function of emotion.
-These theories explain socialization in great detail,
-but one potential limitation is that tey are not embedded in a larger unifying framework.
+Unique aspects emphasized in this theory are the interplay between emotion and `r keyw("communication")`,
+and the internalization of the `r keyw("cultural")` symbolic function of emotion.
+These theories explain the process of socialization in great detail,
+but one potential limitation is that they are not embedded in a larger unifying framework.
 <!--Like Sroufe, Holodynski describes an age graded transition from
@@
 process of emotion regulation from eliciting cue to ultimate response.
-According to Gross, individuals use strategies to modulate the different stages of this process,
-consciously or otherwise. Culture plays a role too, as the effectiveness, desireability, and consequences of different strategies depend on the social context [see
+According to Gross, individuals use `r keyw("strategies")` to modulate the different stages of this process,
+consciously or otherwise. `r keyw("Culture")` plays a role too, as the effectiveness, desireability, and consequences of different strategies depend on the social context [see
 @bariolaChildAdolescentEmotion2011]. Similar to Gross' theory, the social
@@
 to emotional difficulties, we should mention two theories widely invoked to frame research on developmental influences: Bronfenbrenner's bioecological model, and Sameroff's
-transactional model. Bronfenbrenner's model
-[@bronfenbrennerBioecologicalModelHuman2007] describes how the environment
+transactional model.
+Bronfenbrenner's model
+[@bronfenbrennerBioecologicalModelHuman2007] describes how the `r keyw("environment")`
 shapes individual development. Each individual is imbued with certain
-biological predispositions, and develops over time, in interaction with
+`r keyw("biological")` predispositions, and develops over time, in interaction with
 contextual influences. These influences range from the microsystem, composed of
 those people close to the individual, to the macrosystem, consisting of
-indirect political and economic influences, to the exosystem, consisting of
+indirect `r keyw("political")` and `r keyw("economic")` influences, to the exosystem, consisting of
 cultural norms and values. Sameroff's model is somewhat compatible with the
@@
 structural factors indirectly shaping development, like socio-economic status,
-schools, and the community (macro- and exosystem). With increasing age, distal
+`r keyw("schools")`, and the `r keyw("community")` (macro- and exosystem). With increasing age, distal
 influences gradually gain ground on proximal influences.
 These theories are broad enough to contextualize any developmental study,
-but limited by a lack of specificity, which hampers their utility in generating hypotheses.
+but lack specificity, which curtails their utility in generating hypotheses.
 <!-- RK: What do you take from these broad perspectives for your RQ?-->
@@
 
+<!--
+Note that the left panel of Figure \@ref(fig:baseline) visually summarizes the correlates of emotion regulation difficulties (labeled: *Dysregulation*) according to our theoretical review.
+The left panel of Figure \@ref(fig:baseline) summarizes key constructs covered by the theories reviewed above. 
+In the subsequent text mining analysis, we will distinguish the topics covered in this theoretical review visually to highlight unique contributions of our approach.
+This allows us to see in what respects the text mining analysis reflects existing theory,
+and in what respects it complements it.-->
+
 ### Shortcomings of existing theory
 
-<!--Consider splitting this up and putting the shortcomings next to the existing theories-->
-Despite the abundance of relevant theory,
-the existing literature has several limitations when the goals is to
-identify which
-risk factors render some adolescents more susceptible
-to maladaptive emotional development than others.
-One crucial shortcoming is that most theories lack of explicit attention to the life stage of adolescence.
-It is questionable whether theories focused on different ages can be generalized to adolescents,
-because this stage differs qualitatively from infancy, childhood, and adulthood [@bariolaChildAdolescentEmotion2011].
-A related limitation is that many relevant theories lack
-an explicit developmental component <!--, and thus lack a well-substantiated
-understanding of developmental processes--> [see
+Despite the abundance of theory *relevant* to emotion regulation in adolescence,
+the theoretical literature has several limitations.
+First, few theories have explicitly addressed the life stage of adolescence. This life stage differs qualitatively from infancy, childhood, and adulthood [@bariolaChildAdolescentEmotion2011].
+It is therefore questionable whether more general theories, or those focused on different age groups, can be generalized to adolescents.
+<!--Relatedly, many relevant theories lack an explicit developmental component, which renders them and thus lack a well-substantiated
+understanding of developmental processes[see
 @bussTheoriesEmotionalDevelopment2019;
-@croneUnderstandingAdolescencePeriod2012]. 
-Perhaps most importantly, however, these theories
-vary widely in scope: Some are broad but somewhat non-specific, such as the biopsychosocial models of Bronfenbrenner and Sameroff, and others describe a specific phenomenon, but lack a broader perspective.
+@croneUnderstandingAdolescencePeriod2012]. -->
+Furthermore, few theories have comprehensively addressed important predictors of development in this life stage,
+and none directly guide contemporary research in the field [see @bussTheoriesEmotionalDevelopment2019; @riedigerEmotionRegulationAdolescence2014].
+Finally, available theories vary widely in scope:
+Some are broad but somewhat non-specific, and others describe a specific phenomenon in detail,
+but lack a broader perspective.
 It would be beneficial to bridge these levels of analysis.
-Based on these shortcomings,
-there appears to be a need for more theory generation,
-in order to provide a unified framework that could guide future empirical work.
+In sum, there is a need for more integrative theory formation,
+in order to provide a unified framework that could guide future empirical work.<!--[see @riedigerEmotionRegulationAdolescence2014].
+Inductive analysis of the empirical literature may constitute a first step to this end.-->
 <!--Such a theory should focus on -->
 The present study lays the groundwork for such theory development,
-by providing an inductive conceptual
-review of the field.
-Concepts covered in the preceding theoretical review will be tagged in the text mining analysis,
-to highlight the contribution of the inductive approach.
+by providing a text-mining based inductive systematic review of the field.
 
@@
 
-## Bottom-up insights from narrative reviews
-
-Whereas theory provides a top-down understanding of an area of research,
-literature reviews can provide a bottom-up, inductive understanding. Given the
-noted absence of a single overarching theory, reviews might provide additional
+## Prior narrative reviews
+
+Whereas theory provides a top-down frame of reference for understanding a phenomenon,
+literature reviews can provide a bottom-up, inductive understanding.
+Given the noted absence of a single overarching theory, reviews might provide additional
 insight into factors considered relevant in the etiology of adolescents'
-emotion regulation competencies. For example, a review by
+emotion regulation competencies. 
+Innovative text mining methods are promising in this respect, because they can comprehensively review the available literature.
+Narrative reviews, however, constitute the status quo.
+We will therefore examine how two excellent narrative reviews on emotion regulation in adolescence complement the aforementioned theoretical literature [@coe-odessEmergentEmotionsAdolescence2019; @bariolaChildAdolescentEmotion2011].
+The right panel of Figure \@ref(fig:baseline) visually distinguishes constructs  uniquely covered by these narrative reviews,
+relative to the issues also addressed in the theoretical literature (left panel).
+
+<!--
+Note that the left panel of Figure \@ref(fig:baseline) visually summarizes the correlates of emotion regulation difficulties (labeled: *Dysregulation*) according to our theoretical review.
+The left panel of Figure \@ref(fig:baseline) summarizes key constructs covered by the theories reviewed above. 
+In the subsequent text mining analysis, we will distinguish the topics covered in this theoretical review visually to highlight unique contributions of our approach.
+This allows us to see in what respects the text mining analysis reflects existing theory,
+and in what respects it complements it.-->
+
+The seminal review by
 @bariolaChildAdolescentEmotion2011 addresses individual psychological factors
@@
 childhood.
-They further argued that the role of fathers in emotion socialization warrants further scrutiny - a topic that is now receiving more attention [@vanlissaRoleFathersMothers2019;
+They further argued that the role of fathers in emotion socialization warrants further scrutiny - a topic that is now receiving more attention [e.g., see @vanlissaRoleFathersMothers2019;
 @vanlissaMothersFathersQuantitative2020].
 
-Another review by @coe-odessEmergentEmotionsAdolescence2019 offers a nuanced
+A more recent review by @coe-odessEmergentEmotionsAdolescence2019 offers a nuanced
 discussion of several issues that complement prior publications in this field.
@@
 
-There are notable parallels between the relevant factors highlighted by these
+As can be seen in Figure \@ref(fig:baseline), 
+there are notable parallels between the relevant factors highlighted by these
 narrative reviews, and the aforementioned theoretical literature.
@@
 attention in theoretical work.
-These include individual differences, both at the biological and psychological level, including genetic predisposition, hormones, pubertal onset, gender, sexuality, temperament, identity, empathy, and stress.
-Proximal influences not covered in theory include the role of media, norms, and social status.
-Thus, reviews of the empirical literature can contribute additional insight into key factors in adolescents' emotion regulation development.
-One remaining limitation is that all reviews in this field have been unstructured narrative reviews.
-The present publication seeks
-to complement preceding work by conducting a comprehensive empirical
-literature review, and mapping the factors associated with adolescent emotion
-regulation using text mining.
+These include specific individual differences at the biological and psychological level, including genetic predisposition, hormones, pubertal onset, gender, sexuality, temperament, identity, empathy, and stress.
+Further introduced are proximal influences, including the role of media, norms, and social status.
+This illustrates that reviews of the empirical literature can contribute additional insight into key factors in adolescents' emotion regulation development.
+However, an important remaining limitation is that all reviews in this field have been unstructured narrative reviews, which are known to be limited in scope and biased [@littellEvidencebasedBiasedQuality2008].
+We seek to complement preceding work by using text mining to conduct a more comprehensive empirical
+literature review, and map the factors associated with adolescent emotion
+regulation.
 
@@
 phenomenon; a proto-theoretical device that describes relationships between
-constructs relevant to the theory [see @alaviAligningTheoryMethodology2018]. It is a precursor to a more
+constructs relevant to the theory [see @alaviAligningTheoryMethodology2018].
+It is a precursor to a more
 explicit theory of the phenomenon. The present paper uses an inductive approach
@@
 
-All searches were conducted on Web of Science. The search strategy was based on
+All searches were conducted on Web of Science,
+the most comprehensive database for which we had permissions for exporting keywords and abstracts.
+The search strategy was based on
 procedures described by Staaks [@staaksSystematicReviewSearch]. First, we
@@
 search string to retrieve these articles from Web of Science. The search was
-overly inclusive, returning 29 records. As these were all highly relevant, we
-updated the reference set to include all 29 results. Next, we tested our search
-string, which consisted of synonyms of emotion regulation and adolescence: <!--
+overly inclusive, returning 29 records.
+As these were all highly relevant, we
+updated the reference set to include all 29 results.
+Next, we tested our search string, which consisted of synonyms of emotion regulation and adolescence: <!--
 ### Reference set Our reference set is documented in `reference_set.bib`. -->
@@
 This string returned 6653 results, and matched 25 of the 29 records in the
-reference set. Three search terms could be added to match all 29 reference set
-items. The terms `"emotio* socialization" OR "emotio* processes"`, as synonyms
-of emotion regulation, added 191 new hits. However, most of these did not meet the inclusion criteria used for screening, as explained below.
-The term `"development*"`, as synonym
-of adolescence, added 3628 new hits, many of which were not focused on the age
-range of adolescence. We thus deemed these terms to be overly inclusive, and
+reference set. To match all 29 reference set items,
+three additional terms would have to be added to the search string.
+Adding the terms `"emotio* socialization" OR "emotio* processes"`, as synonyms for emotion regulation,
+would result in 191 more hits, most of which did not meet the inclusion criteria used for screening, as explained below.
+Adding the term `"development*"`, as synonym of adolescence, added 3628 new hits,
+many of which were not focused on adolescence.
+We thus deemed these terms to be overly inclusive, and
 proceeded with the original search string above.
@@
 Thus, for example, an article reviewing the role of hormonal changes in emotional adjustment throughout the entire life course, including adolescence, would be deemed relevant.
-Screening was initially conducted in Rayyan QRCI [@Ouzzani2016].
+Preliminary screening was conducted in Rayyan QRCI [@Ouzzani2016].
 Papers were sorted using Rayyan's ranking algorithm.
@@
 After coding `r sum(screen$rayyan == "True")+sum(screen$rayyan == "False")` papers, screening continued in ASReview - a free, open source alternative to Rayyan QRCI [@van_de_schoot_rens_2020_3828293].
-This program uses text mining and active learning to build a customizable machine learning model for article inclusion.
+This program uses active learning to build a customizable machine learning model for article inclusion.
 We used a naive Bayes model, and focused on exclusion of irrelevant papers.
@@
 
-```{r, warning=FALSE, message=FALSE}
-source("study1.R")
-if(run_everything | !file.exists("Study1_lda_dims.txt")) source("LDA_analysis.R")
-lda_dims <- read_yaml("Study1_lda_dims.txt")
-dtm_top <- read_yaml("study1_dtm_top.yml")
-```
+```{r cache=FALSE}
+knitr::read_chunk("study1.R")
+```
+```{r study1chunk}
+```
+
 The corpus for this first analysis consisted of the author-provided keywords for the selected articles.
@@
 and removing records with no (remaining) keywords,
-the resulting corpus consisted of `r number_docs_words[1]` documents with `r number_docs_words[2]` unique words.
+the resulting corpus consisted of `r number_docs_words[1]` documents with `r number_docs_words[2]` unique terms.
 <!--As term-document frequency is irrelevant in the context of keywords (i.e., keywords should not occur twice within the same document, except when two synonyms have been recoded using the dictionary),
@@
 <!-- it might be useful to insert a sentence or two when you are using a method many readers are not familiar with, just to explain the utility of the chose method (what it does/doesn't do potentially as compared to other options)-->
-To assess the homogeneity of the corpus, we conducted topic modeling using latent dirichlet allocation [@bleiLatentDirichletAllocation2003].
-For this analysis, we used the term frequency/inverse document frequency (TF-IDF) to select terms
+One important step before reviewing the literature is to examine heterogeneity in the corpus of collected texts.
+For example, it would be useful to know whether there is a clear divide between psychiatric and developmental texts.
+To empirically test for heterogeneity, we conducted topic modeling using latent dirichlet allocation [@bleiLatentDirichletAllocation2003].
+This is a clustering method suitable to high-dimensional sparse feature matrices.
+In this case, the features are author keywords.
+We used the term frequency/inverse document frequency (TF-IDF) to select terms
 used frequently in a document, but not used frequently in the corpus,
@@
 Congruently, all entropies were near-zero, which means that the posterior document/topic probabilities were effectively uniformly distributed.
-Thus, no interpretable subcorpora could be identified,
+Thus, no subcorpora could be identified,
 and we proceed with an analysis of the whole sample. <!-- Probably because each set of keywords has only a few indicators. -->
@@
 and retained those exceeding the $97.5^{th}$ percentile.
-This resulted in `r dim(dtm_top)[2]` terms, which occurred in `r dim(dtm_top)[1]` documents.
-To illustrate what issues are covered in this body of literature, the selected terms are displayed in Figure \@ref(fig:study1varimp), on a logarithmic scale to reduce the skew of the negative binomial distribution.<!--;
-word size represents frequency of occurrence (squared to reduce the skew of the negative binomial distribution).-->
-
-```{r study1wordcloud, warning=FALSE, eval = FALSE, out.width = "100%", fig.cap="Wordcloud of terms selected for Study 1. More common words are centered and printed in larger font."}
-knitr::include_graphics("study1_wordcloud.svg")
-```
-
-```{r study1varimp, warning=FALSE, eval = TRUE, out.width = "100%", fig.cap="Document frequency of terms selected for Study 1."}
+This resulted in `r dtm_top[2]` terms, which occurred in `r dtm_top[1]` documents.
+To illustrate what issues are covered in this body of literature, the selected terms are displayed in Figure \@ref(fig:study1varimp), on a logarithmic scale to reduce the skew of the negative binomial distribution.
+
+```{r study1varimp, warning=FALSE, eval = TRUE, out.width = "100%", fig.cap="Document frequency of terms selected for Study 1.
+Dashed lines and transparent circles indicate constructs also represented in the theory (cf Figure 1)."}
 knitr::include_graphics("s1_varimp.png") 
@@
 #plot(fig_svg)
+
 ```
@@
 Based on our theoretical review, each of the selected terms was coded as being either a putative 'Cause', 'Outcome', 'Protective factor', or 'Indicator' (a closely related construct) of emotion dysregulation.
-We stress that this is a rudimentary and simplistic classification; many of these associations are likely to be bidirectional [e.g., emotion dysregulation is known to be both a cause and consequence of conflict with parents, @vanlissaCostEmpathyParentadolescent2017].
+We stress that this is a subjective and rudimentary classification,
+intended only to stimulate further reflection on the role of each construct.
+We acknowledge that many of these associations are likely to be bidirectional [e.g., emotion dysregulation is known to be both a cause and consequence of conflict with parents, @vanlissaCostEmpathyParentadolescent2017].
 Next, we computed a term co-occurrence matrix,
@@
 and retaining co-occurrences exceeding the $97.5^{th}$ percentile.
-Figure \@ref(fig:study1network) displays the pruned term cooccurrence matrix as a force directed graph.
-<!--The classification is presented in Table \@ref(tab:study1table1).
-
-r study1table1, results = "asis"}
-df <- tapply(pretty_words(categ$name), categ$category, function(i){paste(strwrap(paste(i, collapse = ", "), width = 90), collapse = "\\\\")})
-df <- data.frame(Category = names(df), Terms = df, row.names = NULL)
-apa_table(df, escape = F)
--->
+Figure \@ref(fig:study1network) displays the term cooccurrence matrix as a force directed graph.
 
 ```{r study1network, warning=FALSE, out.width = "100%", fig.cap="Force directed graph for Study 1 co-occurrence analysis.
-Vertex size represents term frequency; dashed lines for co-occurrences not involving dysregulation.
-Two different layouts are presented to aid interpretation."}
+Two layouts are presented to aid interpretation.
+Size of nodes and edges represents word/co-occurrence frequency.
+Dashed lines represent links not involving dysregulation.
+Transparent circles indicate constructs also represented in the theory (cf Figure 1)."}
 #knitr::include_graphics("study1_network1.svg")
@@
 
-```{r}
-notingraph <- names(topterms)[!names(topterms) %in% unique(c(edg$term1, edg$term2))]
-notingraph <- categ[categ$name %in% notingraph, ]
-notingraph <- tapply(tolower(pretty_words(notingraph$name)), notingraph$category, function(i){paste0(paste(paste0("*", i[-length(i)], "*"), collapse = ", "), ", and *", i[length(i)], "*")})
-```
-
 Based on term document frequency (Figure \@ref(fig:study1varimp)), it is clear that emotion dysregulation and its mental health-related outcomes are foremost among the common terms in the corpus. 
 Other frequent terms reflect important themes discussed in the theoretical review of the literature;
-for instance, the term *neural*, *parenting*, and *stress* correspond to major themes discussed by  @coe-odessEmergentEmotionsAdolescence2019:
+for instance, the terms *neural*, *parenting*, and *stress* correspond to themes discussed by  @coe-odessEmergentEmotionsAdolescence2019:
 Neurocognitive development, the role of the parents, and adolescents' increased stress response.
@@
 This first analysis used author keywords to map common topics in the literature pertaining to adolescents' emotion dysregulation.
-The results reflected some of the constructs commonly accepted as relevant in theoretical literature and empirical reviews.
-However, the analysis also revealed important areas less prominently featured in narrative reviews. 
-This illustrates how inductive reviews may complement existing theory and narrative reviews, and can reveal blindspots.<!-- SH: this point/advantage needs to feature more prominently in the introduction!-->
-
-Connections among topics were relatively sparse: Many constructs were only related to emotion regulation,
+The results reflected some of the constructs commonly accepted as relevant in theoretical literature and empirical reviews - particularly those pertaining to neurodevelopment and socialization.
+The most frequently occurring words were classified as potential outcomes of emotion regulation difficulties, and revealed a theme related to mental health.
+This validates the notion that adolescent emotion regulation is implicated in a range of mental health problems, which underlines the importance of this area of research.
+
+In addition to the themes addressed in the theoretical introduction,
+several novel themes emerge from the terms newly identified in this analysis.
+Developmental disorders constitute such a theme, as ADHD/CD and autism are ranked highly.
+Another theme is the role of physical health (sic), also reflected in terms like sleep, sports, and disability status.
+External stressors are another important theme, reflected in bullying, stress, PTSD, abuse, violence, life events, historic events (e.g., earthquakes, war), and parenting stress.
+Structural disadvantage is certainly a factor overlooked in existing theory,
+and is reflected in minority status, disability status, socio-economic status, adoption status, sexual diversity, and the adorementioned developmental disorders, as neuroatypical individuals may also experience such disadvantage.
+These insights illustrate how inductive reviews may complement existing theory and narrative reviews, and can reveal blindspots.<!-- SH: this point/advantage needs to feature more prominently in the introduction!-->
+
+In terms of the co-occurrence network, connections among topics were notably sparse.
+Many constructs were only related to emotion regulation,
 and there were relatively few interconnections between elements.
 This observation substantiates the prior claim that this literature is somewhat fragmented [@bussTheoriesEmotionalDevelopment2019]. 
-<!--One exception is an emergent cluster of interrelated constructs pertaining to mental health, anxiety, depression, and externalizing symptoms - the frequently occurring mental health-related outcomes.-->
-
 This sparse property of the network explains, in part,
@@
 
-Many of these excluded constructs represent active ongoing areas of research - such as the role of *fathers* [@vanlissaRoleFathersMothers2019], *identity* [@campbellFriendsEducationIdentity2019], *friendship* and *social support* [@wangBidirectionalEffectsExpressive2020], *autonomy* [@vrolijkLongitudinalLinkagesFatherunderreview; @brenningPerceivedMaternalAutonomy2015], *sexual risk* [@brownDepressiveSymptomsPredictor2006], and *loneliness* [@spithovenItAllTheir2017] in adolescents' emotional development.
+Many of these excluded constructs represent active ongoing areas of research, including research on *fathers* [@vanlissaRoleFathersMothers2019], *identity* [@campbellFriendsEducationIdentity2019], *friendship* and *social support* [@wangBidirectionalEffectsExpressive2020], *autonomy* [@vrolijkLongitudinalLinkagesFatherunderreview; @brenningPerceivedMaternalAutonomy2015], *sexual risk* [@brownDepressiveSymptomsPredictor2006], and *loneliness* [@spithovenItAllTheir2017].
 The fact that these constructs are absent from the graph does not suggest that they are unimportant.
-Rather, it indicates that they are not yet well-integrated in the literature,
+Rather, it indicates that they are not yet well-integrated in the broader literature on adolescents' emotion regulation,
 and are therefore prime candidates for future research.<!-- RK: Or could they also suggest that they were relevant in the past, but not any longer?
-Might it be important to run sensitivity analyses by publication year?-->
+Might it be important to run sensitivity analyses by publication year?
 One recommendation for future research might be to study such important but unembedded constructs
 in conjunction with other more well-established constructs,
-as such an approach might help fill gaps in existing knowledge.
+as such an approach might help fill gaps in existing knowledge.-->
 
@@
 To assess the homogeneity of the corpus of abstracts,
-we again conducted topic modeling [@bleiLatentDirichletAllocation2003],
-with features selected based on TF-IDF.
-This resulted in a dataset consisting of `r lda_dims_2[1]` documents and `r lda_dims_2[2]` terms.
-We considered a range from 2-20 topics, evaluating fit based on the BIC, and interpretability based on the entropy of the posterior document/topic probabilities.
+we again conducted topic modeling with features selected based on TF-IDF, following the same procedure as in Analysis 1 [@bleiLatentDirichletAllocation2003].
+The dataset consisted of `r lda_dims_2[1]` documents and `r lda_dims_2[2]` terms.
 As before, the BICs followed a near-perfect linearly increasing trend, and all entropies were near-zero.
@@
 
-```{r study2wordcloud, eval = FALSE, out.width = "100%", fig.cap="Wordcloud of terms selected for Study 2. More common words are centered and printed in larger font."}
-knitr::include_graphics("study2_wordcloud.svg")
-```
-
-```{r study2varimp, eval = TRUE, out.width = "100%", fig.cap="Document frequency of terms selected for Study 2."}
+```{r study2varimp, eval = TRUE, out.width = "100%", fig.cap="Document frequency of terms selected for Study 2.
+Dashed lines and transparent circles indicate constructs also represented in the theory (cf Figure 1)."}
 knitr::include_graphics("s2_varimp.png") 
@@
 Figure \@ref(fig:study2network) displays the resulting matrix as a force directed graph.
-<!--The classification is presented in Table \@ref(tab:study1table1).
-
-r study1table1, results = "asis"}
-df <- tapply(pretty_words(categ$name), categ$category, function(i){paste(strwrap(paste(i, collapse = ", "), width = 90), collapse = "\\\\")})
-df <- data.frame(Category = names(df), Terms = df, row.names = NULL)
-apa_table(df, escape = F)
--->
 
 ```{r study2network, out.width = "100%", fig.cap="Force directed graph for Study 2 co-occurrence analysis.
-Vertex size represents term frequency; dashed lines for co-occurrences not involving dysregulation.
-Two different layouts are presented to aid interpretation."}
+Two layouts are presented to aid interpretation.
+Size of nodes and edges represents word/co-occurrence frequency.
+Dashed lines represent links not involving dysregulation.
+Transparent circles indicate constructs also represented in the theory (cf Figure 1)."}
 #knitr::include_graphics("study2_network1.svg")
@@
 ```{r}
-tt <- sort(topterms, decreasing = TRUE)
-notingraph <- names(tt)[!names(tt) %in% unique(c(edg$term1, edg$term2))]
-notingraph <- categ[categ$name %in% notingraph, ]
-notingraph <- tapply(tolower(pretty_words(notingraph$name)), notingraph$category, function(i){paste0(paste(paste0("*", i[-length(i)], "*"), collapse = ", "), ", and *", i[length(i)], "*")})
-```
-
-Based on term document frequency, it is clear that emotion dysregulation and mental health-related outcomes of emotion dysregulation are among the most common terms in the corpus of abstracts.
-The term "neural", again, occurred frequently, but other top terms were somewhat less predictable than those emerging in Analysis 1.
-The term "sex" is more frequent, and instead of "parenting", we now see "mothers" on top of the list.
-We see that "minority status", "substance use", "attachment","ptsd", and "bullying" are once more among the most frequent words.
+s1 <- read_yaml("s1_words.yml")
+s2 <- read_yaml("s2_words.yml")
+
+#length(unique(c(s1, s2)))
+
+oneintwo <- round(length(s1[s1 %in% s2])/length(s1)*100)
+twoinone <- round(length(s2[s2 %in% s1])/length(s2)*100)
+
+s1order <- data.frame(word = s1, order = 1:length(s1))
+s2order <- data.frame(word = s2, order = 1:length(s2))
+orders <- merge(s1order, s2order, by = "word", all = TRUE)
+orders[is.na(orders)] <- 999
+names(orders) <- c("word", "order1", "order2")
+orders$diff <- orders$order1-orders$order2
+orders <- orders[order(abs(orders$diff), decreasing = TRUE), ]
+```
+
+Based on term document frequency, it is clear that emotion dysregulation and its mental health-related outcomes are among the most common terms in the corpus of abstracts.
+The term *neural* again occurred frequently, but other top terms were somewhat less predictable than those emerging in Analysis 1.
+The term *sex* was more frequent than in Analysis 1, suggesting sex differences are regularly reported in Abstracts, even if they are not a main topic of the study.
+The term *parenting*, which ranked highly in the preceding keyword Analysis, was displaced by *mothers* amonst the top-ranking terms.
+This suggests that when the keyword *parenting* is used,
+the abstract will often reveal that this was operationalized in terms of mothering [as also noted by @pleckPaternalInvolvementRevised2004].
+
+There was substantial agreement between the findings of Analysis 1 and 2;
+$`r oneintwo`%$ of the most frequent terms identified in the author keywords (Analysis 1)
+were also present in the abstracts (Analysis 2),
+and conversely, $`r twoinone`%$ of the most frequent terms from Analysis 2 were present in Analysis 1.
+
+Several themes emerge from the terms newly identified in this analysis relative to the theoretical review.
+These themes bear considerable similarity to the results of Analysis 1.
+Developmental disorders and physical health are both recurring themes, but are ranked much lower in the present analysis.
+External stressors are another recurring theme, with indicators including PTSD, bullying, stress, abuse, historic events, and divorce.
+Finally, structural disadvantage recurs,
+as reflected in minority status and discrimination, disability status, socio-economic status, adoption status, sexual diversity, and the adorementioned developmental disorders.
+
+A new theme emerging from this analysis is addictive behavior, with highly ranked indicators *substance use* and *device use*.
+Another new theme pertains to identity and moral development, two topics with a common root in theory [@lapsleyMoralIdentityDevelopmental2015].
+This theme is also reflected by the terms *values* and *personality*.
+Finally, sexual development emerges as a theme. Aside from the high-ranking construct (biological) *sex*, this theme is reflected in the terms *puberty*, *sexual diversity*, and *romantic*.
+
+```{r, echo = FALSE}
+categ <- read.csv("study1_categorization.csv", stringsAsFactors = FALSE)
+connected <- cooc[which(rownames(cooc) == "dysregulation"), ]
+connected <- names(connected)[connected > 0]
+connected <- connected[connected %in% categ$name[categ$category == "Cause"]]
+```
 
@@
 and that many related terms are connected to this axis, but not always directly to
-dysregulation. Only the terms "neural", "mothers", "attachment" and "ptsd" are 
+dysregulation. Only the terms *neural*, *mothers*, *attachment* and *ptsd* are 
 connected directly to dysregulation.
 
-Again, some prevalent terms are entirely absent from Figure \@ref(fig:study2network), as they were not strongly related
-to any other terms in the main network. 
+Many prevalent terms were entirely absent from the co-occurrence network (Figure \@ref(fig:study2network)),
+as they were not strongly related to any other terms. 
 These terms, which are displayed in Figure \@ref(fig:study2varimp), include the potential causes `r notingraph["Cause"]`, the potential outcomes `r notingraph["Outcome"]`, and the potential protective factors `r notingraph["Protective"]`.
-
-```{r}
-s1 <- read_yaml("s1_words.yml")
-s2 <- read_yaml("s2_words.yml")
-
-#length(unique(c(s1, s2)))
-
-oneintwo <- round(length(s1[s1 %in% s2])/length(s1)*100)
-twoinone <- round(length(s2[s2 %in% s1])/length(s2)*100)
-
-```
-There was substantial agreement between the findings of Analysis 1 and 2;
-$`r oneintwo`%$ of the most frequent terms identified in the author keywords (Analysis 1)
-were also present in the frequent terms extracted from the abstracts using `textrank` (Analysis 2),
-and conversely, $`r twoinone`%$ of the most frequent terms from Analysis 2 were present in Analysis 1.
 
@@
 We observed a sparser network, with fewer selected terms.
-This might be explained by the unstructured format of abstracts,
-which likely introduces greater noise in the analysis.
+This is likely an artifact of the unstructured nature of abstracts,
+which introduces greater noise in the analysis.
 Thus, fewer terms will exceed the detection threshold.
@@
 
-The emergence of a "central axis" of dysregulation and mental health-related outcomes suggest that these phenomena are consistently studied together.
+The emergence of a "central axis" of dysregulation and mental health-related outcomes
+again suggest that these phenomena are consistently studied together.
 By contrast, the lack of interconnectivity among other related constructs
@@
 from the term co-occurrence graph.
-Finally, the substitution of "parenting" with "mothers" amonst the top-ranking terms 
-might suggest that parenting is commonly operationalized in terms of mothering [@pleckPaternalInvolvementRevised2004].
 
@@
 The present study conducted a systematic review of the literature,
-and performed bibliographic analysis to map factors currently
-considered to be relevant to adolescent emotion regulation in a nomological network.
+and performed a text-mining based systematic review to map constructs related to adolescent emotion regulation in a nomological network.
 The results of this inductive approach echoed many of the constructs considered
 relevant in the theoretical literature.
-It also revealed several constructs that have been underrepresented in theory,
-but nonetheless occur frequently in the empirical literature.<!--RK: But is that a bad thing? Can you please elaborate?-->
-The structure of the term co-occurrence networks revealed that most of the relevant constructs are connected
+This suggests that the text mining method can indeed be used to map relevant themes in the literature.
+Our analysis also revealed several themes that have been underrepresented in theories of adolescent emotion regulation,
+but nonetheless occur frequently in the empirical literature.
+These themes include developmental disorders, physical health, external stressors, structural disadvantage, addictive behavior, identity and moral development, and sexual development.
+
+It is important to identify such under-theorized areas of the literature because
+researchers typically rely on theoretical foundations when planning a study.
+By providing a conceptual overview of the empirical literature,
+the present study offers some preliminary guidance regarding potentially relevant topics to consider.
+An important direction for future research would be to formalize these inductive insights into a new overarching theory of adolescent emotion regulation.
+
+Additional insight can be gleaned from the structure of the co-occurrence graphs.
+First, both analyses revealed close connections between emotion regulation and mental health-related outcomes.
+This is consistent with the fact that emotion regulation is implicated in the etiology of a range of mental health problems [see @leeAdolescentMentalHealth2014].
+It further emphasizes the societal relevance of this field of research.
+Both analyses further revealed that most constructs were connected
 directly with emotion dysregulation or its mental health correlates,
-with relatively few interconnections amongst constructs.
-This echoes the sentiment by @bussTheoriesEmotionalDevelopment2019 that this
-literature is somewhat fragmented.
-The present systematic review takes a first step towards integrating this diffuse field.
-
-<!--CJ: Cut this here
-Our work represents one of the first efforts to map the literature on adolescents' emotion dysregulation [cf. @bariolaChildAdolescentEmotion2011; @coe-odessEmergentEmotionsAdolescence2019].
-Moreover, it is one of the first applications of inductive text mining methods in a systematic review.
-Traditional narrative literature reviews have been shown to be marred by reliance on (small) convenience samples of the literature, confirmation bias, and an undue emphasis on positive results [@littellEvidencebasedBiasedQuality2008].
-Text mining, by contrast, is uniquely suited to provide a comprehensive overview of the literature.
-It can cover vastly greater corpora than a human reader,
-and the process by which text mining gleans insights from the literature is less subjective, and more transparant and reproducible.
-The inherent "fairness" of text mining gives emerging themes in the literature a chance to come to the fore,
-where human readers might be inclined to structure their reading of the literature around established ideas.-->
+with few interconnections amongst constructs.
+This sparse property of the networks echoes the sentiment by @bussTheoriesEmotionalDevelopment2019
+that the literature is somewhat fragmented.
+By conducting a comprehensive review using a somewhat objective method (relative to narrative reviews),
+the present study takes a first step towards integrating this diffuse field.
+An important future direction for research might be to jointly investigate disconnected constructs, as the lack of connections in the graph indicates a potential knowledge vacuum.
+
+Our work represents one of the first efforts to comprehensively map the literature on adolescents' emotion dysregulation [cf.
+@bariolaChildAdolescentEmotion2011; @coe-odessEmergentEmotionsAdolescence2019].
+It is also one of the first applications of inductive text mining methods in a systematic review.
+Text mining reviews offer some potential advantages when compared to narrative literature reviews [@littellEvidencebasedBiasedQuality2008]:
+They can cover vastly greater corpora than a human reader,
+and follow a somewhat more objective, transparant, and reproducible procedure.
+As such, text mining reviews offer an interesting perspective that complements theory and narrative reviews.
 
 Of course, the present study also has limitations.
-One such limitation is the fact that the text mining techniques used here
-are not able to extract *meaning* from the literature in the way a sentient reader would.
-This limitation is best addressed by using the output of our text mining analysis as a starting point for further inductive thought,
-or a more in-depth reading of a subset of the reviewed literature.
-Relatedly, our methods do not capture the nature of the relationship between co-occurring terms.
+One key limitation is that the text mining techniques used here
+are not able to extract *meaning* from the literature in the way a sentient reader would, an cannot substantively interpret connections between constructs.
+This limitation is best addressed by considering the output of our text mining analysis as a starting point for further inductive thought or a more in-depth reading of a particular subset of the literature.
+Throughout this paper, we have offered our interpretation of the results - but we also encourage readers to reflect on the objective results presented here (i.e.: which terms are common, and how these terms are connected), and use these results as impetus for independent inductive reflection, and inspiration for future deductive research.
+A related limitation is that our methods do not capture the nature of the relationship between co-occurring terms.
 Instead, we manually classified terms as potential causes, outcomes, protective factors, or indicators based on domain knowledge.
-It is worth noting that efforts are underway to develop unsupervised algorithms capable of distilling causal links from bodies of scientific abstracts [@anExtractingCausalRelations2019].
-Applying such methods to the present corpus might substantially advance theory formation.
+Efforts are currently underway to develop unsupervised algorithms capable of distilling causal links from bodies of scientific abstracts [@anExtractingCausalRelations2019].
+Future research might substantially advance theory formation by applying such methods to the present corpus.
 <!--For example, a human reader would understand that the influence of mothers and fathers both
@@
 covering both familiar ground, and charting unknown territories.
-Our results suggested that several key constructs are currently underrepresented in theory,
+Our results suggested that several key themes are currently underrepresented in theory,
 and that the empirical literature is somewhat fragmented by sub-topic.
@@
 which might represent emerging themes that would benefit from further research [including, for example, the role of fathers @vanlissaMothersFathersQuantitative2020].
-Most importantly, given the lack of an overarching theory tailored specifically to adolescent emotion dysregulation,
-our nomological networks might serve as a starting point for theory development,
-with the aim of integrating the present inductive insights within the framework of existing relevant theory.
+One recommendation for future research might be to study such important but unembedded constructs
+in conjunction with other more well-established constructs,
+to bridge gaps in existing knowledge.
+Several authors have commented on the lack of an overarching theory tailored specifically to adolescent emotion dysregulation.
+The present work might serve as a starting point for future theory development,
+with the aim of incorporating themes from the empirical literature within the framework of existing relevant theory.
 

### 2020-12-16 baseline.R

@@ -11,7 +11,8 @@ library(Matrix)
 library(ggplot2)
 library(yaml)
 source("word_functions.R")
-run_everything = TRUE
+source("circle2.R")
+run_everything = FALSE
 dict <- read_yaml("yaml_dict.txt")
 ## Look at POS tags?
 if(run_everything){
@@ -22,12 +23,13 @@ if(run_everything){
   # Categorize words
   res_cat <- cat_words(df$word, dict, handle_dups = "all")
   df$cat <- res_cat$words
+  df <- df[!duplicated(df$cat), ]
   if(!is.null(res_cat[["unmatched"]])){
     df <- df[!df$cat %in% names(res_cat$unmatched), ]
   }
   
   baseline_cat <- df
-  baseline <- c("dysregulation", unique(df$words[df$source == "theory"]))
+  baseline <- c("dysregulation", unique(df$cat[df$source == "theory"]))
   
   saveRDS(baseline, "baseline.RData")
   saveRDS(baseline_cat, "baseline_cat.RData")
@@ -40,13 +42,13 @@ in_theory <- df$word[df$source == "theory"]
 in_rev <- df$word[!df$source == "theory"]
 in_rev[!in_rev %in% in_theory]
 
-df_plot <- data.frame(term1 = baseline, term2 = "dysregulation")
+df_plot <- data.frame(term1 = df$cat[df$source == "theory"], term2 = "dysregulation")
 df_plot <- df_plot[!df_plot$term1 == df_plot$term2, ]
 edg <- df_plot
 
 edg$width = 1
 
-vert <- data.frame(name = baseline, label = pretty_words(baseline), size = 1)
+vert <- data.frame(name = unique(c(df_plot$term1, df_plot$term2)), label = pretty_words(unique(c(df_plot$term1, df_plot$term2))), size = 1)
 vert <- vert[vert$name %in% unique(c(edg$term1, edg$term2)), ]
 
 categ <- read.csv("study1_categorization.csv", stringsAsFactors = FALSE)
@@ -59,10 +61,10 @@ vert$Category <- categ$category[match(vert$name, categ$name)]
 cat_cols <- c(Outcome = "gray50", Indicator = "tomato", Cause = "gold", Protective = "forestgreen")
 cat_cols <- c(Outcome = "gray50", Indicator = "tomato", Cause = "gold", Protective = "olivedrab2")
 vert$color <- cat_cols[vert$Category]
-
[…]

### 2020-12-16 study1.R

@@ -1,3 +1,4 @@
+# ---- study1chunk ----
 library(data.table)
 #library(bibliometrix)
 #library(yaml)
@@ -11,8 +12,9 @@ library(Matrix)
 library(ggplot2)
 library(yaml)
 source("word_functions.R")
+source("circle2.R")
 
-run_everything = FALSE
+#run_everything = FALSE
 study1details <- read_yaml("study1_details.yml")
 dict <- read_yaml("yaml_dict.txt")
 ## Look at POS tags?
@@ -79,7 +81,9 @@ if(run_everything){
   categ <- read.csv("study1_categorization.csv", stringsAsFactors = FALSE)
   df_plot$cat <- categ$category[match(df_plot$Word, categ$name)]
   df_plot$baseline <- as.character(df_plot$Word %in% baseline)
+  df_plot$faded <- df_plot$Word %in% baseline
   df_plot$Word <- pretty_words(df_plot$Word)
+  
   
   df_plot <- df_plot[order(df_plot$Frequency, decreasing = TRUE), ]
   df_plot$Word <- ordered(df_plot$Word, levels = df_plot$Word[order(df_plot$Frequency)])
@@ -89,23 +93,22 @@ if(run_everything){
   
   write_yaml(df_plot$Word, "s1_words.yml")
   
-  
   p <- ggplot(df_plot, aes(y = Word, x = Frequency)) +
     geom_segment(aes(x = 0, xend = Frequency,
-                     y = Word, yend = Word,
-                     colour = baseline),
-                 linetype = 2) + geom_vline(xintercept = 0, colour = "grey50",
-                                            linetype = 1) + xlab("Word frequency") +
-    geom_point(aes(fill = cat), shape = 21, size = 2) +
-    scale_colour_manual(values = c("TRUE" = "gray70", "FALSE" = "gray30"))+
+                     y = Word, yend = Word, linetype = faded), colour = "grey50"
+    ) + 
+    geom_vline(xintercept = 0, colour = "grey50", linetype = 1) + xlab("Word frequency") +
+    geom_point(data = df_plot[df_plot$faded, ], aes(colour = cat), fill = "white", shape = 21, size = 1.5) +
+    geom_point(data = df_plot[!df_plot$faded, ], aes(colour = cat, fill = cat), shape = 21, size = 1.5) +
[…]

### 2020-12-16 study2.R

@@ -17,7 +17,8 @@ library(tidytext)
 library(ggplot2)
 library(textrank)
 source("word_functions.R")
-run_everything <- TRUE
+source("circle2.R")
+run_everything <- FALSE
 
 ## Look at POS tags?
 
@@ -184,31 +185,23 @@ if(run_everything){
 
 
 # Wordcloud ---------------------------------------------------------------
+# Frequency of word by doc
+nounbydoc <- df_analyze[, list(freq = .N), by = list(doc_id = doc_id, term = word_coded)]
+number_docs_words2 <- c(docs = length(unique(nounbydoc$doc_id)), words = length(unique(nounbydoc$term)))
+
+nounbydoc$freq <- 1
+dtm <- udpipe::document_term_matrix(document_term_frequencies(nounbydoc))
+topterms <- colSums(dtm)
+topterms <- sort(topterms, decreasing = TRUE)
+
+# Select most common terms ------------------------------------------------
+set.seed(720)
+source("word_functions.R")
+dtm_top <- dtm[, select_words(dtm, .975)]
+dtm_top <- dtm_top[rowSums(dtm_top) > 0, ]
 
 if(run_everything){
-  # Frequency of word by doc
-  nounbydoc <- df_analyze[, list(freq = .N), by = list(doc_id = doc_id, term = word_coded)]
-  number_docs_words2 <- c(docs = length(unique(nounbydoc$doc_id)), words = length(unique(nounbydoc$term)))
-  
-  nounbydoc$freq <- 1
-  dtm <- udpipe::document_term_matrix(document_term_frequencies(nounbydoc))
-  topterms <- colSums(dtm)
-  topterms <- sort(topterms, decreasing = TRUE)
-  
-  # Select most common terms ------------------------------------------------
-  set.seed(720)
-  dtm_top <- dtm[, select_words(dtm, .975)]
-  dtm_top <- dtm_top[rowSums(dtm_top) > 0, ]
-  dim(dtm_top)
-  
-  #topterms <- topterms[topterms > .005*nrow(recs)]
-  
-  #which_topterms <- head(topterms, 250)
-  #which_topterms <- names(which_topterms)
-  #dtm_top <- dtm[, which_topterms]
-  #dtm_top <- dtm_top[rowSums(dtm_top) > 0, ]
-  #dim(dtm_top)
-  
+
   # Wordcloud ---------------------------------------------------------------
   
   ## Word frequencies
[…]

### 2020-12-16 word_functions.R

@@ -1,3 +1,7 @@
+shifter <- function(x, n = 1) {
+  if (n == 0) x else c(tail(x, -n), head(x, n))
+}
+
 boot_dtm_old <- function(dtm, iterations = 1000, confidence_boundary = .95){
   bt <- replicate(iterations, {
     b <- dtm[sample.int(nrow(dtm), replace = TRUE), ]
@@ -42,7 +46,8 @@ select_cooc <- function(cooc, q = .95){
                dims = dim(cooc), symmetric = TRUE)
   rownames(out) <- rownames(cooc)
   colnames(out) <- colnames(cooc)
-  return(out)
+  is_zero <- rowSums(out) == 0
+  return(out[!is_zero, !is_zero])
 }
 
 create_cooc <- function(dtm){
@@ -79,7 +84,16 @@ select_fixed_margin <- function(dtm, confidence_boundary = .95, iterations = 100
   out
 }
 
-pretty_words <- function(x){ str_to_sentence(gsub("[_-]", " ", x)) }
+pretty_words <- function(x){ 
+  out <- str_to_sentence(gsub("[_-]", " ", x))
+  out[out == "Adhd cd"] <- "ADHD/CD"
+  out[out == "Ses"] <- "SES"
+  out[out == "Ptsd"] <- "PTSD"
+  out[out == "Schizo"] <- "Schizophrenia"
+  out <- gsub("^Par\\.", "Parenting ", out)
+  out
+}
+
 
 conflicting_matches <- function(words, dict){
   dict_matches <- lapply(unlist(dict), function(this_reg){

### 2020-12-17 manuscript.Rmd
Submitted to CD

@@
 
-wordcount         : "5400"
+wordcount         : "6311"
 bibliography      : ["veni_sysrev.bib"]
@@
 classoption       : "man,noextraspace"
-output            : papaja::apa6_pdf
+output            : papaja::apa6_docx
 knit              : worcs:::cite_essential
+header-includes:
+  - \raggedbottom
 ---
@@
 library("papaja")
-library(bibliometrix)
-library(revtools)
-library(bib2df)
+library(data.table, quietly = TRUE, warn.conflicts = FALSE)
 library(knitr)
@@
 library(cowplot)
-run_everything = FALSE
+run_everything <- TRUE
 notingraph <- list()
+keyw <- function(x){
+  x
+}
 ```
@@
 set.seed(42)
-knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
+knitr::opts_chunk$set(cache.extra = knitr::rand_seed, echo = FALSE, message = FALSE, warning = FALSE, results="hide")
 ```
 
-<!-- Development and Psychopathology is the most relevant source of articles reviewed herein
-Most Relevant Sources
-
-                                                       Sources        Articles
-1  DEVELOPMENT AND PSYCHOPATHOLOGY                                         120
-
-on adolescent emotion regulation development is limited27–29.
-The field is therefore at an impasse: We know that some adolescents are more susceptible to emotion dysregulation than others, but lack tools and theory to identify important predictors of individual development30.
--->
-
-<!-- Emotion regulation in adolescence is important -->
 A key developmental challenge in adolescence is acquiring mature emotion
@@
 
-```{r baseline, warning=FALSE, eval = TRUE, out.width = "100%", fig.cap="Correlates of emotion regulation difficulties according to theory (left panel) and narrative reviews (right panel).
+```{r baseline, warning=FALSE, eval = TRUE, results='asis', out.width = "100%", fig.cap="Correlates of emotion regulation difficulties according to theory (left panel) and narrative reviews (right panel).
 Transparent circles indicate constructs also represented in the theory."}
+source("baseline.R", local = TRUE)
 knitr::include_graphics("baseline_network.png") 
@@
 #plot(fig_svg)
-keyw <- function(x){
-  cat(x)
-}
+
 ```
@@
 
-The present paper aims to develop a nomological network of the constructs
+The present paper aims to map the constructs
 related to adolescent emotion dysregulation, based on a systematic review of
-the literature. A nomological network is a diagrammatic representation of a
-phenomenon; a proto-theoretical device that describes relationships between
-constructs relevant to the theory [see @alaviAligningTheoryMethodology2018].
-It is a precursor to a more
-explicit theory of the phenomenon. The present paper uses an inductive approach
-to develop this nomological network. <!-- CJ Consider removing the following if the purpose is sufficiently clarified in the introduction -->
+the literature. <!-- CJ Consider removing the following if the purpose is sufficiently clarified in the introduction -->
 First, we conducted a systematic search to
@@
 if(!file.exists(filenam)){
+  library(bibliometrix)
   f <- list.files("./recs/18-3-2020/", full.names = TRUE)
@@
 if(!file.exists(filenam)){
+  library(revtools)
   recs$doi <- recs$DI
@@
 
-```{r prismachart, fig.cap="Record screening flowchart"}
+```{r prismachart, results='asis', fig.cap="Record screening flowchart"}
 library(tidySEM)
@@
 
-p <- graph_sem(layout = lo, nodes = nodes, edges = edges, angle = 1, rect_height = 1.2, rect_width = 1.3)
+p <- graph_sem(layout = lo, nodes = nodes, edges = edges, angle = 1, rect_height = 1.2, rect_width = 1.3, text_size = 4)
 ggsave("prismachart.png", p, device = "png")
@@
 
-```{r cache=FALSE}
-knitr::read_chunk("study1.R")
-```
-```{r study1chunk}
+```{r echo=FALSE, message=FALSE, warning=FALSE}
+library(stringr)
+library(udpipe)
+library(igraph)
+library(wordcloud)
+library(Matrix)
+library(ggplot2)
+library(yaml)
+source("word_functions.R")
+source("circle2.R")
+
+#run_everything = FALSE
+study1details <- read_yaml("study1_details.yml")
+dict <- read_yaml("yaml_dict.txt")
+## Look at POS tags?
+if(!isTRUE(tools::md5sum("study1_df.RData") == "042c7d894929b0351f804c1a4b5c5002")){
+  recs <- data.table(read.csv("recs_final.csv"))
+  if(!is.data.table(recs)){
+    browser()
+  }
+  recs[, "doc" := 1:nrow(recs)]
+  study1details <- list(dim_recs = dim(recs))
+
+  # Extract individual words
+  df <- lapply(recs$DE, function(x){strsplit(x, split = "; ")[[1]]})
+  df <- merge_df(recs, df, "word")
+
+  df[, word := tolower(word)]
+
+  # Clean
+  df <- na.omit(df, cols = "word")
+  number_docs_words <- c(docs = length(unique(df$doc)), words = length(unique(df$word)))
+  yaml::write_yaml(number_docs_words, "study1_number_docs_words.txt")
+  # Exclude words
+  exclude_terms <- readLines("exclude_terms.txt")
+  exclude_these <- unique(unlist(lapply(exclude_terms, grep, x = df$word)))
+
+  df <- df[!exclude_these, ]
+
+  # Categorize words
+  res_cat <- cat_words(df$word, dict, handle_dups = "all")
+  # Check coding issues
+  #res_cat$dup
+  #head(res_cat$unmatched)
+  df <- merge_df(df, res_cat$words, "word_coded")
+  saveRDS(df, "study1_df.RData")
+} else {
+  df <- readRDS("study1_df.RData")
+  number_docs_words <- yaml::read_yaml("study1_number_docs_words.txt")
+}
+
+if(run_everything){
+  # Frequency of word by doc
+  nounbydoc <- df[, list(freq = .N), by = list(doc_id = doc, term = word_coded)]
+  # Set frequency to 1; we're not interpreting word frequency, only occurrence
+  nounbydoc$freq <- 1
+
+  dtm <- udpipe::document_term_matrix(document_term_frequencies(nounbydoc))
+
+  # Continue plotting word frequency ----------------------------------------
+
+  set.seed(5348)
+  dtm_top <- dtm[, select_words(dtm, .975)]
+  dtm_top <- dtm_top[rowSums(dtm_top) > 0, ]
+  write_yaml(dim(dtm_top), "study1_dtm_top.yml")
+
+  # Wordcloud ---------------------------------------------------------------
+
+  ## Word frequencies
+  topterms <- colSums(dtm_top)
+  baseline <- readRDS("baseline.RData")
+
+  word_freq <- data.frame(Word = names(topterms), Frequency = topterms, row.names = NULL)
+  write.csv(word_freq, "study1_word_freq.csv", row.names = FALSE)
+  df_plot <- word_freq
+  categ <- read.csv("study1_categorization.csv", stringsAsFactors = FALSE)
+  df_plot$cat <- categ$category[match(df_plot$Word, categ$name)]
+  df_plot$baseline <- as.character(df_plot$Word %in% baseline)
+  df_plot$faded <- df_plot$Word %in% baseline
+  df_plot$Word <- pretty_words(df_plot$Word)
+
+  df_plot <- df_plot[order(df_plot$Frequency, decreasing = TRUE), ]
+  df_plot$Word <- ordered(df_plot$Word, levels = df_plot$Word[order(df_plot$Frequency)])
+
+  cat_cols <- c(Outcome = "gray50", Indicator = "tomato", Cause = "gold", Protective = "forestgreen")
+  df_plot$cat <- ordered(df_plot$cat, levels = c("Outcome", "Indicator", "Cause", "Protective"))
+
+  write_yaml(df_plot$Word, "s1_words.yml")
+
+  p <- ggplot(df_plot, aes(y = Word, x = Frequency)) +
+    geom_segment(aes(x = 0, xend = Frequency,
+                     y = Word, yend = Word, linetype = faded), colour = "grey50"
+    ) + 
+    geom_vline(xintercept = 0, colour = "grey50", linetype = 1) + xlab("Word frequency") +
+    geom_point(data = df_plot[df_plot$faded, ], aes(colour = cat), fill = "white", shape = 21, size = 1.5) +
+    geom_point(data = df_plot[!df_plot$faded, ], aes(colour = cat, fill = cat), shape = 21, size = 1.5) +
+    scale_colour_manual(values = c(Outcome = "gray50", Indicator = "tomato", Cause = "gold", Protective = "forestgreen"), guide = NULL)+
+    scale_fill_manual(values = c(Outcome = "gray50", Indicator = "tomato", Cause = "gold", Protective = "forestgreen")) +
+    scale_x_log10() +
+    scale_linetype_manual(values = c("TRUE" = 2, "FALSE" = 1), guide = NULL) +
+    theme_bw() + theme(panel.grid.major.x = element_blank(),
+                       panel.grid.minor.x = element_blank(), axis.title.y = element_blank(),
+                       legend.position = c(.70,.125),
+                       legend.title = element_blank(),
+                       axis.text.y = element_text(hjust=0, vjust = 0, size = 6))
+
+  svg("s1_varimp.svg", width = 7/2.54, height = 14/2.54)
+  eval(p)
+  dev.off()
+
+  ggsave("s1_varimp.png", p, device = "png", width = 7, height = 14, units = "cm")
+
+  df_plot$Frequency <- sqrt(df_plot$Frequency)
+  ## Visualise them with wordclouds
+  p <- quote({
+    set.seed(46)
+    wordcloud(words = df_plot$Word, freq = df_plot$Frequency, scale = c(2,.4), max.words = 150, rot.per = 0,  random.order = FALSE, colors = brewer.pal(8, "Dark2"))
+  })
+  svg("study1_wordcloud.svg")
+  eval(p)
+  dev.off()
+
+  png("study1_wordcloud.png")
+  eval(p)
+  dev.off()
+}
+
+# LDA analysis ------------------------------------------------------------
+
+if(!isTRUE(tools::md5sum("Study1_lda_dims.txt") == "4e2493d4d618020d4acde61dd7864425")){
+  library(Rmpfr)
+  library(topicmodels)
+  library(udpipe)
+  library(slam)
+  library(tidytext)
+  # Functions:
+  harmonicMean <- function(logLikelihoods, precision = 2000L) {
+    llMed <- median(logLikelihoods)
+    as.double(llMed - log(mean(exp(-mpfr(logLikelihoods,
+                                         prec = precision) + llMed))))
+  }
+  BIC <- function(ll, p, n){
+    -2 * ll + p * log(n)
+  }
+  entropy <- function(post_prob){
+    1 + (1/(nrow(post_prob) * 
+              log(ncol(post_prob)))) * (sum(rowSums(post_prob * 
+                                                      log(post_prob + 1e-12))))
+  }
+
+  # Preprocessing -----------------------------------------------------------
+
+  #nounbydoc <- df[, list(freq = .N), by = list(doc_id = doc, term = word_coded)]
+  df_lda <- nounbydoc #[nounbydoc$term %in% names(dict), ]
+  df_lda <- df_lda %>%
+    bind_tf_idf(term, doc_id, freq)
+  summary(df_lda$tf_idf)
+  df_lda <- df_lda[order(df_lda$tf_idf),]
+
+  select_words <- df_lda[!duplicated(df_lda$term), ]
+  select_words <- select_words$term[select_words$tf_idf >= median(select_words$tf_idf)]
+  df_lda <- df_lda[df_lda$term %in% select_words, ]
+
+  dtm <- udpipe::document_term_matrix(document_term_frequencies(df_lda))
+
+  # dtm <- as.simple_triplet_matrix(dtm)
+  # dim(dtm)
+  # summary(col_sums(dtm))
+  # term_tfidf <- tapply(dtm$v/row_sums(dtm)[dtm$i], dtm$j, mean) * log2(dim(dtm)[1]/col_sums(dtm > 0))
+  # summary(term_tfidf)
+
+  yaml::write_yaml(dim(dtm), file = "Study1_lda_dims.txt")
+
+  # Build topic models
+
+  seqk <- seq(2, 20, 1)
+  burnin <- 1000
+  iter <- 1000
+  keep <- 50
+  set.seed(44773)
+  res_lda <- lapply(seqk, function(k) {
+    topicmodels::LDA(
+      dtm,
+      k = k,
+      method = "Gibbs",
+      control = list(
+        burnin = burnin,
+        iter = iter,
+        keep = keep
+      )
+    )
+  })
+
+  ll <- sapply(res_lda, function(x){harmonicMean(x@logLiks[-c(1:(burnin/keep))])})
+
+  K = seqk
+  N = nrow(dtm)
+  M = ncol(dtm)
+
+  parameters <- K*(M-1)+N*(K-1)
+  N <- nrow(dtm)
+  bics <- BIC(ll, parameters, N)
+
+  entropies <- sapply(res_lda, function(x){entropy(x@gamma)})
+
+  p <- ggplot(data.frame(K = seqk, Entropy = entropies), aes(x = K, y = Entropy)) + geom_path() +
+    xlab('Number of topics') +
+    scale_y_continuous(limits = c(0,1)) +
+    theme_bw()
+
+  ggsave("study1_entropies.png", p, device = "png")
+  ggsave("study1_entropies.svg", p, device = "svg")
+
+  p <- ggplot(data.frame(K = seqk, ll = ll), aes(x = K, y = ll)) + geom_path() +
+    geom_vline(xintercept = (which.max(ll)+1), linetype = 2) +
+    xlab('Number of topics') +
+    geom_smooth(method = "lm", formula = y~log(x), se = FALSE)+
+    theme_bw()
+
+  ggsave("study1_ll.png", p, device = "png")
+  ggsave("study1_ll.svg", p, device = "svg")
+
+  p <- ggplot(data.frame(K = seqk, BIC = bics), aes(x = K, y = BIC)) + geom_path() +
+    geom_vline(xintercept = (which.min(bics)+1), linetype = 2) +
+    xlab('Number of topics') +
+    geom_smooth(method = "lm", formula = y~x, se = FALSE)+
+    theme_bw()
+
+  ggsave("study1_BIC.png", p, device = "png")
+  ggsave("study1_BIC.svg", p, device = "svg")
+}
+
+# Co-occurrence -----------------------------------------------------------
+
+if(run_everything){
+  set.seed(52)
+  cooc <- select_cooc(create_cooc(dtm_top), q = .975)
+  write.csv(as.matrix(cooc), "s1_cooc.csv")
+  df_plot <- as_cooccurrence(cooc)
+  df_plot <- df_plot[!df_plot$term1 == df_plot$term2, ]
+  df_plot <- df_plot[order(df_plot$cooc, decreasing = TRUE), ]
+
+  df_plot$id <- apply(df_plot[, c("term1", "term2")], 1, function(x)paste0(sort(x), collapse = ""))
+  df_plot <- df_plot[!duplicated(df_plot$id), ]
+
+  # Write study details -----------------------------------------------------
+
+  write_yaml(study1details, "study1_details.yml")
+
+  # Create network ----------------------------------------------------------
+
+  edg <- df_plot
+  edg$width = edg$cooc
+
+  vert <- data.frame(name = names(topterms), label = pretty_words(names(topterms)), size = topterms)
+  vert <- vert[vert$name %in% unique(c(edg$term1, edg$term2)), ]
+
+  categ <- read.csv("study1_categorization.csv", stringsAsFactors = FALSE)
+  if(any(!vert$name %in% categ$name)){
+    write.table(vert$name[!vert$name %in% categ$name], "clipboard", sep = "\n", row.names = FALSE, col.names= FALSE)
+    stop("Please re-categorize missing vertices.")
+  } 
+  vert$Category <- categ$category[match(vert$name, categ$name)]
+  vert$faded <- vert$name %in% baseline
+
+  cat_cols <- c(Outcome = "gray50", Indicator = "tomato", Cause = "gold", Protective = "olivedrab2")
+  vert$color <- cat_cols[vert$Category]
+  vert$frame.color <- cat_cols[vert$Category]
+  vert$color[vert$faded] <- "#FFFFFF"
+
+  vert$size <- scales::rescale(log(vert$size), c(4, 12))
+  g <- graph_from_data_frame(edg, vertices = vert,
+                             directed = FALSE)
+
+  # edge thickness
+  E(g)$width <- scales::rescale(sqrt(E(g)$width), to = c(2, 8))
+
+  dysreg_vertex = which(names(V(g)) == "dysregulation")
+
+  edge.start <- ends(g, es=E(g), names = FALSE)[,1]
+  edge.end <- ends(g, es=E(g), names = FALSE)[,2]
+  E(g)$lty <- c(1, 5)[(!(edge.start == dysreg_vertex|edge.end == dysreg_vertex))+1]
+
+  # Layout
+  set.seed(6) #4
+  l1 <- l <- layout_with_fr(g)
+  l1[,1] <- -1*l1[,1]
+  set.seed(64)
+  l2 <- layout_in_circle(g, order = shifter(V(g), -3))
+
+  p <- quote({
+    # Set margins to 0
+    par(mar=c(0,0,0,0),
+        mfrow=c(1,2))
+    plot(g, edge.curved = 0, layout=l1,
+         vertex.label.family = "sans",
+         vertex.label.cex = 0.8,
+         vertex.shape = "circle2",
+         #vertex.frame.color = 'gray40',
+         vertex.label.color = 'black',      # Color of node names
+         vertex.label.font = 1,         # Font of node names
+         vertex.frame.width = 2
+    )
+    legend(x=-1.1, y=1.1, names(cat_cols), pch=21, col="#777777", pt.bg=cat_cols, pt.cex=2, cex=.8, bty="n", ncol=1)
+    plot(g, edge.curved = 0, layout=l2,
+         vertex.label.family = "sans",
+         vertex.label.cex = 0.8,
+         vertex.shape = "circle2",
+         #vertex.frame.color = 'gray40',
+         vertex.label.color = 'black',      # Color of node names
+         vertex.label.font = 1,         # Font of node names
+         vertex.frame.width = 2
+    )
+  })
+
+  # Save files
+  png("study1_network1.png", width = 960)
+  eval(p)
+  dev.off()
+
+  svg("study1_network1.svg", width = 14)
+  eval(p)
+  dev.off()
+}
+categ <- read.csv("study1_categorization.csv", stringsAsFactors = FALSE)
+word_freq <- read.csv("study1_word_freq.csv", stringsAsFactors = FALSE)
+word_graph <- read.csv("s1_cooc.csv", row.names = 1)
+notingraph <- word_freq$Word[!word_freq$Word %in% row.names(word_graph)]
+notingraph <- categ[categ$name %in% notingraph, ]
+cats <- unique(notingraph$category)
+notingraph <- lapply(cats, function(x){ 
+  out <- notingraph$name[notingraph$category == x]
+  out <- pretty_words(out)
+  paste0(paste0("*", out[-length(out)], "*", collapse = ", "), ", and *", tail(out, 1), "*")
+  })
+names(notingraph) <- cats
+
+lda_dims <- read_yaml("Study1_lda_dims.txt")
+dtm_top <- read_yaml("study1_dtm_top.yml")
 ```
@@
 
-```{r study1varimp, warning=FALSE, eval = TRUE, out.width = "100%", fig.cap="Document frequency of terms selected for Study 1.
+```{r study1varimp, warning=FALSE, eval = TRUE, results='asis', out.width = "100%", fig.cap="Document frequency of terms selected for Study 1.
 Dashed lines and transparent circles indicate constructs also represented in the theory (cf Figure 1)."}
@@
 
-Many of these excluded constructs represent active ongoing areas of research, including research on *fathers* [@vanlissaRoleFathersMothers2019], *identity* [@campbellFriendsEducationIdentity2019], *friendship* and *social support* [@wangBidirectionalEffectsExpressive2020], *autonomy* [@vrolijkLongitudinalLinkagesFatherunderreview; @brenningPerceivedMaternalAutonomy2015], *sexual risk* [@brownDepressiveSymptomsPredictor2006], and *loneliness* [@spithovenItAllTheir2017].
+Many of these excluded constructs represent active ongoing areas of research, including research on *fathers* [@vanlissaRoleFathersMothers2019], *identity* [@campbellFriendsEducationIdentity2019], *friendship* and *social support* [@wangBidirectionalEffectsExpressive2020], *autonomy* [@vrolijkLongitudinalLinkagesFather2020a; @brenningPerceivedMaternalAutonomy2015], *sexual risk* [@brownDepressiveSymptomsPredictor2006], and *loneliness* [@spithovenItAllTheir2017].
 The fact that these constructs are absent from the graph does not suggest that they are unimportant.
@@
 
-```{r, warning=FALSE, message=FALSE}
-source("study2.R")
-if(run_everything | !file.exists("Study2_lda_dims.txt")) source("LDA_analysis.R")
+```{r}
+source("word_functions.R")
+source("circle2.R")
+```
+
+```{r}
+library(stringr)
+library(udpipe)
+library(igraph)
+library(wordcloud)
+library(Matrix)
+library(yaml)
+library(Rmpfr)
+library(topicmodels)
+library(udpipe)
+library(slam)
+library(tidytext)
+library(ggplot2)
+library(textrank)
+
+if(isTRUE(tools::md5sum("study2_df.RData") == "21abb2622dfd94d8bd3473ed56697f9e")){
+  df <- readRDS("study2_df.RData")
+} else {
+  stop("Note: Study 2 file is out of date. Please run this code manually.")
+  recs <- data.table(read.csv("recs_final.csv"))
+  if(!is.data.table(recs)){
+    browser()
+  }
+  recs[, "doc" := 1:nrow(recs)]
+
+  recs$AB <- tolower(recs$AB)
+  if(!file.exists("english-ewt-ud-2.4-190531.udpipe")) {
+    ud_model <- udpipe_download_model(language = "english")
+  } else {
+    ud_model <- udpipe_load_model("english-ewt-ud-2.4-190531.udpipe")
+    ud_model <- udpipe_load_model(ud_model$file)
+  }
+  udp_res <- udpipe_annotate(ud_model, x = recs$AB, doc_id = recs$doc)
+  df <- as.data.table(udp_res)
+  saveRDS(df, "study2_df.RData")
+}
+
+# LDA analysis ------------------------------------------------------------
+
+if(!isTRUE(tools::md5sum("Study2_lda_dims.txt") == "2d00a24d8b54ac898eec6cd104086a0f")){
+  # Functions:
+  harmonicMean <- function(logLikelihoods, precision = 2000L) {
+    llMed <- median(logLikelihoods)
+    as.double(llMed - log(mean(exp(-mpfr(logLikelihoods,
+                                         prec = precision) + llMed))))
+  }
+  BIC <- function(ll, p, n){
+    -2 * ll + p * log(n)
+  }
+  entropy <- function(post_prob){
+    1 + (1/(nrow(post_prob) * 
+              log(ncol(post_prob)))) * (sum(rowSums(post_prob * 
+                                                      log(post_prob + 1e-12))))
+  }
+
+  # Preprocessing -----------------------------------------------------------
+
+  # Frequency of word by doc
+  nounbydoc <- df[df$upos %in% c("NOUN", "ADJ"), list(freq = .N), by = list(doc_id = doc_id, term = lemma)]
+  df_lda <- nounbydoc #[nounbydoc$term %in% names(dict), ]
+  df_lda <- df_lda %>%
+    bind_tf_idf(term, doc_id, freq)
+  summary(df_lda$tf_idf)
+
+  select_words <- df_lda[!duplicated(df_lda$term), ]
+  select_words <- select_words$term[select_words$tf_idf >= median(select_words$tf_idf)]
+  df_lda <- df_lda[df_lda$term %in% select_words, ]
+
+  dtm <- udpipe::document_term_matrix(document_term_frequencies(df_lda))
+  yaml::write_yaml(dim(dtm), file = "Study2_lda_dims.txt")
+
+  # Build topic models
+  seqk <- seq(2, 20, 1)
+  burnin <- 1000
+  iter <- 1000
+  keep <- 50
+  set.seed(44773)
+  res_lda <- lapply(seqk, function(k) {
+    topicmodels::LDA(
+      dtm,
+      k = k,
+      method = "Gibbs",
+      control = list(
+        burnin = burnin,
+        iter = iter,
+        keep = keep
+      )
+    )
+  })
+
+  ll <- sapply(res_lda, function(x){harmonicMean(x@logLiks[-c(1:(burnin/keep))])})
+
+  K = seqk
+  N = nrow(dtm)
+  M = ncol(dtm)
+
+  parameters <- K*(M-1)+N*(K-1)
+  N <- nrow(dtm)
+  bics <- BIC(ll, parameters, N)
+
+  entropies <- sapply(res_lda, function(x){entropy(x@gamma)})
+
+  p <- ggplot(data.frame(K = seqk, Entropy = entropies), aes(x = K, y = Entropy)) + geom_path() +
+    xlab('Number of topics') +
+    scale_y_continuous(limits = c(0,1)) +
+    theme_bw()
+
+  ggsave("study2_entropies.png", p, device = "png")
+  ggsave("study2_entropies.svg", p, device = "svg")
+
+  p <- ggplot(data.frame(K = seqk, ll = ll), aes(x = K, y = ll)) + geom_path() +
+    geom_vline(xintercept = (which.max(ll)+1), linetype = 2) +
+    xlab('Number of topics') +
+    geom_smooth(method = "lm", formula = y~log(x), se = FALSE)+
+    theme_bw()
+
+  ggsave("study2_ll.png", p, device = "png")
+  ggsave("study2_ll.svg", p, device = "svg")
+
+  p <- ggplot(data.frame(K = seqk, BIC = bics), aes(x = K, y = BIC)) + geom_path() +
+    geom_vline(xintercept = (which.min(bics)+1), linetype = 2) +
+    xlab('Number of topics') +
+    geom_smooth(method = "lm", formula = y~x, se = FALSE)+
+    theme_bw()
+
+  ggsave("study2_BIC.png", p, device = "png")
+  ggsave("study2_BIC.svg", p, device = "svg")
+}
+
+# Keyword extraction ------------------------------------------------------
+
+# Exclude words
+if(isTRUE(tools::md5sum("study2_df_kw.RData") == "8c9b3d61fa7e9bb6a3b31962b11face1")){
+  df_kw <- readRDS("study2_df_kw.RData")
+} else {
+  df_kw <- df[upos %in% c("NOUN", "ADJ"), ]
+  df_kw <- df_kw[grepl("^[a-zA-Z].", df_kw$lemma), ]
+  exclude_terms <- readLines("exclude_terms.txt")
+  exclude_these <- unique(unlist(lapply(exclude_terms, grep, x = df_kw$lemma)))
+  df_kw <- df_kw[-exclude_these, ]
+  saveRDS(df_kw, "study2_df_kw.RData")
+}
+
+# No numeric values
+# all(is.na(as.numeric(df_kw$lemma)))
+#df_kw$lemma[nchar(df_kw$lemma) == 3]
+
+if(isTRUE(tools::md5sum("study2_textrank.RData") == "dcaf7c9bab7a4abd86d19d4868fad780")){
+  kw_tr <- readRDS("study2_textrank.RData")
+} else {
+  kw_tr <- textrank_keywords(x = df_kw$lemma[df_kw$upos %in% c("NOUN", "ADJ")], 
+                             ngram_max = 3, sep = " ")
+  saveRDS(kw_tr, "study2_textrank.RData")
+}
+
+if(isTRUE(tools::md5sum("study2_df_analyze.RData") == "e50ee4984e0872947342d868e3bc9144")){
+  df_analyze <- data.table(readRDS("study2_df_analyze.RData"))
+} else {
+  # Merge back with original data
+  df_kw$keyword <- txt_recode_ngram(df_kw$lemma, compound = kw_tr$keywords$keyword, ngram = kw_tr$keywords$ngram, sep = " ")
+  df_kw$keyword[!df_kw$keyword %in% kw_tr$keywords$keyword] <- NA
+
+  df_analyze <- df_kw[!is.na(df_kw$keyword), ]
+  dict <- read_yaml("yaml_dict.txt")
+  res_cat <- cat_words(df_analyze$keyword, dict, handle_dups = "all")
+  # Check coding issues
+  #res_cat$dup
+  #head(res_cat$unmatched)
+  df_analyze <- merge_df(df_analyze, res_cat$words, "word_coded")
+  saveRDS(df_analyze, "study2_df_analyze.RData")
+}
+
+# Wordcloud ---------------------------------------------------------------
+# Frequency of word by doc
+if(!is.data.table(df_analyze)) stop("Not a data.table")
+nounbydoc <- df_analyze[, list(freq = .N), by = list(doc_id = doc_id, term = word_coded)]
+number_docs_words2 <- c(docs = length(unique(nounbydoc$doc_id)), words = length(unique(nounbydoc$term)))
+
+nounbydoc$freq <- 1
+dtm <- udpipe::document_term_matrix(document_term_frequencies(nounbydoc))
+topterms <- colSums(dtm)
+topterms <- sort(topterms, decreasing = TRUE)
+
+# Select most common terms ------------------------------------------------
+set.seed(720)
+dtm_top <- dtm[, select_words(dtm, .975)]
+dtm_top <- dtm_top[rowSums(dtm_top) > 0, ]
+
+if(run_everything){
+
+  # Wordcloud ---------------------------------------------------------------
+
+  ## Word frequencies
+  topterms <- colSums(dtm_top)
+  topterms <- sort(topterms, decreasing = TRUE)
+  word_freq <- data.frame(Word = names(topterms), Frequency = topterms, row.names = NULL)
+  write.csv(word_freq, "study2_word_freq.csv", row.names = FALSE)
+  df_plot <- word_freq
+  df_plot$Word <- pretty_words(df_plot$Word)
+  df_plot$Frequency <- sqrt(df_plot$Frequency)
+  ## Visualise them with wordclouds
+  p <- quote({
+    set.seed(46)
+    wordcloud(words = df_plot$Word, freq = df_plot$Frequency, scale = c(4,.4), max.words = 150, rot.per = 0,  random.order = FALSE, colors = brewer.pal(8, "Dark2"))
+  })
+
+  svg("study2_wordcloud.svg")
+  eval(p)
+  dev.off()
+
+  png("study2_wordcloud.png")
+  eval(p)
+  dev.off()
+}
+
+# Feature importance ------------------------------------------------------
+topterms <- colSums(dtm_top)
+if(run_everything){
+  baseline <- readRDS("baseline.RData")
+
+  word_freq <- data.frame(Word = names(topterms), Frequency = topterms, row.names = NULL)
+  df_plot <- word_freq
+  categ <- read.csv("study1_categorization.csv", stringsAsFactors = FALSE)
+  df_plot$cat <- categ$category[match(df_plot$Word, categ$name)]
+  df_plot$faded <- df_plot$Word %in% baseline
+  df_plot$Word <- pretty_words(df_plot$Word)
+
+  df_plot <- df_plot[order(df_plot$Frequency, decreasing = TRUE), ]
+  df_plot$Word <- ordered(df_plot$Word, levels = df_plot$Word[order(df_plot$Frequency)])
+
+  cat_cols <- c(Outcome = "gray50", Indicator = "tomato", Cause = "gold", Protective = "forestgreen")
+  df_plot$cat <- ordered(df_plot$cat, levels = c("Outcome", "Indicator", "Cause", "Protective"))
+
+  write_yaml(df_plot$Word, "s2_words.yml")
+
+  p <- ggplot(df_plot, aes(y = Word, x = Frequency)) +
+    geom_segment(aes(x = 0, xend = Frequency,
+                     y = Word, yend = Word, linetype = faded), colour = "grey50"
+    ) + 
+    geom_vline(xintercept = 0, colour = "grey50", linetype = 1) + xlab("Word frequency") +
+    geom_point(data = df_plot[df_plot$faded, ], aes(colour = cat), fill = "white", shape = 21, size = 1.5) +
+    geom_point(data = df_plot[!df_plot$faded, ], aes(colour = cat, fill = cat), shape = 21, size = 1.5) +
+    scale_colour_manual(values = c(Outcome = "gray50", Indicator = "tomato", Cause = "gold", Protective = "forestgreen"), guide = NULL)+
+    scale_fill_manual(values = c(Outcome = "gray50", Indicator = "tomato", Cause = "gold", Protective = "forestgreen")) +
+    scale_x_log10() +
+    scale_linetype_manual(values = c("TRUE" = 2, "FALSE" = 1), guide = NULL) +
+    theme_bw() + theme(panel.grid.major.x = element_blank(),
+                       panel.grid.minor.x = element_blank(), axis.title.y = element_blank(),
+                       legend.position = c(.70,.125),
+                       legend.title = element_blank(),
+                       axis.text.y = element_text(hjust=0, vjust = 0, size = 6))
+
+  svg("s2_varimp.svg", width = 7/2.54, height = 14/2.54)
+  eval(p)
+  dev.off()
+
+  ggsave("s2_varimp.png", p, device = "png", width = 7, height = 14, units = "cm")
+}
+
+# Co-occurrence -----------------------------------------------------------
+set.seed(5646)
+cooc <- select_cooc(create_cooc(dtm_top), q = .975)
+
+if(run_everything){
+  write.csv(as.matrix(cooc), "s2_cooc.csv")
+  df_plot <- as_cooccurrence(cooc)
+  df_plot <- df_plot[!df_plot$term1 == df_plot$term2, ]
+  df_plot <- df_plot[order(df_plot$cooc, decreasing = TRUE), ]
+
+  df_plot$id <- apply(df_plot[, c("term1", "term2")], 1, function(x)paste0(sort(x), collapse = ""))
+  df_plot <- df_plot[!duplicated(df_plot$id), ]
+
+  # Create network ----------------------------------------------------------
+
+  edg <- df_plot
+  edg$width = edg$cooc
+
+  vert <- data.frame(name = names(topterms), label = pretty_words(names(topterms)), size = topterms)
+  vert <- vert[vert$name %in% unique(c(edg$term1, edg$term2)), ]
+
+  categ <- read.csv("study1_categorization.csv", stringsAsFactors = FALSE)
+  if(any(!vert$name %in% categ$name)){
+    write.table(vert$name[!vert$name %in% categ$name], "clipboard", sep = "\n", row.names = FALSE, col.names= FALSE)
+    stop("Please re-categorize missing vertices.")
+  } 
+  vert$Category <- categ$category[match(vert$name, categ$name)]
+  vert$faded <- vert$name %in% baseline
+
+  cat_cols <- c(Outcome = "gray50", Indicator = "tomato", Cause = "gold", Protective = "olivedrab2")
+  vert$color <- cat_cols[vert$Category]
+  vert$frame.color <- cat_cols[vert$Category]
+
+  vert$color[vert$faded] <- "#FFFFFF"
+
+  vert$size <- scales::rescale(log(vert$size), c(4, 12))
+  g <- graph_from_data_frame(edg, vertices = vert,
+                             directed = FALSE)
+
+  # edge thickness
+  E(g)$width <- scales::rescale(sqrt(E(g)$width), to = c(.2, 8))
+  dysreg_vertex = which(names(V(g)) == "dysregulation")
+
+  edge.start <- ends(g, es=E(g), names = FALSE)[,1]
+  edge.end <- ends(g, es=E(g), names = FALSE)[,2]
+  # Color edges based on origin:
+  #E(g)$color <- V(g)$color[edge.start]
+  E(g)$lty <- c(1, 5)[(!(edge.start == dysreg_vertex|edge.end == dysreg_vertex))+1]
+
+  set.seed(5) #4 #2 #3
+  l1 <- l <- layout_with_fr(g)
+  set.seed(3) #64
+  l2 <- layout_in_circle(g, order = shifter(V(g), -1))
+
+  p <- quote({
+    # Set margins to 0
+    par(mar=c(0,0,0,0),
+        mfrow=c(1,2))
+    plot(g, edge.curved = 0, layout=l1,
+         vertex.label.family = "sans",
+         vertex.label.cex = 0.8,
+         vertex.shape = "circle2",
+         #vertex.frame.color = 'gray40',
+         vertex.label.color = 'black',      # Color of node names
+         vertex.label.font = 1,         # Font of node names
+         vertex.frame.width = 2
+    )
+    legend(x=-1.1, y=1.1, names(cat_cols), pch=21, col="#777777", pt.bg=cat_cols, pt.cex=2, cex=.8, bty="n", ncol=1)
+    plot(g, edge.curved = 0, layout=l2,
+         vertex.label.family = "sans",
+         vertex.label.cex = 0.8,
+         vertex.shape = "circle2",
+         #vertex.frame.color = 'gray40',
+         vertex.label.color = 'black',      # Color of node names
+         vertex.label.font = 1,         # Font of node names
+         vertex.frame.width = 2
+    )
+  })
+
+  # Save files
+  png("study2_network1.png", width = 960)
+  eval(p)
+  dev.off()
+
+  svg("study2_network1.svg", width = 14)
+  eval(p)
+  dev.off()
+}
+
+word_freq <- read.csv("study2_word_freq.csv", stringsAsFactors = FALSE)
+word_graph <- read.csv("s2_cooc.csv", row.names = 1)
+notingraph <- word_freq$Word[!word_freq$Word %in% row.names(word_graph)]
+notingraph <- categ[categ$name %in% notingraph, ]
+cats <- unique(notingraph$category)
+notingraph <- lapply(cats, function(x){ 
+  out <- notingraph$name[notingraph$category == x]
+  out <- pretty_words(out)
+  paste0(paste0("*", out[-length(out)], "*", collapse = ", "), ", and *", tail(out, 1), "*")
+})
+names(notingraph) <- cats
 lda_dims_2 <- read_yaml("Study2_lda_dims.txt")
+
 ```
+
 The corpus for this second analysis consisted of the abstracts of the selected articles.
@@
 
-```{r study2varimp, eval = TRUE, out.width = "100%", fig.cap="Document frequency of terms selected for Study 2.
+```{r study2varimp, eval = TRUE, out.width = "100%", results='asis', fig.cap="Document frequency of terms selected for Study 2.
 Dashed lines and transparent circles indicate constructs also represented in the theory (cf Figure 1)."}
@@
 
-Several themes emerge from the terms newly identified in this analysis relative to the theoretical review.
-These themes bear considerable similarity to the results of Analysis 1.
-Developmental disorders and physical health are both recurring themes, but are ranked much lower in the present analysis.
-External stressors are another recurring theme, with indicators including PTSD, bullying, stress, abuse, historic events, and divorce.
-Finally, structural disadvantage recurs,
-as reflected in minority status and discrimination, disability status, socio-economic status, adoption status, sexual diversity, and the adorementioned developmental disorders.
-
-A new theme emerging from this analysis is addictive behavior, with highly ranked indicators *substance use* and *device use*.
-Another new theme pertains to identity and moral development, two topics with a common root in theory [@lapsleyMoralIdentityDevelopmental2015].
-This theme is also reflected by the terms *values* and *personality*.
-Finally, sexual development emerges as a theme. Aside from the high-ranking construct (biological) *sex*, this theme is reflected in the terms *puberty*, *sexual diversity*, and *romantic*.
-
 ```{r, echo = FALSE}
@@
 This second analysis focused on the abstracts of the reviewed articles.
+Several themes emerged from the terms newly identified in this analysis,
+relative to the theoretical review.
+These themes bear considerable similarity to the results of Analysis 1.
+Developmental disorders and physical health are both recurring themes, but are ranked much lower in the present analysis.
+External stressors are another recurring theme, with indicators including PTSD, bullying, stress, abuse, historic events, and divorce.
+Finally, structural disadvantage recurs,
+as reflected in minority status and discrimination, disability status, socio-economic status, adoption status, sexual diversity, and the adorementioned developmental disorders.
+
+A new theme emerging from this analysis is addictive behavior, with highly ranked indicators *substance use* and *device use*.
+Another new theme pertains to identity and moral development, two topics with a common root in theory [@lapsleyMoralIdentityDevelopmental2015].
+This theme is also reflected by the terms *values* and *personality*.
+Finally, sexual development emerges as a theme. Aside from the high-ranking construct (biological) *sex*, this theme is reflected in the terms *puberty*, *sexual diversity*, and *romantic*.
+
 We observed a sparser network, with fewer selected terms.
@@
 Thus, fewer terms will exceed the detection threshold.
-Nonetheless, the selected terms displayed substantial consistency with the
+Nonetheless, the remaining terms displayed substantial consistency with the
 analysis of author keywords.
@@
 again suggest that these phenomena are consistently studied together.
-By contrast, the lack of interconnectivity among other related constructs
-again suggests that the literature is somewhat fragmented.
-This impression is reinforced by the absence of many frequently occurring terms
+This makes sense, given the central role of emotion dyregulation in the etiology of diverse mental health problems [@leeAdolescentMentalHealth2014].
+This is in contrast to the lack of interconnectivity among other related constructs,
+which once more suggests that the literature is somewhat fragmented.
+This impression is further reinforced by the absence of many frequently occurring terms
 from the term co-occurrence graph.
@@
 The present study conducted a systematic review of the literature,
-and performed a text-mining based systematic review to map constructs related to adolescent emotion regulation in a nomological network.
+and performed a text-mining based systematic review to map constructs related to adolescent emotion regulation.
 The results of this inductive approach echoed many of the constructs considered
@@
 An important direction for future research would be to formalize these inductive insights into a new overarching theory of adolescent emotion regulation.
+In doing so, the co-occurrence graphs of relevant constructs arising from our inductive review may serve as a template for a nomological network:
+a proto-theoretical diagrammatic representation that describes relationships between
+constructs relevant to the theory.
+The generation of such nomological networks constitutes a first step in theory generation [see @alaviAligningTheoryMethodology2018].
 
@@
 
-<!-- RK: But please give us more content!
-Based on your meta-analysis, how would you move theory-formation forward?
-As the text stands now, this feels a bit empty.
-An that is a pity, given that in the intro you have beautifully sketched what theories we have.
-I think this paper would improve if you also explicitly mention what avenues are suggested by your meta-analysis.-->
-
 \newpage

### 2020-12-17 baseline.R

@@ -12,10 +12,10 @@ library(ggplot2)
 library(yaml)
 source("word_functions.R")
 source("circle2.R")
-run_everything = FALSE
+#run_everything = FALSE
 dict <- read_yaml("yaml_dict.txt")
 ## Look at POS tags?
-if(run_everything){
+if(TRUE){
   bl_theory <- readLines("baseline_theory.txt")
   bl_review <- readLines("baseline_reviews.txt")
   df <- data.frame(word = trimws(tolower(bl_theory)), source = "theory")

### 2020-12-17 study1.R

@@ -18,8 +18,11 @@ source("circle2.R")
 study1details <- read_yaml("study1_details.yml")
 dict <- read_yaml("yaml_dict.txt")
 ## Look at POS tags?
-if(run_everything){
+if(!isTRUE(tools::md5sum("study1_df.RData") == "042c7d894929b0351f804c1a4b5c5002")){
   recs <- data.table(read.csv("recs_final.csv"))
+  if(!is.data.table(recs)){
+    browser()
+  }
   recs[, "doc" := 1:nrow(recs)]
   study1details <- list(dim_recs = dim(recs))
   
@@ -134,7 +137,7 @@ if(run_everything){
 
 # LDA analysis ------------------------------------------------------------
 
-if(run_everything | !file.exists("Study1_lda_dims.txt")){
+if(!isTRUE(tools::md5sum("Study1_lda_dims.txt") == "4e2493d4d618020d4acde61dd7864425")){
   library(Rmpfr)
   library(topicmodels)
   library(udpipe)

### 2020-12-17 study2.R

@@ -1,9 +1,6 @@
+## ---- study2chunk ----
 library(data.table)
-#library(bibliometrix)
-#library(yaml)
 library(stringr)
-#library(lattice)
-#library(topicmodels)
 library(udpipe)
 library(igraph)
 library(wordcloud)
@@ -18,21 +15,21 @@ library(ggplot2)
 library(textrank)
 source("word_functions.R")
 source("circle2.R")
-run_everything <- FALSE
+#run_everything <- FALSE
 
 ## Look at POS tags?
-
-recs <- data.table(read.csv("recs_final.csv"))
-recs[, "doc" := 1:nrow(recs)]
-recs$AB <- tolower(recs$AB)
-
-# Detect languages not necessary; only one abstract is (partly) in Spanish.
-#library(cld3)
-#languages <- cld3::detect_language(recs$AB)
-#table(languages)
-#recs$AB[languages == "es"]
-
-if(run_everything){
+browser()
+if(isTRUE(tools::md5sum("study2_df.RData") == "21abb2622dfd94d8bd3473ed56697f9e")){
+  df <- readRDS("study2_df.RData")
+} else {
+  stop("Note: Study 2 file is out of date. Please run this code manually.")
+  recs <- data.table(read.csv("recs_final.csv"))
+  if(!is.data.table(recs)){
+    browser()
+  }
+  recs[, "doc" := 1:nrow(recs)]
+  
+  recs$AB <- tolower(recs$AB)
   if(!file.exists("english-ewt-ud-2.4-190531.udpipe")) {
     ud_model <- udpipe_download_model(language = "english")
   } else {
@@ -42,14 +39,12 @@ if(run_everything){
   udp_res <- udpipe_annotate(ud_model, x = recs$AB, doc_id = recs$doc)
   df <- as.data.table(udp_res)
   saveRDS(df, "study2_df.RData")
-} else {
-  df <- readRDS("study2_df.RData")
 }
 
 
 # LDA analysis ------------------------------------------------------------
 
-if(run_everything){
+if(!isTRUE(tools::md5sum("Study2_lda_dims.txt") == "2d00a24d8b54ac898eec6cd104086a0f")){
   # Functions:
   harmonicMean <- function(logLikelihoods, precision = 2000L) {
     llMed <- median(logLikelihoods)
[…]

### 2020-12-23 manuscript.Rmd
Prepare for JOYA

@@
   an integrating framework is lacking.
-  This systematic review of 6305 papers used text mining to map correlates of adolescents’ (ages 10-25) emotion dysregulation.
-First, we established a baseline of relevant terms gleaned from theory and recent narrative reviews.
-Then, we conducted two text mining analyses to examine term/document frequency and co-occurrence in author-provided keywords and abstracts.
-Results reﬂected constructs commonly featured in theory and narrative reviews, but also identified underrepresented themes.
-This research constitutes a first step towards integrating the literature, and illustrates how text mining reviews may complement narrative reviews.
-<!--may inspire future empirical and theoretical work.
-SH: I would end with a more memorable take-home about how text-mining can be useful to researchers (e.g., when topics are of multi-disciplinary interest but each field has their own preferred methods and/or terminology)-->
+  This systematic review of 6305 papers used text mining to map correlates of adolescents’ (ages 
+  10-25) emotion dysregulation. First, we established a baseline of relevant terms gleaned from 
+  theory and recent narrative reviews. Then, we conducted two text mining analyses to examine 
+  term/document frequency and co-occurrence in author-provided keywords and abstracts. Results 
+  reﬂected constructs commonly featured in theory and narrative reviews, but also identified 
+  underrepresented themes. This research constitutes a first step towards integrating the 
+  literature, and illustrates how text mining reviews may complement narrative reviews.
 
@@
 
-The present systematic review seeks to overcome these limitations by adopting a novel method:
+The present systematic review addressed these limitations by adopting a novel method:
 the text mining based systematic review.
@@
 
-The results of our text mining analysis of the empirical literature are best understood against a backdrop of the existing theoretical landscape.
+Our text mining analysis of the empirical literature is best understood against a backdrop of the existing theoretical landscape.
 We therefore provide a summary theoretical review.
 Other recent publications offer more detailed reviews of theories of emotional development [@bussTheoriesEmotionalDevelopment2019] and emotion regulation in adolescence [@riedigerEmotionRegulationAdolescence2014].
-The correlates of emotion regulation difficulties discussed in the theoretical review below
-are visually summarized in the left panel of Figure \@ref(fig:baseline)^[Based on an author-curated list of keywords, caterogized using the dictionary method introduced in Analysis 1.].
+The correlates of emotion regulation difficulties discussed in our theoretical review
+are summarized in Figure \@ref(fig:baseline)^[Based on an author-curated list of keywords, caterogized using the dictionary method introduced in Analysis 1.].
 
@@
 @arnettAdolescentStormStress1999]. It describes how `r keyw("hormonal")` changes diminish
-`r keyw("self-control")` and increase `r keyw("reactivity")`, leading to difficulties in emotion
-regulation, `r keyw("conflict with parents")`, and `r keyw("risky behavior")`.
-In modern theories, this notion of diminished self-control and increased emotional reactivity has been retained - although it is now considered to be a normative change that facilitates emotional maturation
+`r keyw("self-control")` and increase `r keyw("reactivity")`, leading to emotion
+dysregulation, `r keyw("conflict with parents")`, and `r keyw("risky behavior")`.
+This notion of diminished self-control and increased emotional reactivity persists in modern theory, but is now considered a normative change that facilitates emotional maturation
 [@croneUnderstandingAdolescencePeriod2012], at the risk of emotional
@@
 [@porgesOrientingDefensiveWorld1995].
-A more recent neurocognitive theory relevant to adolescents' emotion regulation development is Crone
-and Dahl's model of social-affective engagement and `r keyw("goal flexibility")`
-[@croneUnderstandingAdolescencePeriod2012]. Like other authors 
+More recently, in their model of social-affective engagement and `r keyw("goal flexibility")`
+<!--. Like other authors 
 [e.g., @caseyBrakingAcceleratingAdolescent2011; @craccoEmotionRegulationChildhood2017],
-Crone and Dahl argue that the developmental
+Crone and Dahl--> Crone and Dahl [-@croneUnderstandingAdolescencePeriod2012] posited that the developmental 
 asymmetry between `r keyw("motivational")` and inhibitory `r keyw("brain")` circuits gives rise to a
 "maturity gap" in middle adolescence. 
-What distinguishes Crone and Dahl from related writings
-is the greater attention to adolescents' diverging destinies:
-the question why some youngsters flourish while others languish.
+What distinguishes Crone and Dahl from related writings [e.g., @craccoEmotionRegulationChildhood2017]
+is the emphasis on adolescents' diverging destinies;
+why some youngsters flourish while others languish.
 They argue that adolescents' cognitive engagement is dynamically responsive to
-social and motivational `r keyw("goal salience")`. This flexibility, on the one hand,
-prepares adolescents to effectively engage cognitive systems in novel
-challenging situations in a way that facilitates developing mature regulatory
-abilities. On the other hand, it places them at risk to act impulsively in
+social and motivational `r keyw("goal salience")`.
+This flexibility <!--, on the one hand,-->
+prepares adolescents to <!--effectively engage cognitive systems in novel
+challenging situations in a way that facilitates--> develop mature regulatory
+abilities, but also places them at risk of impulsivity in
 pursuit of `r keyw("peer approval")`. In terms of explanans,
@@
 and the role of peers, with less attention to factors such as parenting.
-Although this theory focuses on adolescence specifically,
-an important limitation is that it only tangentially relates to emotion regulation.
-
-Other theories emphasize socialization to a greater extent.
-One such theory is Morris' tripartite model, which focuses specifically on `r keyw("parents")`' role in emotion regulation development [-@morrisRoleFamilyContext2007].
+This theory is relevant because it focuses on adolescence specifically,
+but only tangentially addresses emotion regulation.
+
+Other theories emphasize socialization to a greater extent,
+such as Morris' tripartite model, which focuses on `r keyw("parents")`'
+role in emotion regulation development [-@morrisRoleFamilyContext2007].
 It describes three pathways through which parents shape emotion regulation
-development: Through observation and `r keyw("modeling")`, `r keyw("parenting practices")`, and the
-emotional `r keyw("family climate")`, which in turn involves attachment and `r keyw("marital
-relationship")` quality. Morris and colleagues emphasize the relevance of `r keyw("mothers")`, 
+development: `r keyw("modeling")`, `r keyw("parenting practices")`, and the
+emotional `r keyw("family climate")`,
+which subsumes attachment and `r keyw("marital relationship")` quality.
+Morris emphasizes the relevance of `r keyw("mothers")`, 
 `r keyw("fathers")`, and siblings.
-Others have adapted the tripartite model to describe
-the role of peers in adolescents' emotion regulation development
+Others have adapted the tripartite model to describe peers' role in emotion regulation socialization
 [@reindlSocializationEmotionRegulation2016].
@@
 internalization model of emotional development. 
-Unique aspects emphasized in this theory are the interplay between emotion and `r keyw("communication")`,
+Hallmarks of this theory are the interplay between emotion and `r keyw("communication")`,
 and the internalization of the `r keyw("cultural")` symbolic function of emotion.
-These theories explain the process of socialization in great detail,
-but one potential limitation is that they are not embedded in a larger unifying framework.
+Several theories thus explain emotion regulation socialization in detail,
+but a potential limitation is that they are not embedded in a larger unifying framework.
 <!--Like Sroufe, Holodynski describes an age graded transition from
@@
 
-Looking beyond the developmental literature,
-theories of the phenomenon of emotion regulation offer additional insight into
+Theories of the phenomenon of emotion regulation offer insight into
 intra-individual drivers of emotion regulation development.
-Perhaps the most influential theory is Gross'
-[-@grossHandbookEmotionRegulation2013] process model, which describes the
-process of emotion regulation from eliciting cue to ultimate response.
+Gross' [-@grossHandbookEmotionRegulation2013] influential process model describes the
+phenomenon of emotion regulation, from eliciting cue to ultimate response.
 According to Gross, individuals use `r keyw("strategies")` to modulate the different stages of this process,
-consciously or otherwise. `r keyw("Culture")` plays a role too, as the effectiveness, desireability, and consequences of different strategies depend on the social context [see
-@bariolaChildAdolescentEmotion2011]. Similar to Gross' theory, the social
-information processing theory of emotion also describe the role of cognitive
-processes and strategies in emotion experience and regulation
+consciously or otherwise. The effectiveness, desireability, and consequences of some strategies vary across `r keyw("culture")`s [see
+@bariolaChildAdolescentEmotion2011].
+Similar to Gross' theory, the "social
+information processing" theory also describes the role of cognitive
+processes and strategies in emotion regulation
 [@lemeriseIntegratedModelEmotion2000].
+One limitation of these theories in the present context is the lack of a developmental component.
 
@@
 transactional model.
-Bronfenbrenner's model
-[@bronfenbrennerBioecologicalModelHuman2007] describes how the `r keyw("environment")`
-shapes individual development. Each individual is imbued with certain
-`r keyw("biological")` predispositions, and develops over time, in interaction with
-contextual influences. These influences range from the microsystem, composed of
-those people close to the individual, to the macrosystem, consisting of
-indirect `r keyw("political")` and `r keyw("economic")` influences, to the exosystem, consisting of
-cultural norms and values. Sameroff's model is somewhat compatible with the
-bioecological model [@sameroffUnifiedTheoryDevelopment2010], but focuses more
-on the interplay between nature and nurture. It conceptualizes development as a
-product of reciprocal influences between the child and the environment.
-Sameroff distinguishes between proximal influences, for instance, through
-parents (the microsystem in Bronfenbrenner's model), and distal influences;
-structural factors indirectly shaping development, like socio-economic status,
-`r keyw("schools")`, and the `r keyw("community")` (macro- and exosystem). With increasing age, distal
-influences gradually gain ground on proximal influences.
+Bronfenbrenner [-@bronfenbrennerBioecologicalModelHuman2007] describes how the `r keyw("environment")`
+shapes individual development.
+Each individual is imbued with `r keyw("biological")` predispositions,
+and develops in interaction with contextual influences.
+These influences range from the microsystem,
+composed of people close to the individual,
+to the macrosystem, consisting of `r keyw("political")` and `r keyw("economic")` influences,
+to the exosystem, consisting of `r keyw("cultural")` norms and `r keyw("values")`.
+Sameroff's model [-@sameroffUnifiedTheoryDevelopment2010] is compatible with Bronfenbrenner's work,
+but focuses more on the interplay between nature and nurture.
+It conceptualizes development as a product of reciprocal influences between child and environment.
+Sameroff distinguishes proximal influences such as parents (the microsystem in Bronfenbrenner's model)
+from distal influences;
+structural factors indirectly shaping development, like `r keyw("socio-economic status")`,
+`r keyw("schools")`, and the `r keyw("community")` (macro- and exosystem).
+With increasing age, distal influences gain ground on proximal influences.
 These theories are broad enough to contextualize any developmental study,
@@
 Despite the abundance of theory *relevant* to emotion regulation in adolescence,
-the theoretical literature has several limitations.
-First, few theories have explicitly addressed the life stage of adolescence. This life stage differs qualitatively from infancy, childhood, and adulthood [@bariolaChildAdolescentEmotion2011].
-It is therefore questionable whether more general theories, or those focused on different age groups, can be generalized to adolescents.
+the literature has several limitations.
+First, few theories have explicitly addressed adolescence.
+This life stage differs qualitatively from both childhood and adulthood [@bariolaChildAdolescentEmotion2011].
+It is therefore questionable whether theories focused on different age groups can be generalized to adolescents.
 <!--Relatedly, many relevant theories lack an explicit developmental component, which renders them and thus lack a well-substantiated
@@
 and none directly guide contemporary research in the field [see @bussTheoriesEmotionalDevelopment2019; @riedigerEmotionRegulationAdolescence2014].
-Finally, available theories vary widely in scope:
-Some are broad but somewhat non-specific, and others describe a specific phenomenon in detail,
+Finally, existing theories vary widely in scope:
+Some are broad and non-specific; others describe a specific phenomenon in detail,
 but lack a broader perspective.
@@
 
-Whereas theory provides a top-down frame of reference for understanding a phenomenon,
-literature reviews can provide a bottom-up, inductive understanding.
+Whereas theory provides a top-down frame of reference,
+literature reviews can provide a bottom-up, inductive understanding of a phenomenon.
 Given the noted absence of a single overarching theory, reviews might provide additional
@@
 We will therefore examine how two excellent narrative reviews on emotion regulation in adolescence complement the aforementioned theoretical literature [@coe-odessEmergentEmotionsAdolescence2019; @bariolaChildAdolescentEmotion2011].
-The right panel of Figure \@ref(fig:baseline) visually distinguishes constructs  uniquely covered by these narrative reviews,
-relative to the issues also addressed in the theoretical literature (left panel).
+Figure \@ref(fig:baseline) visualizes constructs uniquely covered by these narrative reviews,
+relative to the theoretical literature.
 
@@
 
-The seminal review by
-@bariolaChildAdolescentEmotion2011 addresses individual psychological factors
+A seminal review by
+@bariolaChildAdolescentEmotion2011 addressed intra-individual factors
 such as temperament, and biological factors like neurocognitive development and
-genetic predispositions. Furthermore, the authors address proximal social influences,
-including parents, teachers, and peers, and specific mechanisms through which
-these individuals exert their influence, including parenting and modeling.
-Finally, they address distal factors, including the role of culture and the
-media. Barriola and colleagues also 
-<!--most notably, they call for a robust theoretical framework to guide future
-research.--> call for future research to address parents' role beyond early
-childhood.
-They further argued that the role of fathers in emotion socialization warrants further scrutiny - a topic that is now receiving more attention [e.g., see @vanlissaRoleFathersMothers2019;
+genes.
+Proximal social influences covered include socialization and modeling by parents, teachers, and peers.
+Finally, distal factors include the role of culture and the
+media.
+Barriola and colleagues made several suggestions for future research,
+calling for a robust theoretical framework to guide future
+research, for research on parents' role beyond early childhood,
+and for additional work on the role of fathers in emotion socialization.
+The latter two topics are now receiving more attention [e.g., see @vanlissaRoleFathersMothers2019;
 @vanlissaMothersFathersQuantitative2020].
 
-A more recent review by @coe-odessEmergentEmotionsAdolescence2019 offers a nuanced
-discussion of several issues that complement prior publications in this field.
-For instance, the authors cover the implications of physiological changes in
-detail, including neurocognitive development and pubertal maturation. As
-adolescents become increasingly individuated, conflict with parents peaks. This
-conflict, in turn, impacts emotion regulation, both in terms of day-to-day mood
-variability and dispositional emotion dysregulation [see also
+A recent review by @coe-odessEmergentEmotionsAdolescence2019 offers a nuanced
+discussion of several issues that complement prior publications.
+This includes the implications of physiological changes,
+including neurocognitive development and pubertal maturation.
+Conflict with parents is addressed too, which peaks when adolescents become increasingly individuated.
+Such conflict impacts both day-to-day mood swings and dispositional emotion dysregulation [see also
 @vanlissaCostEmpathyParentadolescent2017].
-Compared to children, adolescents also become increasingly oriented towards peers.
-This includes increased
-sensitivity to social status and norms, along with the associated increase in
-peer pressure and risk taking. Pubertal development also initiates the
-emergence of sexual and romantic behavior, and the intensification of both
-biological sex differences and gender stereotyped behavior. With regard to the
-process of emotion regulation, Coe-Odess and colleagues discuss the importance
+Adolescents also become increasingly oriented towards peers.
+This increases sensitivity to social status and norms,
+along with concomitant increases in peer pressure and risk taking.
+Pubertal development further precipitates sexual and romantic behavior,
+and the intensification of both biological sex differences and gender stereotyped behavior.
+<!--With regard to the process of emotion regulation,
+Coe-Odess and colleagues discuss the importance
 of strategies, and point out that, in addition to negative emotionality,
-positive emotionality also peaks in adolescence. Relatedly, the authors
-describe how hormonal changes precipitate an increased stress response, which
-might help explain adolescents' greater susceptibility to emotion
-dysregulation. Finally, going beyond the implications of cognitive development
-discussed in other publications, the authors discuss how an greater capacity
-for abstract thought relates to identity formation - a key challenge in
+positive emotionality also peaks in adolescence. -->
+Relatedly, the authors describe how hormonal changes intensify the stress response,
+which helps explain adolescents' greater susceptibility to emotion dysregulation.
+Finally, <!--going beyond the implications of cognitive development
+discussed in other publications,--> the authors discuss how cognitive development and increased capacity
+for abstract thought relate to identity formation - a key challenge in
 adolescence [@meeusStudyAdolescentIdentity2011] - and to increased emotional
@@
 As can be seen in Figure \@ref(fig:baseline), 
-there are notable parallels between the relevant factors highlighted by these
-narrative reviews, and the aforementioned theoretical literature.
+there are notable parallels between correlates of emotion regulation identified in these
+narrative reviews, and in the preceding theoretical literature.
 Nevertheless,
@@
 attention in theoretical work.
-These include specific individual differences at the biological and psychological level, including genetic predisposition, hormones, pubertal onset, gender, sexuality, temperament, identity, empathy, and stress.
-Further introduced are proximal influences, including the role of media, norms, and social status.
+<!--These include specific individual differences at the biological and psychological level, including genetic predisposition, hormones, pubertal onset, gender, sexuality, temperament, identity, empathy, and stress.
+Further introduced are proximal influences, including the role of media, norms, and social status.-->
 This illustrates that reviews of the empirical literature can contribute additional insight into key factors in adolescents' emotion regulation development.
-However, an important remaining limitation is that all reviews in this field have been unstructured narrative reviews, which are known to be limited in scope and biased [@littellEvidencebasedBiasedQuality2008].
+An important limitation is that all reviews in this field have been unstructured narrative reviews, which are known to be limited in scope and biased [@littellEvidencebasedBiasedQuality2008].
 We seek to complement preceding work by using text mining to conduct a more comprehensive empirical
@@
 contstructs as potential predictors or outcomes.
-<!--, and we categorize predictors
-by level of analysis-->
-<!-- (CJ: Sameroff, which level of biopsychosocial)-->.
-<!-- t, using text mining to map potential predictors of adolescent emotion
-dysregulation.
-identify relevant constructs of adolescents’ emotion regulation development,
-and moderators of parents’ role therein. The resulting insights are
-consolidated into theory.
-The present study intends to map the extant literature
-First, I will systematically review predictors currently considered relevant in
-the adolescent emotion regulation literature.  -->
+We used the Workflow for Open Reproducible Code in Science (WORCS)
+to ensure transparency and  reproducibility. All code and data are available online at [masked].
 
@@
 
-All searches were conducted on Web of Science,
-the most comprehensive database for which we had permissions for exporting keywords and abstracts.
+We searched Web of Science,
+the most comprehensive database for which we had permissions to export keywords and abstracts.
 The search strategy was based on
 procedures described by Staaks [@staaksSystematicReviewSearch]. First, we
-manually constructed a reference set of 15 articles. Then we constructed a
-search string to retrieve these articles from Web of Science. The search was
-overly inclusive, returning 29 records.
-As these were all highly relevant, we
-updated the reference set to include all 29 results.
-Next, we tested our search string, which consisted of synonyms of emotion regulation and adolescence: <!--
-### Reference set Our reference set is documented in `reference_set.bib`. -->
-```
-TS=("emotio* regulation" OR "anger regulation" OR "sadness regulation" OR
-"emotion* competence" OR "emotion* adjustment" OR "emotio* dysregulation" OR
-"anger dysregulation" OR "sadness dysregulation" OR "emotio* problem*" OR
-"emotion* maladjustment") AND TS=(adolescent* OR teen* OR pubert* OR youth)
-```
-This string returned 6653 results, and matched 25 of the 29 records in the
-reference set. To match all 29 reference set items,
-three additional terms would have to be added to the search string.
-Adding the terms `"emotio* socialization" OR "emotio* processes"`, as synonyms for emotion regulation,
-would result in 191 more hits, most of which did not meet the inclusion criteria used for screening, as explained below.
-Adding the term `"development*"`, as synonym of adolescence, added 3628 new hits,
-many of which were not focused on adolescence.
+constructed a reference set of 29 articles.
+Then we constructed a search string to retrieve this set.
+The search string consisted of synonyms of emotion regulation and adolescence.
+It returned 6653 results, including 25 records in the reference set.
+To match all 29 reference set items required adding the terms `"emotio* socialization" OR "emotio* processes"` as synonyms for emotion regulation.
+Doing so resulted in 191 more hits, most of which did not meet the inclusion criteria explained below.
 We thus deemed these terms to be overly inclusive, and
@@
 
-## Deduplication
-
 ```{r removeduplicates}
@@
 ```
-Duplicates were identified based on exact DOI matches (`r dups[["dup_doi"]]` 
-duplicates), and title similarity (`r dups[["dup_title"]]` duplicates). 
-Manual screening in Rayyan resulted in the removal of an additional `r rayyan_dups` duplicates.
 
@@
 ```
+The screening and deduplication procedure is detailed in Figure \@ref(fig:prismachart).
+Duplicates were identified using DOI and title similarity.
 Papers were screened based on two main criteria:
-First, papers had to address emotion regulation or a synonymous construct.
-Second, the target population must overlap with the life stage of adolescence,
-defined as the age range from 10-24.
-Thus, for example, an article reviewing the role of hormonal changes in emotional adjustment throughout the entire life course, including adolescence, would be deemed relevant.
+They had to address emotion regulation or a synonymous construct, and the target population must overlap with the age range of adolescence (10-24).
 Preliminary screening was conducted in Rayyan QRCI [@Ouzzani2016].
-Papers were sorted using Rayyan's ranking algorithm.
-To train the algorithm on exclusion criteria, screening focused on abstracts most likely to be excluded.
-After coding `r sum(screen$rayyan == "True")+sum(screen$rayyan == "False")` papers, screening continued in ASReview - a free, open source alternative to Rayyan QRCI [@van_de_schoot_rens_2020_3828293].
-This program uses active learning to build a customizable machine learning model for article inclusion.
-We used a naive Bayes model, and focused on exclusion of irrelevant papers.
-In ASReview, an additional `r sum(table(screen$included, screen$rayyan)[, 1])` papers were screened.
-Screening again focused on articles most likely to be excluded, and continued until, among the most recently screened 100 papers, only 6 were excluded.
-The screening procedure is detailed in Figure \@ref(fig:prismachart).
-In total, `r nrow(recs_final)` papers were retained for analysis.
+After coding `r sum(screen$rayyan == "True")+sum(screen$rayyan == "False")` papers, screening continued in ASReview [@van_de_schoot_rens_2020_3828293].
+This program uses machine learning to screen articles.
+We trained the machine learning algorithm by manually screening an additional `r sum(table(screen$included, screen$rayyan)[, 1])` papers, until - among the most recently screened 100 papers - only 6 were excluded.
+In total, `r nrow(recs_final)` papers were deemed suitable for analysis.
 
 ```{r prismachart, results='asis', fig.cap="Record screening flowchart"}
+if(!isTRUE(tools::md5sum("prismachart.png") == "08351426aee2005edd1332a32b958ea0" )){
   library(tidySEM)
@@
   ggsave("prismachart.svg", p, device = "svg")
+}
+
 knitr::include_graphics("prismachart.png")
@@
   df_plot <- word_freq
+  df_plot <- df_plot[order(df_plot$Frequency, decreasing = TRUE), ]
   categ <- read.csv("study1_categorization.csv", stringsAsFactors = FALSE)
@@
   df_plot$faded <- df_plot$Word %in% baseline
+  # Tag words that are not in the cooccurrence graph
+  in_graph <- row.names(read.csv("s1_cooc.csv", row.names = 1))
+  notingraph <- !df_plot$Word %in% in_graph
+  italic_labels <- as.character(df_plot$Word)
+  italic_labels[notingraph] <- sapply(italic_labels[notingraph], function(x){
+    parse(text = paste0("italic('", x, "')"))
+  })
+  # Prettify words
   df_plot$Word <- pretty_words(df_plot$Word)
 
-  df_plot <- df_plot[order(df_plot$Frequency, decreasing = TRUE), ]
   df_plot$Word <- ordered(df_plot$Word, levels = df_plot$Word[order(df_plot$Frequency)])
@@
     geom_segment(aes(x = 0, xend = Frequency,
-                     y = Word, yend = Word, linetype = faded), colour = "grey50"
+                     y = Word, yend = Word, linetype = notingraph), colour = "grey50"
     ) + 
@@
     scale_x_log10() +
-    scale_linetype_manual(values = c("TRUE" = 2, "FALSE" = 1), guide = NULL) +
+    #scale_y_discrete(labels = italic_labels) +
+    scale_linetype_manual(values = c("TRUE" = 3, "FALSE" = 1), guide = NULL) +
     theme_bw() + theme(panel.grid.major.x = element_blank(),
@@
 
-The corpus for this first analysis consisted of the author-provided keywords for the selected articles.
-We extracted keywords by document, and used a dictionary
-created specifically for this study to classify related terms.
+The corpus for this first analysis consisted of author-provided keywords.
+We extracted keywords by document, and applied an exclusion filter of methodological terms and similar non-substantive words.
+Then, we used a dictionary to classify related terms.
 The dictionary describes `r length(dict)` terms using `r length(unlist(dict))`
 regular expression queries.
-The author composed a first draft of the dictionary.
-This draft was subsequently updated in two ways:
-First, key terms from the literature were added to the dictionary while writing the Introduction.
-Second, all frequently occurring uncategorized words were added to the dictionary, until none remained.
-An exclusion list of methodological terms and other non-substantive words was generated using the same procedure.
-After applying the dictionary and exclusion filter,
-and removing records with no (remaining) keywords,
-the resulting corpus consisted of `r number_docs_words[1]` documents with `r number_docs_words[2]` unique terms.
-<!--As term-document frequency is irrelevant in the context of keywords (i.e., keywords should not occur twice within the same document, except when two synonyms have been recoded using the dictionary),
-the term-document matrix was dichotomized.-->
+The resulting term-document matrix consisted of `r number_docs_words[1]` documents with `r number_docs_words[2]` unique terms.
 
@@
 <!-- it might be useful to insert a sentence or two when you are using a method many readers are not familiar with, just to explain the utility of the chose method (what it does/doesn't do potentially as compared to other options)-->
-One important step before reviewing the literature is to examine heterogeneity in the corpus of collected texts.
-For example, it would be useful to know whether there is a clear divide between psychiatric and developmental texts.
-To empirically test for heterogeneity, we conducted topic modeling using latent dirichlet allocation [@bleiLatentDirichletAllocation2003].
-This is a clustering method suitable to high-dimensional sparse feature matrices.
-In this case, the features are author keywords.
+One important step before reviewing the literature is to examine heterogeneity in the corpus;
+for example, whether there is a clear divide between psychiatric and developmental texts.
+To test for heterogeneity, we conducted topic modeling using latent dirichlet allocation [@bleiLatentDirichletAllocation2003].
+This is a clustering method for large sparse matrices.
 We used the term frequency/inverse document frequency (TF-IDF) to select terms
@@
 This resulted in `r dtm_top[2]` terms, which occurred in `r dtm_top[1]` documents.
-To illustrate what issues are covered in this body of literature, the selected terms are displayed in Figure \@ref(fig:study1varimp), on a logarithmic scale to reduce the skew of the negative binomial distribution.
+The issues covered in this body of literature are visualized in Figure \@ref(fig:study1varimp).
 
 ```{r study1varimp, warning=FALSE, eval = TRUE, results='asis', out.width = "100%", fig.cap="Document frequency of terms selected for Study 1.
-Dashed lines and transparent circles indicate constructs also represented in the theory (cf Figure 1)."}
+Transparent circles indicate constructs represented in theory (Figure 1), dotted lines indicate constructs absent from the co-occurrence graph."}
 knitr::include_graphics("s1_varimp.png") 
@@
 
-Based on our theoretical review, each of the selected terms was coded as being either a putative 'Cause', 'Outcome', 'Protective factor', or 'Indicator' (a closely related construct) of emotion dysregulation.
-We stress that this is a subjective and rudimentary classification,
-intended only to stimulate further reflection on the role of each construct.
-We acknowledge that many of these associations are likely to be bidirectional [e.g., emotion dysregulation is known to be both a cause and consequence of conflict with parents, @vanlissaCostEmpathyParentadolescent2017].
 Next, we computed a term co-occurrence matrix,
-which represents how frequently words occurred within the same document.
-To aid interpretability, we again pruned small coefficients by
-modeling co-occurrence using a negative binomial distribution,
-and retaining co-occurrences exceeding the $97.5^{th}$ percentile.
-Figure \@ref(fig:study1network) displays the term cooccurrence matrix as a force directed graph.
-
-```{r study1network, warning=FALSE, out.width = "100%", fig.cap="Force directed graph for Study 1 co-occurrence analysis.
+which represents how frequently words occurred within the same document (see Figure \@ref(fig:study1network)).
+To aid interpretability, we again pruned small coefficients using a negative binomial distribution,
+retaining co-occurrences exceeding the $97.5^{th}$ percentile.
+To stimulate further reflection on the role of each construct,
+we manually classified each of the selected terms as either a putative 'Cause', 'Outcome', 'Protective factor', or 'Indicator' of emotion dysregulation.
+We stress that this classification is subjective and acknowledge that many of these associations are likely to be bidirectional [e.g., emotion dysregulation is known to be both a cause and consequence of conflict with parents, @vanlissaCostEmpathyParentadolescent2017].
+
+```{r study1network, warning=FALSE, out.width = "100%", fig.cap="Study 1 term co-occurrence.
 Two layouts are presented to aid interpretation.
-Size of nodes and edges represents word/co-occurrence frequency.
+Size of lines and circles represents frequency.
 Dashed lines represent links not involving dysregulation.
@@
 
-Based on term document frequency (Figure \@ref(fig:study1varimp)), it is clear that emotion dysregulation and its mental health-related outcomes are foremost among the common terms in the corpus. 
+Emotion dysregulation and its mental health-related outcomes were foremost among the common terms in the corpus (Figure \@ref(fig:study1varimp)). 
 Other frequent terms reflect important themes discussed in the theoretical review of the literature;
@@
 Based on the co-occurrence graph (Figure \@ref(fig:study1network)),
-it is evident that 
-emotion dysregulation is a central construct,
-and that most of the other constructs are linked directly to emotion dysregulation,
-which suggests that our search was successful in identifying factors considered to be relevant
-for adolescents' emotion dysregulation.
-Otherwise, the graph is relatively sparse, with few interconnections between terms.
+emotion dysregulation is evidently a central construct
+to which most other constructs are directly linked.
+This suggests that our search successfully identified factors relevant for adolescents’ emotion dysregulation.
+The remaining graph is notably sparse, with few interconnections between terms.
 
@@
 
-In addition to the themes addressed in the theoretical introduction,
-several novel themes emerge from the terms newly identified in this analysis.
+In addition to the themes addressed in the theoretical Introduction,
+several novel themes emerge from this analysis. 
 Developmental disorders constitute such a theme, as ADHD/CD and autism are ranked highly.
@@
 
-In terms of the co-occurrence network, connections among topics were notably sparse.
-Many constructs were only related to emotion regulation,
+The co-occurrence graph revealed few connections among topics.
+Many constructs were only linked with emotion regulation,
 and there were relatively few interconnections between elements.
@@
 # Analysis 2: Abstract text mining
-
-```{r}
-source("word_functions.R")
-source("circle2.R")
-```
 
@@
 library(textrank)
+source("word_functions.R")
+source("circle2.R")
 
@@
   df_plot$faded <- df_plot$Word %in% baseline
+  # Tag words that are not in the cooccurrence graph
+  in_graph <- row.names(read.csv("s2_cooc.csv", row.names = 1))
+  notingraph <- !df_plot$Word %in% in_graph
+  italic_labels <- as.character(df_plot$Word)
+  italic_labels[notingraph] <- sapply(italic_labels[notingraph], function(x){
+    parse(text = paste0("italic('", x, "')"))
+  })
   df_plot$Word <- pretty_words(df_plot$Word)
 
-  df_plot <- df_plot[order(df_plot$Frequency, decreasing = TRUE), ]
   df_plot$Word <- ordered(df_plot$Word, levels = df_plot$Word[order(df_plot$Frequency)])
@@
 To assess the homogeneity of the corpus of abstracts,
-we again conducted topic modeling with features selected based on TF-IDF, following the same procedure as in Analysis 1 [@bleiLatentDirichletAllocation2003].
-The dataset consisted of `r lda_dims_2[1]` documents and `r lda_dims_2[2]` terms.
-As before, the BICs followed a near-perfect linearly increasing trend, and all entropies were near-zero.
-Thus, no interpretable subcorpora could be identified,
-and we proceed with an analysis of the whole sample.
+we again conducted topic modeling,
+following the procedure described in Analysis 1.
+The data comprised `r lda_dims_2[2]` terms in `r lda_dims_2[1]` documents.
+As before, the BICs followed a linearly increasing trend, and entropies were near-zero.
+Thus, no subcorpora were identified,
+and we proceed with a whole sample analysis.
 
@@
 ```{r study2varimp, eval = TRUE, out.width = "100%", results='asis', fig.cap="Document frequency of terms selected for Study 2.
-Dashed lines and transparent circles indicate constructs also represented in the theory (cf Figure 1)."}
+Transparent circles indicate constructs represented in theory (Figure 1), dotted lines indicate constructs absent from the co-occurrence graph."}
 knitr::include_graphics("s2_varimp.png") 
@@
 
-```{r study2network, out.width = "100%", fig.cap="Force directed graph for Study 2 co-occurrence analysis.
+```{r study2network, out.width = "100%", fig.cap="Study 2 term co-occurrence.
 Two layouts are presented to aid interpretation.
-Size of nodes and edges represents word/co-occurrence frequency.
+Size of lines and circles represents frequency.
 Dashed lines represent links not involving dysregulation.
@@
 
-Based on term document frequency, it is clear that emotion dysregulation and its mental health-related outcomes are among the most common terms in the corpus of abstracts.
-The term *neural* again occurred frequently, but other top terms were somewhat less predictable than those emerging in Analysis 1.
-The term *sex* was more frequent than in Analysis 1, suggesting sex differences are regularly reported in Abstracts, even if they are not a main topic of the study.
+Based on term document frequency, there was substantial agreement between the findings of Analysis 1 and 2;
+$`r oneintwo`\%$ of the most frequent terms identified in the author keywords
+were also present in the abstracts,
+and conversely, $`r twoinone`\%$ of the most frequent terms from the abstracts were present in the keywords.
+In the corpus of abstracts,
+emotion dysregulation and its mental health outcomes were evidently the most common terms.
+The term *neural* again occurred frequently.
+The term *sex* was more frequent than in Analysis 1,
+suggesting that sex differences are regularly reported in Abstracts.
 The term *parenting*, which ranked highly in the preceding keyword Analysis, was displaced by *mothers* amonst the top-ranking terms.
 This suggests that when the keyword *parenting* is used,
-the abstract will often reveal that this was operationalized in terms of mothering [as also noted by @pleckPaternalInvolvementRevised2004].
-
-There was substantial agreement between the findings of Analysis 1 and 2;
-$`r oneintwo`%$ of the most frequent terms identified in the author keywords (Analysis 1)
-were also present in the abstracts (Analysis 2),
-and conversely, $`r twoinone`%$ of the most frequent terms from Analysis 2 were present in Analysis 1.
+the abstract will often reveal that this was operationalized in terms of mothering [as noted by @pleckPaternalInvolvementRevised2004].
 
@@
 connected directly to dysregulation.
-
-Many prevalent terms were entirely absent from the co-occurrence network (Figure \@ref(fig:study2network)),
+Many prevalent terms were absent from the co-occurrence graph,
 as they were not strongly related to any other terms. 
-These terms, which are displayed in Figure \@ref(fig:study2varimp), include the potential causes `r notingraph["Cause"]`, the potential outcomes `r notingraph["Outcome"]`, and the potential protective factors `r notingraph["Protective"]`.
+These terms include the potential causes `r notingraph["Cause"]`, the potential outcomes `r notingraph["Outcome"]`, and the potential protective factors `r notingraph["Protective"]`.
 
@@
 Finally, structural disadvantage recurs,
-as reflected in minority status and discrimination, disability status, socio-economic status, adoption status, sexual diversity, and the adorementioned developmental disorders.
+as reflected in minority status and discrimination, disability status, socio-economic status, adoption status, sexual diversity, and the aforementioned developmental disorders.
 
@@
 This issue is beyond the scope of the present study -->
-The present study conducted a systematic review of the literature,
-and performed a text-mining based systematic review to map constructs related to adolescent emotion regulation.
+The present study systematically reviewed the literature,
+and used text-mining to map constructs related to adolescent emotion regulation.
 The results of this inductive approach echoed many of the constructs considered
@@
 Additional insight can be gleaned from the structure of the co-occurrence graphs.
-First, both analyses revealed close connections between emotion regulation and mental health-related outcomes.
-This is consistent with the fact that emotion regulation is implicated in the etiology of a range of mental health problems [see @leeAdolescentMentalHealth2014].
+First, both analyses revealed close ties between emotion regulation and mental health-related outcomes.
+This is consistent with emotion regulation's putative implication in the etiology of various mental health problems [see @leeAdolescentMentalHealth2014].
 It further emphasizes the societal relevance of this field of research.
-Both analyses further revealed that most constructs were connected
-directly with emotion dysregulation or its mental health correlates,
-with few interconnections amongst constructs.
+Both analyses further revealed that most constructs were
+directly tied to emotion dysregulation or its mental health correlates,
+with few connections among constructs.
 This sparse property of the networks echoes the sentiment by @bussTheoriesEmotionalDevelopment2019
 that the literature is somewhat fragmented.
-By conducting a comprehensive review using a somewhat objective method (relative to narrative reviews),
-the present study takes a first step towards integrating this diffuse field.
+The present study takes a first step towards integrating this diffuse field
+by using a relatively comprehensive and objective method, compared to narrative reviews.
 An important future direction for research might be to jointly investigate disconnected constructs, as the lack of connections in the graph indicates a potential knowledge vacuum.
@@
 This limitation is best addressed by considering the output of our text mining analysis as a starting point for further inductive thought or a more in-depth reading of a particular subset of the literature.
-Throughout this paper, we have offered our interpretation of the results - but we also encourage readers to reflect on the objective results presented here (i.e.: which terms are common, and how these terms are connected), and use these results as impetus for independent inductive reflection, and inspiration for future deductive research.
+Throughout this paper, we have offered our interpretation of the results -
+but we also encourage readers to use these results as impetus for independent reflection,
+and inspiration for future deductive research.
 A related limitation is that our methods do not capture the nature of the relationship between co-occurring terms.
@@
 and has increasingly come to represent paternal influence as well. -->
-
-One final limitation of the present study is that our analysis was limited to keywords and abstracts.
+One final limitation is that our analysis was limited to keywords and abstracts.
 Analysis of full-text papers would undoubtedly yield additional insights.
@@
 With comprehensive open access publishing, we may one day be able to mine the entire published literature for insights.
-A proof of concept for this approach was recently provided by the release of 50k+ full-text papers on topics related to COVID-19 for text mining analysis [@wangCORD19Covid19Open2020].
+The recent release of 100k+ full-text papers on COVID-19 for text mining analysis on <kaggle.com> is proof of concept for this approach.
 

### 2021-01-28 manuscript.Rmd
revisions

@@
 ---
-title             : "Mapping correlates of adolescent emotion dysregulation: A text-mining based systematic review"
-shorttitle        : "ADOLESCENT EMOTION DYSREGULATION"
+title             : "Mapping correlates of adolescent emotion regulation: A text-mining based systematic review"
+shorttitle        : "ADOLESCENT EMOTION REGULATION"
 
@@
 abstract: |
-  Adolesence is a developmentally sensititve period for emotion dysregulation.
+  Adolesence is a developmentally sensititve period for emotion regulation.
   Although substantial empirical research has addressed relevant risk factors,
@@
   This systematic review of 6305 papers used text mining to map correlates of adolescents’ (ages 
-  10-25) emotion dysregulation. First, we established a baseline of relevant terms gleaned from 
+  10-25) emotion regulation. First, we established a baseline of relevant terms gleaned from 
   theory and recent narrative reviews. Then, we conducted two text mining analyses to examine 
@@
   literature, and illustrates how text mining reviews may complement narrative reviews.
-
+keywords          : "emotion regulation, adolescence, systematic review, text mining, machine
+learning"
 wordcount         : "6311"
@@
 library(cowplot)
-run_everything <- TRUE
+run_everything <- FALSE
 notingraph <- list()
@@
 and social functioning [@reindlSocializationEmotionRegulation2016]. For as many
-as one in five individuals, adolescence marks the onset of emotion
-regulation-related mental illness, which can persist throughout the life course
+as one in five individuals, adolescence marks the onset of
+emotion regulation difficulties and associated mental health problems,
+which can persist throughout the life course
 [see @leeAdolescentMentalHealth2014]. 
@@
 
-## Why adolescence is an important life stage for emotion regulation
-
-Adolescence is defined as a life stage ranging from pubertal onset to
-adult-like independence [@steinbergAgeOpportunityLessons2014].
-It is thus demarcated by both biological and socio-cultural factors.
-It has been argued that,
-due to accellerated pubertal onset and delayed transitions to adult roles,
-adolescence now ranges from 10-24 years in the modern Western world
-[@sawyerAgeAdolescence2018].
-<!-- From Barriola:
-* adolescence, more than adulthood or childhood, is characterized by frequent
-and intense emotions (Larson et al. 1980; Larson and Lampmanpetraitis 1989).
-* signi?cant psychosocial changes that call for an increase in sophistication
-of ER strategies (Steinberg 2005)
-* novel stressors associated with social relationships, including pressures to
-conform to adult expectations relating to maturity, educational achievement,
-gender appropriate conduct, and other socially competent behaviors (Yap et al.
-2007)
-* Additionally, adolescents have an increased orientation toward autonomy
-(Spear 2000) including autonomous emotional regulation-->
-Adolescence is increasingly seen as a developmentally sensitive period for
-mature emotion regulation skills. During this period, children experience rapid
+## Relevance and scope
+
+Adolescence is a life stage defined by biological and socio-cultural factors,
+ranging from pubertal onset to adult-like independence [approximately 10-24 years of age, @steinbergAgeOpportunityLessons2014; @sawyerAgeAdolescence2018].
+It constitutes a developmentally sensitive period for
+mature emotion regulation skills, during which children experience
 biological, cognitive, and social changes that prompt new emotional
-experiences, and tax existing regulatory abilities
-[@steinbergAgeOpportunityLessons2014]. At the same time, the staggered
-development of motivational-emotional and regulatory brain circuits gives rise
+experiences and tax regulatory abilities [@steinbergAgeOpportunityLessons2014].
+<!-- At the same time, the staggered development of motivational-emotional and regulatory brain circuits gives rise
 to a maturity gap [@croneUnderstandingAdolescencePeriod2012]. 
 This leads youngsters to pursue new experiences in life and love,
-without being fully prepared to cope with the emotional outcomes.
+without being fully prepared to cope with the emotional outcomes. --> 
 Due to these coalescing changes,
@@
 compared to younger or older individuals
-[@zimmermannEmotionRegulationEarly2014]. Consequently, adolescents experience
-more frequent and intense (negative) emotions than children or adults [see
-@silkAdolescentsEmotionRegulation2003]. The literature thus paints a picture of
+[@zimmermannEmotionRegulationEarly2014].
+Consequently, adolescents experience more frequent and intense (negative) emotions than children or adults [see @silkAdolescentsEmotionRegulation2003].
+<!--The literature thus paints a picture of
 adolescence as a chrysalis for emotional development: Children enter this stage
 with emotion regulation skills adapted to the challenges of childhood. During
-adolescence, emotional systems are rearranged substantially. These changes
-render adolescents temporarily vulnerable to emotional dysregulation, but
-ultimately serve a functional role in acquiring mature emotion regulation
-skills. Eventually, most adolescents emerge ready to take on the challenges of
-early adulthood. Unfortunately, a sizeable proportion of adolescents instead
+adolescence, emotional systems are rearranged substantially.-->
+Eventually, most adolescents emerge ready to take on the challenges of
+early adulthood. Unfortunately, a sizable proportion of adolescents instead
 manifests enduring emotional difficulties [@leeAdolescentMentalHealth2014].
-
 <!--
@@
 -->
-
-## The consequences of difficulties in emotion regulation
-
-<!--Acquiring mature emotion regulation abilities is important, because t-->The
-consequences of difficulties in emotion regulation are extensive,
-well-documented, and persist throughout the life course. Meta-analyses indicate
-that such difficulties are associated with internalizing, and to a lesser extent, externalizing, psychopathology
+According to meta-analyses, such difficulties in emotion regulation are associated with
+extensive and persist internalizing, and to a lesser extent, externalizing, psychopathology
 [@aldaoEmotionregulationStrategiesPsychopathology2010;
@@
 
+```{r baselinecode, message=FALSE, echo = FALSE, warning = FALSE, error=FALSE, results='hide'}
+library(data.table)
+library(stringr)
+library(udpipe)
+library(igraph)
+library(wordcloud)
+library(Matrix)
+library(ggplot2)
+library(yaml)
+source("word_functions.R")
+source("circle2.R")
+dict <- read_yaml("yaml_dict.txt")
+
+  bl_theory <- readLines("baseline_theory.txt")
+  bl_review <- readLines("baseline_reviews.txt")
+  df <- data.frame(word = trimws(tolower(bl_theory)), source = "theory")
+  df <- rbind(df, data.frame(word = trimws(tolower(bl_review)), source = "reviews"))
+  # Categorize words
+  res_cat <- cat_words(df$word, dict, handle_dups = "all")
+  df$cat <- res_cat$words
+  df <- df[!duplicated(df$cat), ]
+  if(!is.null(res_cat[["unmatched"]])){
+    df <- df[!df$cat %in% names(res_cat$unmatched), ]
+  }
+
+  baseline_cat <- df
+  baseline <- c("dysregulation", unique(df$cat[df$source == "theory"]))
+
+  saveRDS(baseline, "baseline.RData")
+  saveRDS(baseline_cat, "baseline_cat.RData")
+
+in_theory <- df$word[df$source == "theory"]
+in_rev <- df$word[!df$source == "theory"]
+in_rev[!in_rev %in% in_theory]
+
+df_plot <- data.frame(term1 = df$cat[df$source == "theory"], term2 = "dysregulation")
+df_plot <- df_plot[!df_plot$term1 == df_plot$term2, ]
+edg <- df_plot
+
+edg$width = 1
+
+vert <- data.frame(name = unique(c(df_plot$term1, df_plot$term2)), label = pretty_words(unique(c(df_plot$term1, df_plot$term2))), size = 1)
+vert <- vert[vert$name %in% unique(c(edg$term1, edg$term2)), ]
+
+categ <- read.csv("study1_categorization.csv", stringsAsFactors = FALSE)
+if(any(!vert$name %in% categ$name)){
+  write.table(vert$name[!vert$name %in% categ$name], "clipboard", sep = "\n", row.names = FALSE, col.names= FALSE)
+  stop("Please re-categorize missing vertices.")
+} 
+vert$Category <- categ$category[match(vert$name, categ$name)]
+
+cat_cols <- c(Outcome = "gray50", Indicator = "tomato", Cause = "gold", Protective = "forestgreen")
+cat_cols <- c(Outcome = "gray50", Indicator = "tomato", Cause = "gold", Protective = "olivedrab2")
+vert$color <- cat_cols[vert$Category]
+vert$frame.color <- cat_cols[vert$Category]
+#min_size <- (strwidth(vert$name[max(nchar(vert$name))]) + strwidth("oo")) * 100
+vert$size <- scales::rescale(log(vert$size), c(4, 12))
+g1 <- graph_from_data_frame(edg, vertices = vert,
+                           directed = FALSE)
+#g <- Rsenal::pruneEdg
+#min_size <- (strwidth(vert$label[max(nchar(vert$label))]) + strwidth("oo"))*100
+
+# edge thickness
+#E(g)$width <- scales::rescale(sqrt(E(g)$width), to = c(2, 8))
+
+# Plot 2 ------------------------------------------------------------------
+
+df_plot <- data.frame(term1 = df$cat, term2 = "dysregulation", source = df$source)
+
+edg <- df_plot
+
+edg$width = 1
+
+vert <- data.frame(name = unique(c(df_plot$term1, df_plot$term2)), label = pretty_words(unique(c(df_plot$term1, df_plot$term2))), size = 1)
+vert <- vert[vert$name %in% unique(c(edg$term1, edg$term2)), ]
+
+categ <- read.csv("study1_categorization.csv", stringsAsFactors = FALSE)
+if(any(!vert$name %in% categ$name)){
+  write.table(vert$name[!vert$name %in% categ$name], "clipboard", sep = "\n", row.names = FALSE, col.names= FALSE)
+  stop("Please re-categorize missing vertices.")
+} 
+vert$Category <- categ$category[match(vert$name, categ$name)]
+vert$faded <- vert$name %in% df$cat[df$source == "theory"]
+cat_cols <- c(Outcome = "gray50", Indicator = "tomato", Cause = "gold", Protective = "olivedrab2")
+vert$color <- cat_cols[vert$Category]
+vert$frame.color <- cat_cols[vert$Category]
+# cat_cols <- c(Outcome = "#E5E5E5", Indicator = "#FFC9AD", Cause = "#FFFF66", Protective = "#E6FF6D")
+vert$color[vert$faded] <- "#FFFFFF"#cat_cols[vert$Category[vert$faded]]
+
+#min_size <- (strwidth(vert$name[max(nchar(vert$name))]) + strwidth("oo")) * 100
+vert$size <- scales::rescale(log(vert$size), c(4, 12))
+g2 <- graph_from_data_frame(edg, vertices = vert,
+                           directed = FALSE)
+#g <- Rsenal::pruneEdg
+#min_size <- (strwidth(vert$label[max(nchar(vert$label))]) + strwidth("oo"))*100
+
+# edge thickness
+#E(g)$width <- scales::rescale(sqrt(E(g)$width), to = c(2, 8))
+
+set.seed(2) #4 #2 #3
+l1 <- l <- layout_with_fr(g1)
+set.seed(33)
+l2 <- layout_with_fr(g2)
+
+p <- quote({
+  # Set margins to 0
+  par(mar=c(0,0,0,0),
+      mfrow=c(1,2))
+  plot(g1, edge.curved = 0, layout=l1,
+       vertex.label.family = "sans",
+       vertex.label.cex = 0.8,
+       vertex.shape = "circle2",
+       #vertex.frame.color = 'gray40',
+       vertex.label.color = 'black',      # Color of node names
+       vertex.label.font = 1,         # Font of node names
+       vertex.frame.width = 2
+  )
+  legend(x=-1.1, y=1.1, names(cat_cols), pch=21, col=cat_cols, pt.bg=cat_cols, pt.cex=2, cex=.8, bty="n", ncol=1)
+  plot(g2, edge.curved = 0, layout=l2,
+       vertex.label.family = "sans",
+       vertex.label.cex = 0.8,
+       vertex.shape = "circle2",
+       #vertex.frame.color = 'gray40',
+       vertex.label.color = 'black',      # Color of node names
+       vertex.label.font = 1,         # Font of node names
+       vertex.frame.width = 2
+  )
+})
+saveRDS(g1, "bl_g1.RData")
+saveRDS(g2, "bl_g2.RData")
+saveRDS(l1, "bl_l1.RData")
+saveRDS(l2, "bl_l2.RData")
+# Save files
+png("baseline_network.png", width = 960)
+eval(p)
+dev.off()
+
+svg("baseline_network.svg", width = 14)
+eval(p)
+dev.off()
+```
+
+```{r baseline, warning=FALSE, eval = TRUE, results='asis', out.width = "100%", fig.cap="Correlates of emotion regulation difficulties according to theory (left panel) and narrative reviews (right panel).
+Transparent circles indicate constructs also represented in the theory."}
+knitr::include_graphics("baseline_network.png") 
+```
+```{r allnetworks, warning=FALSE, eval = TRUE, results='asis', out.width = "100%", fig.cap="Correlates of emotion regulation difficulties according to theory (A), narrative reviews (B), and term co-occurrence in author keywords (C) and abstracts (D).
+Size of lines and circles represents frequency.
+Dashed lines represent links not involving dysregulation.
+Transparent circles indicate constructs also represented in the theory (panel A)."}
+
+knitr::include_graphics("networks.png") 
+```
+
 Our text mining analysis of the empirical literature is best understood against a backdrop of the existing theoretical landscape.
@@
 Other recent publications offer more detailed reviews of theories of emotional development [@bussTheoriesEmotionalDevelopment2019] and emotion regulation in adolescence [@riedigerEmotionRegulationAdolescence2014].
-The correlates of emotion regulation difficulties discussed in our theoretical review
-are summarized in Figure \@ref(fig:baseline)^[Based on an author-curated list of keywords, caterogized using the dictionary method introduced in Analysis 1.].
-
-```{r baseline, warning=FALSE, eval = TRUE, results='asis', out.width = "100%", fig.cap="Correlates of emotion regulation difficulties according to theory (left panel) and narrative reviews (right panel).
-Transparent circles indicate constructs also represented in the theory."}
-source("baseline.R", local = TRUE)
-knitr::include_graphics("baseline_network.png") 
-#fig_svg <- cowplot::ggdraw()+cowplot::draw_image("s1_varimp.svg")
-#plot(fig_svg)
-
-```
 
@@
 <!--
-Note that the left panel of Figure \@ref(fig:baseline) visually summarizes the correlates of emotion regulation difficulties (labeled: *Dysregulation*) according to our theoretical review.
-The left panel of Figure \@ref(fig:baseline) summarizes key constructs covered by the theories reviewed above. 
+Note that the left panel of Figure \@ref(fig:allnetworks) visually summarizes the correlates of emotion regulation difficulties (labeled: *Dysregulation*) according to our theoretical review.
+The left panel of Figure \@ref(fig:allnetworks) summarizes key constructs covered by the theories reviewed above. 
 In the subsequent text mining analysis, we will distinguish the topics covered in this theoretical review visually to highlight unique contributions of our approach.
@@
 We will therefore examine how two excellent narrative reviews on emotion regulation in adolescence complement the aforementioned theoretical literature [@coe-odessEmergentEmotionsAdolescence2019; @bariolaChildAdolescentEmotion2011].
-Figure \@ref(fig:baseline) visualizes constructs uniquely covered by these narrative reviews,
+Figure \@ref(fig:allnetworks) visualizes constructs uniquely covered by these narrative reviews,
 relative to the theoretical literature.
@@
 Conflict with parents is addressed too, which peaks when adolescents become increasingly individuated.
-Such conflict impacts both day-to-day mood swings and dispositional emotion dysregulation [see also
+Such conflict impacts both day-to-day mood swings and dispositional emotion regulation difficulties [see also
 @vanlissaCostEmpathyParentadolescent2017].
@@
 Relatedly, the authors describe how hormonal changes intensify the stress response,
-which helps explain adolescents' greater susceptibility to emotion dysregulation.
+which helps explain adolescents' greater susceptibility to emotion regulation difficulties.
 Finally, <!--going beyond the implications of cognitive development
@@
 
-As can be seen in Figure \@ref(fig:baseline), 
+As can be seen in Figure \@ref(fig:allnetworks), 
 there are notable parallels between correlates of emotion regulation identified in these
@@
 The present paper aims to map the constructs
-related to adolescent emotion dysregulation, based on a systematic review of
+related to adolescent emotion regulation, based on a systematic review of
 the literature. <!-- CJ Consider removing the following if the purpose is sufficiently clarified in the introduction -->
@@
 contstructs as potential predictors or outcomes.
-We used the Workflow for Open Reproducible Code in Science (WORCS)
+We used the Workflow for Open Reproducible Code in Science [WORCS, @vanlissaWORCSWorkflowOpen2020]
 to ensure transparency and  reproducibility. All code and data are available online at [masked].
@@
 We thus deemed these terms to be overly inclusive, and
-proceeded with the original search string above.
+proceeded with the original search string.
 ```{r readrecs}
@@
 ```
-The screening and deduplication procedure is detailed in Figure \@ref(fig:prismachart).
-Duplicates were identified using DOI and title similarity.
-Papers were screened based on two main criteria:
+
+Starting with all `r nrow(recs)` records identified through Web of Science,
+we removed duplicates based on DOI matches (n = 2) and title similarity (n = 54).
+Rayyan QRCI [@Ouzzani2016] identified an additional 13 duplicates.
+We then screened papers based on two main criteria:
 They had to address emotion regulation or a synonymous construct, and the target population must overlap with the age range of adolescence (10-24).
-Preliminary screening was conducted in Rayyan QRCI [@Ouzzani2016].
-After coding `r sum(screen$rayyan == "True")+sum(screen$rayyan == "False")` papers, screening continued in ASReview [@van_de_schoot_rens_2020_3828293].
+Preliminary screening was conducted in Rayyan.
+After coding `r sum(screen$rayyan == "True")+sum(screen$rayyan == "False")` papers (`r sum(screen$rayyan == "False")` excluded),
+we continued screening in ASReview [@van_de_schoot_rens_2020_3828293].
 This program uses machine learning to screen articles.
-We trained the machine learning algorithm by manually screening an additional `r sum(table(screen$included, screen$rayyan)[, 1])` papers, until - among the most recently screened 100 papers - only 6 were excluded.
+We trained the naive Bayes algorithm by manually screening an additional `r sum(table(screen$included, screen$rayyan)[, 1])` papers (`r sum(screen$included == 1, na.rm = TRUE)-sum(screen$rayyan == "False")` excluded), until among the most recently screened 100 papers only 6 were excluded.
 In total, `r nrow(recs_final)` papers were deemed suitable for analysis.
 
-```{r prismachart, results='asis', fig.cap="Record screening flowchart"}
+```{r prismachart, eval = FALSE, results='asis', fig.cap="Record screening flowchart"}
 if(!isTRUE(tools::md5sum("prismachart.png") == "08351426aee2005edd1332a32b958ea0" )){
@@
   p <- graph_sem(layout = lo, nodes = nodes, edges = edges, angle = 1, rect_height = 1.2, rect_width = 1.3, text_size = 4)
-  ggsave("prismachart.png", p, device = "png")
-  ggsave("prismachart.svg", p, device = "svg")
+  ggsave("prismachart.png", p, device = "png", width = 7, height = 4)
+  ggsave("prismachart.svg", p, device = "svg", width = 7, height = 4)
 }
@@
   notingraph <- !df_plot$Word %in% in_graph
+  df_plot$notingraph <- notingraph
   italic_labels <- as.character(df_plot$Word)
@@
 
+  saveRDS(p, "s1_varimp.RData")  
   svg("s1_varimp.svg", width = 7/2.54, height = 14/2.54)
@@
   ggsave("s1_varimp.png", p, device = "png", width = 7, height = 14, units = "cm")
+
+  p1 <- p + theme(legend.position = "none")
 
@@
   # Save files
+  saveRDS(g, "s1_g1.RData")
+  saveRDS(l1, "s1_l1.RData")
+
   png("study1_network1.png", width = 960)
@@
 
+```{r message = FALSE, echo = FALSE, warning = FALSE, results="hide"}
+p <- quote(cowplot::plot_grid(readRDS("s1_varimp.RData")+theme(legend.position = "none")+xlab("Word frequency (Analysis 1)"), readRDS("s2_varimp.RData")+xlab("Word frequency (Analysis 2)")))
+
+png("varimps.png", height = 150, width = 200, units = "mm", res= 300)
+eval(p)
+dev.off()
+```
 To identify what issues are covered in this corpus,
@@
 This resulted in `r dtm_top[2]` terms, which occurred in `r dtm_top[1]` documents.
-The issues covered in this body of literature are visualized in Figure \@ref(fig:study1varimp).
-
-```{r study1varimp, warning=FALSE, eval = TRUE, results='asis', out.width = "100%", fig.cap="Document frequency of terms selected for Study 1.
-Transparent circles indicate constructs represented in theory (Figure 1), dotted lines indicate constructs absent from the co-occurrence graph."}
-knitr::include_graphics("s1_varimp.png") 
-#fig_svg <- cowplot::ggdraw()+cowplot::draw_image("s1_varimp.svg")
-#plot(fig_svg)
-
+The issues covered in this body of literature are visualized in Figure \@ref(fig:varimps).
+
+```{r varimps, warning=FALSE, message = FALSE, eval = TRUE, results='asis', out.width = "100%", fig.cap="Frequency of terms in Analysis 1 and 2.
+Transparent circles are constructs represented in theory (Figure 1), dotted lines are constructs absent from the co-occurrence graph."}
+knitr::include_graphics("varimps.png") 
 ```
@@
 Next, we computed a term co-occurrence matrix,
-which represents how frequently words occurred within the same document (see Figure \@ref(fig:study1network)).
+which represents how frequently words occurred within the same document (see Figure \@ref(fig:allnetworks)).
 To aid interpretability, we again pruned small coefficients using a negative binomial distribution,
@@
 To stimulate further reflection on the role of each construct,
-we manually classified each of the selected terms as either a putative 'Cause', 'Outcome', 'Protective factor', or 'Indicator' of emotion dysregulation.
-We stress that this classification is subjective and acknowledge that many of these associations are likely to be bidirectional [e.g., emotion dysregulation is known to be both a cause and consequence of conflict with parents, @vanlissaCostEmpathyParentadolescent2017].
-
-```{r study1network, warning=FALSE, out.width = "100%", fig.cap="Study 1 term co-occurrence.
+we manually classified each of the selected terms as either a putative 'Cause', 'Outcome', 'Protective factor', or 'Indicator' of emotion regulation.
+We stress that this classification is subjective and acknowledge that many of these associations are likely to be bidirectional [e.g., emotion regulation is known to both predict and be predicted by conflict with parents, @vanlissaCostEmpathyParentadolescent2017].
+
+```{r study1network, eval = FALSE, warning=FALSE, out.width = "100%", fig.cap="Study 1 term co-occurrence.
 Two layouts are presented to aid interpretation.
@@
 
-Emotion dysregulation and its mental health-related outcomes were foremost among the common terms in the corpus (Figure \@ref(fig:study1varimp)). 
+Emotion regulation and associated mental health-related outcomes were foremost among the common terms in the corpus (Figure \@ref(fig:varimps)). 
 Other frequent terms reflect important themes discussed in the theoretical review of the literature;
@@
 
-Based on the co-occurrence graph (Figure \@ref(fig:study1network)),
-emotion dysregulation is evidently a central construct
+Based on the co-occurrence graph (Figure \@ref(fig:allnetworks)),
+emotion regulation is evidently a central construct
 to which most other constructs are directly linked.
-This suggests that our search successfully identified factors relevant for adolescents’ emotion dysregulation.
+This suggests that our search successfully identified factors relevant for adolescents’ emotion regulation.
 The remaining graph is notably sparse, with few interconnections between terms.
@@
 
-This first analysis used author keywords to map common topics in the literature pertaining to adolescents' emotion dysregulation.
+This first analysis used author keywords to map common topics in the literature pertaining to adolescents' emotion regulation.
 The results reflected some of the constructs commonly accepted as relevant in theoretical literature and empirical reviews - particularly those pertaining to neurodevelopment and socialization.
@@
 why some of the most prevalent terms based on term document frequency
-(see Figure \@ref(fig:study1varimp)) are absent from the co-occurrence graph.
-These terms were not strongly related to any other terms in the main network. 
-Amongst the terms culled from the co-occurrence graph are the potential causes `r notingraph["Cause"]`, the potential outcomes `r notingraph["Outcome"]`, and the potential protective factors `r notingraph["Protective"]`.
-
-Many of these excluded constructs represent active ongoing areas of research, including research on *fathers* [@vanlissaRoleFathersMothers2019], *identity* [@campbellFriendsEducationIdentity2019], *friendship* and *social support* [@wangBidirectionalEffectsExpressive2020], *autonomy* [@vrolijkLongitudinalLinkagesFather2020a; @brenningPerceivedMaternalAutonomy2015], *sexual risk* [@brownDepressiveSymptomsPredictor2006], and *loneliness* [@spithovenItAllTheir2017].
-The fact that these constructs are absent from the graph does not suggest that they are unimportant.
-Rather, it indicates that they are not yet well-integrated in the broader literature on adolescents' emotion regulation,
-and are therefore prime candidates for future research.<!-- RK: Or could they also suggest that they were relevant in the past, but not any longer?
-Might it be important to run sensitivity analyses by publication year?
+are absent from the co-occurrence graph (see Figure \@ref(fig:varimps)).
+This does not mean that these terms are unimportant.
+Rather, it suggests that they are not yet well-integrated in the broader literature on adolescents' emotion regulation,
+and are therefore prime candidates for future research.
+Several of these excluded constructs indeed represent active ongoing areas of research, including research on *fathers* [@vanlissaRoleFathersMothers2019], *identity* [@campbellFriendsEducationIdentity2019], *friendship* and *social support* [@wangBidirectionalEffectsExpressive2020], *autonomy* [@vrolijkLongitudinalLinkagesFather2020a; @brenningPerceivedMaternalAutonomy2015], *sexual risk* [@brownDepressiveSymptomsPredictor2006], and *loneliness* [@spithovenItAllTheir2017].
+<!-- RK: Or could they also suggest that they were relevant in the past, but not any longer? Might it be important to run sensitivity analyses by publication year?
 One recommendation for future research might be to study such important but unembedded constructs
@@
                        axis.text.y = element_text(hjust=0, vjust = 0, size = 6))
-
+  saveRDS(p, "s2_varimp.RData")
   svg("s2_varimp.svg", width = 7/2.54, height = 14/2.54)
@@
   ggsave("s2_varimp.png", p, device = "png", width = 7, height = 14, units = "cm")
+
 }
@@
   # Save files
+  saveRDS(g, "s2_g1.RData")
+  saveRDS(l1, "s2_l1.RData")
   png("study2_network1.png", width = 960)
@@
 When conducting text mining analysis on unstructured text data (as opposed to author key words), focusing on individual words out of context can reduce interpretability.
-For instance, our core construct "emotion dysregulation" is already a bigram.
+For instance, our core construct "emotion regulation" is already a bigram.
 To identify more meaningful units of analysis,
@@
 Terms exceeding the $97.5^{th}$ percentile of a negative binomial distribution were retained for analysis.
-The identified important keywords are displayed in Figure \@ref(fig:study2varimp).
-
-```{r study2varimp, eval = TRUE, out.width = "100%", results='asis', fig.cap="Document frequency of terms selected for Study 2.
-Transparent circles indicate constructs represented in theory (Figure 1), dotted lines indicate constructs absent from the co-occurrence graph."}
-knitr::include_graphics("s2_varimp.png") 
-# fig_svg <- cowplot::ggdraw()+cowplot::draw_image("s1_varimp.svg")
-# plot(fig_svg)
-```
+The identified important keywords are displayed in Figure \@ref(fig:varimps).
 
@@
 
-A term co-occurrence matrix was constructed following the procedure described in Analysis 1.
-Figure \@ref(fig:study2network) displays the resulting matrix as a force directed graph.
-
-```{r study2network, out.width = "100%", fig.cap="Study 2 term co-occurrence.
+We constructed a term co-occurrence matrix following the procedure described in Analysis 1;
+Figure \@ref(fig:allnetworks) displays the resulting matrix as a force directed graph.
+
+```{r study2network, eval = FALSE, out.width = "100%", fig.cap="Study 2 term co-occurrence.
 Two layouts are presented to aid interpretation.
@@
 In the corpus of abstracts,
-emotion dysregulation and its mental health outcomes were evidently the most common terms.
+emotion regulation and associated mental health-related outcomes were evidently the most common terms.
 The term *neural* again occurred frequently.
@@
 connected directly to dysregulation.
-Many prevalent terms were absent from the co-occurrence graph,
-as they were not strongly related to any other terms. 
-These terms include the potential causes `r notingraph["Cause"]`, the potential outcomes `r notingraph["Outcome"]`, and the potential protective factors `r notingraph["Protective"]`.
+Again, many prevalent terms were absent from the co-occurrence graph,
+as they were not strongly related to any other terms (see Figure \@ref(fig:varimps)).
 
@@
 Both analyses further revealed that most constructs were
-directly tied to emotion dysregulation or its mental health correlates,
+directly tied to emotion regulation and mental health,
 with few connections among constructs.
@@
 
-Our work represents one of the first efforts to comprehensively map the literature on adolescents' emotion dysregulation [cf.
+Our work represents one of the first efforts to comprehensively map the literature on adolescents' emotion regulation [cf.
 @bariolaChildAdolescentEmotion2011; @coe-odessEmergentEmotionsAdolescence2019].
@@
 
-To conclude, this paper set out to map the factors associated with adolescents' emotion dysregulation, based on a systematic review of the literature, and text mining analysis of author keywords and abstracts.
-We provided a map of the literature on adolescents' emotion dysregulation,
+To conclude, this paper set out to map the factors associated with adolescents' emotion regulation, based on a systematic review of the literature, and text mining analysis of author keywords and abstracts.
+We provided a map of the literature on adolescents' emotion regulation,
 covering both familiar ground, and charting unknown territories.
@@
 might benefit from incorporating additional relevant factors
-to better elucidate the nature of their association with adolescents' emotion dysregulation.
+to better elucidate the nature of their association with adolescents' emotion regulation.
 Our analysis also identified several factors currently on the fringes of the literature,
@@
 to bridge gaps in existing knowledge.
-Several authors have commented on the lack of an overarching theory tailored specifically to adolescent emotion dysregulation.
+Several authors have commented on the lack of an overarching theory tailored specifically to adolescent emotion regulation.
 The present work might serve as a starting point for future theory development,
 with the aim of incorporating themes from the empirical literature within the framework of existing relevant theory.
+
+```{r mergenetworks}
+cat_cols <- c(Outcome = "gray50", Indicator = "tomato", Cause = "gold", Protective = "olivedrab2")
+bl1 <- readRDS("bl_l1.RData")
+bl2 <- readRDS("bl_l2.RData")
+bg1 <- readRDS("bl_g1.RData")
+bg2 <- readRDS("bl_g2.RData")
+s1l <- readRDS("s1_l1.RData")
+s2l <- readRDS("s2_l1.RData")
+s1g <- readRDS("s1_g1.RData")
+s2g <- readRDS("s2_g1.RData")
+p <- quote({
+  # Set margins to 0
+  par(mar=c(0,0,0,0),
+      mfrow=c(2,2))
+  plot(bg1, edge.curved = 0,
+       layout=bl1,
+       vertex.label.family = "sans",
+       vertex.label.cex = 0.8,
+       vertex.shape = "circle2",
+       vertex.label.color = 'black',      # Color of node names
+       vertex.label.font = 1,         # Font of node names
+       vertex.frame.width = 2
+  )
+  text(-1.1, y = -1, labels = "A")
+  legend(x=-1.1, y=1.1, names(cat_cols), pch=21, col=cat_cols, pt.bg=cat_cols, pt.cex=2, cex=.8, bty="n", ncol=1)
+
+  plot(bg2, edge.curved = 0,
+       layout=bl2,
+       vertex.label.family = "sans",
+       vertex.label.cex = 0.8,
+       vertex.shape = "circle2",
+       #vertex.frame.color = 'gray40',
+       vertex.label.color = 'black',      # Color of node names
+       vertex.label.font = 1,         # Font of node names
+       vertex.frame.width = 2
+  )
+  text(-1.1, y = -1, labels = "B")
+  plot(s1g, edge.curved = 0,
+       layout=s1l,
+       vertex.label.family = "sans",
+       vertex.label.cex = 0.8,
+       vertex.shape = "circle2",
+       #vertex.frame.color = 'gray40',
+       vertex.label.color = 'black',      # Color of node names
+       vertex.label.font = 1,         # Font of node names
+       vertex.frame.width = 2
+  )
+  text(-1.1, y = -1, labels = "C")
+  plot(s2g, edge.curved = 0,
+       layout=s2l,
+       vertex.label.family = "sans",
+       vertex.label.cex = 0.8,
+       vertex.shape = "circle2",
+       #vertex.frame.color = 'gray40',
+       vertex.label.color = 'black',      # Color of node names
+       vertex.label.font = 1,         # Font of node names
+       vertex.frame.width = 2
+  )
+  text(-1.1, y = -1, labels = "D")
+})
+
+# Save files
+# png("networks.png", width = 960)
+# eval(p)
+# dev.off()
+png("networks.png", height = 200, width = 200, units = "mm", res= 300)
+eval(p)
+dev.off()
+
+svg("networks.svg", width = 14)
+eval(p)
+dev.off()
+```
 

### 2021-02-10 manuscript.Rmd
Address revisions

@@
   underrepresented themes. This research constitutes a first step towards integrating the 
-  literature, and illustrates how text mining reviews may complement narrative reviews.
+  literature, and illustrates how text mining systematic reviews (TMSR) may complement narrative reviews.
 keywords          : "emotion regulation, adolescence, systematic review, text mining, machine
@@
 
-A key developmental challenge in adolescence is acquiring mature emotion
+Adolescence is a life stage ranging from pubertal onset to adult-like independence [@steinbergAgeOpportunityLessons2014; @sawyerAgeAdolescence2018].
+A key developmental challenge in this stage is acquiring mature emotion
 regulation skills [@croneUnderstandingAdolescencePeriod2012;
-@zimmermannEmotionRegulationEarly2014]. Emotion regulation is integral to
-mental health [@aldaoEmotionregulationStrategiesPsychopathology2010;
-@schaferEmotionRegulationStrategies2017; @braetEmotionRegulationChildren2014]
-and social functioning [@reindlSocializationEmotionRegulation2016]. For as many
-as one in five individuals, adolescence marks the onset of
-emotion regulation difficulties and associated mental health problems,
-which can persist throughout the life course
-[see @leeAdolescentMentalHealth2014]. 
-It is therefore crucial to identify which
-risk factors and environmental hazards render some adolescents more susceptible
-to emotional difficulties than others. <!--SH: Main goal of paper -->
-Although there is an abundance of empirical work on adolescents' emotion regulation, the literature is somewhat fragmented, because the topic has been investigated from different (sub)disciplines.
-As a result, there is a lack of unifying theory,
-and intrinsic limitations of narrative reviews prohibit comprehensive coverage of the vast but diffuse literature [@bussTheoriesEmotionalDevelopment2019].
-
-The present systematic review addressed these limitations by adopting a novel method:
-the text mining based systematic review.
-We set out to map the constructs associated with adolescent emotion regulation based on a systematic review of the empirical literature.
-Traditional narrative literature reviews have been shown to be marred by reliance on small convenience samples of the literature, confirmation bias,
+@zimmermannEmotionRegulationEarly2014]. 
+Adolescents experience biological, cognitive, and social changes that prompt new emotional
+experiences and tax regulatory abilities [@steinbergAgeOpportunityLessons2014].
+These coalescing changes temporarily restrict adolescents' capacity for emotion regulation 
+[@zimmermannEmotionRegulationEarly2014],
+resulting in more frequent and intense (negative) emotions [see @silkAdolescentsEmotionRegulation2003].
+
+Although most adolescents eventually develop mature emotion regulation abilities,
+for as many as one in five [@leeAdolescentMentalHealth2014],
+adolescence marks the onset of
+life course persistent emotion regulation-related psychopathology
+[see also @aldaoEmotionregulationStrategiesPsychopathology2010;
+@schaferEmotionRegulationStrategies2017].
+Given the prevalence of emotion regulation difficulties in adolescence,
+their implications for mental health<!--and social functioning [@braetEmotionRegulationChildren2014]; @reindlSocializationEmotionRegulation2016]-->
+and downstream cost to society,
+it is important to have a comprehensive understanding of the risk factors that render some adolescents more susceptible to emotional difficulties than others.
+Despite the abundance of empirical work on this issue,
+several authors have pointed out that the literature is somewhat fragmented,
+because different (sub)disciplines have approached the issue in disparate ways,
+in the absence of consistent terminology and unifying theory 
+[@bussTheoriesEmotionalDevelopment2019; @bariolaChildAdolescentEmotion2011; @stifterEmotionRegulation2019].
+
+There have been recent calls for the consolidation of empirical insights into overarching theory [e.g., @bussTheoriesEmotionalDevelopment2019]. 
+According to formal methods for theory construction [@borsboomTheoryConstructionMethodologya; @haigExploratoryFactorAnalysis2005],
+the first step in this endeavor is to identify the relevant *empirical phenomena*,
+defined as stable and general features of the world [@bogenSavingPhenomena1988].
+We propose that systematic reviews are a suitable method for taking this first step,
+based on the assumption that phenomena currently considered to be most stable and general will be more frequently represented in the literature.<!-- the frequency with which phenomena occur in the literature is indicative of their relevance.-->
+However, traditional narrative reviews have been shown to be marred by reliance on small convenience samples of the literature, confirmation bias,
 and an undue emphasis on positive results [@littellEvidencebasedBiasedQuality2008].
-Text mining, by contrast, is uniquely suited to provide a comprehensive overview of the literature.
-It can cover vastly greater corpora than a human reader,
-and the process by which text mining gleans insights from the literature is more objective, transparant, and reproducible.
-Where human readers might be inclined to structure their reading of the literature around established ideas,
-the inherent "fairness" of text mining gives emerging themes in the literature a chance to come to the fore.
-Text mining identifies important topics in a body of literature and reveals which constructs are often studied together.
-This potentially reveals topics and connections missed by narrative reviewers,
-thereby laying the groundwork for future empirical and theoretical work. <!-- CJ To fill out gaps, following up on promising constructs and unify heretofore disparate regions of the lit -->
+We intend to overcome these limitations by adopting a novel method:
+the text mining systematic review (TMSR).
+Relative to narrative reviews, text mining can cover arbitrarily greater corpora,
+and gleans insights from the literature by means of a more transparent and reproducible process.
+<!--Where sentient readers tend to structure their reading of the literature around established ideas [@littellEvidencebasedBiasedQuality2008],
+the inherent "fairness" of text mining gives emerging themes a chance to come to the fore.-->
+
+The present paper aims to map the empirical phenomena relevant to adolescent emotion regulation, using text mining systematic review.
+This approach considers the frequency with which phenomena occur in the literature to be indicative of their relevance.
+If we additionally assume that the frequency with which phenomena are studied together is indicative of the extent to which researchers believe them to be associated,
+then the co-occurrence of phenomena within publications can be interpreted as a nomological network: a mapping of relationships between phenomena of theoretical relevance [see @alaviAligningTheoryMethodology2018].
+This can serve as a starting point for the formulation of a proto-theory,
+which would additionally involve specifying putative mechanisms to explain associations between the phenomena [@borsboomTheoryConstructionMethodologya].
+By mapping the phenomena relevant to adolescent emotion regulation,
+the present work thus lays the groundwork for future theory development.
+
+<!--
+Where sentient readers tend to structure their reading of the literature around established ideas [@littellEvidencebasedBiasedQuality2008],
+This potentially reveals phenomena and associations missed by narrative reviewers,
+thereby laying the groundwork for future empirical and theoretical work.
+
+we set out to map these relevant empirical phenomena using a systematic review.
+
+generate a proto-theoretical nomological network of the relevant empirical phenomena.
+We discuss how this nomological network relates to existing relevant theory, and conclude
+with recommendations for future theory-generating efforts.
+There have been calls for the  consolidation of these disparate insights into overarching theory would be an important step forward.
+An important first step 
+and intrinsic limitations of narrative reviews prohibit comprehensive coverage of the vast but diffuse literature .-->
+
+Recent years have seen the publication of several excellent systematic reviews,
+but these have all been narrative reviews.
+
+ <!-- CJ To fill out gaps, following up on promising constructs and unify heretofore disparate regions of the lit -->
 <!-- SH: this implies that the main contribution of the paper is predominantly methodological is that the case?
@@
 with recommendations for future theory-generating efforts.-->
-
-## Relevance and scope
-
-Adolescence is a life stage defined by biological and socio-cultural factors,
-ranging from pubertal onset to adult-like independence [approximately 10-24 years of age, @steinbergAgeOpportunityLessons2014; @sawyerAgeAdolescence2018].
-It constitutes a developmentally sensitive period for
-mature emotion regulation skills, during which children experience
-biological, cognitive, and social changes that prompt new emotional
-experiences and tax regulatory abilities [@steinbergAgeOpportunityLessons2014].
 <!-- At the same time, the staggered development of motivational-emotional and regulatory brain circuits gives rise
@@
 without being fully prepared to cope with the emotional outcomes. -->
-Due to these coalescing changes,
-adolescents display a restricted repertoire of emotion regulation strategies
-compared to younger or older individuals
-[@zimmermannEmotionRegulationEarly2014].
-Consequently, adolescents experience more frequent and intense (negative) emotions than children or adults [see @silkAdolescentsEmotionRegulation2003].
+
 <!--The literature thus paints a picture of
@@
 adolescence, emotional systems are rearranged substantially.-->
-Eventually, most adolescents emerge ready to take on the challenges of
-early adulthood. Unfortunately, a sizable proportion of adolescents instead
-manifests enduring emotional difficulties [@leeAdolescentMentalHealth2014].
+
 <!--
@@
 -->
-According to meta-analyses, such difficulties in emotion regulation are associated with
-extensive and persist internalizing, and to a lesser extent, externalizing, psychopathology
-[@aldaoEmotionregulationStrategiesPsychopathology2010;
-@schaferEmotionRegulationStrategies2017]. 
-Individuals who engage in maladaptive
-emotion regulation strategies also experience more negative emotions,
-diminished well-being, and greater strain in interpersonal relationships
-[@grossIndividualDifferencesTwo2003a; @bellRelationshipsInputsOutputs2000].
-<!--Adolescence also appears to be a key period for developing mature emotion
-regulation skills - but not all adolescents do so successfully. As many as one
-in five adolescents instead develop severe emotional difficulties.--> 
-Given the
-prevalence of emotional difficulties and their implications for
-individual mental health, wellbeing, and social functioning, and their downstream
-cost to society as a whole [@leeAdolescentMentalHealth2014], it is essential to
-have a solid understanding of the risk factors associated with adolescents'
-emotion regulation difficulties.
 
@@
 
-Our text mining analysis of the empirical literature is best understood against a backdrop of the existing theoretical landscape.
-We therefore provide a summary theoretical review.
-Other recent publications offer more detailed reviews of theories of emotional development [@bussTheoriesEmotionalDevelopment2019] and emotion regulation in adolescence [@riedigerEmotionRegulationAdolescence2014].
+Although there is a paucity of theories *specific to* adolescent emotion regulation,
+several relevant theories are commonly invoked in empirical work [see  @bussTheoriesEmotionalDevelopment2019].
+In order to contextualize the results of our systematic review,
+and assess to what extent the identified phenomena through text mining mirror or complement existing theory,
+we provide a brief review of the existing theoretical landscape.
+Others have published more detailed reviews of theories of emotional development [@bussTheoriesEmotionalDevelopment2019] and emotion regulation in adolescence [@riedigerEmotionRegulationAdolescence2014].
+In reading the theoretical literature,
+we recorded relevant phenomena,
+and whether these were discussed as putative causes, outcomes, indicators, or protective factors in relation to emotion regulation.
+The left panel of Figure \@ref(fig:figbaseline) visually summarizes the phenomena so identified in the theoretical literature in a style similar to our subsequent systematic review,
+in order to facilitate contextualizing our original findings.
+<!-- 
+Our text mining analysis of the phenomena empirical literature is best understood against a backdrop of -->
 
@@
 According to Gross, individuals use `r keyw("strategies")` to modulate the different stages of this process,
-consciously or otherwise. The effectiveness, desireability, and consequences of some strategies vary across `r keyw("culture")`s [see
+consciously or otherwise. 
+Individuals who engage in maladaptive emotion regulation strategies tend to experience more negative emotions,
+diminished well-being, and greater strain in interpersonal relationships
+[@grossIndividualDifferencesTwo2003a; @bellRelationshipsInputsOutputs2000].
+However, comparative studies indicate that the adaptive versus maladaptive psychosocial consequences of specific strategies appear to be partly contingent on the `r keyw("cultural context")` [see
 @bariolaChildAdolescentEmotion2011].
@@
 Whereas theory provides a top-down frame of reference,
-literature reviews can provide a bottom-up, inductive understanding of a phenomenon.
-Given the noted absence of a single overarching theory, reviews might provide additional
-insight into factors considered relevant in the etiology of adolescents'
+literature reviews provide a bottom-up understanding of a phenomenon by aggregating empirical evidence.
+Given the noted absence of a single overarching theory [see @bussTheoriesEmotionalDevelopment2019],
+reviews are especially important,
+as they provide additional
+insight into relevant phenomena in the etiology of adolescents'
 emotion regulation competencies.
-Innovative text mining methods are promising in this respect, because they can comprehensively review the available literature.
-Narrative reviews, however, constitute the status quo.
-We will therefore examine how two excellent narrative reviews on emotion regulation in adolescence complement the aforementioned theoretical literature [@coe-odessEmergentEmotionsAdolescence2019; @bariolaChildAdolescentEmotion2011].
+Two recent narrative reviews in particular complement the aforementioned theoretical literature [@coe-odessEmergentEmotionsAdolescence2019; @bariolaChildAdolescentEmotion2011].
 Figure \@ref(fig:allnetworks) visualizes constructs uniquely covered by these narrative reviews,
 relative to the theoretical literature.
-
 <!--
@@
 
-A seminal review by
+The seminal review by
 @bariolaChildAdolescentEmotion2011 addressed intra-individual factors
@@
 An important limitation is that all reviews in this field have been unstructured narrative reviews, which are known to be limited in scope and biased [@littellEvidencebasedBiasedQuality2008].
-We seek to complement preceding work by using text mining to conduct a more comprehensive empirical
+We seek to complement preceding work by using text mining to conduct a more comprehensive and objective empirical
 literature review, and map the factors associated with adolescent emotion
 regulation.
+
+<!--Where sentient readers tend to structure their reading of the literature around established ideas,
+text mining has the potential to reveal phenomena and associations missed by narrative reviewers,
+thereby laying the groundwork for future empirical and theoretical work.-->
 
@@
 
-The present paper aims to map the constructs
-related to adolescent emotion regulation, based on a systematic review of
-the literature. <!-- CJ Consider removing the following if the purpose is sufficiently clarified in the introduction -->
-First, we conducted a systematic search to
-elicit a corpus of relevant literature. Second, we used text mining techniques
-to extract relevant constructs from the corpus. Third, we used a dictionary to
-pare down the extracted constructs to meaningful superordinate categories.
-Fourth, we mapped interrelations between these constructs. Fifth, we classified
-contstructs as potential predictors or outcomes.
+The present paper set out to map the phenomena relevant to adolescent emotion regulation
+using a text mining systematic review (TMSR) of the literature.
+This approach considers the frequency with which a phenomenon is covered in the literature to be indicative of its relevance,
+and the frequency with which phenomena are investigated together within publications to be indicative of a relationship between these constructs.
+The expected outcomes consist of term frequency metrics,
+which can be rank ordered to identify the most relevant phenomena,
+and term co-occurrence metrics.
+These metrics can be jointly visualized as a network graph,
+thereby "mapping" phenomena relevant to adolescent emotion regulation.
+Note that this study is inductive, or exploratory, and as such does not test any hypotheses [].
+
+# Methods
+
 We used the Workflow for Open Reproducible Code in Science [WORCS, @vanlissaWORCSWorkflowOpen2020]
-to ensure transparency and  reproducibility. All code and data are available online at [masked].
-
-# Methods
+to ensure transparency and  reproducibility.
+All analyses are strictly reproducible,
+and the code, data, and historical record of this project are available online at [masked].
 
@@
 We then screened papers based on two main criteria:
-They had to address emotion regulation or a synonymous construct, and the target population must overlap with the age range of adolescence (10-24).
+They had to address emotion regulation or a synonymous construct, and the target population must overlap with the age range of adolescence (10-24) [as defined by @steinbergAgeOpportunityLessons2014; @sawyerAgeAdolescence2018].
 Preliminary screening was conducted in Rayyan.
@@
 we manually classified each of the selected terms as either a putative 'Cause', 'Outcome', 'Protective factor', or 'Indicator' of emotion regulation.
-We stress that this classification is subjective and acknowledge that many of these associations are likely to be bidirectional [e.g., emotion regulation is known to both predict and be predicted by conflict with parents, @vanlissaCostEmpathyParentadolescent2017].
+We stress that this classification is based on our subjective reading of the literature,
+and acknowledge that many of these associations are likely to be bidirectional [e.g., emotion regulation is known to both predict and be predicted by conflict with parents, @vanlissaCostEmpathyParentadolescent2017].
 

### 2021-02-11 manuscript.Rmd
LDA to supplementary matrial

@@
 thereby "mapping" phenomena relevant to adolescent emotion regulation.
-Note that this study is inductive, or exploratory, and as such does not test any hypotheses [].
+Note that this study is inductive or exploratory,
+as opposed to deductive or confirmatory research, and as such does not test any hypotheses [see De Groot's work on the empirical cycle @degrootMethodologieGrondslagenVan1961][^Note that aside from induction, the term "abduction" is also used in the methodological literature.
+Injunction pertains to inferences based purely on statistical data, whereas abduction additionally involves the attribution of observations to explanatory principles.].
+<!--The distinction between inductive and deductive research has recently been recast as a "creativity-verification" cycle [@wagenmakersCreativityVerificationCyclePsychological2018].-->
 
@@
 We extracted keywords by document, and applied an exclusion filter of methodological terms and similar non-substantive words.
-Then, we used a dictionary to classify related terms.
-The dictionary describes `r length(dict)` terms using `r length(unlist(dict))`
-regular expression queries.
-The resulting term-document matrix consisted of `r number_docs_words[1]` documents with `r number_docs_words[2]` unique terms.
-
-## Structural topic modeling
-
-<!-- it might be useful to insert a sentence or two when you are using a method many readers are not familiar with, just to explain the utility of the chose method (what it does/doesn't do potentially as compared to other options)-->
+The resulting corpus consisted of `r number_docs_words[1]` documents with `r number_docs_words[2]` unique terms.
+One important step in reviewing the literature is to examine heterogeneity of the corpus;
+to analyze empirically whether there is, for example, a clear divide between psychiatric and developmental texts.
+To this end, we conducted topic modeling using latent dirichlet allocation [@bleiLatentDirichletAllocation2003].
+However, as no subcorpora could be identified (see [online supplemental material]()), we proceed with an analysis of the whole sample.
+
+<!--## Structural topic modeling
+
 One important step before reviewing the literature is to examine heterogeneity in the corpus;
@@
 Thus, no subcorpora could be identified,
-and we proceed with an analysis of the whole sample. <!-- Probably because each set of keywords has only a few indicators. -->
+and we proceed with an analysis of the whole sample.-->
 
@@
 we examined the terms occurring in the largest number of texts.
+
+Then, we used a dictionary to classify related terms.
+The dictionary describes `r length(dict)` terms using `r length(unlist(dict))`
+regular expression queries.
+After classification,
+
+The total number of unique terms after dictionary encoding was 
 We modeled word frequency using a negative binomial distribution,
 and retained those exceeding the $97.5^{th}$ percentile.
+This cut-off criterion is arbitrary, but necessary to reduce the number of terms considered from 5299.
 This resulted in `r dtm_top[2]` terms, which occurred in `r dtm_top[1]` documents.
@@
 we first applied the natural language processing technique "part-of-speech tagging" (POS-tagging), which identifies a word's grammatical function within the sentence context.
-Then, we used POS-tagging to retain only nouns and adjectives,
-which helps derive more interpretable text mining models [@martinMoreEfficientTopic2015].
+Because our analysis sought to identify phenomena,
+we retained only nouns (to capture terms like "emotion") and adjectives (to capture the "mental" in "mental health").
+Retaining nouns and adjectives generally helps derive more interpretable text mining models [@martinMoreEfficientTopic2015].
 Finally, we used stemming to reduce the retained terms to their root form.
-
-## Structural topic modeling
-
-To assess the homogeneity of the corpus of abstracts,
-we again conducted topic modeling,
-following the procedure described in Analysis 1.
-The data comprised `r lda_dims_2[2]` terms in `r lda_dims_2[1]` documents.
-As before, the BICs followed a linearly increasing trend, and entropies were near-zero.
-Thus, no subcorpora were identified,
-and we proceed with a whole sample analysis.
+As in Analysis 1, we tested for heterogeneity using latent dirichlet allocation - but no subcorpora were identified ([see online supplement]()).
 

### 2021-02-11 topic_models.Rmd
LDA to supplementary matrial

---
title: "Topic models"
author: "Caspar J. van Lissa"
date: "2/10/2021"
output:
  bookdown::html_document2:
    number_sections: false
bibliography      : ["veni_sysrev.bib"]
---

```{r setup, include=FALSE}
library(yaml)
knitr::opts_chunk$set(echo = TRUE)
lda_dims <- read_yaml("Study1_lda_dims.txt")
dtm_top <- read_yaml("study1_dtm_top.yml")
df <- readRDS("study1_df.RData")
number_docs_words <- yaml::read_yaml("study1_number_docs_words.txt")
```

This document describes a supplementary analysis related to the studies
described in the document `manuscript.Rmd`.

## Analysis 1: Author keywords

One important step in reviewing the literature is to examine heterogeneity of the corpus;
to analyze empirically whether there is, for example, a clear divide between psychiatric and developmental texts.
To this end, we conducted topic modeling using latent dirichlet allocation [@bleiLatentDirichletAllocation2003].
This is a clustering method for large sparse matrices.

The corpus for this first analysis consisted of author-provided keywords.
We extracted keywords by document, and applied an exclusion filter of methodological terms and similar non-substantive words.
The resulting corpus consisted of `r number_docs_words[1]` documents with `r number_docs_words[2]` unique terms.

We used the term frequency/inverse document frequency (TF-IDF) to select terms
used frequently in a document, but not used frequently in the corpus,
which could therefore be more diagnostic of subgroup membership.
Selection terms with an TF-IDF greater than the median resulted in a corpus of `r lda_dims[1]` documents and `r lda_dims[2]` terms.

We considered a range from 2-20 topics, evaluating fit based on the BIC, and interpretability based on the entropy of the posterior document/topic probabilities.
As can be seen in Figure \@ref(fig:figbic), the BICs followed a near-perfect linearly increasing trend, and the simplest model had the lowest BIC, indicating that no subcorpora could be identified.

```{r figbic, fig.cap="Analysis 1: Bayesian Information Criteria (BIC) for LDA models with 2-20 clusters."}
knitr::include_graphics("study1_BIC.png")
```
Congruently, all entropies were near-zero, as seen in Figure \@ref(fig:figent). 
Entropy reflects the separability of the extracted clusters.
The low entropies observed in this analysis indicate that the posterior document/topic probabilities were effectively uniformly distributed.
Thus, no subcorpora could be identified,
and we proceeded with an analysis of the whole sample.

```{r figent, fig.cap="Analysis 1: Entropy values for LDA models with 2-20 clusters."}
knitr::include_graphics("study1_entropies.png")
```

## Analysis 2: Abstracts

```{r, warning=FALSE, message=FALSE}
lda_dims_2 <- read_yaml("Study2_lda_dims.txt")
```
The corpus for this second analysis consisted of the abstracts of the selected articles.
To perform feature extraction,
we first applied the natural language processing technique "part-of-speech tagging" (POS-tagging), which identifies a word's grammatical function within the sentence context.
Because our analysis sought to identify phenomena,
we retained only nouns (to capture terms like "emotion") and adjectives (to capture the "mental" in "mental health").
Retaining nouns and adjectives generally helps derive more interpretable text mining models [@martinMoreEfficientTopic2015].
Finally, we used stemming to reduce the retained terms to their root form.
The resulting corpus consisted of 15587 terms in 4414 documents.

To assess the homogeneity of the corpus of abstracts,
we again conducted topic modeling.
We selected terms with an TF-IDF greater than the median, which resulted in a corpus of `r lda_dims_2[2]` terms in `r lda_dims_2[1]` documents.

We considered a range from 2-20 topics, evaluating fit based on the BIC, and interpretability based on the entropy of the posterior document/topic probabilities.
As can be seen in Figure \@ref(fig:figbic2), the BICs again followed a near-perfect linearly increasing trend, and the simplest model had the lowest BIC, indicating that no subcorpora could be identified.

```{r figbic2, fig.cap="Analysis 2: Bayesian Information Criteria (BIC) for LDA models with 2-20 clusters."}
knitr::include_graphics("study2_BIC.png")
```

Congruently, all entropies were near-zero, as seen in Figure \@ref(fig:figent2). 
Entropy reflects the separability of the extracted clusters.
The low entropies observed in this analysis indicate that the posterior document/topic probabilities were effectively uniformly distributed.
Thus, no subcorpora could be identified,
and we proceeded with an analysis of the whole sample.

```{r figent2, fig.cap="Analysis 2: Entropy values for LDA models with 2-20 clusters."}
knitr::include_graphics("study2_entropies.png")
```

As before, the BICs followed a linearly increasing trend, and entropies were near-zero.
Thus, no subcorpora were identified,
and we proceed with a whole sample analysis.

# References

### 2021-02-11 topic_models.Rmd
LDA output format md

@@
 output:
-  bookdown::html_document2:
+  bookdown::github_document2:
     number_sections: false
@@
 library(yaml)
-knitr::opts_chunk$set(echo = TRUE)
+knitr::opts_chunk$set(echo = FALSE)
 lda_dims <- read_yaml("Study1_lda_dims.txt")

### 2021-02-13 action_letter.Rmd
Continued revision

---
title: "Action letter"
author: "Caspar J. van Lissa"
date: "2/11/2021"
output: html_document
---

# Reviewer #1:

## R1C1 The abstract is lacking in two regards:

### R1C1a The actual findings are not reported

### R1C1b it is not clear how the findings integrate te literature.

## R1C2 Key words are not provided.

Response: We apologize; the keywords were not retained when converting the manuscript to the required format for ADRR. We have reinstated them.

## R1C3 The title is about dysregulation but the first paragraph is all about regulation. The manuscript would be more effective if it were more consistent.

Response: We agree that greater consistency would improve the clarity of the writing, and have changed the manuscript to use the more general term "emotion regulation" throughout.

## R1C4 The first paragraph [promises] that the results will help unify theory and address limitations of research areas that the author deems in silos. This is a heavy burden to carry.

Response: We have interpreted this point as an indirect request that we further clarify the intended contribution of the present study. We will address that point below - but first we must clarify that it was not our intention to "promise that our results will help unify theory and address limitations of research areas that the author deams in silos". We have attempted to address this misunderstanding by clarifying that these are not our original claims; these are oft-repeated limitations of the existing literature, and our work is a response to these perceived limitations. We have included three references to support this point. The revision now reads:

> Despite the abundance of empirical work on this issue,
several authors have pointed out that the literature is somewhat fragmented,
because different (sub)disciplines have approached the issue in disparate ways,
in the absence of consistent terminology and unifying theory 
[@bussTheoriesEmotionalDevelopment2019; @bariolaChildAdolescentEmotion2011; @stifterEmotionRegulation2019].

Now, to the main point.
In the revision, we have attempted to clarify the intended contribution of the present study
as follows:

> There have been recent calls for the consolidation of empirical insights into overarching theory [e.g., @bussTheoriesEmotionalDevelopment2019]. 
According to formal methods for theory construction [@borsboomTheoryConstructionMethodologya; @haigExploratoryFactorAnalysis2005],
the first step in this endeavor is to identify the relevant *empirical phenomena*,
defined as stable and general features of the world [@bogenSavingPhenomena1988].
We propose that systematic reviews are a suitable method for taking this first step,
based on the assumption that phenomena currently considered to be most stable and general will be more frequently represented in the literature. [...] The present paper aims to map the empirical phenomena relevant to adolescent emotion regulation, using text mining systematic review.

## R1C5 The entire section on page 3: it is not clear why this is presented. It could be presented in a brief sentence and likely should because it does not really relate to what is reviewed. If it is kept, it should be edited so it relates to the actual review.
The paragraph on page 4 may be relevant, but it is not clear how it eventually relates to the study.

Response: These two paragraphs were intended to substantiate the relevance and scope of the present study.
Based on the Reviewer's comment, we now see that this was perhaps redundant with the opening paragraphs, which already provided rudimentary justification of the relevance and scope.
We have thus attempted to address the Reviewer's comment by cutting these paragraphs on pages 3 and 4,
merging the core arguments with the opening paragraphs.

The opening paragraphs now read:

> Adolescence is a life stage ranging from pubertal onset to adult-like independence [@steinbergAgeOpportunityLessons2014; @sawyerAgeAdolescence2018].
A key developmental challenge in this stage is acquiring mature emotion
regulation skills [@croneUnderstandingAdolescencePeriod2012;
@zimmermannEmotionRegulationEarly2014]. 
Adolescents experience biological, cognitive, and social changes that prompt new emotional
experiences and tax regulatory abilities [@steinbergAgeOpportunityLessons2014].
These coalescing changes temporarily restrict adolescents' capacity for emotion regulation 
[@zimmermannEmotionRegulationEarly2014],
resulting in more frequent and intense (negative) emotions [see @silkAdolescentsEmotionRegulation2003].
Although most adolescents eventually develop mature emotion regulation abilities,
for as many as one in five [@leeAdolescentMentalHealth2014],
adolescence marks the onset of
life course persistent emotion regulation-related psychopathology
[see also @aldaoEmotionregulationStrategiesPsychopathology2010;
@schaferEmotionRegulationStrategies2017].
Given the prevalence of emotion regulation difficulties in adolescence,
their implications for mental health
and downstream cost to society,
it is important to have a comprehensive understanding of the risk factors that render some adolescents more susceptible to emotional difficulties than others.

## R1C6 The existing theoretical landscape is presented in a way that is unclear how it really relates to the review.

Response: We understand that it is essential to clarify why we present this brief theoretical review before diving into the results of the present study.
In order to address this comment, we now explicitly state why a review of the existing theoretical landscape is relevant to the present systematic review. The revised manuscript reads:

> Although there is a paucity of theories *specific to* adolescent emotion regulation,
several relevant theories are commonly invoked in empirical work [see  @bussTheoriesEmotionalDevelopment2019].
In order to contextualize the results of our systematic review,
and assess to what extent the identified phenomena through text mining mirror or complement existing theory,
we provide a summary review of the existing theoretical landscape.

## R1C8 Figure 1 on page 5: it is not clear why it is there. It should come after the introduction. And, in fact, it should appear after the references and the text should simply have a placeholder for the Figure.  It should be referred to at the end of the introduction (before the current study section).

Response: As requested by the Reviewer, we have placed the Figure after the References section, retaining only a placeholder in-text. We also refer to the Figure at the end of the Introduction:

> As can be seen in Figure 1, 
there are notable parallels between correlates of emotion regulation identified in these
narrative reviews, and in the preceding theoretical literature.

## R1C9 The figure nicely points to outcomes, indicators, causes and protective factors. That is not clear from the introductory materials.

Response: In the previous manuscript, we had merged the two Figures from the theoretical Introduction with the two Figures from the Results section in order to facilitate comparisons between the two.
We see now that this caused some confusion.
In order to address this comment, we have separated the Figures from these two sections,
and we have added the following information about the classification of phenomena:

> In reading the theoretical literature,
we recorded relevant phenomena,
and whether these were discussed as putative causes, outcomes, indicators, or protective factors in relation to emotion regulation.
The left panel of Figure \@ref(fig:figbaseline) visually summarizes the phenomena so identified in the theoretical literature in a style similar to our subsequent systematic review,
in order to facilitate contextualizing our original findings.

## R1C10a The section on theory is not presented in a way that would have it appear as authoritative. It reads more like a hodgpode of theories.

Response: This is the state of the theoretical landscape: A hodgpodge. Others have pointed out that there is an absence of authoritative theories to guide research. It would be misleading to give readers the impression that there is a clear, authoritative theoretical framework.

## R1C10b The section would be stronger if it also gave readers a sense of which theories are deemed important/influential and worth using. There needs to be a sense that the important theories are being examined.

Response: Point out how often these theories are cited, perhaps?

## R1C11 The first paragraph on page 9 needs to be edited. It appears too haphazard. (Why use "Finally," as uo were not enumerating.) The problem, just as with the literature review, is that the studies appear presented randomly. One study did this, one did that, and so forth.

Response:

\ToDo

## R1C12 The fundamental problem with the "The present paper" section is that it really does not do what is needed. It is a plan of analysis. This section should note the research questions and hypotheses.

Response: We agree with the Reviewer that "The present paper" section was basically a plan of analysis. In the Revision, we have rewritten this section to summarize the study design, link it to the study aims, and state the intended outcomes. 
Note that this is an inductive (exploratory) study, and as such,
it does not test any hypotheses.
We now explicitly clarify this point in "The present paper".

> The present paper set out to map the phenomena relevant to adolescent emotion regulation
using a text mining systematic review (TMSR) of the literature.
This approach considers the frequency with which a phenomenon is covered in the literature to be indicative of its relevance,
and the frequency with which phenomena are investigated together within publications to be indicative of a relationship between these constructs.
The expected outcomes consist of term frequency metrics,
which can be rank ordered to identify the most relevant phenomena,
and term co-occurrence metrics.
These metrics can be jointly visualized as a network graph,
thereby "mapping" phenomena relevant to adolescent emotion regulation.
Note that this study is inductive or exploratory,
as opposed to deductive or confirmatory research, and as such does not test any hypotheses [see De Groot's work on the empirical cycle @degrootMethodologieGrondslagenVan1961][^Note that aside from induction, the term "abduction" is also used in the methodological literature. Injunction pertains to inferences based purely on statistical data, whereas abduction additionally involves the attribution of observations to explanatory principles.].

## R1C13 By the time I get to eh methods section, including the beginning of this section, I still see a focus on emotion regulation, not emotion dysregulation that appears in the title.

Response: We have addressed this comment as requested; see the response to R1C3.

## R1C13 As I read the materials on pages 11 and 12, I see a heavy reliance on the computerized analytical system to do the research and coding. I think it would be helpful to know what decisions are made by the authors and, if there are any, we should know about reliability checks and, if there are none, that still should be noted.

Response: This is a crucial comment with far-reaching implications.
The Reviewer asks what decisions are made by the authors.
Simply put: All decisions are made by us.
There are infinitely many ways to conduct exploratory analysis on a single data set,
and the present paper represents just one possible way.
The "computerized analytical system", as referred to by the Reviewer,
is nothing more than an explicit representation of our subjective decisions in analyzing the data,
represented as code.

The Reviewer asks for reliability checks, also known as a sensitivity analysis or multiverse analysis [@steegenIncreasingTransparencyMultiverse2016].
Such reliability checks are only defined, however, in the context of deductive (confirmatory) analysis,
where they are used to ensure that hypothesis tests / statistical inferences are robust to permutations of the data processing strategy.
As the present study is inductive (exploratory),
no hypotheses are tested nor inferences are drawn,
and the number of alternative possible analyses is infinite - thus reliability checks are undefined.

We do emphatically agree with the Reviewer that it is important to be clear about what decisions are made by us.

To address this comment, we have taken the following steps:

1) We have documented the methods in detail in the manuscript, and added online supplemental analyses for more complex analyses that we could not describe in sufficient detail.
2) We have made all analysis code and data publicly available in an open access repository.
This repository also contains the entire historical development of this study,
so readers can see that our analysis proceeded in a straightforward way. We mention this explicitly in the revised paper.
3) The revised Methods section now explicitly mentions that these are inductive (exploratory) analyses, and as such, depend on subjective decisions:

> As the purpose of inductive research is to inform hypothesis generation,
this approach affords the researcher with substantial creativity [@wagenmakersCreativityVerificationCyclePsychological2018].
This means that subjective decisions are made throughout the analysis process.
To ensure that all such decisions are properly documented,
we have made all code, data, and the historical record of this project publicly available in an online research repository at [https://github.com/cjvanlissa/veni_sysrev](https://github.com/cjvanlissa/veni_sysrev). 
We used the Workflow for Open Reproducible Code in Science [WORCS, @vanlissaWORCSWorkflowOpen2020]
to make the analyses strictly reproducible.
We encourage reuse of the analysis code,
and secondary analysis of the data.

## R1C14 At the bottom of page 12, it is clear that a decision is made in terms of retaining within a percentile. How do we know if that is the right decision?  There appear to be decisions like this made throughout. Given the reliance on the program, we need to know more.

Response: This is indeed a good example of a subjective decision.
In our response to the previous comment, we explain that we now explicitly acknowledge each such subjective decision in the revised manuscript.
In addition to the blanket statement we have added to the Methods section, 
we now also acknowledge the subjectivity of each decision like this one explicitly in the revised manuscript.

With regard to the Reviewer's question - "How do we know if that is the right decision?" - there is no straightforward answer.
We had thoroughly scoured the literature for established practice for pruning terms in text mining when preparing the initial submission, and did so again during revision,
but most published analyses appear to either retain a fixed number of terms, or drop terms that occur less than a fixed number of times.
Our selection method has the advantage of taking the distribution of word frequencies into account.
It is thus more flexible than a fixed cutoff, and still successful in pruning terms that occur only a few times in the corpus.
We now mention this explicitly in the paper:

> This is a subjective criterion,
but compared to the common practices of either retaining a fixed number of terms or pruning terms below a fixed frequency [see @benoitQuantedaPackageQuantitative2018],
it has the advantage of being responsive to the empirical distribution of term frequencies.

## R1C15 Page 13, there is again pruning. Justifications for the cutoff should be noted. There is a manual classification and we are left with no sense of its reliability/validity.

Please see our response to the previous comment.
Additionally, note that nearly all pruned terms occurred in only one document,
as can be seen in the plot below.
Even if the pruning criterion is subjective, it is hard to argue that we should interpret every word that occurred in the corpus.
Thus, we would argue, some pruning is necessary - and if a better method is available, we would be happy to use that instead.

```{r}
df_plot <- as.data.frame(term_freq)
df_plot <- df_plot[!df_plot$pruned, ]
ggplot(df_plot, aes(x = topterms, y = Freq)) + geom_bar(stat = "identity") + theme_bw() + labs(x = "Frequency of term", y = "Number of terms")
```

## R1C16 I really think the presentation would be more effective if it did not have results/discussions and then more results/discussions, and then a general discussion. We are not really dealing with different studies.

## R1C17 Page 20, the first full paragraph is a good example of text that is meant to show a contribution when it actually does not. Being the first or one of the first is not a contribution. What is more important is the actual finding. I realize that the focus here is on the method. But, being the first to use a method is not a contribution. What is important to highlight is the findings that come from the method, from the study.

## R1C18 Page 21, the political push for open science is not really a point that is relevant. If the authors wanted to review the actual papers, they could. They just need to identify the papers, download them, and search. Right? At any rate, I would avoid making political statements that, essentially, make the point that others should make their data available so that authors who use this method could use their method. Much of what is said here is not really reading well.

We understand that the Reviewer had interpreted this point as a political push for open science. It was not intended as such, and we have attempted to address this comment by rewriting this section. We have also attempted to clarify the important methodological implications of (lack of) open access for text mining analysis of scientific publications.
Availability of large datasets is crucial for machine learning approaches. As such, one of the major bottlenecks for more widespread / more in-depth application of text mining to scientific publication is the limited access to full text papers.

1) According to Archambault and colleagues (https://www.science-metrix.com/pdf/SM_EC_OA_Availability_2004-2011.pdf), only 36% of papers in the general social sciences are published in open access journals. In the present corpus, the proportion of papers published in directory of open access journals (DOAJ) was even lower, 10%. The remainder of publications is behind paywalls, thus requiring additional financial resources and manpower to access.
2) Even for papers that are available under open access licenses, there is no unified API for accessing the text. The reviewer's suggestion that authors can "just [...] identify the papers, download them, and search. Right?" is not scalable. Assuming that it would take only 10 minutes to find, download, and archive the full text, it would have taken 131.35 working days to assemble the corpus for the present study (6305 papers * 10 minutes)/(60 minutes * 8 hours per day). To manually curate a larger dataset, such as CORD-19 (publications about the coronavirus), would take 8333.33 days (400.000+ papers * 10 minutes)/(60 minutes * 8 hours per day).

## R1C19 in the end, it ends up looking like the authors are "hiding the ball". The real issue is what is actually being added to theory? What are the important findings here? What are the practical findings that emerge from this process that are worth making this type of analysis.  I just end up not convinced here.

Response: (hiding the ball = hiding evidence)

## R1C20 The conclusion note that the method charts "unknown territories". Sure that is not the case because the study relies on the published studies.

This is based on a misunderstanding about the level of analysis. We are not charting "unknown territories" with regard to predictors of emotion dysregulation, but with regard to which of those predictors are acknowledged as being relevant in the theoretical / review literature.

## R1C21 I really get a sense of over-selling. The authors should, again, focus on what is actually found that is useful about the topic. There is an example made of emerging themes and fringes, with the example given the little focus on fathers. That may be true, but there was not really a study needed to show that point, as it is well known that the field focuses on primary caretakers (mothers/women).  The conclusion ends with noting that others have noted a need for an overarching theory; but that is what is the apparent contribution being made here; the author does not really get to that and address it; there is no sense of a contribution being made to theory.

Our argument is precisely that the method used here identifies themes that

### 2021-02-13 manuscript.Rmd
Continued revision

@@
 thereby "mapping" phenomena relevant to adolescent emotion regulation.
-Note that this study is inductive or exploratory,
-as opposed to deductive or confirmatory research, and as such does not test any hypotheses [see De Groot's work on the empirical cycle @degrootMethodologieGrondslagenVan1961][^Note that aside from induction, the term "abduction" is also used in the methodological literature.
+Note that this study is inductive (exploratory),
+as opposed to deductive (confirmatory) research, and as such does not test any hypotheses [see De Groot's work on the empirical cycle @degrootMethodologieGrondslagenVan1961][^Note that aside from induction, the term "abduction" is also used in the methodological literature.
 Injunction pertains to inferences based purely on statistical data, whereas abduction additionally involves the attribution of observations to explanatory principles.].
+
 <!--The distinction between inductive and deductive research has recently been recast as a "creativity-verification" cycle [@wagenmakersCreativityVerificationCyclePsychological2018].-->
@@
 
+As the purpose of inductive research is to inform hypothesis generation,
+this approach affords the researcher with substantial creativity [@wagenmakersCreativityVerificationCyclePsychological2018].
+This means that subjective decisions are made throughout the analysis process.
+To ensure that all such decisions are properly documented,
+we have made all code, data, and the historical record of this project publicly available in an online research repository at [masked]. 
 We used the Workflow for Open Reproducible Code in Science [WORCS, @vanlissaWORCSWorkflowOpen2020]
-to ensure transparency and  reproducibility.
-All analyses are strictly reproducible,
-and the code, data, and historical record of this project are available online at [masked].
+to make the analyses strictly reproducible.
+We encourage reuse of the analysis code,
+and secondary analysis of the data.
 
@@
 
-# Analysis 1: Author keyword mapping
+# Analysis 1: Author keywords
 
@@
 
-if(run_everything){
 # Frequency of word by doc
@@
   dtm <- udpipe::document_term_matrix(document_term_frequencies(nounbydoc))
-
+  term_freq <- table(colSums(dtm))
   # Continue plotting word frequency ----------------------------------------
@@
   dtm_top <- dtm_top[rowSums(dtm_top) > 0, ]
+
+if(run_everything){
+
+  term_freqtop <- table(colSums(dtm_top))
+  term_freq <- as.data.frame.table(term_freq)
+  term_freq$pruned <- term_freq$Var1 %in% names(term_freqtop)
+  saveRDS(term_freq, "study1_term_freq_dist.yml")
   write_yaml(dim(dtm_top), "study1_dtm_top.yml")
@@
 # Co-occurrence -----------------------------------------------------------
+set.seed(52)
+cooc <- create_cooc(dtm_top)
+tmp <- cooc == 0
+total_cooc <- sum(tmp[lower.tri(tmp)])
+cooc <- select_cooc(cooc, q = .975)
+tmp <- cooc == 0
+total_cooc <- c(total_cooc, sum(tmp[lower.tri(tmp)]))
 
 if(run_everything){
-  set.seed(52)
-  cooc <- select_cooc(create_cooc(dtm_top), q = .975)
   write.csv(as.matrix(cooc), "s1_cooc.csv")
@@
 dtm_top <- read_yaml("study1_dtm_top.yml")
+term_freq_dist <- readRDS("study1_term_freq_dist.yml")
 ```
@@
 The corpus for this first analysis consisted of author-provided keywords.
-We extracted keywords by document, and applied an exclusion filter of methodological terms and similar non-substantive words.
+We extracted keywords by document,
+and applied an exclusion filter of methodological terms and similar non-substantive words.
 The resulting corpus consisted of `r number_docs_words[1]` documents with `r number_docs_words[2]` unique terms.
 One important step in reviewing the literature is to examine heterogeneity of the corpus;
-to analyze empirically whether there is, for example, a clear divide between psychiatric and developmental texts.
+to determine whether there is, for example, a clear divide between psychiatric and developmental texts.
 To this end, we conducted topic modeling using latent dirichlet allocation [@bleiLatentDirichletAllocation2003].
-However, as no subcorpora could be identified (see [online supplemental material]()), we proceed with an analysis of the whole sample.
-
-<!--## Structural topic modeling
-
-One important step before reviewing the literature is to examine heterogeneity in the corpus;
-for example, whether there is a clear divide between psychiatric and developmental texts.
-To test for heterogeneity, we conducted topic modeling using latent dirichlet allocation [@bleiLatentDirichletAllocation2003].
-This is a clustering method for large sparse matrices.
-We used the term frequency/inverse document frequency (TF-IDF) to select terms
-used frequently in a document, but not used frequently in the corpus,
-which could therefore be more diagnostic of subgroup membership.
-Selection terms with an TF-IDF greater than the median resulted in a corpus of `r lda_dims[1]` documents and `r lda_dims[2]` terms.
-We considered a range from 2-20 topics, evaluating fit based on the BIC, and interpretability based on the entropy of the posterior document/topic probabilities.
-The BICs followed a near-perfect linearly increasing trend, indicating that no subcorpora could be identified.
-Congruently, all entropies were near-zero, which means that the posterior document/topic probabilities were effectively uniformly distributed.
-Thus, no subcorpora could be identified,
-and we proceed with an analysis of the whole sample.-->
+However, as no subcorpora could be identified (see [online supplement](https://github.com/cjvanlissa/veni_sysrev/blob/master/topic_models.md)), we proceed with an analysis of the whole sample.
 
@@
 ```
-To identify what issues are covered in this corpus,
+
+To identify what phenomena are represented in this corpus,
 we examined the terms occurring in the largest number of texts.
-
-Then, we used a dictionary to classify related terms.
-The dictionary describes `r length(dict)` terms using `r length(unlist(dict))`
-regular expression queries.
-After classification,
-
-The total number of unique terms after dictionary encoding was 
-We modeled word frequency using a negative binomial distribution,
+To classify related terms, we used a dictionary which describes `r length(dict)` terms using `r length(unlist(dict))` regular expression queries.
+After dictionary encoding, the remaining number of unique terms was `r length(unique(df$word_coded))`.
+To reduce the number of terms to a more manageable set,
+we modeled word frequency using a negative binomial distribution,
 and retained those exceeding the $97.5^{th}$ percentile.
-This cut-off criterion is arbitrary, but necessary to reduce the number of terms considered from 5299.
-This resulted in `r dtm_top[2]` terms, which occurred in `r dtm_top[1]` documents.
+This corresponded to terms occurring in at least `r min(as.numeric(term_freq_dist$Var1)[term_freq_dist$pruned])` documents.
+This is a subjective criterion,
+but compared to the common practices of either retaining a fixed number of terms or pruning terms below a fixed frequency [see @benoitQuantedaPackageQuantitative2018],
+it has the advantage of being responsive to the empirical distribution of term frequencies.
+Note that the vast majority of pruned terms (`r term_freq_dist$Freq[1]`) occurred only once in the corpus.
+Pruning resulted in `r dtm_top[2]` remaining terms, which occurred in `r dtm_top[1]` documents.
 The issues covered in this body of literature are visualized in Figure \@ref(fig:varimps).
@@
 which represents how frequently words occurred within the same document (see Figure \@ref(fig:allnetworks)).
+In total, there were `r total_cooc[1]` co-occurrence relationships.
 To aid interpretability, we again pruned small coefficients using a negative binomial distribution,
 retaining co-occurrences exceeding the $97.5^{th}$ percentile.
+Note that this is a subjective criterion, which corresponded to terms that co-occurred in more than `r attr(cooc, "thres")` documents.
+After pruning, `r total_cooc[2]` co-occurrence relationships remained.
+
 To stimulate further reflection on the role of each construct,
-we manually classified each of the selected terms as either a putative 'Cause', 'Outcome', 'Protective factor', or 'Indicator' of emotion regulation.
+we categorized each of the remaining terms as either a putative 'Cause', 'Outcome', 'Protective factor', or 'Indicator' of emotion regulation,
+following the same procedure we used to classify phenomena discussed in the theoretical literature.
 We stress that this classification is based on our subjective reading of the literature,
@@
 ```
-
-## Results
-
-Emotion regulation and associated mental health-related outcomes were foremost among the common terms in the corpus (Figure \@ref(fig:varimps)). 
-Other frequent terms reflect important themes discussed in the theoretical review of the literature;
-for instance, the terms *neural*, *parenting*, and *stress* correspond to themes discussed by  @coe-odessEmergentEmotionsAdolescence2019:
-Neurocognitive development, the role of the parents, and adolescents' increased stress response.
-Importantly, the most common terms also include several concepts not featured prominently in the theoretical review.
-For example, *ADHD/CD* [cf.
-@braetEmotionRegulationChildren2014], *substance* use [cf.
-@coe-odessEmergentEmotionsAdolescence2019; @pierrehumbertStrategiesEmotionRegulation2002], and *minority status* [cf.
-@myersEthnicitySocioeconomicStatusrelated2009; @myersEthnicitySocioeconomicStatusrelated2009] are common in the corpus,
-but featured less prominently in the theoretical review.
-
-Based on the co-occurrence graph (Figure \@ref(fig:allnetworks)),
-emotion regulation is evidently a central construct
-to which most other constructs are directly linked.
-This suggests that our search successfully identified factors relevant for adolescents’ emotion regulation.
-The remaining graph is notably sparse, with few interconnections between terms.
-
-## Discussion
-
-This first analysis used author keywords to map common topics in the literature pertaining to adolescents' emotion regulation.
-The results reflected some of the constructs commonly accepted as relevant in theoretical literature and empirical reviews - particularly those pertaining to neurodevelopment and socialization.
-The most frequently occurring words were classified as potential outcomes of emotion regulation difficulties, and revealed a theme related to mental health.
-This validates the notion that adolescent emotion regulation is implicated in a range of mental health problems, which underlines the importance of this area of research.
-
-In addition to the themes addressed in the theoretical Introduction,
-several novel themes emerge from this analysis. 
-Developmental disorders constitute such a theme, as ADHD/CD and autism are ranked highly.
-Another theme is the role of physical health (sic), also reflected in terms like sleep, sports, and disability status.
-External stressors are another important theme, reflected in bullying, stress, PTSD, abuse, violence, life events, historic events (e.g., earthquakes, war), and parenting stress.
-Structural disadvantage is certainly a factor overlooked in existing theory,
-and is reflected in minority status, disability status, socio-economic status, adoption status, sexual diversity, and the adorementioned developmental disorders, as neuroatypical individuals may also experience such disadvantage.
-These insights illustrate how inductive reviews may complement existing theory and narrative reviews, and can reveal blindspots.<!-- SH: this point/advantage needs to feature more prominently in the introduction!-->
-
-The co-occurrence graph revealed few connections among topics.
-Many constructs were only linked with emotion regulation,
-and there were relatively few interconnections between elements.
-This observation substantiates the prior claim that this literature is somewhat fragmented [@bussTheoriesEmotionalDevelopment2019]. 
-This sparse property of the network explains, in part,
-why some of the most prevalent terms based on term document frequency
-are absent from the co-occurrence graph (see Figure \@ref(fig:varimps)).
-This does not mean that these terms are unimportant.
-Rather, it suggests that they are not yet well-integrated in the broader literature on adolescents' emotion regulation,
-and are therefore prime candidates for future research.
-Several of these excluded constructs indeed represent active ongoing areas of research, including research on *fathers* [@vanlissaRoleFathersMothers2019], *identity* [@campbellFriendsEducationIdentity2019], *friendship* and *social support* [@wangBidirectionalEffectsExpressive2020], *autonomy* [@vrolijkLongitudinalLinkagesFather2020a; @brenningPerceivedMaternalAutonomy2015], *sexual risk* [@brownDepressiveSymptomsPredictor2006], and *loneliness* [@spithovenItAllTheir2017].
-<!-- RK: Or could they also suggest that they were relevant in the past, but not any longer? Might it be important to run sensitivity analyses by publication year?
-One recommendation for future research might be to study such important but unembedded constructs
-in conjunction with other more well-established constructs,
-as such an approach might help fill gaps in existing knowledge.-->
 
@@
 dtm <- udpipe::document_term_matrix(document_term_frequencies(nounbydoc))
+
 topterms <- colSums(dtm)
+term_freq <- table(topterms)
 topterms <- sort(topterms, decreasing = TRUE)
@@
 dtm_top <- dtm_top[rowSums(dtm_top) > 0, ]
+
+term_freqtop <- table(colSums(dtm_top))
+term_freq <- as.data.frame.table(term_freq)
+term_freq$pruned <- term_freq[[1]] %in% names(term_freqtop)
+write_yaml(term_freq, "study2_term_freq_dist.yml")
 
@@
 set.seed(5646)
+cooc <- create_cooc(dtm_top)
+tmp <- cooc == 0
+total_cooc_2 <- sum(tmp[lower.tri(tmp)])
 cooc <- select_cooc(create_cooc(dtm_top), q = .975)
+tmp <- cooc == 0
+total_cooc_2 <- c(total_cooc_2, sum(tmp[lower.tri(tmp)]))
 
@@
 lda_dims_2 <- read_yaml("Study2_lda_dims.txt")
+term_freq <- read_yaml("study2_term_freq_dist.yml")
 
@@
 comes to extracting relevant information.
-To perform feature extraction,
-we first applied the natural language processing technique "part-of-speech tagging" (POS-tagging), which identifies a word's grammatical function within the sentence context.
+It has been shown that retaining nouns and adjectives generally helps derive more interpretable text mining models [@martinMoreEfficientTopic2015].
+For example, nouns help capture terms like "emotion", and adjectives help capture the "mental" in "mental health".
+We therefore applied the natural language processing technique "part-of-speech tagging" (POS-tagging) to identify each word's grammatical function within the sentence context.
 Because our analysis sought to identify phenomena,
-we retained only nouns (to capture terms like "emotion") and adjectives (to capture the "mental" in "mental health").
-Retaining nouns and adjectives generally helps derive more interpretable text mining models [@martinMoreEfficientTopic2015].
+
 Finally, we used stemming to reduce the retained terms to their root form.
-As in Analysis 1, we tested for heterogeneity using latent dirichlet allocation - but no subcorpora were identified ([see online supplement]()).
-
-## Identifying keywords
+As in Analysis 1, we tested for heterogeneity using latent dirichlet allocation - but no subcorpora were identified ([see online supplement](https://github.com/cjvanlissa/veni_sysrev/blob/master/topic_models.md)).
+
+## Feature engineering
 
@@
 To identify more meaningful units of analysis,
-we applied the `textrank` algorithm [@wijffelsTextrankSummarizeText2019], an extention of Google's PageRank [@pageMethodNodeRanking2006], to identify relevant $n$-grams (with $n \leq 3$).
+we applied the `textrank` algorithm [@wijffelsTextrankSummarizeText2019],
+an extension of Google's PageRank [@pageMethodNodeRanking2006],
+to identify relevant $n$-grams (with $n \leq 3$).
+This is sufficient to capture trigrams, like "parent-child conflict",
+but would not capture quardragrams like "parent-child conflict resolution".
 The resulting $n$-grams were merged with the original data.
+
+## Identifying common terms
+
 After applying the dictionary and exclusion filter as explained in Analysis 1,
 the resulting corpus consisted of `r number_docs_words2[1]` documents with `r number_docs_words2[2]` unique words.
-Terms exceeding the $97.5^{th}$ percentile of a negative binomial distribution were retained for analysis.
+Again, we used the $97.5^{th}$ percentile of a negative binomial distribution 
+as a (subjective) threshold for pruning the least common terms,
+which corresponded to terms occurring in more than `r max(as.numeric(term_freq[[1]][!term_freq$pruned]))` documents.
 The identified important keywords are displayed in Figure \@ref(fig:varimps).
@@
 
-We constructed a term co-occurrence matrix following the procedure described in Analysis 1;
-Figure \@ref(fig:allnetworks) displays the resulting matrix as a force directed graph.
+We constructed a term co-occurrence matrix following the procedure described in Analysis 1.
+In total, there were `r total_cooc_2[1]` co-occurrence relationships.
+We again pruned small coefficients below the $97.5^{th}$ percentile of a negative binomial distribution.
+This is a subjective criterion, which corresponded to terms that co-occurred in more than `r attr(cooc, "thres")` documents.
+After pruning, `r total_cooc[2]` co-occurrence relationships remained.
+Figure \@ref(fig:allnetworks) displays the resulting co-occurrence matrix as a force directed graph.
 
@@
 
+In the analysis of author keywords (Analysis 1),
+emotion regulation and associated mental health-related outcomes were foremost among the common terms in the corpus (Figure \@ref(fig:varimps)). 
+Other frequent terms reflect important themes discussed in the theoretical review of the literature;
+for instance, the terms *neural*, *parenting*, and *stress* correspond to themes discussed by  @coe-odessEmergentEmotionsAdolescence2019:
+Neurocognitive development, the role of the parents, and adolescents' increased stress response.
+Importantly, the most common terms also include several concepts not featured prominently in the theoretical review.
+For example, *ADHD/CD* [cf.
+@braetEmotionRegulationChildren2014], *substance* use [cf.
+@coe-odessEmergentEmotionsAdolescence2019; @pierrehumbertStrategiesEmotionRegulation2002], and *minority status* [cf.
+@myersEthnicitySocioeconomicStatusrelated2009; @myersEthnicitySocioeconomicStatusrelated2009] are common in the corpus,
+but featured less prominently in the theoretical review.
+
+<!-- Results 2 -->
+
 ```{r}
@@
 
-Based on term document frequency, there was substantial agreement between the findings of Analysis 1 and 2;
-$`r oneintwo`\%$ of the most frequent terms identified in the author keywords
+In the analysis of abstracts (Analysis 2),
+emotion regulation and associated mental health-related outcomes were evidently the most common terms.
+There was substantial agreement between the most common terms identified in the analysis of author keywords and abstracts.
+Specifically, $`r oneintwo`\%$ of the most frequent terms identified in the author keywords
 were also present in the abstracts,
 and conversely, $`r twoinone`\%$ of the most frequent terms from the abstracts were present in the keywords.
-In the corpus of abstracts,
-emotion regulation and associated mental health-related outcomes were evidently the most common terms.
-The term *neural* again occurred frequently.
-The term *sex* was more frequent than in Analysis 1,
-suggesting that sex differences are regularly reported in Abstracts.
-The term *parenting*, which ranked highly in the preceding keyword Analysis, was displaced by *mothers* amonst the top-ranking terms.
-This suggests that when the keyword *parenting* is used,
-the abstract will often reveal that this was operationalized in terms of mothering [as noted by @pleckPaternalInvolvementRevised2004].
+There were also some differences;
+for instance, the term *sex* was more frequent than in Analysis 1,
+suggesting that sex differences are regularly reported in Abstracts even if they are not mentioned in the keywords.
+The term *parenting*, which ranked highly in the keyword analysis, was displaced by *mothers* in the analysis of abstracts.
+This reflects Pleck's  [-@pleckPaternalInvolvementRevised2004] observation that parenting is most often operationalized in terms of mothering.
+<!-- end results 2 -->
+
+According to the term co-occurrence graph of the keyword analysis (Figure \@ref(fig:allnetworks)),
+emotion regulation is evidently a central construct
+to which most other constructs are directly linked.
+This suggests that our search successfully identified factors relevant for adolescents’ emotion regulation.
+The remaining graph is notably sparse, with few interconnections between terms.
 
@@
 
-Inspecting the co-occurrence graph for the keyword data,
-we see a much sparser network than in Analysis 1, with a different structure.
-We now see that dysregulation and mental health-related terms form a central axis,
-and that many related terms are connected to this axis, but not always directly to
-dysregulation. Only the terms *neural*, *mothers*, *attachment* and *ptsd* are 
+Compared to the keyword co-occurrence graph,
+the analysis of abstracts revealed a much sparser network, with a different structure.
+In Analysis 2, dysregulation and mental health-related terms formed a central axis.
+Many relevant terms were connected to this axis, but not directly to
+dysregulation (as was the case in Analysis 1). 
+Only the terms *neural*, *mothers*, *attachment* and *ptsd* are 
 connected directly to dysregulation.
+<!--THIS IS NOT IN THE RESULTS FOR ANALYSIS 1 
 Again, many prevalent terms were absent from the co-occurrence graph,
-as they were not strongly related to any other terms (see Figure \@ref(fig:varimps)).
+as they were not strongly related to any other terms (see Figure \@ref(fig:varimps)). -->
 
@@
 
+The present study used a text mining systematic review (TMSR)
+to identify the most relevant phenomena in the literature on adolescent emotion regulation,
+and used co-occurrence graphs to map conceptual associations between these phenomena.
+We conducted a systematic search of the literature,
+and followed similar procedures to analyze author keywords (Analysis 1) and abstracts (Analysis 2) of the resulting corpus.
+
+We considered term frequency to be indicative of a phenomenon's relevance.
+In line with this interpretation, the results of both analyses
+reflected some of the constructs commonly accepted as relevant in theoretical literature and empirical reviews - particularly those pertaining to neurodevelopment and socialization.
+Some of the most frequently occurring terms were classified as potential outcomes of emotion regulation difficulties, and revealed a theme related to mental health.
+This validates the notion that adolescent emotion regulation is implicated in a range of mental health problems [lee, aldao], which underlines the importance of this area of research.
+
+Our analyses of term frequency also identified several novel themes,
+which were underrepresented in the theoretical literature reviewed in the Introduction.
+One such theme pertains to developmental disorders, such as ADHD/CD and autism.
+This theme recurred in both analyses, although its constituent terms were ranked more highly in the analysis of author keywords as compared to the abstracts.
+Another theme revolved around adolescents' physical health (sic), which was also reflected in terms like sleep, sports, and disability status.
+Again, terms related to physical health were ranked more highly in the keyword analysis than in the abstract analysis.
+External stressors were another important theme, reflected in terms like bullying, stress, PTSD, abuse, violence, life events, historic events (e.g., earthquakes, war), parenting stress, and divorce.
+Finally, one emergent theme that appears to be underrepresented in existing theory is structural disadvantage.
+This theme was reflected in terms like minority status and discrimination, disability status, socio-economic status, adoption status, and sexual diversity. 
+The adorementioned developmental disorders are also relevant in this context, as neuroatypical individuals may also experience such disadvantage [@cappadociaBullyingExperiencesChildren2012].
+
+Our analyses of abstracts identified three additional themes not represented in the analysis of keywords.
+The first of these themes revolved around addictive behavior, with indicators *substance use* and *device use*.
+The second theme pertained to identity and moral development, two topics with a common root in theory [@lapsleyMoralIdentityDevelopmental2015].
+This theme is also reflected by the terms *values* and *personality*.
+Finally, sexual development emerged as a theme. Aside from the high-ranking construct (biological) *sex*, this theme was reflected in the terms *puberty*, *sexual diversity*, and *romantic*.
+These insights illustrate how inductive reviews can identify under-theorized areas,
+thereby complementing existing theory and narrative reviews.
+
+<!-- 
 This second analysis focused on the abstracts of the reviewed articles.
@@
 
-A new theme emerging from this analysis is addictive behavior, with highly ranked indicators *substance use* and *device use*.
-Another new theme pertains to identity and moral development, two topics with a common root in theory [@lapsleyMoralIdentityDevelopmental2015].
-This theme is also reflected by the terms *values* and *personality*.
-Finally, sexual development emerges as a theme. Aside from the high-ranking construct (biological) *sex*, this theme is reflected in the terms *puberty*, *sexual diversity*, and *romantic*.
+-->
+
+The co-occurrence graph revealed few connections among topics.
+Many constructs were only linked with emotion regulation,
+and there were relatively few interconnections between elements.
+This observation substantiates the prior claim that this literature is somewhat fragmented [@bussTheoriesEmotionalDevelopment2019]. 
+This sparse property of the network explains, in part,
+why some of the most prevalent terms based on term document frequency
+are absent from the co-occurrence graph (see Figure \@ref(fig:varimps)).
+This does not mean that these terms are unimportant.
+Rather, it suggests that they are not yet well-integrated in the broader literature on adolescents' emotion regulation,
+and are therefore prime candidates for future research.
+Several of these excluded constructs indeed represent active ongoing areas of research, including research on *fathers* [@vanlissaRoleFathersMothers2019], *identity* [@campbellFriendsEducationIdentity2019], *friendship* and *social support* [@wangBidirectionalEffectsExpressive2020], *autonomy* [@vrolijkLongitudinalLinkagesFather2020a; @brenningPerceivedMaternalAutonomy2015], *sexual risk* [@brownDepressiveSymptomsPredictor2006], and *loneliness* [@spithovenItAllTheir2017].
+<!-- RK: Or could they also suggest that they were relevant in the past, but not any longer? Might it be important to run sensitivity analyses by publication year?
+One recommendation for future research might be to study such important but unembedded constructs
+in conjunction with other more well-established constructs,
+as such an approach might help fill gaps in existing knowledge.-->
+
+<!-- Study 2 -->
 
@@
 This issue is beyond the scope of the present study -->
-The present study systematically reviewed the literature,
-and used text-mining to map constructs related to adolescent emotion regulation.
+
 The results of this inductive approach echoed many of the constructs considered

### 2021-02-13 word_functions.R

@@ -47,7 +47,9 @@ select_cooc <- function(cooc, q = .95){
   rownames(out) <- rownames(cooc)
   colnames(out) <- colnames(cooc)
   is_zero <- rowSums(out) == 0
-  return(out[!is_zero, !is_zero])
+  out <- out[!is_zero, !is_zero]
+  attr(out, "thres") <- thres
+  return(out)
 }
 
 create_cooc <- function(dtm){

### 2021-02-23 action_letter.Rmd
Update

@@
 output: html_document
+bibliography      : ["veni_sysrev.bib"]
 ---
+
+```{r, include = FALSE}
+library(yaml)
+library(ggplot2)
+```
 
@@
 
-Response: We apologize; the keywords were not retained when converting the manuscript to the required format for ADRR. We have reinstated them.
+Response: We apologize for the oversight; the keywords were not retained when converting the manuscript to the required format for ADRR. We have reinstated them.
 
@@
 
+4) The revised Limitations section now addresses this issue:
+
+> Of course, the present study also has limitations.
+One limitation is that several subjective decisions were made throughout the analysis process.
+This limitation is inherent to inductive studies, however [e.g., @wagenmakersCreativityVerificationCyclePsychological2018]:
+There are infinite possible ways to conduct exploratory analysis,
+and researchers have considerable creative license in doing so.
+We have attempted to address this limitation by explicitly mentioning important decisions in the manuscript,
+and by making all analysis code and data publicly available,
+so that others may explore the effect of different analysis strategies.
+
 ## R1C14 At the bottom of page 12, it is clear that a decision is made in terms of retaining within a percentile.
@@
 Please see our response to the previous comment.
-Additionally, note that nearly all pruned terms occurred in only one document,
+Additionally, note that the majority of the pruned terms occurred in only one document,
 as can be seen in the plot below.
@@
 ```{r}
-df_plot <- as.data.frame(term_freq)
+df_plot <- cbind(as.data.frame(read_yaml("study1_term_freq_dist.yml")), Analysis = "Analysis 1")
+names(df_plot)[1] <- "topterms"
+df_plot <- rbind(df_plot, cbind(as.data.frame(read_yaml("study2_term_freq_dist.yml")), Analysis = "Analysis 2"))
 df_plot <- df_plot[!df_plot$pruned, ]
-ggplot(df_plot, aes(x = topterms, y = Freq)) + geom_bar(stat = "identity") + theme_bw() + labs(x = "Frequency of term", y = "Number of terms")
+df_plot$topterms <- ordered(df_plot$topterms, levels = sort(as.numeric(unique(df_plot$topterms))))
+ggplot(df_plot, aes(x = topterms, y = Freq)) + geom_bar(stat = "identity") + theme_bw() + labs(x = "Frequency of term", y = "Number of terms") + facet_wrap(~Analysis, scales = "free")
 ```
@@
 We are not really dealing with different studies.
+
+Response: We have attempted to address the Reviewer's comment by writing a single Results and Discussion section, instead of separate sections for each analysis.
+As this change spans several pages, we do not cite the entire revised section here, but refer to the revised manuscript.
 
@@
 
+Response:
+
 ## R1C18 Page 21, the political push for open science is not really a point that is relevant.
@@
 
-We understand that the Reviewer had interpreted this point as a political push for open science.
-It was not intended as such, and we have attempted to address this comment by rewriting this section.
+Response: This is an important comment, which we will address in four main points.
+
+First, the Reviewer writes that "the political push for open science is not really a point that is relevant." We agree with this sentiment. Our writing was not intended as such,
+and we have rewritten the offending section to avoid misunderstanding.
+In particular, we have removed the more general term "open science",
+as we are really speaking only of open access publishing.
+
+Second, although the *political* implications of open access publishing are not relevant here,
+its *methodological* implications are.
+In order to conduct meta-scientific research of any kind - be it systematic reviews, meta-analyses, or indeed text-mining - publications must be accessible.
+Open access publishing thus has methodological implications for meta-scientific research,
+and as such, is well within scope of the Limitations section of the present paper.
+<!-- Third, there is little reason for a political push towards open science.
+Adolescent Research Review [is a hybrid open access journal](https://www.springer.com/journal/40894/open-access-publishing),
+and all stakeholders involved in this publication are committed to open science,
+including [our host university](https://www.uu.nl/en/research/open-science),
+the [body that funded this research](https://www.nwo.nl/en/open-science),
+the [Dutch government](https://www.rijksoverheid.nl/documenten/publicaties/2019/01/28/nieuwsgierig-en-betrokken),
+the [European Union](https://ec.europa.eu/info/research-and-innovation/strategy/goals-research-and-innovation-policy/open-science_en),
+and the [APA](https://www.apa.org/pubs/journals/resources/open-science).
+At this stage, open access can be considered a mainstream position,
+but it is still relevant to discuss its implications for meta-research.-->
+
+Third, the Reviewer writes "If the authors wanted to review the actual papers, they could [just] identify the papers, download them, and search. Right?".
+Unfortunately, the approach suggested by the Reviewer is not feasible, for two reasons.
+
+* The proposed approach is not scalable: Assuming that it would take only 10 minutes to find, download, and archive a full-text publication, it would have taken 131.35 working days to assemble the corpus for the present study (6305 papers * 10 minutes)/(60 minutes * 8 hours per day).
+To manually curate a larger dataset, such as CORD-19 (publications about the coronavirus), would take 8333.33 days (400.000+ papers * 10 minutes)/(60 minutes * 8 hours per day).
+As we suggest, an API - a programmatic interface for downloading full-text publications - would overcome this bottleneck.
+* It is important to consider that not every scholar has the privilege to simply download papers.
+Aside from the *cost* of the aforementioned man-hours (which could be addressed by the API we propose), not everyone has comprehensive access to paywalled publications.
+Thus, such research could only be conducted at the world's most well-funded universities.
+
+Finally, the Reviewer has apparently misinterpreted our comment about open access publishing as a demand that "others should make their data available so that authors who use this method could use their method".
+This is a simple misunderstanding.
+We are not discussing open data,
+but open access publishing.
+Discussing the benefits of open access publishing for meta-scientific research should not be a contentious or policital topic in a meta-scientific journal [with a hybrid open access policy](https://www.springer.com/journal/40894/open-access-publishing) like Adolescent Research Review.
+
+<!--even for papers that are available under open access licenses, there is no unified API for accessing the text. 
+A
+Such changes would enable meta-scientific research of far greater complexity than the present study.-->
+<!--We believe that this comment is well within the scope of the present paper.
+As an argument by analogy, it is common for cross-sectional studies to call for future longitudinal research.
+Since our method depends on the automated processing of scientific publications,
+factors that would enable researchers to automatically process scientific publications are relevant future directions.
+As such, we believe this comment to be within the scope of the present paper.
+
+-->
+<!--We have attempted to address this comment by rewriting this section.
+
 We have also attempted to clarify the important methodological implications of (lack of) open access for text mining analysis of scientific publications.
-Availability of large datasets is crucial for machine learning approaches.
+Availability of large datasets is crucial for text mining and other machine learning approaches.
 As such, one of the major bottlenecks for more widespread / more in-depth application of text mining to scientific publication is the limited access to full text papers.
@@
 In the present corpus, the proportion of papers published in directory of open access journals (DOAJ) was even lower, 10%.
-The remainder of publications is behind paywalls, thus requiring additional financial resources and manpower to access.
-2) Even for papers that are available under open access licenses, there is no unified API for accessing the text.
-The reviewer's suggestion that authors can "just [...] identify the papers, download them, and search.
-Right?" is not scalable.
-Assuming that it would take only 10 minutes to find, download, and archive the full text, it would have taken 131.35 working days to assemble the corpus for the present study (6305 papers * 10 minutes)/(60 minutes * 8 hours per day).
-To manually curate a larger dataset, such as CORD-19 (publications about the coronavirus), would take 8333.33 days (400.000+ papers * 10 minutes)/(60 minutes * 8 hours per day).
+The remainder of publications is behind paywalls, thus requiring additional financial resources and manpower to access.-->
+
+We have revised this section to avoid giving offense, and to strengthen our argument. The revision now reads:
+
+> One final limitation is that our analysis was limited to keywords and abstracts.
+The primary obstacles to the analysis of full-text publications were limited access to articles behind paywalls,
+and the absence of a standardized Application Programming Interface (API) for the automatic retrieval of articles across publishing outlets.
+<!--As the number of scientific publications on any given topic tends to show exponential increase over time, making it difficult for applied researchers to keep up.
+Meta-scientific analyses of the published literature will likely become increasingly important -->
+Comprehensive access to scientific publications is essential to all meta-scientific research, including classic systematic reviews and meta-analyses (e.g., to avoid bias in summary effect sizes).
+For text mining approaches in particular, the availability of large data sets is crucial.
+<!--Consequently, limited access to full-text publications is a major bottleneck.-->
+One example of a data set suitable for even more complex text mining analyses is a corpus of 400k+ full-text papers on COVID-19 that was made publicly available [@wangCORD19Covid19Open2020].
+Compiling such full-text data sets currently requires substantial manpower and financial resources, thus placing them out of reach for many researchers.
+<!--The authors argued that the sheer volume of available literature made it difficult for individual researchers to remain informed, thus necessitating automated text mining analysis.
+Although our analysis comprised a mere 6305 publications, even this is -->
+<!--As the number of scientific publications tends to grow exponentially across fields [@larsenRateGrowthScientific2010],
+it becomes harder for researchers to remain informed, thus necessitating meta-scientific research.-->
+An increased adoption of open access publishing,
+and the development of a unified API for article retrieval across publishing outlets,
+would facilitate curating full-text data sets.
+These changes would enable more widespread adoption and more informative application of meta-scientific (text mining) analyses.
 
@@
 
-Response: (hiding the ball = hiding evidence)
+Response: The Reviewer comes away with the impression that we are "hiding the ball".
+We regret that our writing raises these concerns about a lack of transparency,
+because we have made thorough efforts to ensure that this adheres to best practices for open science.
+For instance, we have published our data, code, and complete history of this project since its inception in an online repository.
+To make this abundantly clear, the revised manuscript now reads:
+
+> we have made all code, data, and the historical record of this project publicly available in an online research repository at [masked]. 
+We used the Workflow for Open Reproducible Code in Science [WORCS, @vanlissaWORCSWorkflowOpen2020]
+to make the analyses strictly reproducible.
+We encourage reuse of the analysis code,
+and secondary analysis of the data.
+
+Furthermore, the Reviewer understandably asks "what is actually being added to theory?".
+The answer is that we are *not* adding to theory in the present paper, but we are *laying the groundwork* for theory construction.
+Because we did not seek to develop new theory, we had not gone into detail on theory construction methodology in the previous iteration of the manuscript.
+
+We now see that this was a mistake, and that this literature provides necessary context for understanding the purpose of the study.
+We have thus attempted to address this comment by clarifying the relationship between inductive identification of relevant phenomena and formal theory construction:
+
+> There have been recent calls for the consolidation of empirical insights into overarching theory [e.g., @bussTheoriesEmotionalDevelopment2019]. 
+According to formal methods for theory construction [@borsboomTheoryConstructionMethodologya; @haigExploratoryFactorAnalysis2005],
+the first step in this endeavor is to identify the relevant *empirical phenomena*,
+defined as stable and general features of the world [@bogenSavingPhenomena1988].
+We propose that systematic reviews are a suitable method for taking this first step,
+based on the assumption that phenomena currently considered to be most stable and general will be more frequently represented in the literature.
+
+> The first step in theory construction methodology is to identify relevant phenomena [@borsboomTheoryConstructionMethodologya].
+We have argued that text mining systematic reviews are a relatively comprehensive and objective method for identifying such phenomena, because they can evaluate much larger bodies of literature than sentient readers, and are not biased toward pre-existing ideas.s
 
@@
 
-This is based on a misunderstanding about the level of analysis.
-We are not charting "unknown territories" with regard to predictors of emotion dysregulation, but with regard to which of those predictors are acknowledged as being relevant in the theoretical / review literature.
+Response: The point is well-taken.
+We are not charting "unknown territories" at the level of primary research, but we are charting territories underrepresented at the meta-scientific level (i.e., topics rarely addressed in narrative reviews and theory).
+We have attempted to address this comment by rewriting the section as follows:
+
+> Importantly, our results also draw attention to several relevant phenomena that,
+although well-represented in the empirical literature,
+are under-emphasized in narrative reviews and theory.
 
@@
 
-Our argument is precisely that the method used here identifies themes that
+Response: We agree that it is important to clearly communicate what is useful about the present study without over-selling.
+To address this point, we have carefully rewritten all claims about novel contributions.
+
+We are not quite sure what to make of the comment that "there was not really a study needed to show that [there is little focus on fathers], as it is well known that the field focuses on primary caretakers (mothers/women)".
+The Reviewer appears to suggest that we conducted this study in order to show that there is little focus on fathers - but this is not the case.
+We have emphasized throughout the manuscript that our study was inductive (data-driven), with no a-priori expectation about the phenomena we might find.
+We have simply reported the relevant phenomena that emerged from our analysis, and fathers are one of those phenomena.
+It seems relevant to discuss this particular finding in the context of prior work that has *argued* that fathers are underrepresented, but based on narrative reviews, not empirical analysis of the published literature.
+
+<!--Although there is indeed increasing awareness that the field focuses on mothers,
+several authors have argued that this practice is out of step with contemporary Western culture, as fathers are expected to take their responsibility as primary caregivers as well.
+There has thus been a call for increased fatherhood research, along with increased funding an research output.-->
+We further think that the example of fatherhood is particularly instructive, especially because, as the Reviewer points out, "it is well known that the field focuses on primary caretakers (mothers/women)".
+The fact that our analysis picks out a specific theme that is known by many researchers to be just outside the mainstream illustrates the method's ability to detect fringe themes in general,
+and serves as an example to illustrate to readers how this analysis may also pick out other themes about which there is less consensus that they are underrepresented.
+
+Finally, the Reviewer points out that "The conclusion ends with noting that others have noted a need for an overarching theory; but that is what is the apparent contribution being made here; the author does not really get to that and address it; there is no sense of a contribution being made to theory." We have attempted to address this comment by clarifying the intended contribution of the present study (see response to comment R1C4).
+This specific section has been rewritten as follows:
+
+> Finally, several authors have commented on the lack of an overarching theory tailored specifically to adolescent emotion regulation.
+The first step in theory construction methodology is to identify relevant phenomena [@borsboomTheoryConstructionMethodologya].
+We have argued that text mining systematic reviews are a relatively comprehensive and objective method for identifying such phenomena, because they can evaluate much larger bodies of literature than sentient readers, and are not biased toward pre-existing ideas.
+The phenomena identified in the present study might thus serve as a starting point for future theory development.
+Specifically, theorists might revisit existing relevant theory
+and incorporate relevant phenomena as identified in the present analysis.

### 2021-02-27 action_letter.Rmd
Finalize action letter

@@
 date: "2/11/2021"
-output: html_document
+output: bookdown::word_document2
 bibliography      : ["veni_sysrev.bib"]
@@
 
+Dear Prof. Dr. Levesque,
+
+Thank you for considering my manuscript for publication in *Adolescent Research Review*. I genuinely appreciate your personal involvement, and the thorough and critical comments you solicited. 
+I have made a good-faith effort to address all comments as thoroughly as possible, which involved major restructuring and rewriting.
+All changes are explained below.
+We did not discuss a deadline, but I implicitly assumed that two months would be acceptable given the amount of work involved and the additional burden placed upon us by the pandemic.
+I hope that you will find the quality of the work to be sufficiently improved.
+
+Yours sincerely,
+
+Caspar
+
 # Reviewer #1:
 
-## R1C1 The abstract is lacking in two regards:
+**Reviewer 1, comment 1:** The abstract is lacking in two regards:
 
-### R1C1a The actual findings are not reported
+**Reviewer 1, comment 1a:**  The actual findings are not reported
 
-### R1C1b it is not clear how the findings integrate te literature.
+**Response:** As requested, we have summarized the findings in the abstract. The
+abstract now reads:
 
-## R1C2 Key words are not provided.
+>   Adolesence is a developmentally sensititve period for emotion regulation
+  with potentially lifelong implications for mental health and well-being.
+  Although substantial empirical research has addressed this topic, the
+  literature is fragmented across subdisciplines, and an overarching
+  theoretical framework is lacking. The first step towards constructing a
+  unifying framework is identifying relevant phenomena. This systematic
+  review of 6305 papers used text mining to identify phenomena relevant to
+  adolescents' emotion regulation. We first established a baseline of
+  relevant phenomena discussed in theory and recent narrative reviews. We
+  then conducted text mining analyses of article keywords and abstracts,
+  examining term frequency as an indicator of relevance and term
+  co-occurrence as an indicator of association. Results reflected themes
+  commonly featured in theory and narrative reviews, such as socialization
+  and neurocognitive development, but also identified undertheorized themes,
+  such as developmental disorders, physical health, external stressors,
+  structural disadvantage, substance use, identity and moral development, and
+  sexual development. This illustrates how text mining systematic reviews
+  (TMSR), a novel approach, may complement narrative reviews. Future
+  theoretical work might seek to integrate these undertheorized themes into
+  an overarching framework, and empirical research might consider them as
+  promising areas for future research, or potential confounders in research
+  on adolescents' emotion regulation.
 
-Response: We apologize for the oversight; the keywords were not retained when converting the manuscript to the required format for ADRR. We have reinstated them.
+**Reviewer 1, comment 1b:**  it is not clear how the findings integrate te literature.
 
-## R1C3 The title is about dysregulation but the first paragraph is all about regulation. The manuscript would be more effective if it were more consistent.
+**Response:** Perhaps this turn of phrase was somewhat unfortunate.
+When discussing the relevance of the study in the abstract, we now simply state:
 
-Response: We agree that greater consistency would improve the clarity of the writing, and have changed the manuscript to use the more general term "emotion regulation" throughout.
+> Future theoretical work might seek to integrate these undertheorized themes into
+  an overarching framework, and empirical research might consider them as
+  promising areas for future research, or potential confounders in research
+  on adolescents' emotion regulation.
 
-## R1C4 The first paragraph [promises] that the results will help unify theory and address limitations of research areas that the author deems in silos. This is a heavy burden to carry.
+**Reviewer 1, comment 2:** Key words are not provided.
 
-Response: We have interpreted this point as an indirect request that we further clarify the intended contribution of the present study.
-We will address that point below - but first we must clarify that it was not our intention to "promise that our results will help unify theory and address limitations of research areas that the author deams in silos".
-We have attempted to address this misunderstanding by clarifying that these are not our original claims; these are oft-repeated limitations of the existing literature, and our work is a response to these perceived limitations.
-We have included three references to support this point.
-The revision now reads:
+**Response:** We apologize for the oversight; the keywords were not retained when converting the manuscript to the required format for ADRR. We have reinstated them.
 
-> Despite the abundance of empirical work on this issue,
-several authors have pointed out that the literature is somewhat fragmented,
+**Reviewer 1, comment 3:** The title is about dysregulation but the first paragraph is all about regulation. The manuscript would be more effective if it were more consistent.
+
+**Response:** We agree that greater consistency would improve the clarity of the writing, and have changed the manuscript to use the more general term "emotion regulation" throughout.
+
+**Reviewer 1, comment 4:** The first paragraph [promises] that the results will help unify theory and address limitations of research areas that the author deems in silos.
+This is a heavy burden to carry.
+
+**Response:** It was not our intention to give the impression that "our results will help unify theory and address limitations of research areas that the author deams in silos".
+
+First of all, the Reviewer credits us for the observations that research areas are "in silos",
+but this is a commonly mentioned limitation of the existing literature.
+To address this issue, and clarify that this is not our original claim, we have included additional references. The revision now reads:
+
+> Despite the abundance of publications in this field,
+several prior theoretical and empirical reviews have argued that the literature is somewhat fragmented,
 because different (sub)disciplines have approached the issue in disparate ways,
@@
 
-Now, to the main point.
+Second of all, the Reviewer's comments indicate that the intended contribution of the present study was insufficiently clear.
+Our results will not unify theory, but it does lay the foundation for future work that intends to do so, as identification of the relevant empirical phenomena is the first step in theory construction methodology.
 In the revision, we have attempted to clarify the intended contribution of the present study
@@
 
-> There have been recent calls for the consolidation of empirical insights into overarching theory [e.g., @bussTheoriesEmotionalDevelopment2019]. 
-According to formal methods for theory construction [@borsboomTheoryConstructionMethodologya; @haigExploratoryFactorAnalysis2005],
-the first step in this endeavor is to identify the relevant *empirical phenomena*,
+> This has led to recent calls for the consolidation of empirical insights into overarching theory [e.g., @bussTheoriesEmotionalDevelopment2019]. 
+Formal methods for theory construction state that the first step in this endeavor is to identify the relevant *empirical phenomena* [@borsboomTheoryConstructionMethodologya; @haigExploratoryFactorAnalysis2005],
 defined as stable and general features of the world [@bogenSavingPhenomena1988].
 We propose that systematic reviews are a suitable method for taking this first step,
-based on the assumption that phenomena currently considered to be most stable and general will be more frequently represented in the literature.
-[...] The present paper aims to map the empirical phenomena relevant to adolescent emotion regulation, using text mining systematic review.
+based on the assumption that phenomena considered to be stable and general will be more frequently represented in the published literature.<!-- the frequency with which phenomena occur in the literature is indicative of their relevance.-->
+Traditional narrative reviews have some limitations, however, as they been shown to be marred by small convenience samples, confirmation bias,
+and an undue emphasis on positive results [@littellEvidencebasedBiasedQuality2008].
+We intend to overcome these limitations by adopting a novel method:
+the text mining systematic review (TMSR).
 
-## R1C5 The entire section on page 3: it is not clear why this is presented.
+Third of all, the Reviewer's comment indicates that we have raised expectations that we would "address limitations of research areas that the author deams in silos".
+It is not the case.
+A systematic review like the present paper is meta-research.
+Meta-research describes bodies of primary research.
+It therefore cannot address limitations at the level of primary research.
+The only limitation that we address is at the meta-research level: The lack of a comprehensive overview of factors relevant to adolescent emotion regulation in prior theory and reviews.
+We have attempted to address this comment by clarifying the intended contribution of the study throughout the manuscript.
+
+**Reviewer 1, comment 5:** The entire section on page 3: it is not clear why this is presented.
 It could be presented in a brief sentence and likely should because it does not really relate to what is reviewed.
@@
 
-Response: These two paragraphs were intended to substantiate the relevance and scope of the present study.
+**Response:** These two paragraphs were intended to substantiate the relevance and scope of the present study.
 Based on the Reviewer's comment, we now see that this was perhaps redundant with the opening paragraphs, which already provided rudimentary justification of the relevance and scope.
@@
 Given the prevalence of emotion regulation difficulties in adolescence,
-their implications for mental health
+their implications for mental health<!--and social functioning [@braetEmotionRegulationChildren2014]; @reindlSocializationEmotionRegulation2016]-->
 and downstream cost to society,
-it is important to have a comprehensive understanding of the risk factors that render some adolescents more susceptible to emotional difficulties than others.
+it is important to have a comprehensive overview of the factors associated with adolescents' emotion regulation.
 
-## R1C6 The existing theoretical landscape is presented in a way that is unclear how it really relates to the review.
+**Reviewer 1, comment 6:** The existing theoretical landscape is presented in a way that is unclear how it really relates to the review.
 
-Response: We understand that it is essential to clarify why we present this brief theoretical review before diving into the results of the present study.
+**Response:** We understand that it is essential to clarify why we present this brief theoretical review before diving into the results of the present study.
 In order to address this comment, we now explicitly state why a review of the existing theoretical landscape is relevant to the present systematic review. The revised manuscript reads:
 
-> Although there is a paucity of theories *specific to* adolescent emotion regulation,
-several relevant theories are commonly invoked in empirical work [see  @bussTheoriesEmotionalDevelopment2019].
-In order to contextualize the results of our systematic review,
+> Although it has been argued that there is a paucity of theories *specific to* adolescent emotion regulation,
+many *relevant* theories are commonly invoked in empirical work [see  @bussTheoriesEmotionalDevelopment2019].
+In order to contextualize the results of our systematic review
 and assess to what extent the identified phenomena through text mining mirror or complement existing theory,
-we provide a summary review of the existing theoretical landscape.
+we provide a brief review of the existing theoretical landscape.
 
-## R1C8 Figure 1 on page 5: it is not clear why it is there.
+**Reviewer 1, comment 7:** Figure 1 on page 5: it is not clear why it is there.
 It should come after the introduction.
@@
 
-Response: As requested by the Reviewer, we have placed the Figure after the References section, retaining only a placeholder in-text. We also refer to the Figure at the end of the Introduction:
+**Response:** As requested by the Reviewer, we have placed the Figure after the References section, retaining only a placeholder in-text.
+As requested, we also refer to the Figure at the end of the Introduction:
 
-> As can be seen in Figure 1, 
-there are notable parallels between correlates of emotion regulation identified in these
-narrative reviews, and in the preceding theoretical literature.
+> There are notable parallels between phenomena relevant to adolescents' emotion regulation as identified in these
+narrative reviews, and in the preceding theoretical literature, as can be seen in Figure 1.
 
-## R1C9 The figure nicely points to outcomes, indicators, causes and protective factors. That is not clear from the introductory materials.
+**Reviewer 1, comment 8:** The figure nicely points to outcomes, indicators, causes and protective factors. That is not clear from the introductory materials.
 
-Response: In the previous manuscript, we had merged the two Figures from the theoretical Introduction with the two Figures from the Results section in order to facilitate comparisons between the two.
+**Response:** In the previous manuscript, we had merged the two Figures from the theoretical Introduction with the two Figures from the Results section in order to facilitate comparisons between the two.
 We see now that this caused some confusion.
@@
 > In reading the theoretical literature,
-we recorded relevant phenomena,
-and whether these were discussed as putative causes, outcomes, indicators, or protective factors in relation to emotion regulation.
-The left panel of Figure \@ref(fig:figbaseline) visually summarizes the phenomena so identified in the theoretical literature in a style similar to our subsequent systematic review,
+we documented relevant phenomena and whether these were discussed as putative causes, outcomes, indicators, or protective factors in relation to emotion regulation.
+The left panel of Figure 1 visually summarizes the phenomena discussed in the theoretical literature, using a style similar to our subsequent systematic review,
 in order to facilitate contextualizing our original findings.
 
-## R1C10a The section on theory is not presented in a way that would have it appear as authoritative. It reads more like a hodgpode of theories.
+**Reviewer 1, comment 9:** The section on theory is not presented in a way that would have it appear as authoritative. It reads more like a hodgpode of theories.
 
-Response: This is the state of the theoretical landscape: A hodgpodge.
-Others have pointed out that there is an absence of authoritative theories to guide research.
-It would be misleading to give readers the impression that there is a clear, authoritative theoretical framework.
+**Response:** The Reviewer's point is well-taken, and yet one of the main motivations for the present study is the fact that the theoretical landscape *is indeed a bit of a hodgepodge*.
+This has been stressed by several prior reviewers, as pointed out in our response to the Reviewer's 4th comment.
+We feel that any attempt to impose an apparently "authoritative" structure on this messy field would be somewhat misleading, and would undermine the intended contribution of the present study.
+To address the Reviewer's comment, we have substantially edited the theoretical review for increased readability, while explicitly acknowledging the lack of overarching structure.
 
-## R1C10b The section would be stronger if it also gave readers a sense of which theories are deemed important/influential and worth using.
+**Reviewer 1, comment 10:** The section would be stronger if it also gave readers a sense of which theories are deemed important/influential and worth using.
 There needs to be a sense that the important theories are being examined.
 
-Response: Point out how often these theories are cited, perhaps?
+**Response:** We are happy to do so if there is an objective way to do so, but it's not clear what metric should be used.
+Citation counts are obvious but problematic - they are confounded with publication date (favoring Bronfenbrenner and Sameroff),
+some theories are influential but rarely credited (e.g., polyvagal theory),
+and other theories are published by different authors at approximately the same time (e.g., the maturity gap was described approximately simultaneously by Casey, by Crone, and by Cracco).
+We are open to other suggestions.
 
-## R1C11 The first paragraph on page 9 needs to be edited.
+Importantly, as we have argued in the paper, the state of theory in the field is a bit of a "hodgepodge", and much research lacks explicit theoretical foundations.
+The theories that *are* available are limited because they are not uniquely suited to this particular area of research,
+and some are vague but all-encompassing macro-theories (e.g., Bronfenbrenner, Sameroff), and others are concrete and specific, but not embedded in an overarching framework (e.g., Crone, Morris).
+Pending further guidance on how to address this comment,
+we have made an effort to reinforce these points throughout the manuscript.
+
+**Reviewer 1, comment 11:** The first paragraph on page 9 needs to be edited.
 It appears too haphazard.
@@
 
-Response:
+**Response:** We have rewritten this as requested.
+We have attempted to clarify that we are not presenting many different studies, but merely summarizing one seminal literature review, and one recent "update" that covers more recent literature in greater detail.
+We have further organized the phenomena discussed in these two reviews in line with the classification of Bronfenbrenner and Sameroff, introduced in the opening paragraph on relevant theory.
+We thus begin with phenomena at the individual level, followed by proximal influences (microsystem), followed by distal influences (mesosystem and exosystem).
 
-\ToDo
-
-## R1C12 The fundamental problem with the "The present paper" section is that it really does not do what is needed.
+**Reviewer 1, comment 12:** The fundamental problem with the "The present paper" section is that it really does not do what is needed.
 It is a plan of analysis.
@@
 
-Response: We agree with the Reviewer that "The present paper" section was basically a plan of analysis.
-In the Revision, we have rewritten this section to summarize the study design, link it to the study aims, and state the intended outcomes.
-Note that this is an inductive (exploratory) study, and as such,
-it does not test any hypotheses.
-We now explicitly clarify this point in "The present paper".
+**Response:** We agree with the Reviewer that "The present paper" section was basically written as a plan of analysis.
+
+To address this comment, we have rewritten this section to be more in line with the APA guidelines,
+by summarizing the study design, linking it to the study aims, and stating the intended outcomes. 
+Note that we cannot honor the Reviewer's request for hypotheses, because this is an inductive (exploratory) study, and as such, it does not test any hypotheses.
+To avoid confusion about this point, we now emphasize the inductive nature of the study throughout the manuscript, including in "The present paper". This section now reads:
 
@@
 thereby "mapping" phenomena relevant to adolescent emotion regulation.
-Note that this study is inductive or exploratory,
-as opposed to deductive or confirmatory research, and as such does not test any hypotheses [see De Groot's work on the empirical cycle @degrootMethodologieGrondslagenVan1961][^Note that aside from induction, the term "abduction" is also used in the methodological literature.
-Injunction pertains to inferences based purely on statistical data, whereas abduction additionally involves the attribution of observations to explanatory principles.].
+Note that this study is inductive (exploratory),
+as opposed to deductive (confirmatory) research, and as such does not test any hypotheses [see De Groot's work on the empirical cycle @degrootMethodologieGrondslagenVan1961](footnote: Note that aside from induction, the term "abduction" is also used in the methodological literature.
+We consider injunction to refer to inferences based purely on observations (data).
+Abduction differs from induction because it additionally involves the attribution of observations to explanatory principles).
 
-## R1C13 By the time I get to eh methods section, including the beginning of this section, I still see a focus on emotion regulation, not emotion dysregulation that appears in the title.
+**Reviewer 1, comment 13:** By the time I get to eh methods section, including the beginning of this section, I still see a focus on emotion regulation, not emotion dysregulation that appears in the title.
 
-Response: We have addressed this comment as requested; see the response to R1C3.
+**Response:** We have addressed this comment as requested; see the response to R1C3.
 
-## R1C13 As I read the materials on pages 11 and 12, I see a heavy reliance on the computerized analytical system to do the research and coding.
+**Reviewer 1, comment 14:** As I read the materials on pages 11 and 12, I see a heavy reliance on the computerized analytical system to do the research and coding.
 I think it would be helpful to know what decisions are made by the authors and, if there are any, we should know about reliability checks and, if there are none, that still should be noted.
 
-Response: This is a crucial comment with far-reaching implications.
+**Response:** This is a crucial comment with far-reaching implications.
 The Reviewer asks what decisions are made by the authors.
-Simply put: All decisions are made by us.
-There are infinitely many ways to conduct exploratory analysis on a single data set,
-and the present paper represents just one possible way.
+The straightforward answer is: all decisions.
+The reason for this is that inductive / exploratory research affords considerable creative license to the researcher [@wagenmakersCreativityVerificationCyclePsychological2018; @degrootMethodologieGrondslagenVan1961].
+This is because the number of ways to conduct exploratory analysis on a single data set are infinite.
+The present paper represents just one possible way.
 The "computerized analytical system", as referred to by the Reviewer,
-is nothing more than an explicit representation of our subjective decisions in analyzing the data,
-represented as code.
+is an explicit representation of our subjective decisions in analyzing the data in the form of code.
 
-The Reviewer asks for reliability checks, also known as a sensitivity analysis or multiverse analysis [@steegenIncreasingTransparencyMultiverse2016].
+The Reviewer further asks for reliability checks, also known as a sensitivity analysis or multiverse analysis [@steegenIncreasingTransparencyMultiverse2016].
 Such reliability checks are only defined, however, in the context of deductive (confirmatory) analysis,
 where they are used to ensure that hypothesis tests / statistical inferences are robust to permutations of the data processing strategy.
-As the present study is inductive (exploratory),
+Reliability checks are undefined in the context of the present study,
+because it is inductive (exploratory),
 no hypotheses are tested nor inferences are drawn,
-and the number of alternative possible analyses is infinite - thus reliability checks are undefined.
+and the number of alternative possible analyses is infinite.
 
@@
 
-1) We have documented the methods in detail in the manuscript, and added online supplemental analyses for more complex analyses that we could not describe in sufficient detail.
+1) We have documented the methods in as much detail as possible in the manuscript, and added new online supplemental analyses for more complex analyses that we could not describe in sufficient detail.
 2) We have made all analysis code and data publicly available in an open access repository.
@@
 so readers can see that our analysis proceeded in a straightforward way. We mention this explicitly in the revised paper.
-3) The revised Methods section now explicitly mentions that these are inductive (exploratory) analyses, and as such, depend on subjective decisions:
+3) Throughout the manuscript, including in the revised Methods section, we now emphasize that these are inductive (exploratory) analyses, and as such, depend on subjective decisions:
 
@@
 To ensure that all such decisions are properly documented,
-we have made all code, data, and the historical record of this project publicly available in an online research repository at [https://github.com/cjvanlissa/veni_sysrev](https://github.com/cjvanlissa/veni_sysrev).
+we have made all code, data, and the historical record of this project publicly available in an online research repository at [masked]. 
 We used the Workflow for Open Reproducible Code in Science [WORCS, @vanlissaWORCSWorkflowOpen2020]
-to make the analyses strictly reproducible.
+to make the analyses reproducible.
 We encourage reuse of the analysis code,
@@
 
-> Of course, the present study also has limitations.
-One limitation is that several subjective decisions were made throughout the analysis process.
+> One final limitation is that several subjective decisions were made throughout the analysis process.
 This limitation is inherent to inductive studies, however [e.g., @wagenmakersCreativityVerificationCyclePsychological2018]:
@@
 and researchers have considerable creative license in doing so.
-We have attempted to address this limitation by explicitly mentioning important decisions in the manuscript,
-and by making all analysis code and data publicly available,
-so that others may explore the effect of different analysis strategies.
+We have attempted to address this limitation by explicitly mentioning important decisions in the manuscript where possible,
+and by making all analysis code and data publicly available in a fully reproducible format [based on @vanlissaWORCSWorkflowOpen2020],
+so that others may explore alternative exploratory analysis strategies.
 
-## R1C14 At the bottom of page 12, it is clear that a decision is made in terms of retaining within a percentile.
+**Reviewer 1, comment 15:** At the bottom of page 12, it is clear that a decision is made in terms of retaining within a percentile.
 How do we know if that is the right decision?
@@
 
-Response: This is indeed a good example of a subjective decision.
+**Response:** This is indeed a good example of a subjective decision.
 In our response to the previous comment, we explain that we now explicitly acknowledge each such subjective decision in the revised manuscript.
@@
 It is thus more flexible than a fixed cutoff, and still successful in pruning terms that occur only a few times in the corpus.
-We now mention this explicitly in the paper:
+To address this comment, we now mention the fact that this is a subjective decision explicitly in the paper (see excerpt below).
+We also provide more quantitative information about the thresholds and the cut terms.
 
@@
 it has the advantage of being responsive to the empirical distribution of term frequencies.
+Note that the vast majority of pruned terms occurred only once in the corpus.
 
-## R1C15 Page 13, there is again pruning. Justifications for the cutoff should be noted. There is a manual classification and we are left with no sense of its reliability/validity.
+**Reviewer 1, comment 16:** Page 13, there is again pruning. Justifications for the cutoff should be noted. There is a manual classification and we are left with no sense of its reliability/validity.
 
@@
 
-```{r}
+```{r, echo = FALSE}
 df_plot <- cbind(as.data.frame(read_yaml("study1_term_freq_dist.yml")), Analysis = "Analysis 1")
@@
 
-## R1C16 I really think the presentation would be more effective if it did not have results/discussions and then more results/discussions, and then a general discussion.
+**Reviewer 1, comment 17:** I really think the presentation would be more effective if it did not have results/discussions and then more results/discussions, and then a general discussion.
 We are not really dealing with different studies.
 
-Response: We have attempted to address the Reviewer's comment by writing a single Results and Discussion section, instead of separate sections for each analysis.
+**Response:** As requested, we have rewritten these sections as a single Results and Discussion section.
 As this change spans several pages, we do not cite the entire revised section here, but refer to the revised manuscript.
 
-## R1C17 Page 20, the first full paragraph is a good example of text that is meant to show a contribution when it actually does not.
+**Reviewer 1, comment 18:** Page 20, the first full paragraph is a good example of text that is meant to show a contribution when it actually does not.
 Being the first or one of the first is not a contribution.
@@
 
-Response:
+**Response:** Point well taken; we have rewritten the paragraph in line with the Reviewer's suggestions.
+We do still mention that we are the first to do this - but merely as a statement of fact, not as a contribution.
+The contributions section now reads:
 
-## R1C18 Page 21, the political push for open science is not really a point that is relevant.
+> One strength of the present study is that it was more comprehensive than previous reviews of the literature in two respects [cf.
+@bariolaChildAdolescentEmotion2011; @coe-odessEmergentEmotionsAdolescence2019]:
+We conducted a systematic literature search, and we used text mining to comprehensively map the phenomena relevant to adolescents' emotion regulation.
+<!-- To this end, we applied text mining methods in a systematic review. We used For this purpose, It is also one of the first applications of inductive-->
+Using text mining offers unique advantages compared to narrative reviews [@littellEvidencebasedBiasedQuality2008],
+because it can cover vastly greater corpora than a sentient reader,
+and follows a somewhat more objective, transparent, and reproducible procedure.
+As such, text mining systematic reviews offer an interesting perspective that complements theory and narrative reviews.
+Moreover, text mining systematic reviews offer an inductive approach to identify relevant phenomena in a particular area of research.
+This can serve as the first step towards formal theory construction [@borsboomTheoryConstructionMethodologya].
+Our study was the first to implement this novel approach.
+
+**Reviewer 1, comment 19:** Page 21, the political push for open science is not really a point that is relevant.
 If the authors wanted to review the actual papers, they could.
@@
 
-Response: This is an important comment, which we will address in four main points.
+**Response:** This is an important comment, which we will address in four main points.
 
@@
 
-> One final limitation is that our analysis was limited to keywords and abstracts.
+> Another limitation is that our analysis was limited to keywords and abstracts.
 The primary obstacles to the analysis of full-text publications were limited access to articles behind paywalls,
@@
 
-## R1C19 in the end, it ends up looking like the authors are "hiding the ball".
+**Reviewer 1, comment 20:** in the end, it ends up looking like the authors are "hiding the ball".
 The real issue is what is actually being added to theory?
@@
 
-Response: The Reviewer comes away with the impression that we are "hiding the ball".
-We regret that our writing raises these concerns about a lack of transparency,
+**Response:** We regret that our writing raises these concerns about a lack of transparency,
 because we have made thorough efforts to ensure that this adheres to best practices for open science.
@@
 
-> There have been recent calls for the consolidation of empirical insights into overarching theory [e.g., @bussTheoriesEmotionalDevelopment2019]. 
-According to formal methods for theory construction [@borsboomTheoryConstructionMethodologya; @haigExploratoryFactorAnalysis2005],
-the first step in this endeavor is to identify the relevant *empirical phenomena*,
+> This has led to recent calls for the consolidation of empirical insights into overarching theory [e.g., @bussTheoriesEmotionalDevelopment2019]. 
+Formal methods for theory construction state that the first step in this endeavor is to identify the relevant *empirical phenomena* [@borsboomTheoryConstructionMethodologya; @haigExploratoryFactorAnalysis2005],
 defined as stable and general features of the world [@bogenSavingPhenomena1988].
 We propose that systematic reviews are a suitable method for taking this first step,
-based on the assumption that phenomena currently considered to be most stable and general will be more frequently represented in the literature.
+based on the assumption that phenomena considered to be stable and general will be more frequently represented in the published literature.
 
-> The first step in theory construction methodology is to identify relevant phenomena [@borsboomTheoryConstructionMethodologya].
-We have argued that text mining systematic reviews are a relatively comprehensive and objective method for identifying such phenomena, because they can evaluate much larger bodies of literature than sentient readers, and are not biased toward pre-existing ideas.s
+> The first step in theory construction methodology (TCM) is to identify relevant phenomena [@borsboomTheoryConstructionMethodologya].
+We have argued that text mining systematic reviews are a relatively comprehensive and objective method for identifying such phenomena, because they can evaluate much larger bodies of literature than sentient readers, and are not biased toward pre-existing ideas.
 
-## R1C20 The conclusion note that the method charts "unknown territories". Sure that is not the case because the study relies on the published studies.
+The Reviewer further asks "What are the important findings here?".
+To address this comment, we have added more extensive interpretations of the emerging themes in the Discussion and in the Abstract.
+For the sake of brevity, we just copy this excerpt from the Abstract to illustrate:
 
-Response: The point is well-taken.
+> Results reflected themes
+  commonly featured in theory and narrative reviews, such as socialization
+  and neurocognitive development, but also identified undertheorized themes,
+  such as developmental disorders, physical health, external stressors,
+  structural disadvantage, substance use, identity and moral development, and
+  sexual development.
+
+**Reviewer 1, comment 21:** The conclusion note that the method charts "unknown territories". Sure that is not the case because the study relies on the published studies.
+
+**Response:** The point is well-taken.
 We are not charting "unknown territories" at the level of primary research, but we are charting territories underrepresented at the meta-scientific level (i.e., topics rarely addressed in narrative reviews and theory).
@@
 although well-represented in the empirical literature,
-are under-emphasized in narrative reviews and theory.
+are under-emphasized in narrative reviews and theory - such as developmental disorders, physical health, external stressors, structural disadvantage, substance use, identity and moral development, and sexual development.
 
-## R1C21 I really get a sense of over-selling.
+**Reviewer 1, comment 22:** I really get a sense of over-selling.
 The authors should, again, focus on what is actually found that is useful about the topic.
@@
 
-Response: We agree that it is important to clearly communicate what is useful about the present study without over-selling.
+**Response:** We agree that it is important to clearly communicate what is useful about the present study without over-selling.
 To address this point, we have carefully rewritten all claims about novel contributions.
@@
 > Finally, several authors have commented on the lack of an overarching theory tailored specifically to adolescent emotion regulation.
-The first step in theory construction methodology is to identify relevant phenomena [@borsboomTheoryConstructionMethodologya].
+The first step in theory construction methodology (TCM) is to identify relevant phenomena [@borsboomTheoryConstructionMethodologya].
 We have argued that text mining systematic reviews are a relatively comprehensive and objective method for identifying such phenomena, because they can evaluate much larger bodies of literature than sentient readers, and are not biased toward pre-existing ideas.
-The phenomena identified in the present study might thus serve as a starting point for future theory development.
-Specifically, theorists might revisit existing relevant theory
-and incorporate relevant phenomena as identified in the present analysis.
+The next step in formal theory construction methodology would be to describe and quantify the nature of the relationship of each phenomenon in relation to adolescent emotion regulation.
+The phenomena identified in the present study might thus serve as a starting point for future theory development,
+and sensitize empirical researchers to potential confounders in research on adolescents' emotion regulation.
+
+## References

### 2021-02-27 manuscript.Rmd
Finalize action letter

@@
 abstract: |
-  Adolesence is a developmentally sensititve period for emotion regulation.
-  Although substantial empirical research has addressed relevant risk factors,
-  the literature is fragmented across subdisciplines, and
-  an integrating framework is lacking.
-  This systematic review of 6305 papers used text mining to map correlates of adolescents’ (ages 
-  10-25) emotion regulation. First, we established a baseline of relevant terms gleaned from 
-  theory and recent narrative reviews. Then, we conducted two text mining analyses to examine 
-  term/document frequency and co-occurrence in author-provided keywords and abstracts. Results 
-  reﬂected constructs commonly featured in theory and narrative reviews, but also identified 
-  underrepresented themes. This research constitutes a first step towards integrating the 
-  literature, and illustrates how text mining systematic reviews (TMSR) may complement narrative reviews.
+  Adolesence is a developmentally sensititve period for emotion regulation
+  with potentially lifelong implications for mental health and well-being.
+  Although substantial empirical research has addressed this topic, the
+  literature is fragmented across subdisciplines, and an overarching
+  theoretical framework is lacking. The first step towards constructing a
+  unifying framework is identifying relevant phenomena. This systematic
+  review of 6305 papers used text mining to identify phenomena relevant to
+  adolescents' emotion regulation. We first established a baseline of
+  relevant phenomena discussed in theory and recent narrative reviews. We
+  then conducted text mining analyses of article keywords and abstracts,
+  examining term frequency as an indicator of relevance and term
+  co-occurrence as an indicator of association. Results reflected themes
+  commonly featured in theory and narrative reviews, such as socialization
+  and neurocognitive development, but also identified undertheorized themes,
+  such as developmental disorders, physical health, external stressors,
+  structural disadvantage, substance use, identity and moral development, and
+  sexual development. This illustrates how text mining systematic reviews
+  (TMSR), a novel approach, may complement narrative reviews. Future
+  theoretical work might seek to integrate these undertheorized themes into
+  an overarching framework, and empirical research might consider them as
+  promising areas for future research, or potential confounders in research
+  on adolescents' emotion regulation.
 keywords          : "emotion regulation, adolescence, systematic review, text mining, machine
@@
 and downstream cost to society,
-it is important to have a comprehensive understanding of the risk factors that render some adolescents more susceptible to emotional difficulties than others.
-Despite the abundance of empirical work on this issue,
-several authors have pointed out that the literature is somewhat fragmented,
+it is important to have a comprehensive overview of the factors associated with adolescents' emotion regulation.
+Of particular interest are potential risk factors that render some youth susceptible to emotion regulation difficulties.
+Despite the abundance of publications in this field,
+several prior theoretical and empirical reviews have argued that the literature is somewhat fragmented,
 because different (sub)disciplines have approached the issue in disparate ways,
@@
 
-There have been recent calls for the consolidation of empirical insights into overarching theory [e.g., @bussTheoriesEmotionalDevelopment2019]. 
-According to formal methods for theory construction [@borsboomTheoryConstructionMethodologya; @haigExploratoryFactorAnalysis2005],
-the first step in this endeavor is to identify the relevant *empirical phenomena*,
+This has led to recent calls for the consolidation of empirical insights into overarching theory [e.g., @bussTheoriesEmotionalDevelopment2019]. 
+Formal methods for theory construction state that the first step in this endeavor is to identify the relevant *empirical phenomena* [@borsboomTheoryConstructionMethodologya; @haigExploratoryFactorAnalysis2005],
 defined as stable and general features of the world [@bogenSavingPhenomena1988].
 We propose that systematic reviews are a suitable method for taking this first step,
-based on the assumption that phenomena currently considered to be most stable and general will be more frequently represented in the literature.<!-- the frequency with which phenomena occur in the literature is indicative of their relevance.-->
-However, traditional narrative reviews have been shown to be marred by reliance on small convenience samples of the literature, confirmation bias,
+based on the assumption that phenomena considered to be stable and general will be more frequently represented in the published literature.<!-- the frequency with which phenomena occur in the literature is indicative of their relevance.-->
+Traditional narrative reviews have some limitations, however, as they been shown to be marred by small convenience samples, confirmation bias,
 and an undue emphasis on positive results [@littellEvidencebasedBiasedQuality2008].
@@
 
-The present paper aims to map the empirical phenomena relevant to adolescent emotion regulation, using text mining systematic review.
+The present paper uses this novel approach to map the empirical phenomena relevant to adolescent emotion regulation.
 This approach considers the frequency with which phenomena occur in the literature to be indicative of their relevance.
 If we additionally assume that the frequency with which phenomena are studied together is indicative of the extent to which researchers believe them to be associated,
-then the co-occurrence of phenomena within publications can be interpreted as a nomological network: a mapping of relationships between phenomena of theoretical relevance [see @alaviAligningTheoryMethodology2018].
-This can serve as a starting point for the formulation of a proto-theory,
-which would additionally involve specifying putative mechanisms to explain associations between the phenomena [@borsboomTheoryConstructionMethodologya].
+then the co-occurrence of phenomena within publications can be interpreted as a rudimentary nomological network: a mapping of relationships between theoretically relevant phenomena [see @alaviAligningTheoryMethodology2018].
+This network can serve as a starting point for the formulation of a proto-theory,
+which would additionally involve abductive reasoning: specifying putative mechanisms to explain associations between the phenomena [@borsboomTheoryConstructionMethodologya].
 By mapping the phenomena relevant to adolescent emotion regulation,
@@
 and intrinsic limitations of narrative reviews prohibit comprehensive coverage of the vast but diffuse literature .-->
-
+<!--
 Recent years have seen the publication of several excellent systematic reviews,
-but these have all been narrative reviews.
+but these have all been narrative reviews.-->
 
@@
 
-Although there is a paucity of theories *specific to* adolescent emotion regulation,
-several relevant theories are commonly invoked in empirical work [see  @bussTheoriesEmotionalDevelopment2019].
-In order to contextualize the results of our systematic review,
+Although it has been argued that there is a paucity of theories *specific to* adolescent emotion regulation,
+many *relevant* theories are commonly invoked in empirical work [see  @bussTheoriesEmotionalDevelopment2019].
+In order to contextualize the results of our systematic review
 and assess to what extent the identified phenomena through text mining mirror or complement existing theory,
@@
 In reading the theoretical literature,
-we recorded relevant phenomena,
-and whether these were discussed as putative causes, outcomes, indicators, or protective factors in relation to emotion regulation.
-The left panel of Figure \@ref(fig:figbaseline) visually summarizes the phenomena so identified in the theoretical literature in a style similar to our subsequent systematic review,
+we documented relevant phenomena and whether these were discussed as putative causes, outcomes, indicators, or protective factors in relation to emotion regulation.
+The left panel of Figure \@ref(fig:figbaseline) visually summarizes the phenomena discussed in the theoretical literature, using a style similar to our subsequent systematic review,
 in order to facilitate contextualizing our original findings.
@@
 
-Among the oldest relevant theories of adolescents' emotional development is Hall's notion of "storm and stress" [see
-@arnettAdolescentStormStress1999]. It describes how `r keyw("hormonal")` changes diminish
-`r keyw("self-control")` and increase `r keyw("reactivity")`, leading to emotion
-dysregulation, `r keyw("conflict with parents")`, and `r keyw("risky behavior")`.
-This notion of diminished self-control and increased emotional reactivity persists in modern theory, but is now considered a normative change that facilitates emotional maturation
-[@croneUnderstandingAdolescencePeriod2012], at the risk of emotional
+Two of the most general theories invoked to frame developmental research are Bronfenbrenner's bioecological model, and Sameroff's
+transactional model.
+Bronfenbrenner [-@bronfenbrennerBioecologicalModelHuman2007] describes how the `r keyw("environment")`
+shapes individual development.
+At the individual level, every person is imbued with `r keyw("biological")` predispositions,
+and develops over time in interaction with contextual influences.
+The most immediate source of contextual influences is the microsystem,
+composed of people close to the individual.
+Other influences stem from the macrosystem, consisting of `r keyw("political")` and `r keyw("economic")` influences,
+and the exosystem, consisting of `r keyw("cultural")` norms and `r keyw("values")`.
+Sameroff's model [-@sameroffUnifiedTheoryDevelopment2010] is compatible with Bronfenbrenner's work,
+but places a stronger emphasis on development as a product of reciprocal influences between child and environment.
+Sameroff distinguishes between proximal influences, which roughly correspond to the microsystem in Bronfenbrenner's model, and distal influences, which derive from
+structural factors indirectly shaping development, like `r keyw("socio-economic status")`,
+`r keyw("schools")`, and the `r keyw("community")` (macro- and exosystem).
+With increasing age, distal influences gain ground on proximal influences.
+These two theories have a broader scope than most.
+This means that they can be invoked to contextualize any developmental study,
+but lack specificity - a shortcoming that curtails a theory's utility in generating hypotheses.
+We thus turn toward more domain-specific theories.
+
+Among the oldest domain-specific theories of adolescents' emotional development is Hall's notion of "storm and stress" [see
+@arnettAdolescentStormStress1999].
+It describes how `r keyw("hormonal")` changes diminish `r keyw("self-control")` and increase `r keyw("reactivity")`, which in turn leads to emotion
+regulation difficulties, increased `r keyw("conflict with parents")`, and `r keyw("risky behavior")`.
+Hall's notion of diminished self-control and increased emotional reactivity still persists in modern theory, but is increasingly recast as a normative change that facilitates emotional maturation at the risk of emotional
 disturbance [@arnettAdolescentStormStress1999; @leeAdolescentMentalHealth2014].
-
+[@croneUnderstandingAdolescencePeriod2012] 
+A potential limitation of Hall's notion of storm and stress is that it describes emotion regulation difficulties as a part of normative development, and thus underemphasizes adolescents' diverging destinies [cf.
+@croneUnderstandingAdolescencePeriod2012].
 <!--SH I am still not sure what the empirical contribution is - can you be more specific with it in this sentence? -->
@@
 
-One example of a normative theory of emotional development in early childhood is presented by Sroufe [-@sroufeEmotionalDevelopmentOrganization1995].
+Sroufe's [-@sroufeEmotionalDevelopmentOrganization1995] theory of normative emotional development focuses on developmental influences to a greater extent.
 Sroufe argues that, as children grow older,
@@
 drive a transition from external emotion regulation by `r keyw("primary caregivers")`
-towards autonomous emotion regulation. This theory focuses on two drivers of
-development: `r keyw("social")` and `r keyw("cognitive influences")`. Social influences mainly occur
+towards autonomous emotion regulation.
+This theory focuses on two drivers of
+development: `r keyw("social")` and `r keyw("cognitive influences")`. 
+Social influences mainly occur
 through `r keyw("parental co-regulation")`, `r keyw("parenting behaviors")`, and parent-child
@@
 nervous system")` (CNS), `r keyw("cognition")`, and `r keyw("self-regulation")`.
-
-This emphasis on social influences and `r keyw("neurocognitive development")` is reflected in many theories.
-Some of these focus primarily on neurocognitive development.
-For example, `r keyw("polyvagal theory")` closely links `r keyw("emotional experience")`
-- and regulation - to autonomous nervous system functioning
-[@porgesOrientingDefensiveWorld1995].
-More recently, in their model of social-affective engagement and `r keyw("goal flexibility")`
-<!--. Like other authors 
-[e.g., @caseyBrakingAcceleratingAdolescent2011; @craccoEmotionRegulationChildhood2017],
-Crone and Dahl--> Crone and Dahl [-@croneUnderstandingAdolescencePeriod2012] posited that the developmental 
-asymmetry between `r keyw("motivational")` and inhibitory `r keyw("brain")` circuits gives rise to a
-"maturity gap" in middle adolescence. 
-What distinguishes Crone and Dahl from related writings [e.g., @craccoEmotionRegulationChildhood2017]
-is the emphasis on adolescents' diverging destinies;
-why some youngsters flourish while others languish.
-They argue that adolescents' cognitive engagement is dynamically responsive to
+This theory's relevance for adolescent research may be diminished by its focus on early childhood,
+although there is substantial continuity in developmental influences throughout childhood and adolescence.
+For instance, there is substantial similarity between mothers' and fathers' unique roles in emotional development in childhood [@vanlissaMothersFathersQuantitative2020] and adolescence [@vanlissaRoleFathersMothers2019].
+In terms of level of analysis, the scope of Sroufe's and Hall's theories corresponds approximately to the individual and the microsystem in Bronfenbrenner's ecological model.
+The emphasis on socialization and `r keyw("neurocognitive development")` as two drivers of emotional development, which is evident from both theories,
+is the focus of several theories with a narrower scope.
+
+Among theories focused on socialization, Morris' tripartite model is widely cited in the field [-@morrisRoleFamilyContext2007].
+This theory describes three pathways through which `r keyw("parents")` shape emotion regulation
+development: `r keyw("modeling")`, `r keyw("parenting practices")`, and the
+emotional `r keyw("family climate")`,
+which subsumes attachment and `r keyw("marital relationship")` quality.
+This theory focuses parents, acknowledging unique contributions by `r keyw("mothers")` and `r keyw("fathers")`, but also recognizes the importance of siblings.
+Others in turn have adapted the tripartite model to describe the influence of peers [@reindlSocializationEmotionRegulation2016], thus illustrating its wider usefulness in understanding socialization.
+A more abstract take on socialization is found in @holodynskiDevelopmentEmotionsEmotion2006's
+internalization model of emotional development. 
+This theory describes the role of emotion in `r keyw("communication")`, and the `r keyw("cultural")` symbolic function of emotion.
+
+In research on neurocognitive aspects of adolescents' emotion regulation,
+`r keyw("polyvagal theory")` has been influential [@porgesOrientingDefensiveWorld1995].
+This theory examines `r keyw("emotional experience")` and -regulation in relation to autonomous nervous system functioning, respiratory sinus arrhythmia, and the stress response.
+Although polyvagal theory is relevant for development,
+it does not explicitly address it.
+Among neurocognitive developmental theories,
+there is some consensus that the developmental asymmetry between `r keyw("motivational")`-emotional and inhibitory `r keyw("brain")` circuits gives rise to a "maturity gap" in middle adolescence [@croneUnderstandingAdolescencePeriod2012; @caseyBrakingAcceleratingAdolescent2011; @craccoEmotionRegulationChildhood2017].
+Particularly noteworthy is Crone and Dahl's  model of social-affective engagement and `r keyw("goal flexibility")`.
+According to this model, adolescents' cognitive engagement is dynamically responsive to
 social and motivational `r keyw("goal salience")`.
@@
 abilities, but also places them at risk of impulsivity in
-pursuit of `r keyw("peer approval")`. In terms of explanans,
-this theory focuses primarily on cognitive factors
-and the role of peers, with less attention to factors such as parenting.
-This theory is relevant because it focuses on adolescence specifically,
-but only tangentially addresses emotion regulation.
-
-Other theories emphasize socialization to a greater extent,
-such as Morris' tripartite model, which focuses on `r keyw("parents")`'
-role in emotion regulation development [-@morrisRoleFamilyContext2007].
-It describes three pathways through which parents shape emotion regulation
-development: `r keyw("modeling")`, `r keyw("parenting practices")`, and the
-emotional `r keyw("family climate")`,
-which subsumes attachment and `r keyw("marital relationship")` quality.
-Morris emphasizes the relevance of `r keyw("mothers")`, 
-`r keyw("fathers")`, and siblings.
-Others have adapted the tripartite model to describe peers' role in emotion regulation socialization
-[@reindlSocializationEmotionRegulation2016].
-A more abstract take on socialization is found in @holodynskiDevelopmentEmotionsEmotion2006's
-internalization model of emotional development. 
-Hallmarks of this theory are the interplay between emotion and `r keyw("communication")`,
-and the internalization of the `r keyw("cultural")` symbolic function of emotion.
-Several theories thus explain emotion regulation socialization in detail,
-but a potential limitation is that they are not embedded in a larger unifying framework.
+pursuit of `r keyw("peer approval")`.
+To a greater extent than related writings, Crone and Dahl's model focuses on adolescents diverging destinies;
+why some youngsters flourish while others languish.
+This is important for understanding individual differences in development.
+The relevance of this theory is enhanced by its focus on adolescence,
+but is curtailed because it only tangentially addresses emotion regulation.
+Furthermore, whereas this theory addresses the role of cognitive factors and peers as drivers of development, it devotes less attention to other relevant phenomena, such as parenting [cf.
+@morrisRoleFamilyContext2007].
+Micro-scale theories as reviewed here are useful in explaining specific phenomena in detail,
+but do not provide a comprehensive understanding of adolescent's emotion regulation.
+To this end, it is important to consider these micro-scale theories in the context of a larger framework of relevant phenomena.
+
 <!--Like Sroufe, Holodynski describes an age graded transition from
@@
 regulation.-->
-
 Theories of the phenomenon of emotion regulation offer insight into
@@
 [@lemeriseIntegratedModelEmotion2000].
-One limitation of these theories in the present context is the lack of a developmental component.
-
-Finally, given our interest in risk factors that render adolescents susceptible
-to emotional difficulties, we should mention two theories widely invoked to frame research on developmental influences: Bronfenbrenner's bioecological model, and Sameroff's
-transactional model.
-Bronfenbrenner [-@bronfenbrennerBioecologicalModelHuman2007] describes how the `r keyw("environment")`
-shapes individual development.
-Each individual is imbued with `r keyw("biological")` predispositions,
-and develops in interaction with contextual influences.
-These influences range from the microsystem,
-composed of people close to the individual,
-to the macrosystem, consisting of `r keyw("political")` and `r keyw("economic")` influences,
-to the exosystem, consisting of `r keyw("cultural")` norms and `r keyw("values")`.
-Sameroff's model [-@sameroffUnifiedTheoryDevelopment2010] is compatible with Bronfenbrenner's work,
-but focuses more on the interplay between nature and nurture.
-It conceptualizes development as a product of reciprocal influences between child and environment.
-Sameroff distinguishes proximal influences such as parents (the microsystem in Bronfenbrenner's model)
-from distal influences;
-structural factors indirectly shaping development, like `r keyw("socio-economic status")`,
-`r keyw("schools")`, and the `r keyw("community")` (macro- and exosystem).
-With increasing age, distal influences gain ground on proximal influences.
-These theories are broad enough to contextualize any developmental study,
-but lack specificity, which curtails their utility in generating hypotheses.
+One shortcoming of these theories for understanding adolescents' emotion regulation 
+is the lack of a developmental component.
+
 <!-- RK: What do you take from these broad perspectives for your RQ?-->
@@
 but lack a broader perspective.
-It would be beneficial to bridge these levels of analysis.
+Broad theories can be used to frame a wide variety of research,
+and specific theories are more suitable for deductive hypothesis generation.
+To combine the strength of both, it would be beneficial to bridge these levels of analysis.
 In sum, there is a need for more integrative theory formation,
@@
 The present study lays the groundwork for such theory development,
-by providing a text-mining based inductive systematic review of the field.
+by identifying theoretically relevant phenomena based on a text-mining systematic review of the literature.
 
@@
 
-Whereas theory provides a top-down frame of reference,
-literature reviews provide a bottom-up understanding of a phenomenon by aggregating empirical evidence.
+Whereas theory provides a top-down deductive understanding of adolescents' emotion regulation,
+literature reviews synthesize inductive insights emerging from the empirical literature.
 Given the noted absence of a single overarching theory [see @bussTheoriesEmotionalDevelopment2019],
@@
 as they provide additional
-insight into relevant phenomena in the etiology of adolescents'
-emotion regulation competencies.
+insight into undertheorized relevant phenomena.
 Two recent narrative reviews in particular complement the aforementioned theoretical literature [@coe-odessEmergentEmotionsAdolescence2019; @bariolaChildAdolescentEmotion2011].
-Figure \@ref(fig:allnetworks) visualizes constructs uniquely covered by these narrative reviews,
-relative to the theoretical literature.
+The right panel of Figure \@ref(fig:figbaseline) visualizes constructs uniquely covered by these narrative reviews,
+relative to the preceding theoretical literature.
+This illustrates in what respects these reviews reflect existing theory,
+and in what respects they complement it.
 <!--
@@
 
-The seminal review by
-@bariolaChildAdolescentEmotion2011 addressed intra-individual factors
-such as temperament, and biological factors like neurocognitive development and
-genes.
-Proximal social influences covered include socialization and modeling by parents, teachers, and peers.
-Finally, distal factors include the role of culture and the
-media.
-Barriola and colleagues made several suggestions for future research,
-calling for a robust theoretical framework to guide future
-research, for research on parents' role beyond early childhood,
-and for additional work on the role of fathers in emotion socialization.
-The latter two topics are now receiving more attention [e.g., see @vanlissaRoleFathersMothers2019;
+The seminal review by @bariolaChildAdolescentEmotion2011 was one of the first to stress the urgent lack of an overarching theoretical framework to guide research in this field.
+Their review addressed relevant phenomena at different levels of analysis. 
+At the individual level, relevant phenomena include temperament and biological factors, like neurocognitive development and genes.
+At the level of proximal influences, the authors discuss socialization and modeling by parents, teachers, and peers.
+Finally, at the level of distal influences, culture and the media are discussed.
+Barriola and colleagues made several important observations about the state of the literature in this field.
+For instance, they emphasized that work on children cannot be straightforwardly extrapolated to the life stage of adolescence.
+They also called for further research on parents' role beyond early childhood, and on fathers' role in emotion socialization -
+a topic that of increasing importance [see @pleckPaternalInvolvementRevised2004].
+Several recent publications have conducted research in line with these recommendations [e.g., see @vanlissaRoleFathersMothers2019;
 @vanlissaMothersFathersQuantitative2020].
 
-A recent review by @coe-odessEmergentEmotionsAdolescence2019 offers a nuanced
-discussion of several issues that complement prior publications.
-This includes the implications of physiological changes,
+As the review by Barriola and colleagues is now a decade old,
+it is worth considering the more recent review by @coe-odessEmergentEmotionsAdolescence2019. 
+This review complements prior work by offering a nuanced discussion of several topics.
+At the individual level, this includes the implications of physiological changes,
 including neurocognitive development and pubertal maturation.
-Conflict with parents is addressed too, which peaks when adolescents become increasingly individuated.
-Such conflict impacts both day-to-day mood swings and dispositional emotion regulation difficulties [see also
-@vanlissaCostEmpathyParentadolescent2017].
-Adolescents also become increasingly oriented towards peers.
-This increases sensitivity to social status and norms,
-along with concomitant increases in peer pressure and risk taking.
-Pubertal development further precipitates sexual and romantic behavior,
+Pubertal development also precipitates sexual and romantic behavior,
 and the intensification of both biological sex differences and gender stereotyped behavior.
+This, in turn, likely modulates proximal influences through peers.
 <!--With regard to the process of emotion regulation,
@@
 positive emotionality also peaks in adolescence. -->
-Relatedly, the authors describe how hormonal changes intensify the stress response,
-which helps explain adolescents' greater susceptibility to emotion regulation difficulties.
-Finally, <!--going beyond the implications of cognitive development
-discussed in other publications,--> the authors discuss how cognitive development and increased capacity
+The authors further describe how individual hormonal changes intensify the stress response,
+which relates to adolescents' greater susceptibility to emotion regulation difficulties.
+Finally, going beyond the implications of cognitive development
+discussed in other publications, the authors discuss how cognitive development and increased capacity
 for abstract thought relate to identity formation - a key challenge in
@@
 @vanlissaLongitudinalInterplayAffective2014].
-
-As can be seen in Figure \@ref(fig:allnetworks), 
-there are notable parallels between correlates of emotion regulation identified in these
-narrative reviews, and in the preceding theoretical literature.
+At the level of proximal influences, Coe-Odess and colleagues expand on the role of conflict with parents, which peaks in adolescence as youth become increasingly individuated.
+This is relevant because parent-adolescent conflict has been shown to impact both day-to-day mood swings and dispositional emotion regulation [see @vanlissaCostEmpathyParentadolescent2017].
+Coe-Odess and colleagues further detail the mechanisms by which peers exert proximal influences: Adolescents become increasingly oriented towards peers, which
+increases their sensitivity to social status and norms,
+along with concomitant increases in peer pressure and risk taking.
+This review devotes limited attention to distal influences.
+
+There are notable parallels between phenomena relevant to adolescents' emotion regulation as identified in these
+narrative reviews, and in the preceding theoretical literature, as can be seen in Figure \@ref(fig:figbaseline).
 Nevertheless,
@@
 Further introduced are proximal influences, including the role of media, norms, and social status.-->
-This illustrates that reviews of the empirical literature can contribute additional insight into key factors in adolescents' emotion regulation development.
-An important limitation is that all reviews in this field have been unstructured narrative reviews, which are known to be limited in scope and biased [@littellEvidencebasedBiasedQuality2008].
+This illustrates the general principle that reviews of the empirical literature can contribute inductive insight into relevant phenomena underrepresented in theory.
+An important shortcoming is that all reviews in this field have been unstructured narrative reviews, which are known to be limited in scope and biased [@littellEvidencebasedBiasedQuality2008].
 We seek to complement preceding work by using text mining to conduct a more comprehensive and objective empirical
-literature review, and map the factors associated with adolescent emotion
-regulation.
+literature review, and map the phenomena relevant to adolescent emotion regulation.
 
@@
 as opposed to deductive (confirmatory) research, and as such does not test any hypotheses [see De Groot's work on the empirical cycle @degrootMethodologieGrondslagenVan1961][^Note that aside from induction, the term "abduction" is also used in the methodological literature.
-Injunction pertains to inferences based purely on statistical data, whereas abduction additionally involves the attribution of observations to explanatory principles.].
+We consider injunction to refer to inferences based purely on observations (data).
+Abduction differs from induction because it additionally involves the attribution of observations to explanatory principles.].
 
@@
 We used the Workflow for Open Reproducible Code in Science [WORCS, @vanlissaWORCSWorkflowOpen2020]
-to make the analyses strictly reproducible.
+to make the analyses reproducible.
 We encourage reuse of the analysis code,
@@
   term_freq$pruned <- term_freq$Var1 %in% names(term_freqtop)
-  saveRDS(term_freq, "study1_term_freq_dist.yml")
+  write_yaml(term_freq, "study1_term_freq_dist.yml")
   write_yaml(dim(dtm_top), "study1_dtm_top.yml")
@@
 dtm_top <- read_yaml("study1_dtm_top.yml")
-term_freq_dist <- readRDS("study1_term_freq_dist.yml")
+term_freq_dist <- read_yaml("study1_term_freq_dist.yml")
 ```
@@
 and retained those exceeding the $97.5^{th}$ percentile.
-This corresponded to terms occurring in at least `r min(as.numeric(term_freq_dist$Var1)[term_freq_dist$pruned])` documents.
+This corresponded to terms occurring in at least `r min(as.numeric(term_freq_dist[[1]])[term_freq_dist$pruned])` documents.
 This is a subjective criterion,
@@
 
-<!-- Results 2 -->
-
 ```{r}
@@
 This reflects Pleck's  [-@pleckPaternalInvolvementRevised2004] observation that parenting is most often operationalized in terms of mothering.
-<!-- end results 2 -->
-
-According to the term co-occurrence graph of the keyword analysis (Figure \@ref(fig:allnetworks)),
+
+<!-- Co-occurrence -->
+With regard to the term co-occurrence analyses, the analysis of  keywords (Analysis 1, see Figure \@ref(fig:allnetworks)) indicated that 
 emotion regulation is evidently a central construct
-to which most other constructs are directly linked.
+to which most other constructs were directly linked.
 This suggests that our search successfully identified factors relevant for adolescents’ emotion regulation.
-The remaining graph is notably sparse, with few interconnections between terms.
+The remaining graph was notably sparse, with few interconnections between terms.
 
@@
 Compared to the keyword co-occurrence graph,
-the analysis of abstracts revealed a much sparser network, with a different structure.
-In Analysis 2, dysregulation and mental health-related terms formed a central axis.
+the analysis of abstracts (Analysis 2) revealed an even sparser network. 
+The structure also differed, as emotion regulation and mental health-related terms appeared to form a central axis.
 Many relevant terms were connected to this axis, but not directly to
-dysregulation (as was the case in Analysis 1). 
-Only the terms *neural*, *mothers*, *attachment* and *ptsd* are 
-connected directly to dysregulation.
+emotion regulation (as was the case in Analysis 1). 
+The only terms directly connected to emotion regulation were *neural*, *mothers*, *attachment* and *ptsd*.
 <!--THIS IS NOT IN THE RESULTS FOR ANALYSIS 1 
@@
 The present study used a text mining systematic review (TMSR)
-to identify the most relevant phenomena in the literature on adolescent emotion regulation,
-and used co-occurrence graphs to map conceptual associations between these phenomena.
-We conducted a systematic search of the literature,
-and followed similar procedures to analyze author keywords (Analysis 1) and abstracts (Analysis 2) of the resulting corpus.
+to identify relevant phenomena in the literature on adolescent emotion regulation,
+and used co-occurrence graphs to map associations among these phenomena.
+We conducted a systematic literature search,
+and developed procedures to analyze the author keywords (Analysis 1) and abstracts (Analysis 2) of the resulting corpus.
 
 We considered term frequency to be indicative of a phenomenon's relevance.
-In line with this interpretation, the results of both analyses
+In line with this assumption, the results of both analyses
 reflected some of the constructs commonly accepted as relevant in theoretical literature and empirical reviews - particularly those pertaining to neurodevelopment and socialization.
-Some of the most frequently occurring terms were classified as potential outcomes of emotion regulation difficulties, and revealed a theme related to mental health.
-This validates the notion that adolescent emotion regulation is implicated in a range of mental health problems [lee, aldao], which underlines the importance of this area of research.
+Furthermore, some of the most frequently occurring terms were mental health-related outcomes that involve emotion regulation difficulties [see @aldaoEmotionregulationStrategiesPsychopathology2010].
+This validates the notion that adolescent emotion regulation is implicated in a range of mental health problems [@leeAdolescentMentalHealth2014],
+and underlines the importance of this area of research.
 
 Our analyses of term frequency also identified several novel themes,
-which were underrepresented in the theoretical literature reviewed in the Introduction.
+which were underrepresented in the theoretical literature and prior systematic reviews.
 One such theme pertains to developmental disorders, such as ADHD/CD and autism.
-This theme recurred in both analyses, although its constituent terms were ranked more highly in the analysis of author keywords as compared to the abstracts.
+This theme recurred in both analyses, although its constituent terms were ranked more highly in the analysis of author keywords as compared to abstracts.
 Another theme revolved around adolescents' physical health (sic), which was also reflected in terms like sleep, sports, and disability status.
-Again, terms related to physical health were ranked more highly in the keyword analysis than in the abstract analysis.
+There thus appears to be substantial empirical work linking emotion regulation and physical health, although this association is underrepresented in theory.
+As with the theme of developmental disorders, terms related to physical health ranked more highly in the keyword analysis than in the abstract analysis.
+This might indicate that a broader vocabulary was used to describe physical health in the abstracts.
 External stressors were another important theme, reflected in terms like bullying, stress, PTSD, abuse, violence, life events, historic events (e.g., earthquakes, war), parenting stress, and divorce.
+Based on our review of the theoretical literature, this indeed appears to be an under-theorized area.
+Conceptually, external stressors most closely align with Bronfenbrenner's notion of the exosystem [@bronfenbrennerBioecologicalModelHuman2007], but to our knowledge, they have rarely been discussed as such in the theoretical literature.
+The impression that external stressors are an undertheorized theme is reinforced by the fact that studies linking adverse life events to adolescent emotion regulation tend to appeal to prior empirical work, but not to a theoretical framework [e.g., @garnefskiNegativeLifeEvents2001; @stikkelbroekAdolescentDepressionNegative2016].
 Finally, one emergent theme that appears to be underrepresented in existing theory is structural disadvantage.
 This theme was reflected in terms like minority status and discrimination, disability status, socio-economic status, adoption status, and sexual diversity. 
-The adorementioned developmental disorders are also relevant in this context, as neuroatypical individuals may also experience such disadvantage [@cappadociaBullyingExperiencesChildren2012].
+The aforementioned developmental disorders are also relevant in this context, as neuroatypical individuals tend to experience social exclusion [@cappadociaBullyingExperiencesChildren2012].
+Future theoretical work might address these shortcomings.
 
@@
 
-<!-- 
-This second analysis focused on the abstracts of the reviewed articles.
-Several themes emerged from the terms newly identified in this analysis,
-relative to the theoretical review.
-These themes bear considerable similarity to the results of Analysis 1.
-Developmental disorders and physical health are both recurring themes, but are ranked much lower in the present analysis.
-External stressors are another recurring theme, with indicators including PTSD, bullying, stress, abuse, historic events, and divorce.
-Finally, structural disadvantage recurs,
-as reflected in minority status and discrimination, disability status, socio-economic status, adoption status, sexual diversity, and the aforementioned developmental disorders.
-
--->
-
-The co-occurrence graph revealed few connections among topics.
-Many constructs were only linked with emotion regulation,
-and there were relatively few interconnections between elements.
-This observation substantiates the prior claim that this literature is somewhat fragmented [@bussTheoriesEmotionalDevelopment2019]. 
-This sparse property of the network explains, in part,
-why some of the most prevalent terms based on term document frequency
-are absent from the co-occurrence graph (see Figure \@ref(fig:varimps)).
-This does not mean that these terms are unimportant.
-Rather, it suggests that they are not yet well-integrated in the broader literature on adolescents' emotion regulation,
-and are therefore prime candidates for future research.
-Several of these excluded constructs indeed represent active ongoing areas of research, including research on *fathers* [@vanlissaRoleFathersMothers2019], *identity* [@campbellFriendsEducationIdentity2019], *friendship* and *social support* [@wangBidirectionalEffectsExpressive2020], *autonomy* [@vrolijkLongitudinalLinkagesFather2020a; @brenningPerceivedMaternalAutonomy2015], *sexual risk* [@brownDepressiveSymptomsPredictor2006], and *loneliness* [@spithovenItAllTheir2017].
-<!-- RK: Or could they also suggest that they were relevant in the past, but not any longer? Might it be important to run sensitivity analyses by publication year?
-One recommendation for future research might be to study such important but unembedded constructs
-in conjunction with other more well-established constructs,
-as such an approach might help fill gaps in existing knowledge.-->
-
-<!-- Study 2 -->
-
-We observed a sparser network, with fewer selected terms.
+With regard to term co-occurrence, most phenomena were directly linked with emotion regulation in the keyword analysis,
+and with a central axis of emotion regulation and its mental health-related outcomes in the abstract analysis.
+The emergence of a "central axis" of dysregulation and mental health-related outcomes
+again suggest that these phenomena are consistently studied together.
+This makes sense, given the central role of emotion dyregulation in the etiology of diverse mental health problems [@leeAdolescentMentalHealth2014].
+
+Compared to the keyword analysis, the abstract analysis yielded a sparser network,
+with fewer selected terms.
 This is likely an artifact of the unstructured nature of abstracts,
@@
 Thus, fewer terms will exceed the detection threshold.
-Nonetheless, the remaining terms displayed substantial consistency with the
-analysis of author keywords.
+In line with this interpretation, exploratory analyses indicated that 99% of terms occurred only once in the abstract analysis, compared to only 78% in the keyword analysis.
+Despite the sparser network, there was substantial consistency between the terms retained in both networks.
 This supports the validity of the findings,
 suggesting that automatic keyword extraction from abstracts can identify relevant constructs,
-and may constitute a suitable alternative to author-provided keywords.
-
-The emergence of a "central axis" of dysregulation and mental health-related outcomes
-again suggest that these phenomena are consistently studied together.
-This makes sense, given the central role of emotion dyregulation in the etiology of diverse mental health problems [@leeAdolescentMentalHealth2014].
-This is in contrast to the lack of interconnectivity among other related constructs,
-which once more suggests that the literature is somewhat fragmented.
-This impression is further reinforced by the absence of many frequently occurring terms
-from the term co-occurrence graph.
-
-# General Discussion
-
-<!--it is worth noting that many different theories of *emotion* exist, and yet there is relatively little attention for the subtleties of 
-distinct from theories of emotional development, and that there is no one-to-one relationship between theories of emotion (regulation) development and theories of emotion.
-This issue is beyond the scope of the present study -->
+and may be a suitable alternative to author-provided keywords.
+
+Both analyses revealed relatively few interconnections between phenomena,
+and many of the frequently occurring terms were absent from the co-occurrence graphs due to a lack of connectivity.
+These observations empirically support the prior claim that this literature is somewhat fragmented [@bussTheoriesEmotionalDevelopment2019]. 
+The sparseness of both networks explains, in part,
+why some of the most prevalent terms based on term document frequency
+are absent from the co-occurrence graph (see Figure \@ref(fig:varimps)).
+This does not mean that these terms represent unimportant phenomena.
+Rather, it suggests that they are not well-integrated in the broader literature on adolescents' emotion regulation.
+Such phenomena might be suitable candidates for future research.
+Indeed, several of these excluded constructs represent active ongoing areas of research, including research on *fathers* [@vanlissaRoleFathersMothers2019], *identity* [@campbellFriendsEducationIdentity2019], *friendship* and *social support* [@wangBidirectionalEffectsExpressive2020], *autonomy* [@vrolijkLongitudinalLinkagesFather2020a; @brenningPerceivedMaternalAutonomy2015], *sexual risk* [@brownDepressiveSymptomsPredictor2006], and *loneliness* [@spithovenItAllTheir2017].
+One recommendation for future research might be to study such important but unembedded constructs
+in conjunction with other more well-established constructs,
+as such an approach might help fill gaps in existing knowledge.
+
+## Implications
 
@@
 
-Our work represents one of the first efforts to comprehensively map the literature on adolescents' emotion regulation [cf.
-@bariolaChildAdolescentEmotion2011; @coe-odessEmergentEmotionsAdolescence2019].
-It is also one of the first applications of inductive text mining methods in a systematic review.
-Text mining reviews offer some potential advantages when compared to narrative literature reviews [@littellEvidencebasedBiasedQuality2008]:
-They can cover vastly greater corpora than a human reader,
-and follow a somewhat more objective, transparant, and reproducible procedure.
-As such, text mining reviews offer an interesting perspective that complements theory and narrative reviews.
-
-Of course, the present study also has limitations.
-One key limitation is that the text mining techniques used here
+One strength of the present study is that it was more comprehensive than previous reviews of the literature in two respects [cf.
+@bariolaChildAdolescentEmotion2011; @coe-odessEmergentEmotionsAdolescence2019]:
+We conducted a systematic literature search, and we used text mining to comprehensively map the phenomena relevant to adolescents' emotion regulation.
+<!-- To this end, we applied text mining methods in a systematic review. We used For this purpose, It is also one of the first applications of inductive-->
+Using text mining offers unique advantages compared to narrative reviews [@littellEvidencebasedBiasedQuality2008],
+because it can cover vastly greater corpora than a sentient reader,
+and follows a somewhat more objective, transparent, and reproducible procedure.
+As such, text mining systematic reviews offer an interesting perspective that complements theory and narrative reviews.
+Moreover, text mining systematic reviews offer an inductive approach to identify relevant phenomena in a particular area of research.
+This can serve as the first step towards formal theory construction [@borsboomTheoryConstructionMethodologya].
+Our study was the first to implement this novel approach.
+
+It should be noted that this method has disadvantages as well.
+The key limitation of the present study is that the text mining techniques used here
 are not able to extract *meaning* from the literature in the way a sentient reader would, an cannot substantively interpret connections between constructs.
@@
 and has increasingly come to represent paternal influence as well. -->
-One final limitation is that our analysis was limited to keywords and abstracts.
-Analysis of full-text papers would undoubtedly yield additional insights.
-Regrettably, paywalls and the lack of a unified API currently prevent such analysis.
-This highlights the importance of open science: 
-With comprehensive open access publishing, we may one day be able to mine the entire published literature for insights.
-The recent release of 100k+ full-text papers on COVID-19 for text mining analysis on <kaggle.com> is proof of concept for this approach.
+Another limitation is that our analysis was limited to keywords and abstracts.
+The primary obstacles to the analysis of full-text publications were limited access to articles behind paywalls,
+and the absence of a standardized Application Programming Interface (API) for the automatic retrieval of articles across publishing outlets.
+<!--As the number of scientific publications on any given topic tends to show exponential increase over time, making it difficult for applied researchers to keep up.
+Meta-scientific analyses of the published literature will likely become increasingly important -->
+Comprehensive access to scientific publications is essential to all meta-scientific research, including classic systematic reviews and meta-analyses (e.g., to avoid bias in summary effect sizes).
+For text mining approaches in particular, the availability of large data sets is crucial.
+<!--Consequently, limited access to full-text publications is a major bottleneck.-->
+One example of a data set suitable for even more complex text mining analyses is a corpus of 400k+ full-text papers on COVID-19 that was made publicly available [@wangCORD19Covid19Open2020].
+Compiling such full-text data sets currently requires substantial manpower and financial resources, thus placing them out of reach for many researchers.
+<!--The authors argued that the sheer volume of available literature made it difficult for individual researchers to remain informed, thus necessitating automated text mining analysis.
+Although our analysis comprised a mere 6305 publications, even this is -->
+<!--As the number of scientific publications tends to grow exponentially across fields [@larsenRateGrowthScientific2010],
+it becomes harder for researchers to remain informed, thus necessitating meta-scientific research.-->
+An increased adoption of open access publishing,
+and the development of a unified API for article retrieval across publishing outlets,
+would facilitate curating full-text data sets.
+These changes would enable more widespread adoption and more informative application of meta-scientific (text mining) analyses.
+One final limitation is that several subjective decisions were made throughout the analysis process.
+This limitation is inherent to inductive studies, however [e.g., @wagenmakersCreativityVerificationCyclePsychological2018]:
+There are infinite possible ways to conduct exploratory analysis,
+and researchers have considerable creative license in doing so.
+We have attempted to address this limitation by explicitly mentioning important decisions in the manuscript where possible,
+and by making all analysis code and data publicly available in a fully reproducible format [based on @vanlissaWORCSWorkflowOpen2020],
+so that others may explore alternative exploratory analysis strategies.
 
 To conclude, this paper set out to map the factors associated with adolescents' emotion regulation, based on a systematic review of the literature, and text mining analysis of author keywords and abstracts.
-We provided a map of the literature on adolescents' emotion regulation,
-covering both familiar ground, and charting unknown territories.
-Our results suggested that several key themes are currently underrepresented in theory,
-and that the empirical literature is somewhat fragmented by sub-topic.
-These inductive insights are relevant for the design of new deductive studies which,
-even though grounded in theory,
-might benefit from incorporating additional relevant factors
-to better elucidate the nature of their association with adolescents' emotion regulation.
-Our analysis also identified several factors currently on the fringes of the literature,
-which might represent emerging themes that would benefit from further research [including, for example, the role of fathers @vanlissaMothersFathersQuantitative2020].
-One recommendation for future research might be to study such important but unembedded constructs
-in conjunction with other more well-established constructs,
-to bridge gaps in existing knowledge.
-Several authors have commented on the lack of an overarching theory tailored specifically to adolescent emotion regulation.
-The present work might serve as a starting point for future theory development,
-with the aim of incorporating themes from the empirical literature within the framework of existing relevant theory.
+This map covered familiar phenomena that are well-represented in existing theory,
+such as socialization and neurocognitive factors,
+which speaks to the validity of this approach.
+The structure of the map further reinforced the observation of several previous authors [e.g., @bussTheoriesEmotionalDevelopment2019]
+that the empirical literature is somewhat fragmented by subject area.
+
+Importantly, our results also draw attention to several relevant phenomena that,
+although well-represented in the empirical literature,
+are under-emphasized in narrative reviews and theory - such as developmental disorders, physical health, external stressors, structural disadvantage, substance use, identity and moral development, and sexual development.
+This has several implications for future research.
+First, the major themes identified in our inductive analysis are relevant for the design of empirical studies.
+Even when such designs are grounded in theory,
+they might benefit from additionally considering relevant phenomena as identified in our analysis as potential confounders or contributing causes.
+Second, the phenomena that appear to exist on the fringes of the existing literature according to our analysis might be suitable candidates for further study.
+These phenomena might represent emerging themes in the literature, for example, as is the case for the role of fathers [see @pleckPaternalInvolvementRevised2004; @vanlissaMothersFathersQuantitative2020].
+Future research might focus on these emerging themes in order to better elucidate the nature of their association with adolescents' emotion regulation.
+Moreover, studying these fringe phenomena in conjunction with other more well-established constructs could help embed these important but loosely connected phenomena into the mainstream literature and bridge gaps in existing knowledge.
+
+Finally, several authors have commented on the lack of an overarching theory tailored specifically to adolescent emotion regulation.
+The first step in theory construction methodology (TCM) is to identify relevant phenomena [@borsboomTheoryConstructionMethodologya].
+We have argued that text mining systematic reviews are a relatively comprehensive and objective method for identifying such phenomena, because they can evaluate much larger bodies of literature than sentient readers, and are not biased toward pre-existing ideas.
+The next step in formal theory construction methodology would be to describe and quantify the nature of the relationship of each phenomenon in relation to adolescent emotion regulation.
+The phenomena identified in the present study might thus serve as a starting point for future theory development,
+and sensitize empirical researchers to potential confounders in research on adolescents' emotion regulation.
+
+<!--
+Informally, much can be gained by revisiting existing relevant theory
+and incorporating relevant phenomena as identified in the present analysis.
 

### 2021-02-27 word_functions.R

@@ -87,6 +87,7 @@ select_fixed_margin <- function(dtm, confidence_boundary = .95, iterations = 100
 }
 
 pretty_words <- function(x){ 
+  out[out == "dysregulation"] <- "Emotion regulation"
   out <- str_to_sentence(gsub("[_-]", " ", x))
   out[out == "Adhd cd"] <- "ADHD/CD"
   out[out == "Ses"] <- "SES"

### 2021-03-01 manuscript.Rmd
Submitted revision

@@
 ---
-title             : "Mapping correlates of adolescent emotion regulation: A text-mining based systematic review"
+title             : "Mapping Correlates of Adolescent Emotion Dysregulation: A Text-mining Systematic Review"
 shorttitle        : "ADOLESCENT EMOTION REGULATION"
@@
 This has led to recent calls for the consolidation of empirical insights into overarching theory [e.g., @bussTheoriesEmotionalDevelopment2019]. 
-Formal methods for theory construction state that the first step in this endeavor is to identify the relevant *empirical phenomena* [@borsboomTheoryConstructionMethodologya; @haigExploratoryFactorAnalysis2005],
+Formal methods for theory construction state that the first step in this endeavor is to identify the relevant *empirical phenomena* [@borsboomTheoryConstructionMethodology2020; @haigExploratoryFactorAnalysis2005],
 defined as stable and general features of the world [@bogenSavingPhenomena1988].
@@
 This network can serve as a starting point for the formulation of a proto-theory,
-which would additionally involve abductive reasoning: specifying putative mechanisms to explain associations between the phenomena [@borsboomTheoryConstructionMethodologya].
+which would additionally involve abductive reasoning: specifying putative mechanisms to explain associations between the phenomena [@borsboomTheoryConstructionMethodology2020].
 By mapping the phenomena relevant to adolescent emotion regulation,
@@
 vert$frame.color <- cat_cols[vert$Category]
-#min_size <- (strwidth(vert$name[max(nchar(vert$name))]) + strwidth("oo")) * 100
+
 vert$size <- scales::rescale(log(vert$size), c(4, 12))
@@
                            directed = FALSE)
-#g <- Rsenal::pruneEdg
-#min_size <- (strwidth(vert$label[max(nchar(vert$label))]) + strwidth("oo"))*100
-
-# edge thickness
-#E(g)$width <- scales::rescale(sqrt(E(g)$width), to = c(2, 8))
 
@@
 vert$frame.color <- cat_cols[vert$Category]
-# cat_cols <- c(Outcome = "#E5E5E5", Indicator = "#FFC9AD", Cause = "#FFFF66", Protective = "#E6FF6D")
-vert$color[vert$faded] <- "#FFFFFF"#cat_cols[vert$Category[vert$faded]]
-
-#min_size <- (strwidth(vert$name[max(nchar(vert$name))]) + strwidth("oo")) * 100
+
+vert$color[vert$faded] <- "#FFFFFF"
+
 vert$size <- scales::rescale(log(vert$size), c(4, 12))
@@
                            directed = FALSE)
-#g <- Rsenal::pruneEdg
-#min_size <- (strwidth(vert$label[max(nchar(vert$label))]) + strwidth("oo"))*100
-
-# edge thickness
-#E(g)$width <- scales::rescale(sqrt(E(g)$width), to = c(2, 8))
-
-set.seed(2) #4 #2 #3
+
+set.seed(4) #4 #2 #3
 l1 <- l <- layout_with_fr(g1)
-set.seed(33)
+set.seed(3)
 l2 <- layout_with_fr(g2)
@@
   # Set margins to 0
-  par(mar=c(0,0,0,0),
+  par(mar=c(0.5,0.5,0.5,0.5),
       mfrow=c(1,2))
@@
        vertex.label.family = "sans",
-       vertex.label.cex = 0.8,
+       vertex.label.cex = 0.7,
        vertex.shape = "circle2",
@@
   )
-  legend(x=-1.1, y=1.1, names(cat_cols), pch=21, col=cat_cols, pt.bg=cat_cols, pt.cex=2, cex=.8, bty="n", ncol=1)
+  text(-1.1, y = -1, labels = "A")
+  legend(x=-1.2, y=1.1, names(cat_cols), pch=21, col=cat_cols, pt.bg=cat_cols, pt.cex=1.6, cex=.7, bty="n", ncol=1)
   plot(g2, edge.curved = 0, layout=l2,
        vertex.label.family = "sans",
-       vertex.label.cex = 0.8,
+       vertex.label.cex = 0.7,
        vertex.shape = "circle2",
@@
   )
+  text(-1.1, y = -1, labels = "B")
 })
@@
 # Save files
-png("baseline_network.png", width = 960)
+
+png("baseline_network.png", height = 100, width = 200, units = "mm", res= 300)
 eval(p)
@@
 
-```{r baseline, warning=FALSE, eval = TRUE, results='asis', out.width = "100%", fig.cap="Correlates of emotion regulation difficulties according to theory (left panel) and narrative reviews (right panel).
-Transparent circles indicate constructs also represented in the theory."}
+```{r figbaseline, warning=FALSE, eval = TRUE, results='asis', out.width = "100%", fig.cap="Phenomena relevant to adolescents' emotion regulation according to theory (A) and narrative reviews (B; transparent circles indicate constructs also present in the theory)."}
 knitr::include_graphics("baseline_network.png") 
 ```
-```{r allnetworks, warning=FALSE, eval = TRUE, results='asis', out.width = "100%", fig.cap="Correlates of emotion regulation difficulties according to theory (A), narrative reviews (B), and term co-occurrence in author keywords (C) and abstracts (D).
+```{r allnetworks, warning=FALSE, eval = FALSE, results='asis', out.width = "100%", fig.cap="Correlates of emotion regulation difficulties according to theory (A), narrative reviews (B), and term co-occurrence in author keywords (C) and abstracts (D).
 Size of lines and circles represents frequency.
@@
 <!--
-Note that the left panel of Figure \@ref(fig:allnetworks) visually summarizes the correlates of emotion regulation difficulties (labeled: *Dysregulation*) according to our theoretical review.
-The left panel of Figure \@ref(fig:allnetworks) summarizes key constructs covered by the theories reviewed above. 
+Note that the left panel of Figure \@ref(fig:tmnetworks) visually summarizes the correlates of emotion regulation difficulties (labeled: *Dysregulation*) according to our theoretical review.
+The left panel of Figure \@ref(fig:tmnetworks) summarizes key constructs covered by the theories reviewed above. 
 In the subsequent text mining analysis, we will distinguish the topics covered in this theoretical review visually to highlight unique contributions of our approach.
@@
 Note that this study is inductive (exploratory),
-as opposed to deductive (confirmatory) research, and as such does not test any hypotheses [see De Groot's work on the empirical cycle @degrootMethodologieGrondslagenVan1961][^Note that aside from induction, the term "abduction" is also used in the methodological literature.
-We consider injunction to refer to inferences based purely on observations (data).
-Abduction differs from induction because it additionally involves the attribution of observations to explanatory principles.].
+as opposed to deductive (confirmatory) research, and as such does not test any hypotheses [see De Groot's work on the empirical cycle @degrootMethodologieGrondslagenVan1961].
+Inductive methods are suitable for the detection of phenomena,
+as they aim to generalize from observations (data) without appeal to theory [@haigExploratoryFactorAnalysis2005].
 
@@
 The search strategy was based on
-procedures described by Staaks [@staaksSystematicReviewSearch]. First, we
+procedures described by Staaks [@staaksSystematicReviewSearch2019]. First, we
 constructed a reference set of 29 articles.
@@
 ```{r prismachart, eval = FALSE, results='asis', fig.cap="Record screening flowchart"}
-if(!isTRUE(tools::md5sum("prismachart.png") == "08351426aee2005edd1332a32b958ea0" )){
+if(run_everything){
   library(tidySEM)
@@
 ## Look at POS tags?
-if(!isTRUE(tools::md5sum("study1_df.RData") == "042c7d894929b0351f804c1a4b5c5002")){
-  recs <- data.table(read.csv("recs_final.csv"))
+if(run_everything){
+  recs <- read.csv("recs_final.csv")
+  recs <- as.data.table(recs)
   if(!is.data.table(recs)){
@@
 
-# LDA analysis ------------------------------------------------------------
-
-if(!isTRUE(tools::md5sum("Study1_lda_dims.txt") == "4e2493d4d618020d4acde61dd7864425")){
-  library(Rmpfr)
-  library(topicmodels)
-  library(udpipe)
-  library(slam)
-  library(tidytext)
-  # Functions:
-  harmonicMean <- function(logLikelihoods, precision = 2000L) {
-    llMed <- median(logLikelihoods)
-    as.double(llMed - log(mean(exp(-mpfr(logLikelihoods,
-                                         prec = precision) + llMed))))
-  }
-  BIC <- function(ll, p, n){
-    -2 * ll + p * log(n)
-  }
-  entropy <- function(post_prob){
-    1 + (1/(nrow(post_prob) * 
-              log(ncol(post_prob)))) * (sum(rowSums(post_prob * 
-                                                      log(post_prob + 1e-12))))
-  }
-
-  # Preprocessing -----------------------------------------------------------
-
-  #nounbydoc <- df[, list(freq = .N), by = list(doc_id = doc, term = word_coded)]
-  df_lda <- nounbydoc #[nounbydoc$term %in% names(dict), ]
-  df_lda <- df_lda %>%
-    bind_tf_idf(term, doc_id, freq)
-  summary(df_lda$tf_idf)
-  df_lda <- df_lda[order(df_lda$tf_idf),]
-
-  select_words <- df_lda[!duplicated(df_lda$term), ]
-  select_words <- select_words$term[select_words$tf_idf >= median(select_words$tf_idf)]
-  df_lda <- df_lda[df_lda$term %in% select_words, ]
-
-  dtm <- udpipe::document_term_matrix(document_term_frequencies(df_lda))
-
-  # dtm <- as.simple_triplet_matrix(dtm)
-  # dim(dtm)
-  # summary(col_sums(dtm))
-  # term_tfidf <- tapply(dtm$v/row_sums(dtm)[dtm$i], dtm$j, mean) * log2(dim(dtm)[1]/col_sums(dtm > 0))
-  # summary(term_tfidf)
-
-  yaml::write_yaml(dim(dtm), file = "Study1_lda_dims.txt")
-
-  # Build topic models
-
-  seqk <- seq(2, 20, 1)
-  burnin <- 1000
-  iter <- 1000
-  keep <- 50
-  set.seed(44773)
-  res_lda <- lapply(seqk, function(k) {
-    topicmodels::LDA(
-      dtm,
-      k = k,
-      method = "Gibbs",
-      control = list(
-        burnin = burnin,
-        iter = iter,
-        keep = keep
-      )
-    )
-  })
-
-  ll <- sapply(res_lda, function(x){harmonicMean(x@logLiks[-c(1:(burnin/keep))])})
-
-  K = seqk
-  N = nrow(dtm)
-  M = ncol(dtm)
-
-  parameters <- K*(M-1)+N*(K-1)
-  N <- nrow(dtm)
-  bics <- BIC(ll, parameters, N)
-
-  entropies <- sapply(res_lda, function(x){entropy(x@gamma)})
-
-  p <- ggplot(data.frame(K = seqk, Entropy = entropies), aes(x = K, y = Entropy)) + geom_path() +
-    xlab('Number of topics') +
-    scale_y_continuous(limits = c(0,1)) +
-    theme_bw()
-
-  ggsave("study1_entropies.png", p, device = "png")
-  ggsave("study1_entropies.svg", p, device = "svg")
-
-  p <- ggplot(data.frame(K = seqk, ll = ll), aes(x = K, y = ll)) + geom_path() +
-    geom_vline(xintercept = (which.max(ll)+1), linetype = 2) +
-    xlab('Number of topics') +
-    geom_smooth(method = "lm", formula = y~log(x), se = FALSE)+
-    theme_bw()
-
-  ggsave("study1_ll.png", p, device = "png")
-  ggsave("study1_ll.svg", p, device = "svg")
-
-  p <- ggplot(data.frame(K = seqk, BIC = bics), aes(x = K, y = BIC)) + geom_path() +
-    geom_vline(xintercept = (which.min(bics)+1), linetype = 2) +
-    xlab('Number of topics') +
-    geom_smooth(method = "lm", formula = y~x, se = FALSE)+
-    theme_bw()
-
-  ggsave("study1_BIC.png", p, device = "png")
-  ggsave("study1_BIC.svg", p, device = "svg")
-}
-
 # Co-occurrence -----------------------------------------------------------
@@
 cooc <- create_cooc(dtm_top)
-tmp <- cooc == 0
+tmp <- cooc > 0
 total_cooc <- sum(tmp[lower.tri(tmp)])
-cooc <- select_cooc(cooc, q = .975)
-tmp <- cooc == 0
+cooc <- select_cooc(create_cooc(dtm_top), q = .975)
+tmp <- cooc > 0
 total_cooc <- c(total_cooc, sum(tmp[lower.tri(tmp)]))
@@
          vertex.label.family = "sans",
-         vertex.label.cex = 0.8,
+         vertex.label.cex = 0.5,
          vertex.shape = "circle2",
@@
 Next, we computed a term co-occurrence matrix,
-which represents how frequently words occurred within the same document (see Figure \@ref(fig:allnetworks)).
+which represents how frequently words occurred within the same document (see Figure \@ref(fig:tmnetworks)).
 In total, there were `r total_cooc[1]` co-occurrence relationships.
@@
 
+```{r tmnetworks, warning=FALSE, eval = TRUE, results='asis', out.width = "100%", fig.cap="Map of phenomena relevant to adolescents' emotion regulation based on term co-occurrence in author keywords (A) and abstracts (B).
+Size of lines and circles represents frequency.
+Dashed lines represent links not involving emotion regulation.
+Transparent circles indicate constructs also represented in the theoretical review."}
+
+knitr::include_graphics("tmnetworks.png") 
+```
 ```{r study1network, eval = FALSE, warning=FALSE, out.width = "100%", fig.cap="Study 1 term co-occurrence.
@@
 
-# LDA analysis ------------------------------------------------------------
-
-if(!isTRUE(tools::md5sum("Study2_lda_dims.txt") == "2d00a24d8b54ac898eec6cd104086a0f")){
-  # Functions:
-  harmonicMean <- function(logLikelihoods, precision = 2000L) {
-    llMed <- median(logLikelihoods)
-    as.double(llMed - log(mean(exp(-mpfr(logLikelihoods,
-                                         prec = precision) + llMed))))
-  }
-  BIC <- function(ll, p, n){
-    -2 * ll + p * log(n)
-  }
-  entropy <- function(post_prob){
-    1 + (1/(nrow(post_prob) * 
-              log(ncol(post_prob)))) * (sum(rowSums(post_prob * 
-                                                      log(post_prob + 1e-12))))
-  }
-
-  # Preprocessing -----------------------------------------------------------
-
-  # Frequency of word by doc
-  nounbydoc <- df[df$upos %in% c("NOUN", "ADJ"), list(freq = .N), by = list(doc_id = doc_id, term = lemma)]
-  df_lda <- nounbydoc #[nounbydoc$term %in% names(dict), ]
-  df_lda <- df_lda %>%
-    bind_tf_idf(term, doc_id, freq)
-  summary(df_lda$tf_idf)
-
-  select_words <- df_lda[!duplicated(df_lda$term), ]
-  select_words <- select_words$term[select_words$tf_idf >= median(select_words$tf_idf)]
-  df_lda <- df_lda[df_lda$term %in% select_words, ]
-
-  dtm <- udpipe::document_term_matrix(document_term_frequencies(df_lda))
-  yaml::write_yaml(dim(dtm), file = "Study2_lda_dims.txt")
-
-  # Build topic models
-  seqk <- seq(2, 20, 1)
-  burnin <- 1000
-  iter <- 1000
-  keep <- 50
-  set.seed(44773)
-  res_lda <- lapply(seqk, function(k) {
-    topicmodels::LDA(
-      dtm,
-      k = k,
-      method = "Gibbs",
-      control = list(
-        burnin = burnin,
-        iter = iter,
-        keep = keep
-      )
-    )
-  })
-
-  ll <- sapply(res_lda, function(x){harmonicMean(x@logLiks[-c(1:(burnin/keep))])})
-
-  K = seqk
-  N = nrow(dtm)
-  M = ncol(dtm)
-
-  parameters <- K*(M-1)+N*(K-1)
-  N <- nrow(dtm)
-  bics <- BIC(ll, parameters, N)
-
-  entropies <- sapply(res_lda, function(x){entropy(x@gamma)})
-
-  p <- ggplot(data.frame(K = seqk, Entropy = entropies), aes(x = K, y = Entropy)) + geom_path() +
-    xlab('Number of topics') +
-    scale_y_continuous(limits = c(0,1)) +
-    theme_bw()
-
-  ggsave("study2_entropies.png", p, device = "png")
-  ggsave("study2_entropies.svg", p, device = "svg")
-
-  p <- ggplot(data.frame(K = seqk, ll = ll), aes(x = K, y = ll)) + geom_path() +
-    geom_vline(xintercept = (which.max(ll)+1), linetype = 2) +
-    xlab('Number of topics') +
-    geom_smooth(method = "lm", formula = y~log(x), se = FALSE)+
-    theme_bw()
-
-  ggsave("study2_ll.png", p, device = "png")
-  ggsave("study2_ll.svg", p, device = "svg")
-
-  p <- ggplot(data.frame(K = seqk, BIC = bics), aes(x = K, y = BIC)) + geom_path() +
-    geom_vline(xintercept = (which.min(bics)+1), linetype = 2) +
-    xlab('Number of topics') +
-    geom_smooth(method = "lm", formula = y~x, se = FALSE)+
-    theme_bw()
-
-  ggsave("study2_BIC.png", p, device = "png")
-  ggsave("study2_BIC.svg", p, device = "svg")
-}
-
 # Keyword extraction ------------------------------------------------------
@@
 # Exclude words
-if(isTRUE(tools::md5sum("study2_df_kw.RData") == "8c9b3d61fa7e9bb6a3b31962b11face1")){
+if(!run_everything){
   df_kw <- readRDS("study2_df_kw.RData")
@@
 
-if(isTRUE(tools::md5sum("study2_textrank.RData") == "dcaf7c9bab7a4abd86d19d4868fad780")){
+if(!run_everything){
   kw_tr <- readRDS("study2_textrank.RData")
@@
 
-if(isTRUE(tools::md5sum("study2_df_analyze.RData") == "e50ee4984e0872947342d868e3bc9144")){
+if(!run_everything){
   df_analyze <- data.table(readRDS("study2_df_analyze.RData"))
@@
 cooc <- create_cooc(dtm_top)
-tmp <- cooc == 0
+tmp <- cooc > 0
 total_cooc_2 <- sum(tmp[lower.tri(tmp)])
 cooc <- select_cooc(create_cooc(dtm_top), q = .975)
-tmp <- cooc == 0
-total_cooc_2 <- c(total_cooc_2, sum(tmp[lower.tri(tmp)]))
+tmp <- cooc > 0
+total_cooc_2 <- c(total_cooc_2, sum((tmp > 0)[lower.tri(tmp)]))
 
@@
     )
+    text(-1.1, y = -1, labels = "A")
     legend(x=-1.1, y=1.1, names(cat_cols), pch=21, col="#777777", pt.bg=cat_cols, pt.cex=2, cex=.8, bty="n", ncol=1)
@@
     )
+    text(-1.1, y = -1, labels = "B")
   })
@@
 ```
-
+```{r mergenetworks}
+cat_cols <- c(Outcome = "gray50", Indicator = "tomato", Cause = "gold", Protective = "olivedrab2")
+bl1 <- readRDS("bl_l1.RData")
+bl2 <- readRDS("bl_l2.RData")
+bg1 <- readRDS("bl_g1.RData")
+bg2 <- readRDS("bl_g2.RData")
+s1l <- readRDS("s1_l1.RData")
+s2l <- readRDS("s2_l1.RData")
+s1g <- readRDS("s1_g1.RData")
+s2g <- readRDS("s2_g1.RData")
+p <- quote({
+  # Set margins to 0
+  par(mar=c(0,0,0,0),
+      mfrow=c(2,2))
+  plot(bg1, edge.curved = 0,
+       layout=bl1,
+       vertex.label.family = "sans",
+       vertex.label.cex = 0.5,
+       vertex.shape = "circle2",
+       vertex.label.color = 'black',      # Color of node names
+       vertex.label.font = 1,         # Font of node names
+       vertex.frame.width = 2
+  )
+  text(-1.1, y = -1, labels = "A")
+  legend(x=-1.1, y=1.1, names(cat_cols), pch=21, col=cat_cols, pt.bg=cat_cols, pt.cex=2, cex=.8, bty="n", ncol=1)
+
+  plot(bg2, edge.curved = 0,
+       layout=bl2,
+       vertex.label.family = "sans",
+       vertex.label.cex = 0.5,
+       vertex.shape = "circle2",
+       #vertex.frame.color = 'gray40',
+       vertex.label.color = 'black',      # Color of node names
+       vertex.label.font = 1,         # Font of node names
+       vertex.frame.width = 2
+  )
+  text(-1.1, y = -1, labels = "B")
+  plot(s1g, edge.curved = 0,
+       layout=s1l,
+       vertex.label.family = "sans",
+       vertex.label.cex = 0.5,
+       vertex.shape = "circle2",
+       #vertex.frame.color = 'gray40',
+       vertex.label.color = 'black',      # Color of node names
+       vertex.label.font = 1,         # Font of node names
+       vertex.frame.width = 2
+  )
+  text(-1.1, y = -1, labels = "C")
+  plot(s2g, edge.curved = 0,
+       layout=s2l,
+       vertex.label.family = "sans",
+       vertex.label.cex = 0.5,
+       vertex.shape = "circle2",
+       #vertex.frame.color = 'gray40',
+       vertex.label.color = 'black',      # Color of node names
+       vertex.label.font = 1,         # Font of node names
+       vertex.frame.width = 2
+  )
+  text(-1.1, y = -1, labels = "D")
+})
+
+# Save files
+# png("networks.png", width = 960)
+# eval(p)
+# dev.off()
+png("networks.png", height = 200, width = 200, units = "mm", res= 300)
+eval(p)
+dev.off()
+
+svg("networks.svg", width = 14)
+eval(p)
+dev.off()
+
+p <- quote({
+  # Set margins to 0
+  par(mar=c(0.5,0.5,0.5,0.5),
+      mfrow=c(1,2))
+  plot(s1g, edge.curved = 0,
+       layout=s1l,
+       vertex.label.family = "sans",
+       vertex.label.cex = 0.5,
+       vertex.shape = "circle2",
+       #vertex.frame.color = 'gray40',
+       vertex.label.color = 'black',      # Color of node names
+       vertex.label.font = 1,         # Font of node names
+       vertex.frame.width = 2
+  )
+  text(-1.1, y = -1, labels = "A")
+  legend(x=-1.2, y=1.1, names(cat_cols), pch=21, col=cat_cols, pt.bg=cat_cols, pt.cex=1.6, cex=.6, bty="n", ncol=1)
+
+  plot(s2g, edge.curved = 0,
+       layout=s2l,
+       vertex.label.family = "sans",
+       vertex.label.cex = 0.5,
+       vertex.shape = "circle2",
+       #vertex.frame.color = 'gray40',
+       vertex.label.color = 'black',      # Color of node names
+       vertex.label.font = 1,         # Font of node names
+       vertex.frame.width = 2
+  )
+  text(-1.1, y = -1, labels = "B")
+
+})
+
+png("tmnetworks.png", height = 100, width = 200, units = "mm", res= 300)
+eval(p)
+dev.off()
+
+svg("tmnetworks.svg", width = 14)
+eval(p)
+dev.off()
+```
 The corpus for this second analysis consisted of the abstracts of the selected articles.
@@
 This is sufficient to capture trigrams, like "parent-child conflict",
-but would not capture quardragrams like "parent-child conflict resolution".
+but would not capture quadragrams like "parent-child conflict resolution".
 The resulting $n$-grams were merged with the original data.
@@
 This is a subjective criterion, which corresponded to terms that co-occurred in more than `r attr(cooc, "thres")` documents.
-After pruning, `r total_cooc[2]` co-occurrence relationships remained.
-Figure \@ref(fig:allnetworks) displays the resulting co-occurrence matrix as a force directed graph.
+After pruning, `r total_cooc_2[2]` co-occurrence relationships remained.
+Figure \@ref(fig:tmnetworks) displays the resulting co-occurrence matrix as a force directed graph.
 
@@
 <!-- Co-occurrence -->
-With regard to the term co-occurrence analyses, the analysis of  keywords (Analysis 1, see Figure \@ref(fig:allnetworks)) indicated that 
+With regard to the term co-occurrence analyses, the analysis of  keywords (Analysis 1, see Figure \@ref(fig:tmnetworks)) indicated that 
 emotion regulation is evidently a central construct
@@
 researchers typically rely on theoretical foundations when planning a study.
-By providing a conceptual overview of the empirical literature,
-the present study offers some preliminary guidance regarding potentially relevant topics to consider.
+By providing an overview of phenomena relevant to adolescents' emotion regulation based on an inductive analysis of the empirical literature,
+the present study offers guidance regarding potentially relevant topics to consider.
 An important direction for future research would be to formalize these inductive insights into a new overarching theory of adolescent emotion regulation.
-In doing so, the co-occurrence graphs of relevant constructs arising from our inductive review may serve as a template for a nomological network:
-a proto-theoretical diagrammatic representation that describes relationships between
-constructs relevant to the theory.
-The generation of such nomological networks constitutes a first step in theory generation [see @alaviAligningTheoryMethodology2018].
+Going beyond the inductive identification of relevant phenomena,
+the next step in theory construction would involve abductive reasoning: the attribution of observations to causal explanatory principles [@haigExploratoryFactorAnalysis2005].
+As a starting point for this effort, the co-occurrence graphs derived from our analyses could be
+used as templates for a nomological network:
+a proto-theoretical diagrammatic representation that describes causal relationships between
+relevant phenomena [see @alaviAligningTheoryMethodology2018].
 
@@
 Moreover, text mining systematic reviews offer an inductive approach to identify relevant phenomena in a particular area of research.
-This can serve as the first step towards formal theory construction [@borsboomTheoryConstructionMethodologya].
+This can serve as the first step towards formal theory construction [@borsboomTheoryConstructionMethodology2020].
 Our study was the first to implement this novel approach.
@@
 Finally, several authors have commented on the lack of an overarching theory tailored specifically to adolescent emotion regulation.
-The first step in theory construction methodology (TCM) is to identify relevant phenomena [@borsboomTheoryConstructionMethodologya].
+The first step in theory construction methodology (TCM) is to identify relevant phenomena [@borsboomTheoryConstructionMethodology2020].
 We have argued that text mining systematic reviews are a relatively comprehensive and objective method for identifying such phenomena, because they can evaluate much larger bodies of literature than sentient readers, and are not biased toward pre-existing ideas.
@@
 
+On behalf of all authors, the corresponding author states that there is no conflict of interest
 <!--
 Informally, much can be gained by revisiting existing relevant theory
-and incorporating relevant phenomena as identified in the present analysis.
-
-```{r mergenetworks}
-cat_cols <- c(Outcome = "gray50", Indicator = "tomato", Cause = "gold", Protective = "olivedrab2")
-bl1 <- readRDS("bl_l1.RData")
-bl2 <- readRDS("bl_l2.RData")
-bg1 <- readRDS("bl_g1.RData")
-bg2 <- readRDS("bl_g2.RData")
-s1l <- readRDS("s1_l1.RData")
-s2l <- readRDS("s2_l1.RData")
-s1g <- readRDS("s1_g1.RData")
-s2g <- readRDS("s2_g1.RData")
-p <- quote({
-  # Set margins to 0
-  par(mar=c(0,0,0,0),
-      mfrow=c(2,2))
-  plot(bg1, edge.curved = 0,
-       layout=bl1,
-       vertex.label.family = "sans",
-       vertex.label.cex = 0.8,
-       vertex.shape = "circle2",
-       vertex.label.color = 'black',      # Color of node names
-       vertex.label.font = 1,         # Font of node names
-       vertex.frame.width = 2
-  )
-  text(-1.1, y = -1, labels = "A")
-  legend(x=-1.1, y=1.1, names(cat_cols), pch=21, col=cat_cols, pt.bg=cat_cols, pt.cex=2, cex=.8, bty="n", ncol=1)
-
-  plot(bg2, edge.curved = 0,
-       layout=bl2,
-       vertex.label.family = "sans",
-       vertex.label.cex = 0.8,
-       vertex.shape = "circle2",
-       #vertex.frame.color = 'gray40',
-       vertex.label.color = 'black',      # Color of node names
-       vertex.label.font = 1,         # Font of node names
-       vertex.frame.width = 2
-  )
-  text(-1.1, y = -1, labels = "B")
-  plot(s1g, edge.curved = 0,
-       layout=s1l,
-       vertex.label.family = "sans",
-       vertex.label.cex = 0.8,
-       vertex.shape = "circle2",
-       #vertex.frame.color = 'gray40',
-       vertex.label.color = 'black',      # Color of node names
-       vertex.label.font = 1,         # Font of node names
-       vertex.frame.width = 2
-  )
-  text(-1.1, y = -1, labels = "C")
-  plot(s2g, edge.curved = 0,
-       layout=s2l,
-       vertex.label.family = "sans",
-       vertex.label.cex = 0.8,
-       vertex.shape = "circle2",
-       #vertex.frame.color = 'gray40',
-       vertex.label.color = 'black',      # Color of node names
-       vertex.label.font = 1,         # Font of node names
-       vertex.frame.width = 2
-  )
-  text(-1.1, y = -1, labels = "D")
-})
-
-# Save files
-# png("networks.png", width = 960)
-# eval(p)
-# dev.off()
-png("networks.png", height = 200, width = 200, units = "mm", res= 300)
-eval(p)
-dev.off()
-
-svg("networks.svg", width = 14)
-eval(p)
-dev.off()
+and incorporating relevant phenomena as identified in the present analysis.-->
+```{r, eval = FALSE}
+# These analyses takes very long (~30m); set eval = TRUE to re-run them.
+if(run_everything){
+  rmarkdown::render("topic_models.Rmd")
+}
 ```

### 2021-03-01 topic_models.Rmd
Submitted revision

@@
 library(yaml)
+library(stringr)
+library(udpipe)
+library(igraph)
+library(wordcloud)
+library(Matrix)
+library(yaml)
+library(Rmpfr)
+library(topicmodels)
+library(udpipe)
+library(slam)
+library(tidytext)
+library(ggplot2)
+library(textrank)
+source("word_functions.R")
 knitr::opts_chunk$set(echo = FALSE)
+
+# LDA analysis ------------------------------------------------------------
+
+# Functions:
+harmonicMean <- function(logLikelihoods, precision = 2000L) {
+  llMed <- median(logLikelihoods)
+  as.double(llMed - log(mean(exp(-mpfr(logLikelihoods,
+                                       prec = precision) + llMed))))
+}
+BIC <- function(ll, p, n){
+  -2 * ll + p * log(n)
+}
+entropy <- function(post_prob){
+  1 + (1/(nrow(post_prob) * 
+            log(ncol(post_prob)))) * (sum(rowSums(post_prob * 
+                                                    log(post_prob + 1e-12))))
+}
+
+# Preprocessing -----------------------------------------------------------
+df <- readRDS("study1_df.RData")
+
+# Frequency of word by doc
+nounbydoc <- df[, list(freq = .N), by = list(doc_id = doc, term = word_coded)]
+# Set frequency to 1; we're not interpreting word frequency, only occurrence
+nounbydoc$freq <- 1
+
+df_lda <- nounbydoc #[nounbydoc$term %in% names(dict), ]
+df_lda <- df_lda %>%
+  bind_tf_idf(term, doc_id, freq)
+summary(df_lda$tf_idf)
+df_lda <- df_lda[order(df_lda$tf_idf),]
+
+select_these <- df_lda[!duplicated(df_lda$term), ]
+select_these <- select_these$term[select_these$tf_idf >= median(select_these$tf_idf)]
+df_lda <- df_lda[df_lda$term %in% select_these, ]
+
+dtm <- udpipe::document_term_matrix(document_term_frequencies(df_lda))
+
+# dtm <- as.simple_triplet_matrix(dtm)
+# dim(dtm)
+# summary(col_sums(dtm))
+# term_tfidf <- tapply(dtm$v/row_sums(dtm)[dtm$i], dtm$j, mean) * log2(dim(dtm)[1]/col_sums(dtm > 0))
+# summary(term_tfidf)
+
+yaml::write_yaml(dim(dtm), file = "Study1_lda_dims.txt")
+
+# Build topic models
+
+seqk <- seq(2, 20, 1)
+burnin <- 1000
+iter <- 1000
+keep <- 50
+set.seed(44773)
+res_lda <- lapply(seqk, function(k) {
+  topicmodels::LDA(
+    dtm,
+    k = k,
+    method = "Gibbs",
+    control = list(
+      burnin = burnin,
+      iter = iter,
+      keep = keep
+    )
+  )
+})
+
+ll <- sapply(res_lda, function(x){harmonicMean(x@logLiks[-c(1:(burnin/keep))])})
+
+K = seqk
+N = nrow(dtm)
+M = ncol(dtm)
+
+parameters <- K*(M-1)+N*(K-1)
+N <- nrow(dtm)
+bics <- BIC(ll, parameters, N)
+
+entropies <- sapply(res_lda, function(x){entropy(x@gamma)})
+
+p <- ggplot(data.frame(K = seqk, Entropy = entropies), aes(x = K, y = Entropy)) + geom_path() +
+  xlab('Number of topics') +
+  scale_y_continuous(limits = c(0,1)) +
+  theme_bw()
+
+ggsave("study1_entropies.png", p, device = "png")
+ggsave("study1_entropies.svg", p, device = "svg")
+
+p <- ggplot(data.frame(K = seqk, ll = ll), aes(x = K, y = ll)) + geom_path() +
+  geom_vline(xintercept = (which.max(ll)+1), linetype = 2) +
+  xlab('Number of topics') +
+  geom_smooth(method = "lm", formula = y~log(x), se = FALSE)+
+  theme_bw()
+
+ggsave("study1_ll.png", p, device = "png")
+ggsave("study1_ll.svg", p, device = "svg")
+
+p <- ggplot(data.frame(K = seqk, BIC = bics), aes(x = K, y = BIC)) + geom_path() +
+  geom_vline(xintercept = (which.min(bics)+1), linetype = 2) +
+  xlab('Number of topics') +
+  geom_smooth(method = "lm", formula = y~x, se = FALSE)+
+  theme_bw()
+
+ggsave("study1_BIC.png", p, device = "png")
+ggsave("study1_BIC.svg", p, device = "svg")
+
 lda_dims <- read_yaml("Study1_lda_dims.txt")
@@
 ```{r, warning=FALSE, message=FALSE}
+df <- readRDS("study2_df.RData")
+# Functions:
+harmonicMean <- function(logLikelihoods, precision = 2000L) {
+  llMed <- median(logLikelihoods)
+  as.double(llMed - log(mean(exp(-mpfr(logLikelihoods,
+                                       prec = precision) + llMed))))
+}
+BIC <- function(ll, p, n){
+  -2 * ll + p * log(n)
+}
+entropy <- function(post_prob){
+  1 + (1/(nrow(post_prob) * 
+            log(ncol(post_prob)))) * (sum(rowSums(post_prob * 
+                                                    log(post_prob + 1e-12))))
+}
+
+# Preprocessing -----------------------------------------------------------
+
+# Frequency of word by doc
+nounbydoc <- df[df$upos %in% c("NOUN", "ADJ"), list(freq = .N), by = list(doc_id = doc_id, term = lemma)]
+df_lda <- nounbydoc #[nounbydoc$term %in% names(dict), ]
+df_lda <- df_lda %>%
+  bind_tf_idf(term, doc_id, freq)
+summary(df_lda$tf_idf)
+
+select_these <- df_lda[!duplicated(df_lda$term), ]
+select_these <- select_these$term[select_these$tf_idf >= median(select_these$tf_idf)]
+df_lda <- df_lda[df_lda$term %in% select_these, ]
+
+dtm <- udpipe::document_term_matrix(document_term_frequencies(df_lda))
+yaml::write_yaml(dim(dtm), file = "Study2_lda_dims.txt")
+
+# Build topic models
+seqk <- seq(2, 20, 1)
+burnin <- 1000
+iter <- 1000
+keep <- 50
+set.seed(44773)
+res_lda <- lapply(seqk, function(k) {
+  topicmodels::LDA(
+    dtm,
+    k = k,
+    method = "Gibbs",
+    control = list(
+      burnin = burnin,
+      iter = iter,
+      keep = keep
+    )
+  )
+})
+
+ll <- sapply(res_lda, function(x){harmonicMean(x@logLiks[-c(1:(burnin/keep))])})
+
+K = seqk
+N = nrow(dtm)
+M = ncol(dtm)
+
+parameters <- K*(M-1)+N*(K-1)
+N <- nrow(dtm)
+bics <- BIC(ll, parameters, N)
+
+entropies <- sapply(res_lda, function(x){entropy(x@gamma)})
+
+p <- ggplot(data.frame(K = seqk, Entropy = entropies), aes(x = K, y = Entropy)) + geom_path() +
+  xlab('Number of topics') +
+  scale_y_continuous(limits = c(0,1)) +
+  theme_bw()
+
+ggsave("study2_entropies.png", p, device = "png")
+ggsave("study2_entropies.svg", p, device = "svg")
+
+p <- ggplot(data.frame(K = seqk, ll = ll), aes(x = K, y = ll)) + geom_path() +
+  geom_vline(xintercept = (which.max(ll)+1), linetype = 2) +
+  xlab('Number of topics') +
+  geom_smooth(method = "lm", formula = y~log(x), se = FALSE)+
+  theme_bw()
+
+ggsave("study2_ll.png", p, device = "png")
+ggsave("study2_ll.svg", p, device = "svg")
+
+p <- ggplot(data.frame(K = seqk, BIC = bics), aes(x = K, y = BIC)) + geom_path() +
+  geom_vline(xintercept = (which.min(bics)+1), linetype = 2) +
+  xlab('Number of topics') +
+  geom_smooth(method = "lm", formula = y~x, se = FALSE)+
+  theme_bw()
+
+ggsave("study2_BIC.png", p, device = "png")
+ggsave("study2_BIC.svg", p, device = "svg")
 lda_dims_2 <- read_yaml("Study2_lda_dims.txt")

### 2021-03-01 word_functions.R

@@ -87,8 +87,9 @@ select_fixed_margin <- function(dtm, confidence_boundary = .95, iterations = 100
 }
 
 pretty_words <- function(x){ 
-  out[out == "dysregulation"] <- "Emotion regulation"
-  out <- str_to_sentence(gsub("[_-]", " ", x))
+  out <- x
+  out[tolower(out) == "dysregulation"] <- "Emotion regulation"
+  out <- str_to_sentence(gsub("[_-]", " ", out))
   out[out == "Adhd cd"] <- "ADHD/CD"
   out[out == "Ses"] <- "SES"
   out[out == "Ptsd"] <- "PTSD"

### 2021-03-02 manuscript.Rmd
update 2021-03-02 16:51:13

@@
   literature is fragmented across subdisciplines, and an overarching
-  theoretical framework is lacking. The first step towards constructing a
+  theoretical framework is lacking. The first step toward constructing a
   unifying framework is identifying relevant phenomena. This systematic
   review of 6305 papers used text mining to identify phenomena relevant to
-  adolescents' emotion regulation. We first established a baseline of
-  relevant phenomena discussed in theory and recent narrative reviews. We
-  then conducted text mining analyses of article keywords and abstracts,
+  adolescents' emotion regulation. First, a baseline was established of
+  relevant phenomena discussed in theory and recent narrative reviews. Then,
+  article keywords and abstracts were analyzed using text mining,
   examining term frequency as an indicator of relevance and term
-  co-occurrence as an indicator of association. Results reflected themes
+  co-occurrence as an indicator of association. The results reflected themes
   commonly featured in theory and narrative reviews, such as socialization
@@
   structural disadvantage, substance use, identity and moral development, and
-  sexual development. This illustrates how text mining systematic reviews
-  (TMSR), a novel approach, may complement narrative reviews. Future
-  theoretical work might seek to integrate these undertheorized themes into
+  sexual development. The findings illustrate how text mining systematic
+  reviews, a novel approach, may complement narrative reviews. Future
+  theoretical work might integrate these undertheorized themes into
   an overarching framework, and empirical research might consider them as
-  promising areas for future research, or potential confounders in research
+  promising areas for future research, or as potential confounders in research
   on adolescents' emotion regulation.
+
 keywords          : "emotion regulation, adolescence, systematic review, text mining, machine
 learning"
-wordcount         : "6311"
 bibliography      : ["veni_sysrev.bib"]
@@
 
-Adolescence is a life stage ranging from pubertal onset to adult-like independence [@steinbergAgeOpportunityLessons2014; @sawyerAgeAdolescence2018].
+Adolescence is a life stage ranging from pubertal onset to adult-like independence [@steinbergAgeOpportunityLessons2014; @@sawyerAgeAdolescence2018].
 A key developmental challenge in this stage is acquiring mature emotion
-regulation skills [@croneUnderstandingAdolescencePeriod2012;
+regulation skills [@@croneUnderstandingAdolescencePeriod2012;
 @zimmermannEmotionRegulationEarly2014]. 
@@
 Although most adolescents eventually develop mature emotion regulation abilities,
-for as many as one in five [@leeAdolescentMentalHealth2014],
+for as many as one in five,
 adolescence marks the onset of
-life course persistent emotion regulation-related psychopathology
-[see also @aldaoEmotionregulationStrategiesPsychopathology2010;
-@schaferEmotionRegulationStrategies2017].
+life course persistent psychopathology [@leeAdolescentMentalHealth2014]
+rooted in emotion regulation difficulties
+[@aldaoEmotionregulationStrategiesPsychopathology2010;
+@@schaferEmotionRegulationStrategies2017].
 Given the prevalence of emotion regulation difficulties in adolescence,
@@
 Despite the abundance of publications in this field,
-several prior theoretical and empirical reviews have argued that the literature is somewhat fragmented,
-because different (sub)disciplines have approached the issue in disparate ways,
-in the absence of consistent terminology and unifying theory 
-[@bussTheoriesEmotionalDevelopment2019; @bariolaChildAdolescentEmotion2011; @stifterEmotionRegulation2019].
-
-This has led to recent calls for the consolidation of empirical insights into overarching theory [e.g., @bussTheoriesEmotionalDevelopment2019]. 
-Formal methods for theory construction state that the first step in this endeavor is to identify the relevant *empirical phenomena* [@borsboomTheoryConstructionMethodology2020; @haigExploratoryFactorAnalysis2005],
-defined as stable and general features of the world [@bogenSavingPhenomena1988].
-We propose that systematic reviews are a suitable method for taking this first step,
+prior reviews have argued that it is difficult to obtain a comprehensive understanding of emotion regulation in adolescence [@riedigerEmotionRegulationAdolescence2014] because
+because different (sub)disciplines have approached the issue in disparate ways [@riedigerEmotionRegulationAdolescence2014],
+in the absence of consistent terminology [@bariolaChildAdolescentEmotion2011] and conceptual frameworks [@stifterEmotionRegulation2019], and a lack of unifying theory 
+[@bussTheoriesEmotionalDevelopment2019].
+
+The fragmented state of the literature has prompted recent calls for the integration of heterogeneous research areas [@riedigerEmotionRegulationAdolescence2014] and consolidation of empirical insights into overarching theory [e.g., @bussTheoriesEmotionalDevelopment2019].
+Formal methods for theory construction state that the first step in this endeavor is to identify the relevant *empirical phenomena* [@borsboomTheoryConstructionMethodology2020],
+defined as stable and general features of the world[@@bogenSavingPhenomena1988].
+The present paper argues that systematic reviews are a suitable method for taking this first step,
 based on the assumption that phenomena considered to be stable and general will be more frequently represented in the published literature.<!-- the frequency with which phenomena occur in the literature is indicative of their relevance.-->
@@
 and an undue emphasis on positive results [@littellEvidencebasedBiasedQuality2008].
-We intend to overcome these limitations by adopting a novel method:
+This paper aims to overcome these limitations by adopting a novel method:
 the text mining systematic review (TMSR).
@@
 This approach considers the frequency with which phenomena occur in the literature to be indicative of their relevance.
-If we additionally assume that the frequency with which phenomena are studied together is indicative of the extent to which researchers believe them to be associated,
+If it is additionally assumed that the frequency with which phenomena are studied together is indicative of the extent to which researchers believe them to be associated,
 then the co-occurrence of phenomena within publications can be interpreted as a rudimentary nomological network: a mapping of relationships between theoretically relevant phenomena [see @alaviAligningTheoryMethodology2018].
@@
 <!--
+stifterEmotionRegulation2019
+* call for studies incorporating predictors of ER across multiple levels of analysis
+* different conceptual frameworks
+
+riedigerEmotionRegulationAdolescence2014
+* difficulty in deriving a cohesive picture about emotion regulation in adolescence
+* different conceptual frameworks
+
+* three themes (neurocognitive development, socialization, interplay between internal and external factors) currently represent relatively independent bodies of research
+* A more explicit integration of these various research perspectives will help us to arrive at a more integrated and interpretable picture of the development of emorion regulation during adolescence.
+
+@bussTheoriesEmotionalDevelopment2019
+
+* emotional development theory is still in its own state of development. 
+* empirical evidence can contribute to theory development.
+
+@bariolaChildAdolescentEmotion2011
+* Further research apply reﬁned theoretical conceptualizations of ER.
+
 Where sentient readers tend to structure their reading of the literature around established ideas [@littellEvidencebasedBiasedQuality2008],
@@
 many *relevant* theories are commonly invoked in empirical work [see  @bussTheoriesEmotionalDevelopment2019].
-In order to contextualize the results of our systematic review
+In order to contextualize the results of the present systematic review
 and assess to what extent the identified phenomena through text mining mirror or complement existing theory,
-we provide a brief review of the existing theoretical landscape.
+a brief review of the existing theoretical landscape is provided.
 Others have published more detailed reviews of theories of emotional development [@bussTheoriesEmotionalDevelopment2019] and emotion regulation in adolescence [@riedigerEmotionRegulationAdolescence2014].
 In reading the theoretical literature,
-we documented relevant phenomena and whether these were discussed as putative causes, outcomes, indicators, or protective factors in relation to emotion regulation.
-The left panel of Figure \@ref(fig:figbaseline) visually summarizes the phenomena discussed in the theoretical literature, using a style similar to our subsequent systematic review,
-in order to facilitate contextualizing our original findings.
+relevant phenomena were documented, along with whether these were discussed as putative causes, outcomes, indicators, or protective factors in relation to emotion regulation.
+The left panel of Figure \@ref(fig:figbaseline) visually summarizes the phenomena discussed in the theoretical literature, using a style similar to the subsequent systematic review,
+in order to contextualize the original contributions of this approach.
 <!-- 
@@
 
-Two of the most general theories invoked to frame developmental research are Bronfenbrenner's bioecological model, and Sameroff's
-transactional model.
-Bronfenbrenner [-@bronfenbrennerBioecologicalModelHuman2007] describes how the `r keyw("environment")`
+Two of the most general theories invoked to frame developmental research are the bioecological model [@bronfenbrennerBioecologicalModelHuman2007], and the transactional model [@sameroffUnifiedTheoryDevelopment2010].
+The bioecological model describes how the `r keyw("environment")`
 shapes individual development.
@@
 and the exosystem, consisting of `r keyw("cultural")` norms and `r keyw("values")`.
-Sameroff's model [-@sameroffUnifiedTheoryDevelopment2010] is compatible with Bronfenbrenner's work,
+The transactional model [@sameroffUnifiedTheoryDevelopment2010] is compatible with the bioecological model,
 but places a stronger emphasis on development as a product of reciprocal influences between child and environment.
-Sameroff distinguishes between proximal influences, which roughly correspond to the microsystem in Bronfenbrenner's model, and distal influences, which derive from
+The transactional model distinguishes between proximal influences, which roughly correspond to the microsystem in the bioecological model, and distal influences, which derive from
 structural factors indirectly shaping development, like `r keyw("socio-economic status")`,
@@
 but lack specificity - a shortcoming that curtails a theory's utility in generating hypotheses.
-We thus turn toward more domain-specific theories.
+Domain-specific theories, by comprarison, offer greater specificity.
 
@@
 regulation difficulties, increased `r keyw("conflict with parents")`, and `r keyw("risky behavior")`.
-Hall's notion of diminished self-control and increased emotional reactivity still persists in modern theory, but is increasingly recast as a normative change that facilitates emotional maturation at the risk of emotional
-disturbance [@arnettAdolescentStormStress1999; @leeAdolescentMentalHealth2014].
-[@croneUnderstandingAdolescencePeriod2012] 
-A potential limitation of Hall's notion of storm and stress is that it describes emotion regulation difficulties as a part of normative development, and thus underemphasizes adolescents' diverging destinies [cf.
+This notion of diminished self-control and increased emotional reactivity still persists in modern theory, but is increasingly recast as a normative change that facilitates emotional maturation at the risk of emotional
+disturbance [@arnettAdolescentStormStress1999; @@leeAdolescentMentalHealth2014; @@croneUnderstandingAdolescencePeriod2012] 
+A potential limitation of the notion of storm and stress is that it considers emotion regulation difficulties to be part of normative development, and thus underemphasizes adolescents' diverging destinies [cf.
 @croneUnderstandingAdolescencePeriod2012].
@@
 
-Sroufe's [-@sroufeEmotionalDevelopmentOrganization1995] theory of normative emotional development focuses on developmental influences to a greater extent.
-Sroufe argues that, as children grow older,
+One theory of normative emotional development [@sroufeEmotionalDevelopmentOrganization1995] focuses on developmental influences to a greater extent.
+This theory posits that, as children grow older,
 their increasing `r keyw("self-regulatory")` abilities
 drive a transition from external emotion regulation by `r keyw("primary caregivers")`
-towards autonomous emotion regulation.
+toward autonomous emotion regulation.
 This theory focuses on two drivers of
@@
 For instance, there is substantial similarity between mothers' and fathers' unique roles in emotional development in childhood [@vanlissaMothersFathersQuantitative2020] and adolescence [@vanlissaRoleFathersMothers2019].
-In terms of level of analysis, the scope of Sroufe's and Hall's theories corresponds approximately to the individual and the microsystem in Bronfenbrenner's ecological model.
+In terms of level of analysis, the scope of Sroufe's and Hall's theories corresponds approximately to the individual and the microsystem in the ecological model [@bronfenbrennerBioecologicalModelHuman2007].
 The emphasis on socialization and `r keyw("neurocognitive development")` as two drivers of emotional development, which is evident from both theories,
@@
 
-Among theories focused on socialization, Morris' tripartite model is widely cited in the field [-@morrisRoleFamilyContext2007].
+Among theories focused on socialization, the tripartite model [@morrisRoleFamilyContext2007] is widely cited.
 This theory describes three pathways through which `r keyw("parents")` shape emotion regulation
@@
 Others in turn have adapted the tripartite model to describe the influence of peers [@reindlSocializationEmotionRegulation2016], thus illustrating its wider usefulness in understanding socialization.
-A more abstract take on socialization is found in @holodynskiDevelopmentEmotionsEmotion2006's
-internalization model of emotional development. 
+A more abstract take on socialization is found in the internalization model of emotional development [@holodynskiDevelopmentEmotionsEmotion2006]. 
 This theory describes the role of emotion in `r keyw("communication")`, and the `r keyw("cultural")` symbolic function of emotion.
@@
 Among neurocognitive developmental theories,
-there is some consensus that the developmental asymmetry between `r keyw("motivational")`-emotional and inhibitory `r keyw("brain")` circuits gives rise to a "maturity gap" in middle adolescence [@croneUnderstandingAdolescencePeriod2012; @caseyBrakingAcceleratingAdolescent2011; @craccoEmotionRegulationChildhood2017].
-Particularly noteworthy is Crone and Dahl's  model of social-affective engagement and `r keyw("goal flexibility")`.
-According to this model, adolescents' cognitive engagement is dynamically responsive to
+there is some consensus that the developmental asymmetry between `r keyw("motivational")`-emotional and inhibitory `r keyw("brain")` circuits gives rise to a "maturity gap" in middle adolescence [@croneUnderstandingAdolescencePeriod2012; @@caseyBrakingAcceleratingAdolescent2011; @@craccoEmotionRegulationChildhood2017].
+According to the model of social-affective engagement and `r keyw("goal flexibility")` [@croneUnderstandingAdolescencePeriod2012],
+adolescents' cognitive engagement is dynamically responsive to
 social and motivational `r keyw("goal salience")`.
@@
 pursuit of `r keyw("peer approval")`.
-To a greater extent than related writings, Crone and Dahl's model focuses on adolescents diverging destinies;
-why some youngsters flourish while others languish.
+To a greater extent than related writings [cf. @craccoEmotionRegulationChildhood2017], this model focuses on adolescents diverging destinies;
+why some youngsters flourish while others languish [@croneUnderstandingAdolescencePeriod2012].
 This is important for understanding individual differences in development.
@@
 intra-individual drivers of emotion regulation development.
-Gross' [-@grossHandbookEmotionRegulation2013] influential process model describes the
+The influential process model [@grossHandbookEmotionRegulation2013] describes the
 phenomenon of emotion regulation, from eliciting cue to ultimate response.
-According to Gross, individuals use `r keyw("strategies")` to modulate the different stages of this process,
+This model posits that individuals use `r keyw("strategies")` to modulate the different stages of this process,
 consciously or otherwise. 
@@
 diminished well-being, and greater strain in interpersonal relationships
-[@grossIndividualDifferencesTwo2003a; @bellRelationshipsInputsOutputs2000].
+[@@grossIndividualDifferencesTwo2003a; @bellRelationshipsInputsOutputs2000].
 However, comparative studies indicate that the adaptive versus maladaptive psychosocial consequences of specific strategies appear to be partly contingent on the `r keyw("cultural context")` [see
 @bariolaChildAdolescentEmotion2011].
-Similar to Gross' theory, the "social
+Similar to the process model, the "social
 information processing" theory also describes the role of cognitive
@@
 and in what respects it complements it.-->
-
-### Shortcomings of existing theory
+<!--### Shortcomings of existing theory-->
 
@@
 Furthermore, few theories have comprehensively addressed important predictors of development in this life stage,
-and none directly guide contemporary research in the field [see @bussTheoriesEmotionalDevelopment2019; @riedigerEmotionRegulationAdolescence2014].
+and none directly guide contemporary research in the field [@bussTheoriesEmotionalDevelopment2019; @@riedigerEmotionRegulationAdolescence2014].
 Finally, existing theories vary widely in scope:
@@
 insight into undertheorized relevant phenomena.
-Two recent narrative reviews in particular complement the aforementioned theoretical literature [@coe-odessEmergentEmotionsAdolescence2019; @bariolaChildAdolescentEmotion2011].
+One recent narrative review, in exploring which factors contribute to adolescents' emotion regulation development, clearly reflected the emphasis on neurocognitive factors and socialization that is evident from the theoretical literature [@riedigerEmotionRegulationAdolescence2014].
+Other recent narrative reviews complement the aforementioned theoretical literature to a greater extent [@coe-odessEmergentEmotionsAdolescence2019; @bariolaChildAdolescentEmotion2011].
 The right panel of Figure \@ref(fig:figbaseline) visualizes constructs uniquely covered by these narrative reviews,
@@
 
-The seminal review by @bariolaChildAdolescentEmotion2011 was one of the first to stress the urgent lack of an overarching theoretical framework to guide research in this field.
-Their review addressed relevant phenomena at different levels of analysis. 
-At the individual level, relevant phenomena include temperament and biological factors, like neurocognitive development and genes.
+One seminal review discussed relevant phenomena at different levels of analysis [@bariolaChildAdolescentEmotion2011]. 
+At the individual level, such relevant phenomena include temperament and biological factors, like neurocognitive development and genes.
 At the level of proximal influences, the authors discuss socialization and modeling by parents, teachers, and peers.
 Finally, at the level of distal influences, culture and the media are discussed.
-Barriola and colleagues made several important observations about the state of the literature in this field.
-For instance, they emphasized that work on children cannot be straightforwardly extrapolated to the life stage of adolescence.
+This review addressed several important limitations of the literature in this field [@bariolaChildAdolescentEmotion2011].
+For instance, that work on children cannot be straightforwardly extrapolated to the life stage of adolescence.
 They also called for further research on parents' role beyond early childhood, and on fathers' role in emotion socialization -
 a topic that of increasing importance [see @pleckPaternalInvolvementRevised2004].
-Several recent publications have conducted research in line with these recommendations [e.g., see @vanlissaRoleFathersMothers2019;
-@vanlissaMothersFathersQuantitative2020].
-
-As the review by Barriola and colleagues is now a decade old,
-it is worth considering the more recent review by @coe-odessEmergentEmotionsAdolescence2019. 
+In line with these recommendations, several recent publications have investigated mothers' and fathers' unique roles in emotion regulation socialization from childhood to adolescence [see @vanlissaMothersFathersQuantitative2020] and throughout adolescence [see @vanlissaRoleFathersMothers2019].
+
+As the aforementioned review is now a decade old,
+it is worth considering a more recent review for additional insight [@coe-odessEmergentEmotionsAdolescence2019]. 
 This review complements prior work by offering a nuanced discussion of several topics.
@@
 positive emotionality also peaks in adolescence. -->
-The authors further describe how individual hormonal changes intensify the stress response,
+The review further describes how individual hormonal changes intensify the stress response,
 which relates to adolescents' greater susceptibility to emotion regulation difficulties.
@@
 adolescence [@meeusStudyAdolescentIdentity2011] - and to increased emotional
-understanding, and by extension, empathy [see also
-@vanlissaLongitudinalInterplayAffective2014].
-At the level of proximal influences, Coe-Odess and colleagues expand on the role of conflict with parents, which peaks in adolescence as youth become increasingly individuated.
+understanding, and by extension, empathy [see @vanlissaLongitudinalInterplayAffective2014].
+At the level of proximal influences, the review expands on the role of conflict with parents, which peaks in adolescence as youth become increasingly individuated.
 This is relevant because parent-adolescent conflict has been shown to impact both day-to-day mood swings and dispositional emotion regulation [see @vanlissaCostEmpathyParentadolescent2017].
-Coe-Odess and colleagues further detail the mechanisms by which peers exert proximal influences: Adolescents become increasingly oriented towards peers, which
+The review further describes mechanisms by which peers exert proximal influences: Adolescents become increasingly oriented toward peers, which
 increases their sensitivity to social status and norms,
@@
 An important shortcoming is that all reviews in this field have been unstructured narrative reviews, which are known to be limited in scope and biased [@littellEvidencebasedBiasedQuality2008].
-We seek to complement preceding work by using text mining to conduct a more comprehensive and objective empirical
+The current study seeks to complement preceding work by using text mining to conduct a more comprehensive and objective empirical
 literature review, and map the phenomena relevant to adolescent emotion regulation.
@@
 Note that this study is inductive (exploratory),
-as opposed to deductive (confirmatory) research, and as such does not test any hypotheses [see De Groot's work on the empirical cycle @degrootMethodologieGrondslagenVan1961].
+as opposed to deductive (confirmatory) research, and as such does not test any hypotheses [@@degrootMethodologieGrondslagenVan1961; @wagenmakersCreativityVerificationCyclePsychological2018].
 Inductive methods are suitable for the detection of phenomena,
@@
 To ensure that all such decisions are properly documented,
-we have made all code, data, and the historical record of this project publicly available in an online research repository at [masked]. 
-We used the Workflow for Open Reproducible Code in Science [WORCS, @vanlissaWORCSWorkflowOpen2020]
-to make the analyses reproducible.
-We encourage reuse of the analysis code,
-and secondary analysis of the data.
+all code, data, and the historical record of this project are available in a public research repository at [https://github.com/cjvanlissa/veni_sysrev](https://github.com/cjvanlissa/veni_sysrev). 
+This study used the Workflow for Open Reproducible Code in Science [WORCS, @vanlissaWORCSWorkflowOpen2020]
+to make all analyses reproducible.
+Reuse of the analysis code and secondary analysis of the data are encouraged.
 
@@
 
-We searched Web of Science,
-the most comprehensive database for which we had permissions to export keywords and abstracts.
+The search was conducted in Web of Science,
+the most comprehensive database accessible to the lead author with permissions to export keywords and abstracts.
 The search strategy was based on
-procedures described by Staaks [@staaksSystematicReviewSearch2019]. First, we
-constructed a reference set of 29 articles.
-Then we constructed a search string to retrieve this set.
+procedures described by Staaks [@staaksSystematicReviewSearch2019].
+First, a reference set of 29 articles was compiled.
+Then, a search string was constructed to retrieve the articles in this set.
 The search string consisted of synonyms of emotion regulation and adolescence.
@@
 Doing so resulted in 191 more hits, most of which did not meet the inclusion criteria explained below.
-We thus deemed these terms to be overly inclusive, and
-proceeded with the original search string.
+These terms thus appeared to be overly inclusive, and the original search string was used.
 ```{r readrecs}
@@
 Starting with all `r nrow(recs)` records identified through Web of Science,
-we removed duplicates based on DOI matches (n = 2) and title similarity (n = 54).
+duplicates were removed based on DOI matches (n = 2) and title similarity (n = 54).
 Rayyan QRCI [@Ouzzani2016] identified an additional 13 duplicates.
-We then screened papers based on two main criteria:
-They had to address emotion regulation or a synonymous construct, and the target population must overlap with the age range of adolescence (10-24) [as defined by @steinbergAgeOpportunityLessons2014; @sawyerAgeAdolescence2018].
+Papers were screened based on two main criteria:
+They had to address emotion regulation or a synonymous construct, and the target population must overlap with the age range of adolescence (10-24) [as defined by @steinbergAgeOpportunityLessons2014; @@sawyerAgeAdolescence2018].
 Preliminary screening was conducted in Rayyan.
-After coding `r sum(screen$rayyan == "True")+sum(screen$rayyan == "False")` papers (`r sum(screen$rayyan == "False")` excluded),
-we continued screening in ASReview [@van_de_schoot_rens_2020_3828293].
-This program uses machine learning to screen articles.
-We trained the naive Bayes algorithm by manually screening an additional `r sum(table(screen$included, screen$rayyan)[, 1])` papers (`r sum(screen$included == 1, na.rm = TRUE)-sum(screen$rayyan == "False")` excluded), until among the most recently screened 100 papers only 6 were excluded.
+After `r sum(screen$rayyan == "True")+sum(screen$rayyan == "False")` papers were screened (`r sum(screen$rayyan == "False")` excluded),
+screening continued in the free open source program ASReview [@van_de_schoot_rens_2020_3828293].
+This program uses machine learning to screen articles; the algorithm used in the present study was "naive Bayes".
+An additional `r sum(table(screen$included, screen$rayyan)[, 1])` papers were screened (`r sum(screen$included == 1, na.rm = TRUE)-sum(screen$rayyan == "False")` excluded),
+until among the most recently screened 100 papers only 6 were excluded.
 In total, `r nrow(recs_final)` papers were deemed suitable for analysis.
@@
 The corpus for this first analysis consisted of author-provided keywords.
-We extracted keywords by document,
-and applied an exclusion filter of methodological terms and similar non-substantive words.
+Keywords were extracted by document,
+and an exclusion filter of methodological terms and similar non-substantive words was applied.
 The resulting corpus consisted of `r number_docs_words[1]` documents with `r number_docs_words[2]` unique terms.
@@
 to determine whether there is, for example, a clear divide between psychiatric and developmental texts.
-To this end, we conducted topic modeling using latent dirichlet allocation [@bleiLatentDirichletAllocation2003].
-However, as no subcorpora could be identified (see [online supplement](https://github.com/cjvanlissa/veni_sysrev/blob/master/topic_models.md)), we proceed with an analysis of the whole sample.
+To this end, topic modeling using latent dirichlet allocation was conducted [@bleiLatentDirichletAllocation2003].
+However, as no subcorpora could be identified (see [online supplement](https://github.com/cjvanlissa/veni_sysrev/blob/master/topic_models.md)), the sample was analyzed in its entirety.
 
@@
 To identify what phenomena are represented in this corpus,
-we examined the terms occurring in the largest number of texts.
-To classify related terms, we used a dictionary which describes `r length(dict)` terms using `r length(unlist(dict))` regular expression queries.
+terms occurring in the largest number of texts were analyzed.
+To classify closely related terms, a dictionary was used that described `r length(dict)` terms using `r length(unlist(dict))` regular expression queries.
+This dictionary and the classification function are available for reuse.
 After dictionary encoding, the remaining number of unique terms was `r length(unique(df$word_coded))`.
 To reduce the number of terms to a more manageable set,
-we modeled word frequency using a negative binomial distribution,
-and retained those exceeding the $97.5^{th}$ percentile.
+word frequency was modeled with a negative binomial distribution.
+Terms exceeding the $97.5^{th}$ percentile were retained.
 This corresponded to terms occurring in at least `r min(as.numeric(term_freq_dist[[1]])[term_freq_dist$pruned])` documents.
@@
 
-Next, we computed a term co-occurrence matrix,
+To map the literature, a term co-occurrence matrix was computed,
 which represents how frequently words occurred within the same document (see Figure \@ref(fig:tmnetworks)).
 In total, there were `r total_cooc[1]` co-occurrence relationships.
-To aid interpretability, we again pruned small coefficients using a negative binomial distribution,
+To aid interpretability, small coefficients were again pruned using a negative binomial distribution,
 retaining co-occurrences exceeding the $97.5^{th}$ percentile.
@@
 To stimulate further reflection on the role of each construct,
-we categorized each of the remaining terms as either a putative 'Cause', 'Outcome', 'Protective factor', or 'Indicator' of emotion regulation,
-following the same procedure we used to classify phenomena discussed in the theoretical literature.
-We stress that this classification is based on our subjective reading of the literature,
-and acknowledge that many of these associations are likely to be bidirectional [e.g., emotion regulation is known to both predict and be predicted by conflict with parents, @vanlissaCostEmpathyParentadolescent2017].
+each of the remaining terms were categorized as either a putative 'Cause', 'Outcome', 'Protective factor', or 'Indicator' of emotion regulation,
+following the same procedure described in the introduction to classify phenomena discussed in the theoretical literature.
+Note that this classification is based on a subjective reading of the literature,
+and that the nature of associations between phenomena is likely to be more complex than presented here.
+For example, some of these associations are likely to be spurious, or bidirectional [e.g., emotion regulation is known to both predict and be predicted by conflict with parents, @vanlissaCostEmpathyParentadolescent2017].
 
@@
 For example, nouns help capture terms like "emotion", and adjectives help capture the "mental" in "mental health".
-We therefore applied the natural language processing technique "part-of-speech tagging" (POS-tagging) to identify each word's grammatical function within the sentence context.
-Because our analysis sought to identify phenomena,
-
-Finally, we used stemming to reduce the retained terms to their root form.
-As in Analysis 1, we tested for heterogeneity using latent dirichlet allocation - but no subcorpora were identified ([see online supplement](https://github.com/cjvanlissa/veni_sysrev/blob/master/topic_models.md)).
+The natural language processing technique "part-of-speech tagging" (POS-tagging) was used to identify each word's grammatical function within the sentence context.
+Finally, stemming was used to reduce the retained terms to their root form;
+a common procedure to ensure that terms are correctly classified regardless of their use in a sentence.
+As in Analysis 1, heterogeneity was explored using latent dirichlet allocation - but no subcorpora were identified ([see online supplement](https://github.com/cjvanlissa/veni_sysrev/blob/master/topic_models.md)).
 
@@
 When conducting text mining analysis on unstructured text data (as opposed to author key words), focusing on individual words out of context can reduce interpretability.
-For instance, our core construct "emotion regulation" is already a bigram.
-To identify more meaningful units of analysis,
-we applied the `textrank` algorithm [@wijffelsTextrankSummarizeText2019],
-an extension of Google's PageRank [@pageMethodNodeRanking2006],
-to identify relevant $n$-grams (with $n \leq 3$).
+For instance, the central construct of this review, "emotion regulation", is already a bigram.
+To obtain more meaningful units of analysis,
+the `textrank` algorithm [@wijffelsTextrankSummarizeText2019; @@pageMethodNodeRanking2006] was used to identify $n$-grams (with $n \leq 3$).
 This is sufficient to capture trigrams, like "parent-child conflict",
@@
 the resulting corpus consisted of `r number_docs_words2[1]` documents with `r number_docs_words2[2]` unique words.
-Again, we used the $97.5^{th}$ percentile of a negative binomial distribution 
+Again, the $97.5^{th}$ percentile of a negative binomial distribution was used
 as a (subjective) threshold for pruning the least common terms,
@@
 
-We constructed a term co-occurrence matrix following the procedure described in Analysis 1.
+A term co-occurrence matrix was constructed following the procedure described in Analysis 1.
 In total, there were `r total_cooc_2[1]` co-occurrence relationships.
-We again pruned small coefficients below the $97.5^{th}$ percentile of a negative binomial distribution.
+Small coefficients below the $97.5^{th}$ percentile of a negative binomial distribution were again pruned.
 This is a subjective criterion, which corresponded to terms that co-occurred in more than `r attr(cooc, "thres")` documents.
@@
 @braetEmotionRegulationChildren2014], *substance* use [cf.
-@coe-odessEmergentEmotionsAdolescence2019; @pierrehumbertStrategiesEmotionRegulation2002], and *minority status* [cf.
-@myersEthnicitySocioeconomicStatusrelated2009; @myersEthnicitySocioeconomicStatusrelated2009] are common in the corpus,
+@pierrehumbertStrategiesEmotionRegulation2002], and *minority status* [cf.
+@myersEthnicitySocioeconomicStatusrelated2009] are common in the corpus,
 but featured less prominently in the theoretical review.
@@
 The term *parenting*, which ranked highly in the keyword analysis, was displaced by *mothers* in the analysis of abstracts.
-This reflects Pleck's  [-@pleckPaternalInvolvementRevised2004] observation that parenting is most often operationalized in terms of mothering.
+This reflects the prior observation that parenting is most often operationalized in terms of mothering [@pleckPaternalInvolvementRevised2004].
 
@@
 to which most other constructs were directly linked.
-This suggests that our search successfully identified factors relevant for adolescents’ emotion regulation.
+This suggests that the search successfully identified factors relevant for adolescents’ emotion regulation.
 The remaining graph was notably sparse, with few interconnections between terms.
@@
 and used co-occurrence graphs to map associations among these phenomena.
-We conducted a systematic literature search,
-and developed procedures to analyze the author keywords (Analysis 1) and abstracts (Analysis 2) of the resulting corpus.
-
-We considered term frequency to be indicative of a phenomenon's relevance.
+A systematic literature search was conducted,
+and new procedures were developed to analyze the author keywords (Analysis 1) and abstracts (Analysis 2) of the resulting corpus.
+
+The TMSR approach considers term frequency to be indicative of a phenomenon's relevance.
 In line with this assumption, the results of both analyses
@@
 
-Our analyses of term frequency also identified several novel themes,
+The analyses of term frequency also identified several novel themes,
 which were underrepresented in the theoretical literature and prior systematic reviews.
@@
 External stressors were another important theme, reflected in terms like bullying, stress, PTSD, abuse, violence, life events, historic events (e.g., earthquakes, war), parenting stress, and divorce.
-Based on our review of the theoretical literature, this indeed appears to be an under-theorized area.
-Conceptually, external stressors most closely align with Bronfenbrenner's notion of the exosystem [@bronfenbrennerBioecologicalModelHuman2007], but to our knowledge, they have rarely been discussed as such in the theoretical literature.
-The impression that external stressors are an undertheorized theme is reinforced by the fact that studies linking adverse life events to adolescent emotion regulation tend to appeal to prior empirical work, but not to a theoretical framework [e.g., @garnefskiNegativeLifeEvents2001; @stikkelbroekAdolescentDepressionNegative2016].
+Based on a review of the theoretical literature, this indeed appears to be an under-theorized area.
+Conceptually, external stressors most closely align with the notion of the exosystem in the bioecological model [@bronfenbrennerBioecologicalModelHuman2007], but have rarely been discussed as such in the theoretical literature.
+The impression that external stressors are an undertheorized theme is reinforced by the fact that studies linking adverse life events to adolescent emotion regulation tend to appeal to prior empirical work, but not to a theoretical framework [e.g., @@garnefskiNegativeLifeEvents2001; @stikkelbroekAdolescentDepressionNegative2016].
 Finally, one emergent theme that appears to be underrepresented in existing theory is structural disadvantage.
@@
 
-Our analyses of abstracts identified three additional themes not represented in the analysis of keywords.
+The analysis of abstracts identified three additional themes not represented in the analysis of keywords.
 The first of these themes revolved around addictive behavior, with indicators *substance use* and *device use*.
@@
 and many of the frequently occurring terms were absent from the co-occurrence graphs due to a lack of connectivity.
-These observations empirically support the prior claim that this literature is somewhat fragmented [@bussTheoriesEmotionalDevelopment2019]. 
+These observations empirically support the prior claim that this literature is somewhat fragmented [@riedigerEmotionRegulationAdolescence2014] and lacks an overarching theoretical framework [@bussTheoriesEmotionalDevelopment2019].
 The sparseness of both networks explains, in part,
@@
 Such phenomena might be suitable candidates for future research.
-Indeed, several of these excluded constructs represent active ongoing areas of research, including research on *fathers* [@vanlissaRoleFathersMothers2019], *identity* [@campbellFriendsEducationIdentity2019], *friendship* and *social support* [@wangBidirectionalEffectsExpressive2020], *autonomy* [@vrolijkLongitudinalLinkagesFather2020a; @brenningPerceivedMaternalAutonomy2015], *sexual risk* [@brownDepressiveSymptomsPredictor2006], and *loneliness* [@spithovenItAllTheir2017].
+Indeed, several of these excluded constructs represent active ongoing areas of research, including research on *fathers* [@vanlissaRoleFathersMothers2019], *identity* [@campbellFriendsEducationIdentity2019], *friendship* and *social support* [@wangBidirectionalEffectsExpressive2020], *autonomy* [@vrolijkLongitudinalLinkagesFather2020a; @@brenningPerceivedMaternalAutonomy2015], *sexual risk* [@brownDepressiveSymptomsPredictor2006], and *loneliness* [@spithovenItAllTheir2017].
 One recommendation for future research might be to study such important but unembedded constructs
@@
 This suggests that the text mining method can indeed be used to map relevant themes in the literature.
-Our analysis also revealed several themes that have been underrepresented in theories of adolescent emotion regulation,
+The present analyses also revealed several themes that have been underrepresented in theories of adolescent emotion regulation,
 but nonetheless occur frequently in the empirical literature.
@@
 the next step in theory construction would involve abductive reasoning: the attribution of observations to causal explanatory principles [@haigExploratoryFactorAnalysis2005].
-As a starting point for this effort, the co-occurrence graphs derived from our analyses could be
+As a starting point for this effort, the co-occurrence graphs presented here could be
 used as templates for a nomological network:
@@
 with few connections among constructs.
-This sparse property of the networks echoes the sentiment by @bussTheoriesEmotionalDevelopment2019
-that the literature is somewhat fragmented.
-The present study takes a first step towards integrating this diffuse field
+This sparse property of the networks echoes the observation by other authors 
+that the literature is somewhat fragmented [@riedigerEmotionRegulationAdolescence2014]
+and lacks an overarching theoretical framework [@bussTheoriesEmotionalDevelopment2019].
+The present study takes a first step toward integrating this diffuse field
 by using a relatively comprehensive and objective method, compared to narrative reviews.
@@
 
+```{r countreferences, eval = FALSE}
+count_refs <- function(txt){
+  tmp <- paste0(txt, collapse = "\r\n")
+tmp <- strsplit(tmp, "\r\n")[[1]]
+tmp <- tmp[grep("References", tmp):length(tmp)]
+sum(stringr::str_count(tmp, "\\(\\d{4}.?\\)\\."))
+}
+flz <- c(
+  "C:/Users/lissa102/Zotero/storage/CVUUAUGU/Bariola et al. - 2011 - Child and adolescent emotion regulation The role .pdf",
+  "C:/Users/lissa102/Zotero/storage/GR3XBSYH/Coe-Odess et al. - 2019 - Emergent Emotions in Adolescence.pdf",
+  "C:/Users/lissa102/Zotero/storage/P6B5XMVB/Riediger_Klipker_2014_Emotion regulation in adolescence.pdf",
+  "C:/Users/lissa102/Zotero/storage/WHFYNBBN/Stifter and Augustine - 2019 - Emotion Regulation.pdf"
+)
+refs <- sapply(flz, function(x){
+  count_refs(pdftools::pdf_text(x))
+})
+flz[which.max(refs)]
+max(refs)
+```
+
 One strength of the present study is that it was more comprehensive than previous reviews of the literature in two respects [cf.
 @bariolaChildAdolescentEmotion2011; @coe-odessEmergentEmotionsAdolescence2019]:
-We conducted a systematic literature search, and we used text mining to comprehensively map the phenomena relevant to adolescents' emotion regulation.
-<!-- To this end, we applied text mining methods in a systematic review. We used For this purpose, It is also one of the first applications of inductive-->
-Using text mining offers unique advantages compared to narrative reviews [@littellEvidencebasedBiasedQuality2008],
+First, in contrast to prior literature reviews, the present study was based on a systematic literature search.
+Second, prior reviews relied on narrative synthesis of a comparatively smaller number of publications, at most 241 [@coe-odessEmergentEmotionsAdolescence2019].
+By contrast, the present study was able to map the literature more comprehensively, using text mining analysis to synthesize all 6305 identified records.
+Text mining offers unique advantages compared to narrative reviews [@littellEvidencebasedBiasedQuality2008],
 because it can cover vastly greater corpora than a sentient reader,
 and follows a somewhat more objective, transparent, and reproducible procedure.
-As such, text mining systematic reviews offer an interesting perspective that complements theory and narrative reviews.
+Both narrative and text mining reviews are initially labor-intensive.
+The key differences are that text mining systematic reviews are more scalable,
+because code can be applied to corpora of arbitrary size,
+are easily updated when new literature is published.
+Once written, analysis code can be repurposed for reviews in different areas of research with relatively little effort.
+The present study illustrates that text mining systematic reviews offer an interesting perspective of the published literature that complements theory and narrative reviews.
 Moreover, text mining systematic reviews offer an inductive approach to identify relevant phenomena in a particular area of research.
-This can serve as the first step towards formal theory construction [@borsboomTheoryConstructionMethodology2020].
-Our study was the first to implement this novel approach.
+This can serve as the first step toward formal theory construction [@borsboomTheoryConstructionMethodology2020].
+The present study was the first to implement this novel approach.
 
@@
 are not able to extract *meaning* from the literature in the way a sentient reader would, an cannot substantively interpret connections between constructs.
-This limitation is best addressed by considering the output of our text mining analysis as a starting point for further inductive thought or a more in-depth reading of a particular subset of the literature.
-Throughout this paper, we have offered our interpretation of the results -
-but we also encourage readers to use these results as impetus for independent reflection,
-and inspiration for future deductive research.
-A related limitation is that our methods do not capture the nature of the relationship between co-occurring terms.
-Instead, we manually classified terms as potential causes, outcomes, protective factors, or indicators based on domain knowledge.
+This limitation is best addressed by considering the output of a text mining analysis as a starting point for further inductive thought or a more in-depth reading of a particular subset of the literature.
+Throughout this paper, results are interpreted subjectively.
+Readers are encouraged to reflect on these results independently,
+and use them as inspiration for future deductive research.
+A related limitation is that the text mining methods used do not capture the nature of the relationship between co-occurring terms.
+Instead, terms were manually classified as potential causes, outcomes, protective factors, or indicators, based on domain knowledge.
 Efforts are currently underway to develop unsupervised algorithms capable of distilling causal links from bodies of scientific abstracts [@anExtractingCausalRelations2019].
@@
 and has increasingly come to represent paternal influence as well. -->
-Another limitation is that our analysis was limited to keywords and abstracts.
+Another limitation is that the present analyses were limited to keywords and abstracts.
 The primary obstacles to the analysis of full-text publications were limited access to articles behind paywalls,
@@
 and researchers have considerable creative license in doing so.
-We have attempted to address this limitation by explicitly mentioning important decisions in the manuscript where possible,
-and by making all analysis code and data publicly available in a fully reproducible format [based on @vanlissaWORCSWorkflowOpen2020],
+To address this limitation, subjective decisions are explicitly discussed throughout the manuscript,
+and all analysis code and data are made publicly available in a fully reproducible format [based on @vanlissaWORCSWorkflowOpen2020],
 so that others may explore alternative exploratory analysis strategies.
@@
 which speaks to the validity of this approach.
-The structure of the map further reinforced the observation of several previous authors [e.g., @bussTheoriesEmotionalDevelopment2019]
-that the empirical literature is somewhat fragmented by subject area.
-
-Importantly, our results also draw attention to several relevant phenomena that,
+The structure of the map further reinforced the observation of several previous authors
+that the empirical literature is somewhat fragmented by subject area [@riedigerEmotionRegulationAdolescence2014] and lacks an overarching theoretical framework [@bussTheoriesEmotionalDevelopment2019].
+
+Importantly, the present results also draw attention to several relevant phenomena that,
 although well-represented in the empirical literature,
@@
 This has several implications for future research.
-First, the major themes identified in our inductive analysis are relevant for the design of empirical studies.
+First, the major themes identified in these inductive analyses are relevant for the design of empirical studies.
 Even when such designs are grounded in theory,
-they might benefit from additionally considering relevant phenomena as identified in our analysis as potential confounders or contributing causes.
-Second, the phenomena that appear to exist on the fringes of the existing literature according to our analysis might be suitable candidates for further study.
-These phenomena might represent emerging themes in the literature, for example, as is the case for the role of fathers [see @pleckPaternalInvolvementRevised2004; @vanlissaMothersFathersQuantitative2020].
+they might benefit from additionally considering relevant phenomena as identified in the present study as potential confounders or contributing causes.
+Second, the phenomena that appear to exist on the fringes of the existing literature according to the present analyses might be suitable candidates for further study.
+These phenomena might represent emerging themes in the literature, for example, as is the case for the role of fathers [see @pleckPaternalInvolvementRevised2004; @@vanlissaMothersFathersQuantitative2020].
 Future research might focus on these emerging themes in order to better elucidate the nature of their association with adolescents' emotion regulation.
@@
 The first step in theory construction methodology (TCM) is to identify relevant phenomena [@borsboomTheoryConstructionMethodology2020].
-We have argued that text mining systematic reviews are a relatively comprehensive and objective method for identifying such phenomena, because they can evaluate much larger bodies of literature than sentient readers, and are not biased toward pre-existing ideas.
+Text mining systematic reviews offer a relatively comprehensive and objective method for identifying such phenomena, because they can evaluate much larger bodies of literature than sentient readers, and are not biased toward pre-existing ideas.
 The next step in formal theory construction methodology would be to describe and quantify the nature of the relationship of each phenomenon in relation to adolescent emotion regulation.

### 2021-03-26 manuscript.Rmd
make images grayscale friendly

@@
 
-keywords          : "emotion regulation, adolescence, systematic review, text mining, machine
-learning"
+keywords          : "emotion regulation, adolescence, systematic review, text mining, machine learning"
 bibliography      : ["veni_sysrev.bib"]
@@
 classoption       : "man,noextraspace"
-output            : papaja::apa6_docx
-knit              : worcs:::cite_essential
+output            : papaja::apa6_pdf
+knit              : worcs::cite_essential
 header-includes:
@@
 library(cowplot)
-run_everything <- FALSE
+run_everything <- TRUE
 notingraph <- list()
@@
 }
+cat_shapes <- c(Outcome = "square2", Indicator = "circle2", Cause = "quad2", Protective = "tri2")
+legend_shapes <- c("circle2" = 21, "square2" = 22, "quad2" = 23, "tri2" = 24)[cat_shapes]
+scale_shapes <- legend_shapes
+names(scale_shapes) <- names(cat_shapes)[match(names(legend_shapes), cat_shapes)]
 ```
@@
 
-Adolescence is a life stage ranging from pubertal onset to adult-like independence [@steinbergAgeOpportunityLessons2014; @@sawyerAgeAdolescence2018].
-A key developmental challenge in this stage is acquiring mature emotion
-regulation skills [@@croneUnderstandingAdolescencePeriod2012;
-@zimmermannEmotionRegulationEarly2014]. 
-Adolescents experience biological, cognitive, and social changes that prompt new emotional
+Adolescence is a developmentally sensitive period for emotion regulation [@zimmermannEmotionRegulationEarly2014]. 
+<!--Adolescents experience biological, cognitive, and social changes that prompt new emotional
 experiences and tax regulatory abilities [@steinbergAgeOpportunityLessons2014].
@@
 [@zimmermannEmotionRegulationEarly2014],
-resulting in more frequent and intense (negative) emotions [see @silkAdolescentsEmotionRegulation2003].
-
-Although most adolescents eventually develop mature emotion regulation abilities,
-for as many as one in five,
-adolescence marks the onset of
-life course persistent psychopathology [@leeAdolescentMentalHealth2014]
-rooted in emotion regulation difficulties
-[@aldaoEmotionregulationStrategiesPsychopathology2010;
-@@schaferEmotionRegulationStrategies2017].
+resulting in more frequent and intense (negative) emotions [see @silkAdolescentsEmotionRegulation2003].-->
+Although most adolescents successfully develop mature emotion regulation abilities,
+as many as one in five develop psychopathology [@leeAdolescentMentalHealth2014]
+with roots in emotion regulation difficulties
+[@aldaoEmotionregulationStrategiesPsychopathology2010].
 Given the prevalence of emotion regulation difficulties in adolescence,
@@
 it is important to have a comprehensive overview of the factors associated with adolescents' emotion regulation.
-Of particular interest are potential risk factors that render some youth susceptible to emotion regulation difficulties.
+<!--Of particular interest are potential risk factors that render some youth susceptible to emotion regulation difficulties.-->
 Despite the abundance of publications in this field,
-prior reviews have argued that it is difficult to obtain a comprehensive understanding of emotion regulation in adolescence [@riedigerEmotionRegulationAdolescence2014] because
-because different (sub)disciplines have approached the issue in disparate ways [@riedigerEmotionRegulationAdolescence2014],
-in the absence of consistent terminology [@bariolaChildAdolescentEmotion2011] and conceptual frameworks [@stifterEmotionRegulation2019], and a lack of unifying theory 
+it is difficult to obtain a comprehensive understanding of emotion regulation in adolescence [@riedigerEmotionRegulationAdolescence2014]:
+Different (sub)disciplines have approached the topic in disparate ways [@riedigerEmotionRegulationAdolescence2014],
+without consistent terminology [@bariolaChildAdolescentEmotion2011], conceptual frameworks [@stifterEmotionRegulation2019], or an overarching theoretical framework
 [@bussTheoriesEmotionalDevelopment2019].
-
-The fragmented state of the literature has prompted recent calls for the integration of heterogeneous research areas [@riedigerEmotionRegulationAdolescence2014] and consolidation of empirical insights into overarching theory [e.g., @bussTheoriesEmotionalDevelopment2019].
-Formal methods for theory construction state that the first step in this endeavor is to identify the relevant *empirical phenomena* [@borsboomTheoryConstructionMethodology2020],
-defined as stable and general features of the world[@@bogenSavingPhenomena1988].
-The present paper argues that systematic reviews are a suitable method for taking this first step,
-based on the assumption that phenomena considered to be stable and general will be more frequently represented in the published literature.<!-- the frequency with which phenomena occur in the literature is indicative of their relevance.-->
-Traditional narrative reviews have some limitations, however, as they been shown to be marred by small convenience samples, confirmation bias,
+This has prompted calls for the integration of knowledge across research areas [@riedigerEmotionRegulationAdolescence2014] and consolidation of empirical research into overarching theory [e.g., @bussTheoriesEmotionalDevelopment2019].
+Formal methods for theory construction state that the first step in this endeavor is to identify well-established relevant *empirical phenomena*,
+defined as stable and general features of the world [@borsboomTheoryConstructionMethodology2020].
+This study used a text mining systematic review to provide a comprehensive map of the empirical phenomena relevant to adolescent emotion regulation.
+
+Despite recent interest in theory construction method,
+few specific techniques exist for identifying relevant phenomena, aside from expert opinion [@borsboomTheoryConstructionMethodology2020].
+This paper argues that systematic reviews are a suitable method for quantifying which phenomena experts consider to be relevant.
+Traditional narrative reviews are limited, however, by small convenience samples,
+confirmation bias,
 and an undue emphasis on positive results [@littellEvidencebasedBiasedQuality2008].
@@
 the inherent "fairness" of text mining gives emerging themes a chance to come to the fore.-->
-
-The present paper uses this novel approach to map the empirical phenomena relevant to adolescent emotion regulation.
-This approach considers the frequency with which phenomena occur in the literature to be indicative of their relevance.
+This approach assumes the frequency with which phenomena recur in the literature to be indicative of their relevance.
 If it is additionally assumed that the frequency with which phenomena are studied together is indicative of the extent to which researchers believe them to be associated,
@@
 
-## Existing theoretical landscape
+## Theoretical Approaches to Emotion Regulation
 
@@
 vert$color <- cat_cols[vert$Category]
+vert$shape <- cat_shapes[vert$Category]
 vert$frame.color <- cat_cols[vert$Category]
@@
        vertex.label.cex = 0.7,
-       vertex.shape = "circle2",
+       #vertex.shape = "circle2",
        #vertex.frame.color = 'gray40',
@@
   text(-1.1, y = -1, labels = "A")
-  legend(x=-1.2, y=1.1, names(cat_cols), pch=21, col=cat_cols, pt.bg=cat_cols, pt.cex=1.6, cex=.7, bty="n", ncol=1)
+  legend(x=-1.2, y=1.1, names(cat_cols), pch=legend_shapes, col=cat_cols, pt.bg=cat_cols, pt.cex=1.4, cex=.7, bty="n", ncol=1)
   plot(g2, edge.curved = 0, layout=l2,
@@
 
-Although it has been argued that there is a paucity of theories *specific to* adolescent emotion regulation,
-many *relevant* theories are commonly invoked in empirical work [see  @bussTheoriesEmotionalDevelopment2019].
+Although it has been argued that there is a paucity of theories *specific to* adolescent emotion regulation [see @bussTheoriesEmotionalDevelopment2019],
+many *relevant* theories are commonly invoked in empirical work.
 In order to contextualize the results of the present systematic review
@@
 Others have published more detailed reviews of theories of emotional development [@bussTheoriesEmotionalDevelopment2019] and emotion regulation in adolescence [@riedigerEmotionRegulationAdolescence2014].
-In reading the theoretical literature,
-relevant phenomena were documented, along with whether these were discussed as putative causes, outcomes, indicators, or protective factors in relation to emotion regulation.
-The left panel of Figure \@ref(fig:figbaseline) visually summarizes the phenomena discussed in the theoretical literature, using a style similar to the subsequent systematic review,
-in order to contextualize the original contributions of this approach.
+The left panel of Figure \@ref(fig:figbaseline) visually summarizes the phenomena discussed in the theoretical literature,
+along with whether these were discussed as putative causes, outcomes, indicators, or protective factors in relation to emotion regulation.
+This establishes a baseline for the original contributions of the text minning analysis.
 <!-- 
@@
 but lack specificity - a shortcoming that curtails a theory's utility in generating hypotheses.
-Domain-specific theories, by comprarison, offer greater specificity.
-
-Among the oldest domain-specific theories of adolescents' emotional development is Hall's notion of "storm and stress" [see
+Domain-specific theories, by comparison, offer greater specificity.
+
+One such domain-specific theory is Hall's notion of "storm and stress" [see
 @arnettAdolescentStormStress1999].
@@
 regulation difficulties, increased `r keyw("conflict with parents")`, and `r keyw("risky behavior")`.
-This notion of diminished self-control and increased emotional reactivity still persists in modern theory, but is increasingly recast as a normative change that facilitates emotional maturation at the risk of emotional
-disturbance [@arnettAdolescentStormStress1999; @@leeAdolescentMentalHealth2014; @@croneUnderstandingAdolescencePeriod2012] 
-A potential limitation of the notion of storm and stress is that it considers emotion regulation difficulties to be part of normative development, and thus underemphasizes adolescents' diverging destinies [cf.
+In contemporary theory, this notion of diminished self-control and increased emotional reactivity is recast as a normative change that facilitates emotional maturation at the risk of emotional
+disturbance [@arnettAdolescentStormStress1999] 
+A potential limitation of conceptualizing emotion regulation difficulties as normative aspects of development is that adolescents' diverging destinies are underemphasized [cf.
 @croneUnderstandingAdolescencePeriod2012].
@@
 toward autonomous emotion regulation.
-This theory focuses on two drivers of
-development: `r keyw("social")` and `r keyw("cognitive influences")`. 
+This theory emphasizes `r keyw("social")` and `r keyw("cognitive influences")` as 
+drivers of development. 
 Social influences mainly occur
 through `r keyw("parental co-regulation")`, `r keyw("parenting behaviors")`, and parent-child
-`r keyw("attachment")`. Cognitive influences occur through the development of the `r keyw("central
+`r keyw("attachment")`.
+Cognitive influences occur through the development of the `r keyw("central
 nervous system")` (CNS), `r keyw("cognition")`, and `r keyw("self-regulation")`.
-This theory's relevance for adolescent research may be diminished by its focus on early childhood,
+<!--In terms of level of analysis, Sroufe's and Hall's theories corresponds approximately to the individual- and microsystem level of the ecological model [@bronfenbrennerBioecologicalModelHuman2007].-->
+This theory's relevance for adolescent research is somewhat diminished by its focus on early childhood,
 although there is substantial continuity in developmental influences throughout childhood and adolescence.
 For instance, there is substantial similarity between mothers' and fathers' unique roles in emotional development in childhood [@vanlissaMothersFathersQuantitative2020] and adolescence [@vanlissaRoleFathersMothers2019].
-In terms of level of analysis, the scope of Sroufe's and Hall's theories corresponds approximately to the individual and the microsystem in the ecological model [@bronfenbrennerBioecologicalModelHuman2007].
-The emphasis on socialization and `r keyw("neurocognitive development")` as two drivers of emotional development, which is evident from both theories,
+The emphasis on socialization and `r keyw("neurocognitive development")`,
+which is evident from both theories,
 is the focus of several theories with a narrower scope.
 
-Among theories focused on socialization, the tripartite model [@morrisRoleFamilyContext2007] is widely cited.
-This theory describes three pathways through which `r keyw("parents")` shape emotion regulation
-development: `r keyw("modeling")`, `r keyw("parenting practices")`, and the
+One widely cited theory of socialization is the tripartite model [@morrisRoleFamilyContext2007].
+It describes three pathways through which `r keyw("parents")` shape emotion regulation: `r keyw("modeling")`, `r keyw("parenting practices")`, and the
 emotional `r keyw("family climate")`,
 which subsumes attachment and `r keyw("marital relationship")` quality.
-This theory focuses parents, acknowledging unique contributions by `r keyw("mothers")` and `r keyw("fathers")`, but also recognizes the importance of siblings.
-Others in turn have adapted the tripartite model to describe the influence of peers [@reindlSocializationEmotionRegulation2016], thus illustrating its wider usefulness in understanding socialization.
+This theory acknowledges unique contributions by `r keyw("mothers")` and `r keyw("fathers")`, and the importance of siblings.
+Others have adapted the tripartite model to describe peer socialization [@reindlSocializationEmotionRegulation2016], thus illustrating its wider usefulness.
 A more abstract take on socialization is found in the internalization model of emotional development [@holodynskiDevelopmentEmotionsEmotion2006]. 
@@
 it does not explicitly address it.
-Among neurocognitive developmental theories,
-there is some consensus that the developmental asymmetry between `r keyw("motivational")`-emotional and inhibitory `r keyw("brain")` circuits gives rise to a "maturity gap" in middle adolescence [@croneUnderstandingAdolescencePeriod2012; @@caseyBrakingAcceleratingAdolescent2011; @@craccoEmotionRegulationChildhood2017].
+Among developmental neurocognitive theories,
+there is some consensus that the developmental asymmetry between `r keyw("motivational")`-emotional and inhibitory `r keyw("brain")` circuits gives rise to a "maturity gap" in middle adolescence [@croneUnderstandingAdolescencePeriod2012].
 According to the model of social-affective engagement and `r keyw("goal flexibility")` [@croneUnderstandingAdolescencePeriod2012],
@@
 This is important for understanding individual differences in development.
-The relevance of this theory is enhanced by its focus on adolescence,
-but is curtailed because it only tangentially addresses emotion regulation.
-Furthermore, whereas this theory addresses the role of cognitive factors and peers as drivers of development, it devotes less attention to other relevant phenomena, such as parenting [cf.
-@morrisRoleFamilyContext2007].
-Micro-scale theories as reviewed here are useful in explaining specific phenomena in detail,
+Although the relevance of this theory is enhanced by its focus on adolescence,
+it only tangentially addresses emotion regulation.
+Furthermore, whereas this theory addresses cognitive factors and peers as drivers of development, it underemphasizes other relevant phenomena, such as parenting [cf. @morrisRoleFamilyContext2007].
+Micro-scale theories like these are useful in explaining specific phenomena in detail,
 but do not provide a comprehensive understanding of adolescent's emotion regulation.
-To this end, it is important to consider these micro-scale theories in the context of a larger framework of relevant phenomena.
+To this end, it is important to consider them in the context of a larger framework of relevant phenomena.
 
@@
 diminished well-being, and greater strain in interpersonal relationships
-[@@grossIndividualDifferencesTwo2003a; @bellRelationshipsInputsOutputs2000].
+[ @bellRelationshipsInputsOutputs2000].
 However, comparative studies indicate that the adaptive versus maladaptive psychosocial consequences of specific strategies appear to be partly contingent on the `r keyw("cultural context")` [see
@@
 Furthermore, few theories have comprehensively addressed important predictors of development in this life stage,
-and none directly guide contemporary research in the field [@bussTheoriesEmotionalDevelopment2019; @@riedigerEmotionRegulationAdolescence2014].
+and none directly guide contemporary research in the field [@bussTheoriesEmotionalDevelopment2019].
 Finally, existing theories vary widely in scope:
@@
 <!--Such a theory should focus on -->
-The present study lays the groundwork for such theory development,
-by identifying theoretically relevant phenomena based on a text-mining systematic review of the literature.
-
 <!--
@@
 
-Whereas theory provides a top-down deductive understanding of adolescents' emotion regulation,
-literature reviews synthesize inductive insights emerging from the empirical literature.
-Given the noted absence of a single overarching theory [see @bussTheoriesEmotionalDevelopment2019],
-reviews are especially important,
-as they provide additional
-insight into undertheorized relevant phenomena.
+<!--Whereas theory provides a top-down deductive understanding of adolescents' emotion regulation,-->
+Literature reviews synthesize inductive insights emerging from the empirical literature.
+They can thus shed a light on undertheorized relevant phenomena.
+This is especially important given the noted absence of a single overarching theory [see @bussTheoriesEmotionalDevelopment2019].
 One recent narrative review, in exploring which factors contribute to adolescents' emotion regulation development, clearly reflected the emphasis on neurocognitive factors and socialization that is evident from the theoretical literature [@riedigerEmotionRegulationAdolescence2014].
@@
 
-## The present paper
+# The Current Study
 
@@
 Note that this study is inductive (exploratory),
-as opposed to deductive (confirmatory) research, and as such does not test any hypotheses [@@degrootMethodologieGrondslagenVan1961; @wagenmakersCreativityVerificationCyclePsychological2018].
+as opposed to deductive (confirmatory) research, and as such does not test any hypotheses [ @wagenmakersCreativityVerificationCyclePsychological2018].
 Inductive methods are suitable for the detection of phenomena,
 as they aim to generalize from observations (data) without appeal to theory [@haigExploratoryFactorAnalysis2005].
+By identifying theoretically relevant phenomena based on a text-mining systematic review of the literature, the present study lays the groundwork for future theory development.
 
@@
 Papers were screened based on two main criteria:
-They had to address emotion regulation or a synonymous construct, and the target population must overlap with the age range of adolescence (10-24) [as defined by @steinbergAgeOpportunityLessons2014; @@sawyerAgeAdolescence2018].
+They had to address emotion regulation or a synonymous construct, and the target population must overlap with the age range of adolescence (10-24) [as defined by @steinbergAgeOpportunityLessons2014].
 Preliminary screening was conducted in Rayyan.
@@
 
-# Analysis 1: Author keywords
+## Analysis 1: Author keywords
 
@@
     geom_vline(xintercept = 0, colour = "grey50", linetype = 1) + xlab("Word frequency") +
-    geom_point(data = df_plot[df_plot$faded, ], aes(colour = cat), fill = "white", shape = 21, size = 1.5) +
-    geom_point(data = df_plot[!df_plot$faded, ], aes(colour = cat, fill = cat), shape = 21, size = 1.5) +
-    scale_colour_manual(values = c(Outcome = "gray50", Indicator = "tomato", Cause = "gold", Protective = "forestgreen"), guide = NULL)+
+    geom_point(data = df_plot[df_plot$faded, ], aes(colour = cat, shape = cat), fill = "white", size = 1.5) +
+    geom_point(data = df_plot[!df_plot$faded, ], aes(colour = cat, fill = cat, shape = cat), size = 1.5) +
+    scale_colour_manual(values = c(Outcome = "gray50", Indicator = "tomato", Cause = "gold", Protective = "forestgreen"))+ #, guide = NULL
+    scale_shape_manual(values = scale_shapes)+#, guide = NULL
     scale_fill_manual(values = c(Outcome = "gray50", Indicator = "tomato", Cause = "gold", Protective = "forestgreen")) +
@@
   vert$color <- cat_cols[vert$Category]
+  vert$shape <- cat_shapes[vert$Category]
   vert$frame.color <- cat_cols[vert$Category]
@@
          vertex.label.cex = 0.5,
-         vertex.shape = "circle2",
+         #vertex.shape = "circle2",
          #vertex.frame.color = 'gray40',
@@
     )
-    legend(x=-1.1, y=1.1, names(cat_cols), pch=21, col="#777777", pt.bg=cat_cols, pt.cex=2, cex=.8, bty="n", ncol=1)
+    legend(x=-1.1, y=1.1, names(cat_cols), pch=legend_shapes, col="#777777", pt.bg=cat_cols, pt.cex=1.5, cex=.7, bty="n", ncol=1)
     plot(g, edge.curved = 0, layout=l2,
@@
 
-## Identifying common terms
+### Identifying common terms
 
@@
 
-## Mapping the literature
+### Mapping the literature
 
@@
 
-# Analysis 2: Abstract text mining
+## Analysis 2: Abstract text mining
 
@@
   geom_vline(xintercept = 0, colour = "grey50", linetype = 1) + xlab("Word frequency") +
-    geom_point(data = df_plot[df_plot$faded, ], aes(colour = cat), fill = "white", shape = 21, size = 1.5) +
-    geom_point(data = df_plot[!df_plot$faded, ], aes(colour = cat, fill = cat), shape = 21, size = 1.5) +
-    scale_colour_manual(values = c(Outcome = "gray50", Indicator = "tomato", Cause = "gold", Protective = "forestgreen"), guide = NULL)+
-    scale_fill_manual(values = c(Outcome = "gray50", Indicator = "tomato", Cause = "gold", Protective = "forestgreen")) +
+  geom_point(data = df_plot[df_plot$faded, ], aes(colour = cat, shape = cat), fill = "white", size = 1.5) +
+  geom_point(data = df_plot[!df_plot$faded, ], aes(colour = cat, fill = cat, shape = cat), size = 1.5) +
+  scale_colour_manual(values = c(Outcome = "gray50", Indicator = "tomato", Cause = "gold", Protective = "forestgreen"), guide = NULL)+#
+  scale_shape_manual(values = scale_shapes, guide = NULL)+#
+  scale_fill_manual(values = c(Outcome = "gray50", Indicator = "tomato", Cause = "gold", Protective = "forestgreen"), guide = NULL) +
   scale_x_log10() +
@@
   scale_linetype_manual(values = c("TRUE" = 3, "FALSE" = 1), guide = NULL) +
+  guides(fill = guide_legend(title = NULL,
+                               override.aes = list(linetype = c(1, 1, 1,1),
+                                                   shape = scale_shapes,
+                                                   colour = cat_cols[names(scale_shapes)]))) + 
 theme_bw() + theme(panel.grid.major.x = element_blank(),
@@
     text(-1.1, y = -1, labels = "A")
-    legend(x=-1.1, y=1.1, names(cat_cols), pch=21, col="#777777", pt.bg=cat_cols, pt.cex=2, cex=.8, bty="n", ncol=1)
+    legend(x=-1.1, y=1.1, names(cat_cols), pch=legend_shapes, col="#777777", pt.bg=cat_cols, pt.cex=1.5, cex=.7, bty="n", ncol=1)
     plot(g, edge.curved = 0, layout=l2,
@@
        vertex.label.cex = 0.5,
-       vertex.shape = "circle2",
+       #vertex.shape = "circle2",
        vertex.label.color = 'black',      # Color of node names
@@
   text(-1.1, y = -1, labels = "A")
-  legend(x=-1.1, y=1.1, names(cat_cols), pch=21, col=cat_cols, pt.bg=cat_cols, pt.cex=2, cex=.8, bty="n", ncol=1)
+  legend(x=-1.1, y=1.1, names(cat_cols), pch=legend_shapes, col=cat_cols, pt.bg=cat_cols, pt.cex=1.5, cex=.7, bty="n", ncol=1)
 
@@
        vertex.label.cex = 0.5,
-       vertex.shape = "circle2",
+       #vertex.shape = "circle2",
        #vertex.frame.color = 'gray40',
@@
        vertex.label.cex = 0.5,
-       vertex.shape = "circle2",
+       ##vertex.shape = "circle2",
        #vertex.frame.color = 'gray40',
@@
   text(-1.1, y = -1, labels = "A")
-  legend(x=-1.2, y=1.1, names(cat_cols), pch=21, col=cat_cols, pt.bg=cat_cols, pt.cex=1.6, cex=.6, bty="n", ncol=1)
+  legend(x=-1.2, y=1.1, names(cat_cols), pch=legend_shapes, col=cat_cols, pt.bg=cat_cols, pt.cex=1.4, cex=.6, bty="n", ncol=1)
 
@@
 
-## Feature engineering
+### Feature engineering
 
@@
 To obtain more meaningful units of analysis,
-the `textrank` algorithm [@wijffelsTextrankSummarizeText2019; @@pageMethodNodeRanking2006] was used to identify $n$-grams (with $n \leq 3$).
+the `textrank` algorithm [@wijffelsTextrankSummarizeText2019] was used to identify $n$-grams (with $n \leq 3$).
 This is sufficient to capture trigrams, like "parent-child conflict",
@@
 
-## Results
+# Results
 
@@
 
-## Discussion
+# Discussion
 
@@
 Conceptually, external stressors most closely align with the notion of the exosystem in the bioecological model [@bronfenbrennerBioecologicalModelHuman2007], but have rarely been discussed as such in the theoretical literature.
-The impression that external stressors are an undertheorized theme is reinforced by the fact that studies linking adverse life events to adolescent emotion regulation tend to appeal to prior empirical work, but not to a theoretical framework [e.g., @@garnefskiNegativeLifeEvents2001; @stikkelbroekAdolescentDepressionNegative2016].
+The impression that external stressors are an undertheorized theme is reinforced by the fact that studies linking adverse life events to adolescent emotion regulation tend to appeal to prior empirical work, but not to a theoretical framework [ @stikkelbroekAdolescentDepressionNegative2016].
 Finally, one emergent theme that appears to be underrepresented in existing theory is structural disadvantage.
@@
 Such phenomena might be suitable candidates for future research.
-Indeed, several of these excluded constructs represent active ongoing areas of research, including research on *fathers* [@vanlissaRoleFathersMothers2019], *identity* [@campbellFriendsEducationIdentity2019], *friendship* and *social support* [@wangBidirectionalEffectsExpressive2020], *autonomy* [@vrolijkLongitudinalLinkagesFather2020a; @@brenningPerceivedMaternalAutonomy2015], *sexual risk* [@brownDepressiveSymptomsPredictor2006], and *loneliness* [@spithovenItAllTheir2017].
+Indeed, several of these excluded constructs represent active ongoing areas of research, including research on *fathers* [@vanlissaRoleFathersMothers2019], *identity* [@campbellFriendsEducationIdentity2019], *friendship* and *social support* [@wangBidirectionalEffectsExpressive2020], *autonomy* [@vrolijkLongitudinalLinkagesFather2020a], *sexual risk* [@brownDepressiveSymptomsPredictor2006], and *loneliness* [@spithovenItAllTheir2017].
 One recommendation for future research might be to study such important but unembedded constructs
@@
 Second, the phenomena that appear to exist on the fringes of the existing literature according to the present analyses might be suitable candidates for further study.
-These phenomena might represent emerging themes in the literature, for example, as is the case for the role of fathers [see @pleckPaternalInvolvementRevised2004; @@vanlissaMothersFathersQuantitative2020].
+These phenomena might represent emerging themes in the literature, for example, as is the case for the role of fathers [see @pleckPaternalInvolvementRevised2004].
 Future research might focus on these emerging themes in order to better elucidate the nature of their association with adolescents' emotion regulation.
@@
 and sensitize empirical researchers to potential confounders in research on adolescents' emotion regulation.
+
+# Conclusion
+
+<!-- Here is what I typically tell authors regarding what I need in the conclusion. 
+Insert this level 1 heading before it: Conclusion Begin by (briefly) reminding the reader of the topic, the research gap, and how you addressed it.
+Then go to what you found and its importance.
+Be sure to state your findings very clearly.
+The implications can focus on many aspects of the study, such as the practice implications (briefly).
+But, for us, the implications also should include a focus on the understanding of adolescence/early adulthood/emerging adulthood and the contribution to that research.
+The bulk of the paragraph, though, should be focused on the key findings.
+Do try to have it be just one strong paragraph.-->
+
+# Acknowledgements
+<!-- This is what I need:
+
+As our journal is multidisciplinary and some fields are now moving toward encouraging preregistration, and given that we seek to have authors distinguish between confirmatory and exploratory analyses, we now encourage authors to note whether parts of their study were preregistered.
+If it is not, then simply ignore.
+If it is, then please provide the relevant link (URL, DOI or other permanent path to a public, open access repository) and note what was registered (the study design, hypotheses, and target analyses, and so forth).
+
+I will need a statement regarding conflicts of interests.
+It should have this heading "Conflicts of Interest" and, below it, a sentence reporting your potential conflicts.
+If you have none, please write a full sentence to this effect: "The authors report no conflict of interests." If you do have conflicts of interests, please report them.
+For guidance, see the journal's instructions to authors that are posted online.
+The only part that the journal follows that is different from the online instructions is that we require that the statements be presented in the acknowledgment page rather than in the title page.
+
+I also need a note on funding. [But only if there was funding.]
+
+Just so we are clear, the acknowledgment page should have these items addressed:
+Acknowledgment (if you have a general one, otherwise do not use this heading).
+Conflicts of Interest
+Preregistration (only if relevant)
+Funding  (only if relevant)-->
 

### 2021-03-26 baseline.R

@@ -61,6 +61,8 @@ vert$Category <- categ$category[match(vert$name, categ$name)]
 cat_cols <- c(Outcome = "gray50", Indicator = "tomato", Cause = "gold", Protective = "forestgreen")
 cat_cols <- c(Outcome = "gray50", Indicator = "tomato", Cause = "gold", Protective = "olivedrab2")
 vert$color <- cat_cols[vert$Category]
+cat_shapes <- c(Outcome = "square2", Indicator = "circle2", Cause = "tri2", Protective = "quad2")
+vert$shape <- cat_shapes[vert$Category]
 vert$frame.color <- cat_cols[vert$Category]
 #min_size <- (strwidth(vert$name[max(nchar(vert$name))]) + strwidth("oo")) * 100
 vert$size <- scales::rescale(log(vert$size), c(4, 12))
@@ -93,8 +95,11 @@ if(any(!vert$name %in% categ$name)){
 vert$Category <- categ$category[match(vert$name, categ$name)]
 vert$faded <- vert$name %in% df$cat[df$source == "theory"]
 cat_cols <- c(Outcome = "gray50", Indicator = "tomato", Cause = "gold", Protective = "olivedrab2")
+cat_shapes <- c(Outcome = "square2", Indicator = "circle2", Cause = "tri2", Protective = "quad2")
+legend_shapes <- c("circle2" = 21, "square2" = 22, "quad2" = 23, "tri2" = 24)[cat_shapes]
 vert$color <- cat_cols[vert$Category]
 vert$frame.color <- cat_cols[vert$Category]
+vert$shape <- cat_shapes[vert$Category]
 # cat_cols <- c(Outcome = "#E5E5E5", Indicator = "#FFC9AD", Cause = "#FFFF66", Protective = "#E6FF6D")
 vert$color[vert$faded] <- "#FFFFFF"#cat_cols[vert$Category[vert$faded]]
 
@@ -122,17 +127,17 @@ p <- quote({
   plot(g1, edge.curved = 0, layout=l1,
        vertex.label.family = "sans",
        vertex.label.cex = 0.8,
-       vertex.shape = "circle2",
+       #vertex.shape = "circle2",
        #vertex.frame.color = 'gray40',
        vertex.label.color = 'black',      # Color of node names
        vertex.label.font = 1,         # Font of node names
        vertex.frame.width = 2
   )
[…]

### 2021-03-26 circle2.R

@@ -27,3 +27,123 @@ mycircle <- function(coords, v=NULL, params) {
 add.vertex.shape("circle2", clip=igraph.shape.noclip,
                  plot=mycircle, parameters=list(vertex.frame.color=1,
                                                 vertex.frame.width=1))
+
+mycircle <- function(coords, v=NULL, params) {
+  vertex.color <- params("vertex", "color")
+  if (length(vertex.color) != 1 && !is.null(v)) {
+    vertex.color <- vertex.color[v]
+  }
+  vertex.size  <- 1/200 * params("vertex", "size")
+  if (length(vertex.size) != 1 && !is.null(v)) {
+    vertex.size <- vertex.size[v]
+  }
+  vertex.frame.color <- params("vertex", "frame.color")
+  if (length(vertex.frame.color) != 1 && !is.null(v)) {
+    vertex.frame.color <- vertex.frame.color[v]
+  }
+  vertex.frame.width <- params("vertex", "frame.width")
+  if (length(vertex.frame.width) != 1 && !is.null(v)) {
+    vertex.frame.width <- vertex.frame.width[v]
+  }
+  
+  mapply(coords[,1], coords[,2], vertex.color, vertex.frame.color,
+         vertex.size, vertex.frame.width,
+         FUN=function(x, y, bg, fg, size, lwd) {
+           symbols(x=x, y=y, bg=bg, fg=fg, lwd=lwd,
+                   circles=size, add=TRUE, inches=FALSE)
+         })
+}
+
+add.vertex.shape("circle2", clip=igraph.shape.noclip,
+                 plot=mycircle, parameters=list(vertex.frame.color=1,
+                                                vertex.frame.width=1))
+
+mysquare <- function(coords, v=NULL, params) {
+  vertex.color <- params("vertex", "color")
+  if (length(vertex.color) != 1 && !is.null(v)) {
+    vertex.color <- vertex.color[v]
+  }
+  vertex.size  <- 1/200 * params("vertex", "size")
+  if (length(vertex.size) != 1 && !is.null(v)) {
+    vertex.size <- vertex.size[v]
+  }
+  vertex.frame.color <- params("vertex", "frame.color")
+  if (length(vertex.frame.color) != 1 && !is.null(v)) {
+    vertex.frame.color <- vertex.frame.color[v]
+  }
+  vertex.frame.width <- params("vertex", "frame.width")
[…]

### 2021-03-30 manuscript.Rmd
restructure discussion

@@
     institution   : "Utrecht University faculty of Social and Behavioral Sciences, department of Methodology & Statistics"
-
-authornote: |
-  This work is supported by a NWO Veni grant (NWO
-  grant number VI.Veni.191G.090). Acknowledgement: Lukas Beinhauer contributed
-  substantially to the screening of articles. Conflicts of Interest: None.
 
@@
 To combine the strength of both, it would be beneficial to bridge these levels of analysis.
-In sum, there is a need for more integrative theory formation,
-in order to provide a unified framework that could guide future empirical work.<!--[see @riedigerEmotionRegulationAdolescence2014].
+There is a need for integrative theory formation,
+which could provide a unified framework to guide future empirical work.<!--[see @riedigerEmotionRegulationAdolescence2014].
 Inductive analysis of the empirical literature may constitute a first step to this end.-->
@@
 
-## Prior narrative reviews
+## Prior Narrative Reviews
 
 <!--Whereas theory provides a top-down deductive understanding of adolescents' emotion regulation,-->
-Literature reviews synthesize inductive insights emerging from the empirical literature.
-They can thus shed a light on undertheorized relevant phenomena.
+Literature reviews can shed a light on undertheorized relevant phenomena by
+synthesizing inductive insights emerging from the empirical literature.
 This is especially important given the noted absence of a single overarching theory [see @bussTheoriesEmotionalDevelopment2019].
@@
 
-The present study used a text mining systematic review (TMSR)
+The present study used a novel method, the text mining systematic review (TMSR),
 to identify relevant phenomena in the literature on adolescent emotion regulation,
 and used co-occurrence graphs to map associations among these phenomena.
-A systematic literature search was conducted,
-and new procedures were developed to analyze the author keywords (Analysis 1) and abstracts (Analysis 2) of the resulting corpus.
-
-The TMSR approach considers term frequency to be indicative of a phenomenon's relevance.
+This approach considers term frequency to be indicative of a phenomenon's relevance.
 In line with this assumption, the results of both analyses
-reflected some of the constructs commonly accepted as relevant in theoretical literature and empirical reviews - particularly those pertaining to neurodevelopment and socialization.
-Furthermore, some of the most frequently occurring terms were mental health-related outcomes that involve emotion regulation difficulties [see @aldaoEmotionregulationStrategiesPsychopathology2010].
-This validates the notion that adolescent emotion regulation is implicated in a range of mental health problems [@leeAdolescentMentalHealth2014],
-and underlines the importance of this area of research.
-
-The analyses of term frequency also identified several novel themes,
-which were underrepresented in the theoretical literature and prior systematic reviews.
+reflected some of the phenomena broadly considered to be relevant in theoretical literature and empirical reviews - particularly those pertaining to neurodevelopment and socialization.
+Other frequently occurring phenomena were mental health-related outcomes that involve emotion regulation difficulties [see @aldaoEmotionregulationStrategiesPsychopathology2010].
+This result is consistent with the notion that adolescent emotion regulation is implicated in a range of mental health problems [@leeAdolescentMentalHealth2014],
+and underlines the importance of research in this area.
+
+The term frequency analyses also identified several novel themes of relevant phenomena that are underrepresented in the theoretical literature and prior systematic reviews.
 One such theme pertains to developmental disorders, such as ADHD/CD and autism.
-This theme recurred in both analyses, although its constituent terms were ranked more highly in the analysis of author keywords as compared to abstracts.
+This theme recurred in both analyses, although its constituent terms were ranked more highly in the analysis of keywords as compared to abstracts.
 Another theme revolved around adolescents' physical health (sic), which was also reflected in terms like sleep, sports, and disability status.
-There thus appears to be substantial empirical work linking emotion regulation and physical health, although this association is underrepresented in theory.
+This finding indicates that there is substantial empirical work on emotion regulation and physical health, although physical health is underrepresented in theory.
 As with the theme of developmental disorders, terms related to physical health ranked more highly in the keyword analysis than in the abstract analysis.
-This might indicate that a broader vocabulary was used to describe physical health in the abstracts.
+This might indicate that a broader vocabulary was used to describe physical health in the abstracts; a diverse vocabulary increases the difficulty of correctly classifying terms belonging to a theme.
 External stressors were another important theme, reflected in terms like bullying, stress, PTSD, abuse, violence, life events, historic events (e.g., earthquakes, war), parenting stress, and divorce.
-Based on a review of the theoretical literature, this indeed appears to be an under-theorized area.
-Conceptually, external stressors most closely align with the notion of the exosystem in the bioecological model [@bronfenbrennerBioecologicalModelHuman2007], but have rarely been discussed as such in the theoretical literature.
-The impression that external stressors are an undertheorized theme is reinforced by the fact that studies linking adverse life events to adolescent emotion regulation tend to appeal to prior empirical work, but not to a theoretical framework [ @stikkelbroekAdolescentDepressionNegative2016].
+Based on the review of the theoretical literature, this indeed appears to be an under-theorized area.
+Conceptually, external stressors most closely align with the notion of the exosystem in the bioecological model [@bronfenbrennerBioecologicalModelHuman2007], but they have rarely been discussed as such in the theoretical literature.
+The impression that external stressors are an undertheorized theme is reinforced by the fact that studies linking adverse life events to adolescent emotion regulation tend to reference mostly prior empirical work, but not a theoretical framework [e.g., @stikkelbroekAdolescentDepressionNegative2016].
 Finally, one emergent theme that appears to be underrepresented in existing theory is structural disadvantage.
@@
 The analysis of abstracts identified three additional themes not represented in the analysis of keywords.
-The first of these themes revolved around addictive behavior, with indicators *substance use* and *device use*.
+The first of these themes revolved around addictive behavior (e.g., substance use and device use).
 The second theme pertained to identity and moral development, two topics with a common root in theory [@lapsleyMoralIdentityDevelopmental2015].
-This theme is also reflected by the terms *values* and *personality*. 
-Finally, sexual development emerged as a theme. Aside from the high-ranking construct (biological) *sex*, this theme was reflected in the terms *puberty*, *sexual diversity*, and *romantic*.
+This theme is also reflected by the terms values and personality. 
+Finally, sexual development emerged as a theme. Aside from the high-ranking construct (biological) sex, this theme was reflected in the terms puberty, sexual diversity, and romantic relationships.
 These insights illustrate how inductive reviews can identify under-theorized areas,
@@
 and with a central axis of emotion regulation and its mental health-related outcomes in the abstract analysis.
-The emergence of a "central axis" of dysregulation and mental health-related outcomes
+The emergence of a central axis of dysregulation and mental health-related outcomes
 again suggest that these phenomena are consistently studied together.
@@
 In line with this interpretation, exploratory analyses indicated that 99% of terms occurred only once in the abstract analysis, compared to only 78% in the keyword analysis.
-Despite the sparser network, there was substantial consistency between the terms retained in both networks.
+Despite the sparser network, there was substantial correspondence between the terms retained in both networks.
 This supports the validity of the findings,
-suggesting that automatic keyword extraction from abstracts can identify relevant constructs,
+and suggests that automatic keyword extraction from abstracts can identify relevant constructs,
 and may be a suitable alternative to author-provided keywords.
 
-Both analyses revealed relatively few interconnections between phenomena,
-and many of the frequently occurring terms were absent from the co-occurrence graphs due to a lack of connectivity.
-These observations empirically support the prior claim that this literature is somewhat fragmented [@riedigerEmotionRegulationAdolescence2014] and lacks an overarching theoretical framework [@bussTheoriesEmotionalDevelopment2019].
-The sparseness of both networks explains, in part,
-why some of the most prevalent terms based on term document frequency
-are absent from the co-occurrence graph (see Figure \@ref(fig:varimps)).
-This does not mean that these terms represent unimportant phenomena.
-Rather, it suggests that they are not well-integrated in the broader literature on adolescents' emotion regulation.
-Such phenomena might be suitable candidates for future research.
-Indeed, several of these excluded constructs represent active ongoing areas of research, including research on *fathers* [@vanlissaRoleFathersMothers2019], *identity* [@campbellFriendsEducationIdentity2019], *friendship* and *social support* [@wangBidirectionalEffectsExpressive2020], *autonomy* [@vrolijkLongitudinalLinkagesFather2020a], *sexual risk* [@brownDepressiveSymptomsPredictor2006], and *loneliness* [@spithovenItAllTheir2017].
-One recommendation for future research might be to study such important but unembedded constructs
-in conjunction with other more well-established constructs,
-as such an approach might help fill gaps in existing knowledge.
+Both co-occurrence networks revealed relatively few interconnections between phenomena,
+and several frequently occurring terms were pruned due to a lack of connectivity.
+This empirically supports the prior (anecdotal) claim that this literature is somewhat fragmented [@riedigerEmotionRegulationAdolescence2014]. 
+The absence of terms from the co-occurrence networks does not mean that these phenomena are unimportant, but rather, that they are not well-integrated in the broader literature on adolescents' emotion regulation.
+Several of these unembedded phenomena represent emerging themes in the literature; as is the case for research on fathers [see @pleckPaternalInvolvementRevised2004], identity [@campbellFriendsEducationIdentity2019], friendship and social support [@wangBidirectionalEffectsExpressive2020], autonomy [@vrolijkLongitudinalLinkagesFather2020a], sexual risk [@brownDepressiveSymptomsPredictor2006], and loneliness [@spithovenItAllTheir2017].
 
@@
 
-The results of this inductive approach echoed many of the constructs considered
-relevant in the theoretical literature.
-This suggests that the text mining method can indeed be used to map relevant themes in the literature.
-The present analyses also revealed several themes that have been underrepresented in theories of adolescent emotion regulation,
-but nonetheless occur frequently in the empirical literature.
-These themes include developmental disorders, physical health, external stressors, structural disadvantage, addictive behavior, identity and moral development, and sexual development.
-
-It is important to identify such under-theorized areas of the literature because
-researchers typically rely on theoretical foundations when planning a study.
-By providing an overview of phenomena relevant to adolescents' emotion regulation based on an inductive analysis of the empirical literature,
-the present study offers guidance regarding potentially relevant topics to consider.
+This results of this text mining systematic review reflected several familiar phenomena that are well-represented in existing theory.
+This has implications for the validity of the method, as it suggests that text mining can indeed be used to map relevant themes in the literature.
+The results also revealed relevant phenomena that,
+although well-represented in the empirical literature,
+are under-emphasized in narrative reviews and theory - phenomena such as developmental disorders, physical health, external stressors, structural disadvantage, substance use, identity and moral development, and sexual development.
+This has implication for future empirical research:
+In designing a study, researchers typically rely on theoretical foundations - and under-theorized phenomena are at risk of being overlooked.
+The present study offers guidance regarding additional relevant phenomena to consider as potential confounders or contributing causes.
+
+The results further revealed that several relevant phenomena were relatively unembedded.
+This has implications for future research, as the absence of these phenomena from the co-occurrence networks, and the sparsity of connections in the network, suggest potential knowledge gaps.
+Future research might study these unembedded phenomena in conjunction with other more well-established constructs,
+in order to bridge gaps in existing knowledge and bring these phenomena into the mainstream literature.
+
+Additional implications arise from the structure of the co-occurrence graphs.
+Both analyses revealed close ties between emotion regulation and mental health-related outcomes, which is consistent with the role of emotion regulation in the etiology of mental health problems [see @leeAdolescentMentalHealth2014].
+This has implications for the societal relevance of research in this area.
+Furthermore, both analyses revealed that most constructs were
+directly tied to emotion regulation and mental health,
+with few connections among constructs.
+These sparse networks validate prior anecdotal claims
+that the literature in this field is somewhat fragmented [@riedigerEmotionRegulationAdolescence2014]
+and lacks an overarching theoretical framework [@bussTheoriesEmotionalDevelopment2019].
+An important implication of this finding is that, indeed, work remains to be done to integrate this diffuse field, and to generate an overarching theory of adolescent emotion regulation.
+The first step in theory construction methodology (TCM) is to identify relevant phenomena [@borsboomTheoryConstructionMethodology2020].
+The present study takes that first step
+by mapping the relevant phenomena in this area of research using a relatively comprehensive and objective method.<!--The relevant phenomena identified in the present study might thus serve as a starting point for future theory development.-->
+
 An important direction for future research would be to formalize these inductive insights into a new overarching theory of adolescent emotion regulation.
-Going beyond the inductive identification of relevant phenomena,
-the next step in theory construction would involve abductive reasoning: the attribution of observations to causal explanatory principles [@haigExploratoryFactorAnalysis2005].
+According to formal theory construction methodology, the next step would be to describe and quantify the nature of the relationship of each phenomenon in relation to adolescent emotion regulation.
+This involves abductive reasoning: the attribution of observations to causal explanatory principles [@haigExploratoryFactorAnalysis2005].
 As a starting point for this effort, the co-occurrence graphs presented here could be
@@
 relevant phenomena [see @alaviAligningTheoryMethodology2018].
-
-Additional insight can be gleaned from the structure of the co-occurrence graphs.
-First, both analyses revealed close ties between emotion regulation and mental health-related outcomes.
-This is consistent with emotion regulation's putative implication in the etiology of various mental health problems [see @leeAdolescentMentalHealth2014].
-It further emphasizes the societal relevance of this field of research.
-Both analyses further revealed that most constructs were
-directly tied to emotion regulation and mental health,
-with few connections among constructs.
-This sparse property of the networks echoes the observation by other authors 
-that the literature is somewhat fragmented [@riedigerEmotionRegulationAdolescence2014]
-and lacks an overarching theoretical framework [@bussTheoriesEmotionalDevelopment2019].
-The present study takes a first step toward integrating this diffuse field
-by using a relatively comprehensive and objective method, compared to narrative reviews.
-An important future direction for research might be to jointly investigate disconnected constructs, as the lack of connections in the graph indicates a potential knowledge vacuum.
 
@@
 ```
+
+## Stengths and Limitations
 
@@
 
-It should be noted that this method has disadvantages as well.
-The key limitation of the present study is that the text mining techniques used here
-are not able to extract *meaning* from the literature in the way a sentient reader would, an cannot substantively interpret connections between constructs.
-This limitation is best addressed by considering the output of a text mining analysis as a starting point for further inductive thought or a more in-depth reading of a particular subset of the literature.
-Throughout this paper, results are interpreted subjectively.
-Readers are encouraged to reflect on these results independently,
-and use them as inspiration for future deductive research.
+It should be noted that the present study has limitations as well.
+The key disadvantage of the method used is that these text mining techniques
+are not able to extract *meaning* from the literature in the way a sentient reader would.
+This limitation is best addressed by considering the results as a starting point for inductive reasoning, further deductive research, or a more detailed narrative review on specific sub-topics.
 A related limitation is that the text mining methods used do not capture the nature of the relationship between co-occurring terms.
 Instead, terms were manually classified as potential causes, outcomes, protective factors, or indicators, based on domain knowledge.
-Efforts are currently underway to develop unsupervised algorithms capable of distilling causal links from bodies of scientific abstracts [@anExtractingCausalRelations2019].
+Efforts are currently underway to develop unsupervised algorithms capable of distilling implied causal links from scientific abstracts [@anExtractingCausalRelations2019].
 Future research might substantially advance theory formation by applying such methods to the present corpus.
@@
 
-To conclude, this paper set out to map the factors associated with adolescents' emotion regulation, based on a systematic review of the literature, and text mining analysis of author keywords and abstracts.
-This map covered familiar phenomena that are well-represented in existing theory,
-such as socialization and neurocognitive factors,
-which speaks to the validity of this approach.
-The structure of the map further reinforced the observation of several previous authors
-that the empirical literature is somewhat fragmented by subject area [@riedigerEmotionRegulationAdolescence2014] and lacks an overarching theoretical framework [@bussTheoriesEmotionalDevelopment2019].
-
-Importantly, the present results also draw attention to several relevant phenomena that,
-although well-represented in the empirical literature,
-are under-emphasized in narrative reviews and theory - such as developmental disorders, physical health, external stressors, structural disadvantage, substance use, identity and moral development, and sexual development.
-This has several implications for future research.
-First, the major themes identified in these inductive analyses are relevant for the design of empirical studies.
-Even when such designs are grounded in theory,
-they might benefit from additionally considering relevant phenomena as identified in the present study as potential confounders or contributing causes.
-Second, the phenomena that appear to exist on the fringes of the existing literature according to the present analyses might be suitable candidates for further study.
-These phenomena might represent emerging themes in the literature, for example, as is the case for the role of fathers [see @pleckPaternalInvolvementRevised2004].
-Future research might focus on these emerging themes in order to better elucidate the nature of their association with adolescents' emotion regulation.
-Moreover, studying these fringe phenomena in conjunction with other more well-established constructs could help embed these important but loosely connected phenomena into the mainstream literature and bridge gaps in existing knowledge.
-
-Finally, several authors have commented on the lack of an overarching theory tailored specifically to adolescent emotion regulation.
-The first step in theory construction methodology (TCM) is to identify relevant phenomena [@borsboomTheoryConstructionMethodology2020].
-Text mining systematic reviews offer a relatively comprehensive and objective method for identifying such phenomena, because they can evaluate much larger bodies of literature than sentient readers, and are not biased toward pre-existing ideas.
-The next step in formal theory construction methodology would be to describe and quantify the nature of the relationship of each phenomenon in relation to adolescent emotion regulation.
-The phenomena identified in the present study might thus serve as a starting point for future theory development,
-and sensitize empirical researchers to potential confounders in research on adolescents' emotion regulation.
-
 # Conclusion
 
-<!-- Here is what I typically tell authors regarding what I need in the conclusion. 
-Insert this level 1 heading before it: Conclusion Begin by (briefly) reminding the reader of the topic, the research gap, and how you addressed it.
-Then go to what you found and its importance.
-Be sure to state your findings very clearly.
-The implications can focus on many aspects of the study, such as the practice implications (briefly).
-But, for us, the implications also should include a focus on the understanding of adolescence/early adulthood/emerging adulthood and the contribution to that research.
-The bulk of the paragraph, though, should be focused on the key findings.
-Do try to have it be just one strong paragraph.-->
+<!-- Begin by (briefly) reminding the reader of the topic
+this paper set out to map the factors associated with adolescents' emotion regulation, based on a systematic review of the literature, and text mining analysis of author keywords and abstracts.
+-->
+There has been a call for the integration of the empirical literature on adolescent emotion regulation.
+<!--, the research gap, and how you addressed it.-->
+This paper used a text mining systematic review to identify phenomena relevant to adolescents' emotion regulation based on term frequency,
+and to map potential associations between phenomena based on term co-occurrence.
+<!--Then go to what you found and its importance.  Be sure to state your findings very clearly. -->
+The findings reflected several themes commonly featured in theory and narrative reviews,
+such associalization and neurocognitive factors,
+which suggests that this is a valid method for identifying relevant phenomena.
+Importantly, the findings also revealed undertheorized themes,
+such as developmental disorders, physical health, external stressors,
+structural disadvantage, substance use, identity and moral development, and
+sexual development.
+
+<!-- The implications can focus on many aspects of the study, such as the practice implications (briefly).-->
+
+<!--the implications also should include a focus on the understanding of adolescence/early adulthood/emerging adulthood and the contribution to that research.-->
+Several of these themes
+
+The findings illustrate how text mining systematic
+  reviews, a novel approach, may complement narrative reviews. Future
+  theoretical work might integrate these undertheorized themes into
+  an overarching framework, and empirical research might consider them as
+  promising areas for future research, or as potential confounders in research
+  on adolescents' emotion regulation.
 
 # Acknowledgements
-<!-- This is what I need:
-
-As our journal is multidisciplinary and some fields are now moving toward encouraging preregistration, and given that we seek to have authors distinguish between confirmatory and exploratory analyses, we now encourage authors to note whether parts of their study were preregistered.
-If it is not, then simply ignore.
-If it is, then please provide the relevant link (URL, DOI or other permanent path to a public, open access repository) and note what was registered (the study design, hypotheses, and target analyses, and so forth).
-
-I will need a statement regarding conflicts of interests.
-It should have this heading "Conflicts of Interest" and, below it, a sentence reporting your potential conflicts.
-If you have none, please write a full sentence to this effect: "The authors report no conflict of interests." If you do have conflicts of interests, please report them.
-For guidance, see the journal's instructions to authors that are posted online.
-The only part that the journal follows that is different from the online instructions is that we require that the statements be presented in the acknowledgment page rather than in the title page.
-
-I also need a note on funding. [But only if there was funding.]
-
-Just so we are clear, the acknowledgment page should have these items addressed:
-Acknowledgment (if you have a general one, otherwise do not use this heading).
-Conflicts of Interest
-Preregistration (only if relevant)
-Funding  (only if relevant)-->
-
-On behalf of all authors, the corresponding author states that there is no conflict of interest
+
+## Acknowledgement
+
+Lukas Beinhauer contributed substantially to the screening of articles.
+
+## Conflicts of Interest
+
+The author reports no conflict of interests.
+
+## Preregistration
+
+This study was wholly exploratory. The analyses were not preregistered.
+A full historical record of the analyses is available at https://github.com/cjvanlissa/veni_sysrev.
+
+## Funding
+
+This work is supported by a NWO Veni grant (NWO grant number VI.Veni.191G.090),
+awarded to the author.
+
 <!--

### 2021-03-30 baseline.R

@@ -58,10 +58,12 @@ if(any(!vert$name %in% categ$name)){
 } 
 vert$Category <- categ$category[match(vert$name, categ$name)]
 
+cat_shapes <- c(Outcome = "square2", Indicator = "circle2", Cause = "quad2", Protective = "tri2")
+legend_shapes <- c("circle2" = 21, "square2" = 22, "quad2" = 23, "tri2" = 24)[cat_shapes]
+
 cat_cols <- c(Outcome = "gray50", Indicator = "tomato", Cause = "gold", Protective = "forestgreen")
 cat_cols <- c(Outcome = "gray50", Indicator = "tomato", Cause = "gold", Protective = "olivedrab2")
 vert$color <- cat_cols[vert$Category]
-cat_shapes <- c(Outcome = "square2", Indicator = "circle2", Cause = "tri2", Protective = "quad2")
 vert$shape <- cat_shapes[vert$Category]
 vert$frame.color <- cat_cols[vert$Category]
 #min_size <- (strwidth(vert$name[max(nchar(vert$name))]) + strwidth("oo")) * 100
@@ -95,8 +97,6 @@ if(any(!vert$name %in% categ$name)){
 vert$Category <- categ$category[match(vert$name, categ$name)]
 vert$faded <- vert$name %in% df$cat[df$source == "theory"]
 cat_cols <- c(Outcome = "gray50", Indicator = "tomato", Cause = "gold", Protective = "olivedrab2")
-cat_shapes <- c(Outcome = "square2", Indicator = "circle2", Cause = "tri2", Protective = "quad2")
-legend_shapes <- c("circle2" = 21, "square2" = 22, "quad2" = 23, "tri2" = 24)[cat_shapes]
 vert$color <- cat_cols[vert$Category]
 vert$frame.color <- cat_cols[vert$Category]
 vert$shape <- cat_shapes[vert$Category]

### 2021-04-06 manuscript.Rmd
finalize revisions

@@
 ---
-title             : "Mapping Correlates of Adolescent Emotion Dysregulation: A Text-mining Systematic Review"
+title             : "Mapping Phenomena Relevant to Adolescent Emotion Dysregulation: A Text-mining Systematic Review"
 shorttitle        : "ADOLESCENT EMOTION REGULATION"
@@
 and downstream cost to society,
-it is important to have a comprehensive overview of the factors associated with adolescents' emotion regulation.
+it is important to have a comprehensive overview of the phenomena associated with adolescents' emotion regulation.
 <!--Of particular interest are potential risk factors that render some youth susceptible to emotion regulation difficulties.-->
@@
 defined as stable and general features of the world [@borsboomTheoryConstructionMethodology2020].
-This study used a text mining systematic review to provide a comprehensive map of the empirical phenomena relevant to adolescent emotion regulation.
-
-Despite recent interest in theory construction method,
-few specific techniques exist for identifying relevant phenomena, aside from expert opinion [@borsboomTheoryConstructionMethodology2020].
-This paper argues that systematic reviews are a suitable method for quantifying which phenomena experts consider to be relevant.
+The current study used a text mining systematic review to provide a comprehensive map of the empirical phenomena relevant to adolescent emotion regulation.
+
+Currently, few instruments exist for the identification of relevant phenomena; instead, theorists typically rely on expert opinion [@borsboomTheoryConstructionMethodology2020].
+This paper argues that systematic reviews are a suitable and relatively more objective method for phenomena detection.
 Traditional narrative reviews are limited, however, by small convenience samples,
@@
 and an undue emphasis on positive results [@littellEvidencebasedBiasedQuality2008].
-This paper aims to overcome these limitations by adopting a novel method:
+These limitations are overcome by a novel method:
 the text mining systematic review (TMSR).
 Relative to narrative reviews, text mining can cover arbitrarily greater corpora,
-and gleans insights from the literature by means of a more transparent and reproducible process.
+and gleans insights from the literature by means of a relatively more transparent, objective, and reproducible process.
 <!--Where sentient readers tend to structure their reading of the literature around established ideas [@littellEvidencebasedBiasedQuality2008],
@@
 This approach assumes the frequency with which phenomena recur in the literature to be indicative of their relevance.
-If it is additionally assumed that the frequency with which phenomena are studied together is indicative of the extent to which researchers believe them to be associated,
+If it is additionally assumed that the frequency with which phenomena are studied together is indicative of the extent to which they are thought to be associated,
 then the co-occurrence of phenomena within publications can be interpreted as a rudimentary nomological network: a mapping of relationships between theoretically relevant phenomena [see @alaviAligningTheoryMethodology2018].
-This network can serve as a starting point for the formulation of a proto-theory,
+Such a network can serve as a starting point for the formulation of a proto-theory,
 which would additionally involve abductive reasoning: specifying putative mechanisms to explain associations between the phenomena [@borsboomTheoryConstructionMethodology2020].
-By mapping the phenomena relevant to adolescent emotion regulation,
-the present work thus lays the groundwork for future theory development.
+Text mining systematic reviews constitute an inductive and exploratory approach:
+Their aim is phenomena detection based on generalization from observations (data) without appeal to theory [@haigExploratoryFactorAnalysis2005].
+By identifying and mapping the phenomena relevant to adolescent emotion regulation,
+such an inductive approach lays the groundwork for future theory development.
 
@@
   )
-  text(-1.1, y = -1, labels = "A")
+  text(-1.1, y = -1, labels = "a")
   legend(x=-1.2, y=1.1, names(cat_cols), pch=legend_shapes, col=cat_cols, pt.bg=cat_cols, pt.cex=1.4, cex=.7, bty="n", ncol=1)
@@
   )
-  text(-1.1, y = -1, labels = "B")
+  text(-1.1, y = -1, labels = "b")
 })
@@
 
-```{r figbaseline, warning=FALSE, eval = TRUE, results='asis', out.width = "100%", fig.cap="Phenomena relevant to adolescents' emotion regulation according to theory (A) and narrative reviews (B; transparent circles indicate constructs also present in the theory)."}
+```{r figbaseline, warning=FALSE, eval = TRUE, results='asis', out.width = "100%", fig.cap="Phenomena relevant to adolescents' emotion regulation according to theory (a) and narrative reviews (b; transparent nodes indicate constructs also present in the theory)."}
 knitr::include_graphics("baseline_network.png") 
 ```
-```{r allnetworks, warning=FALSE, eval = FALSE, results='asis', out.width = "100%", fig.cap="Correlates of emotion regulation difficulties according to theory (A), narrative reviews (B), and term co-occurrence in author keywords (C) and abstracts (D).
-Size of lines and circles represents frequency.
+```{r allnetworks, warning=FALSE, eval = FALSE, results='asis', out.width = "100%", fig.cap="Correlates of emotion regulation difficulties according to theory (a), narrative reviews (b), and term co-occurrence in author keywords (c) and abstracts (d).
+Size of lines and nodes represents frequency.
 Dashed lines represent links not involving dysregulation.
-Transparent circles indicate constructs also represented in the theory (panel A)."}
+Transparent nodes indicate constructs also represented in the theory."}
 
@@
 Although it has been argued that there is a paucity of theories *specific to* adolescent emotion regulation [see @bussTheoriesEmotionalDevelopment2019],
-many *relevant* theories are commonly invoked in empirical work.
-In order to contextualize the results of the present systematic review
-and assess to what extent the identified phenomena through text mining mirror or complement existing theory,
-a brief review of the existing theoretical landscape is provided.
-Others have published more detailed reviews of theories of emotional development [@bussTheoriesEmotionalDevelopment2019] and emotion regulation in adolescence [@riedigerEmotionRegulationAdolescence2014].
-The left panel of Figure \@ref(fig:figbaseline) visually summarizes the phenomena discussed in the theoretical literature,
+several *relevant* theories are commonly invoked in empirical work.
+A brief review of the existing theoretical landscape is provided here
+to contextualize the present systematic review
+and assess to what extent phenomena identified through text mining mirror or complement existing theory.
+Others have published detailed reviews of theories of emotional development [@bussTheoriesEmotionalDevelopment2019] and of empirical research on adolescent emotion regulation [@riedigerEmotionRegulationAdolescence2014].
+The left panel of Figure \@ref(fig:figbaseline) visually summarizes the phenomena discussed in the theoretical literature reviewed below,
 along with whether these were discussed as putative causes, outcomes, indicators, or protective factors in relation to emotion regulation.
@@
 The most immediate source of contextual influences is the microsystem,
-composed of people close to the individual.
-Other influences stem from the macrosystem, consisting of `r keyw("political")` and `r keyw("economic")` influences,
-and the exosystem, consisting of `r keyw("cultural")` norms and `r keyw("values")`.
+composed of primary caregivers and other close ties.
+Other environmental influences originate in the macrosystem - including `r keyw("political")` and `r keyw("economic")` influences - and the exosystem,
+consisting of `r keyw("cultural")` norms and `r keyw("values")`.
 The transactional model [@sameroffUnifiedTheoryDevelopment2010] is compatible with the bioecological model,
@@
 The transactional model distinguishes between proximal influences, which roughly correspond to the microsystem in the bioecological model, and distal influences, which derive from
-structural factors indirectly shaping development, like `r keyw("socio-economic status")`,
+structural and environmental factors indirectly shaping development, like `r keyw("socio-economic status")`,
 `r keyw("schools")`, and the `r keyw("community")` (macro- and exosystem).
-With increasing age, distal influences gain ground on proximal influences.
+With increasing age, these distal influences gain ground on proximal influences.
 These two theories have a broader scope than most.
@@
 
-One such domain-specific theory is Hall's notion of "storm and stress" [see
+One such domain-specific theory is Hall's notion of "storm and stress" in adolescence [see
 @arnettAdolescentStormStress1999].
@@
 regulation difficulties, increased `r keyw("conflict with parents")`, and `r keyw("risky behavior")`.
-In contemporary theory, this notion of diminished self-control and increased emotional reactivity is recast as a normative change that facilitates emotional maturation at the risk of emotional
-disturbance [@arnettAdolescentStormStress1999] 
-A potential limitation of conceptualizing emotion regulation difficulties as normative aspects of development is that adolescents' diverging destinies are underemphasized [cf.
+Contemporary theories recast this notion of diminished self-control and increased emotional reactivity as a normative change that facilitates emotional maturation at the risk of emotional
+disturbance [@arnettAdolescentStormStress1999].
+A potential limitation of conceptualizing emotion regulation difficulties as normative is that this underemphasizes heterogeneity in developmental trajectories [cf.
 @croneUnderstandingAdolescencePeriod2012].
@@
 
-One theory of normative emotional development [@sroufeEmotionalDevelopmentOrganization1995] focuses on developmental influences to a greater extent.
-This theory posits that, as children grow older,
+One theory of normative emotional development focuses on developmental influences to a greater extent [@sroufeEmotionalDevelopmentOrganization1995].
+It posits that, as children grow older,
 their increasing `r keyw("self-regulatory")` abilities
@@
 This theory emphasizes `r keyw("social")` and `r keyw("cognitive influences")` as 
-drivers of development. 
+drivers of emotion regulation development.
 Social influences mainly occur
@@
 <!--In terms of level of analysis, Sroufe's and Hall's theories corresponds approximately to the individual- and microsystem level of the ecological model [@bronfenbrennerBioecologicalModelHuman2007].-->
-This theory's relevance for adolescent research is somewhat diminished by its focus on early childhood,
-although there is substantial continuity in developmental influences throughout childhood and adolescence.
-For instance, there is substantial similarity between mothers' and fathers' unique roles in emotional development in childhood [@vanlissaMothersFathersQuantitative2020] and adolescence [@vanlissaRoleFathersMothers2019].
+This theory's relevance for adolescent research is somewhat diminished by its focus on early childhood.
+However, research indicates that there is some continuity in developmental influences throughout childhood and adolescence; for instance, mothers' and fathers' unique roles in emotional development are similar in childhood and adolescence [see @vanlissaMothersFathersQuantitative2020; @vanlissaRoleFathersMothers2019].
 The emphasis on socialization and `r keyw("neurocognitive development")`,
@@
 A more abstract take on socialization is found in the internalization model of emotional development [@holodynskiDevelopmentEmotionsEmotion2006]. 
-This theory describes the role of emotion in `r keyw("communication")`, and the `r keyw("cultural")` symbolic function of emotion.
+This theory describes the socialization of the role of emotion in `r keyw("communication")`, and the `r keyw("cultural")` symbolic function of emotion.
 
@@
 challenging situations in a way that facilitates--> develop mature regulatory
-abilities, but also places them at risk of impulsivity in
+abilities, but also places them at risk of greater impulsivity - for example, in
 pursuit of `r keyw("peer approval")`.
@@
 regulation.-->
-Theories of the phenomenon of emotion regulation offer insight into
+Theories of emotion regulation offer further insight into
 intra-individual drivers of emotion regulation development.
-The influential process model [@grossHandbookEmotionRegulation2013] describes the
-phenomenon of emotion regulation, from eliciting cue to ultimate response.
-This model posits that individuals use `r keyw("strategies")` to modulate the different stages of this process,
+The influential process model describes emotion regulation throughout the progression from eliciting cue to ultimate response [@grossHandbookEmotionRegulation2013].
+This model posits that individuals use `r keyw("strategies")` to modulate this process at different stages,
 consciously or otherwise. 
-Individuals who engage in maladaptive emotion regulation strategies tend to experience more negative emotions,
+Maladaptive emotion regulation strategies tend to result in more negative emotions,
 diminished well-being, and greater strain in interpersonal relationships
@@
 [@lemeriseIntegratedModelEmotion2000].
-One shortcoming of these theories for understanding adolescents' emotion regulation 
+One shortcoming of these theories for understanding adolescent emotion regulation 
 is the lack of a developmental component.
@@
 
-Despite the abundance of theory *relevant* to emotion regulation in adolescence,
+Despite the abundance of theory relevant to emotion regulation in adolescence,
 the literature has several limitations.
 First, few theories have explicitly addressed adolescence.
-This life stage differs qualitatively from both childhood and adulthood [@bariolaChildAdolescentEmotion2011].
-It is therefore questionable whether theories focused on different age groups can be generalized to adolescents.
+As this life stage differs qualitatively from both childhood and adulthood,
+it is questionable whether theories focused on different age groups can be generalized to adolescents [@bariolaChildAdolescentEmotion2011].
 <!--Relatedly, many relevant theories lack an explicit developmental component, which renders them and thus lack a well-substantiated
@@
 but lack a broader perspective.
-Broad theories can be used to frame a wide variety of research,
+Broad theories can be used to frame a wide range of research,
 and specific theories are more suitable for deductive hypothesis generation.
@@
 <!--Whereas theory provides a top-down deductive understanding of adolescents' emotion regulation,-->
-Literature reviews can shed a light on undertheorized relevant phenomena by
+Literature reviews can shed light on undertheorized relevant phenomena by
 synthesizing inductive insights emerging from the empirical literature.
-This is especially important given the noted absence of a single overarching theory [see @bussTheoriesEmotionalDevelopment2019].
+This is especially important given the noted absence of overarching theory [see @bussTheoriesEmotionalDevelopment2019].
 One recent narrative review, in exploring which factors contribute to adolescents' emotion regulation development, clearly reflected the emphasis on neurocognitive factors and socialization that is evident from the theoretical literature [@riedigerEmotionRegulationAdolescence2014].
-Other recent narrative reviews complement the aforementioned theoretical literature to a greater extent [@coe-odessEmergentEmotionsAdolescence2019; @bariolaChildAdolescentEmotion2011].
-The right panel of Figure \@ref(fig:figbaseline) visualizes constructs uniquely covered by these narrative reviews,
-relative to the preceding theoretical literature.
-This illustrates in what respects these reviews reflect existing theory,
+Other recent narrative reviews complement the theoretical literature to a greater extent by addressing relevant but undertheorized phenomena [@coe-odessEmergentEmotionsAdolescence2019; @bariolaChildAdolescentEmotion2011].
+The right panel of Figure \@ref(fig:figbaseline) illustrates in what respects these narrative reviews reflect existing theory,
 and in what respects they complement it.
@@
 Finally, at the level of distal influences, culture and the media are discussed.
-This review addressed several important limitations of the literature in this field [@bariolaChildAdolescentEmotion2011].
-For instance, that work on children cannot be straightforwardly extrapolated to the life stage of adolescence.
-They also called for further research on parents' role beyond early childhood, and on fathers' role in emotion socialization -
-a topic that of increasing importance [see @pleckPaternalInvolvementRevised2004].
+This review also called for research on emotion regulation beyond early childhood and into adolescence, and on fathers' unique contributions -
+a topic receiving increasing interest [see @pleckPaternalInvolvementRevised2004].
 In line with these recommendations, several recent publications have investigated mothers' and fathers' unique roles in emotion regulation socialization from childhood to adolescence [see @vanlissaMothersFathersQuantitative2020] and throughout adolescence [see @vanlissaRoleFathersMothers2019].
@@
 it is worth considering a more recent review for additional insight [@coe-odessEmergentEmotionsAdolescence2019]. 
-This review complements prior work by offering a nuanced discussion of several topics.
+This review complements offers a nuanced discussion of several additional topics.
 At the individual level, this includes the implications of physiological changes,
@@
 discussed in other publications, the authors discuss how cognitive development and increased capacity
-for abstract thought relate to identity formation - a key challenge in
-adolescence [@meeusStudyAdolescentIdentity2011] - and to increased emotional
-understanding, and by extension, empathy [see @vanlissaLongitudinalInterplayAffective2014].
+for abstract thought relate to identity formation and increased emotional
+understanding.
+These themes relate to two key challenges in adolescence, namely identity [@meeusStudyAdolescentIdentity2011] and empathy development [@vanlissaLongitudinalInterplayAffective2014].
 At the level of proximal influences, the review expands on the role of conflict with parents, which peaks in adolescence as youth become increasingly individuated.
 This is relevant because parent-adolescent conflict has been shown to impact both day-to-day mood swings and dispositional emotion regulation [see @vanlissaCostEmpathyParentadolescent2017].
-The review further describes mechanisms by which peers exert proximal influences: Adolescents become increasingly oriented toward peers, which
+The review further describes how adolescents become increasingly oriented toward peers, which
 increases their sensitivity to social status and norms,
-along with concomitant increases in peer pressure and risk taking.
-This review devotes limited attention to distal influences.
+and prompts concomitant increases in peer pressure and risk taking.
+The review devotes limited attention to distal influences.
 
@@
 This illustrates the general principle that reviews of the empirical literature can contribute inductive insight into relevant phenomena underrepresented in theory.
-An important shortcoming is that all reviews in this field have been unstructured narrative reviews, which are known to be limited in scope and biased [@littellEvidencebasedBiasedQuality2008].
-The current study seeks to complement preceding work by using text mining to conduct a more comprehensive and objective empirical
-literature review, and map the phenomena relevant to adolescent emotion regulation.
+An important shortcoming is that all reviews in this field have been unstructured narrative reviews; a method that is often limited in scope and susceptible to bias [@littellEvidencebasedBiasedQuality2008].
 
@@
 
-The present paper set out to map the phenomena relevant to adolescent emotion regulation
-using a text mining systematic review (TMSR) of the literature.
-This approach considers the frequency with which a phenomenon is covered in the literature to be indicative of its relevance,
-and the frequency with which phenomena are investigated together within publications to be indicative of a relationship between these constructs.
-The expected outcomes consist of term frequency metrics,
-which can be rank ordered to identify the most relevant phenomena,
-and term co-occurrence metrics.
-These metrics can be jointly visualized as a network graph,
+The empirical literature on adolescent emotion regulation is somewhat fragmented accross subdisciplines, and lacks an overarching theoretical framework.
+The current study seeks to integrate this body of work by means of a comprehensive text mining systematic review (TMSR).
+This is an inductive study, and as such,
+does not test hypotheses [@wagenmakersCreativityVerificationCyclePsychological2018].
+The aims of the study are to identify the most relevant phenomena in the body of literature,
+based on the frequency with which phenomena are reported,
+and to map potential relationships between phenomena, based on their co-occurrence within studies.
+The resulting map of relevant phenomena helps integrate the empirical literature.
+Moreover, as identifying relevant empirical phenomena is the first step in theory construction methodology,
+this study lays the groundwork for future theory development.
+<!--The distinction between inductive and deductive research has recently been recast as a "creativity-verification" cycle [@wagenmakersCreativityVerificationCyclePsychological2018].-->
+
+# Methods
+
+This text mining systematic review considered the frequency with which a phenomenon is covered in the literature, or *term frequency*, to be indicative of its relevance.
+Term frequency can be rank ordered to identify the most relevant phenomena.
+Furthermore, the frequency with which phenomena are investigated together within publications, or *term co-occurrence*, is considered to be indicative of a putative relationship between them.
+These two metrics can be jointly visualized as a network graph,
 thereby "mapping" phenomena relevant to adolescent emotion regulation.
-Note that this study is inductive (exploratory),
-as opposed to deductive (confirmatory) research, and as such does not test any hypotheses [ @wagenmakersCreativityVerificationCyclePsychological2018].
-Inductive methods are suitable for the detection of phenomena,
-as they aim to generalize from observations (data) without appeal to theory [@haigExploratoryFactorAnalysis2005].
-By identifying theoretically relevant phenomena based on a text-mining systematic review of the literature, the present study lays the groundwork for future theory development.
-
-<!--The distinction between inductive and deductive research has recently been recast as a "creativity-verification" cycle [@wagenmakersCreativityVerificationCyclePsychological2018].-->
-
-# Methods
-
-As the purpose of inductive research is to inform hypothesis generation,
-this approach affords the researcher with substantial creativity [@wagenmakersCreativityVerificationCyclePsychological2018].
+
+Inductive research affords the researcher with substantial creativity [@wagenmakersCreativityVerificationCyclePsychological2018].
 This means that subjective decisions are made throughout the analysis process.
@@
 all code, data, and the historical record of this project are available in a public research repository at [https://github.com/cjvanlissa/veni_sysrev](https://github.com/cjvanlissa/veni_sysrev). 
-This study used the Workflow for Open Reproducible Code in Science [WORCS, @vanlissaWORCSWorkflowOpen2020]
-to make all analyses reproducible.
+The Workflow for Open Reproducible Code in Science was used to make all analyses reproducible [WORCS, @vanlissaWORCSWorkflowOpen2020].
 Reuse of the analysis code and secondary analysis of the data are encouraged.
@@
 Papers were screened based on two main criteria:
-They had to address emotion regulation or a synonymous construct, and the target population must overlap with the age range of adolescence (10-24) [as defined by @steinbergAgeOpportunityLessons2014].
+They had to address emotion regulation or a synonymous construct, and the target population must overlap with the age range of adolescence [10-24, as defined by @steinbergAgeOpportunityLessons2014].
 Preliminary screening was conducted in Rayyan.
@@
 ```{r varimps, warning=FALSE, message = FALSE, eval = TRUE, results='asis', out.width = "100%", fig.cap="Frequency of terms in Analysis 1 and 2.
-Transparent circles are constructs represented in theory (Figure 1), dotted lines are constructs absent from the co-occurrence graph."}
+Transparent nodes are constructs represented in theory (Figure 1), dotted lines are constructs absent from the co-occurrence graph."}
 knitr::include_graphics("varimps.png") 
@@
 
-To stimulate further reflection on the role of each construct,
-each of the remaining terms were categorized as either a putative 'Cause', 'Outcome', 'Protective factor', or 'Indicator' of emotion regulation,
-following the same procedure described in the introduction to classify phenomena discussed in the theoretical literature.
+Following the procedure described in the introduction to classify phenomena discussed in the theoretical literature,
+each of the remaining terms were categorized as either a putative cause, outcome, protective factor, or indicator of emotion regulation.
 Note that this classification is based on a subjective reading of the literature,
@@
 For example, some of these associations are likely to be spurious, or bidirectional [e.g., emotion regulation is known to both predict and be predicted by conflict with parents, @vanlissaCostEmpathyParentadolescent2017].
-
-```{r tmnetworks, warning=FALSE, eval = TRUE, results='asis', out.width = "100%", fig.cap="Map of phenomena relevant to adolescents' emotion regulation based on term co-occurrence in author keywords (A) and abstracts (B).
-Size of lines and circles represents frequency.
+This classification is merely intended as a starting point for further reflection on the potential role of each construct.
+
+```{r tmnetworks, warning=FALSE, eval = TRUE, results='asis', out.width = "100%", fig.cap="Map of phenomena relevant to adolescents' emotion regulation based on term co-occurrence in author keywords (a) and abstracts (b).
+Size of lines and nodes represents frequency.
 Dashed lines represent links not involving emotion regulation.
-Transparent circles indicate constructs also represented in the theoretical review."}
+Transparent nodes indicate constructs also represented in the theoretical review."}
 
@@
 Two layouts are presented to aid interpretation.
-Size of lines and circles represents frequency.
+Size of lines and nodes represents frequency.
 Dashed lines represent links not involving dysregulation.
-Transparent circles indicate constructs also represented in the theory (cf Figure 1)."}
+Transparent nodes indicate constructs also represented in the theory (cf Figure 1)."}
 #knitr::include_graphics("study1_network1.svg")
@@
                    panel.grid.minor.x = element_blank(), axis.title.y = element_blank(),
-                   legend.position = c(.70,.125),
+                   legend.position = c(.825,.1125),
                    legend.title = element_blank(),
@@
     )
-    text(-1.1, y = -1, labels = "A")
-    legend(x=-1.1, y=1.1, names(cat_cols), pch=legend_shapes, col="#777777", pt.bg=cat_cols, pt.cex=1.5, cex=.7, bty="n", ncol=1)
+    text(-1.1, y = -1, labels = "a")
+    legend(x=-1.1, y=1.1, names(cat_cols), pch=legend_shapes, col="#777777", pt.bg=cat_cols, pt.cex=1.4, cex=.7, bty="n", ncol=1)
     plot(g, edge.curved = 0, layout=l2,
@@
     )
-    text(-1.1, y = -1, labels = "B")
+    text(-1.1, y = -1, labels = "b")
   })
@@
   )
-  text(-1.1, y = -1, labels = "A")
-  legend(x=-1.1, y=1.1, names(cat_cols), pch=legend_shapes, col=cat_cols, pt.bg=cat_cols, pt.cex=1.5, cex=.7, bty="n", ncol=1)
+  text(-1.1, y = -1, labels = "a")
+  legend(x=-1.1, y=1.1, names(cat_cols), pch=legend_shapes, col=cat_cols, pt.bg=cat_cols, pt.cex=1.4, cex=.7, bty="n", ncol=1)
 
@@
   )
-  text(-1.1, y = -1, labels = "B")
+  text(-1.1, y = -1, labels = "b")
   plot(s1g, edge.curved = 0,
@@
   )
-  text(-1.1, y = -1, labels = "C")
+  text(-1.1, y = -1, labels = "c")
   plot(s2g, edge.curved = 0,
@@
   )
-  text(-1.1, y = -1, labels = "D")
+  text(-1.1, y = -1, labels = "d")
 })
@@
   )
-  text(-1.1, y = -1, labels = "A")
+  text(-1.1, y = -1, labels = "a")
   legend(x=-1.2, y=1.1, names(cat_cols), pch=legend_shapes, col=cat_cols, pt.bg=cat_cols, pt.cex=1.4, cex=.6, bty="n", ncol=1)
@@
   )
-  text(-1.1, y = -1, labels = "B")
+  text(-1.1, y = -1, labels = "b")
 
@@
 Again, the $97.5^{th}$ percentile of a negative binomial distribution was used
-as a (subjective) threshold for pruning the least common terms,
+as a subjective threshold for pruning the least common terms,
 which corresponded to terms occurring in more than `r max(as.numeric(term_freq[[1]][!term_freq$pruned]))` documents.
@@
 Two layouts are presented to aid interpretation.
-Size of lines and circles represents frequency.
+Size of lines and nodes represents frequency.
 Dashed lines represent links not involving dysregulation.
-Transparent circles indicate constructs also represented in the theory (cf Figure 1)."}
+Transparent nodes indicate constructs also represented in the theory (cf Figure 1)."}
 #knitr::include_graphics("study2_network1.svg")
@@
 
-The present study used a novel method, the text mining systematic review (TMSR),
-to identify relevant phenomena in the literature on adolescent emotion regulation,
-and used co-occurrence graphs to map associations among these phenomena.
-This approach considers term frequency to be indicative of a phenomenon's relevance.
-In line with this assumption, the results of both analyses
-reflected some of the phenomena broadly considered to be relevant in theoretical literature and empirical reviews - particularly those pertaining to neurodevelopment and socialization.
+<!-- start more broadly and give readers a good sense of the issues that need to be addressed in this area -->
+<!-- highlight the complexities/questions involved and GENERALLY how you addressed them (such as in one sentence at the end of the paragraph). -->
+
+<!-- Assume, for example, that readers have skipped much of your study and jumped straight to the discussion section.
+In the sentences after that, present what you found and the importance of your contribution (and limitations and so forth).
+I apologize for this journal style edit.-->
+Although a substantial body of research has investigated emotion regulation in adolescence,
+this literature is somewhat fragmented across subdisciplines and lacks a unifying theoretical framework.
+The first step toward constructing such a unifying framework is identifying relevant empirical phenomena in this field.
+The present study set out to identify such relevant phenomena and map associations among them using a novel method: the text mining systematic review (TMSR).
+
+The results of both analyses
+reflected some of the phenomena broadly considered to be relevant in prior theoretical literature and empirical reviews - particularly phenomena related to neurodevelopment and socialization.
 Other frequently occurring phenomena were mental health-related outcomes that involve emotion regulation difficulties [see @aldaoEmotionregulationStrategiesPsychopathology2010].
-This result is consistent with the notion that adolescent emotion regulation is implicated in a range of mental health problems [@leeAdolescentMentalHealth2014],
+This finding is consistent with emotion regulation's implication in a range of mental health problems [@leeAdolescentMentalHealth2014],
 and underlines the importance of research in this area.
 
-The term frequency analyses also identified several novel themes of relevant phenomena that are underrepresented in the theoretical literature and prior systematic reviews.
+The analyses also identified several novel themes of relevant phenomena that are underrepresented in the theoretical literature and prior systematic reviews.
 One such theme pertains to developmental disorders, such as ADHD/CD and autism.
@@
 The first of these themes revolved around addictive behavior (e.g., substance use and device use).
-The second theme pertained to identity and moral development, two topics with a common root in theory [@lapsleyMoralIdentityDevelopmental2015].
+The second theme pertained to identity and moral development, two central topics in adolescent research [@meeusStudyAdolescentIdentity2011] with a common root in theory [@lapsleyMoralIdentityDevelopmental2015].
 This theme is also reflected by the terms values and personality. 
-Finally, sexual development emerged as a theme. Aside from the high-ranking construct (biological) sex, this theme was reflected in the terms puberty, sexual diversity, and romantic relationships.
-These insights illustrate how inductive reviews can identify under-theorized areas,
-thereby complementing existing theory and narrative reviews.
-
-With regard to term co-occurrence, most phenomena were directly linked with emotion regulation in the keyword analysis,
+A final emerging theme related to sexual development, as indicated by the terms (biological) sex, puberty, sexual diversity, and romantic relationships.
+Taken together, these insights illustrate how inductive reviews can identify themes that are underemphasized in existing theory and narrative reviews.
+
+The co-occurrence analyses revealed that most phenomena were directly linked with emotion regulation in the keyword analysis,
 and with a central axis of emotion regulation and its mental health-related outcomes in the abstract analysis.
-The emergence of a central axis of dysregulation and mental health-related outcomes
+The emergence of a central axis of emotion regulation and mental health-related outcomes
 again suggest that these phenomena are consistently studied together.
-This makes sense, given the central role of emotion dyregulation in the etiology of diverse mental health problems [@leeAdolescentMentalHealth2014].
+This makes sense, given the central role of emotion regulation in the etiology of mental health problems [@leeAdolescentMentalHealth2014].
 
@@
 and several frequently occurring terms were pruned due to a lack of connectivity.
-This empirically supports the prior (anecdotal) claim that this literature is somewhat fragmented [@riedigerEmotionRegulationAdolescence2014]. 
+This provides empirical supports for the prior anecdotal claim that this literature is somewhat fragmented [@riedigerEmotionRegulationAdolescence2014]. 
 The absence of terms from the co-occurrence networks does not mean that these phenomena are unimportant, but rather, that they are not well-integrated in the broader literature on adolescents' emotion regulation.
@@
 This has implications for the validity of the method, as it suggests that text mining can indeed be used to map relevant themes in the literature.
-The results also revealed relevant phenomena that,
-although well-represented in the empirical literature,
-are under-emphasized in narrative reviews and theory - phenomena such as developmental disorders, physical health, external stressors, structural disadvantage, substance use, identity and moral development, and sexual development.
+The results also revealed relevant phenomena that
+are under-emphasized in narrative reviews and theory, such as developmental disorders, physical health, external stressors, structural disadvantage, substance use, and identity-, moral-, and sexual development.
 This has implication for future empirical research:
@@
 
-The results further revealed that several relevant phenomena were relatively unembedded.
-This has implications for future research, as the absence of these phenomena from the co-occurrence networks, and the sparsity of connections in the network, suggest potential knowledge gaps.
-Future research might study these unembedded phenomena in conjunction with other more well-established constructs,
+The results further revealed that several relevant phenomena were relatively unembedded:
+These scored highly on term frequency,
+but were sparsely connected to other terms in the co-occurrence networks, or pruned from the graph altogether.
+This finding has implications for future research, as unembedded terms indicate potential knowledge gaps.
+Future research might study these phenomena in conjunction with other more well-established constructs
 in order to bridge gaps in existing knowledge and bring these phenomena into the mainstream literature.
@@
 An important direction for future research would be to formalize these inductive insights into a new overarching theory of adolescent emotion regulation.
-According to formal theory construction methodology, the next step would be to describe and quantify the nature of the relationship of each phenomenon in relation to adolescent emotion regulation.
+This would require describing and quantifying the nature of the relationship of each phenomenon in relation to adolescent emotion regulation [@borsboomTheoryConstructionMethodology2020].
 This involves abductive reasoning: the attribution of observations to causal explanatory principles [@haigExploratoryFactorAnalysis2005].
@@
 because code can be applied to corpora of arbitrary size,
-are easily updated when new literature is published.
+and are easily updated when new literature is published.
 Once written, analysis code can be repurposed for reviews in different areas of research with relatively little effort.
-The present study illustrates that text mining systematic reviews offer an interesting perspective of the published literature that complements theory and narrative reviews.
-Moreover, text mining systematic reviews offer an inductive approach to identify relevant phenomena in a particular area of research.
+The present study illustrates that text mining systematic reviews extract relevant information from the published literature in a way that complements theory and narrative reviews.
+Moreover, text mining systematic reviews appear to be a suitable method for identifying relevant phenomena in a particular area of research.
 This can serve as the first step toward formal theory construction [@borsboomTheoryConstructionMethodology2020].
-The present study was the first to implement this novel approach.
+The present study was the first to develop and implement this novel approach.
 
 It should be noted that the present study has limitations as well.
-The key disadvantage of the method used is that these text mining techniques
+The key disadvantage of the method used is that these inductive text mining techniques
 are not able to extract *meaning* from the literature in the way a sentient reader would.
-This limitation is best addressed by considering the results as a starting point for inductive reasoning, further deductive research, or a more detailed narrative review on specific sub-topics.
+This limitation is best addressed by considering the results as a starting point for further abductive reasoning and theory formation, deductive empirical research, or a narrative review focused on the emergent relevant phenomena.
 A related limitation is that the text mining methods used do not capture the nature of the relationship between co-occurring terms.
 Instead, terms were manually classified as potential causes, outcomes, protective factors, or indicators, based on domain knowledge.
-Efforts are currently underway to develop unsupervised algorithms capable of distilling implied causal links from scientific abstracts [@anExtractingCausalRelations2019].
+Efforts are underway to develop unsupervised algorithms capable of distilling implied causal links from scientific abstracts [@anExtractingCausalRelations2019].
 Future research might substantially advance theory formation by applying such methods to the present corpus.
@@
 Meta-scientific analyses of the published literature will likely become increasingly important -->
-Comprehensive access to scientific publications is essential to all meta-scientific research, including classic systematic reviews and meta-analyses (e.g., to avoid bias in summary effect sizes).
+Comprehensive access to scientific publications is essential to all meta-scientific research, including narrative reviews and meta-analyses (e.g., to avoid bias in summary effect sizes).
 For text mining approaches in particular, the availability of large data sets is crucial.
@@
 it becomes harder for researchers to remain informed, thus necessitating meta-scientific research.-->
-An increased adoption of open access publishing,
+Increased adoption of open access publishing,
 and the development of a unified API for article retrieval across publishing outlets,
@@
 One final limitation is that several subjective decisions were made throughout the analysis process.
-This limitation is inherent to inductive studies, however [e.g., @wagenmakersCreativityVerificationCyclePsychological2018]:
-There are infinite possible ways to conduct exploratory analysis,
-and researchers have considerable creative license in doing so.
+This creative license is inherent to inductive studies, however [@wagenmakersCreativityVerificationCyclePsychological2018], as there are infinite possible ways to conduct exploratory analyses.
 To address this limitation, subjective decisions are explicitly discussed throughout the manuscript,
@@
 -->
-There has been a call for the integration of the empirical literature on adolescent emotion regulation.
+There has been a call for the integration of the empirical literature on adolescent emotion regulation into an overarching framework.
+The first step towards this end is identifying relevant phenomena in this area of research.
 <!--, the research gap, and how you addressed it.-->
@@
 <!--Then go to what you found and its importance.  Be sure to state your findings very clearly. -->
-The findings reflected several themes commonly featured in theory and narrative reviews,
-such associalization and neurocognitive factors,
-which suggests that this is a valid method for identifying relevant phenomena.
+The findings echoed several themes featured in the theoretical literature review,
+such as socialization and neurocognitive factors,
+which illustrates the validity of this new method for identifying relevant phenomena.
 Importantly, the findings also revealed undertheorized themes,
 such as developmental disorders, physical health, external stressors,
-structural disadvantage, substance use, identity and moral development, and
+structural disadvantage, substance use, identity, moral, and
 sexual development.
-
+The findings illustrate how text mining systematic reviews may complement narrative reviews<!--,
+and sensitize researchers to potential confounders and contributing causes to consider in future empirical work-->.
+Several of the identified themes are particularly relevant in adolescence;
+either because they first emerge in this life phase (e.g., sexual development), or because they relate to age-graded developmental challenges (e.g., identity development).
+This reinforces the prior observation that general theories of emotion regulation cannot simply be generalized to adolescence,<!-- a life phase qualitatively distinct from childhood and adulthood,--> and emphasizes the importance of developing theory specific to adolescence.
 <!-- The implications can focus on many aspects of the study, such as the practice implications (briefly).-->
-
 <!--the implications also should include a focus on the understanding of adolescence/early adulthood/emerging adulthood and the contribution to that research.-->
-Several of these themes
-
-The findings illustrate how text mining systematic
-  reviews, a novel approach, may complement narrative reviews. Future
-  theoretical work might integrate these undertheorized themes into
+Future theoretical work might integrate these undertheorized themes into
 an overarching framework, and empirical research might consider them as
-  promising areas for future research, or as potential confounders in research
+promising areas for future research, or as potential confounders and contributing causes in research
 on adolescents' emotion regulation.

### 2021-05-10 action_letter_final.Rmd
Final submission

---
title: "Action letter"
author: "Caspar J. van Lissa"
date: "4/6/2021"
output: bookdown::word_document2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**Comment 1:** _Please do be sure to “unblind” your manuscript, if needed._

**Response:** I have done as requested.

**Comment 2:** _Title: Please capitalize the first letters of key words (look at a few articles in the journal or check with the APA manual).  Ensure that it is the same every time you enter it into the editorial manager. It should appear the same ever time it appears in the pdf that you approve. Also, do not use bold. …. Well, given where we are with the manuscript, I might as well give you exactly what I need to have you upload: Mapping Correlates of Adolescent Emotion Dysregulation: A Text-mining Systematic Review_

**Comment 3:** _Page 1, remove this at the bottom: Word count: 6776_

**Response:** I have done as requested.

**Comment 4:** _THROUGHOUT: use “toward” rather than “towards”_

**Response:** I have done as requested.

**Comment 5:** _In the abstract and throughout: Remove the use of the first person (we, our). [I note this in case you use it in your revision.]_

**Response:** This has been done.

**Comment 6:** _THROUGHOUT: use youth instead of youths. We consider youth plural. Thanks. [I note this in case you use it in your revisions.]_

**Response:** I don't believe I made this mistake. I did find one instance of "youth".

**Comment 7:** _Abstract, line 24 of the pdf, change “papers” to this: studies Abstract, avoided stilted language. Begin sentence with The results rather than Results. _

**Response:** Respectfully, I do not understand the first comment. I have changed "Results" to "The results". Please let me know if further action needs to be taken here.

**Comment 8:** _Abstract, line 43 of the pdf,  replace “This” with something more specific, perhaps something like: The findings illustrate …_

**Response:** I have done as requested.

**Comment 9:** _Abstract: remove this: (TMSR)_

**Response:** I have done as requested.

**Comment 10:** _Page 2, at the top, remove the title and insert this level 1 heading: Introduction These are the typical headings that typesetters will be able to work with:_

**Response:** I have done as requested.

**Comment 11:** _Level 1: Centered, Bold, Upper and Lower Case Level 2: Flush Left, Bold, Upper and Lower Case Level 3: Flush left, bold, Initial cap/lower case, period. Run in text Level 4: Flush left, bold italic, Initial cap/lower case, period. Run in text Level 5 Paragraph indent, nobold italic, Initial cap/lower case, period. Run in text_

**Response:** I have done as requested.

**Comment 12:** _As a reminder, you need at least two subheadings if you are going to have one._

**Response:** I have removed the offending subheading; it was not essential.

**Comment 13:** _Throughout, please avoid string (and even most double) citations. If your cite is important, you should have more text to go with it; no need for redundancy if it can be avoided. Also avoid dated citations unless it is a classic or central to your arguments. I know that this will be a challenge for you as you are trying to give readers a sense of the field. Please rest assured that I am ok with the overall number of citations (I have no issue with that), it is when you cite multiple citations for the same proposition. A way around this issue is to increase specificity in what you present, and then cite to the appropriate sources. Or, of course, simply deleting some citations also would work. [Generally, do avoid citations from the last century.] Please do see what you can do in this regard._

**Response:** I have removed string citations throughout. In some cases, I have left only essential references; in other cases I have split up the string and explicated the specific contribution of each reference. The only remaining exception is a situation where I specifically refer to two systematic reviews, and must thus cite them both.

**Comment 14:** _Another consideration, depending on how you edit this draft: Have the author names in parentheses.  Just state the proposition and have the cite at the end of it; we do not want to focus readers on the names of authors.  [The exception to that could be when you refer to someone’s theory that needs to have the author’s name.  Otherwise, authors should remain in the back ground.]  Avoid name-dropping. Studies should be evaluated on their merit, not who did them._

**Response:** I have done as requested throughout the manuscript.

**Comment 15:** _I need a different introductory paragraph. This is what I now ask of authors: I need an introductory paragraph that begins by noting the topic, its importance, the research gap, and a general statement about how you will address the research gap.  That is, the first paragraph works best with a closing sentence that begins with something like: This study…..   Then, in the paragraphs that follow, we’d expect to have you go straight to reviewing the relevant research.   Try to keep the introductory paragraph to the introductory literature review to one full paragraph that really gets to the point. [One strong paragraph is preferred; do two only if you absolutely  have to. …. Save specifics and nuances for the literature review. Here, you are just introducing the topic. Clear?]_

**Response:** I have done as requested. Note that I deviate from the recommended structure in one respect: As the previous Reviewer's comments emphasized the importance of clarifying the rationale behind the methods used, I have retained the newly written paragraph explaining the approach after the opening paragraph. The structure is thus:
1) Topic
2) Importance
3) Research gap
4) How you will address the research gap
5) (New paragraph) Rationale behind the method
This seems like an appropriate structure for a substantive paper that also introduces a methodological innovation - but please let me know if you feel differently.

**Comment 16:** _Also regarding the introductory paragraph, avoid tangents.  As an example, the first sentence of the first paragraph is not needed. In fact, much of the first paragraph could be trimmed to one sentence.  Several of the other introductory paragraphs also can go, or be integrated later. Again, you are just introducing here. _

**Response:** In rewriting the introductory paragraph as requested in the previous comment, I have made sure to avoid tangents.

**Comment 17:** _Page 4, use a more specific heading than “Existing theoretical landscape”. [...] So, given that, the heading should be something like: Theoretical Approaches to Emotional Regulation.  It should be a level 2 heading. _

**Response:** I have done as requested.

**Comment 18:** _Also, in the section below it, you have too much tangential information. Just present the relevant theories that are influencing research at this point in time. Just describe the theories as they are, focus on those that relate directly to emotional regulation. We don’t need history or to know much about where they come from. Just describe the theories as they relate to the issue at hand. _

**Response:** I have tried to make the requested cuts throughout the theory section. Note that the previous Reviewer had asked me to provide more of an "authoritative" narrative in this section. To do so, I have contextualized the micro-level theories within the macro frameworks like Bronfenbrenner's and Sameroff's models. I assumed that this is not what you mean by "tangential information", and left these additions intact.

**Comment 19:** _There should not be a need for the first subheading on page 8 (plus, you would have needed two at the same level). The theory section should end up shorter. _

**Response:** I have removed this subheader, as requested.

**Comment 20:** _Page 8, the new section beginning on line 48: the topic sentence of the paragraph should be about the paragraph; remove the first part that focuses on  the part before._

**Response:** I have done as requested.

**Comment 21:** _Right before that section, you have something about “The present study lays…”.  I need you to remove sentences like that. What the present study does should be presented in the current study section, it should not be interspersed in the literature review introducing the study.  The literature review does just that, review. It should lead to the research questions/hypotheses; it is just laying a foundation._

**Response:** I have moved this sentence to "The Current Study" section as requested.

**Comment 22:** _Page 10, center the heading, and have it read like this: The Current Study_

**Response:** I have done as requested.

**Comment 23:** _I need an edit to this section. The current study section should briefly note the research gap, note aims/expectations/hypotheses/research questions and briefly remind readers of the rationales for them. The rationales should be obvious from the literature review above it (you should not introduce new research/cites in this section)._

**Response:** I have rewritten "The Current Study" according to these specifications.

**Comment 24:** _Ironically, the first  sentence or so of the Methods section is what should be in the current study section._

**Response:** This sentence has been moved to "The Current Study".

**Comment 25:** _Page 12, line 46, this should not be a level 1 heading._

**Response:** I have changed it to level 2.

**Comment 26:** _These are the level 1 headings that we need to have: Abstract Introduction Current Study Methods Results Discussion Conclusion Acknowledgments_

**Response:** All these headers are now present.

**Comment 27:** _Page 17, I need a different introductory paragraph to the discussion._
The first paragraph of the discussion should start more broadly and give readers a good sense of the issues that need to be addressed in this area, as well as highlight the complexities/questions involved and GENERALLY how you addressed them (such as in one sentence at the end of the paragraph).  Assume, for example, that readers have skipped much of your study and jumped straight to the discussion section. In the sentences after that, present what you found and the importance of your contribution (and limitations and so forth). I apologize for this journal style edit.

**Response:** I have rewritten the introductory paragraph and remainder of the Discussion as requested.

**Comment 28:** _Page 23, line 29, you should not have a paragraph that begins with “To conclude….”and then follow that with two more paragraphs. Conclusions should conclude, should be the last word._

**Response:** Thank you, good point. I have removed this in rewriting the Discussion and Conclusion.

**Comment 29:** _Conclusion: do not start with “In sum,” It should stand on its own. Much of what you have in the conclusion is implications. I need it more conclusory._

**Response:** I have removed this turn of phrase and rewritten the Discussion and Conclusion. Implications are now in a separate subsection, and the Conclusion is more conclusory.

Comments: Your current conclusion has much in it that should be in the discussion. 
Here is what I typically tell authors regarding what I need in the conclusion. 
Insert this level 1 heading before it: Conclusion Begin by (briefly) reminding the reader of the topic, the research gap, and how you addressed it. Then go to what you found and its importance.  Be sure to state your findings very clearly. The implications can focus on many aspects of the study, such as the practice implications (briefly). But, for us, the implications also should include a focus on the understanding of adolescence/early adulthood/emerging adulthood and the contribution to that research.  The bulk of the paragraph, though, should be focused on the key findings. Do try to have it be just one strong paragraph.

**Response:** I have restructured the Conclusion according to these specifications. The previous conclusion has been merged with the Discussion; there was much redundancy. Thank you for spotting this.

**Comment 30:** _Page 23, line 50 of the pdf: delete the sentence._

**Response:** I have done as requested.<!--In restructuring the Conclusion, this sentence has been removed and spliced into the Discussion.I have not deleted this sentence; I'm not unwilling, but I don't understand why you want me to do so. This line, and line 34 on the same page, were added to address a comment by the previous Reviewer, who asked to clarify "What are the important findings" in the Discussion. I mention "familiar" themes emerging from the findings on line 34, and "novel" findings on line 50. It seems to me that I should either not discuss any of the findings at all, or discuss both familiar and novel findings - but that it would be counterintuitive for a paper that set out to identify under-theorized themes to discuss only familiar findings and not novel ones.-->

**Comment 31:** _You have figures with color.   I would like to note at this point that when we get to proof stage, and I sure hope we get to that stage, you will be asked to pay more for the use of color. Please be sure to read that very carefully. It is NOT asking you to pay more for what will be electronic copies; it asks you to pay more for the actual print copies. Just decline to pay for the print copies.  I note this because authors often misread and then try to edit their text so they do not need to pay a hefty sum of money. There is no need for that. Just read it carefully. Of course, if you wish to pay, then that is up to you. _

**Response:** Understood, will do. I've also adapted the plots so they will still be intelligible when printed in grayscale, or when viewed by the color-blind.

**Comment 32:** _You acknowledgment page (the one to be uploaded separately) needs to report more information._

**Response:** I have included all requested information.

### 2021-05-10 manuscript.Rmd
Final submission

@@
 classoption       : "man,noextraspace"
-output            : papaja::apa6_pdf
+output            : papaja::apa6_docx
 knit              : worcs::cite_essential
@@
 
-cat_cols <- c(Outcome = "gray50", Indicator = "tomato", Cause = "gold", Protective = "forestgreen")
-cat_cols <- c(Outcome = "gray50", Indicator = "tomato", Cause = "gold", Protective = "olivedrab2")
+cat_cols <- c(Outcome = "gray55", Indicator = "tomato", Cause = "darkgoldenrod3", Protective = "olivedrab4")
+cat_cols <- c(Outcome = "gray55", Indicator = "tomato", Cause = "darkgoldenrod3", Protective = "olivedrab4")
 vert$color <- cat_cols[vert$Category]
@@
 vert$faded <- vert$name %in% df$cat[df$source == "theory"]
-cat_cols <- c(Outcome = "gray50", Indicator = "tomato", Cause = "gold", Protective = "olivedrab2")
+cat_cols <- c(Outcome = "gray55", Indicator = "tomato", Cause = "darkgoldenrod3", Protective = "olivedrab4")
 vert$color <- cat_cols[vert$Category]
@@
 l1 <- l <- layout_with_fr(g1)
+l1[1,] <- c(-2.21258774559817, 25.7)
+l1[28, 2] <- 29.5
+l1[6, 2] <- 30
+l1[21, 1] <- -0.05
+
 set.seed(3)
 l2 <- layout_with_fr(g2)
+l2[28, 2] <- -1.8
+l2[5, 2] <- -4.5
+l2[15, 2] <- -6.8
 
@@
   plot(g1, edge.curved = 0, layout=l1,
-       vertex.label.family = "sans",
+       vertex.label.family = "Arial",
        vertex.label.cex = 0.7,
@@
        vertex.label.font = 1,         # Font of node names
-       vertex.frame.width = 2
+       vertex.frame.width = 2,
+         edge.color = "gray70" # edge.color = rgb(0,0,0,.2)
   )
   text(-1.1, y = -1, labels = "a")
-  legend(x=-1.2, y=1.1, names(cat_cols), pch=legend_shapes, col=cat_cols, pt.bg=cat_cols, pt.cex=1.4, cex=.7, bty="n", ncol=1)
+  legend(x=-1.2, y=1.1, names(cat_cols), pch=legend_shapes, col=cat_cols, pt.bg=cat_cols, pt.cex=1.2, cex=.7, bty="n", ncol=1)
   plot(g2, edge.curved = 0, layout=l2,
-       vertex.label.family = "sans",
+       vertex.label.family = "Arial",
        vertex.label.cex = 0.7,
@@
        vertex.label.font = 1,         # Font of node names
-       vertex.frame.width = 2
+       vertex.frame.width = 2,
+         edge.color = "gray70" # edge.color = rgb(0,0,0,.2)
   )
@@
 png("baseline_network.png", height = 100, width = 200, units = "mm", res= 300)
+eval(p)
+dev.off()
+
+loadfonts(device = "postscript") ## for postscript()
+postscript("baseline_network.eps", height = (.5*7.9), width = 7.9,
+           family = "Arial", paper = "special", onefile = FALSE,
+           horizontal = FALSE)
 eval(p)
@@
 
-  cat_cols <- c(Outcome = "gray50", Indicator = "tomato", Cause = "gold", Protective = "forestgreen")
+  cat_cols <- c(Outcome = "gray55", Indicator = "tomato", Cause = "darkgoldenrod3", Protective = "olivedrab4")
   df_plot$cat <- ordered(df_plot$cat, levels = c("Outcome", "Indicator", "Cause", "Protective"))
@@
     geom_point(data = df_plot[!df_plot$faded, ], aes(colour = cat, fill = cat, shape = cat), size = 1.5) +
-    scale_colour_manual(values = c(Outcome = "gray50", Indicator = "tomato", Cause = "gold", Protective = "forestgreen"))+ #, guide = NULL
+    scale_colour_manual(values = c(Outcome = "gray55", Indicator = "tomato", Cause = "darkgoldenrod3", Protective = "olivedrab4"))+ #, guide = NULL
     scale_shape_manual(values = scale_shapes)+#, guide = NULL
-    scale_fill_manual(values = c(Outcome = "gray50", Indicator = "tomato", Cause = "gold", Protective = "forestgreen")) +
+    scale_fill_manual(values = c(Outcome = "gray55", Indicator = "tomato", Cause = "darkgoldenrod3", Protective = "olivedrab4")) +
     scale_x_log10() +
@@
 
-  cat_cols <- c(Outcome = "gray50", Indicator = "tomato", Cause = "gold", Protective = "olivedrab2")
+  cat_cols <- c(Outcome = "gray55", Indicator = "tomato", Cause = "darkgoldenrod3", Protective = "olivedrab4")
   vert$color <- cat_cols[vert$Category]
@@
   l1[,1] <- -1*l1[,1]
+  l1[23,2] <- 6.5
+  l1[44,2] <- 6
+  l1[6,2] <- 5.7
+  l1[34,2] <- 5.3
+  l1[26,] <- c(-1.8, 2.2)
+  l1[5,1] <- -.4
+  l1[40,1] <- -1.1
+  l1[29,] <- c(-1,1.7)
+
   set.seed(64)
@@
     plot(g, edge.curved = 0, layout=l1,
-         vertex.label.family = "sans",
+         vertex.label.family = "Arial",
          vertex.label.cex = 0.5,
@@
          vertex.label.font = 1,         # Font of node names
-         vertex.frame.width = 2
+         vertex.frame.width = 2,
+         edge.color = "gray70" # edge.color = rgb(0,0,0,.2)
     )
@@
     plot(g, edge.curved = 0, layout=l2,
-         vertex.label.family = "sans",
+         vertex.label.family = "Arial",
          vertex.label.cex = 0.5,
@@
 
-```{r message = FALSE, echo = FALSE, warning = FALSE, results="hide"}
+```{r eval = TRUE, message = FALSE, echo = FALSE, warning = FALSE, results="hide"}
 p <- quote(cowplot::plot_grid(readRDS("s1_varimp.RData")+theme(legend.position = "none")+xlab("Word frequency (Analysis 1)"), readRDS("s2_varimp.RData")+xlab("Word frequency (Analysis 2)")))
@@
 dev.off()
+save_plot("varimps.eps", plot = eval(p), device = cairo_ps, base_height = ((150/200)*7.9), base_width = 7.9)
+# loadfonts(device = "postscript") ## for postscript()
+# postscript("varimps.eps", height = ((150/200)*7.9), width = 7.9,
+#            family = "Arial", paper = "special", onefile = FALSE,
+#            horizontal = FALSE)
+# eval(p)
+# dev.off()
 ```
@@
 source("circle2.R")
-
-if(isTRUE(tools::md5sum("study2_df.RData") == "21abb2622dfd94d8bd3473ed56697f9e")){
+run_intensive = FALSE
+if(!run_intensive){
   df <- readRDS("study2_df.RData")
@@
 # Exclude words
-if(!run_everything){
+if(!run_intensive){
   df_kw <- readRDS("study2_df_kw.RData")
@@
 
-if(!run_everything){
+if(!run_intensive){
   kw_tr <- readRDS("study2_textrank.RData")
@@
 
-if(!run_everything){
+if(!run_intensive){
   df_analyze <- data.table(readRDS("study2_df_analyze.RData"))
@@
   geom_point(data = df_plot[!df_plot$faded, ], aes(colour = cat, fill = cat, shape = cat), size = 1.5) +
-  scale_colour_manual(values = c(Outcome = "gray50", Indicator = "tomato", Cause = "gold", Protective = "forestgreen"), guide = NULL)+#
+  scale_colour_manual(values = c(Outcome = "gray55", Indicator = "tomato", Cause = "darkgoldenrod3", Protective = "olivedrab4"), guide = NULL)+#
   scale_shape_manual(values = scale_shapes, guide = NULL)+#
-  scale_fill_manual(values = c(Outcome = "gray50", Indicator = "tomato", Cause = "gold", Protective = "forestgreen"), guide = NULL) +
+  scale_fill_manual(values = c(Outcome = "gray55", Indicator = "tomato", Cause = "darkgoldenrod3", Protective = "olivedrab4"), guide = NULL) +
   scale_x_log10() +
@@
                    panel.grid.minor.x = element_blank(), axis.title.y = element_blank(),
-                   legend.position = c(.825,.1125),
+                   legend.position = c(.81,.1125),
                    legend.title = element_blank(),
@@
          vertex.label.font = 1,         # Font of node names
-         vertex.frame.width = 2
+         vertex.frame.width = 2,
+         edge.color = "gray70" # edge.color = rgb(0,0,0,.2)
     )
     text(-1.1, y = -1, labels = "a")
-    legend(x=-1.1, y=1.1, names(cat_cols), pch=legend_shapes, col="#777777", pt.bg=cat_cols, pt.cex=1.4, cex=.7, bty="n", ncol=1)
+    legend(x=-1.1, y=1.1, names(cat_cols), pch=legend_shapes, col="#777777", pt.bg=cat_cols, pt.cex=1.2, cex=.7, bty="n", ncol=1)
     plot(g, edge.curved = 0, layout=l2,
-         vertex.label.family = "sans",
+         vertex.label.family = "Arial",
          vertex.label.cex = 0.5,
@@
 ```{r mergenetworks}
-cat_cols <- c(Outcome = "gray50", Indicator = "tomato", Cause = "gold", Protective = "olivedrab2")
+cat_cols <- c(Outcome = "gray55", Indicator = "tomato", Cause = "darkgoldenrod3", Protective = "olivedrab4")
 bl1 <- readRDS("bl_l1.RData")
@@
 s1l <- readRDS("s1_l1.RData")
+s1l[23,2] <- 6.5
+s1l[44,2] <- 6
+s1l[6,2] <- 5.7
+s1l[34,2] <- 5.3
+s1l[26,] <- c(-1.8, 2.2)
+s1l[5,1] <- -.4
+s1l[40,1] <- -1.1
+s1l[29,] <- c(-1,1.7)
 s2l <- readRDS("s2_l1.RData")
@@
        layout=bl1,
-       vertex.label.family = "sans",
+       vertex.label.family = "Arial",
        vertex.label.cex = 0.5,
@@
        vertex.label.font = 1,         # Font of node names
-       vertex.frame.width = 2
+       vertex.frame.width = 2,
+         edge.color = "gray70" # edge.color = rgb(0,0,0,.2)
   )
   text(-1.1, y = -1, labels = "a")
-  legend(x=-1.1, y=1.1, names(cat_cols), pch=legend_shapes, col=cat_cols, pt.bg=cat_cols, pt.cex=1.4, cex=.7, bty="n", ncol=1)
+  legend(x=-1.1, y=1.1, names(cat_cols), pch=legend_shapes, col=cat_cols, pt.bg=cat_cols, pt.cex=1.2, cex=.7, bty="n", ncol=1)
 
@@
        layout=bl2,
-       vertex.label.family = "sans",
+       vertex.label.family = "Arial",
        vertex.label.cex = 0.5,
@@
        layout=s1l,
-       vertex.label.family = "sans",
+       vertex.label.family = "Arial",
        vertex.label.cex = 0.5,
@@
        layout=s2l,
-       vertex.label.family = "sans",
+       vertex.label.family = "Arial",
        vertex.label.cex = 0.5,
@@
        vertex.label.font = 1,         # Font of node names
-       vertex.frame.width = 2
+       vertex.frame.width = 2,
+         edge.color = "gray70" # edge.color = rgb(0,0,0,.2)
   )
   text(-1.1, y = -1, labels = "a")
-  legend(x=-1.2, y=1.1, names(cat_cols), pch=legend_shapes, col=cat_cols, pt.bg=cat_cols, pt.cex=1.4, cex=.6, bty="n", ncol=1)
+  legend(x=-1.2, y=1.1, names(cat_cols), pch=legend_shapes, col=cat_cols, pt.bg=cat_cols, pt.cex=1.2, cex=.6, bty="n", ncol=1)
 
@@
 svg("tmnetworks.svg", width = 14)
+eval(p)
+dev.off()
+
+loadfonts(device = "postscript") ## for postscript()
+postscript("tmnetworks.eps", height = (.5*7.9), width = 7.9,
+           family = "Arial", paper = "special", onefile = FALSE,
+           horizontal = FALSE)
 eval(p)

### 2021-05-10 ASREVIEW.R

@@ -3,6 +3,6 @@ library(reticulate)
 use_condaenv("veni_sysrev") #C:\Users\lissa102\AppData\Local\Continuum\miniconda3\envs\veni_sysrev
 asreview <- import("asreview")
 asreview
-asreview oracle YOUR_DATA.csv --state_file myreview.h5
+#asreview oracle YOUR_DATA.csv --state_file myreview.h5
 
 py_run_string("asreview oracle")

### 2021-05-10 bibliometrix_tutorial.R

@@ -8,11 +8,11 @@ recs$AB[recs$TI == "FAMILY DYNAMICS AND CHILD OUTCOMES IN EARLY INTERVENTION: TH
 recs$AB[recs$TI == "PEER VICTIMIZATION AND NEUROBIOLOGICAL MODELS: BUILDING TOWARD COMPREHENSIVE DEVELOPMENTAL THEORIES"]
 
 
-ANXIETY AND DEPRESSION DURING CHILDHOOD AND ADOLESCENCE: TESTING THEORETICAL MODELS OF CONTINUITY AND DISCONTINUITY"
+#ANXIETY AND DEPRESSION DURING CHILDHOOD AND ADOLESCENCE: TESTING THEORETICAL MODELS OF CONTINUITY AND DISCONTINUITY"
 
-FAMILY DYNAMICS AND CHILD OUTCOMES IN EARLY INTERVENTION: THE ROLE OF DEVELOPMENTAL THEORY IN THE SPECIFICATION OF EFFECTS"
+# FAMILY DYNAMICS AND CHILD OUTCOMES IN EARLY INTERVENTION: THE ROLE OF DEVELOPMENTAL THEORY IN THE SPECIFICATION OF EFFECTS"
 
-GENERAL STRAIN THEORY, GENDER, AND THE CONDITIONING INFLUENCE OF NEGATIVE INTERNALIZING EMOTIONS ON YOUTH RISK BEHAVIORS
+# GENERAL STRAIN THEORY, GENDER, AND THE CONDITIONING INFLUENCE OF NEGATIVE INTERNALIZING EMOTIONS ON YOUTH RISK BEHAVIORS
 
 library(bibliometrix)
 library(dplyr)
@@ -62,10 +62,10 @@ dim(NetMatrix)
 
 CS <- conceptualStructure(recs,field="DE", method="CA", minDegree=4, k.max=8, stemming=TRUE, labelsize=10, documents=10)
 saveRDS(CS, "CS.RData")
-net		bipartite network
-res		Results of CA, MCA or MDS method
-km.res		Results of cluster analysis
-graph_terms		Conceptual structure map (class "ggplot2")
+# net		bipartite network
+# res		Results of CA, MCA or MDS method
+# km.res		Results of cluster analysis
+# graph_terms		Conceptual structure map (class "ggplot2")
 
 CS2 <- conceptualStructure(recs,field="ID", method="CA", minDegree=4, clust=5, stemming=FALSE, labelsize=10, documents=10)
 

### 2021-09-01 presentation.Rmd
EADP presentation

---
title: "Mapping Phenomena Relevant to Adolescent Emotion Dysregulation: A Text-mining Systematic Review"
author: "Caspar J. Van Lissa<sup>1</sup> (2021), *Adolescent Research Review*, DOI: [10.1007/s40894-021-00160-7](https://link.springer.com/article/10.1007%2Fs40894-021-00160-7)"
date: "<p><sup>1</sup>: Utrecht University, dept. Methodology & Statistics<br>Funded by NWO Veni grant  VI.Veni.191G.090"
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding, output_dir = "docs") })
output: 
  ioslides_presentation:
    widescreen: true
    css: slide.css
bibliography      : ["veni_sysrev.bib"]
---

```{r setup, include=FALSE}
#css: https://maxcdn.bootstrapcdn.com/bootstrap/3.3.7/css/bootstrap.min.css
knitr::opts_chunk$set(echo = FALSE)
```

## Emotion regulation in adolescence

Developmentally sensitive period for emotion regulation [@zimmermannEmotionRegulationEarly2014]

As many as one in five develop psychopathology [@leeAdolescentMentalHealth2014]

Potentially lifelong implications for mental health and well-being

Need to know what phenomena are associated with adolescents' emotion regulation

## Knowledge gap

Substantial empirical research has addressed this topic, but:

* Different (sub)disciplines have approached the topic in disparate ways [@riedigerEmotionRegulationAdolescence2014]
* No consistent terminology [@bariolaChildAdolescentEmotion2011]
* No conceptual frameworks [@stifterEmotionRegulation2019]
* No overarching theoretical framework [@bussTheoriesEmotionalDevelopment2019]

There is a need for the integration of knowledge across research areas and consolidation of empirical research into overarching theory.

## Moving forward

According to *Theory Construction Methods*, first step toward a unifying framework is identifying relevant phenomena [@borsboomTheoryConstructionMethodology2020]

* Phenomena: stable and general features of the world

Few tools exist for identifying relevant phenomena (aside from expert opinion)

*This paper argues that systematic reviews are a suitable and relatively more objective method for phenomena detection.*

## Why text mining?

Narrative reviews are limited by small samples, confirmation bias, and emphasis on positive results [@littellEvidencebasedBiasedQuality2008]

*Text mining systematic review (TMSR):*

* Covers arbitrarily greater corpora
* Derives insights through a transparent, objective, and reproducible process
* Assumes that term frequency indicates relevance of phenomena
* Assumes that co-occurrence frequency indicates putative associations
    + These metrics can be jointly visualized as a network graph
    + Thus "mapping" phenomena relevant to adolescent emotion regulation
    + Co-occurrence graph ~= rudimentary nomological network

## Relevant theory

* Bioecological model [@bronfenbrennerBioecologicalModelHuman2007]
* Transactional model [@sameroffUnifiedTheoryDevelopment2010]
* Hall's notion of "storm and stress"
* Theory of normative emotional development [@sroufeEmotionalDevelopmentOrganization1995]
* Tripartite model [@morrisRoleFamilyContext2007]
* Internalization model of emotional development [@holodynskiDevelopmentEmotionsEmotion2006]
* Polyvagal theory [@porgesOrientingDefensiveWorld1995].
* Model of social-affective engagement and goal flexibility [@croneUnderstandingAdolescencePeriod2012]
* Process model of emotion regulation [@grossHandbookEmotionRegulation2013]
* Social Information Processing Theory [@lemeriseIntegratedModelEmotion2000]

## Baseline network

```{r figbaseline, warning=FALSE, eval = TRUE, results='asis', out.width = "90%", fig.cap="Phenomena relevant to adolescents' emotion regulation according to theory (a) and narrative reviews (b; transparent nodes indicate constructs also present in the theory)."}
knitr::include_graphics("baseline_network.png") 
```

Phenomena relevant to adolescents' emotion regulation according to theory (a) and narrative reviews (b; transparent nodes indicate constructs also present in the theory).

## Limitations of relevant theory

* Few explicitly address adolescence
* Few have comprehensively addressed important predictors of development in this life stage
* None directly guide contemporary research 
* Theories vary widely in scope: Some are broad and non-specific; others describe a specific phenomenon in detail, but lack a broader perspective.
    + Broad theories can frame any research, specific theories generate hypotheses.
    + It would be beneficial to bridge these levels of analysis.

# Methods

## Open science

All code and data available at github.com/cjvanlissa/veni_sysrev

Workflow for Open Reproducible Code in Science (WORCS) used to make analyses reproducible [@vanlissaWORCSWorkflowOpen2020]

## Search strategy

Based on procedures by Staaks [@staaksSystematicReviewSearch2019]

Web of Science

Reference set of 29 articles

Search string constructed to retrieve this set (synonyms of emotion regulation and adolescence)

6653 results including 25 of the reference set

## Screening

```{r prismachart, eval = TRUE, results='asis', out.width = "80%"}

knitr::include_graphics("prismachart.png")
```

Addresses **emotion regulation** in population overlapping with age range [10-24]

## Screening contd.

Preliminary screening was conducted in Rayyan.

After 367 papers, screening continued in the free open source program ASReview [@van_de_schoot_rens_2020_3828293]

Algorithm: "naive Bayes"

Reverse coding: Excluded articles coded as hits

Screening continued until among the most recently screened 100 papers only 6 were excluded

## Screening contd.

Experienced challenges:

* First version required NVidia CUDA
* Difficult to set up Python environment
* Workaround for corpus with mostly relevant publications
* Would be better to have automatic cutoff

# Analysis 1: Author keywords

## Method

* Keywords extracted by document
* Exclusion filter of methodological terms etc
* The resulting corpus consisted of 5031 documents with 8080 terms
* Dictionary of 108 terms with 464 regular expression queries
* Remaining unique terms: 5292
* Terms exceeding $97.5^{th}$ percentile of negative binomial distribution pruned (= 21+ documents)
* Most pruned terms (4004) occurred only once in the corpus

84 remaining terms, occurring in 4827 documents

## Mapping the literature

* Term co-occurrence matrix, 2498 co-occurrence relationships
* Small coefficients again pruned using $97.5^{th}$ percentile of negative binomial (25+ documents)

106 co-occurrence relationships remained

Terms categorized as cause, outcome, protective factor, or indicator of emotion regulation

# Analysis 2: Abstract text mining

## Method

Nouns and adjectives help derive more interpretable text mining models [@martinMoreEfficientTopic2015]

Nouns capture terms like "emotion"; adjectives capture the "mental" in "mental health"

Used "part-of-speech tagging" (POS-tagging) to identify words' grammatical functions

Stemmed terms to their root

Identified trigrams using `textrank` [@wijffelsTextrankSummarizeText2019]

* E.g., "emotion regulation" is already a bigram

Merged trigrams with original data

## Method contd.

* 5097 documents with 11448 unique words
* Pruned $97.5^{th}$ percentile (6+ documents)
* 850 co-occurrence relationships
* Pruned $97.5^{th}$ percentile (10+ documents)

43 remaining co-occurrence relationships

<!-- ## Common terms

```{r varimps1, eval = TRUE, results='asis', out.width = "90%"}
knitr::include_graphics("varimps_small.png")
```

Author keywords (a) and abstracts (b)-->

## {.fullslide}

![](varimps_small.png)

## Co-occurrence graph

```{r networks1, eval = TRUE, results='asis', out.width = "90%"}
knitr::include_graphics("tmnetworks_small.png")
```

Author keywords (a) and abstracts (b)

<!--## {.fullslide}

![](tmnetworks_small.png)-->

## Results: Important phenomena

* Emotion regulation and related mental health outcomes among top terms
* Theoretically important themes: *neural*, *parenting*, and *stress*
* Also several under-theorized concepts: *ADHD/CD*, *substance* use, *minority status*
* Substantial correspondence between keywords and abstracts
    + 75% of frequent terms from keywords also present in abstracts
    + 89% of the frequent terms from abstracts present in keywords
* *sex* was more frequent in the Abstracts: sex differences are regularly reported in Abstracts even if they are not mentioned in the keywords
* *parenting* (keywords) was displaced by *mothers* (Abstracts): Parenting is often operationalized as mothering

## Results: Co-occurrence

Keywords:

* Emotion regulation is a central construct to which other constructs are directly linked
* Graph was sparse, with few interconnections between terms (fragmented literature?)

Abstracts:

* Emotion regulation and mental health-related outcomes formed central axis
* Relevant terms connected to this axis, but not directly to emotion regulation
* Only terms directly connected to emotion regulation were *neural*, *mothers*, *attachment* and *ptsd*
* even sparser network

## Discussion

* Both analyses reflected some phenomena from theoretical literature
    + Particularly related to neurodevelopment and socialization
* Mental health-related outcomes feature prominently
    + Emotion regulation implicated in mental health problems [@leeAdolescentMentalHealth2014],
    + This underlines the importance of research in this area

## Undertheorized themes

* Developmental disorders
    + E.g., ADHD/CD and autism
* Physical health (sic)
    + sleep, sports, and disability status
* External stressors
    + bullying, stress, PTSD, abuse, violence, life events, historic events (e.g., earthquakes, war), parenting stress, and divorce.
* Structural disadvantage
    + minority status, discrimination, disability status, socio-economic status, adoption status, and sexual diversity
    + Developmental disorders also relevant in this context, as neuroatypical individuals tend to experience social exclusion [@cappadociaBullyingExperiencesChildren2012]

## Undertheorized themes contd.

* Addictive behavior
    + substance use and device use
* Identity and moral development
    + values and personality. 
* Sexual development
    + (biological) sex, puberty, sexual diversity, and romantic relationships

Text mining systematic reviews can thus identify undertheorized themes

## Structural findings

Central axis of emotion regulation and mental health outcomes suggests that these phenomena are closely linked

Sparse networks (fragmented literature)

* Most phenomena directly linked with emotion regulation/mental health
* Absence of terms suggests that they are not well-integrated in the literature
* Sparser network for Abstractslikely reflects greater noise

Substantial correspondence between both networks

* Supports validity of the findings, suggests that automatic keyword extraction identifies relevant constructs

## Implications

Results reflected familiar phenomena: Suggests validity of the method

Results also revealed under-theorized phenomena: TMSR may complement theory and narrative reviews

Implications for future empirical research:

* Researchers typically rely on theory
* Under-theorized phenomena may be overlooked
* This study offers guidance regarding relevant phenomena to consider as confounders or contributing causes
* Unembedded terms indicate potential knowledge gaps; promising areas of future research

## Theoretical implications

* Sparse graphs indicate fragmented literature
* Important to generate an overarching theory of adolescent emotion regulation
* First step in theory construction methodology is to identify relevant phenomena [@borsboomTheoryConstructionMethodology2020]
* Present study thus serves as starting point for theory development

## Stengths

* This study was more comprehensive than previous narrative reviews [cf. @bariolaChildAdolescentEmotion2011; @coe-odessEmergentEmotionsAdolescence2019]
    + Used systematic search and included much larger corpus
* TMSR can include corpora of arbitrary size, and derive insights by transparant and reproducible procedures

## Limitations

* These text mining techniques do not extract *meaning* from the literature
* Analyses limited to keywords and abstracts
    + Many full text articles are behind paywalls
    + No standardized Application Programming Interface (API)
* Comprehensive access to scientific publications is essential to all meta-scientific research
* Recommend open access publishing and the development of a unified API for article retrieval
* Subjective decisions were made throughout the analysis process
    + creative license is inherent to inductive studies [@wagenmakersCreativityVerificationCyclePsychological2018]
    + There are infinite possible ways to conduct exploratory analyses

## Conclusion

Text mining systematic reviews can identify theoretically relevant phenomena,
and map potential associations

* This illustrates validity of the method

Results also revealed undertheorized themes

* E.g., developmental disorders, physical health, external stressors, structural disadvantage, substance use, identity, moral, and
sexual development

Text mining systematic reviews thus complement theory and narrative reviews

Future theoretical work should integrate undertheorized themes into an overarching framework

Empirical research might consider them as promising areas for future research, or potential confounders and contributing causes

## References

### 2021-09-01 presentation_eadp.Rmd
EADP presentation

--- 2021-09-01 presentation.Rmd
@@
 ---
-title: "Mapping Phenomena Relevant to Adolescent Emotion Dysregulation: A Text-mining Systematic Review"
+title: "Mapping Phenomena Relevant to Adolescent Emotion Regulation: A Text-mining Systematic Review"
 author: "Caspar J. Van Lissa<sup>1</sup> (2021), *Adolescent Research Review*, DOI: [10.1007/s40894-021-00160-7](https://link.springer.com/article/10.1007%2Fs40894-021-00160-7)"
@@
 
-As many as one in five develop psychopathology [@leeAdolescentMentalHealth2014]
+20% develop psychopathology [@leeAdolescentMentalHealth2014]
 
@@
 
-Need to know what phenomena are associated with adolescents' emotion regulation
+What phenomena are associated with adolescents' emotion regulation?
 
@@
 
-There is a need for the integration of knowledge across research areas and consolidation of empirical research into overarching theory.
+Knowledge across research areas must be integrated and consolidated into overarching theory.
 
@@
 
-According to *Theory Construction Methods*, first step toward a unifying framework is identifying relevant phenomena [@borsboomTheoryConstructionMethodology2020]
+First step in *Theory Construction Methods* is identifying relevant phenomena [@borsboomTheoryConstructionMethodology2020]
 
@@
 
-Few tools exist for identifying relevant phenomena (aside from expert opinion)
+Few tools for identifying relevant phenomena
 
-*This paper argues that systematic reviews are a suitable and relatively more objective method for phenomena detection.*
+* aside from expert opinion
+
+*Text mining systematic reviews are a suitable and relatively objective method for phenomena detection.*
 
@@
 
-Narrative reviews are limited by small samples, confirmation bias, and emphasis on positive results [@littellEvidencebasedBiasedQuality2008]
+**Narrative reviews:** small samples, confirmation bias, emphasis on positive results [@littellEvidencebasedBiasedQuality2008]
 
-*Text mining systematic review (TMSR):*
+**Text mining systematic review (TMSR):**
 
-* Covers arbitrarily greater corpora
-* Derives insights through a transparent, objective, and reproducible process
-* Assumes that term frequency indicates relevance of phenomena
-* Assumes that co-occurrence frequency indicates putative associations
-    + These metrics can be jointly visualized as a network graph
-    + Thus "mapping" phenomena relevant to adolescent emotion regulation
+* No limit on sample size
+* Transparent, objective, reproducible process
+* Assumes that *term frequency indicates relevance* of phenomena
+* Assumes that *co-occurrence frequency indicates association*
     + Co-occurrence graph ~= rudimentary nomological network
 
-## Relevant theory
+## Baseline
+
+Manual selection of key constructs from relevant theory and prior reviews [ @bariolaChildAdolescentEmotion2011; @coe-odessEmergentEmotionsAdolescence2019]:
 
@@
 * Tripartite model [@morrisRoleFamilyContext2007]
-* Internalization model of emotional development [@holodynskiDevelopmentEmotionsEmotion2006]
+* Internalization model [@holodynskiDevelopmentEmotionsEmotion2006]
 * Polyvagal theory [@porgesOrientingDefensiveWorld1995].
@@
 
-Phenomena relevant to adolescents' emotion regulation according to theory (a) and narrative reviews (b; transparent nodes indicate constructs also present in the theory).
+(a) Theory (b) narrative reviews; transparent nodes indicate constructs also present in theory.
 
@@
 * Few explicitly address adolescence
-* Few have comprehensively addressed important predictors of development in this life stage
+* Few comprehensively address predictors of emotion regulation
 * None directly guide contemporary research 
@@
 
-All code and data available at github.com/cjvanlissa/veni_sysrev
+All code and data available at <https://github.com/cjvanlissa/veni_sysrev>
 
@@
 
-## Screening contd.
+# Method
 
-Preliminary screening was conducted in Rayyan.
+## Analysis 1: Author keywords
 
-After 367 papers, screening continued in the free open source program ASReview [@van_de_schoot_rens_2020_3828293]
-
-Algorithm: "naive Bayes"
-
-Reverse coding: Excluded articles coded as hits
-
-Screening continued until among the most recently screened 100 papers only 6 were excluded
-
-## Screening contd.
-
-Experienced challenges:
-
-* First version required NVidia CUDA
-* Difficult to set up Python environment
-* Workaround for corpus with mostly relevant publications
-* Would be better to have automatic cutoff
-
-# Analysis 1: Author keywords
-
-## Method
-
-* Keywords extracted by document
-* Exclusion filter of methodological terms etc
-* The resulting corpus consisted of 5031 documents with 8080 terms
+* Extract author keywords
+* Exclude methodological terms etc: 5031 documents with 8080 terms
 * Dictionary of 108 terms with 464 regular expression queries
 * Remaining unique terms: 5292
-* Terms exceeding $97.5^{th}$ percentile of negative binomial distribution pruned (= 21+ documents)
-* Most pruned terms (4004) occurred only once in the corpus
+* Pruned terms exceeding $97.5^{th}$ percentile of negative binomial distribution (= 21+ documents)
+* Most pruned terms (4004) occurred only once
+* 2498 term co-occurrence relationships
+* Pruned using negative binomial (25+ documents)
 
-84 remaining terms, occurring in 4827 documents
+Final data: **4827 documents** with **84 terms** and **106 co-occurrence relationships**
 
-## Mapping the literature
+Categorized causes, outcomes, protective factors, and indicators
 
-* Term co-occurrence matrix, 2498 co-occurrence relationships
-* Small coefficients again pruned using $97.5^{th}$ percentile of negative binomial (25+ documents)
+## Analysis 2: Abstract text mining
 
-106 co-occurrence relationships remained
-
-Terms categorized as cause, outcome, protective factor, or indicator of emotion regulation
-
-# Analysis 2: Abstract text mining
-
-## Method
-
-Nouns and adjectives help derive more interpretable text mining models [@martinMoreEfficientTopic2015]
-
-Nouns capture terms like "emotion"; adjectives capture the "mental" in "mental health"
-
-Used "part-of-speech tagging" (POS-tagging) to identify words' grammatical functions
-
-Stemmed terms to their root
-
-Identified trigrams using `textrank` [@wijffelsTextrankSummarizeText2019]
-
-* E.g., "emotion regulation" is already a bigram
-
-Merged trigrams with original data
-
-## Method contd.
-
+* Selected nouns and adjectives using "part-of-speech tagging"
+* Stemmed terms to their root
+* Identified trigrams using `textrank` [@wijffelsTextrankSummarizeText2019]
 * 5097 documents with 11448 unique words
@@
 
-43 remaining co-occurrence relationships
+Final data: **3096 documents** with **71** and **43 co-occurrence relationships**
 
@@
 
-## Results: Important phenomena
+## Results
 
-* Emotion regulation and related mental health outcomes among top terms
-* Theoretically important themes: *neural*, *parenting*, and *stress*
-* Also several under-theorized concepts: *ADHD/CD*, *substance* use, *minority status*
-* Substantial correspondence between keywords and abstracts
-    + 75% of frequent terms from keywords also present in abstracts
-    + 89% of the frequent terms from abstracts present in keywords
-* *sex* was more frequent in the Abstracts: sex differences are regularly reported in Abstracts even if they are not mentioned in the keywords
-* *parenting* (keywords) was displaced by *mothers* (Abstracts): Parenting is often operationalized as mothering
-
-## Results: Co-occurrence
-
-Keywords:
-
-* Emotion regulation is a central construct to which other constructs are directly linked
-* Graph was sparse, with few interconnections between terms (fragmented literature?)
-
-Abstracts:
-
-* Emotion regulation and mental health-related outcomes formed central axis
-* Relevant terms connected to this axis, but not directly to emotion regulation
-* Only terms directly connected to emotion regulation were *neural*, *mothers*, *attachment* and *ptsd*
-* even sparser network
-
-## Discussion
-
-* Both analyses reflected some phenomena from theoretical literature
+* Both analyses reflected some constructs from theoretical literature
     + Particularly related to neurodevelopment and socialization
@@
     + This underlines the importance of research in this area
+* Substantial correspondence between keywords and abstracts, suggesting validity of method
+* Networks are sparse; few connections among constructs: fragmented literature
 
@@
 * Developmental disorders
-    + E.g., ADHD/CD and autism
 * Physical health (sic)
-    + sleep, sports, and disability status
 * External stressors
-    + bullying, stress, PTSD, abuse, violence, life events, historic events (e.g., earthquakes, war), parenting stress, and divorce.
 * Structural disadvantage
-    + minority status, discrimination, disability status, socio-economic status, adoption status, and sexual diversity
-    + Developmental disorders also relevant in this context, as neuroatypical individuals tend to experience social exclusion [@cappadociaBullyingExperiencesChildren2012]
-
-## Undertheorized themes contd.
-
 * Addictive behavior
-    + substance use and device use
 * Identity and moral development
-    + values and personality. 
 * Sexual development
-    + (biological) sex, puberty, sexual diversity, and romantic relationships
-
-Text mining systematic reviews can thus identify undertheorized themes
-
-## Structural findings
-
-Central axis of emotion regulation and mental health outcomes suggests that these phenomena are closely linked
-
-Sparse networks (fragmented literature)
-
-* Most phenomena directly linked with emotion regulation/mental health
-* Absence of terms suggests that they are not well-integrated in the literature
-* Sparser network for Abstractslikely reflects greater noise
-
-Substantial correspondence between both networks
-
-* Supports validity of the findings, suggests that automatic keyword extraction identifies relevant constructs
 
@@
 
-Results reflected familiar phenomena: Suggests validity of the method
-
-Results also revealed under-theorized phenomena: TMSR may complement theory and narrative reviews
-
-Implications for future empirical research:
-
-* Researchers typically rely on theory
-* Under-theorized phenomena may be overlooked
-* This study offers guidance regarding relevant phenomena to consider as confounders or contributing causes
-* Unembedded terms indicate potential knowledge gaps; promising areas of future research
-
-## Theoretical implications
-
-* Sparse graphs indicate fragmented literature
-* Important to generate an overarching theory of adolescent emotion regulation
-* First step in theory construction methodology is to identify relevant phenomena [@borsboomTheoryConstructionMethodology2020]
-* Present study thus serves as starting point for theory development
+* Empirical research relies on theory; under-theorized phenomena may be overlooked
+    + This study offers guidance for phenomena to consider as confounders/causes
+* Unembedded terms indicate promising areas of future research
+* Present study serves as starting point for theory development
 
@@
 
-* This study was more comprehensive than previous narrative reviews [cf. @bariolaChildAdolescentEmotion2011; @coe-odessEmergentEmotionsAdolescence2019]
+* More comprehensive than previous narrative reviews [cf. @bariolaChildAdolescentEmotion2011; @coe-odessEmergentEmotionsAdolescence2019]
     + Used systematic search and included much larger corpus
-* TMSR can include corpora of arbitrary size, and derive insights by transparant and reproducible procedures
+* TMSR can process samples of any size, derive insights by transparent and reproducible procedures
 
@@
 
-* These text mining techniques do not extract *meaning* from the literature
-* Analyses limited to keywords and abstracts
-    + Many full text articles are behind paywalls
-    + No standardized Application Programming Interface (API)
-* Comprehensive access to scientific publications is essential to all meta-scientific research
-* Recommend open access publishing and the development of a unified API for article retrieval
-* Subjective decisions were made throughout the analysis process
-    + creative license is inherent to inductive studies [@wagenmakersCreativityVerificationCyclePsychological2018]
-    + There are infinite possible ways to conduct exploratory analyses
+* These techniques do not extract *meaning* from the literature
+* No access to full text articles (paywalls)
+* Subjective decisions in analysis process [@wagenmakersCreativityVerificationCyclePsychological2018]
 
@@
 
-Text mining systematic reviews can identify theoretically relevant phenomena,
-and map potential associations
+Text mining systematic reviews can complement theory and narrative reviews
 
-* This illustrates validity of the method
-
-Results also revealed undertheorized themes
-
-* E.g., developmental disorders, physical health, external stressors, structural disadvantage, substance use, identity, moral, and
-sexual development
-
-Text mining systematic reviews thus complement theory and narrative reviews
+* Identify (undertheorized) relevant phenomena
+* Map potential associations
 
